### 2013-02-07 LaTeX/RhodiumConcl.tex
pushing up latex file structure

\section{Conclusion}
\label{conclusion}

If NATO had not intervened, the expected duration of the conflict would have been much shorter. But the rebels would have lost, so there is a trade-off.

### 2013-02-07 LaTeX/RhodiumIntro.tex
pushing up latex file structure

\section{The Politics of Third-Party Intervention}
\label{intro}

When do third parties decide to intervene in civil conflict? How does this intervention affect the outcome? These questions are motivated largely by recent events in North Africa and Southwest Asia. In particular, the intervention of coalition forces in the conflict between Libyan rebels and the government of Muammar Qaddafi presented us with a puzzle. In late spring 2011, the rebel militias were in dire shape; it appeared as if they were just trying to hold on until they received outside help. The rebels' dire straits indicated to Western leaders that their window of opportunity to remove Col. Qaddafi was narrowing.

On 17 March, 2011, the United Nations Security Council adopted Resolution 1973, which \href{http://www.un.org/News/Press/docs//2011/sc10200.doc.htm}{authorized} member states to undertake ``all necessary measures'' to protect Libyan civilians. Military operations involving air and naval forces began two days later. Almost exactly 7 months after international forces intervened, on October 20, Muammar Qaddafi was killed, effectively solidifying the rebel victory.

Was third-party intervention necessary for rebel victory? By how much did it change the expected duration of the conflict? In this paper we develop an agent-based model of civil war focused on three actors and two variables. Governments and rebels differ in their \emph{identity} (a one-dimensional scale that could be understood as any measure of identity over which groups conflict), and the outside actor is closer to one or the other of them. In the Libya case, international powers sided with the rebels. All three actors also have certain levels of \emph{strength}, which is allocated to each party independently of the others' allocations. The outcome of each round of conflict is probabilistic based on the relative power of each side, and eventually results in the total victory of one side when it controls the entire territory. We measure three outcome variables: the percent of rebel-controlled territory at the end of the conflict, the duration of the conflict, and whether the third party chose to intervene.

Specifically, we model the conflict as a ``gambler's ruin,'' where intervention can improve rebels' chances of winning each round, and therefore the whole conflict. Later in this section we discuss how our model relates to previous models of civil wars and insurgencies, as well as empirical evidence to support several of our assumptions. We present further details of our model in Section \ref{formal}. Section \ref{sims} discusses the results of our simulations. We find that intervention increases the chances of rebel success, but also increased the expected duration of the conflict. In Section \ref{libya} we return to the Libyan case to identify what leverage the model gives us in a counterfactual analysis. The paper concludes policy implications and a discussion of future steps in this research program in Section \ref{conclusion}.

### 2013-02-07 LaTeX/RhodiumLit.tex
pushing up latex file structure

\subsection{Previous Research on Third-Party Intervention}
\label{lit}

\begin{itemize}
	\item Third-party intervention on behalf of a rebel group is more likely to occur when there are ideological/ethnic linkages between rebel groups and actors in other countries (Carment, James \& Rowlands, 1997; Bryman et al., 2001; Salehyan, Gleditsch \& Cunningham, 2011) 
	% \pause
	\item Many studies show that third-party interventions in civil wars are associated with wars of longer duration (Balch-Lindsay \& Enterline, 2000; Elbadawi \& Sambanis, 2000; and Regan, 2002)
	% \pause
	\item Other studies suggest that biased third-party support increases the likelihood that a civil war will end in a victory by the supported group (Balch-Lindsay, Enterline \& Joyce, 2006; Mason, Weingarten \& Fett, 1999)
\end{itemize}

\subsection{Computational Models of Civil War}
\begin{itemize}
	\item Agent-Based Modeling (ABM) provides a bottom-up method for building complex systems
	% \pause
	\item A number of studies have used this technique in an attempt to build realistic computational models of civil war (Cederman \& Girardin, 2007; Cioffi-Revilla \& Rouleau, 2010; Weidmann \& Salehyan, 2010)
\end{itemize}

### 2013-02-08 LaTeX/RhodiumIntro.tex
file structure, few initial throughts

@@
-\section{The Politics of Third-Party Intervention}
+\section{Introduction}
 \label{intro}
 
-When do third parties decide to intervene in civil conflict?
-How does this intervention affect the outcome?
-These questions are motivated largely by recent events in North Africa and Southwest Asia.
-In particular, the intervention of coalition forces in the conflict between Libyan rebels and the government of Muammar Qaddafi presented us with a puzzle.
-In late spring 2011, the rebel militias were in dire shape; it appeared as if they were just trying to hold on until they received outside help.
-The rebels' dire straits indicated to Western leaders that their window of opportunity to remove Col.
-Qaddafi was narrowing.
+Mexico case: high levels of violence since 2008 but little effect on economic growth
 
-On 17 March, 2011, the United Nations Security Council adopted Resolution 1973, which \href{http://www.un.org/News/Press/docs//2011/sc10200.doc.htm}{authorized} member states to undertake ``all necessary measures'' to protect Libyan civilians.
-Military operations involving air and naval forces began two days later.
-Almost exactly 7 months after international forces intervened, on October 20, Muammar Qaddafi was killed, effectively solidifying the rebel victory.
-
-Was third-party intervention necessary for rebel victory?
-By how much did it change the expected duration of the conflict?
-In this paper we develop an agent-based model of civil war focused on three actors and two variables.
-Governments and rebels differ in their \emph{identity} (a one-dimensional scale that could be understood as any measure of identity over which groups conflict), and the outside actor is closer to one or the other of them.
-In the Libya case, international powers sided with the rebels.
-All three actors also have certain levels of \emph{strength}, which is allocated to each party independently of the others' allocations.
-The outcome of each round of conflict is probabilistic based on the relative power of each side, and eventually results in the total victory of one side when it controls the entire territory.
-We measure three outcome variables: the percent of rebel-controlled territory at the end of the conflict, the duration of the conflict, and whether the third party chose to intervene.
-
-Specifically, we model the conflict as a ``gambler's ruin,'' where intervention can improve rebels' chances of winning each round, and therefore the whole conflict.
-Later in this section we discuss how our model relates to previous models of civil wars and insurgencies, as well as empirical evidence to support several of our assumptions.
-We present further details of our model in Section \ref{formal}.
-Section \ref{sims} discusses the results of our simulations.
-We find that intervention increases the chances of rebel success, but also increased the expected duration of the conflict.
-In Section \ref{libya} we return to the Libyan case to identify what leverage the model gives us in a counterfactual analysis.
-The paper concludes policy implications and a discussion of future steps in this research program in Section \ref{conclusion}.
+Two schools of thought on civil war and economic development: ``war renewal'' and ``war ruin'' schools

### 2013-02-08 LaTeX/RhodiumLit.tex
file structure, few initial throughts

@@
-\subsection{Previous Research on Third-Party Intervention}
+\subsection{Literature Review}
 \label{lit}
@@
 \begin{itemize}
-	\item Third-party intervention on behalf of a rebel group is more likely to occur when there are ideological/ethnic linkages between rebel groups and actors in other countries (Carment, James \& Rowlands, 1997; Bryman et al., 2001; Salehyan, Gleditsch \& Cunningham, 2011)
-	% \pause
-	\item Many studies show that third-party interventions in civil wars are associated with wars of longer duration (Balch-Lindsay \& Enterline, 2000; Elbadawi \& Sambanis, 2000; and Regan, 2002)
-	% \pause
-	\item Other studies suggest that biased third-party support increases the likelihood that a civil war will end in a victory by the supported group (Balch-Lindsay, Enterline \& Joyce, 2006; Mason, Weingarten \& Fett, 1999)
+	\item varying hypotheses about the effect of war on economic development, war ruin v war renewal hypotheses
+	\item 
 \end{itemize}
-
-\subsection{Computational Models of Civil War}
-\begin{itemize}
-	\item Agent-Based Modeling (ABM) provides a bottom-up method for building complex systems
-	% \pause
-	\item A number of studies have used this technique in an attempt to build realistic computational models of civil war (Cederman \& Girardin, 2007; Cioffi-Revilla \& Rouleau, 2010; Weidmann \& Salehyan, 2010)
-\end{itemize}

### 2013-02-08 R/setup.R

@@ -1,7 +1,7 @@
 # Clearing workspace
 rm(list=ls())
 
-# SetDisting working directory
+# Setting working directory
 if(Sys.info()["user"]=="janus829")
 {pathMain="~/Desktop/Research/Rhodium/R";
 	pathGraphics="~/Dropbox/Research/Rhodium/Graphics";
@@ -11,3 +11,4 @@ if(Sys.info()["user"]=="janus829")
 library(ggplot2)
 theme_set(theme_bw())
 library(reshape)
+library(foreign)

### 2013-02-26 LaTeX/RhodiumIntro.tex
added notes

@@
 
-Two schools of thought on civil war and economic development: ``war renewal'' and ``war ruin'' schools
+Mexico facing serious internal political stability (civil violence, civil war...) yet this has little effect on economic growth as of yet.
+When should we expect to see the adverse effects of civil war manifest themselves in terms of lower economic growth?
+
+Cases apart from Mexico:
+Pakistan - NWFP
+India
+Israel
+Russia - Chechnya
+Columbia - FAARC

### 2013-10-03 LaTeX/Abstract.tex
mpsa abstract

Within the conflict literature there has been much disagreement about the relationship between civil wars, natural resources, and state economic performance. We find that this disagreement results from not accounting for the spatial disaggregation of conflict events within a country.  Other recent work has suggested that the location of civil conflicts within a state can lead to disparate outcomes in terms of conflict duration, state response, and the probability of rebel victory.  Drawing on these two literatures, we develop a theory to explain the economic consequences of civil conflict.

Our theoretical model states that the economic impacts of civil conflict is contingent on the conflict's location relative to major economic and labor resources within a state.

We use subnational data on the spatial distribution of conflict, resources, and infrastructure to test the long-term impact of domestic conflict on state economic performance. To estimate the spatial distribution of conflict we use data from the PRIO Armed Conflict Location and Event Data and supplement this source with GDELT in more recent years. We combine the conflict location data with geospatial data on economic centers, natural resource locations, and infrastructure grids within the country to generate country-level spatial variables that approximate how far each conflict is from centers of interest for the government. We then use a hierarchical Bayesian model to estimate the effect of our spatially constructed variables on economic performance. By doing so, we are able to resolve some of the tensions in the literature regarding the relationship between economic performance and civil wars.

### 2013-10-03 LaTeX/Abstract.tex
min edit

@@
 
-Our theoretical model states that the economic impacts of civil conflict is contingent on the conflict's location relative to major economic and labor resources within a state.
+Our theoretical model states that the economic impact of civil conflict is contingent on the conflict's location relative to major economic and labor resources within a state.
 

### 2014-03-12 LaTeX/RhodiumConcl.tex
Model updates, slight outline updates

@@
 
-If NATO had not intervened, the expected duration of the conflict would have been much shorter. But the rebels would have lost, so there is a trade-off.
+\begin{itemize}
+	\item Note that sub-state conflict location may have implications for contagion.
+Are regional economic consequences of civil war not a function of civil war existence but proximity of the conflict to cities or resources in neighboring states?
+\end{itemize}

### 2014-03-12 LaTeX/RhodiumEmp.tex
Model updates, slight outline updates

\section{Empirics}
\label{empirics}

\begin{itemize}
	\item Note data aggregation choices.  Multiple conflicts in one country?
	\item Note dropping interstate conflict.
	\item Describe city data collection.
\end{itemize}

### 2014-03-13 LaTeX/RhodiumConcl.tex
mods to outline

@@
 
-\begin{itemize}
-	\item Note that sub-state conflict location may have implications for contagion.
+Contributed to our understanding of why some civil conflicts impact economic performance more severely than others using a novel spatial approach.
+
+Note that sub-state conflict location may have implications for contagion.
 Are regional economic consequences of civil war not a function of civil war existence but proximity of the conflict to cities or resources in neighboring states?
-\end{itemize}

### 2014-03-13 LaTeX/RhodiumEmp.tex
mods to outline

@@
 
-\begin{itemize}
-	\item Note data aggregation choices.  Multiple conflicts in one country?
-	\item Note dropping interstate conflict.
-	\item Describe city data collection.
-\end{itemize}
+\subsection{Data and Sample}
+
+Conflict data: comes from PRIO Conflict Location Even Data
+
+	Note data aggregation choices.  Multiple conflicts in one country?
+
+	Note dropping interstate conflict.
+
+City data: Collection of major population centers by year
+
+World Bank data: Econ indicators
+
+Variables: Determined distance between conflicts in a year and city centers. then calculcate min distance to determine effect on conflict
+
+\subsection{Sample and Estimation Method}
+
+Sample: Only country-years undergoing a civil conflict. Coverage restricted to 1989-2008.
+
+Measured as a random effects model with country effects
+
+\subsection{Results}
+
+Maybe we should begin this section by showing the distribution of econ performance among the cntry-years in the dataset.
+this would illustrate that there is noticeable variation in economic performance to explain.
+
+Conflicts occuring more proximate to major cities have stronger adverse effects on economic performance than those farther away.

### 2014-03-13 LaTeX/RhodiumIntro.tex
mods to outline

@@
 
-Mexico case: high levels of violence since 2008 but little effect on economic growth
+Puzzle: Why do some conflicts have immediate impacts on a country's economy while others that fester for decades have little to no impact.
 
+	Mexico case: high levels of violence since 2008 but little effect on economic growth.
 Mexico facing serious internal political stability (civil violence, civil war...) yet this has little effect on economic growth as of yet.
@@
 		Columbia - FAARC
+
+Background: Show charts of Mexico and/or India's growth in GDP per capita versus number/duration of conflicts
+
+Spatial Dist Hypothesis: Location of conflicts to major cities and capitals determine effect of civil conflict on economic performance

### 2014-03-13 LaTeX/RhodiumLit.tex
Model updates, slight outline updates
mods to outline

@@
 
-\begin{itemize}
-	\item varying hypotheses about the effect of war on economic development, war ruin v war renewal hypotheses
-	\item 
-\end{itemize}
+varying hypotheses about the effect of war on economic development, war ruin v war renewal hypotheses
+
+literature on endogeneity of conflict and economic performance (sambanis 2001, worldbank 2003)
+
+literature on sub-state determinants of conflict and outcome (pierskala hollenbach 2013)
+
+literature on application of spatial variables to studying conflict and how it hasnt captures what we are doing at the sub-national level with city data

### 2014-03-13 LaTeX/RhodiumTheory.tex
mods to outline

\section{Theory}
\label{theory}

Begin this section by showing a chart that tracks the effect of conflict duration on economic performance. The purpose of the chart would be to show that long running conflicts are not permanently depressing economic performance.

Laying out our hypothesis in a formal way

	Use the case study of Mexico/India as a way to explain our hypothesis:

	Or instead of relying on just one case study maybe we can walk through the example for a number of countries.

### 2014-03-13 LaTeX/RhodiumEmp.tex
more mods

@@
 \subsection{Data and Sample}
+
+Dependent variable: World Bank data GDP per capita growth
+
+Key Independent variables:
 
@@
 	City data: Collection of major population centers by year
-
-World Bank data: Econ indicators
 
@@
 
-Maybe we should begin this section by showing the distribution of econ performance among the cntry-years in the dataset.
-this would illustrate that there is noticeable variation in economic performance to explain.
+Conflicts occuring more proximate to major cities have stronger adverse effects on economic performance than those farther away.
 
-Conflicts occuring more proximate to major cities have stronger adverse effects on economic performance than those farther away.
+Use simulations to determine substantive effects

### 2014-03-13 LaTeX/RhodiumIntro.tex
more mods

--- 2013-02-26 LaTeX/RhodiumIntro.tex
@@
 
-Mexico case: high levels of violence since 2008 but little effect on economic growth
+Puzzle: Why do some conflicts have immediate impacts on a country's economy while others that fester for decades have little to none.
 
+	Mexico case: high levels of violence since 2008 but little effect on economic growth.
 Mexico facing serious internal political stability (civil violence, civil war...) yet this has little effect on economic growth as of yet.
@@
 		Columbia - FAARC
+
+Spatial Dist Hypothesis: Location of conflicts to major cities and capitals determine effect of civil conflict on economic performance.
+thesis: conflicts only significantly dampens economic performance if they are a threat to major population centers.
+conflicts isolated in sparsely populated territories of the country have little to no effect on the whole.

### 2014-03-13 LaTeX/RhodiumLit.tex
more mods

@@
 
-literature on endogeneity of conflict and economic performance (sambanis 2001, worldbank 2003)
-
 literature on sub-state determinants of conflict and outcome (pierskala hollenbach 2013)
 
-literature on application of spatial variables to studying conflict and how it hasnt captures what we are doing at the sub-national level with city data
+	explain how what has been done in the spatial conflict literature and even the sub-nat/spat literature does not capture what we have done in this paper
+
+% literature on endogeneity of conflict and economic performance (sambanis 2001, worldbank 2003)
+
+% 	do we want to wade in to the endogeneity debate?
+i'm not sure we do that's why i've commented this out temporarily.
+seems to me our life would be made easier if we just tied ourselves to teh literature that puts econ growth as the dv nad conflict as the iv.
+u probably know better than me if this position is untenable.

### 2014-03-13 LaTeX/RhodiumTheory.tex
more mods

@@
 
-Begin this section by showing a chart that tracks the effect of conflict duration on economic performance.
+Begin this section by showing a chart that tracks the effect of conflict duration on economic performance in the aggregate.
 The purpose of the chart would be to show that long running conflicts are not permanently depressing economic performance.
+
+thesis: conflicts only significantly dampens economic performance if they are a threat to major population centers.
+conflicts isolated in sparsely populated territories of the country have little to no effect on the whole.
 
@@
 	Or instead of relying on just one case study maybe we can walk through the example for a number of countries.
+
+	maps: would be cool if maybe we could show the progression of a certain conflict across time and space.
+according to our theory what we would expect to happen as a conflict gets farther away from population centers is for econ performnace to improve.
+on the other hand, a conflict that moves closer and closer to population centers should lead to declined in econ performance.
+
+End with a chart to show the distribution of econ performance among conflict-cntry-years to illustrate that there is noticeable variation in economic performance to explain.
+ending with this might help us lead into the empirics section and
+
+	seems like the density plot you've already made in the models.R file highlights that the gdp growth var is kind of normal centered at zero which is good for us

### 2014-03-20 LaTeX/RhodiumIntro.tex
added duration vars

@@
 Puzzle: Why do some conflicts have immediate impacts on a country's economy while others that fester for decades have little to none.
+
+	Negative cases (cases where there was civil war but no major declines in economic growth)
 
@@
 	Cases apart from Mexico:
+
 			Pakistan - NWFP
@@
 
+	Positive cases
+
+			Syria
+			Sudan
+			Congo
+			Maybe European Countries
+
+	To tell the stories from these cases we should have a descriptive paragraph talking about a couple of cases.
+Then we should construct a chart that shows just two countries one from the negative case bucket and one from the positive case bucket where we have GDP per capita or GDP per capita growth on the Y-Axis and time on the X-axis.
+We can have separate charts for each country so that we can take into acount varying times in conflict periods.
+Then have another paragraph describing the plot.
+
+Current literature has focused on examining the effect of conflict on economic growth at the national level.
+Additionally, much of the literature has focused on the effect of declines in economic growth on the incidence of civil war.
+We will argue that the analyses presented to date have been conducted at the wrong level.
+Analyzing the effect of civil conflict on economic growth needs to be done at a subnational level.
+
 Spatial Dist Hypothesis: Location of conflicts to major cities and capitals determine effect of civil conflict on economic performance.

### 2014-03-20 R/Databuilder/04 - DistanceCalc.R

@@ -27,6 +27,12 @@ prioAC=prioAC[which(prioAC$YEAR %in%  1989:2008),]
 ##################################################################
 
 ##################################################################
+# calc duration
+prioAC$startYr1=numSM(substr(charSM(prioAC$Startdate),1,4))
+prioAC$startYr2=numSM(substr(charSM(prioAC$StartDate2),1,4))
+##################################################################
+
+##################################################################
 # Calc distances from conflict sites
 prioAC$cname[prioAC$Location=="Ethiopia"] <- "ETHIOPIA"
 prioAC$cname[prioAC$Location=="Rwanda"] <- "RWANDA"
@@ -68,7 +74,9 @@ prioAC$capDist <- minDist(prioAC$Latitude, prioAC$Longitude, prioAC$cname, prioA
 ##################################################################
 # Aggregate to the country-year
 prioAC$territorial <- as.numeric(prioAC$Incomp%in%c(1,3))
-prioAC <- prioAC[,c("ID","Incomp","Int","CumInt","territorial","Conflict.area","Type","StartDate2","EpEndDate","Region","minDist","inRadius","capDist","cname","YEAR")]
+prioAC <- prioAC[,c("ID","Incomp","Int","CumInt","territorial","Conflict.area",
+	"Type","Region","minDist","inRadius","capDist",
+	"cname","YEAR", 'startYr1', 'startYr2')]
 prioAC$ccode=panel$ccode[match(prioAC$cname,panel$cname)]
 prioAC$cyear=paste0(prioAC$ccode, prioAC$YEAR)
 prioAC=prioAC[prioAC$Type!=2,]
@@ -78,8 +86,19 @@ aggAll=summaryBy(. ~ cyear, data=prioAC, FUN=c(mean,sum,min,max))
 
 # Create country year
 yData=aggAll[ ,c('cyear', 'YEAR.mean', 'ccode.mean',
-                    'Int.mean', 'Int.max', 'CumInt.mean', 'CumInt.max', 'Type.mean','territorial.max','Conflict.area.mean','Conflict.area.max','Region.mean', 'minDist.mean', 'minDist.min', 'inRadius.sum', 'inRadius.max', 'capDist.min') ]
+                    'Int.mean', 'Int.max', 'CumInt.mean', 'CumInt.max', 'Type.mean',
+                    'territorial.max','Conflict.area.mean','Conflict.area.max',
[…]

### 2014-03-20 LaTeX/RhodiumTheory.tex
added duration vars
manuscript edits

@@
 
-Begin this section by showing a chart that tracks the effect of conflict duration on economic performance in the aggregate.
-The purpose of the chart would be to show that long running conflicts are not permanently depressing economic performance.
-
 thesis: conflicts only significantly dampens economic performance if they are a threat to major population centers.
 conflicts isolated in sparsely populated territories of the country have little to no effect on the whole.
+point to the imai & weinstein paper as an example of this.
 
@@
 
-	Use the case study of Mexico/India as a way to explain our hypothesis:
-
-	Or instead of relying on just one case study maybe we can walk through the example for a number of countries.
-
-	maps: would be cool if maybe we could show the progression of a certain conflict across time and space.
-according to our theory what we would expect to happen as a conflict gets farther away from population centers is for econ performnace to improve.
-on the other hand, a conflict that moves closer and closer to population centers should lead to declined in econ performance.
+	Columbia +/- (BR), Pakistan - (SM), Philippines (BR), Israel (SM), Chad (BR), Democratic Republic of Congo (SM)
+	(  + = Case where conflict was close to center and economy declined; - = Case where conflict far from center and no effect on econ )
 

### 2014-03-20 LaTeX/RhodiumLit.tex
Added inflation

@@
 u probably know better than me if this position is untenable.
+
+\cite{imai:weinstein:2000} explored the differing economic impacts of civil war by distinguinshing between those conflicts cover larger or smaller geographic areas.
+Using a pooled OLS regression, they find that there is a negative correlation between geographical spread and the decade average of economic growth for each country.
+However, in subsequent simulations that account for estimation and fundamental uncertainty,

### 2014-03-20 R/models.R

@@ -4,6 +4,7 @@ if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
 # Load conflict country year data
 setwd(pathData)
 load('combinedData.rda')
+library(plm)
 
 yData$upperincome=0
 yData$upperincome[which(yData$income_l0 %in% c('High income: OECD', 'High income: nonOECD'  ) )] = 1
@@ -26,8 +27,10 @@ yData <- yData[order(yData$year),]
 
 ## MODELS FOR GDP GROWTH PER CAPITA (ANNUAL %)
 ####################################################################################################################
-model1 <- lmer(NY.GDP.PCAP.KD.ZG_l0 ~ upperincome + Int.max + lnArea + lnminDist.min + territorial.max + (1|ccode), data=yData)
+model1 <- lmer(NY.GDP.PCAP.KD.ZG_l0 ~ upperincome + Int.max + lnArea + lnminDist.min + territorial.max + durSt1max + NY.GDP.DEFL.KD.ZG_l1 + (1|ccode) + (1|year), data=yData)
 summary(model1)
+model1FE <- lm(NY.GDP.PCAP.KD.ZG_l0 ~ upperincome + Int.max + lnArea + lnminDist.min + territorial.max + durSt1max + NY.GDP.DEFL.KD.ZG_l1 + as.factor(ccode), data=yData)
+summary(model1FE)
 
 resid <- resid(model1)
 resid <- resid+(model1@frame$lnminDist.min*1.3566)
@@ -47,13 +50,17 @@ abline(lm(resid~model1@frame$lnminDist.min),lty=1,col="red",lwd=3)
 ## MODELS FOR GDP GROWTH (ANNUAL %)
 ####################################################################################################################
 plot(density(yData$NY.GDP.MKTP.KD.ZG_l0,na.rm=T))
-
+names(yData)
 # yData$GDP_transform_l0 <- sqrt(abs(yData$NY.GDP.MKTP.KD.ZG_l0))
 # yData$GDP_transform_l0 <- yData$GDP_transform_l0 * ifelse(yData$NY.GDP.MKTP.KD.ZG_l0<0,-1,1)
 # plot(density(yData$GDP_transform_l0,na.rm=T))
 
[…]

### 2014-03-23 LaTeX/RhodiumTheory.tex
Added some theory about Colombia.

@@
 
-thesis: conflicts only significantly dampens economic performance if they are a threat to major population centers.
+% thesis: conflicts only significantly dampens economic performance if they are a threat to major population centers.
 conflicts isolated in sparsely populated territories of the country have little to no effect on the whole.
-point to the imai & weinstein paper as an example of this.
+point to the imai weinstein paper as an example of this.
 
@@
 
-	Columbia +/- (BR), Pakistan - (SM), Philippines (BR), Israel (SM), Chad (BR), Democratic Republic of Congo (SM)
-	(  + = Case where conflict was close to center and economy declined; - = Case where conflict far from center and no effect on econ )
+The guerilla group Fuerzas Armadas Revolucionarios de Colombia (FARC) appears to have to internalized these lessons.
+In 1998 and 1999, the organization moved its violent operations from mostly rural areas of Colombia into major cities and near to the capital (Petras and Brescia 2000).
+This coincided with economic strain caused by the implementation of an IMF/World Bank structural readjustment program.
+However, the timing was likely not coincidental.
+FARC advocates a number of political and economic reforms and chooses targets strategically related to these objectives.
+
+Forbes magazine, reporting on peace talks between FARC guerillas and the Colombian government in 2012, wrote: 
+\begin{quote}FARC's strategy and [beliefs have] always been to make economic pressure on both, multinational companies and the Colombian government.
+This has been done by attacking oil and natural gas infrastructure affecting companies such as Pacific Rubiales Energy, Oxy and Ecopetrol.
+For non-fuel related international companies with subsidiaries in Colombia, such as Goodyear, Nestle, Microsoft, Toyota, among others, FARC’s modus operandi was mainly racketeering, kidnappings and extortion.
+(Flannery 2012)\end{quote}
+By targeting economic centers and resource infrastructure, FARC can strain Colombia's economy, frighten investors, and bolster support from poor and rural workers sensitive to wealth disparity in the country.
+Rabasa and Chalk (2001) identify a three-pronged strategy pursued by FARC in the 1990s: to consolidate power in coca-growing regions, to conduct military operations in economically valuable areas, and to isolate major cities from the rest of the country by limiting communication and travel between them.
+
+%	Columbia +/- (BR), Pakistan - (SM), Philippines (BR), Israel (SM), Chad (BR), Democratic Republic of Congo (SM)
+%	(  + = Case where conflict was close to center and economy declined; - = Case where conflict far from center and no effect on econ )
 

### 2014-03-26 LaTeX/RhodiumTheory.tex
Added some theory. Added map making code
Don’t use the map-making stuff yet.  It doesn’t look so great.

@@
 
-Laying out our hypothesis in a formal way
+We suspect that substate factors will determine the economic impacts of civil conflict.
+While lootable resources are often pointed to as sources of funding for rebel groups, these same resources are often critical to state economic performance.
+The loss of safe access to these resources due to internal conflict should adversly affect a state's economy.
+Companies that rely on the extraction of resources may find themselves unable to access those resources if armed conflict is proximately located to the resource sites.
+Therefore, we expect state economic performance to be inversely related to the distance from conflict zones to valuable resources.
 
-The guerilla group Fuerzas Armadas Revolucionarios de Colombia (FARC) appears to have to internalized these lessons.
+Other resources are also valuable to a state's ability to conduct business.
+In particular, citizens must be able and willing to participate in commerce.
+When major population centers are threatened by violence, residents will be less likely to engage in economically productive activities.
+Violence near major population centers not only threatens residents directly, but impedes business by threatening trade between the population center and other cities or rural areas.
+For this same reason, violence near important transporation hubs such as airports and sea ports should threaten business.
+
+Finally, the perception of violence near major cities and resource centers should negatively impact foreign investment.
+Investors will react negatively to news that violence is occuring near major cities and resources.
+Investment is generally contingent on the expectation of a stable labor base and, sometimes, reliable access to resources.
+Conflicts that appear to threaten these, whether they do or not, should correspond to a decrease in foreign investment.
+
+These hypotheses do not seem unknown to armed actors.
+The guerilla group Fuerzas Armadas Revolucionarios de Colombia (FARC) appears to have to internalized these mechanisms.
 In 1998 and 1999, the organization moved its violent operations from mostly rural areas of Colombia into major cities and near to the capital (Petras and Brescia 2000).

### 2014-03-26 R/conflictMaps.R

@@ -1,0 +1,40 @@
+if(Sys.info()["user"]=="janus829"){source('/Users/janus829/Desktop/Research/Rhodium/R/setup.R')}
+if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
+
+library(cshapes)
+
+# Load conflict country year data
+setwd(pathData)
+load('combinedData.rda')
+load("cityTotPopLatLongvFinal.rda")
+prio <- read.csv("PRIO - Conflict Site Data/ConflictSite 4-2010_v3 Dataset.csv",stringsAsFactors=F)
+source(paste0(pathMain,"/geodistance.R"))
+
+fYrCty$cname <- toupper(countrycode(fYrCty$cname,"country.name","country.name"))
+prio$Conflict.territory <- toupper(countrycode(prio$Conflict.territory,"country.name","country.name"))
+
+plotConflict <- function(cname, threshold=1)
+{
+  worldmap <- cshp(date=as.Date("1990-01-01"),useGW=F)
+
+  ccode <- countrycode(cname,"country.name","cown")
+  country.shape <- worldmap[worldmap$COWCODE==ccode,]
+  # gradient <- colorRampPalette(c("#ffffcc","#c7e9b4","#7fcdbb","#41b6c4","#1d91c0","#225ea8","#0c2c84"))
+  # years <- sort(prio$Year[prio$Conflict.territory==cname])
+  # years <- years-min(years)
+  
+  growth <- data.frame(low=ifelse(yData$NY.GDP.PCAP.KD.ZG_l0[yData$ccode==ccode]<=1,"#d53e4f","#3288bd"),year=yData$year[yData$ccode==ccode])
+  newprio <- na.omit(prio[prio$Conflict.territory==cname,])
+  newprio <- merge(newprio,growth,by.x="Year",by.y="year",all.x=T,all.y=F,sort=F)
+  
+  par(mfrow=c(1,2))
+  plot(country.shape)
+  points(fYrCty$cleanLong[fYrCty$cname==cname], fYrCty$cleanLat[fYrCty$cname==cname], pch=16)
+  points(newprio$Longitude,newprio$Latitude, col=as.character(newprio$low), pch=16)
[…]

### 2014-03-26 R/models.R

@@ -20,6 +20,7 @@ yData$Int.max <- yData$Int.max-1
 yData$intPerKm <- yData$Int.max/yData$lnArea
 yData$USA <- yData$ccode==2
 yData$coldwar <- yData$year<1991
+yData$BX.KLT.DINV.CD.WD <- 
 
 yData <- yData[order(yData$year),]
 ####################################################################################################################

### 2014-03-27 LaTeX/RhodiumLit.tex
Added a little theory.  Just syncing for the hell of it

--- 2014-03-13 LaTeX/RhodiumLit.tex
@@
 u probably know better than me if this position is untenable.
+
+\cite{imai:weinstein:2000} explored the differing economic impacts of civil war by distinguinshing between those conflicts cover larger or smaller geographic areas.
+Using a variety of regression techniques, they find that there is a negative correlation between geographical spread of conflict and the decade average of economic growth for each country.
+Widespread conflicts, they argue, are more likely to result in damage to infrastructure, divestment from normal state spending, and capital flight.
+However, in subsequent simulations that account for estimation and fundamental uncertainty, the authors show that these results are uncertain and should be interpreted with caution.

### 2014-03-27 LaTeX/RhodiumTheory.tex
Added a little theory.  Just syncing for the hell of it

@@
 Investment is generally contingent on the expectation of a stable labor base and, sometimes, reliable access to resources.
-Conflicts that appear to threaten these, whether they do or not, should correspond to a decrease in foreign investment.
+Conflicts that appear to threaten these, whether they do or not, should correspond to a decrease in foreign investment.\footnote{While we intend to test each of these hypotheses carefully, our project in its current form addresses only the second hypothesis - the effect of conflict distance from city centers on aggregate state economic performance.
+Future iterations of this paper will also include tests of the remaining hypotheses using foreign investment, economic growth, and domestic investment as dependent variables.}
+
+While these hypotheses may resemble those of \cite{imai:weinstein:2000}, ours differs somewhat in the hypothesized mechanism through which conflict affects economic performance.
+While we do not disagree that the spread of a conflict could impact state economic prospects, we argue that conflict area is not necessary for adverse economic performance.
+Conflict area is only one possible proxy for overall destructiveness.
+However, conflicts with smaller spatial areas can be similarly disruptive if they are centered near (and impede access to) those resources outlined above.
+In fact, we feel measures of proximity rather than spread are more appropriate to test the hypothesis that conflict obstucts vital economic activity.
 

### 2014-03-28 LaTeX/RhodiumLit.tex

--- 2014-03-13 LaTeX/RhodiumLit.tex
@@
 u probably know better than me if this position is untenable.
+
+\cite{collier:1999} identifies five avenues through with civil conflict can impede economic performance: through the \textit{destruction} of resources, through \textit{disruption} of social and economic activity, through \textit{diversion} of resources to the war effort, through \textit{dissaving}, and through \textit{portfolio substition} or divestment.
+Of course, these mechanisms are related to one another; portfolio substitution may be exacerbated by the destruction of resources or the distruption of socioeconomic activity.
+Overall, Collier finds that civil wars correspond to a 2.2 percent decrease in annual economic growth.
+While he suspects that the impact will differ across economic sectors, reliable and disaggregated data was not available to test this hypothesis thoroughly.
+However, preliminary evidence for this is found in their analysis of the National Accounts data of Uganda before, during, and after its civil war.
+
+Instead of disaggregating economic outcomes, \cite{imai:weinstein:2000} instead disaggregate conflict itself.
+They distinguish between those conflicts that cover larger or smaller geographic areas and hypothesize that larger conflicts (in terms of geographical spread) will result in worse economic performance.
+Using a variety of regression techniques, they find that there is a negative correlation between the geographical spread of conflict and the decade average of economic growth for each country.
+Widespread conflicts, they argue, are more likely to result in damage to infrastructure, divestment from normal state spending, and capital flight.
+However, in subsequent simulations that account for estimation and fundamental uncertainty, the authors show that these results are uncertain and should be interpreted with caution.

### 2014-03-28 LaTeX/RhodiumLit.tex
Literature updates

@@
 
+\subsubsection{Civil War $\rightarrow$ Economic Performance}
+
 \cite{collier:1999} identifies five avenues through with civil conflict can impede economic performance: through the \textit{destruction} of resources, through \textit{disruption} of social and economic activity, through \textit{diversion} of resources to the war effort, through \textit{dissaving}, and through \textit{portfolio substition} or divestment.
@@
 However, in subsequent simulations that account for estimation and fundamental uncertainty, the authors show that these results are uncertain and should be interpreted with caution.
+
+That civil wars negatively impact economic performance, while in line with the ``war ruin'' hypothesis, runs counter to the ``war renewal'' hypothesis.
+Some scholars have argued that wars, international wars in particular, can spur economic development \citep{}.
+The prevailing wisdom with regard to civil war, however, is that outcomes of this nature are the exception rather than the rule.
+In a test of economic and social determinants of post-conflict recovery in the context of civil war, \cite{kang:meernick:2005} find that these conflicts can lead, under different conditions, to either rapid or stagnant economic recovery.
+They conclude that the long-term economic impacts of civil war are largely dependent on post-war governance and foreign assistance.
+They also find, perhaps unsuprisingly, that aggregate estimates of conflict destructiveness are negatively correlated with long-term growth.
+
+\subsubsection{Economic Performance $\rightarrow$ Civil War}
+
+Much work has been done on the causal effects of economic performance on civil war.
+Indeed, there is likely an endogenous relationship between economic performance and civil war; each exacerbates the other.
+While our work here sidesteps this argument by focusing exclusively on observations of civil war, we will briefly review the relevant literature here.
+In a report for the World Bank by \cite{collier:etal:2003}, the authors describe what they term the \textit{conflict trap}.
+States that find themselves in the \textit{conflict trap} are those that have experienced civil war with, are subsequently affected by its economic and social consequences, and are therefore more likely to experience further civil conflict.
+During civil wars, resources are diverted from productive economic activity to destructive activity.
+These diverted resources act to stall progress during the conflict and are often used to destroy the infrastructure necessary for growth afterwards.
+These changes to economic performance, as well as structural changes to the economy itself, make the resurgence of war more likely.
+In accord with this theory, \cite{fearon:laitin:2003} aruge that poor economic growth is the primary condition conducive for civil war.
+More specifically, they believe that strong economic growth proxies for robust governance and that states with low GDP growth likely have infrastructures that are unable to implement counterinsurgent policies.
+In an effort to parse out the causal effect of economic growth shocks on civil war, \cite{miguel:elal:2004} instrument income growth with rainfall.
+They find that rainfall is strongly correlated with income in sub-Saharan Africa, a region also prone to civil conflict in recent decades.
+Using a two-stage estimation approach, they find that rainfall, their exogenous instrument for income, is positively correlated with the likelihood of civil war.
+
+More recent work has attempted to assessthe

### 2014-03-28 LaTeX/Abstract.tex
mpsa abstract submitted
pushing stuff

@@
-Within the conflict literature there has been much disagreement about the relationship between civil wars, natural resources, and state economic performance.
+% Within the conflict literature there has been much disagreement about the relationship between civil wars, natural resources, and state economic performance.
 We find that this disagreement results from not accounting for the spatial disaggregation of conflict events within a country.
@@
 
-Our theoretical model states that the economic impact of civil conflict is contingent on the conflict's location relative to major economic and labor resources within a state.
+% Our theoretical model states that the economic impacts of civil conflict is contingent on the conflict's location relative to major economic and labor resources within a state.
 
-We use subnational data on the spatial distribution of conflict, resources, and infrastructure to test the long-term impact of domestic conflict on state economic performance.
+% We use subnational data on the spatial distribution of conflict, resources, and infrastructure to test the long-term impact of domestic conflict on state economic performance.
 To estimate the spatial distribution of conflict we use data from the PRIO Armed Conflict Location and Event Data and supplement this source with GDELT in more recent years.
@@
 By doing so, we are able to resolve some of the tensions in the literature regarding the relationship between economic performance and civil wars.
+
+% Version submitted to MPSA:
+Within the conflict literature there has been much disagreement about the relationship between civil wars, natural resources, and state economic performance.
+We find that this disagreement results from not accounting for the spatial disaggregation of conflict events within a country.
+
+Our theoretical model states that the economic impact of civil conflict is contingent on the conflict's location relative to major economic and labor resources within a state.
+
+We use subnational data on the spatial distribution of conflict, resources, and infrastructure to test the long-term impact of domestic conflict on state economic performance.
+To estimate the spatial distribution of conflict we use data from the PRIO Armed Conflict Location and Event Data.
+We combine the conflict location data with geospatial data on economic centers, natural resource locations, and infrastructure grids to generate spatial variables that approximate how far each conflict is from centers of interest.
+We then use a hierarchical Bayesian model to estimate the effect of the spatial variables on economic performance.
+By doing so, we are able to resolve some of the tensions in the literature regarding the relationship between economic performance and civil wars.

### 2014-03-28 LaTeX/RhodiumEmp.tex
manuscript edits
pushing stuff

@@
 
-Dependent variable: World Bank data GDP per capita growth
+To measure economic performance we use annual percent change in GDP, which we collect from the World Development Indicators at the World Bank.
+We choose to focus on year over change in GDP because we expect conflicts proximate to major cities
+to lead to reductions in growth not changes in levels.\footnote{Alternative measures of economic performance would have included changes in FDI inflows or changes in GDP per capita, in using either of these measures are results remain relatively the same.} Unlike much of the extant literature in constructing our dependent variable we focus on year over change instead of a ten year average.
+We believe this approach to be superior because it allows us to estimate the direct effect of the conflict on economic performance in that year.
+A ten-year average approach might hide important variation in our dependent variable that can be explained by the proximity of conflict to economic centers.
+
+Our key independent variable on the location of conflicts come from the PRIO Conflict Site Dataset.
+This dataset contains geo-referenced armed conflict events from 1989 to 2008.\footnote{We only include examine the effect of internal armed conflicts.} A downside of this geo-referenced database is that every conflict-year is assigned a circular conflict zone, which leads to the dataset reporting that the conflict is covering more territory than actually affected.
+Crafting a more specfic approach to the spread of conflict would, however, eliminate important cases from our analysis.
+In total this dataset provides us with almost 800 geo-referenced conflict-year cases.
+
+The key theory that we advance here is that the effects of conflict on economic performance are conditional on the proximity of those conflicts to major city centers.
+Thus a key part of the research here was determining major city centers by year.
+The only data source we found with enough geographical and temporal coverage on major cities was The World Alamanac.
+To gather data from these textbooks we hired several undergraduate students to code the major cities by country for each year of the Almanac from 1989 to 2008.
+Major cities are classified as those that have relatively large shares of a country's population and/or are economic centers.
+On average, for each country at least three major cities are identified in each year from 1989 to 2008.
+In figure \ref{fig:CityConfMap}, we show the geographic distribution of conflicts and cities.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=.9/textwidth]{CityConfMap-crop}
+	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008.
+Countries for which no armed conflicts are recorded are shaded in grey.}
+	\label{fig:CityConfMap}
+\end{figure}
+
+We restrict our sample to only those countries that are listed as having conflicts in the PRIO dataset.
+Specifically, this means that our analysis focuses on exploring variations in economic growth among countries currently engaged in internal armed conflict by the proximity of those conflicts to major cities.
+To do this we first calculate the distance between the centroid of each of the conflicts identified in the PRIO armed conflict dataset with the centroids of the city locations.
+Doing this between every city and every conflict
+
+A key problem face in conducting this analysis is reconciling the unit of analysis for our independent and dependent variables.
+Our dependent variable is at the country-year and our independent variables are actaully at the conflict-country-year level.
 
 Key Independent variables:
-
-	Conflict data: comes from PRIO Conflict Location Even Data
 
@@
 
-Use simulations to determine substantive effects
+\begin{figure}[ht]
+	\centering
+	\resizebox{.6\textwidth}{!}{\input{mod3CoefPlot.tex}}
+\end{figure}
+\FloatBarrier
+
+Use simulations to determine substantive effects - SM
+
+\begin{figure}[ht]
+	\centering
+	\resizebox{.8\textwidth}{!}{\input{mod3SimPlot.tex}}
+\end{figure}
+\FloatBarrier

### 2014-03-28 LaTeX/mod3CoefPlot.tex
pushing stuff

% Created by tikzDevice version 0.6.2 on 2014-03-28 11:43:10
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\fill[color=fillColor,fill opacity=0.00,] (0,0) rectangle (289.08,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\draw[color=drawColor,line width= 0.6pt,line cap=round,line join=round,fill=fillColor,] ( -0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (129.77, 34.03) rectangle (277.03,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\draw[fill=fillColor,draw opacity=0.00,] (129.77, 34.03) rectangle (277.03,277.03);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (214.56, 51.82) -- (214.56, 51.82);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (214.52, 81.45) -- (214.54, 81.45);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (215.47,111.08) -- (216.65,111.08);

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (222.76,140.72) -- (255.30,140.72);

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (220.66,170.35) -- (235.55,170.35);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (209.97,199.99) -- (220.09,199.99);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (178.06,229.62) -- (213.50,229.62);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (166.20,259.25) -- (242.30,259.25);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (214.56, 51.82) -- (214.56, 51.82);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (214.52, 81.45) -- (214.53, 81.45);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (215.57,111.08) -- (216.56,111.08);

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (225.38,140.72) -- (252.69,140.72);

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (221.86,170.35) -- (234.36,170.35);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (210.79,199.99) -- (219.28,199.99);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (180.91,229.62) -- (210.65,229.62);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (172.32,259.25) -- (236.19,259.25);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
\definecolor[named]{fillColor}{rgb}{0.00,0.00,0.00}

\draw[color=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor,] (214.56, 34.03) -- (214.56,277.03);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (204.25,259.25) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (195.78,229.62) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (215.03,199.99) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (228.11,170.35) circle (  2.85);

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (239.03,140.72) circle (  2.85);

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (216.06,111.08) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (214.53, 81.45) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (214.56, 51.82) circle (  2.85);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.56, 50.33) --
	(214.56, 53.30);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.56, 51.82) --
	(214.56, 51.82);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.56, 50.33) --
	(214.56, 53.30);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.54, 79.97) --
	(214.54, 82.93);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.54, 81.45) --
	(214.52, 81.45);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.52, 79.97) --
	(214.52, 82.93);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\draw[color=drawColor,line width= 0.6pt,line join=round,] (216.65,109.60) --
	(216.65,112.57);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (216.65,111.08) --
	(215.47,111.08);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (215.47,109.60) --
	(215.47,112.57);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (255.30,139.24) --
	(255.30,142.20);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (255.30,140.72) --
	(222.76,140.72);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (222.76,139.24) --
	(222.76,142.20);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (235.55,168.87) --
	(235.55,171.83);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (235.55,170.35) --
	(220.66,170.35);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (220.66,168.87) --
	(220.66,171.83);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 0.6pt,line join=round,] (220.09,198.50) --
	(220.09,201.47);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (220.09,199.99) --
	(209.97,199.99);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (209.97,198.50) --
	(209.97,201.47);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\draw[color=drawColor,line width= 0.6pt,line join=round,] (213.50,228.14) --
	(213.50,231.10);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (213.50,229.62) --
	(178.06,229.62);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (178.06,228.14) --
	(178.06,231.10);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 0.6pt,line join=round,] (242.30,257.77) --
	(242.30,260.74);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (242.30,259.25) --
	(166.20,259.25);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (166.20,257.77) --
	(166.20,260.74);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\draw[color=drawColor,line width= 0.6pt,line join=round,fill opacity=0.00,] (129.77, 34.03) --
	(129.77,277.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[color=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (122.65, 48.51) {Country Land Mass};

\node[color=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (122.65, 78.14) {Inflation$_{t-1}$};

\node[color=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (122.65,107.78) {Conflict Duration$_{t}$};

\node[color=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (122.65,137.41) {Conflict Type$_{t}$};

\node[color=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (122.65,167.05) {Ln(Min. Conflict Dist.)$_{t}$};

\node[color=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (122.65,196.68) {Ln(Conflict Area)$_{t}$};

\node[color=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (122.65,226.31) {Conflict Intensity$_{t}$};

\node[color=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (122.65,255.95) {Upper Income};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\draw[color=drawColor,line width= 0.6pt,line join=round,fill opacity=0.00,] (129.77, 34.03) --
	(277.03, 34.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (136.46, 20.31) {-7};

\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (158.77, 20.31) {-5};

\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (181.09, 20.31) {-3};

\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (203.40, 20.31) {-1};

\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (225.71, 20.31) {1};

\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (248.03, 20.31) {3};

\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (270.34, 20.31) {5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\end{tikzpicture}

### 2014-03-28 LaTeX/modCoefPlot.tex
pushing stuff

--- 2014-03-28 LaTeX/mod3CoefPlot.tex
@@
-% Created by tikzDevice version 0.6.2 on 2014-03-28 11:43:10
+% Created by tikzDevice version 0.6.2 on 2014-03-28 11:37:36
 % !TEX encoding = UTF-8 Unicode
@@
 
-\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (214.52, 81.45) -- (214.54, 81.45);
+\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (214.53, 81.45) -- (214.55, 81.45);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (215.47,111.08) -- (216.65,111.08);
+\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (214.90,111.08) -- (215.62,111.08);
 
-\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (222.76,140.72) -- (255.30,140.72);
+\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (219.64,140.72) -- (243.62,140.72);
+\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
+\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
 
-\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (220.66,170.35) -- (235.55,170.35);
+\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (214.53,170.35) -- (223.35,170.35);
+\definecolor[named]{drawColor}{rgb}{0.99,0.57,0.45}
+\definecolor[named]{fillColor}{rgb}{0.99,0.57,0.45}
+
+\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (208.31,199.99) -- (214.71,199.99);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (209.97,199.99) -- (220.09,199.99);
-\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
-\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}
+\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (200.24,229.62) -- (218.68,229.62);
 
-\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (178.06,229.62) -- (213.50,229.62);
-\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
-\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}
-
-\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (166.20,259.25) -- (242.30,259.25);
+\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (170.81,259.25) -- (224.20,259.25);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (214.52, 81.45) -- (214.53, 81.45);
+\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (214.53, 81.45) -- (214.55, 81.45);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (215.57,111.08) -- (216.56,111.08);
+\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (214.96,111.08) -- (215.57,111.08);
 
-\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (225.38,140.72) -- (252.69,140.72);
+\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (221.57,140.72) -- (241.69,140.72);
+\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
+\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
 
-\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (221.86,170.35) -- (234.36,170.35);
+\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (215.24,170.35) -- (222.64,170.35);
+\definecolor[named]{drawColor}{rgb}{0.99,0.57,0.45}
+\definecolor[named]{fillColor}{rgb}{0.99,0.57,0.45}
+
+\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (208.82,199.99) -- (214.20,199.99);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (210.79,199.99) -- (219.28,199.99);
-\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
-\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}
+\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (201.72,229.62) -- (217.20,229.62);
 
-\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (180.91,229.62) -- (210.65,229.62);
-\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
-\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}
-
-\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (172.32,259.25) -- (236.19,259.25);
+\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (175.10,259.25) -- (219.90,259.25);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
@@
 
-\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (204.25,259.25) circle (  2.85);
+\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (197.50,259.25) circle (  2.85);
+
+\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (209.46,229.62) circle (  2.85);
+\definecolor[named]{drawColor}{rgb}{0.99,0.57,0.45}
+\definecolor[named]{fillColor}{rgb}{0.99,0.57,0.45}
+
+\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (211.51,199.99) circle (  2.85);
+\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
+\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
+
+\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (218.94,170.35) circle (  2.85);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (231.63,140.72) circle (  2.85);
+
+\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (215.26,111.08) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (195.78,229.62) circle (  2.85);
-\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
-\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}
-
-\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (215.03,199.99) circle (  2.85);
-\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
-\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
-
-\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (228.11,170.35) circle (  2.85);
-
-\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (239.03,140.72) circle (  2.85);
-
-\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (216.06,111.08) circle (  2.85);
-\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
-\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}
-
-\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (214.53, 81.45) circle (  2.85);
+\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (214.54, 81.45) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.54, 79.97) --
-	(214.54, 82.93);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.55, 79.97) --
+	(214.55, 82.93);
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.54, 81.45) --
-	(214.52, 81.45);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.55, 81.45) --
+	(214.53, 81.45);
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.52, 79.97) --
-	(214.52, 82.93);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.53, 79.97) --
+	(214.53, 82.93);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (216.65,109.60) --
-	(216.65,112.57);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (215.62,109.60) --
+	(215.62,112.57);
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (216.65,111.08) --
-	(215.47,111.08);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (215.62,111.08) --
+	(214.90,111.08);
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (215.47,109.60) --
-	(215.47,112.57);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.90,109.60) --
+	(214.90,112.57);
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (255.30,139.24) --
-	(255.30,142.20);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (243.62,139.24) --
+	(243.62,142.20);
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (255.30,140.72) --
-	(222.76,140.72);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (243.62,140.72) --
+	(219.64,140.72);
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (222.76,139.24) --
-	(222.76,142.20);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (219.64,139.24) --
+	(219.64,142.20);
+\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
+\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (235.55,168.87) --
-	(235.55,171.83);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (223.35,168.87) --
+	(223.35,171.83);
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (235.55,170.35) --
-	(220.66,170.35);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (223.35,170.35) --
+	(214.53,170.35);
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (220.66,168.87) --
-	(220.66,171.83);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.53,168.87) --
+	(214.53,171.83);
+\definecolor[named]{drawColor}{rgb}{0.99,0.57,0.45}
+\definecolor[named]{fillColor}{rgb}{0.99,0.57,0.45}
+
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.71,198.50) --
+	(214.71,201.47);
+
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.71,199.99) --
+	(208.31,199.99);
+
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (208.31,198.50) --
+	(208.31,201.47);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (220.09,198.50) --
-	(220.09,201.47);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (218.68,228.14) --
+	(218.68,231.10);
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (220.09,199.99) --
-	(209.97,199.99);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (218.68,229.62) --
+	(200.24,229.62);
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (209.97,198.50) --
-	(209.97,201.47);
-\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
-\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (200.24,228.14) --
+	(200.24,231.10);
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (213.50,228.14) --
-	(213.50,231.10);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (224.20,257.77) --
+	(224.20,260.74);
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (213.50,229.62) --
-	(178.06,229.62);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (224.20,259.25) --
+	(170.81,259.25);
 
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (178.06,228.14) --
-	(178.06,231.10);
-\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
-\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}
-
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (242.30,257.77) --
-	(242.30,260.74);
-
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (242.30,259.25) --
-	(166.20,259.25);
-
-\draw[color=drawColor,line width= 0.6pt,line join=round,] (166.20,257.77) --
-	(166.20,260.74);
+\draw[color=drawColor,line width= 0.6pt,line join=round,] (170.81,257.77) --
+	(170.81,260.74);
 \end{scope}
@@
 
+\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (147.62, 20.31) {-6};
+
 \node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (158.77, 20.31) {-5};
+
+\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (169.93, 20.31) {-4};
 
@@
 
+\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (192.24, 20.31) {-2};
+
 \node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (203.40, 20.31) {-1};
+
+\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (214.56, 20.31) {0};
 
@@
 
+\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (236.87, 20.31) {2};
+
 \node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (248.03, 20.31) {3};
+
+\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (259.18, 20.31) {4};
 

### 2014-03-28 LaTeX/RhodiumLit.tex

@@
 That civil wars negatively impact economic performance, while in line with the ``war ruin'' hypothesis, runs counter to the ``war renewal'' hypothesis.
-Some scholars have argued that wars, international wars in particular, can spur economic development \citep{}.
+Some scholars have argued that wars, international wars in particular, can spur economic development\footnote{For a review of this discussion, see \cite{rasler:thompson:1985}}.
 The prevailing wisdom with regard to civil war, however, is that outcomes of this nature are the exception rather than the rule.
@@
 They also find, perhaps unsuprisingly, that aggregate estimates of conflict destructiveness are negatively correlated with long-term growth.
+
+Not only do several studies link civil war to domestic economic performance, there is also evidence that civil wars have regional economic consequences.
+\cite{murdoch:sandler:2002} find some evidence that states neighboring civil war states are more likely to experience poor short-term economic performance.
+They attribute this effect to the disruption of trade and uncertainty about the potential for conflict to spread across the border.
 
@@
 More specifically, they believe that strong economic growth proxies for robust governance and that states with low GDP growth likely have infrastructures that are unable to implement counterinsurgent policies.
-In an effort to parse out the causal effect of economic growth shocks on civil war, \cite{miguel:elal:2004} instrument income growth with rainfall.
+In an effort to parse out the causal effect of economic growth shocks on civil war, \cite{miguel:etal:2004} instrument income growth with rainfall.
 They find that rainfall is strongly correlated with income in sub-Saharan Africa, a region also prone to civil conflict in recent decades.
 Using a two-stage estimation approach, they find that rainfall, their exogenous instrument for income, is positively correlated with the likelihood of civil war.
-
-More recent work has attempted to assessthe

### 2014-03-28 R/conflictMaps.R
more maps

@@ -12,70 +12,7 @@ fYrCty$cname <- toupper(countrycode(fYrCty$cname,"country.name","country.name"))
 prio$Conflict.territory <- toupper(countrycode(prio$Conflict.territory,"country.name","country.name"))
 
 ######################################################################
-# Plot conflict spread and gdp
-# plotConflict <- function(cname, threshold=1)
-# {
-#   worldmap <- cshp(date=as.Date("1990-01-01"),useGW=F)
-
-#   ccode <- countrycode(cname,"country.name","cown")
-#   country.shape <- worldmap[worldmap$COWCODE==ccode,]
-#   # gradient <- colorRampPalette(c("#ffffcc","#c7e9b4","#7fcdbb","#41b6c4","#1d91c0","#225ea8","#0c2c84"))
-#   # years <- sort(prio$Year[prio$Conflict.territory==cname])
-#   # years <- years-min(years)
-  
-#   growth <- data.frame(low=ifelse(yData$NY.GDP.PCAP.KD.ZG_l0[yData$ccode==ccode]<=1,"#d53e4f","#3288bd"),year=yData$year[yData$ccode==ccode])
-#   newprio <- na.omit(prio[prio$Conflict.territory==cname,])
-#   newprio <- merge(newprio,growth,by.x="Year",by.y="year",all.x=T,all.y=F,sort=F)
-  
-#   par(mfrow=c(1,2))
-#   plot(country.shape)
-#   points(fYrCty$cleanLong[fYrCty$cname==cname], fYrCty$cleanLat[fYrCty$cname==cname], pch=16)
-#   points(newprio$Longitude,newprio$Latitude, col=as.character(newprio$low), pch=16)
-#   plot(yData$year[yData$ccode==ccode],yData$NY.GDP.PCAP.KD.ZG_l0[yData$ccode==ccode],ylab="GDP Growth",xlab="Year",las=1,frame=F,type="l")
-#   abline(h=0,lty=2)
-#   lines(yData$year[yData$ccode==ccode],yData$NY.GDP.PCAP.KD.ZG_l0[yData$ccode==ccode])
-#   points(yData$year[yData$ccode==ccode],yData$NY.GDP.PCAP.KD.ZG_l0[yData$ccode==ccode],col=as.character(growth$low),pch=16)
-# }
-
-# plotConflict("SIERRA LEONE")
-# plotConflict("INDIA")
-######################################################################
-
-######################################################################
[…]

### 2014-03-28 LaTeX/RhodiumEmp.tex
more maps
more stuff

@@
 	\centering
-	\includegraphics[width=.9/textwidth]{CityConfMap-crop}
+	\includegraphics[width=.9\textwidth]{CityConfMap-crop}
 	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008.
@@
 We restrict our sample to only those countries that are listed as having conflicts in the PRIO dataset.
-Specifically, this means that our analysis focuses on exploring variations in economic growth among countries currently engaged in internal armed conflict by the proximity of those conflicts to major cities.
+Specifically, this means that our analysis focuses on exploring variations in economic growth in countries undergoing conflict by the proximity of those conflicts to major cities.
 To do this we first calculate the distance between the centroid of each of the conflicts identified in the PRIO armed conflict dataset with the centroids of the city locations.
-Doing this between every city and every conflict
+We calculate the
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=.7\textwidth]{colombiaMap-crop}
+	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008.
+Countries for which no armed conflicts are recorded are shaded in grey.}
+	\label{fig:CityConfMap}
+\end{figure}
 

### 2014-03-28 R/conflictMaps.R

@@ -29,7 +29,7 @@ ggmapData$id = as.numeric(as.character(ggmapData$id))
 
 temp = ggplot(ggmapData, aes(map_id = id))
 temp = temp + geom_map(map=ggmap, fill='white', linetype=1, colour='black') + expand_limits(x = ggmap$long, y = ggmap$lat) 
-temp = temp + geom_point(aes(x=fYrCty$cleanLong[fYrCty$cname==cname], y=fYrCty$cleanLat[fYrCty$cname==cname]))
+temp = temp + geom_point(aes(x=fYrCty$cleanLong[fYrCty$cname==cname], y=fYrCty$cleanLat[fYrCty$cname==cname]), pch=18)
 temp = temp + geom_point(aes(x=newprio$Longitude, y=newprio$Latitude, color=newprio$Year))
 temp = temp + scale_colour_gradient('',breaks=newprio$Year[c(1,5,10,15,20)])
 temp = temp + theme(

### 2014-03-28 LaTeX/RhodiumEmp.tex
more stuff

@@
 We restrict our sample to only those countries that are listed as having conflicts in the PRIO dataset.
-Specifically, this means that our analysis focuses on exploring variations in economic growth in countries undergoing conflict by the proximity of those conflicts to major cities.
-To do this we first calculate the distance between the centroid of each of the conflicts identified in the PRIO armed conflict dataset with the centroids of the city locations.
-We calculate the
+As a result, our analysis focuses on exploring variations in economic growth in countries undergoing conflict by the proximity of those conflicts to major cities.
+To determine proximity, we calculate the distance in kilometers between the centroid of each of the conflicts with the centroids of city locations.
+Thus for each year we determine the distance between every conflict and every major city within the state.
+For example, in figure \ref{fig:columbiaMap} we show the location of armed conflicts in Colombia, circles filled in shades of red, and the major cities therein, blue diamonds.\footnote{One armed conflict involving rebel actors and the Colombian government occurred outside of Colombia's borders.} For Colombia each of these points represents the same conflict but a different year, with earlier years shaded in light red and later years shaded in dark red.
+Thus for each year we calculated the distance between the centroid conflict location provided by PRIO and every major city identified in blue.
 
@@
 Countries for which no armed conflicts are recorded are shaded in grey.}
-	\label{fig:CityConfMap}
+	\label{fig:columbiaMap}
 \end{figure}
 
-A key problem face in conducting this analysis is reconciling the unit of analysis for our independent and dependent variables.
-Our dependent variable is at the country-year and our independent variables are actaully at the conflict-country-year level.
+A key problem we face in conducting this analysis is reconciling the unit of analysis for our key independent and dependent variables.
+Our dependent variable is at the country-year and our key independent variable, distance between conflicts and major cities, are at the conflict-country-year level.
+To deal with this, we aggregate up to the country-year level by calculating the minimum logged distance any conflict is from a major city.
+Thus if a country faced, for example, four conflicts in one year, the datapoint that we would aggregate up to the country-year level would be for the conflict that was closest to a major city.
+This obviously is somewhat problematic as we end up discarding the information from the other conflicts.
+At the same time, we argue that this choice of aggregation is what conforms closest to our theoretical claims about economic activity only being severely disrupted in cases of conflicts being proximate to major cities.
+From the PRIO dataset we also bring in additional information about that conflict, specifically:
 
-Key Independent variables:
+\begin{itemize}
+	\item Conflict intensity
+	\item Ln(Conflict Area)
+	\item Civil Conflict Type (e.g., territory or non-territory dispute)
+	\item Conflict Duration (Years)
+\end{itemize}
 
-		Note data aggregation choices.  Multiple conflicts in one country?
+Last, we include a number of additional control measures.
+First, we control for a country's total, logged land area to differentiate between the proximity effects of conflicts within large and small countries.
+We also control for a couple of macroeconomic variables that could affect year over year changes in GDP, specifically, lagged inflation and whether or not the state is an upper income country, as defined by the World Bank.
 
-		Note dropping interstate conflict.
+\subsection{Estimation Method}
 
-	City data: Collection of major population centers by year
+To estimate the model we use random effects clustered on countries and years. Results using a fixed effects estimation approach are similar. The model we estimate is shown below:
 
-	Variables: Determined distance between conflicts in a year and city centers. then calculcate min distance to determine effect on conflict
-
-\subsection{Sample and Estimation Method}
-
-Sample: Only country-years undergoing a civil conflict. Coverage restricted to 1989-2008.
-
-Measured as a random effects model with country effects
+\begin{align*}
+	\Delta GDP_{i,t} &= \beta_{1}(Upper \; Income_{i,t}) \\
+	& \;+\; \beta_{2}(Conflict \; Intensity_{t}) \;+\; \beta_{3}(Ln(Conflict \; Area)_{t}) \\
+	& \;+\; \beta_{4}(Ln(Min. \; Conflict \; Dist.)_{t}) \;+\; \beta_{5}(Conflict \; Type_{t}) \\
+	& \;+\; \beta_{6}(Conflict \; Duration_{t}) \;+\; \beta_{7}(Inflation_{t-1}) \\
+	& \;+\; \beta_{8}(Ln(Land \; Area)_{t}) \;+\; \alpha_{i} + \gamma_{t} + \mu_{i,t}
+\end{align*}
 
@@
 
-Conflicts occuring more proximate to major cities have stronger adverse effects on economic performance than those farther away.
+We depict the results of our model in figure \ref{fig:coefPlot}.
+Most of the findings here are in line with our theoretical expectations.
+We find that higher levels of conflict intensity are associated with lower levels of GDP growth.
+The effect of conflict type is positive, indicating that non-territorial disputes are related to lower levels of GDP growth as well.
+Surprisingly, conflicts that are of a longer duration are, on average, not having a negative effect on GDP growth.
+
+Most importantly, we find strong support for our key hypothesis relating the proximity of a conflict to lower levels of GDP growth.
+The fact that the logged, minimum conflict distance variable is positive indicates that conflicts closer to major cities have an adverse effect on economic growth.
 
@@
 \end{figure}
+	\caption{Here we show the random effect regression results on GDP growth.
+Darker colors indicates that the coefficient estimate is significantly different from zero at a 95\% CI, while lighter the same for a 90\% CI.
+Grey indicates that the estimate is not significantly different from zero at either of those intervals.}
+	\label{fig:coefPlot}
 \FloatBarrier
 
-Use simulations to determine substantive effects - SM
+To assess the substantive effect of the minimum conflict distance variable we conduct a number of simulations.
+
+Although the effect of ratified and signed BITs on FDI inflows is significant, their substantive meaning is questionable when taking into account the uncertainty of the coefficient estimates and the model itself.
+To do so I examine the difference in the level of FDI inflows a country can expect if they have signed no BITs compared to a country that has signed 105 BITs, the maximum number of signed BITs in \citeauthor{allee2011contingent}'s sample.
+I then repeat this procedure for the number of BITs a country has ratified.
+The first step in doing so is to construct a set of scenarios where the only value varying is that of the independent variable whose substantive effect is to be measured.
+I set up two scenarios, one where the number of BITs a country has signed is set to its minimum in the dataset and another where it is set to its maximum -- all other variables were set to their median value.
+Next, I conduct 1,000 random draws from a multivariate normal to obtain distributions for the point estimates of each of the regression coefficients.
+After obtaining these distributions, I calculate the predicted value of FDI inflows based on the conditions set by the two scenarios.
+To account for uncertainty in the model itself, I resample from a univariate normal to generate a distribution of predicted values for both scenarios.
+The result of this analysis is visualized in figure \ref{fig:BITsims}.
+The same analysis for the number of BITs a country has ratified is shown in figure \ref{fig:Dispsims}.
 
@@
 	\resizebox{.8\textwidth}{!}{\input{mod3SimPlot.tex}}
+	\caption{Expected values for GDP growth based on scenarios where all variables are held to their constants but Ln(Min.
+Conflict Dist.) varies from its minimum to maximum.
+The 90\% interval of each distribution is shaded in dark grey and the 95\% in a lighter color.}
+	\label{fig:simsPlot}
 \end{figure}

### 2014-03-28 LaTeX/RhodiumLit.tex
Added literature

@@
 \label{lit}
-
-varying hypotheses about the effect of war on economic development, war ruin v war renewal hypotheses
-
-literature on sub-state determinants of conflict and outcome (pierskala hollenbach 2013)
-
-	explain how what has been done in the spatial conflict literature and even the sub-nat/spat literature does not capture what we have done in this paper
-
-% literature on endogeneity of conflict and economic performance (sambanis 2001, worldbank 2003)
-
-% 	do we want to wade in to the endogeneity debate?
-i'm not sure we do that's why i've commented this out temporarily.
-seems to me our life would be made easier if we just tied ourselves to teh literature that puts econ growth as the dv nad conflict as the iv.
-u probably know better than me if this position is untenable.
 
@@
 They attribute this effect to the disruption of trade and uncertainty about the potential for conflict to spread across the border.
+In a follow up study, \cite{murdoch:sandler:2002} suggest that the spatial dispersion of economic effects from civil conflict differ from region to region.
 
@@
 These changes to economic performance, as well as structural changes to the economy itself, make the resurgence of war more likely.
+
 In accord with this theory, \cite{fearon:laitin:2003} aruge that poor economic growth is the primary condition conducive for civil war.
@@
 Using a two-stage estimation approach, they find that rainfall, their exogenous instrument for income, is positively correlated with the likelihood of civil war.
+
+\subsubsection{Disaggregating Civil Wars}
+
+Recently, scholars have begun to spatially disaggregate civil conflicts.
+New data allows researchers to focus on how the geography of internal conflict varies.
+\cite{pierskalla:hollenbach:2013} use subnational data on African states to asses the role cell phone coverage plays in facilitating violent conflict.
+They theorize that cell phone coverage will enhance the collective action capabilities of rebel groups by improving coordination, communication, and in-group monitoring.
+A series of empirical tests confirm this hypothesis and indicate that cell phone coverage corresponds to a 50\%-300\% increase in conflict likelihood for a given area (depending on the estimation strategy used).
+
+\cite{berman:couttenier:2013} explore another sub-state determinant of civil conflict.
+Recognizing that economic shocks are associated with changes to the probability of civil conflict,\footnote{For more, see \cite{miguel:etal:2004} and \cite{dube:vargas:forthcoming}.} they seek to determine where conflict will emerge when these shocks occur.
+Given an external economic shock in a trading partner, Berman and Couttenier expect that states should be at an increased risk of experiencing conflict.
+However, not all locations within a state will feel the effects equally.
+Those areas most directly connected to the trading partner will be more likely to experience violent conflict than those areas that are less dependent on the trading partner.
+They operationalize this measure of dependence, or ``remoteness,'' as distance from a seaport.
+Indeed, they find that conflicts are more likley to arise near seaports following an economic shock than they are further away.

### 2014-03-28 LaTeX/RhodiumEmp.tex
cleaning
done with empirics

@@
 \begin{align*}
-	\Delta GDP_{i,t} &= \beta_{1}(Upper \; Income_{i,t}) \\
+	\% \Delta GDP_{i,t} &= \beta_{1}(Upper \; Income_{i,t}) \\
 	& \;+\; \beta_{2}(Conflict \; Intensity_{t}) \;+\; \beta_{3}(Ln(Conflict \; Area)_{t}) \\
@@
 	\resizebox{.6\textwidth}{!}{\input{mod3CoefPlot.tex}}
-\end{figure}
 	\caption{Here we show the random effect regression results on GDP growth.
@@
 	\label{fig:coefPlot}	
+\end{figure}
 \FloatBarrier
@@
 To assess the substantive effect of the minimum conflict distance variable we conduct a number of simulations.
-
-Although the effect of ratified and signed BITs on FDI inflows is significant, their substantive meaning is questionable when taking into account the uncertainty of the coefficient estimates and the model itself.
-To do so I examine the difference in the level of FDI inflows a country can expect if they have signed no BITs compared to a country that has signed 105 BITs, the maximum number of signed BITs in \citeauthor{allee2011contingent}'s sample.
-I then repeat this procedure for the number of BITs a country has ratified.
-The first step in doing so is to construct a set of scenarios where the only value varying is that of the independent variable whose substantive effect is to be measured.
-I set up two scenarios, one where the number of BITs a country has signed is set to its minimum in the dataset and another where it is set to its maximum -- all other variables were set to their median value.
-Next, I conduct 1,000 random draws from a multivariate normal to obtain distributions for the point estimates of each of the regression coefficients.
-After obtaining these distributions, I calculate the predicted value of FDI inflows based on the conditions set by the two scenarios.
-To account for uncertainty in the model itself, I resample from a univariate normal to generate a distribution of predicted values for both scenarios.
-The result of this analysis is visualized in figure \ref{fig:BITsims}.
-The same analysis for the number of BITs a country has ratified is shown in figure \ref{fig:Dispsims}.
+We set up scenarios where we hold all variables to their median except for the logged, minimum conflict distance, which we range from its minimum to maximum value.
+Next, we conduct 1,000 random draws from a multivariate normal to obtain distributions for the point estimates of each of the regression coefficients.
+After obtaining these distributions, we calculate the predicted value of GDP growth based on the conditions set by the scenarios.
+We plot the results of this analyis in figure \ref{fig:simsPlot}.
 
@@
 \FloatBarrier
+
+Here we can clearly see that conflicts located farther away from major cities have almost no adverse impact on economic growth.
+On average, countries for which conflicts are farther away see almost no declines in economic growth and, in fact, are likely to still see positive growth.
+Where we see more variation, however, is on the effect of conflicts near to major cities.
+Although on average our model estimates that these more proximate conflicts are associated with negative levels of economic growth our estimate of this effect is highly uncertain.
+This just indicates to us that more work needs to be done in parsing out possible variation in economic growth levels for those countries that are experiencing conflicts proximate to their major cities.
+Nonetheless, overall our results are quite in line with our theoretical expectations.

### 2014-03-28 R/models.R

@@ -121,13 +121,13 @@ tRange=seq(quantile(yData[,toTest])[1],quantile(yData[,toTest])[length(quantile(
 temp = ggsimplot(sims=10000, simData=data, vars=coefs, 
   vi=toTest, vRange=tRange, ostat=median,
   betas=estimates, vcov=varcov, sigma=error, intercept=TRUE,
-  ylabel="GDP Growth$_{t}$", xlabel="Ln(Min. Conflict Dist.)$_{t}$",
+  ylabel="\\% $\\Delta$ GDP$_{t}$", xlabel="Ln(Min. Conflict Dist.)$_{t}$",
   specX=TRUE, ggxbreaks=seq(-1,7,1), plotType='ribbon'
   # specY=TRUE, ggybreaks=seq(0,12,2), ggylims=c(2,12)
   )
 temp
-# setwd(pathTex)
-# tikz(file='mod3SimPlot.tex', width=6, height=4, standAlone=F)
-# temp
-# dev.off()
+setwd(pathTex)
+tikz(file='mod3SimPlot.tex', width=6, height=4, standAlone=F)
+temp
+dev.off()
 ####################################################################################################################

### 2014-03-29 LaTeX/RhodiumTheory.tex
built pdf

@@
 
-End with a chart to show the distribution of econ performance among conflict-cntry-years to illustrate that there is noticeable variation in economic performance to explain.
+%End with a chart to show the distribution of econ performance among conflict-cntry-years to illustrate that there is noticeable variation in economic performance to explain.
 ending with this might help us lead into the empirics section and
-
-	seems like the density plot you've already made in the models.R file highlights that the gdp growth var is kind of normal centered at zero which is good for us
+%
+%	seems like the density plot you've already made in the models.R file highlights that the gdp growth var is kind of normal centered at zero which is good for us

### 2014-03-29 LaTeX/RhodiumEmp.tex
more changes in empirics

@@
 To measure economic performance we use annual percent change in GDP, which we collect from the World Development Indicators at the World Bank.
-We choose to focus on year over change in GDP because we expect conflicts proximate to major cities
-to lead to reductions in growth not changes in levels.\footnote{Alternative measures of economic performance would have included changes in FDI inflows or changes in GDP per capita, in using either of these measures are results remain relatively the same.} Unlike much of the extant literature in constructing our dependent variable we focus on year over change instead of a ten year average.
+We choose to focus on year over change in GDP because we expect conflicts proximate to major cities to lead to reductions in growth.\footnote{Alternative measures of economic performance would have included changes in FDI inflows or changes in GDP per capita, in using either of these measures are results remain relatively the same.} Unlike much of the extant literature in constructing our dependent variable we focus on year over change instead of a ten year average.
 We believe this approach to be superior because it allows us to estimate the direct effect of the conflict on economic performance in that year.
@@
 The key theory that we advance here is that the effects of conflict on economic performance are conditional on the proximity of those conflicts to major city centers.
-Thus a key part of the research here was determining major city centers by year.
+Thus a crucial part of our work here involved determining major city centers by year.
 The only data source we found with enough geographical and temporal coverage on major cities was The World Alamanac.
-To gather data from these textbooks we hired several undergraduate students to code the major cities by country for each year of the Almanac from 1989 to 2008.
+To gather data from these textbooks we hired several undergraduate students to identify the major cities listed for each country within a yearly edition of the Almanac from 1989 to 2008.
 Major cities are classified as those that have relatively large shares of a country's population and/or are economic centers.
-On average, for each country at least three major cities are identified in each year from 1989 to 2008.
+Typically, the Alamanacs listed at least three major cities for each country and year from 1989 to 2008.
+After we had gathered a yearly list of major cities by country, we determined the centroid location of each city using Google's Geocoding API.
+
 In figure \ref{fig:CityConfMap}, we show the geographic distribution of conflicts and cities.
+The centroid locations of conflicts are shown by red dots.
+Not surprisingly, we can see that in many cases conflict locations are clustered within specific parts of a country.
+In most cases, this clustering is indicative of the same conflict moving within the geographic boundaries of a country over time.
+The blue diamonds in \ref{fig:CityConfMap} denote the locations of major cities as identified in The World Alamanacs from 1989 to 2008.
+Countries shaded in grey are those for which no armed conflict took place in this period according to the PRIO dataset.
 
-\begin{figure}[ht]
+\begin{sidewaysfigure}[ht]
 	\centering
@@
 	\label{fig:CityConfMap}
-\end{figure}
+\end{sidewaysfigure}
+\FloatBarrier
 
-We restrict our sample to only those countries that are listed as having conflicts in the PRIO dataset.
-As a result, our analysis focuses on exploring variations in economic growth in countries undergoing conflict by the proximity of those conflicts to major cities.
+Our analysis focuses on exploring variations in economic growth in countries undergoing conflict by the proximity of those conflicts to major cities, thus we restrict our sample to only those countries that are listed as having conflicts in the PRIO dataset.
 To determine proximity, we calculate the distance in kilometers between the centroid of each of the conflicts with the centroids of city locations.
-Thus for each year we determine the distance between every conflict and every major city within the state.
-For example, in figure \ref{fig:columbiaMap} we show the location of armed conflicts in Colombia, circles filled in shades of red, and the major cities therein, blue diamonds.\footnote{One armed conflict involving rebel actors and the Colombian government occurred outside of Colombia's borders.} For Colombia each of these points represents the same conflict but a different year, with earlier years shaded in light red and later years shaded in dark red.
-Thus for each year we calculated the distance between the centroid conflict location provided by PRIO and every major city identified in blue.
+Meaning that for each year we determine the distance between every conflict and every major city within a state.
+For example, in figure \ref{fig:columbiaMap} we show the location of armed conflicts in Colombia, dots colored in shades of red, and the major cities therein, blue diamonds.\footnote{One armed conflict involving rebel actors and the Colombian government occurred outside of Colombia's borders.} For Colombia each of the red dots represents the same conflict but a different year, with earlier years shaded in light red and later years shaded in dark red.
+Thus for every year we made six distance calculations -- one for every city.
 
@@
 	\centering
-	\includegraphics[width=.7\textwidth]{colombiaMap-crop}
+	\includegraphics[width=.5\textwidth]{colombiaMap-crop}
 	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008.
@@
 A key problem we face in conducting this analysis is reconciling the unit of analysis for our key independent and dependent variables.
-Our dependent variable is at the country-year and our key independent variable, distance between conflicts and major cities, are at the conflict-country-year level.
+Our dependent variable is at the country-year and our key independent variable, distance between conflicts and major cities, is at the conflict-country-year level.
 To deal with this, we aggregate up to the country-year level by calculating the minimum logged distance any conflict is from a major city.

### 2014-03-29 LaTeX/RhodiumConcl.tex
Short conclusion added. Needs more work.

--- 2013-02-07 LaTeX/RhodiumConcl.tex
@@
 
-If NATO had not intervened, the expected duration of the conflict would have been much shorter. But the rebels would have lost, so there is a trade-off.
+Our project seeks to explain observed discrepencies in the economic impact of civil conflict.
+Violent intrastate conflicts have occured in one third of countries in just the past several decades.
+While civil wars seem to primarily afflict developing states, their actual economic impacts are still subject to debate.
+Some states weather civil conflict for years or even decades while simultaneously prospering economically.
+Other states see their economies stall and suffer substantial declines in growth.
+Despite this heterogeneity observed among civil war states, the individual characteristics of civil conflict that lead to disparate outcomes have only recently been subject to academic scrutiny.
+In this first step of a larger project to distinguish the geography of civil conflict, we hope to have contributed to our understanding of why some civil conflicts impact economic performance more severely than others.
+We have used a novel approach in the study of civil conflict to distinguish between spatially dissimilar events and shown that this new measure of interest, the minimum distance between conflict epicenters and major population centers, is a substantive determinant of economic growth.
+While the proximity of conflict to major cities helps us to better understand how domestic armed conflict produces disparate economic outcomes across countries, one can imagine a number of other hypotheses that derive from this research.
+
+Population centers are critical to economic performance, but still tell only a part of the story.
+States rely on various natural resources as well as critical infrastructure to prosper.
+Trade depends on safe and reliable access to ports, airports, and railways.
+Businesses rely on safe and reliable access to natural resources.
+And foreign direct investment relies on the investor's perception of state stability.
+While there is a large literature on natural resources and conflict at the state level, little work has disaggregated this data and explored the micro-relationship between conflict and resources.
+Future iterations of this paper will explore each of these hypotheses using geospatial data on the economic assets of interest.
+
+Looking beyond aggregate measures of state economic performance, we hope to further explore how the geography of conflict impacts the surrounding region.
+A growing body of work suggests that civil conflict is, in and of itself, contagious.
+However, the precise mechanisms that determine contagion risk are still unclear.
+We propose that looking at the location of conflict within a state will shed light on how conflicts and their economic effects spread across borders.
+The same logic that applies to the hypotheses presented in this paper applies to neighboring states as well.
+Resources and population centers that are near the border between a peaceful state and a civil war state may be impacted in the same way that resources and cities within the conflict state are.
+This may help to explain the disparate regional economic effects of civil war observed by \cite{murdoch:sandler:2002}.

### 2014-03-29 LaTeX/RhodiumTheory.tex
Short conclusion added. Needs more work.

@@
 Companies that rely on the extraction of resources may find themselves unable to access those resources if armed conflict is proximately located to the resource sites.
-Therefore, we expect state economic performance to be inversely related to the distance from conflict zones to valuable resources.
+Therefore, we expect state economic performance to be directly related to the distance from conflict zones to valuable resources.
 
@@
 By targeting economic centers and resource infrastructure, FARC can strain Colombia's economy, frighten investors, and bolster support from poor and rural workers sensitive to wealth disparity in the country.
-Rabasa and Chalk (2001) identify a three-pronged strategy pursued by FARC in the 1990s: to consolidate power in coca-growing regions, to conduct military operations in economically valuable areas, and to isolate major cities from the rest of the country by limiting communication and travel between them.
+\cite{rabasa:chalk:2001} identify a three-pronged strategy pursued by FARC in the 1990s: to consolidate power in coca-growing regions, to conduct military operations in economically valuable areas, and to isolate major cities from the rest of the country by limiting communication and travel between them.
+
+While FARC seems to exploit its ability to target areas of economic importance including cities, other insurgencies tend to be more peripheral.
+India, for instance, has faced challenges by armed groups in its north-east for half a century.
+However, this area of India is remote, primarily agrarian, and relatively less populous than other parts of India.
+Indeed, for much of this period, India has experienced relatively robust economic growth.
+
+We turn now to an empirical test of our proposition.
+Using a dataset that includes 510 instances of civil war from 71 different countries, we seek to determine how the geography of conflict impacts state economic outcomes.
 

### 2014-03-30 LaTeX/RhodiumLit.tex
double space, added lit
Updated bib.

@@
 The prevailing wisdom with regard to civil war, however, is that outcomes of this nature are the exception rather than the rule.
-In a test of economic and social determinants of post-conflict recovery in the context of civil war, \cite{kang:meernick:2005} find that these conflicts can lead, under different conditions, to either rapid or stagnant economic recovery.
+In a test of economic and social determinants of post-conflict recovery in the context of civil war, \cite{kang:meernik:2005} find that these conflicts can lead, under different conditions, to either rapid or stagnant economic recovery.
 They conclude that the long-term economic impacts of civil war are largely dependent on post-war governance and foreign assistance.
@@
 Not only do several studies link civil war to domestic economic performance, there is also evidence that civil wars have regional economic consequences.
-\cite{murdoch:sandler:2002} find some evidence that states neighboring civil war states are more likely to experience poor short-term economic performance.
+\cite{murdoch:sandler:2002a} find some evidence that states neighboring civil war states are more likely to experience poor short-term economic performance.
 They attribute this effect to the disruption of trade and uncertainty about the potential for conflict to spread across the border.
-In a follow up study, \cite{murdoch:sandler:2002} suggest that the spatial dispersion of economic effects from civil conflict differ from region to region.
+In a follow up study, \cite{murdoch:sandler:2002b} suggest that the spatial dispersion of economic effects from civil conflict differ from region to region.
 
@@
 \cite{berman:couttenier:2013} explore another sub-state determinant of civil conflict.
-Recognizing that economic shocks are associated with changes to the probability of civil conflict,\footnote{For more, see \cite{miguel:etal:2004} and \cite{dube:vargas:forthcoming}.} they seek to determine where conflict will emerge when these shocks occur.
+Recognizing that economic shocks are associated with changes to the probability of civil conflict,\footnote{For more, see \cite{miguel:etal:2004} and \cite{dube:vargas:2013}.} they seek to determine where conflict will emerge when these shocks occur.
 Given an external economic shock in a trading partner, Berman and Couttenier expect that states should be at an increased risk of experiencing conflict.
@@
 Indeed, they find that conflicts are more likley to arise near seaports following an economic shock than they are further away.
+
+\cite{buhaug:2010} argues that the geography of conflict is a function of rebel strength.
+In particular, strong rebel groups are able to conduct military operations near capital cities while weak ones are not.
+These weaker groups are only able to survive in areas more distant from capitals.

### 2014-04-01 LaTeX/RhodiumEmp.tex
cleaning
Fixed subscripts on equation (I think)
Check this - I added i,t to all the beta subscripts as I believe all
our variables are unit and time varying.  That’s cool, right?

@@
-\section{Empirics}
+\section{Data and Sample}
 \label{empirics}
 
-\subsection{Data and Sample}
+\subsection{Conflict and City Data}
 
@@
 
+\subsection{Level of Aggregation}
+
 A key problem we face in conducting this analysis is reconciling the unit of analysis for our key independent and dependent variables.
@@
 	\% \Delta GDP_{i,t} &= \beta_{1}(Upper \; Income_{i,t}) \\
-	& \;+\; \beta_{2}(Conflict \; Intensity_{t}) \;+\; \beta_{3}(Ln(Conflict \; Area)_{t}) \\
-	& \;+\; \beta_{4}(Ln(Min. \; Conflict \; Dist.)_{t}) \;+\; \beta_{5}(Conflict \; Type_{t}) \\
-	& \;+\; \beta_{6}(Conflict \; Duration_{t}) \;+\; \beta_{7}(Inflation_{t-1}) \\
-	& \;+\; \beta_{8}(Ln(Land \; Area)_{t}) \;+\; \alpha_{i} + \gamma_{t} + \mu_{i,t}
+	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t}) \;+\; \beta_{3}(Ln(Conflict \; Area)_{i,t}) \\
+	& \;+\; \beta_{4}(Ln(Min. \; Conflict \; Dist.)_{i,t}) \;+\; \beta_{5}(Conflict \; Type_{i,t}) \\
+	& \;+\; \beta_{6}(Conflict \; Duration_{i,t}) \;+\; \beta_{7}(Inflation_{i,t-1}) \\
+	& \;+\; \beta_{8}(Ln(Land \; Area)_{i,t}) \;+\; \alpha_{i} + \gamma_{t} + \mu_{i,t}
 \end{align*}
 
-\subsection{Results}
+\section{Results}
 

### 2014-04-01 LaTeX/Abstract.tex
cleaning

@@
 We find that this disagreement results from not accounting for the spatial disaggregation of conflict events within a country.
-
-Our theoretical model states that the economic impact of civil conflict is contingent on the conflict's location relative to major economic and labor resources within a state.
-
+Our hypothesis is that the economic impact of civil conflict is contingent on the conflict's location relative to major economic and labor resources within a state.
 We use subnational data on the spatial distribution of conflict, resources, and infrastructure to test the long-term impact of domestic conflict on state economic performance.

### 2014-04-02 LaTeX/RhodiumEmp.tex

@@
 
-To estimate the model we use random effects clustered on countries and years. Results using a fixed effects estimation approach are similar. The model we estimate is shown below:
+To estimate the model we use random effects clustered on countries and years.
+Results using a fixed effects estimation approach are similar.\footnote{The fixed effects model includes the same regressors as the random effects model but adds indicator variables for each country in the sample.}  The model we estimate is shown below:
 

### 2014-04-02 LaTeX/RhodiumIntro.tex
manuscript edits
updated intro and other stuff

--- 2014-03-13 LaTeX/RhodiumIntro.tex
@@
 
-Puzzle: Why do some conflicts have immediate impacts on a country's economy while others that fester for decades have little to no impact.
+Understanding the effects of civil conflict has become an integral part of the study of economic development \citep{serneels:verpoorten:2013}.
+From a theoretical perspective there is little consensus as to the impact that conflict has on ecomic performance.
+While neoclassical models predict that recovery from conflict should be relatively quick, others such as \citet{barro:martin:2004} and \citet{sachs:2006} argue that recovery will be extremely slow or even trapped in a low level equilibrium.
+Empirical analyses have borne out no clear answers either as results on the economic ramifications of civil war vary depending on the cases and time periods included \citep{kang:meernik:2005}.
 
-	Mexico case: high levels of violence since 2008 but little effect on economic growth.
-Mexico facing serious internal political stability (civil violence, civil war...) yet this has little effect on economic growth as of yet.
-When should we expect to see the adverse effects of civil war manifest themselves in terms of lower economic growth?
+There are also puzzling cases of countries enmeshed in civil armed conflict that have seemingly little impact on economic growth.
+Mexico, for example, has been engaged in a drug war since December 2006 and the number of deaths stemming from this civil conflict have only increased since that time.
+Yet, even as fatalities due to the drug war reached new peaks, Vikram Pandit of Citigroup cited Mexico in 2012 as being extremely well poised for growth and others argued that Mexico was actually beginning to catch up to its regional rival, Brazil \citep{vardi:2012}.
+This contrasts greatly with the economic fortunes of other countries in the midst of civil war where the economies have plumetted.
 
-	Cases apart from Mexico:
-		Pakistan - NWFP
-		India
-		Israel
-		Russia - Chechnya
-		Columbia - FAARC
+In this paper we argue that to explain variation in economic performance between countries in the midst of civil war, it is necessary to account for the spatial location of the conflict relative to major population and economic centers.
+Much of the extant literature has focused on examining the effect of conflict on economic growth at the national level.
+The implicit assumption of these approaches is that all civil wars are alike, whether they be occuring right outside the capital or on the fringes of the country.
+We argue that the location of conflicts to major cities and capitals will determine the effect of civil conflict on economic performance, and that conflicts only significantly dampens economic performance if they are proximate to major population and economic centers.
 
-Background: Show charts of Mexico and/or India's growth in GDP per capita versus number/duration of conflicts
-
-Spatial Dist Hypothesis: Location of conflicts to major cities and capitals determine effect of civil conflict on economic performance
+The rest of the paper proceeds as follows, we begin with a review of the literature on the relationship between economic growth and civil war.
+In section \ref{theory}, we explain the mechanisms of our hypothesis through the case of Colombia.
+In section \ref{empirics}, we describe how we construct our measures capturing distance of conflicts between major economic and population centers and lay out our estimation approach.
+Finally, we discuss the findings of our analysis and end with next steps.

### 2014-04-02 LaTeX/RhodiumTheory.tex
updated intro and other stuff

@@
 
-While these hypotheses may resemble those of \cite{imai:weinstein:2000}, ours differs somewhat in the hypothesized mechanism through which conflict affects economic performance.
+While these hypotheses may resemble those of \cite{imai:weinstein:2000}, ours differs in the hypothesized mechanism through which conflict affects economic performance.
 While we do not disagree that the spread of a conflict could impact state economic prospects, we argue that conflict area is not necessary for adverse economic performance.
@@
 These hypotheses do not seem unknown to armed actors.
-The guerilla group Fuerzas Armadas Revolucionarios de Colombia (FARC) appears to have to internalized these mechanisms.
+The guerilla group Fuerzas Armadas Revolucionarios de Colombia (FARC) appears to have internalized these mechanisms.
 In 1998 and 1999, the organization moved its violent operations from mostly rural areas of Colombia into major cities and near to the capital (Petras and Brescia 2000).

### 2014-04-02 R/Analysis/descStats.R

@@ -26,11 +26,11 @@ mapColors=rep('white',length(Wcntries))
 mapColors[which(Wcntries %in% noConfCntries)] = 'grey'
 
 setwd(pathTex)
-pdf(file='CityConfMap.pdf', width=12, height=6)
+# pdf(file='CityConfMap.pdf', width=12, height=6)
 plot(worldmap, col=mapColors)
 points(fYrCty$cleanLong, fYrCty$cleanLat, col='blue', pch=18, cex=0.5)
 points(prioData$Longitude,prioData$Latitude, col='red', pch=16,cex=0.5)
-dev.off()
+# dev.off()
 ########################################################################
 
 ########################################################################
@@ -44,4 +44,61 @@ cityStats=summaryBy(temp ~ Country + YearAlmanac, data=fYrCty, FUN=sum)
 cityGraph=summaryBy(temp.sum ~ YearAlmanac, data=cityStats, FUN=mean)
 temp=ggplot(cityGraph, aes(x=YearAlmanac, y=temp.sum.mean)) + geom_line()
 temp
+########################################################################
+
+########################################################################
+# Conflict and Growth country by country
+setwd(pathMain)
+source('vizResults.R')
+setwd(paste0(pathData,'/PRIO - Conflict Site Data'))
+prioAC=read.csv('ucdp.prio.armed.conflict.v4.2013.csv')
+prioAC=prioAC[which(prioAC$Type %in% c(3,4)),]
+prioAC=prioAC[which(prioAC$YEAR >= 1980),]
+# Add cnames to this shit
+prioAC$cname = countrycode(prioAC$SideA, 'country.name', 'country.name')
+prioAC = prioAC[!is.na(prioAC$cname),]
+prioAC$ccode = panel$ccode[match(prioAC$cname, panel$cname)]
+prioAC = prioAC[!is.na(prioAC$ccode),]
+
+# [94,] "NY.GDP.PCAP.KD"                 "GDP per capita (constant 2000 US$)"
+# [95,] "NY.GDP.PCAP.KD.ZG"              "GDP per capita growth (annual %)"
+# [86,] "NY.GDP.MKTP.KD"                 "GDP (constant 2000 US$)"  
[…]

### 2014-04-02 R/Databuilder/05 - addWDI.R

@@ -19,7 +19,11 @@ load('countryYear_ConflictData.rda')
 # [82,] "NY.GDP.MKTP.CD"                 "GDP (current US$)"  
 # [86,] "NY.GDP.MKTP.KD"                 "GDP (constant 2000 US$)"  
 # [87,] "NY.GDP.MKTP.KD.ZG"              "GDP growth (annual %)"
-wbData=WDI(country='all', indicator=c("BX.KLT.DINV.CD.WD","AG.LND.TOTL.K2", "NY.GDP.DEFL.KD.ZG", "NY.GDP.PCAP.KD", "NY.GDP.PCAP.KD.ZG", "NY.GDP.MKTP.CD", "NY.GDP.MKTP.KD", "NY.GDP.MKTP.KD.ZG"), start=1988, end=2010, extra=T)
+wbData=WDI(country='all', 
+	indicator=c("BX.KLT.DINV.CD.WD","AG.LND.TOTL.K2", "NY.GDP.DEFL.KD.ZG", 
+		"NY.GDP.PCAP.KD", "NY.GDP.PCAP.KD.ZG", "NY.GDP.MKTP.CD", 
+		"NY.GDP.MKTP.KD", "NY.GDP.MKTP.KD.ZG"), 
+	start=1988, end=2010, extra=T)
 
 # Add cnames to this shit
 wbData$cname = countrycode(wbData$iso2c, 'iso2c', 'country.name')

### 2014-04-02 R/vizResults.R

@@ -192,3 +192,33 @@ ggsimplot = function(sims=10000, simData, vars, vi, vRange, ostat=median,
   temp
 }
 #######################################################################
+
+#######################################################################
+# Par mfrow equiv for ggplot
+multiplot <- function(plots, cols) {
+  require(grid)
+  
+  # Make a list from the ... arguments and plotlist
+  # plots <- c(list(...), plotlist)
+  
+  numPlots = length(plots)
+  
+  # Make the panel
+  plotCols = cols                          # Number of columns of plots
+  plotRows = ceiling(numPlots/plotCols) # Number of rows needed, calculated from # of cols
+  
+  # Set up the page
+  grid.newpage()
+  pushViewport(viewport(layout = grid.layout(plotRows, plotCols)))
+  vplayout <- function(x, y)
+    viewport(layout.pos.row = x, layout.pos.col = y)
+  
+  # Make each plot, in the correct location
+  for (i in 1:numPlots) {
+    curRow = ceiling(i/plotCols)
+    curCol = (i-1) %% plotCols + 1
+    print(plots[[i]], vp = vplayout(curRow, curCol ))
+  }
+  
+}
+#######################################################################

### 2014-04-02 LaTeX/RhodiumLit.tex
minor edits

@@
 
-\cite{collier:1999} identifies five avenues through with civil conflict can impede economic performance: through the \textit{destruction} of resources, through \textit{disruption} of social and economic activity, through \textit{diversion} of resources to the war effort, through \textit{dissaving}, and through \textit{portfolio substition} or divestment.
+\cite{collier:1999} identifies five avenues through which civil conflict can impede economic performance: through the \textit{destruction} of resources, through \textit{disruption} of social and economic activity, through \textit{diversion} of resources to the war effort, through \textit{dissaving}, and through \textit{portfolio substition} or divestment.
 Of course, these mechanisms are related to one another; portfolio substitution may be exacerbated by the destruction of resources or the distruption of socioeconomic activity.
@@
 
-In accord with this theory, \cite{fearon:laitin:2003} aruge that poor economic growth is the primary condition conducive for civil war.
+In accordance with this theory, \cite{fearon:laitin:2003} aruge that poor economic growth is the primary condition conducive for civil war.
 More specifically, they believe that strong economic growth proxies for robust governance and that states with low GDP growth likely have infrastructures that are unable to implement counterinsurgent policies.

### 2014-04-02 LaTeX/PreezeText.tex
skeleton for preeze

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\titlepage
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Motivating Question}

\begin{itemize}
	\item When and why do states comply with economic sanctions? 
	\item We demonstrate the necessity of incorporating network dynamics into understanding the time until sanction compliance
	\item We show that the connectivity between target and sender states--in terms of cultural similarities, geographical proximity, and alliance patterns--plays an important and previously overlooked role on sanction outcomes
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Sanctions and domestic factors}
Previous literature has suggested sanctions ``work'' by destablizing leaders and other domestic factors:
\begin{itemize}
	\item Marinov 2005
	\item Lektzian and Souva 2003
\end{itemize}

Such work has often utilized a duration modeling approach to capture the time until sanction compliance: 
\begin{itemize}
	\item Bolks Al-Sowayel 2000
	\item McGillivray and Stam 2004
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Sanctions and Network Dynamics}
Domestic conditions are important but cross-cutting relationships and network dynamics should play a key role in understanding sanction outcomes as well:
\begin{itemize}
	\item Bapat and Morgan 2009
	\item Cranmer and Heinrich 2013
\end{itemize}

The importance of network dynamics are noted in other IR works:
\begin{itemize}
	\item Ward, Siverson, and Xao 2007
	\item Cranmer and Desmarais 2012
\end{itemize} 
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Understanding the Network:}
\framesubtitle{1984 Sanction Spaghetti Bowl}
\vspace{-0.25cm}
% \begin{figure}[ht]
%   \centering
%   \includegraphics[width=0.74\textwidth]{84net}
% \end{figure}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Untangling Spaghetti:}
\framesubtitle{South Africa 1984 Sanction Case Network}

\vspace{-.4cm}
% \begin{figure}[ht]
% 	\centering
% 	\includegraphics[width=1.05\textwidth]{saneti}
% \end{figure}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Untangling Spaghetti:}
\framesubtitle{South Africa 1984 Aggregate Network}

% \begin{figure}[ht]
% 	\centering
% 	\includegraphics[width=0.75\textwidth]{sanet}
% \end{figure}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Bridging the Gaps}
We suggest that present duration approaches fail to incorporate the network pressures instrinstic to international sanction processes

\begin{itemize}
	\item Target states face sanctioners to whom they have a variety of relationships
	\item At any given point in time, target states may be faced with a multitude of sanction cases
	\item We present a duration model that incorporates these network dynamics
	\item We also explore the role domestic institutions play in conditioning network effects
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Network Pressure Hypotheses}
\framesubtitle{Sanction Case Network}

\begin{block}{Hypothesis 1}
	Sanction Case Network: The relationship between sender(s) and the target matters for sanction compliance: 
\end{block}

\begin{itemize}
	\item Sanctions involving coalitions of sender(s) will be more quickly resolved than sanctions sent by just one state
	\item Sanction cases where relationships are more proximate will be more quickly resolved
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Network Pressure Hypotheses}
\framesubtitle{Aggregate Network}

\begin{block}{Hypothesis 2}
	Aggregate Network: Targets of sanctions often face a multitude of sanction cases at any given point in time
\end{block}

\begin{itemize}
	\item States under the pressure of a multitude of sanctions will more quickly resolve sanction cases than those facing only a few
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Institutions Hypothesis}

\begin{block}{\textbf{Hypothesis 3}}
	Target states with stronger democratic institutions that are under the pressure of sanctions will more quickly comply than those with less democratic institutions
\end{block}

\begin{itemize}
	\item Sanctions are designed to impose costs on key groups within countries
	\item Affected groups will lobby the government to reach an accommodation with sanctioning states
	\item The ability to successfully lobby is dependent upon political institutions (Manin, Przeworski and Stokes 1999; Barro 1973; Ferejohn 1986)
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Conceptualizing Networks}

Two types of network effects that we capture:

\begin{itemize}
	\item Sanction Case Network
	\begin{itemize}
		\item Number of senders associated with a sanction case
		\item Distance: The average distance between sender(s) and the receiver
		\item Trade: The share of total trade that the sender(s) make up for the receiver		
		\item Alliances: The proportion of sender(s) that are allied with the receiver
		\item IGOs: The average number of common IGOs that the sender(s) and receiver belong to
		\item Religion: Similarity of religious group makeups between sender(s) and the receiver
	\end{itemize}
	\item Aggregate Network
	\begin{itemize}
		\item Sanctions Received: Total number of sanctions to which the target state is currently exposed
	\end{itemize}
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Data}

\begin{itemize}
	\item Threat and Imposition of Sanctions Database (Morgan 2009) provides information on 1,412 sanction case initiations and outcomes from 1945 to 2005 
		\vspace{0.1cm}
	\item Our focus is economic sanctions and the period of 1984 to 2005, providing us with 184 sanction cases \\
		\vspace{0.1cm}
	\item Our unit of analysis is the sanction case-year, providing us with a total of 1,920 observations
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Dependent Variable}
\framesubtitle{Sanction Compliance}

\begin{block}{Conceptualization of Dependent Variable}
	We define compliance as:
	\begin{itemize}
		\item Complete/Partial Acquiescence by Target to threat
		\item Negotiated Settlement
		\item Total/Partial Acquiescence by the Target State following sanctions imposition
		\item Negotiated Settlement following sanctions imposition
	\end{itemize}
\end{block}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Estimated Duration Model}

% \vspace{-0.5cm}
\begin{block}{Time-Varying Duration Model}
	\begin{align*}
		Compliance_{i,t} =\; & No. \; Senders_{j} + Distance_{j,t} + Trade_{j,t}  + \\
		 &Ally_{j,t} + IGOs_{j,t} + Religion_{j,t} +\\
 		 &Sanc. \; Rec'd_{i,t} + \\
		 &Constraints_{i,t} + GDP \; Capita_{i,t-1} +\\
		 & Internal \; Conflict_{i,t} +\\
		 &Constraints_{i,t}*No. \; Senders_{j} + \epsilon_{i,t}
	\end{align*}
\end{block}

\begin{itemize}
	\item $i$ represents the target of the sanction
	\item $j$ represents the relationship between the set of sender(s) for a particular sanction case and $i$
	\item $t$ the time period
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Results}
\framesubtitle{Duration Model Summary}

\footnotesize{
	\begin{table}[ht]
		\begin{center}
		\begin{tabular}{lccc}
		  \hline\hline
		 &$\hat{\beta}$&$\hat{\sigma}$& Pr($>$$|$z$|$) \\ 
		  \hline
		  Case Network Measures \\
		  \;\;\;   Number of senders & 0.59 & 0.15 & 0.00 \\ 
		  \;\;\;   Distance & -218.15 & 97.87 & 0.03 \\
		  \;\;\;   Trade & 0.65 & 0.85 & 0.44 \\ 
		  \;\;\;   Ally & 1.12 & 0.49 & 0.02 \\ 
		  \;\;\;   IGOs & -0.03 & 0.01 & 0.04 \\ 
		  \;\;\;   Religion & -0.90 & 0.40 & 0.02 \\ 
		  Aggregate Network Measure \\
		  \;\;\;   Sanc. Recieved & -0.06 & 0.09 & 0.49 \\ 
		  Controls \\
		  \;\;\;   Constraints & 0.02 & 0.04 & 0.69 \\ 		  
		  \;\;\;   GDP per Capita (lagged) & -0.00 & 0.00 & 0.43 \\ 
		  \;\;\;   Internal Conflict & -0.03 & 0.08 & 0.74 \\ 
		   \hline
		   Time at risk = 1,027 &&&\\
			 Number of cases = 154 &&&\\
		   Number of compliances = 44 &&&\\
		  \hline\hline
		\end{tabular}
		\end{center}
	\end{table}
}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Results:}
\framesubtitle{Duration Model with Interaction}

\footnotesize{
	\begin{table}[ht]
		\begin{center}
			\begin{tabular}{lccc}
			\hline\hline
			&$\hat{\beta}$&$\hat{\sigma}$& Pr($>$$|$z$|$) \\
			\hline
			Case Network Measures \\		
			\;\;\; Number of senders & 1.21 & 0.36 & 0.00 \\ 
			\;\;\; Senders*Constraints & -1.66 & 0.92 & 0.07 \\ 		
			\;\;\; Distance & -253.00 & 102.73 & 0.01 \\ 		
			\;\;\; Trade & 0.50 & 0.84 & 0.55 \\ 
			\;\;\; Ally & 1.44 & 0.54 & 0.01 \\ 
			\;\;\; IGOs & -0.02 & 0.01 & 0.12 \\		
			\;\;\; Religion & -1.33 & 0.45 & 0.00 \\ 
			Aggregate Network Measures \\		
			\;\;\; Rec'd Sanctions & -0.13 & 0.10 & 0.20 \\ 
			Controls \\		
			\;\;\; Constraints & -0.58 & 1.61 & 0.72 \\ 
			\;\;\; GDP per Capita (lagged) & -0.00 & 0.00 & 0.38 \\ 
			\;\;\; Internal Conflcit & 0.03 & 0.09 & 0.71 \\ 
			\hline
			Time at risk = 1,027 &&&\\
			Number of cases = 154 &&&\\
			Number of compliances = 44 &&&\\
			\hline\hline
		\end{tabular}
		\end{center}
	\end{table}
}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Results:}
\framesubtitle{Survival Probability by Number of Senders in a Sanction Case}

% \vspace{0.7cm}
% \begin{figure}[ht]
% 	\centering
% 	\includegraphics[width=1\textwidth]{nosSurv}
% \end{figure}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Results:}	
\framesubtitle{Survival Probability by Other Network Variables Relating to Sanction Case}

% \begin{figure}[ht]
% 	\centering
% 	\includegraphics[width=1\textwidth]{oNet}
% \end{figure}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Next Steps}

\begin{itemize}
	\item The relationships between sender(s) of a sanction and the target matter, and the specific facets of the relationship that matter extend beyond trade
	\item So far we have not found that the aggregate network structure faced by a state matters for compliance
	\begin{itemize}
		\item There are other conceptualizations of aggregate network pressures that we can pursue
	\end{itemize}
	\item We also did not find support for the institutions hypothesis
	\begin{itemize}
		\item Greater specification of this hypothesis is likely necessary
	\end{itemize}
\end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-04-02 LaTeX/PreezeText.tex
Fixed name. Added question.

@@
 
-\begin{itemize}
-	\item When and why do states comply with economic sanctions? 
-	\item We demonstrate the necessity of incorporating network dynamics into understanding the time until sanction compliance
-	\item We show that the connectivity between target and sender states--in terms of cultural similarities, geographical proximity, and alliance patterns--plays an important and previously overlooked role on sanction outcomes
-\end{itemize}
+Why do some states facing internal armed conflict suffer severe economic consequences while others enjoy continued growth?
 

### 2014-04-02 LaTeX/PreezeText.tex
preeze draft

@@
 
-Why do some states facing internal armed conflict suffer severe economic consequences while others enjoy continued growth?
-
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{Sanctions and domestic factors}
-Previous literature has suggested sanctions ``work'' by destablizing leaders and other domestic factors:
+\begin{block}{Puzzle}
+High variation in economic performance between countries in the midst of internal armed conflict
 \begin{itemize}
-	\item Marinov 2005
-	\item Lektzian and Souva 2003
-\end{itemize}
-
-Such work has often utilized a duration modeling approach to capture the time until sanction compliance: 
-\begin{itemize}
-	\item Bolks Al-Sowayel 2000
-	\item McGillivray and Stam 2004
-\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{Sanctions and Network Dynamics}
-Domestic conditions are important but cross-cutting relationships and network dynamics should play a key role in understanding sanction outcomes as well:
-\begin{itemize}
-	\item Bapat and Morgan 2009
-	\item Cranmer and Heinrich 2013
-\end{itemize}
-
-The importance of network dynamics are noted in other IR works:
-\begin{itemize}
-	\item Ward, Siverson, and Xao 2007
-	\item Cranmer and Desmarais 2012
-\end{itemize} 
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{Understanding the Network:}
-\framesubtitle{1984 Sanction Spaghetti Bowl}
-\vspace{-0.25cm}
-% \begin{figure}[ht]
-%   \centering
-%   \includegraphics[width=0.74\textwidth]{84net}
-% \end{figure}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{Untangling Spaghetti:}
-\framesubtitle{South Africa 1984 Sanction Case Network}
-
-\vspace{-.4cm}
-% \begin{figure}[ht]
-% 	\centering
-% 	\includegraphics[width=1.05\textwidth]{saneti}
-% \end{figure}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{Untangling Spaghetti:}
-\framesubtitle{South Africa 1984 Aggregate Network}
-
-% \begin{figure}[ht]
-% 	\centering
-% 	\includegraphics[width=0.75\textwidth]{sanet}
-% \end{figure}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{Bridging the Gaps}
-We suggest that present duration approaches fail to incorporate the network pressures instrinstic to international sanction processes
-
-\begin{itemize}
-	\item Target states face sanctioners to whom they have a variety of relationships
-	\item At any given point in time, target states may be faced with a multitude of sanction cases
-	\item We present a duration model that incorporates these network dynamics
-	\item We also explore the role domestic institutions play in conditioning network effects
-\end{itemize}
-
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{Network Pressure Hypotheses}
-\framesubtitle{Sanction Case Network}
-
-\begin{block}{Hypothesis 1}
-	Sanction Case Network: The relationship between sender(s) and the target matters for sanction compliance: 
-\end{block}
-
-\begin{itemize}
-	\item Sanctions involving coalitions of sender(s) will be more quickly resolved than sanctions sent by just one state
-	\item Sanction cases where relationships are more proximate will be more quickly resolved
-\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{Network Pressure Hypotheses}
-\framesubtitle{Aggregate Network}
-
-\begin{block}{Hypothesis 2}
-	Aggregate Network: Targets of sanctions often face a multitude of sanction cases at any given point in time
-\end{block}
-
-\begin{itemize}
-	\item States under the pressure of a multitude of sanctions will more quickly resolve sanction cases than those facing only a few
-\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{Institutions Hypothesis}
-
-\begin{block}{\textbf{Hypothesis 3}}
-	Target states with stronger democratic institutions that are under the pressure of sanctions will more quickly comply than those with less democratic institutions
-\end{block}
-
-\begin{itemize}
-	\item Sanctions are designed to impose costs on key groups within countries
-	\item Affected groups will lobby the government to reach an accommodation with sanctioning states
-	\item The ability to successfully lobby is dependent upon political institutions (Manin, Przeworski and Stokes 1999; Barro 1973; Ferejohn 1986)
-\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{Conceptualizing Networks}
-
-Two types of network effects that we capture:
-
-\begin{itemize}
-	\item Sanction Case Network
-	\begin{itemize}
-		\item Number of senders associated with a sanction case
-		\item Distance: The average distance between sender(s) and the receiver
-		\item Trade: The share of total trade that the sender(s) make up for the receiver		
-		\item Alliances: The proportion of sender(s) that are allied with the receiver
-		\item IGOs: The average number of common IGOs that the sender(s) and receiver belong to
-		\item Religion: Similarity of religious group makeups between sender(s) and the receiver
-	\end{itemize}
-	\item Aggregate Network
-	\begin{itemize}
-		\item Sanctions Received: Total number of sanctions to which the target state is currently exposed
-	\end{itemize}
-\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{Data}
-
-\begin{itemize}
-	\item Threat and Imposition of Sanctions Database (Morgan 2009) provides information on 1,412 sanction case initiations and outcomes from 1945 to 2005 
-		\vspace{0.1cm}
-	\item Our focus is economic sanctions and the period of 1984 to 2005, providing us with 184 sanction cases \\
-		\vspace{0.1cm}
-	\item Our unit of analysis is the sanction case-year, providing us with a total of 1,920 observations
-\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{Dependent Variable}
-\framesubtitle{Sanction Compliance}
-
-\begin{block}{Conceptualization of Dependent Variable}
-	We define compliance as:
-	\begin{itemize}
-		\item Complete/Partial Acquiescence by Target to threat
-		\item Negotiated Settlement
-		\item Total/Partial Acquiescence by the Target State following sanctions imposition
-		\item Negotiated Settlement following sanctions imposition
+\item Mexico
+\item India
+\item Nicaragua
 \end{itemize}
@@
 \begin{frame}
-\frametitle{Estimated Duration Model}
-
-% \vspace{-0.5cm}
-\begin{block}{Time-Varying Duration Model}
-	\begin{align*}
-		Compliance_{i,t} =\; & No. \; Senders_{j} + Distance_{j,t} + Trade_{j,t}  + \\
-		 &Ally_{j,t} + IGOs_{j,t} + Religion_{j,t} +\\
- 		 &Sanc. \; Rec'd_{i,t} + \\
-		 &Constraints_{i,t} + GDP \; Capita_{i,t-1} +\\
-		 & Internal \; Conflict_{i,t} +\\
-		 &Constraints_{i,t}*No. \; Senders_{j} + \epsilon_{i,t}
-	\end{align*}
-\end{block}
+\frametitle{Literature Review}
 
 \begin{itemize}
-	\item $i$ represents the target of the sanction
-	\item $j$ represents the relationship between the set of sender(s) for a particular sanction case and $i$
-	\item $t$ the time period
+	\item Civil War $\rightarrow$ Economic Performance
+	\item Economic Performance $\rightarrow$ Civil War
+	\item Disaggregating Civil Wars
 \end{itemize}
@@
 \begin{frame}
-\frametitle{Results}
-\framesubtitle{Duration Model Summary}
+\frametitle{Disaggregating Conflict and Growth}
 
-\footnotesize{
-	\begin{table}[ht]
-		\begin{center}
-		\begin{tabular}{lccc}
-		  \hline\hline
-		 &$\hat{\beta}$&$\hat{\sigma}$& Pr($>$$|$z$|$) \\ 
-		  \hline
-		  Case Network Measures \\
-		  \;\;\;   Number of senders & 0.59 & 0.15 & 0.00 \\ 
-		  \;\;\;   Distance & -218.15 & 97.87 & 0.03 \\
-		  \;\;\;   Trade & 0.65 & 0.85 & 0.44 \\ 
-		  \;\;\;   Ally & 1.12 & 0.49 & 0.02 \\ 
-		  \;\;\;   IGOs & -0.03 & 0.01 & 0.04 \\ 
-		  \;\;\;   Religion & -0.90 & 0.40 & 0.02 \\ 
-		  Aggregate Network Measure \\
-		  \;\;\;   Sanc. Recieved & -0.06 & 0.09 & 0.49 \\ 
-		  Controls \\
-		  \;\;\;   Constraints & 0.02 & 0.04 & 0.69 \\ 		  
-		  \;\;\;   GDP per Capita (lagged) & -0.00 & 0.00 & 0.43 \\ 
-		  \;\;\;   Internal Conflict & -0.03 & 0.08 & 0.74 \\ 
-		   \hline
-		   Time at risk = 1,027 &&&\\
-			 Number of cases = 154 &&&\\
-		   Number of compliances = 44 &&&\\
-		  \hline\hline
-		\end{tabular}
-		\end{center}
-	\end{table}
-}
+\begin{block}{Our argument}
+State economic performance in countries experiencing civil conflict is conditional on the proximity of conflict from major population, economic, and resource centers
+\end{block}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{frame}
+\frametitle{FARC guerillas \& the Colombian government}
+
+\begin{quote}FARC's strategy and [beliefs have] always been to make economic pressure on both, multinational companies and the Colombian government.
+This has been done by attacking oil and natural gas infrastructure affecting companies such as Pacific Rubiales Energy, Oxy and Ecopetrol.
+For non-fuel related international companies with subsidiaries in Colombia, such as Goodyear, Nestle, Microsoft, Toyota, among others, FARC’s modus operandi was mainly racketeering, kidnappings and extortion.
+(Flannery 2012)\end{quote}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Conflict \& City Data}
+
+\vspace{-0.25cm}
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=1\textwidth]{CityConfMap-crop}
+\end{figure}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{frame}
-\frametitle{Results:}
-\framesubtitle{Duration Model with Interaction}
+\frametitle{Aggregating to Country-Year}
 
-\footnotesize{
-	\begin{table}[ht]
-		\begin{center}
-			\begin{tabular}{lccc}
-			\hline\hline
-			&$\hat{\beta}$&$\hat{\sigma}$& Pr($>$$|$z$|$) \\
-			\hline
-			Case Network Measures \\		
-			\;\;\; Number of senders & 1.21 & 0.36 & 0.00 \\ 
-			\;\;\; Senders*Constraints & -1.66 & 0.92 & 0.07 \\ 		
-			\;\;\; Distance & -253.00 & 102.73 & 0.01 \\ 		
-			\;\;\; Trade & 0.50 & 0.84 & 0.55 \\ 
-			\;\;\; Ally & 1.44 & 0.54 & 0.01 \\ 
-			\;\;\; IGOs & -0.02 & 0.01 & 0.12 \\		
-			\;\;\; Religion & -1.33 & 0.45 & 0.00 \\ 
-			Aggregate Network Measures \\		
-			\;\;\; Rec'd Sanctions & -0.13 & 0.10 & 0.20 \\ 
-			Controls \\		
-			\;\;\; Constraints & -0.58 & 1.61 & 0.72 \\ 
-			\;\;\; GDP per Capita (lagged) & -0.00 & 0.00 & 0.38 \\ 
-			\;\;\; Internal Conflcit & 0.03 & 0.09 & 0.71 \\ 
-			\hline
-			Time at risk = 1,027 &&&\\
-			Number of cases = 154 &&&\\
-			Number of compliances = 44 &&&\\
-			\hline\hline
-		\end{tabular}
-		\end{center}
-	\end{table}
-}
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=.6\textwidth]{colombiaMap-crop}
+\end{figure}
+
 \end{frame}
@@
 \begin{frame}
-\frametitle{Results:}
-\framesubtitle{Survival Probability by Number of Senders in a Sanction Case}
+\frametitle{Estimation Approach}
 
-% \vspace{0.7cm}
-% \begin{figure}[ht]
-% 	\centering
-% 	\includegraphics[width=1\textwidth]{nosSurv}
-% \end{figure}
+\begin{align*}
+	\% \Delta GDP_{i,t} &= \beta_{1}(Upper \; Income_{i,t}) \\
+	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t}) \;+\; \beta_{3}(Ln(Conflict \; Area)_{i,t}) \\
+	& \;+\; \beta_{4}(Ln(Min. \; Conflict \; Dist.)_{i,t}) \;+\; \beta_{5}(Conflict \; Type_{i,t}) \\
+	& \;+\; \beta_{6}(Conflict \; Duration_{i,t}) \;+\; \beta_{7}(Inflation_{i,t-1}) \\
+	& \;+\; \beta_{8}(Ln(Land \; Area)_{i,t}) \;+\; \alpha_{i} + \gamma_{t} + \mu_{i,t}
+\end{align*}
 
@@
 \begin{frame}
-\frametitle{Results:}	
-\framesubtitle{Survival Probability by Other Network Variables Relating to Sanction Case}
+\frametitle{Findings}
 
-% \begin{figure}[ht]
-% 	\centering
-% 	\includegraphics[width=1\textwidth]{oNet}
-% \end{figure}
+\begin{figure}[ht]
+	\centering
+	\resizebox{.8\textwidth}{!}{\input{mod3CoefPlot.tex}}
+\end{figure}
 
@@
 
+\begin{frame}
+\frametitle{Substantive Effects}
+
+\begin{figure}[ht]
+	\centering
+	\resizebox{.9\textwidth}{!}{\input{mod3SimPlot.tex}}
+\end{figure}
+
+\end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}
-\frametitle{Next Steps}
+\frametitle{Conclusions \& Next Steps}
 
+\begin{block}{Conclusions}
 \begin{itemize}
-	\item The relationships between sender(s) of a sanction and the target matter, and the specific facets of the relationship that matter extend beyond trade
-	\item So far we have not found that the aggregate network structure faced by a state matters for compliance
+	\item Novel approach in the study of civil conflict to distinguish between spatially dissimilar events
+	\item Proximity of conflict to major cities explains disparate economic outcomes
+\end{itemize}
+\end{block}
+
+\begin{block}{Next Steps}
 \begin{itemize}
-		\item There are other conceptualizations of aggregate network pressures that we can pursue
+\item Account for other economically important locations (e.g., oil fields)
+\item Alternative methods to address aggregation problem
+\item More refined analysis within a country using subnational economic data
 \end{itemize}
-	\item We also did not find support for the institutions hypothesis
-	\begin{itemize}
-		\item Greater specification of this hypothesis is likely necessary
-	\end{itemize}
-\end{itemize}
+\end{block}
+
 \end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-04-05 LaTeX/PreezeText.tex
MPSA presentation update

@@
 	\item Civil War $\rightarrow$ Economic Performance
+	\begin{itemize}
+	\item Collier (1999) - \emph{destruction, disruption, diversion, dissaving, portfolio substitution}
+	\item Kang \& Meernik (2005) - seek to explain rapid or stagnant post-war recovery
+	\end{itemize}
 	\item Economic Performance $\rightarrow$ Civil War
+	\begin{itemize}
+	\item Collier et al. (2003) - the conflict trap
+	\item Miguel et al (2004) - rainfall IV for economic shocks
+	\end{itemize}
 	\item Disaggregating Civil Wars
+	\begin{itemize}
+	\item Pierskalla \& Hollenbach (2013) - cell phone coverage $\rightarrow$ rebel mobilization
+	\end{itemize}
 \end{itemize}

### 2014-07-15 LaTeX/Abstract.tex
updates

@@
 We combine the conflict location data with geospatial data on economic centers, natural resource locations, and infrastructure grids to generate spatial variables that approximate how far each conflict is from centers of interest.
-We then use a hierarchical Bayesian model to estimate the effect of the spatial variables on economic performance.
-By doing so, we are able to resolve some of the tensions in the literature regarding the relationship between economic performance and civil wars.
+We then estimate the effect of the spatial variables on economic performance.
+By doing so, we are able to resolve tensions in the literature regarding the relationship between economic performance and civil wars.

### 2014-07-15 R/Databuilder/04 - DistanceCalc.R

@@ -1,8 +1,6 @@
 if(Sys.info()["user"]=="janus829"){source('/Users/janus829/Desktop/Research/Rhodium/R/setup.R')}
 if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
 
-library(shapefiles)
-
 # Load City pop data
 setwd(pathData)
 load("cityTotPopLatLongvFinal.rda")
@@ -21,7 +19,8 @@ prioAC=read.csv('ucdp.prio.armed.conflict.v4.2013.csv')
 
 prioData$idyear=paste0(prioData$ID, prioData$Year)
 prioAC$idyear=paste0(prioAC$ID, prioAC$YEAR)
-prioAC=merge(prioAC, prioData[,3:ncol(prioData)], by='idyear', all.x=T, all.y=T)
+prioAC=merge(prioAC, prioData[,3:ncol(prioData)], 
+  by='idyear', all.x=T, all.y=T)
 prioAC = prioAC[which(prioAC$ID %in% unique(prioData$ID)),]
 prioAC=prioAC[which(prioAC$YEAR %in%  1989:2008),]
 ##################################################################
@@ -40,10 +39,25 @@ prioAC$cname[prioAC$Location=="Sierra Leone"] <- "SIERRA LEONE"
 prioAC$cname[prioAC$Location=="Chad"] <- "CHAD"
 prioAC <- prioAC[!is.na(prioAC$Latitude),]
 prioAC <- prioAC[!prioAC$Latitude<(-360),]
-prioAC$minDist <- minDist(prioAC$Latitude, prioAC$Longitude, prioAC$cname, prioAC$YEAR, fYrCty$cleanLat, fYrCty$cleanLong, fYrCty$cname, fYrCty$YearAlmanac)
-prioAC$inRadius <- inRadius(prioAC$Latitude, prioAC$Longitude, prioAC$cname, prioAC$YEAR, fYrCty$cleanLat, fYrCty$cleanLong, fYrCty$cname, fYrCty$YearAlmanac, prioAC$Radius)$value
-cityInRadius <- inRadius(fYrCty$cleanLat, fYrCty$cleanLong, fYrCty$cname, fYrCty$YearAlmanac, prioAC$Latitude, prioAC$Longitude, prioAC$cname, prioAC$YEAR, prioAC$Radius)
[…]

### 2014-07-15 R/Databuilder/05 - addWDI.R

@@ -25,7 +25,7 @@ wbData=WDI(country='all',
 		"NY.GDP.MKTP.KD", "NY.GDP.MKTP.KD.ZG"), 
 	start=1988, end=2010, extra=T)
 
-# Add cnames to this shit
+# Add cnames
 wbData$cname = countrycode(wbData$iso2c, 'iso2c', 'country.name')
 wbData = wbData[!is.na(wbData$cname),]
 wbData$ccode = panel$ccode[match(wbData$cname, panel$cname)]
@@ -40,6 +40,6 @@ yData = merge(yData, wbData[,c(4:11,17,ncol(wbData))], by='cyear', all.x=T, all.
 wbData$cyear = paste0(wbData$ccode, wbData$year+1)
 yData = merge(yData, wbData[,c(4:11,17,ncol(wbData))], by='cyear', all.x=T, all.y=F, suffixes=c("_l1","_p1"))
 
-# Save this things
+# Save
 setwd(pathData)
 save(yData, file='combinedData.rda')

### 2014-07-15 R/setup.R

@@ -22,6 +22,7 @@ load('panel.rda')
 # Loading libraries and functions
 require(ggplot2)
 theme_set(theme_bw())
+require(grid)
 require(tikzDevice)
 require(RColorBrewer)
 
@@ -30,6 +31,7 @@ require(foreign)
 require(doBy)
 require(lme4)
 
+require(shapefiles)
 require(cshapes)
 require(WDI)
 require(countrycode)
@@ -37,3 +39,4 @@ require(countrycode)
 # Helpful functions
 numSM=function(x){as.numeric(as.character(x))}
 charSM=function(x){as.character(x)}
+rmse=function(x){sqrt( mean( (residuals(x)^2) ) )}

### 2014-08-31 LaTeX/RhodiumIntro.tex
Tweaks in progress to intro and theory.

@@
 This contrasts greatly with the economic fortunes of other countries in the midst of civil war where the economies have plumetted.
+\cite{collier:elliott:etal:2003}, for instance, describe civil war as ``development in reverse.''  ``The overall economic and political legacy from civil war,'' they write, ``is thus sufficiently adverse that rapid recovery is unlikely.''  Nevertheless, some countries appear to weather domestic conflict better than others.
 

### 2014-08-31 LaTeX/RhodiumTheory.tex
Tweaks in progress to intro and theory.

@@
 We suspect that substate factors will determine the economic impacts of civil conflict.
-While lootable resources are often pointed to as sources of funding for rebel groups, these same resources are often critical to state economic performance.
-The loss of safe access to these resources due to internal conflict should adversly affect a state's economy.
-Companies that rely on the extraction of resources may find themselves unable to access those resources if armed conflict is proximately located to the resource sites.
-Therefore, we expect state economic performance to be directly related to the distance from conflict zones to valuable resources.
-
-Other resources are also valuable to a state's ability to conduct business.
 In particular, citizens must be able and willing to participate in commerce.
@@
 
-Finally, the perception of violence near major cities and resource centers should negatively impact foreign investment.
-Investors will react negatively to news that violence is occuring near major cities and resources.
-Investment is generally contingent on the expectation of a stable labor base and, sometimes, reliable access to resources.
-Conflicts that appear to threaten these, whether they do or not, should correspond to a decrease in foreign investment.\footnote{While we intend to test each of these hypotheses carefully, our project in its current form addresses only the second hypothesis - the effect of conflict distance from city centers on aggregate state economic performance.
-Future iterations of this paper will also include tests of the remaining hypotheses using foreign investment, economic growth, and domestic investment as dependent variables.}
-
-While these hypotheses may resemble those of \cite{imai:weinstein:2000}, ours differs in the hypothesized mechanism through which conflict affects economic performance.
+While this hypothesis may resemble those of \cite{imai:weinstein:2000}, ours differs in the hypothesized mechanism through which conflict affects economic performance.
 While we do not disagree that the spread of a conflict could impact state economic prospects, we argue that conflict area is not necessary for adverse economic performance.

### 2014-08-31 LaTeX/RhodiumTheory.tex
A little bit on Mexico added.

@@
 
-These hypotheses do not seem unknown to armed actors.
+This hypothesis does not seem unknown to armed actors.
 The guerilla group Fuerzas Armadas Revolucionarios de Colombia (FARC) appears to have internalized these mechanisms.
@@
 Indeed, for much of this period, India has experienced relatively robust economic growth.
+Mexico, now nearly a decade into a violent and complicated conflict between several organized criminal enterprises and the federal government, has maintained healthy economic performance.
+For much of this time, the cartel violence generally occurred in rural areas along drug trafficking routes and not within major cities.
+\cite{beittel:2011} writes in 2011 that ``drug trafficking-related killings remain concentrated in a relatively few cities,'' but notes that the violence was beginning to expand in geographic range by 2010.
 

### 2014-09-11 LaTeX/RhodiumTheory.tex
Added to theory section (incomplete)

@@
 Violence near major population centers not only threatens residents directly, but impedes business by threatening trade between the population center and other cities or rural areas.
-For this same reason, violence near important transporation hubs such as airports and sea ports should threaten business.
 
@@
 Conflict area is only one possible proxy for overall destructiveness.
-However, conflicts with smaller spatial areas can be similarly disruptive if they are centered near (and impede access to) those resources outlined above.
-In fact, we feel measures of proximity rather than spread are more appropriate to test the hypothesis that conflict obstucts vital economic activity.
+However, conflicts with smaller spatial areas can be similarly disruptive if they are centered near (and impede access to) the urban centers described above.
+In fact, we anticipate measures of proximity rather than spread to be more appropriate to test the hypothesis that conflict obstructs vital economic activity.
+
+\cite{glaeser:shapiro:2001} discuss the historic role of cities in warfare and their current role with respect to terrorism.
+Cities, they argue, once provided safe haven in the midst of conflict; defense of a concentrated population is easier than defense of a dispersed population.
+However, as the tactics of warfare have shifted over the centuries, the relationship between violent conflict and cities has become more complex.
+Their dense populations also tempt belligerents and maximize the impact to cost ratio of a given violent action.
+Finally, the authors point out that warfare destroys transportation infrastructure which can interfere both with commerce and with rebuilding during a conflict.
+
+That armed conflict near and within cities should impact national economic performance is not surprising given the existing body of literature that suggests a close relationship between urban agglomeration and national economies.
+\cite[p.
+137]{quigley:1998} concludes that ``large cities have been and will continue to be an important source of economic growth.''  This echoes the work of Jane Jacobs who argued that cities are the primary motivators of state economies and should be given primacy over the national state in economic analysis \citep{jacobs:1969,jacobs:1984}.
+In the past three decades, economists have begun
 
@@
 We turn now to an empirical test of our proposition.
-Using a dataset that includes 510 instances of civil war from 71 different countries, we seek to determine how the geography of conflict impacts state economic outcomes.
+Using a dataset that includes 510 years of civil war from 71 different countries, we seek to determine how the geography of conflict impacts state economic outcomes.
 

### 2014-09-19 LaTeX/RhodiumTheory.tex
Added more citations to take up space.

@@
 
-\cite{glaeser:shapiro:2001} discuss the historic role of cities in warfare and their current role with respect to terrorism.
+\cite{glaeser:shapiro:2002} discuss the historic role of cities in warfare and their current role with respect to terrorism.
 Cities, they argue, once provided safe haven in the midst of conflict; defense of a concentrated population is easier than defense of a dispersed population.
@@
 \cite[p.
-137]{quigley:1998} concludes that ``large cities have been and will continue to be an important source of economic growth.''  This echoes the work of Jane Jacobs who argued that cities are the primary motivators of state economies and should be given primacy over the national state in economic analysis \citep{jacobs:1969,jacobs:1984}.
-In the past three decades, economists have begun
+137]{quigley:1998} concludes that ``large cities have been and will continue to be an important source of economic growth.''  This echoes the work of Jane Jacobs who argued that cities are the primary motivators of state economies and should be given primacy over the nation state in economic analysis \citep{jacobs:1969,jacobs:1984}.
+In the past three decades, economists have followed Jacobs' lead and investigated city-level economic drivers \citep{lucas:1988, ciccone:hall:1996, begg:1999}.
+
+We extend this line of research by conceptualizing civil wars not as homogeneous national phenomenon, but as a diverse class of violent conflict with properties that distinguish the effects of one conflict from another.
+Since urban economies are responsible for a disproportionate share of national economic performance, civil conflicts in or near these engines of commerce should likewise exert a disproportionate influence on state performance.
 
@@
 We turn now to an empirical test of our proposition.
-Using a dataset that includes 510 years of civil war from 71 different countries, we seek to determine how the geography of conflict impacts state economic outcomes.
+Using a dataset that includes 510 country-years of civil war from 71 different countries, we seek to determine how the geography of conflict impacts state economic outcomes.
 

### 2014-09-23 LaTeX/RhodiumEmp.tex
updated intro and other stuff
cleaning
updates
plots in paper

@@
 
-To measure economic performance we use annual percent change in GDP, which we collect from the World Development Indicators at the World Bank.
-We choose to focus on year over change in GDP because we expect conflicts proximate to major cities to lead to reductions in growth.\footnote{Alternative measures of economic performance would have included changes in FDI inflows or changes in GDP per capita, in using either of these measures are results remain relatively the same.} Unlike much of the extant literature in constructing our dependent variable we focus on year over change instead of a ten year average.
+To measure economic performance we use logged, annual percent change in GDP, which we collect from the World Development Indicators at the World Bank.
+We choose to focus on year over change in GDP because we expect conflicts proximate to major cities to lead to reductions in growth.\footnote{Alternative measures of economic performance would have included changes in FDI inflows or changes in GDP per capita, in using either of these measures our results remain relatively the same.} Unlike much of the extant literature in constructing our dependent variable we focus on year over change instead of a ten year average.
 We believe this approach to be superior because it allows us to estimate the direct effect of the conflict on economic performance in that year.
@@
 In total this dataset provides us with almost 800 geo-referenced conflict-year cases.
+
+% Might want to drop this stuff about getting city data from the almanac
 
@@
 
+\begin{amssidewaysfigure}
+	\centering
+	\includegraphics[width=1\textwidth]{CityConfMap-crop}
+	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008.
+Countries for which no armed conflicts are recorded are shaded in grey.}
+	\label{fig:CityConfMap}
+\end{amssidewaysfigure}
+\FloatBarrier
+
 In figure \ref{fig:CityConfMap}, we show the geographic distribution of conflicts and cities.
@@
 Countries shaded in grey are those for which no armed conflict took place in this period according to the PRIO dataset.
-
-\begin{sidewaysfigure}[ht]
-	\centering
-	\includegraphics[width=.9\textwidth]{CityConfMap-crop}
-	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008.
-Countries for which no armed conflicts are recorded are shaded in grey.}
-	\label{fig:CityConfMap}
-\end{sidewaysfigure}
-\FloatBarrier
 
@@
 \section{Results}
+\label{findings}
 
@@
 
-\begin{figure}[ht]
+\begin{figure}
 	\centering
-	\resizebox{.6\textwidth}{!}{\input{mod3CoefPlot.tex}}
-	\caption{Here we show the random effect regression results on GDP growth.
+	\begin{tabular}{cc}
+		\subfloat[SubFigure 1][Capital City]{
+			\resizebox{.45\textwidth}{!}{\input{mCapCoefPlot}}
+		\label{fig:capCoef}} &
+		\subfloat[SubFigure 2][Any City]{
+			\resizebox{.45\textwidth}{!}{\input{mCityCoefPlot}}
+		\label{fig:cityCoef}}
+	\end{tabular}
+	\caption{Regression results using conflict distance from capital city on the left, and the chart on the right shows regression results using minimum conflict distance from any major city.
 Darker colors indicates that the coefficient estimate is significantly different from zero at a 95\% CI, while lighter the same for a 90\% CI.
 Grey indicates that the estimate is not significantly different from zero at either of those intervals.}
-	\label{fig:coefPlot}	
+	\label{fig:coefplot}
 \end{figure}
-\FloatBarrier
 
@@
 
-\begin{figure}[ht]
+\begin{figure}
 	\centering
-	\resizebox{.8\textwidth}{!}{\input{mod3SimPlot.tex}}
+	\begin{tabular}{cc}
+		\subfloat[SubFigure 1][Capital City]{
+			\resizebox{.45\textwidth}{!}{\input{mCapSimPlot}}
+		\label{fig:capCoef}} &
+		\subfloat[SubFigure 2][Any City]{
+			\resizebox{.45\textwidth}{!}{\input{mCitySimPlot}}
+		\label{fig:cityCoef}}
+	\end{tabular}
 	\caption{Expected values for GDP growth based on scenarios where all variables are held to their constants but Ln(Min.
@@
 \end{figure}
-\FloatBarrier
 
@@
 Nonetheless, overall our results are quite in line with our theoretical expectations.
+
+\subsection{Model Performance}
+
+RMSE: in and out of sample
+
+\begin{figure}
+	\centering
+	\resizebox{.8\textwidth}{!}{\input{rmseInOut}}
+	\caption{In and out of sample performance.}
+	\label{fig:rmsePlot}
+\end{figure}
+
+Model heterogeneity:
+
+\begin{figure}
+	\centering
+	\resizebox{.8\textwidth}{!}{\input{crossValPlot}}
+	\caption{Each row here shows the coefficient estimate of distance from rerunning the model on eight random subsamples within the dataset.
+All the covariates used in the initial models were included as well.}
+	\label{fig:crossPlot}
+\end{figure}

### 2014-09-23 LaTeX/crossValPlot.tex
plots in paper

% Created by tikzDevice version 0.7.0 on 2014-09-23 12:02:28
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 44.49, 52.60) rectangle (217.04,264.40);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] ( 44.49, 52.60) rectangle (217.04,264.40);
\definecolor[named]{drawColor}{rgb}{0.40,0.40,0.40}
\definecolor[named]{fillColor}{rgb}{0.40,0.40,0.40}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 57.11,118.35) -- ( 57.11,223.64);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 78.15, 90.67) -- ( 78.15,235.31);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 99.20,100.76) -- ( 99.20,242.14);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (120.24, 62.23) -- (120.24,203.29);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (141.28, 62.56) -- (141.28,185.24);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (162.33,109.01) -- (162.33,254.77);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (183.37, 75.66) -- (183.37,214.67);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (204.41, 97.04) -- (204.41,227.78);
\definecolor[named]{drawColor}{rgb}{0.40,0.40,0.40}
\definecolor[named]{fillColor}{rgb}{0.40,0.40,0.40}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 57.11,126.81) -- ( 57.11,215.18);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 78.15,102.30) -- ( 78.15,223.69);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 99.20,112.12) -- ( 99.20,230.77);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (120.24, 73.57) -- (120.24,191.95);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (141.28, 72.43) -- (141.28,175.38);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (162.33,120.73) -- (162.33,243.06);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (183.37, 86.84) -- (183.37,203.49);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (204.41,107.55) -- (204.41,217.27);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
\definecolor[named]{fillColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] ( 44.49, 66.40) -- (217.04, 66.40);
\definecolor[named]{drawColor}{rgb}{0.40,0.40,0.40}
\definecolor[named]{fillColor}{rgb}{0.40,0.40,0.40}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 57.11,171.00) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.15,162.99) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.20,171.45) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.24,132.76) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.28,123.90) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.33,181.89) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.37,145.16) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (204.41,162.41) circle (  2.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.06,223.64) --
	( 58.16,223.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 57.11,223.64) --
	( 57.11,118.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.06,118.35) --
	( 58.16,118.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.10,235.31) --
	( 79.21,235.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.15,235.31) --
	( 78.15, 90.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.10, 90.67) --
	( 79.21, 90.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 98.14,242.14) --
	(100.25,242.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.20,242.14) --
	( 99.20,100.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 98.14,100.76) --
	(100.25,100.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (119.19,203.29) --
	(121.29,203.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.24,203.29) --
	(120.24, 62.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (119.19, 62.23) --
	(121.29, 62.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (140.23,185.24) --
	(142.33,185.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (141.28,185.24) --
	(141.28, 62.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (140.23, 62.56) --
	(142.33, 62.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.27,254.77) --
	(163.38,254.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.33,254.77) --
	(162.33,109.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.27,109.01) --
	(163.38,109.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (182.32,214.67) --
	(184.42,214.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (183.37,214.67) --
	(183.37, 75.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (182.32, 75.66) --
	(184.42, 75.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (203.36,227.78) --
	(205.46,227.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (204.41,227.78) --
	(204.41, 97.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (203.36, 97.04) --
	(205.46, 97.04);
\definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 44.49, 52.60) rectangle (217.04,264.40);
\end{scope}
\begin{scope}
\path[clip] (249.02, 52.60) rectangle (421.58,264.40);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] (249.02, 52.60) rectangle (421.58,264.40);
\definecolor[named]{drawColor}{rgb}{0.40,0.40,0.40}
\definecolor[named]{fillColor}{rgb}{0.40,0.40,0.40}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (261.65,115.91) -- (261.65,221.67);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (282.69, 92.41) -- (282.69,232.88);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (303.73, 97.96) -- (303.73,237.72);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (324.78, 63.40) -- (324.78,200.67);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (345.82, 62.23) -- (345.82,180.88);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (366.86,111.64) -- (366.86,254.77);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (387.91, 79.34) -- (387.91,214.49);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (408.95, 95.65) -- (408.95,223.62);
\definecolor[named]{drawColor}{rgb}{0.40,0.40,0.40}
\definecolor[named]{fillColor}{rgb}{0.40,0.40,0.40}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (261.65,124.41) -- (261.65,213.17);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (282.69,103.70) -- (282.69,221.59);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (303.73,109.19) -- (303.73,226.48);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (324.78, 74.43) -- (324.78,189.64);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (345.82, 71.76) -- (345.82,171.34);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (366.86,123.15) -- (366.86,243.27);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (387.91, 90.21) -- (387.91,203.63);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (408.95,105.94) -- (408.95,213.34);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
\definecolor[named]{fillColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (249.02, 72.38) -- (421.58, 72.38);
\definecolor[named]{drawColor}{rgb}{0.40,0.40,0.40}
\definecolor[named]{fillColor}{rgb}{0.40,0.40,0.40}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (261.65,168.79) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.69,162.65) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (303.73,167.84) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (324.78,132.03) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (345.82,121.55) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (366.86,183.21) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (387.91,146.92) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (408.95,159.64) circle (  2.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (260.60,221.67) --
	(262.70,221.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (261.65,221.67) --
	(261.65,115.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (260.60,115.91) --
	(262.70,115.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (281.64,232.88) --
	(283.74,232.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (282.69,232.88) --
	(282.69, 92.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (281.64, 92.41) --
	(283.74, 92.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (302.68,237.72) --
	(304.79,237.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (303.73,237.72) --
	(303.73, 97.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (302.68, 97.96) --
	(304.79, 97.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (323.73,200.67) --
	(325.83,200.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (324.78,200.67) --
	(324.78, 63.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (323.73, 63.40) --
	(325.83, 63.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.77,180.88) --
	(346.87,180.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (345.82,180.88) --
	(345.82, 62.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.77, 62.23) --
	(346.87, 62.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.81,254.77) --
	(367.92,254.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (366.86,254.77) --
	(366.86,111.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.81,111.64) --
	(367.92,111.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (386.85,214.49) --
	(388.96,214.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (387.91,214.49) --
	(387.91, 79.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] (386.85, 79.34) --
	(388.96, 79.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] (407.90,223.62) --
	(410.00,223.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (408.95,223.62) --
	(408.95, 95.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (407.90, 95.65) --
	(410.00, 95.65);
\definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (249.02, 52.60) rectangle (421.58,264.40);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
\definecolor[named]{fillColor}{rgb}{0.80,0.80,0.80}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] ( 44.49,264.40) rectangle (217.04,277.04);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.76,267.41) {Ln(Min. Capital Dist.)$_{t-1}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
\definecolor[named]{fillColor}{rgb}{0.80,0.80,0.80}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (249.02,264.40) rectangle (421.58,277.04);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (335.30,267.41) {Ln(Min. City Dist.)$_{t-1}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 37.37, 63.09) {0.00};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 37.37,108.14) {0.02};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 37.37,153.18) {0.04};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 37.37,198.23) {0.06};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 37.37,243.28) {0.08};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (241.91, 69.07) {0.000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (241.91,122.66) {0.025};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (241.91,176.25) {0.050};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (241.91,229.84) {0.075};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 61.79, 40.81) {Fold A};

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 82.83, 40.81) {Fold B};

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (103.87, 40.81) {Fold C};

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (124.92, 40.81) {Fold D};

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (145.96, 40.81) {Fold E};

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (167.00, 40.81) {Fold F};

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (188.04, 40.81) {Fold G};

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (209.09, 40.81) {Fold H};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (266.32, 40.81) {Fold A};

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (287.37, 40.81) {Fold B};

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (308.41, 40.81) {Fold C};

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (329.45, 40.81) {Fold D};

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (350.50, 40.81) {Fold E};

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (371.54, 40.81) {Fold F};

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (392.58, 40.81) {Fold G};

\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (413.62, 40.81) {Fold H};
\end{scope}
\end{tikzpicture}

### 2014-09-23 LaTeX/mCapCoefPlot.tex
plots in paper

% Created by tikzDevice version 0.7.0 on 2014-09-23 11:36:12
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (137.46, 34.03) rectangle (277.03,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] (137.46, 34.03) rectangle (277.03,277.03);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (206.43, 49.88) -- (213.45, 49.88);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (198.47, 76.30) -- (231.75, 76.30);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (183.03,102.71) -- (196.68,102.71);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (165.42,129.12) -- (249.46,129.12);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (175.86,155.53) -- (202.88,155.53);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (207.28,181.95) -- (208.37,181.95);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (194.89,208.36) -- (229.18,208.36);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (189.15,234.77) -- (216.25,234.77);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (209.85,261.19) -- (221.60,261.19);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (206.99, 49.88) -- (212.88, 49.88);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (201.15, 76.30) -- (229.08, 76.30);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (184.13,102.71) -- (195.58,102.71);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (172.18,129.12) -- (242.71,129.12);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (178.04,155.53) -- (200.70,155.53);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (207.37,181.95) -- (208.28,181.95);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (197.65,208.36) -- (226.42,208.36);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (191.33,234.77) -- (214.07,234.77);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (210.79,261.19) -- (220.66,261.19);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
\definecolor[named]{fillColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (207.25, 34.03) -- (207.25,277.03);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.73,261.19) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (202.70,234.77) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (212.04,208.36) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.82,181.95) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.37,155.53) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.44,129.12) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.85,102.71) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.11, 76.30) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.94, 49.88) circle (  2.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.45, 48.56) --
	(213.45, 51.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.45, 49.88) --
	(206.43, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (206.43, 48.56) --
	(206.43, 51.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.75, 74.97) --
	(231.75, 77.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.75, 76.30) --
	(198.47, 76.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (198.47, 74.97) --
	(198.47, 77.62);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,line width= 0.6pt,line join=round] (196.68,101.39) --
	(196.68,104.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] (196.68,102.71) --
	(183.03,102.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (183.03,101.39) --
	(183.03,104.03);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 0.6pt,line join=round] (249.46,127.80) --
	(249.46,130.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (249.46,129.12) --
	(165.42,129.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.42,127.80) --
	(165.42,130.44);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,line width= 0.6pt,line join=round] (202.88,154.21) --
	(202.88,156.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] (202.88,155.53) --
	(175.86,155.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (175.86,154.21) --
	(175.86,156.86);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,line width= 0.6pt,line join=round] (208.37,180.63) --
	(208.37,183.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (208.37,181.95) --
	(207.28,181.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.28,180.63) --
	(207.28,183.27);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.18,207.04) --
	(229.18,209.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.18,208.36) --
	(194.89,208.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (194.89,207.04) --
	(194.89,209.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.25,233.45) --
	(216.25,236.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.25,234.77) --
	(189.15,234.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (189.15,233.45) --
	(189.15,236.09);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,line width= 0.6pt,line join=round] (221.60,259.87) --
	(221.60,262.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (221.60,261.19) --
	(209.85,261.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.85,259.87) --
	(209.85,262.51);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.46, 34.03) --
	(137.46,277.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 46.58) {World GDP Growth$_{t}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 72.99) {Democracy$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 99.40) {Ln(Inflation)$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,125.82) {Upper Income};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,152.23) {Area$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,178.64) {Duration$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,205.06) {Type$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,231.47) {Intensity$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,257.88) {Ln(Min. Capital Dist.)$_{t-1}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.46, 34.03) --
	(277.03, 34.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (143.80, 20.31) {-0.3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (186.10, 20.31) {-0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (228.40, 20.31) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (270.69, 20.31) {0.3};
\end{scope}
\end{tikzpicture}

### 2014-09-23 LaTeX/mCapSimPlot.tex
plots in paper

% Created by tikzDevice version 0.7.0 on 2014-09-23 11:40:21
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 39.69, 34.03) rectangle (421.57,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] ( 39.69, 34.03) rectangle (421.57,277.03);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 57.05,107.99) --
	( 61.80,109.63) --
	( 66.56,111.28) --
	( 71.31,112.93) --
	( 76.07,114.58) --
	( 80.82,116.22) --
	( 85.58,117.87) --
	( 90.34,119.52) --
	( 95.09,121.16) --
	( 99.85,122.81) --
	(104.60,124.46) --
	(109.36,126.11) --
	(114.11,127.75) --
	(118.87,129.40) --
	(123.63,131.05) --
	(128.38,132.70) --
	(133.14,134.34) --
	(137.89,135.99) --
	(142.65,137.64) --
	(147.40,139.28) --
	(152.16,140.93) --
	(156.92,142.58) --
	(161.67,144.23) --
	(166.43,145.87) --
	(171.18,147.52) --
	(175.94,149.17) --
	(180.70,150.81) --
	(185.45,152.46) --
	(190.21,154.11) --
	(194.96,155.76) --
	(199.72,157.40) --
	(204.47,159.05) --
	(209.23,160.70) --
	(213.99,162.34) --
	(218.74,163.99) --
	(223.50,165.64) --
	(228.25,167.29) --
	(233.01,168.93) --
	(237.76,170.58) --
	(242.52,172.23) --
	(247.28,173.88) --
	(252.03,175.52) --
	(256.79,177.17) --
	(261.54,178.82) --
	(266.30,180.46) --
	(271.05,182.11) --
	(275.81,183.76) --
	(280.57,185.41) --
	(285.32,187.05) --
	(290.08,188.70) --
	(294.83,190.35) --
	(299.59,191.99) --
	(304.35,193.64) --
	(309.10,195.29) --
	(313.86,196.94) --
	(318.61,198.58) --
	(323.37,200.23) --
	(328.12,201.88) --
	(332.88,203.52) --
	(337.64,205.17) --
	(342.39,206.82) --
	(347.15,208.47) --
	(351.90,210.11) --
	(356.66,211.76) --
	(361.41,213.41) --
	(366.17,215.05) --
	(370.93,216.70) --
	(375.68,218.35) --
	(380.44,220.00) --
	(385.19,221.64) --
	(389.95,223.29) --
	(394.70,224.94) --
	(399.46,226.59) --
	(404.22,228.23);
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.30] ( 57.05,170.30) --
	( 61.80,170.75) --
	( 66.56,171.43) --
	( 71.31,172.00) --
	( 76.07,172.73) --
	( 80.82,173.39) --
	( 85.58,174.13) --
	( 90.34,174.65) --
	( 95.09,175.20) --
	( 99.85,175.83) --
	(104.60,176.50) --
	(109.36,177.16) --
	(114.11,177.80) --
	(118.87,178.59) --
	(123.63,179.29) --
	(128.38,179.81) --
	(133.14,180.41) --
	(137.89,181.20) --
	(142.65,181.89) --
	(147.40,182.78) --
	(152.16,183.41) --
	(156.92,183.93) --
	(161.67,184.69) --
	(166.43,185.42) --
	(171.18,186.20) --
	(175.94,187.05) --
	(180.70,188.02) --
	(185.45,188.60) --
	(190.21,189.50) --
	(194.96,190.46) --
	(199.72,191.24) --
	(204.47,192.15) --
	(209.23,193.07) --
	(213.99,194.11) --
	(218.74,195.08) --
	(223.50,196.00) --
	(228.25,196.95) --
	(233.01,198.08) --
	(237.76,199.37) --
	(242.52,200.49) --
	(247.28,201.79) --
	(252.03,203.07) --
	(256.79,204.30) --
	(261.54,205.54) --
	(266.30,207.04) --
	(271.05,208.33) --
	(275.81,209.80) --
	(280.57,211.29) --
	(285.32,212.83) --
	(290.08,214.53) --
	(294.83,216.23) --
	(299.59,217.85) --
	(304.35,219.60) --
	(309.10,221.58) --
	(313.86,223.41) --
	(318.61,225.32) --
	(323.37,227.31) --
	(328.12,229.50) --
	(332.88,231.70) --
	(337.64,233.85) --
	(342.39,235.89) --
	(347.15,238.03) --
	(351.90,240.17) --
	(356.66,242.38) --
	(361.41,244.58) --
	(366.17,246.95) --
	(370.93,249.06) --
	(375.68,251.34) --
	(380.44,253.72) --
	(385.19,255.97) --
	(389.95,258.60) --
	(394.70,261.10) --
	(399.46,263.65) --
	(404.22,265.99) --
	(404.22,189.23) --
	(399.46,188.51) --
	(394.70,187.90) --
	(389.95,187.02) --
	(385.19,186.13) --
	(380.44,185.09) --
	(375.68,184.39) --
	(370.93,183.61) --
	(366.17,182.69) --
	(361.41,181.83) --
	(356.66,180.81) --
	(351.90,179.77) --
	(347.15,178.57) --
	(342.39,177.44) --
	(337.64,176.32) --
	(332.88,175.29) --
	(328.12,174.08) --
	(323.37,172.90) --
	(318.61,171.57) --
	(313.86,170.24) --
	(309.10,168.76) --
	(304.35,167.31) --
	(299.59,165.82) --
	(294.83,164.52) --
	(290.08,162.91) --
	(285.32,161.16) --
	(280.57,159.46) --
	(275.81,157.79) --
	(271.05,155.95) --
	(266.30,154.07) --
	(261.54,152.24) --
	(256.79,150.23) --
	(252.03,148.25) --
	(247.28,146.22) --
	(242.52,143.99) --
	(237.76,141.83) --
	(233.01,139.84) --
	(228.25,137.63) --
	(223.50,135.49) --
	(218.74,133.10) --
	(213.99,130.62) --
	(209.23,128.31) --
	(204.47,125.87) --
	(199.72,123.59) --
	(194.96,121.22) --
	(190.21,118.75) --
	(185.45,116.43) --
	(180.70,114.03) --
	(175.94,111.47) --
	(171.18,108.99) --
	(166.43,106.38) --
	(161.67,103.74) --
	(156.92,101.22) --
	(152.16, 98.74) --
	(147.40, 96.24) --
	(142.65, 93.73) --
	(137.89, 91.21) --
	(133.14, 88.50) --
	(128.38, 85.77) --
	(123.63, 83.16) --
	(118.87, 80.48) --
	(114.11, 77.79) --
	(109.36, 75.08) --
	(104.60, 72.30) --
	( 99.85, 69.52) --
	( 95.09, 66.86) --
	( 90.34, 64.14) --
	( 85.58, 61.43) --
	( 80.82, 58.71) --
	( 76.07, 55.94) --
	( 71.31, 53.21) --
	( 66.56, 50.50) --
	( 61.80, 47.80) --
	( 57.05, 45.08) --
	cycle;
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.50] ( 57.05,159.56) --
	( 61.80,160.25) --
	( 66.56,160.98) --
	( 71.31,161.86) --
	( 76.07,162.52) --
	( 80.82,163.37) --
	( 85.58,164.21) --
	( 90.34,164.90) --
	( 95.09,165.74) --
	( 99.85,166.75) --
	(104.60,167.59) --
	(109.36,168.46) --
	(114.11,169.19) --
	(118.87,170.16) --
	(123.63,170.99) --
	(128.38,171.84) --
	(133.14,172.69) --
	(137.89,173.59) --
	(142.65,174.41) --
	(147.40,175.17) --
	(152.16,176.19) --
	(156.92,177.17) --
	(161.67,178.09) --
	(166.43,178.94) --
	(171.18,179.97) --
	(175.94,180.98) --
	(180.70,181.99) --
	(185.45,182.96) --
	(190.21,183.82) --
	(194.96,184.88) --
	(199.72,185.88) --
	(204.47,186.83) --
	(209.23,187.76) --
	(213.99,188.99) --
	(218.74,190.13) --
	(223.50,191.26) --
	(228.25,192.31) --
	(233.01,193.53) --
	(237.76,194.62) --
	(242.52,195.84) --
	(247.28,197.18) --
	(252.03,198.48) --
	(256.79,199.68) --
	(261.54,201.07) --
	(266.30,202.56) --
	(271.05,204.06) --
	(275.81,205.62) --
	(280.57,207.24) --
	(285.32,209.00) --
	(290.08,210.51) --
	(294.83,212.14) --
	(299.59,213.87) --
	(304.35,215.72) --
	(309.10,217.52) --
	(313.86,219.34) --
	(318.61,221.26) --
	(323.37,223.16) --
	(328.12,225.10) --
	(332.88,227.06) --
	(337.64,228.96) --
	(342.39,231.01) --
	(347.15,233.07) --
	(351.90,235.12) --
	(356.66,237.31) --
	(361.41,239.43) --
	(366.17,241.62) --
	(370.93,243.83) --
	(375.68,246.04) --
	(380.44,248.34) --
	(385.19,250.61) --
	(389.95,252.92) --
	(394.70,255.34) --
	(399.46,257.65) --
	(404.22,260.08) --
	(404.22,196.18) --
	(399.46,195.16) --
	(394.70,194.11) --
	(389.95,193.22) --
	(385.19,192.29) --
	(380.44,191.22) --
	(375.68,190.29) --
	(370.93,189.27) --
	(366.17,188.31) --
	(361.41,187.21) --
	(356.66,185.94) --
	(351.90,184.86) --
	(347.15,183.77) --
	(342.39,182.69) --
	(337.64,181.59) --
	(332.88,180.34) --
	(328.12,179.09) --
	(323.37,177.75) --
	(318.61,176.29) --
	(313.86,174.79) --
	(309.10,173.33) --
	(304.35,171.86) --
	(299.59,170.35) --
	(294.83,168.77) --
	(290.08,167.23) --
	(285.32,165.59) --
	(280.57,163.88) --
	(275.81,162.14) --
	(271.05,160.29) --
	(266.30,158.47) --
	(261.54,156.48) --
	(256.79,154.63) --
	(252.03,152.76) --
	(247.28,150.64) --
	(242.52,148.69) --
	(237.76,146.57) --
	(233.01,144.54) --
	(228.25,142.40) --
	(223.50,140.17) --
	(218.74,137.98) --
	(213.99,135.99) --
	(209.23,133.82) --
	(204.47,131.54) --
	(199.72,129.37) --
	(194.96,127.03) --
	(190.21,124.77) --
	(185.45,122.49) --
	(180.70,120.16) --
	(175.94,117.80) --
	(171.18,115.40) --
	(166.43,113.13) --
	(161.67,110.68) --
	(156.92,108.42) --
	(152.16,105.89) --
	(147.40,103.39) --
	(142.65,100.83) --
	(137.89, 98.32) --
	(133.14, 95.77) --
	(128.38, 93.33) --
	(123.63, 90.81) --
	(118.87, 88.34) --
	(114.11, 85.90) --
	(109.36, 83.33) --
	(104.60, 80.84) --
	( 99.85, 78.40) --
	( 95.09, 75.83) --
	( 90.34, 73.27) --
	( 85.58, 70.75) --
	( 80.82, 68.24) --
	( 76.07, 65.78) --
	( 71.31, 63.28) --
	( 66.56, 60.67) --
	( 61.80, 58.16) --
	( 57.05, 55.65) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
	( 39.69,277.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,101.49) {3.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,183.81) {4.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,266.13) {4.2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
	(421.57, 34.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 41.46, 20.31) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 89.02, 20.31) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (136.58, 20.31) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (184.13, 20.31) {3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (231.69, 20.31) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (279.25, 20.31) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.81, 20.31) {6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (374.36, 20.31) {7};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (230.63,  4.82) {Ln(Min. Cap Dist.)$_{t}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at ( 19.11,155.53) {\% $\Delta$ Ln(GDP)$_{t}$};
\end{scope}
\end{tikzpicture}

### 2014-09-23 LaTeX/mCityCoefPlot.tex
plots in paper

% Created by tikzDevice version 0.7.0 on 2014-09-23 11:36:07
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (124.66, 34.03) rectangle (277.03,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] (124.66, 34.03) rectangle (277.04,277.03);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.10, 49.88) -- (207.76, 49.88);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (193.68, 76.30) -- (230.11, 76.30);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (174.88,102.71) -- (189.88,102.71);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (155.06,129.12) -- (247.73,129.12);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (165.59,155.53) -- (195.00,155.53);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.88,181.95) -- (202.07,181.95);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (187.98,208.36) -- (225.50,208.36);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (180.79,234.77) -- (210.45,234.77);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (203.18,261.19) -- (216.39,261.19);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (200.72, 49.88) -- (207.15, 49.88);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (196.61, 76.30) -- (227.18, 76.30);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (176.09,102.71) -- (188.68,102.71);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (162.51,129.12) -- (240.28,129.12);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (167.95,155.53) -- (192.63,155.53);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (200.97,181.95) -- (201.98,181.95);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (191.00,208.36) -- (222.48,208.36);

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (183.17,234.77) -- (208.07,234.77);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (204.24,261.19) -- (215.33,261.19);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
\definecolor[named]{fillColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (200.85, 34.03) -- (200.85,277.03);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.79,261.19) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (195.62,234.77) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (206.74,208.36) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.47,181.95) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.29,155.53) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.39,129.12) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.38,102.71) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (211.89, 76.30) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (203.93, 49.88) circle (  2.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.76, 48.56) --
	(207.76, 51.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.76, 49.88) --
	(200.10, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (200.10, 48.56) --
	(200.10, 51.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.11, 74.97) --
	(230.11, 77.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.11, 76.30) --
	(193.68, 76.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (193.68, 74.97) --
	(193.68, 77.62);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,line width= 0.6pt,line join=round] (189.88,101.39) --
	(189.88,104.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] (189.88,102.71) --
	(174.88,102.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (174.88,101.39) --
	(174.88,104.03);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.73,127.80) --
	(247.73,130.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.73,129.12) --
	(155.06,129.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (155.06,127.80) --
	(155.06,130.44);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}

\path[draw=drawColor,line width= 0.6pt,line join=round] (195.00,154.21) --
	(195.00,156.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] (195.00,155.53) --
	(165.59,155.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.59,154.21) --
	(165.59,156.86);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,line width= 0.6pt,line join=round] (202.07,180.63) --
	(202.07,183.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (202.07,181.95) --
	(200.88,181.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (200.88,180.63) --
	(200.88,183.27);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}

\path[draw=drawColor,line width= 0.6pt,line join=round] (225.50,207.04) --
	(225.50,209.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] (225.50,208.36) --
	(187.98,208.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (187.98,207.04) --
	(187.98,209.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] (210.45,233.45) --
	(210.45,236.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (210.45,234.77) --
	(180.79,234.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (180.79,233.45) --
	(180.79,236.09);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.39,259.87) --
	(216.39,262.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.39,261.19) --
	(203.18,261.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] (203.18,259.87) --
	(203.18,262.51);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] (124.66, 34.03) --
	(124.66,277.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55, 46.58) {World GDP Growth$_{t}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55, 72.99) {Democracy$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55, 99.40) {Ln(Inflation)$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,125.82) {Upper Income};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,152.23) {Area$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,178.64) {Duration$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,205.06) {Type$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,231.47) {Intensity$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,257.88) {Ln(Min. City Dist.)$_{t-1}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] (124.66, 34.03) --
	(277.03, 34.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (131.59, 20.31) {-0.3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (177.76, 20.31) {-0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (223.94, 20.31) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (270.11, 20.31) {0.3};
\end{scope}
\end{tikzpicture}

### 2014-09-23 LaTeX/mCitySimPlot.tex
plots in paper

% Created by tikzDevice version 0.7.0 on 2014-09-23 11:39:59
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 39.69, 34.03) rectangle (421.57,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] ( 39.69, 34.03) rectangle (421.57,277.03);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 57.05,110.46) --
	( 62.08,112.14) --
	( 67.11,113.83) --
	( 72.14,115.51) --
	( 77.17,117.20) --
	( 82.20,118.88) --
	( 87.23,120.57) --
	( 92.27,122.25) --
	( 97.30,123.94) --
	(102.33,125.62) --
	(107.36,127.30) --
	(112.39,128.99) --
	(117.42,130.67) --
	(122.45,132.36) --
	(127.49,134.04) --
	(132.52,135.73) --
	(137.55,137.41) --
	(142.58,139.10) --
	(147.61,140.78) --
	(152.64,142.47) --
	(157.67,144.15) --
	(162.71,145.84) --
	(167.74,147.52) --
	(172.77,149.20) --
	(177.80,150.89) --
	(182.83,152.57) --
	(187.86,154.26) --
	(192.89,155.94) --
	(197.93,157.63) --
	(202.96,159.31) --
	(207.99,161.00) --
	(213.02,162.68) --
	(218.05,164.37) --
	(223.08,166.05) --
	(228.12,167.74) --
	(233.15,169.42) --
	(238.18,171.11) --
	(243.21,172.79) --
	(248.24,174.47) --
	(253.27,176.16) --
	(258.30,177.84) --
	(263.34,179.53) --
	(268.37,181.21) --
	(273.40,182.90) --
	(278.43,184.58) --
	(283.46,186.27) --
	(288.49,187.95) --
	(293.52,189.64) --
	(298.56,191.32) --
	(303.59,193.01) --
	(308.62,194.69) --
	(313.65,196.38) --
	(318.68,198.06) --
	(323.71,199.74) --
	(328.74,201.43) --
	(333.78,203.11) --
	(338.81,204.80) --
	(343.84,206.48) --
	(348.87,208.17) --
	(353.90,209.85) --
	(358.93,211.54) --
	(363.96,213.22) --
	(369.00,214.91) --
	(374.03,216.59) --
	(379.06,218.28) --
	(384.09,219.96) --
	(389.12,221.65) --
	(394.15,223.33) --
	(399.18,225.01) --
	(404.22,226.70);
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.30] ( 57.05,174.43) --
	( 62.08,174.80) --
	( 67.11,175.43) --
	( 72.14,175.95) --
	( 77.17,176.45) --
	( 82.20,177.01) --
	( 87.23,177.60) --
	( 92.27,178.07) --
	( 97.30,178.83) --
	(102.33,179.63) --
	(107.36,180.19) --
	(112.39,180.68) --
	(117.42,181.22) --
	(122.45,181.91) --
	(127.49,182.61) --
	(132.52,183.22) --
	(137.55,183.85) --
	(142.58,184.72) --
	(147.61,185.27) --
	(152.64,185.85) --
	(157.67,186.68) --
	(162.71,187.40) --
	(167.74,188.19) --
	(172.77,188.79) --
	(177.80,189.72) --
	(182.83,190.53) --
	(187.86,191.58) --
	(192.89,192.32) --
	(197.93,193.15) --
	(202.96,194.08) --
	(207.99,195.20) --
	(213.02,196.17) --
	(218.05,197.04) --
	(223.08,198.12) --
	(228.12,199.15) --
	(233.15,200.19) --
	(238.18,201.29) --
	(243.21,202.47) --
	(248.24,203.82) --
	(253.27,205.19) --
	(258.30,206.48) --
	(263.34,207.77) --
	(268.37,209.20) --
	(273.40,210.73) --
	(278.43,212.20) --
	(283.46,213.76) --
	(288.49,215.30) --
	(293.52,216.81) --
	(298.56,218.76) --
	(303.59,220.71) --
	(308.62,222.73) --
	(313.65,224.51) --
	(318.68,226.51) --
	(323.71,228.57) --
	(328.74,230.64) --
	(333.78,232.65) --
	(338.81,234.73) --
	(343.84,236.98) --
	(348.87,239.31) --
	(353.90,241.60) --
	(358.93,243.92) --
	(363.96,246.40) --
	(369.00,248.74) --
	(374.03,251.08) --
	(379.06,253.40) --
	(384.09,255.89) --
	(389.12,258.42) --
	(394.15,260.84) --
	(399.18,263.30) --
	(404.22,265.99) --
	(404.22,186.70) --
	(399.18,185.91) --
	(394.15,185.08) --
	(389.12,184.30) --
	(384.09,183.58) --
	(379.06,182.70) --
	(374.03,181.87) --
	(369.00,180.89) --
	(363.96,179.93) --
	(358.93,178.91) --
	(353.90,178.04) --
	(348.87,176.86) --
	(343.84,175.89) --
	(338.81,174.74) --
	(333.78,173.45) --
	(328.74,172.28) --
	(323.71,171.02) --
	(318.68,169.43) --
	(313.65,167.97) --
	(308.62,166.54) --
	(303.59,165.18) --
	(298.56,163.70) --
	(293.52,162.08) --
	(288.49,160.29) --
	(283.46,158.60) --
	(278.43,156.91) --
	(273.40,155.18) --
	(268.37,153.23) --
	(263.34,151.42) --
	(258.30,149.61) --
	(253.27,147.65) --
	(248.24,145.45) --
	(243.21,143.23) --
	(238.18,141.02) --
	(233.15,138.72) --
	(228.12,136.35) --
	(223.08,133.80) --
	(218.05,131.34) --
	(213.02,128.83) --
	(207.99,126.45) --
	(202.96,124.00) --
	(197.93,121.57) --
	(192.89,119.03) --
	(187.86,116.41) --
	(182.83,113.90) --
	(177.80,111.23) --
	(172.77,108.70) --
	(167.74,105.98) --
	(162.71,103.34) --
	(157.67,100.79) --
	(152.64, 98.10) --
	(147.61, 95.49) --
	(142.58, 92.64) --
	(137.55, 89.85) --
	(132.52, 87.02) --
	(127.49, 84.25) --
	(122.45, 81.44) --
	(117.42, 78.59) --
	(112.39, 75.96) --
	(107.36, 73.32) --
	(102.33, 70.44) --
	( 97.30, 67.62) --
	( 92.27, 64.83) --
	( 87.23, 61.80) --
	( 82.20, 58.96) --
	( 77.17, 56.21) --
	( 72.14, 53.52) --
	( 67.11, 50.65) --
	( 62.08, 47.79) --
	( 57.05, 45.08) --
	cycle;
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.50] ( 57.05,165.69) --
	( 62.08,166.26) --
	( 67.11,166.92) --
	( 72.14,167.65) --
	( 77.17,168.34) --
	( 82.20,169.03) --
	( 87.23,169.66) --
	( 92.27,170.38) --
	( 97.30,171.07) --
	(102.33,171.75) --
	(107.36,172.44) --
	(112.39,173.12) --
	(117.42,173.84) --
	(122.45,174.45) --
	(127.49,175.12) --
	(132.52,175.81) --
	(137.55,176.59) --
	(142.58,177.35) --
	(147.61,178.25) --
	(152.64,179.27) --
	(157.67,180.18) --
	(162.71,181.11) --
	(167.74,181.96) --
	(172.77,182.76) --
	(177.80,183.71) --
	(182.83,184.54) --
	(187.86,185.47) --
	(192.89,186.43) --
	(197.93,187.51) --
	(202.96,188.46) --
	(207.99,189.58) --
	(213.02,190.58) --
	(218.05,191.75) --
	(223.08,192.84) --
	(228.12,194.00) --
	(233.15,195.12) --
	(238.18,196.45) --
	(243.21,197.65) --
	(248.24,199.02) --
	(253.27,200.34) --
	(258.30,201.75) --
	(263.34,203.21) --
	(268.37,204.61) --
	(273.40,206.24) --
	(278.43,207.82) --
	(283.46,209.30) --
	(288.49,210.93) --
	(293.52,212.69) --
	(298.56,214.53) --
	(303.59,216.36) --
	(308.62,218.21) --
	(313.65,220.05) --
	(318.68,222.00) --
	(323.71,224.00) --
	(328.74,225.95) --
	(333.78,227.98) --
	(338.81,230.07) --
	(343.84,232.25) --
	(348.87,234.41) --
	(353.90,236.60) --
	(358.93,238.76) --
	(363.96,240.91) --
	(369.00,243.13) --
	(374.03,245.40) --
	(379.06,247.74) --
	(384.09,250.09) --
	(389.12,252.61) --
	(394.15,255.21) --
	(399.18,257.56) --
	(404.22,259.93) --
	(404.22,192.89) --
	(399.18,192.12) --
	(394.15,191.18) --
	(389.12,190.22) --
	(384.09,189.28) --
	(379.06,188.36) --
	(374.03,187.32) --
	(369.00,186.30) --
	(363.96,185.20) --
	(358.93,184.18) --
	(353.90,182.99) --
	(348.87,181.90) --
	(343.84,180.64) --
	(338.81,179.59) --
	(333.78,178.30) --
	(328.74,176.91) --
	(323.71,175.49) --
	(318.68,174.05) --
	(313.65,172.59) --
	(308.62,171.06) --
	(303.59,169.50) --
	(298.56,167.92) --
	(293.52,166.28) --
	(288.49,164.66) --
	(283.46,162.97) --
	(278.43,161.38) --
	(273.40,159.49) --
	(268.37,157.55) --
	(263.34,155.74) --
	(258.30,153.81) --
	(253.27,151.84) --
	(248.24,149.82) --
	(243.21,147.69) --
	(238.18,145.73) --
	(233.15,143.60) --
	(228.12,141.48) --
	(223.08,139.15) --
	(218.05,136.75) --
	(213.02,134.58) --
	(207.99,132.15) --
	(202.96,129.81) --
	(197.93,127.34) --
	(192.89,124.90) --
	(187.86,122.54) --
	(182.83,119.97) --
	(177.80,117.68) --
	(172.77,115.15) --
	(167.74,112.73) --
	(162.71,110.22) --
	(157.67,107.87) --
	(152.64,105.34) --
	(147.61,102.80) --
	(142.58,100.16) --
	(137.55, 97.55) --
	(132.52, 94.94) --
	(127.49, 92.32) --
	(122.45, 89.72) --
	(117.42, 87.08) --
	(112.39, 84.45) --
	(107.36, 81.80) --
	(102.33, 79.16) --
	( 97.30, 76.57) --
	( 92.27, 74.01) --
	( 87.23, 71.42) --
	( 82.20, 68.63) --
	( 77.17, 65.97) --
	( 72.14, 63.37) --
	( 67.11, 60.74) --
	( 62.08, 58.05) --
	( 57.05, 55.38) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
	( 39.69,277.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 52.86) {3.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 96.58) {3.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,140.30) {3.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,184.02) {4.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,227.74) {4.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,271.45) {4.2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
	(421.57, 34.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 40.56, 20.31) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 90.87, 20.31) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (141.19, 20.31) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (191.50, 20.31) {3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (241.82, 20.31) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (292.13, 20.31) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (342.45, 20.31) {6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (392.76, 20.31) {7};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (230.63,  4.82) {Ln(Min. City Dist.)$_{t}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at ( 19.11,155.53) {\% $\Delta$ Ln(GDP)$_{t}$};
\end{scope}
\end{tikzpicture}

### 2014-09-23 LaTeX/rmseInOut.tex
plots in paper

% Created by tikzDevice version 0.7.0 on 2014-09-23 12:42:48
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 39.69, 54.77) rectangle (229.13,264.40);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] ( 39.69, 54.77) rectangle (229.13,264.40);
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor] ( 52.60, 64.30) rectangle (130.10,254.87);

\path[fill=fillColor] (138.71, 64.30) rectangle (216.21,165.65);
\definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 39.69, 54.77) rectangle (229.13,264.40);
\end{scope}
\begin{scope}
\path[clip] (232.14, 54.77) rectangle (421.57,264.40);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] (232.14, 54.77) rectangle (421.57,264.40);
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor] (245.05, 64.30) rectangle (322.55,254.76);

\path[fill=fillColor] (331.16, 64.30) rectangle (408.66,164.41);
\definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.14, 54.77) rectangle (421.57,264.40);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
\definecolor[named]{fillColor}{rgb}{0.80,0.80,0.80}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] ( 39.69,264.40) rectangle (229.13,277.04);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (134.41,267.41) {Ln(Min. Cap Dist.)$_{t}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
\definecolor[named]{fillColor}{rgb}{0.80,0.80,0.80}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (232.14,264.40) rectangle (421.57,277.04);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.86,267.41) {Ln(Min. City Dist.)$_{t}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 60.99) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,128.89) {0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,196.78) {0.2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 91.35, 41.05) {In-Sample };

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 91.35, 30.68) { n=375 };

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 91.35, 20.31) { N=66};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (177.46, 41.05) {Out-Sample };

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (177.46, 30.68) { n=186 };

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (177.46, 20.31) { N=42};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (283.80, 41.05) {In-Sample };

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (283.80, 30.68) { n=375 };

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (283.80, 20.31) { N=66};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (369.91, 41.05) {Out-Sample };

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (369.91, 30.68) { n=186 };

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (369.91, 20.31) { N=42};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at ( 17.30,159.59) {RMSE};
\end{scope}
\end{tikzpicture}

### 2014-09-23 R/Analysis/models.R

@@ -52,7 +52,7 @@ source('vizResults.R')
 
 coefs=na.omit(rownames(summary(mCity)$'coefficients')[2:100])
 vnames=c('Ln(Min. City Dist.)$_{t-1}$', 
-  'Intensity$_{t-1}$', 'Type$_{t-1}$', 'Duration$_{t-1}$', 'Area$_{t-1}',
+  'Intensity$_{t-1}$', 'Type$_{t-1}$', 'Duration$_{t-1}$', 'Area$_{t-1}$',
   'Upper Income', 'Ln(Inflation)$_{t-1}$', 'Democracy$_{t-1}$',
   'World GDP Growth$_{t}$')
 temp <- ggcoefplot(coefData=summary(mCity)$'coefficients',
@@ -67,7 +67,7 @@ temp
 
 coefs=na.omit(rownames(summary(mCap)$'coefficients')[2:100])
 vnames=c('Ln(Min. Capital Dist.)$_{t-1}$', 
-  'Intensity$_{t-1}$', 'Type$_{t-1}$', 'Duration$_{t-1}$', 'Area$_{t-1}',
+  'Intensity$_{t-1}$', 'Type$_{t-1}$', 'Duration$_{t-1}$', 'Area$_{t-1}$',
   'Upper Income', 'Ln(Inflation)$_{t-1}$', 'Democracy$_{t-1}$',
   'World GDP Growth$_{t}$')
 temp <- ggcoefplot(coefData=summary(mCap)$'coefficients',
@@ -76,7 +76,7 @@ temp <- ggcoefplot(coefData=summary(mCap)$'coefficients',
     colorGrey=FALSE, grSTA=0.5, grEND=0.1)
 temp
 setwd(pathTex)
-# tikz(file='mCityCoefPlot.tex', width=4, height=4, standAlone=F)
+# tikz(file='mCapCoefPlot.tex', width=4, height=4, standAlone=F)
 temp
 # dev.off()
 ###################################################################
@@ -137,6 +137,27 @@ outSampPerf = function(mod){
 
 rmse(mCityTr); rmse(mCapTr)
 outSampPerf(mCityTr); outSampPerf(mCapTr)
+
+ggRMSE=data.frame(rbind(
+  cbind(var="Ln(Min. City Dist.)$_{t}$", type='In-Sample \n n=375 \n N=66', stat=rmse(mCityTr) ),
[…]

### 2014-09-25 LaTeX/RhodiumEmp.tex
edits

@@
 
-\begin{itemize}
-	\item Conflict intensity
-	\item Ln(Conflict Area)
-	\item Civil Conflict Type (e.g., territory or non-territory dispute)
-	\item Conflict Duration (Years)
-\end{itemize}
+% Replace list with sentences
+
+% \begin{itemize}
+% 	\item Conflict intensity
+% 	\item Ln(Conflict Area)
+% 	\item Civil Conflict Type (e.g., territory or non-territory dispute)
+% 	\item Conflict Duration (Years)
+% \end{itemize}
 
@@
 
-To estimate the model we use random effects clustered on countries and years.
+To estimate the model we use random effects clustered on countries.
 Results using a fixed effects estimation approach are similar.\footnote{The fixed effects model includes the same regressors as the random effects model but adds indicator variables for each country in the sample.} The model we estimate is shown below:
 
+Add in descriptors for each of these variables and expectations of their sign.
+
 \begin{align*}
-	\% \Delta GDP_{i,t} &= \beta_{1}(Upper \; Income_{i,t}) \\
-	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t}) \;+\; \beta_{3}(Ln(Conflict \; Area)_{i,t}) \\
-	& \;+\; \beta_{4}(Ln(Min. \; Conflict \; Dist.)_{i,t}) \;+\; \beta_{5}(Conflict \; Type_{i,t}) \\
-	& \;+\; \beta_{6}(Conflict \; Duration_{i,t}) \;+\; \beta_{7}(Inflation_{i,t-1}) \\
-	& \;+\; \beta_{8}(Ln(Land \; Area)_{i,t}) \;+\; \alpha_{i} + \gamma_{t} + \mu_{i,t}
+	\% \Delta Log(GDP_{i,t}) &= \beta_{1}(Ln(Min. \; Conflict \; Dist.)_{i,t}) \\
+	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t}) \;+\; \beta_{3}(Conflict \; Type_{i,t}) \\
+	& \;+\; \beta_{4}(Conflict \; Duration_{i,t}) \;+\; \beta_{5}(Ln(Conflict \; Area)_{i,t}) \\	
+	& \;+\; \beta_{6}(Upper \; Income_{i,t}) \;+\; \beta_{7}(Inflation_{i,t-1}) \\
+	&  \;+\; \beta_{8}(Democracy_{i,t-1}) \;+\; \beta_{9}(World \; GDP \; Growth_{t}) \\
+	& \;+\; \alpha_{i} + \mu_{i,t}
 \end{align*}

### 2014-09-25 LaTeX/RhodiumTheory.tex
minor comments

@@
 
+% I like the last idea where we say that conflict impedes trade between cities.
+
 We suspect that substate factors will determine the economic impacts of civil conflict.
@@
 Violence near major population centers not only threatens residents directly, but impedes business by threatening trade between the population center and other cities or rural areas.
+
+% Do we even need to bring up Imai and Weinstein here? I dont think it helps us if people keep contrasting our approach with theirs as they read our paper.
 
@@
 In the past three decades, economists have followed Jacobs' lead and investigated city-level economic drivers \citep{lucas:1988, ciccone:hall:1996, begg:1999}.
+One oft-cited mechanism by which cities can provide economic advantages to industry is knowledge spillover.
+Industries that concentrate in cities benefit from one another through knowledge transfer \citep{jaffe:etal:1993, glaeser:1994, firestone:2010}.
+Empirical estimates of agglomeration effects indicate that a doubling of employment density correspond to a 5\% increase in labor productivity \citep{ciccone:hall:1996,ciccone:2002}.
+
+% Add some references here about cities accounting for larger portions of economies. Would be nice if we found this to be particularly true for developing countries as well.
 

### 2014-09-25 LaTeX/RhodiumEmp.tex
updates to tex, and plots

@@
 
-To measure economic performance we use logged, annual percent change in GDP, which we collect from the World Development Indicators at the World Bank.
-We choose to focus on year over change in GDP because we expect conflicts proximate to major cities to lead to reductions in growth.\footnote{Alternative measures of economic performance would have included changes in FDI inflows or changes in GDP per capita, in using either of these measures our results remain relatively the same.} Unlike much of the extant literature in constructing our dependent variable we focus on year over change instead of a ten year average.
+To measure economic performance we use annual percent change in logged GDP collected from the World Development Indicators at the World Bank.
+We choose to focus on year over change in logged GDP because we expect conflicts proximate to major cities to lead to immediate reductions in overall growth.
+Unlike much of the extant literature in constructing our dependent variable we focus on year over change instead of a ten year average.
 We believe this approach to be superior because it allows us to estimate the direct effect of the conflict on economic performance in that year.
@@
 Our key independent variable on the location of conflicts come from the PRIO Conflict Site Dataset.
-This dataset contains geo-referenced armed conflict events from 1989 to 2008.\footnote{We only include examine the effect of internal armed conflicts.} A downside of this geo-referenced database is that every conflict-year is assigned a circular conflict zone, which leads to the dataset reporting that the conflict is covering more territory than actually affected.
-Crafting a more specfic approach to the spread of conflict would, however, eliminate important cases from our analysis.
-In total this dataset provides us with almost 800 geo-referenced conflict-year cases.
+This dataset contains geo-referenced armed conflict events from 1989 to 2008.\footnote{We only include examine the effect of internal armed conflicts.} In total this dataset provides us with almost 800 geo-referenced conflict-year cases.
 
@@
 
-The key theory that we advance here is that the effects of conflict on economic performance are conditional on the proximity of those conflicts to major city centers.
-Thus a crucial part of our work here involved determining major city centers by year.
-The only data source we found with enough geographical and temporal coverage on major cities was The World Alamanac.
-To gather data from these textbooks we hired several undergraduate students to identify the major cities listed for each country within a yearly edition of the Almanac from 1989 to 2008.
-Major cities are classified as those that have relatively large shares of a country's population and/or are economic centers.
+A crucial part of our work here involved determining major city centers by year.
+The only data source we found with enough geographical and temporal coverage on major cities was The World Alamanac.\footnote{To gather data from these textbooks we hired several research assistants to identify the major cities listed for each country within a yearly edition of the Almanac from 1989 to 2008.} Major cities are classified as those that have relatively large shares of a country's population and/or are economic centers.
 Typically, the Alamanacs listed at least three major cities for each country and year from 1989 to 2008.
@@
 
-\subsection{Level of Aggregation}
-
-A key problem we face in conducting this analysis is reconciling the unit of analysis for our key independent and dependent variables.
 Our dependent variable is at the country-year and our key independent variable, distance between conflicts and major cities, is at the conflict-country-year level.
@@
 At the same time, we argue that this choice of aggregation is what conforms closest to our theoretical claims about economic activity only being severely disrupted in cases of conflicts being proximate to major cities.
-From the PRIO dataset we also bring in additional information about that conflict, specifically:
-
-% Replace list with sentences
-
-% \begin{itemize}
-% 	\item Conflict intensity
-% 	\item Ln(Conflict Area)
-% 	\item Civil Conflict Type (e.g., territory or non-territory dispute)
-% 	\item Conflict Duration (Years)
-% \end{itemize}
+From the PRIO dataset we also bring in additional information about that conflict, specifically its intensity, the area of conflict, whether the conflict involves a territorial dispute, and its duration.
 
@@
 
-\subsection{Estimation Method}
+Add in descriptors for each of these variables and expectations of their sign.
 
-To estimate the model we use random effects clustered on countries.
-Results using a fixed effects estimation approach are similar.\footnote{The fixed effects model includes the same regressors as the random effects model but adds indicator variables for each country in the sample.} The model we estimate is shown below:
-
-Add in descriptors for each of these variables and expectations of their sign.
+To estimate the model we use random effects clustered on countries. The model we estimate is shown below:
 
@@
 
-RMSE: in and out of sample
+To assess the accuracy and performance of these estimates we employ a simple two-fold cross validation procedure.\footnote{Results of analysis were similar when employing a 10-fold cross validation as well, however, we limit to showing six here for the sake of space.} We use this procedure both to determine the robustness of our coefficient estimates when estimated on different subsamples of our dataset, and to assess how well the results of our model would generalize to an independent dataset.
+To begin the cross-validation, we split the 653 sanction cases in our dataset into six approximately equal subsets.
+We then run each model shown in Table \ref{tab:regResults} six times, where in each iteration we left out one subsample to use as a test set.
+This allows us to compare the prediction accuracy of each model, thereby helping us to determine the gains from incorporating the reciprocity covariates that are key to our argument.
 
@@
 
-Model heterogeneity:
+First, however, we show the results for our reciprocity covariates when we rerun our survival analysis on each of the six folds from the cross-validation.
+This analysis helps us to understand whether some of the subsets in our dataset follow a different pattern than what is in the broader set.\footnote{\cite{beck2008time}} Figure \ref{fig:crossval} shows that this is not the case for the analysis we present here, the coefficient estimates for compliance and sanction reciprocity remain consistent across each of these subsamples.\footnote{The parameter estimates for the other covariates also remain consistent across each of the six folds but we leave them out here due to space constraints.}
 

### 2014-09-25 LaTeX/crossValPlot.tex
updates to tex, and plots

@@
-% Created by tikzDevice version 0.7.0 on 2014-09-23 12:02:28
+% Created by tikzDevice version 0.7.0 on 2014-09-25 14:00:56
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 44.49, 52.60) rectangle (217.04,264.40);
+\path[clip] ( 53.55, 52.60) rectangle (216.77,264.40);
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
 
-\path[fill=fillColor] ( 44.49, 52.60) rectangle (217.04,264.40);
-\definecolor[named]{drawColor}{rgb}{0.40,0.40,0.40}
-\definecolor[named]{fillColor}{rgb}{0.40,0.40,0.40}
+\path[fill=fillColor] ( 53.55, 52.60) rectangle (216.77,264.40);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 57.11,118.35) -- ( 57.11,223.64);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 67.15, 65.03) -- ( 67.15,209.31);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 78.15, 90.67) -- ( 78.15,235.31);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 89.82, 74.37) -- ( 89.82,223.23);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 99.20,100.76) -- ( 99.20,242.14);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (112.49, 92.67) -- (112.49,254.77);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (120.24, 62.23) -- (120.24,203.29);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (135.16, 83.37) -- (135.16,232.52);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (141.28, 62.56) -- (141.28,185.24);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (157.83, 82.70) -- (157.83,233.97);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (162.33,109.01) -- (162.33,254.77);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (180.50, 65.59) -- (180.50,215.32);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (183.37, 75.66) -- (183.37,214.67);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (203.17, 95.32) -- (203.17,230.62);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (204.41, 97.04) -- (204.41,227.78);
-\definecolor[named]{drawColor}{rgb}{0.40,0.40,0.40}
-\definecolor[named]{fillColor}{rgb}{0.40,0.40,0.40}
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 67.15, 76.63) -- ( 67.15,197.71);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 57.11,126.81) -- ( 57.11,215.18);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 89.82, 86.34) -- ( 89.82,211.26);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 78.15,102.30) -- ( 78.15,223.69);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (112.49,105.70) -- (112.49,241.74);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 99.20,112.12) -- ( 99.20,230.77);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (135.16, 95.36) -- (135.16,220.53);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (120.24, 73.57) -- (120.24,191.95);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (157.83, 94.86) -- (157.83,221.81);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (141.28, 72.43) -- (141.28,175.38);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (180.50, 77.62) -- (180.50,203.28);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (162.33,120.73) -- (162.33,243.06);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (183.37, 86.84) -- (183.37,203.49);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (204.41,107.55) -- (204.41,217.27);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (203.17,106.20) -- (203.17,219.75);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] ( 44.49, 66.40) -- (217.04, 66.40);
-\definecolor[named]{drawColor}{rgb}{0.40,0.40,0.40}
-\definecolor[named]{fillColor}{rgb}{0.40,0.40,0.40}
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] ( 53.55, 62.23) -- (216.77, 62.23);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 57.11,171.00) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 67.15,137.17) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.15,162.99) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.82,148.80) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.20,171.45) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.49,173.72) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.24,132.76) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.16,157.94) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.28,123.90) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.83,158.33) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.33,181.89) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.50,140.45) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.37,145.16) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (203.17,162.97) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (204.41,162.41) circle (  2.85);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.02,209.31) --
+	( 68.29,209.31);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.06,223.64) --
-	( 58.16,223.64);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.15,209.31) --
+	( 67.15, 65.03);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 57.11,223.64) --
-	( 57.11,118.35);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.02, 65.03) --
+	( 68.29, 65.03);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.06,118.35) --
-	( 58.16,118.35);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.69,223.23) --
+	( 90.95,223.23);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.10,235.31) --
-	( 79.21,235.31);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.82,223.23) --
+	( 89.82, 74.37);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.15,235.31) --
-	( 78.15, 90.67);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.69, 74.37) --
+	( 90.95, 74.37);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.10, 90.67) --
-	( 79.21, 90.67);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (111.36,254.77) --
+	(113.62,254.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 98.14,242.14) --
-	(100.25,242.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (112.49,254.77) --
+	(112.49, 92.67);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.20,242.14) --
-	( 99.20,100.76);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (111.36, 92.67) --
+	(113.62, 92.67);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 98.14,100.76) --
-	(100.25,100.76);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (134.03,232.52) --
+	(136.29,232.52);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (119.19,203.29) --
-	(121.29,203.29);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (135.16,232.52) --
+	(135.16, 83.37);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.24,203.29) --
-	(120.24, 62.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (134.03, 83.37) --
+	(136.29, 83.37);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (119.19, 62.23) --
-	(121.29, 62.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.70,233.97) --
+	(158.96,233.97);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (140.23,185.24) --
-	(142.33,185.24);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (157.83,233.97) --
+	(157.83, 82.70);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (141.28,185.24) --
-	(141.28, 62.56);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.70, 82.70) --
+	(158.96, 82.70);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (140.23, 62.56) --
-	(142.33, 62.56);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (179.37,215.32) --
+	(181.63,215.32);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.27,254.77) --
-	(163.38,254.77);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (180.50,215.32) --
+	(180.50, 65.59);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (162.33,254.77) --
-	(162.33,109.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (179.37, 65.59) --
+	(181.63, 65.59);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.27,109.01) --
-	(163.38,109.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.04,230.62) --
+	(204.30,230.62);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (182.32,214.67) --
-	(184.42,214.67);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (203.17,230.62) --
+	(203.17, 95.32);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (183.37,214.67) --
-	(183.37, 75.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (182.32, 75.66) --
-	(184.42, 75.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (203.36,227.78) --
-	(205.46,227.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (204.41,227.78) --
-	(204.41, 97.04);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (203.36, 97.04) --
-	(205.46, 97.04);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.04, 95.32) --
+	(204.30, 95.32);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 44.49, 52.60) rectangle (217.04,264.40);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 53.55, 52.60) rectangle (216.77,264.40);
 \end{scope}
 \begin{scope}
-\path[clip] (249.02, 52.60) rectangle (421.58,264.40);
+\path[clip] (258.35, 52.60) rectangle (421.58,264.40);
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
 
-\path[fill=fillColor] (249.02, 52.60) rectangle (421.58,264.40);
-\definecolor[named]{drawColor}{rgb}{0.40,0.40,0.40}
-\definecolor[named]{fillColor}{rgb}{0.40,0.40,0.40}
+\path[fill=fillColor] (258.35, 52.60) rectangle (421.57,264.40);
+\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
+\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (261.65,115.91) -- (261.65,221.67);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (271.96, 62.23) -- (271.96,215.06);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (282.69, 92.41) -- (282.69,232.88);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (294.63, 95.75) -- (294.63,252.44);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (303.73, 97.96) -- (303.73,237.72);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (317.30, 80.30) -- (317.30,254.77);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (324.78, 63.40) -- (324.78,200.67);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (339.96, 87.24) -- (339.96,249.09);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (345.82, 62.23) -- (345.82,180.88);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (362.63, 83.04) -- (362.63,245.02);
+\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
+\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (366.86,111.64) -- (366.86,254.77);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (385.30, 69.14) -- (385.30,229.47);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (387.91, 79.34) -- (387.91,214.49);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (407.97, 99.45) -- (407.97,243.12);
+\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
+\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (408.95, 95.65) -- (408.95,223.62);
-\definecolor[named]{drawColor}{rgb}{0.40,0.40,0.40}
-\definecolor[named]{fillColor}{rgb}{0.40,0.40,0.40}
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (271.96, 74.51) -- (271.96,202.78);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (261.65,124.41) -- (261.65,213.17);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (294.63,108.35) -- (294.63,239.84);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (282.69,103.70) -- (282.69,221.59);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (317.30, 94.33) -- (317.30,240.75);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (303.73,109.19) -- (303.73,226.48);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (339.96,100.25) -- (339.96,236.08);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (324.78, 74.43) -- (324.78,189.64);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (362.63, 96.06) -- (362.63,232.00);
+\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
+\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (345.82, 71.76) -- (345.82,171.34);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (385.30, 82.03) -- (385.30,216.58);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (366.86,123.15) -- (366.86,243.27);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (387.91, 90.21) -- (387.91,203.63);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (408.95,105.94) -- (408.95,213.34);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (407.97,111.00) -- (407.97,231.57);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (249.02, 72.38) -- (421.58, 72.38);
-\definecolor[named]{drawColor}{rgb}{0.40,0.40,0.40}
-\definecolor[named]{fillColor}{rgb}{0.40,0.40,0.40}
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (258.35, 69.66) -- (421.58, 69.66);
+\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
+\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (261.65,168.79) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (271.96,138.64) circle (  2.85);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.69,162.65) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (294.63,174.10) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (303.73,167.84) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (317.30,167.54) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (324.78,132.03) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (339.96,168.16) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (345.82,121.55) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.63,164.03) circle (  2.85);
+\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
+\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (366.86,183.21) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (385.30,149.31) circle (  2.85);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (387.91,146.92) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (407.97,171.29) circle (  2.85);
+\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (408.95,159.64) circle (  2.85);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (270.82,215.06) --
+	(273.09,215.06);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (260.60,221.67) --
-	(262.70,221.67);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (271.96,215.06) --
+	(271.96, 62.23);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (261.65,221.67) --
-	(261.65,115.91);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (270.82, 62.23) --
+	(273.09, 62.23);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (260.60,115.91) --
-	(262.70,115.91);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (293.49,252.44) --
+	(295.76,252.44);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (281.64,232.88) --
-	(283.74,232.88);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (294.63,252.44) --
+	(294.63, 95.75);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (282.69,232.88) --
-	(282.69, 92.41);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (293.49, 95.75) --
+	(295.76, 95.75);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (281.64, 92.41) --
-	(283.74, 92.41);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (316.16,254.77) --
+	(318.43,254.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (302.68,237.72) --
-	(304.79,237.72);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (317.30,254.77) --
+	(317.30, 80.30);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (303.73,237.72) --
-	(303.73, 97.96);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (316.16, 80.30) --
+	(318.43, 80.30);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (302.68, 97.96) --
-	(304.79, 97.96);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (338.83,249.09) --
+	(341.10,249.09);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (323.73,200.67) --
-	(325.83,200.67);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.96,249.09) --
+	(339.96, 87.24);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (324.78,200.67) --
-	(324.78, 63.40);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (338.83, 87.24) --
+	(341.10, 87.24);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (323.73, 63.40) --
-	(325.83, 63.40);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (361.50,245.02) --
+	(363.77,245.02);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.77,180.88) --
-	(346.87,180.88);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (362.63,245.02) --
+	(362.63, 83.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (345.82,180.88) --
-	(345.82, 62.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (361.50, 83.04) --
+	(363.77, 83.04);
+\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.77, 62.23) --
-	(346.87, 62.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (384.17,229.47) --
+	(386.44,229.47);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (365.81,254.77) --
-	(367.92,254.77);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (385.30,229.47) --
+	(385.30, 69.14);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (366.86,254.77) --
-	(366.86,111.64);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (384.17, 69.14) --
+	(386.44, 69.14);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (365.81,111.64) --
-	(367.92,111.64);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (406.84,243.12) --
+	(409.11,243.12);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (386.85,214.49) --
-	(388.96,214.49);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (407.97,243.12) --
+	(407.97, 99.45);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (387.91,214.49) --
-	(387.91, 79.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (386.85, 79.34) --
-	(388.96, 79.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (407.90,223.62) --
-	(410.00,223.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (408.95,223.62) --
-	(408.95, 95.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (407.90, 95.65) --
-	(410.00, 95.65);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (406.84, 99.45) --
+	(409.11, 99.45);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (249.02, 52.60) rectangle (421.58,264.40);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (258.35, 52.60) rectangle (421.57,264.40);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] ( 44.49,264.40) rectangle (217.04,277.04);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] ( 53.55,264.40) rectangle (216.77,277.04);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.76,267.41) {Ln(Min. Capital Dist.)$_{t-1}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (135.16,267.41) {Ln(Min. Capital Dist.)$_{t-1}$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (249.02,264.40) rectangle (421.58,277.04);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (258.35,264.40) rectangle (421.57,277.04);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (335.30,267.41) {Ln(Min. City Dist.)$_{t-1}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (339.96,267.41) {Ln(Min. City Dist.)$_{t-1}$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 37.37, 63.09) {0.00};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 46.44, 58.92) {0e+00};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 37.37,108.14) {0.02};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 46.44,111.38) {3e-04};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 37.37,153.18) {0.04};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 46.44,163.84) {6e-04};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 37.37,198.23) {0.06};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 37.37,243.28) {0.08};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 46.44,216.30) {9e-04};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (241.91, 69.07) {0.000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (251.24, 66.35) {0.00000};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (241.91,122.66) {0.025};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (251.24,111.91) {0.00025};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (241.91,176.25) {0.050};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (251.24,157.46) {0.00050};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (241.91,229.84) {0.075};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (251.24,203.02) {0.00075};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (251.24,248.58) {0.00100};
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 61.79, 40.81) {Fold A};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 71.83, 40.81) {Fold A};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 82.83, 40.81) {Fold B};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 94.50, 40.81) {Fold B};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (103.87, 40.81) {Fold C};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.17, 40.81) {Fold C};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (124.92, 40.81) {Fold D};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (139.84, 40.81) {Fold D};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (145.96, 40.81) {Fold E};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (162.51, 40.81) {Fold E};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (167.00, 40.81) {Fold F};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (185.17, 40.81) {Fold F};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (188.04, 40.81) {Fold G};
-
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (209.09, 40.81) {Fold H};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (207.84, 40.81) {Fold G};
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (266.32, 40.81) {Fold A};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (276.63, 40.81) {Fold A};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (287.37, 40.81) {Fold B};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (299.30, 40.81) {Fold B};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (308.41, 40.81) {Fold C};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (321.97, 40.81) {Fold C};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (329.45, 40.81) {Fold D};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (344.64, 40.81) {Fold D};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (350.50, 40.81) {Fold E};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (367.31, 40.81) {Fold E};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (371.54, 40.81) {Fold F};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (389.98, 40.81) {Fold F};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (392.58, 40.81) {Fold G};
-
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (413.62, 40.81) {Fold H};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (412.65, 40.81) {Fold G};
 \end{scope}

### 2014-09-25 LaTeX/mCapCoefPlot.tex
updates to tex, and plots

@@
-% Created by tikzDevice version 0.7.0 on 2014-09-23 11:36:12
+% Created by tikzDevice version 0.7.0 on 2014-09-25 14:01:56
 % !TEX encoding = UTF-8 Unicode
@@
 \path[fill=fillColor] (137.46, 34.03) rectangle (277.03,277.03);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (207.65, 49.88) -- (215.05, 49.88);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (206.43, 49.88) -- (213.45, 49.88);
-
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (198.47, 76.30) -- (231.75, 76.30);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (198.55, 76.30) -- (233.74, 76.30);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (183.03,102.71) -- (196.68,102.71);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (176.10,102.71) -- (190.46,102.71);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (165.42,129.12) -- (249.46,129.12);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (154.85,129.12) -- (247.54,129.12);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (175.86,155.53) -- (202.88,155.53);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (172.69,155.53) -- (201.44,155.53);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (207.28,181.95) -- (208.37,181.95);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (207.34,181.95) -- (208.56,181.95);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (194.89,208.36) -- (229.18,208.36);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (197.01,208.36) -- (234.79,208.36);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (189.15,234.77) -- (216.25,234.77);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (183.40,234.77) -- (211.73,234.77);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (209.85,261.19) -- (221.60,261.19);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (209.89,261.19) -- (222.37,261.19);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (208.25, 49.88) -- (214.45, 49.88);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (206.99, 49.88) -- (212.88, 49.88);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (201.15, 76.30) -- (229.08, 76.30);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (201.38, 76.30) -- (230.91, 76.30);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (184.13,102.71) -- (195.58,102.71);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (177.26,102.71) -- (189.31,102.71);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (172.18,129.12) -- (242.71,129.12);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (162.30,129.12) -- (240.08,129.12);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (178.04,155.53) -- (200.70,155.53);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (175.00,155.53) -- (199.13,155.53);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (207.37,181.95) -- (208.28,181.95);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (207.43,181.95) -- (208.46,181.95);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (197.65,208.36) -- (226.42,208.36);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (200.05,208.36) -- (231.75,208.36);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (191.33,234.77) -- (214.07,234.77);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (185.67,234.77) -- (209.45,234.77);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (210.79,261.19) -- (220.66,261.19);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (210.89,261.19) -- (221.37,261.19);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.73,261.19) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (216.13,261.19) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (202.70,234.77) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (197.56,234.77) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (212.04,208.36) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.90,208.36) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.82,181.95) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.95,181.95) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.37,155.53) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.07,155.53) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.44,129.12) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.19,129.12) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.85,102.71) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.28,102.71) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.11, 76.30) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (216.15, 76.30) circle (  2.85);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.94, 49.88) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (211.35, 49.88) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.45, 48.56) --
-	(213.45, 51.20);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (215.05, 48.56) --
+	(215.05, 51.20);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.45, 49.88) --
-	(206.43, 49.88);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (215.05, 49.88) --
+	(207.65, 49.88);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (206.43, 48.56) --
-	(206.43, 51.20);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (207.65, 48.56) --
+	(207.65, 51.20);
+\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (231.75, 74.97) --
-	(231.75, 77.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (233.74, 74.97) --
+	(233.74, 77.62);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (231.75, 76.30) --
-	(198.47, 76.30);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (233.74, 76.30) --
+	(198.55, 76.30);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (198.47, 74.97) --
-	(198.47, 77.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (198.55, 74.97) --
+	(198.55, 77.62);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (196.68,101.39) --
-	(196.68,104.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (190.46,101.39) --
+	(190.46,104.03);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (196.68,102.71) --
-	(183.03,102.71);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (190.46,102.71) --
+	(176.10,102.71);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (183.03,101.39) --
-	(183.03,104.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (176.10,101.39) --
+	(176.10,104.03);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (249.46,127.80) --
-	(249.46,130.44);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (247.54,127.80) --
+	(247.54,130.44);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (249.46,129.12) --
-	(165.42,129.12);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (247.54,129.12) --
+	(154.85,129.12);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.42,127.80) --
-	(165.42,130.44);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.85,127.80) --
+	(154.85,130.44);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (202.88,154.21) --
-	(202.88,156.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (201.44,154.21) --
+	(201.44,156.86);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (202.88,155.53) --
-	(175.86,155.53);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (201.44,155.53) --
+	(172.69,155.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (175.86,154.21) --
-	(175.86,156.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (172.69,154.21) --
+	(172.69,156.86);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (208.37,180.63) --
-	(208.37,183.27);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (208.56,180.63) --
+	(208.56,183.27);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (208.37,181.95) --
-	(207.28,181.95);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (208.56,181.95) --
+	(207.34,181.95);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.28,180.63) --
-	(207.28,183.27);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (207.34,180.63) --
+	(207.34,183.27);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (229.18,207.04) --
-	(229.18,209.68);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (234.79,207.04) --
+	(234.79,209.68);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (229.18,208.36) --
-	(194.89,208.36);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (234.79,208.36) --
+	(197.01,208.36);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (194.89,207.04) --
-	(194.89,209.68);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (197.01,207.04) --
+	(197.01,209.68);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.25,233.45) --
-	(216.25,236.09);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (211.73,233.45) --
+	(211.73,236.09);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.25,234.77) --
-	(189.15,234.77);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (211.73,234.77) --
+	(183.40,234.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (189.15,233.45) --
-	(189.15,236.09);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (183.40,233.45) --
+	(183.40,236.09);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (221.60,259.87) --
-	(221.60,262.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (222.37,259.87) --
+	(222.37,262.51);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (221.60,261.19) --
-	(209.85,261.19);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (222.37,261.19) --
+	(209.89,261.19);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.85,259.87) --
-	(209.85,262.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.89,259.87) --
+	(209.89,262.51);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (143.80, 20.31) {-0.3};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (143.80, 20.31) {-0.004};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (186.10, 20.31) {-0.1};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (175.53, 20.31) {-0.002};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (228.40, 20.31) {0.1};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (207.25, 20.31) {0.000};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (270.69, 20.31) {0.3};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (238.97, 20.31) {0.002};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (270.69, 20.31) {0.004};
 \end{scope}

### 2014-09-25 LaTeX/mCapSimPlot.tex
updates to tex, and plots

@@
-% Created by tikzDevice version 0.7.0 on 2014-09-23 11:40:21
+% Created by tikzDevice version 0.7.0 on 2014-09-25 14:22:37
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 39.69, 34.03) rectangle (421.57,277.03);
+\path[clip] ( 52.48, 34.03) rectangle (421.57,277.03);
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
 
-\path[fill=fillColor] ( 39.69, 34.03) rectangle (421.57,277.03);
+\path[fill=fillColor] ( 52.48, 34.03) rectangle (421.57,277.03);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 57.05,107.99) --
-	( 61.80,109.63) --
-	( 66.56,111.28) --
-	( 71.31,112.93) --
-	( 76.07,114.58) --
-	( 80.82,116.22) --
-	( 85.58,117.87) --
-	( 90.34,119.52) --
-	( 95.09,121.16) --
-	( 99.85,122.81) --
-	(104.60,124.46) --
-	(109.36,126.11) --
-	(114.11,127.75) --
-	(118.87,129.40) --
-	(123.63,131.05) --
-	(128.38,132.70) --
-	(133.14,134.34) --
-	(137.89,135.99) --
-	(142.65,137.64) --
-	(147.40,139.28) --
-	(152.16,140.93) --
-	(156.92,142.58) --
-	(161.67,144.23) --
-	(166.43,145.87) --
-	(171.18,147.52) --
-	(175.94,149.17) --
-	(180.70,150.81) --
-	(185.45,152.46) --
-	(190.21,154.11) --
-	(194.96,155.76) --
-	(199.72,157.40) --
-	(204.47,159.05) --
-	(209.23,160.70) --
-	(213.99,162.34) --
-	(218.74,163.99) --
-	(223.50,165.64) --
-	(228.25,167.29) --
-	(233.01,168.93) --
-	(237.76,170.58) --
-	(242.52,172.23) --
-	(247.28,173.88) --
-	(252.03,175.52) --
-	(256.79,177.17) --
-	(261.54,178.82) --
-	(266.30,180.46) --
-	(271.05,182.11) --
-	(275.81,183.76) --
-	(280.57,185.41) --
-	(285.32,187.05) --
-	(290.08,188.70) --
-	(294.83,190.35) --
-	(299.59,191.99) --
-	(304.35,193.64) --
-	(309.10,195.29) --
-	(313.86,196.94) --
-	(318.61,198.58) --
-	(323.37,200.23) --
-	(328.12,201.88) --
-	(332.88,203.52) --
-	(337.64,205.17) --
-	(342.39,206.82) --
-	(347.15,208.47) --
-	(351.90,210.11) --
-	(356.66,211.76) --
-	(361.41,213.41) --
-	(366.17,215.05) --
-	(370.93,216.70) --
-	(375.68,218.35) --
-	(380.44,220.00) --
-	(385.19,221.64) --
-	(389.95,223.29) --
-	(394.70,224.94) --
-	(399.46,226.59) --
-	(404.22,228.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 69.26,107.02) --
+	( 76.56,109.63) --
+	( 80.61,111.07) --
+	( 80.74,111.12) --
+	( 93.47,115.66) --
+	(101.51,118.53) --
+	(106.88,120.45) --
+	(109.99,121.56) --
+	(116.04,123.72) --
+	(124.61,126.77) --
+	(153.74,137.17) --
+	(166.44,141.70) --
+	(169.66,142.85) --
+	(182.48,147.43) --
+	(189.23,149.83) --
+	(198.25,153.05) --
+	(202.82,154.68) --
+	(205.60,155.68) --
+	(205.69,155.71) --
+	(206.30,155.92) --
+	(207.92,156.50) --
+	(209.67,157.13) --
+	(214.56,158.87) --
+	(214.75,158.94) --
+	(219.02,160.46) --
+	(220.78,161.09) --
+	(224.96,162.59) --
+	(226.35,163.08) --
+	(226.45,163.12) --
+	(226.69,163.20) --
+	(227.16,163.37) --
+	(229.07,164.05) --
+	(229.22,164.10) --
+	(229.80,164.31) --
+	(230.46,164.55) --
+	(231.37,164.87) --
+	(232.05,165.12) --
+	(232.29,165.20) --
+	(232.34,165.22) --
+	(232.73,165.36) --
+	(237.64,167.11) --
+	(239.57,167.80) --
+	(239.75,167.86) --
+	(240.75,168.22) --
+	(241.66,168.54) --
+	(242.52,168.85) --
+	(243.48,169.19) --
+	(244.41,169.52) --
+	(245.54,169.93) --
+	(245.55,169.93) --
+	(247.34,170.57) --
+	(247.36,170.58) --
+	(248.05,170.82) --
+	(248.78,171.09) --
+	(249.23,171.25) --
+	(249.60,171.38) --
+	(252.59,172.45) --
+	(255.95,173.64) --
+	(257.34,174.14) --
+	(257.79,174.30) --
+	(257.94,174.35) --
+	(258.24,174.46) --
+	(259.46,174.90) --
+	(259.93,175.06) --
+	(261.11,175.48) --
+	(261.30,175.55) --
+	(261.73,175.70) --
+	(263.06,176.18) --
+	(264.22,176.59) --
+	(266.18,177.29) --
+	(267.22,177.66) --
+	(267.29,177.69) --
+	(268.47,178.11) --
+	(269.59,178.51) --
+	(270.46,178.82) --
+	(271.09,179.05) --
+	(271.37,179.15) --
+	(271.86,179.32) --
+	(271.89,179.33) --
+	(272.02,179.38) --
+	(272.38,179.51) --
+	(272.44,179.53) --
+	(273.54,179.92) --
+	(273.54,179.92) --
+	(274.54,180.28) --
+	(274.62,180.31) --
+	(274.74,180.35) --
+	(274.93,180.42) --
+	(275.09,180.47) --
+	(275.27,180.54) --
+	(275.51,180.62) --
+	(275.85,180.75) --
+	(276.03,180.81) --
+	(276.19,180.86) --
+	(276.46,180.96) --
+	(276.61,181.01) --
+	(278.14,181.56) --
+	(278.91,181.83) --
+	(278.99,181.86) --
+	(279.48,182.04) --
+	(279.57,182.07) --
+	(279.84,182.17) --
+	(280.03,182.23) --
+	(280.82,182.52) --
+	(281.34,182.70) --
+	(281.36,182.71) --
+	(281.96,182.92) --
+	(282.46,183.10) --
+	(282.56,183.14) --
+	(283.13,183.34) --
+	(283.17,183.36) --
+	(283.65,183.53) --
+	(283.74,183.56) --
+	(285.14,184.06) --
+	(285.23,184.09) --
+	(285.29,184.11) --
+	(285.32,184.13) --
+	(285.65,184.24) --
+	(286.10,184.40) --
+	(286.16,184.42) --
+	(286.46,184.53) --
+	(286.60,184.58) --
+	(286.65,184.60) --
+	(286.71,184.62) --
+	(286.73,184.63) --
+	(286.83,184.66) --
+	(286.86,184.67) --
+	(287.36,184.85) --
+	(287.70,184.97) --
+	(287.78,185.00) --
+	(289.22,185.51) --
+	(289.39,185.58) --
+	(289.45,185.60) --
+	(289.83,185.73) --
+	(289.89,185.75) --
+	(290.32,185.91) --
+	(290.49,185.97) --
+	(290.52,185.98) --
+	(290.79,186.08) --
+	(290.84,186.09) --
+	(290.85,186.10) --
+	(290.85,186.10) --
+	(290.88,186.11) --
+	(290.92,186.12) --
+	(291.46,186.31) --
+	(291.68,186.39) --
+	(292.03,186.52) --
+	(292.66,186.74) --
+	(292.90,186.83) --
+	(293.68,187.11) --
+	(294.05,187.24) --
+	(294.33,187.34) --
+	(294.72,187.48) --
+	(294.89,187.54) --
+	(294.98,187.57) --
+	(295.14,187.63) --
+	(295.44,187.73) --
+	(295.54,187.77) --
+	(295.80,187.86) --
+	(296.23,188.02) --
+	(297.04,188.31) --
+	(297.20,188.36) --
+	(297.32,188.41) --
+	(297.39,188.43) --
+	(297.92,188.62) --
+	(298.07,188.67) --
+	(298.46,188.81) --
+	(298.47,188.82) --
+	(298.54,188.84) --
+	(298.62,188.87) --
+	(299.15,189.06) --
+	(299.26,189.10) --
+	(299.54,189.20) --
+	(299.58,189.21) --
+	(300.71,189.62) --
+	(301.41,189.86) --
+	(302.13,190.12) --
+	(302.61,190.29) --
+	(303.45,190.59) --
+	(303.55,190.63) --
+	(303.59,190.64) --
+	(303.66,190.67) --
+	(303.89,190.75) --
+	(303.92,190.76) --
+	(304.13,190.84) --
+	(304.31,190.90) --
+	(304.32,190.90) --
+	(304.63,191.01) --
+	(305.44,191.30) --
+	(306.03,191.51) --
+	(306.65,191.74) --
+	(307.10,191.90) --
+	(307.15,191.91) --
+	(307.34,191.98) --
+	(307.36,191.99) --
+	(307.48,192.03) --
+	(307.57,192.06) --
+	(307.71,192.11) --
+	(307.78,192.14) --
+	(307.86,192.17) --
+	(308.14,192.27) --
+	(308.17,192.28) --
+	(308.40,192.36) --
+	(309.29,192.68) --
+	(309.65,192.80) --
+	(309.66,192.81) --
+	(309.77,192.85) --
+	(309.85,192.88) --
+	(310.26,193.02) --
+	(310.42,193.08) --
+	(310.88,193.25) --
+	(310.97,193.28) --
+	(311.25,193.38) --
+	(312.09,193.68) --
+	(312.22,193.72) --
+	(312.41,193.79) --
+	(313.42,194.15) --
+	(313.62,194.22) --
+	(313.78,194.28) --
+	(314.05,194.38) --
+	(314.50,194.54) --
+	(314.58,194.57) --
+	(314.67,194.60) --
+	(315.27,194.81) --
+	(315.36,194.84) --
+	(315.70,194.96) --
+	(315.87,195.03) --
+	(315.98,195.06) --
+	(316.35,195.20) --
+	(316.56,195.27) --
+	(316.72,195.33) --
+	(317.21,195.50) --
+	(317.49,195.60) --
+	(317.56,195.63) --
+	(318.84,196.09) --
+	(318.87,196.09) --
+	(319.28,196.24) --
+	(319.56,196.34) --
+	(319.75,196.41) --
+	(319.97,196.49) --
+	(320.23,196.58) --
+	(320.29,196.60) --
+	(320.33,196.62) --
+	(320.94,196.84) --
+	(321.01,196.86) --
+	(321.22,196.93) --
+	(321.25,196.94) --
+	(321.36,196.98) --
+	(321.75,197.12) --
+	(323.15,197.62) --
+	(323.66,197.81) --
+	(325.17,198.34) --
+	(325.77,198.56) --
+	(325.89,198.60) --
+	(326.94,198.97) --
+	(327.01,199.00) --
+	(327.29,199.10) --
+	(328.29,199.46) --
+	(328.36,199.48) --
+	(328.82,199.65) --
+	(329.10,199.75) --
+	(329.71,199.96) --
+	(330.08,200.10) --
+	(330.10,200.10) --
+	(330.14,200.12) --
+	(330.37,200.20) --
+	(330.66,200.30) --
+	(331.19,200.49) --
+	(331.66,200.66) --
+	(331.92,200.75) --
+	(332.49,200.96) --
+	(333.01,201.14) --
+	(334.21,201.57) --
+	(334.41,201.64) --
+	(334.89,201.81) --
+	(337.42,202.72) --
+	(337.45,202.72) --
+	(337.58,202.77) --
+	(337.70,202.81) --
+	(337.71,202.82) --
+	(337.80,202.85) --
+	(339.18,203.34) --
+	(339.28,203.38) --
+	(341.35,204.12) --
+	(341.75,204.26) --
+	(342.17,204.41) --
+	(342.48,204.52) --
+	(342.53,204.54) --
+	(342.69,204.60) --
+	(342.85,204.65) --
+	(343.03,204.72) --
+	(343.17,204.77) --
+	(343.37,204.84) --
+	(343.45,204.87) --
+	(343.75,204.97) --
+	(343.88,205.02) --
+	(344.23,205.14) --
+	(345.06,205.44) --
+	(346.03,205.79) --
+	(346.49,205.95) --
+	(347.23,206.21) --
+	(347.38,206.27) --
+	(348.49,206.66) --
+	(348.58,206.70) --
+	(349.13,206.89) --
+	(349.81,207.14) --
+	(350.10,207.24) --
+	(350.24,207.29) --
+	(350.58,207.41) --
+	(351.85,207.86) --
+	(352.05,207.94) --
+	(352.77,208.19) --
+	(353.17,208.34) --
+	(353.42,208.43) --
+	(353.71,208.53) --
+	(354.71,208.88) --
+	(355.56,209.19) --
+	(357.56,209.90) --
+	(357.72,209.96) --
+	(357.97,210.05) --
+	(358.00,210.06) --
+	(358.30,210.17) --
+	(358.37,210.19) --
+	(358.57,210.26) --
+	(358.60,210.27) --
+	(358.96,210.40) --
+	(358.97,210.41) --
+	(359.44,210.57) --
+	(359.71,210.67) --
+	(359.84,210.72) --
+	(359.89,210.73) --
+	(359.95,210.75) --
+	(360.12,210.82) --
+	(360.50,210.95) --
+	(360.53,210.96) --
+	(361.15,211.18) --
+	(361.24,211.21) --
+	(361.57,211.33) --
+	(362.32,211.60) --
+	(362.86,211.79) --
+	(362.88,211.80) --
+	(362.99,211.84) --
+	(363.37,211.98) --
+	(365.15,212.61) --
+	(365.51,212.74) --
+	(365.58,212.76) --
+	(365.58,212.76) --
+	(366.24,213.00) --
+	(366.27,213.01) --
+	(366.79,213.19) --
+	(367.09,213.30) --
+	(367.28,213.37) --
+	(367.50,213.45) --
+	(367.74,213.54) --
+	(368.30,213.73) --
+	(368.30,213.73) --
+	(368.38,213.76) --
+	(368.49,213.80) --
+	(368.90,213.95) --
+	(369.46,214.15) --
+	(370.56,214.54) --
+	(370.74,214.60) --
+	(370.85,214.64) --
+	(372.47,215.22) --
+	(373.39,215.55) --
+	(373.79,215.69) --
+	(374.21,215.84) --
+	(375.70,216.37) --
+	(378.93,217.53) --
+	(380.42,218.06) --
+	(385.52,219.88) --
+	(386.08,220.08) --
+	(386.54,220.24) --
+	(386.90,220.37) --
+	(387.31,220.52) --
+	(387.53,220.60) --
+	(388.24,220.85) --
+	(388.35,220.89) --
+	(388.69,221.01) --
+	(388.71,221.02) --
+	(388.75,221.03) --
+	(388.90,221.08) --
+	(389.17,221.18) --
+	(389.73,221.38) --
+	(390.59,221.69) --
+	(391.22,221.91) --
+	(391.77,222.11) --
+	(391.82,222.13) --
+	(392.15,222.25) --
+	(392.41,222.34) --
+	(396.33,223.74) --
+	(397.13,224.02) --
+	(397.28,224.07) --
+	(404.32,226.59) --
+	(404.80,226.76);
 \definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}
 
-\path[fill=fillColor,fill opacity=0.30] ( 57.05,170.30) --
-	( 61.80,170.75) --
-	( 66.56,171.43) --
-	( 71.31,172.00) --
-	( 76.07,172.73) --
-	( 80.82,173.39) --
-	( 85.58,174.13) --
-	( 90.34,174.65) --
-	( 95.09,175.20) --
-	( 99.85,175.83) --
-	(104.60,176.50) --
-	(109.36,177.16) --
-	(114.11,177.80) --
-	(118.87,178.59) --
-	(123.63,179.29) --
-	(128.38,179.81) --
-	(133.14,180.41) --
-	(137.89,181.20) --
-	(142.65,181.89) --
-	(147.40,182.78) --
-	(152.16,183.41) --
-	(156.92,183.93) --
-	(161.67,184.69) --
-	(166.43,185.42) --
-	(171.18,186.20) --
-	(175.94,187.05) --
-	(180.70,188.02) --
-	(185.45,188.60) --
-	(190.21,189.50) --
-	(194.96,190.46) --
-	(199.72,191.24) --
-	(204.47,192.15) --
-	(209.23,193.07) --
-	(213.99,194.11) --
-	(218.74,195.08) --
-	(223.50,196.00) --
-	(228.25,196.95) --
-	(233.01,198.08) --
-	(237.76,199.37) --
-	(242.52,200.49) --
-	(247.28,201.79) --
-	(252.03,203.07) --
-	(256.79,204.30) --
-	(261.54,205.54) --
-	(266.30,207.04) --
-	(271.05,208.33) --
-	(275.81,209.80) --
-	(280.57,211.29) --
-	(285.32,212.83) --
-	(290.08,214.53) --
-	(294.83,216.23) --
-	(299.59,217.85) --
-	(304.35,219.60) --
-	(309.10,221.58) --
-	(313.86,223.41) --
-	(318.61,225.32) --
-	(323.37,227.31) --
-	(328.12,229.50) --
-	(332.88,231.70) --
-	(337.64,233.85) --
-	(342.39,235.89) --
-	(347.15,238.03) --
-	(351.90,240.17) --
-	(356.66,242.38) --
-	(361.41,244.58) --
-	(366.17,246.95) --
-	(370.93,249.06) --
-	(375.68,251.34) --
-	(380.44,253.72) --
-	(385.19,255.97) --
-	(389.95,258.60) --
-	(394.70,261.10) --
-	(399.46,263.65) --
-	(404.22,265.99) --
-	(404.22,189.23) --
-	(399.46,188.51) --
-	(394.70,187.90) --
-	(389.95,187.02) --
-	(385.19,186.13) --
-	(380.44,185.09) --
-	(375.68,184.39) --
-	(370.93,183.61) --
-	(366.17,182.69) --
-	(361.41,181.83) --
-	(356.66,180.81) --
-	(351.90,179.77) --
-	(347.15,178.57) --
-	(342.39,177.44) --
-	(337.64,176.32) --
-	(332.88,175.29) --
-	(328.12,174.08) --
-	(323.37,172.90) --
-	(318.61,171.57) --
-	(313.86,170.24) --
-	(309.10,168.76) --
-	(304.35,167.31) --
-	(299.59,165.82) --
-	(294.83,164.52) --
-	(290.08,162.91) --
-	(285.32,161.16) --
-	(280.57,159.46) --
-	(275.81,157.79) --
-	(271.05,155.95) --
-	(266.30,154.07) --
-	(261.54,152.24) --
-	(256.79,150.23) --
-	(252.03,148.25) --
-	(247.28,146.22) --
-	(242.52,143.99) --
-	(237.76,141.83) --
-	(233.01,139.84) --
-	(228.25,137.63) --
-	(223.50,135.49) --
-	(218.74,133.10) --
-	(213.99,130.62) --
-	(209.23,128.31) --
-	(204.47,125.87) --
-	(199.72,123.59) --
-	(194.96,121.22) --
-	(190.21,118.75) --
-	(185.45,116.43) --
-	(180.70,114.03) --
-	(175.94,111.47) --
-	(171.18,108.99) --
-	(166.43,106.38) --
-	(161.67,103.74) --
-	(156.92,101.22) --
-	(152.16, 98.74) --
-	(147.40, 96.24) --
-	(142.65, 93.73) --
-	(137.89, 91.21) --
-	(133.14, 88.50) --
-	(128.38, 85.77) --
-	(123.63, 83.16) --
-	(118.87, 80.48) --
-	(114.11, 77.79) --
-	(109.36, 75.08) --
-	(104.60, 72.30) --
-	( 99.85, 69.52) --
-	( 95.09, 66.86) --
-	( 90.34, 64.14) --
-	( 85.58, 61.43) --
-	( 80.82, 58.71) --
-	( 76.07, 55.94) --
-	( 71.31, 53.21) --
-	( 66.56, 50.50) --
-	( 61.80, 47.80) --
-	( 57.05, 45.08) --
+\path[fill=fillColor,fill opacity=0.30] ( 69.26,167.58) --
+	( 76.56,168.49) --
+	( 80.61,169.02) --
+	( 80.74,169.02) --
+	( 93.47,170.57) --
+	(101.51,171.61) --
+	(106.88,172.38) --
+	(109.99,172.78) --
+	(116.04,173.71) --
+	(124.61,175.00) --
+	(153.74,179.40) --
+	(166.44,181.37) --
+	(169.66,181.90) --
+	(182.48,184.32) --
+	(189.23,185.73) --
+	(198.25,187.43) --
+	(202.82,188.36) --
+	(205.60,189.03) --
+	(205.69,189.04) --
+	(206.30,189.17) --
+	(207.92,189.53) --
+	(209.67,189.86) --
+	(214.56,191.01) --
+	(214.75,191.06) --
+	(219.02,191.93) --
+	(220.78,192.25) --
+	(224.96,193.40) --
+	(226.35,193.80) --
+	(226.45,193.83) --
+	(226.69,193.88) --
+	(227.16,193.97) --
+	(229.07,194.38) --
+	(229.22,194.47) --
+	(229.80,194.62) --
+	(230.46,194.79) --
+	(231.37,195.05) --
+	(232.05,195.24) --
+	(232.29,195.30) --
+	(232.34,195.31) --
+	(232.73,195.42) --
+	(237.64,196.73) --
+	(239.57,197.26) --
+	(239.75,197.33) --
+	(240.75,197.60) --
+	(241.66,197.84) --
+	(242.52,198.05) --
+	(243.48,198.31) --
+	(244.41,198.51) --
+	(245.54,198.84) --
+	(245.55,198.85) --
+	(247.34,199.26) --
+	(247.36,199.27) --
+	(248.05,199.47) --
+	(248.78,199.61) --
+	(249.23,199.75) --
+	(249.60,199.85) --
+	(252.59,200.68) --
+	(255.95,201.50) --
+	(257.34,201.84) --
+	(257.79,201.94) --
+	(257.94,202.01) --
+	(258.24,202.10) --
+	(259.46,202.47) --
+	(259.93,202.59) --
+	(261.11,202.97) --
+	(261.30,203.05) --
+	(261.73,203.20) --
+	(263.06,203.72) --
+	(264.22,204.06) --
+	(266.18,204.56) --
+	(267.22,204.89) --
+	(267.29,204.91) --
+	(268.47,205.25) --
+	(269.59,205.73) --
+	(270.46,206.09) --
+	(271.09,206.28) --
+	(271.37,206.36) --
+	(271.86,206.51) --
+	(271.89,206.52) --
+	(272.02,206.57) --
+	(272.38,206.68) --
+	(272.44,206.71) --
+	(273.54,207.03) --
+	(273.54,207.03) --
+	(274.54,207.35) --
+	(274.62,207.37) --
+	(274.74,207.40) --
+	(274.93,207.48) --
+	(275.09,207.54) --
+	(275.27,207.59) --
+	(275.51,207.69) --
+	(275.85,207.76) --
+	(276.03,207.79) --
+	(276.19,207.84) --
+	(276.46,207.94) --
+	(276.61,207.99) --
+	(278.14,208.40) --
+	(278.91,208.64) --
+	(278.99,208.66) --
+	(279.48,208.87) --
+	(279.57,208.92) --
+	(279.84,208.96) --
+	(280.03,208.99) --
+	(280.82,209.17) --
+	(281.34,209.31) --
+	(281.36,209.32) --
+	(281.96,209.48) --
+	(282.46,209.66) --
+	(282.56,209.69) --
+	(283.13,209.95) --
+	(283.17,209.97) --
+	(283.65,210.14) --
+	(283.74,210.15) --
+	(285.14,210.63) --
+	(285.23,210.67) --
+	(285.29,210.69) --
+	(285.32,210.71) --
+	(285.65,210.81) --
+	(286.10,210.98) --
+	(286.16,211.01) --
+	(286.46,211.13) --
+	(286.60,211.18) --
+	(286.65,211.20) --
+	(286.71,211.21) --
+	(286.73,211.21) --
+	(286.83,211.23) --
+	(286.86,211.24) --
+	(287.36,211.42) --
+	(287.70,211.53) --
+	(287.78,211.57) --
+	(289.22,212.06) --
+	(289.39,212.10) --
+	(289.45,212.13) --
+	(289.83,212.25) --
+	(289.89,212.27) --
+	(290.32,212.44) --
+	(290.49,212.49) --
+	(290.52,212.50) --
+	(290.79,212.58) --
+	(290.84,212.60) --
+	(290.85,212.60) --
+	(290.85,212.60) --
+	(290.88,212.61) --
+	(290.92,212.62) --
+	(291.46,212.83) --
+	(291.68,212.92) --
+	(292.03,213.07) --
+	(292.66,213.31) --
+	(292.90,213.41) --
+	(293.68,213.72) --
+	(294.05,213.86) --
+	(294.33,213.95) --
+	(294.72,214.08) --
+	(294.89,214.17) --
+	(294.98,214.23) --
+	(295.14,214.31) --
+	(295.44,214.42) --
+	(295.54,214.45) --
+	(295.80,214.55) --
+	(296.23,214.74) --
+	(297.04,215.07) --
+	(297.20,215.13) --
+	(297.32,215.18) --
+	(297.39,215.20) --
+	(297.92,215.38) --
+	(298.07,215.42) --
+	(298.46,215.59) --
+	(298.47,215.59) --
+	(298.54,215.62) --
+	(298.62,215.65) --
+	(299.15,215.80) --
+	(299.26,215.83) --
+	(299.54,215.92) --
+	(299.58,215.93) --
+	(300.71,216.45) --
+	(301.41,216.73) --
+	(302.13,217.04) --
+	(302.61,217.20) --
+	(303.45,217.53) --
+	(303.55,217.56) --
+	(303.59,217.58) --
+	(303.66,217.61) --
+	(303.89,217.71) --
+	(303.92,217.72) --
+	(304.13,217.80) --
+	(304.31,217.89) --
+	(304.32,217.89) --
+	(304.63,218.07) --
+	(305.44,218.39) --
+	(306.03,218.64) --
+	(306.65,218.85) --
+	(307.10,219.05) --
+	(307.15,219.08) --
+	(307.34,219.17) --
+	(307.36,219.18) --
+	(307.48,219.22) --
+	(307.57,219.26) --
+	(307.71,219.29) --
+	(307.78,219.32) --
+	(307.86,219.33) --
+	(308.14,219.41) --
+	(308.17,219.43) --
+	(308.40,219.53) --
+	(309.29,219.89) --
+	(309.65,220.03) --
+	(309.66,220.04) --
+	(309.77,220.06) --
+	(309.85,220.08) --
+	(310.26,220.25) --
+	(310.42,220.31) --
+	(310.88,220.51) --
+	(310.97,220.54) --
+	(311.25,220.65) --
+	(312.09,220.89) --
+	(312.22,220.94) --
+	(312.41,221.03) --
+	(313.42,221.40) --
+	(313.62,221.47) --
+	(313.78,221.52) --
+	(314.05,221.67) --
+	(314.50,221.90) --
+	(314.58,221.94) --
+	(314.67,221.97) --
+	(315.27,222.21) --
+	(315.36,222.23) --
+	(315.70,222.38) --
+	(315.87,222.44) --
+	(315.98,222.48) --
+	(316.35,222.60) --
+	(316.56,222.70) --
+	(316.72,222.78) --
+	(317.21,222.97) --
+	(317.49,223.13) --
+	(317.56,223.16) --
+	(318.84,223.77) --
+	(318.87,223.77) --
+	(319.28,223.88) --
+	(319.56,224.01) --
+	(319.75,224.09) --
+	(319.97,224.18) --
+	(320.23,224.27) --
+	(320.29,224.29) --
+	(320.33,224.31) --
+	(320.94,224.63) --
+	(321.01,224.66) --
+	(321.22,224.74) --
+	(321.25,224.75) --
+	(321.36,224.78) --
+	(321.75,224.91) --
+	(323.15,225.56) --
+	(323.66,225.78) --
+	(325.17,226.53) --
+	(325.77,226.82) --
+	(325.89,226.87) --
+	(326.94,227.29) --
+	(327.01,227.33) --
+	(327.29,227.43) --
+	(328.29,227.87) --
+	(328.36,227.90) --
+	(328.82,228.09) --
+	(329.10,228.24) --
+	(329.71,228.50) --
+	(330.08,228.68) --
+	(330.10,228.68) --
+	(330.14,228.70) --
+	(330.37,228.80) --
+	(330.66,228.94) --
+	(331.19,229.21) --
+	(331.66,229.41) --
+	(331.92,229.55) --
+	(332.49,229.78) --
+	(333.01,230.05) --
+	(334.21,230.64) --
+	(334.41,230.77) --
+	(334.89,230.98) --
+	(337.42,232.04) --
+	(337.45,232.05) --
+	(337.58,232.13) --
+	(337.70,232.18) --
+	(337.71,232.18) --
+	(337.80,232.22) --
+	(339.18,232.90) --
+	(339.28,232.95) --
+	(341.35,233.86) --
+	(341.75,234.03) --
+	(342.17,234.21) --
+	(342.48,234.37) --
+	(342.53,234.40) --
+	(342.69,234.46) --
+	(342.85,234.53) --
+	(343.03,234.60) --
+	(343.17,234.65) --
+	(343.37,234.74) --
+	(343.45,234.77) --
+	(343.75,234.90) --
+	(343.88,234.96) --
+	(344.23,235.11) --
+	(345.06,235.47) --
+	(346.03,235.91) --
+	(346.49,236.10) --
+	(347.23,236.53) --
+	(347.38,236.62) --
+	(348.49,237.12) --
+	(348.58,237.18) --
+	(349.13,237.46) --
+	(349.81,237.76) --
+	(350.10,237.92) --
+	(350.24,237.98) --
+	(350.58,238.16) --
+	(351.85,238.80) --
+	(352.05,238.90) --
+	(352.77,239.24) --
+	(353.17,239.44) --
+	(353.42,239.54) --
+	(353.71,239.66) --
+	(354.71,240.11) --
+	(355.56,240.57) --
+	(357.56,241.53) --
+	(357.72,241.60) --
+	(357.97,241.72) --
+	(358.00,241.74) --
+	(358.30,241.88) --
+	(358.37,241.91) --
+	(358.57,242.01) --
+	(358.60,242.02) --
+	(358.96,242.21) --
+	(358.97,242.22) --
+	(359.44,242.45) --
+	(359.71,242.56) --
+	(359.84,242.65) --
+	(359.89,242.68) --
+	(359.95,242.70) --
+	(360.12,242.82) --
+	(360.50,242.98) --
+	(360.53,242.99) --
+	(361.15,243.34) --
+	(361.24,243.39) --
+	(361.57,243.56) --
+	(362.32,243.88) --
+	(362.86,244.15) --
+	(362.88,244.16) --
+	(362.99,244.21) --
+	(363.37,244.41) --
+	(365.15,245.33) --
+	(365.51,245.52) --
+	(365.58,245.55) --
+	(365.58,245.55) --
+	(366.24,245.88) --
+	(366.27,245.90) --
+	(366.79,246.19) --
+	(367.09,246.30) --
+	(367.28,246.39) --
+	(367.50,246.52) --
+	(367.74,246.66) --
+	(368.30,246.92) --
+	(368.30,246.92) --
+	(368.38,246.95) --
+	(368.49,247.00) --
+	(368.90,247.19) --
+	(369.46,247.45) --
+	(370.56,248.00) --
+	(370.74,248.06) --
+	(370.85,248.13) --
+	(372.47,248.84) --
+	(373.39,249.28) --
+	(373.79,249.49) --
+	(374.21,249.72) --
+	(375.70,250.52) --
+	(378.93,252.19) --
+	(380.42,253.06) --
+	(385.52,255.81) --
+	(386.08,256.12) --
+	(386.54,256.36) --
+	(386.90,256.56) --
+	(387.31,256.78) --
+	(387.53,256.89) --
+	(388.24,257.30) --
+	(388.35,257.37) --
+	(388.69,257.57) --
+	(388.71,257.58) --
+	(388.75,257.60) --
+	(388.90,257.69) --
+	(389.17,257.84) --
+	(389.73,258.09) --
+	(390.59,258.54) --
+	(391.22,258.88) --
+	(391.77,259.16) --
+	(391.82,259.17) --
+	(392.15,259.38) --
+	(392.41,259.49) --
+	(396.33,261.54) --
+	(397.13,261.95) --
+	(397.28,262.02) --
+	(404.32,265.72) --
+	(404.80,265.99) --
+	(404.80,187.19) --
+	(404.32,187.06) --
+	(397.28,186.09) --
+	(397.13,186.06) --
+	(396.33,185.88) --
+	(392.41,185.16) --
+	(392.15,185.08) --
+	(391.82,184.98) --
+	(391.77,184.96) --
+	(391.22,184.83) --
+	(390.59,184.77) --
+	(389.73,184.61) --
+	(389.17,184.48) --
+	(388.90,184.43) --
+	(388.75,184.40) --
+	(388.71,184.40) --
+	(388.69,184.39) --
+	(388.35,184.33) --
+	(388.24,184.32) --
+	(387.53,184.20) --
+	(387.31,184.16) --
+	(386.90,184.09) --
+	(386.54,183.99) --
+	(386.08,183.85) --
+	(385.52,183.74) --
+	(380.42,182.74) --
+	(378.93,182.37) --
+	(375.70,181.71) --
+	(374.21,181.28) --
+	(373.79,181.13) --
+	(373.39,181.02) --
+	(372.47,180.83) --
+	(370.85,180.50) --
+	(370.74,180.49) --
+	(370.56,180.44) --
+	(369.46,180.14) --
+	(368.90,179.97) --
+	(368.49,179.90) --
+	(368.38,179.87) --
+	(368.30,179.85) --
+	(368.30,179.85) --
+	(367.74,179.77) --
+	(367.50,179.74) --
+	(367.28,179.72) --
+	(367.09,179.69) --
+	(366.79,179.59) --
+	(366.27,179.50) --
+	(366.24,179.50) --
+	(365.58,179.36) --
+	(365.58,179.36) --
+	(365.51,179.34) --
+	(365.15,179.23) --
+	(363.37,178.83) --
+	(362.99,178.73) --
+	(362.88,178.70) --
+	(362.86,178.69) --
+	(362.32,178.55) --
+	(361.57,178.28) --
+	(361.24,178.19) --
+	(361.15,178.17) --
+	(360.53,178.07) --
+	(360.50,178.06) --
+	(360.12,177.98) --
+	(359.95,177.95) --
+	(359.89,177.93) --
+	(359.84,177.92) --
+	(359.71,177.88) --
+	(359.44,177.80) --
+	(358.97,177.71) --
+	(358.96,177.71) --
+	(358.60,177.64) --
+	(358.57,177.63) --
+	(358.37,177.60) --
+	(358.30,177.60) --
+	(358.00,177.51) --
+	(357.97,177.49) --
+	(357.72,177.41) --
+	(357.56,177.37) --
+	(355.56,176.98) --
+	(354.71,176.78) --
+	(353.71,176.53) --
+	(353.42,176.47) --
+	(353.17,176.42) --
+	(352.77,176.32) --
+	(352.05,176.22) --
+	(351.85,176.14) --
+	(350.58,175.77) --
+	(350.24,175.68) --
+	(350.10,175.64) --
+	(349.81,175.57) --
+	(349.13,175.50) --
+	(348.58,175.34) --
+	(348.49,175.31) --
+	(347.38,175.04) --
+	(347.23,175.00) --
+	(346.49,174.84) --
+	(346.03,174.73) --
+	(345.06,174.54) --
+	(344.23,174.31) --
+	(343.88,174.22) --
+	(343.75,174.18) --
+	(343.45,174.11) --
+	(343.37,174.09) --
+	(343.17,174.02) --
+	(343.03,173.97) --
+	(342.85,173.91) --
+	(342.69,173.86) --
+	(342.53,173.81) --
+	(342.48,173.80) --
+	(342.17,173.68) --
+	(341.75,173.58) --
+	(341.35,173.51) --
+	(339.28,173.04) --
+	(339.18,173.03) --
+	(337.80,172.73) --
+	(337.71,172.72) --
+	(337.70,172.72) --
+	(337.58,172.70) --
+	(337.45,172.64) --
+	(337.42,172.63) --
+	(334.89,171.98) --
+	(334.41,171.89) --
+	(334.21,171.81) --
+	(333.01,171.45) --
+	(332.49,171.27) --
+	(331.92,171.05) --
+	(331.66,170.98) --
+	(331.19,170.85) --
+	(330.66,170.74) --
+	(330.37,170.62) --
+	(330.14,170.56) --
+	(330.10,170.55) --
+	(330.08,170.54) --
+	(329.71,170.44) --
+	(329.10,170.30) --
+	(328.82,170.26) --
+	(328.36,170.16) --
+	(328.29,170.15) --
+	(327.29,169.86) --
+	(327.01,169.78) --
+	(326.94,169.75) --
+	(325.89,169.42) --
+	(325.77,169.39) --
+	(325.17,169.23) --
+	(323.66,168.80) --
+	(323.15,168.62) --
+	(321.75,168.21) --
+	(321.36,168.09) --
+	(321.25,168.05) --
+	(321.22,168.04) --
+	(321.01,167.98) --
+	(320.94,167.93) --
+	(320.33,167.77) --
+	(320.29,167.76) --
+	(320.23,167.74) --
+	(319.97,167.67) --
+	(319.75,167.57) --
+	(319.56,167.52) --
+	(319.28,167.46) --
+	(318.87,167.33) --
+	(318.84,167.33) --
+	(317.56,166.94) --
+	(317.49,166.92) --
+	(317.21,166.84) --
+	(316.72,166.71) --
+	(316.56,166.68) --
+	(316.35,166.61) --
+	(315.98,166.48) --
+	(315.87,166.43) --
+	(315.70,166.38) --
+	(315.36,166.28) --
+	(315.27,166.25) --
+	(314.67,166.07) --
+	(314.58,166.04) --
+	(314.50,166.02) --
+	(314.05,165.88) --
+	(313.78,165.83) --
+	(313.62,165.78) --
+	(313.42,165.72) --
+	(312.41,165.41) --
+	(312.22,165.34) --
+	(312.09,165.30) --
+	(311.25,165.06) --
+	(310.97,165.00) --
+	(310.88,164.98) --
+	(310.42,164.86) --
+	(310.26,164.82) --
+	(309.85,164.69) --
+	(309.77,164.66) --
+	(309.66,164.62) --
+	(309.65,164.61) --
+	(309.29,164.48) --
+	(308.40,164.29) --
+	(308.17,164.21) --
+	(308.14,164.19) --
+	(307.86,164.11) --
+	(307.78,164.09) --
+	(307.71,164.08) --
+	(307.57,164.04) --
+	(307.48,164.01) --
+	(307.36,163.96) --
+	(307.34,163.95) --
+	(307.15,163.88) --
+	(307.10,163.87) --
+	(306.65,163.74) --
+	(306.03,163.55) --
+	(305.44,163.36) --
+	(304.63,163.10) --
+	(304.32,162.99) --
+	(304.31,162.99) --
+	(304.13,162.94) --
+	(303.92,162.88) --
+	(303.89,162.87) --
+	(303.66,162.79) --
+	(303.59,162.77) --
+	(303.55,162.76) --
+	(303.45,162.74) --
+	(302.61,162.56) --
+	(302.13,162.46) --
+	(301.41,162.29) --
+	(300.71,162.10) --
+	(299.58,161.75) --
+	(299.54,161.74) --
+	(299.26,161.63) --
+	(299.15,161.58) --
+	(298.62,161.31) --
+	(298.54,161.31) --
+	(298.47,161.28) --
+	(298.46,161.28) --
+	(298.07,161.14) --
+	(297.92,161.07) --
+	(297.39,160.94) --
+	(297.32,160.90) --
+	(297.20,160.85) --
+	(297.04,160.83) --
+	(296.23,160.63) --
+	(295.80,160.53) --
+	(295.54,160.46) --
+	(295.44,160.41) --
+	(295.14,160.30) --
+	(294.98,160.22) --
+	(294.89,160.18) --
+	(294.72,160.12) --
+	(294.33,159.97) --
+	(294.05,159.87) --
+	(293.68,159.78) --
+	(292.90,159.50) --
+	(292.66,159.42) --
+	(292.03,159.17) --
+	(291.68,159.07) --
+	(291.46,158.95) --
+	(290.92,158.76) --
+	(290.88,158.74) --
+	(290.85,158.72) --
+	(290.85,158.72) --
+	(290.84,158.72) --
+	(290.79,158.69) --
+	(290.52,158.56) --
+	(290.49,158.55) --
+	(290.32,158.46) --
+	(289.89,158.32) --
+	(289.83,158.30) --
+	(289.45,158.18) --
+	(289.39,158.16) --
+	(289.22,158.11) --
+	(287.78,157.56) --
+	(287.70,157.54) --
+	(287.36,157.49) --
+	(286.86,157.37) --
+	(286.83,157.36) --
+	(286.73,157.33) --
+	(286.71,157.31) --
+	(286.65,157.28) --
+	(286.60,157.25) --
+	(286.46,157.17) --
+	(286.16,157.04) --
+	(286.10,157.03) --
+	(285.65,156.93) --
+	(285.32,156.82) --
+	(285.29,156.80) --
+	(285.23,156.77) --
+	(285.14,156.75) --
+	(283.74,156.26) --
+	(283.65,156.23) --
+	(283.17,156.09) --
+	(283.13,156.08) --
+	(282.56,155.90) --
+	(282.46,155.87) --
+	(281.96,155.72) --
+	(281.36,155.53) --
+	(281.34,155.52) --
+	(280.82,155.34) --
+	(280.03,155.03) --
+	(279.84,154.97) --
+	(279.57,154.88) --
+	(279.48,154.85) --
+	(278.99,154.69) --
+	(278.91,154.66) --
+	(278.14,154.34) --
+	(276.61,153.82) --
+	(276.46,153.75) --
+	(276.19,153.66) --
+	(276.03,153.58) --
+	(275.85,153.49) --
+	(275.51,153.32) --
+	(275.27,153.24) --
+	(275.09,153.18) --
+	(274.93,153.13) --
+	(274.74,153.07) --
+	(274.62,153.01) --
+	(274.54,152.96) --
+	(273.54,152.47) --
+	(273.54,152.47) --
+	(272.44,152.06) --
+	(272.38,152.04) --
+	(272.02,151.89) --
+	(271.89,151.85) --
+	(271.86,151.85) --
+	(271.37,151.64) --
+	(271.09,151.55) --
+	(270.46,151.24) --
+	(269.59,150.90) --
+	(268.47,150.47) --
+	(267.29,149.94) --
+	(267.22,149.89) --
+	(266.18,149.49) --
+	(264.22,148.70) --
+	(263.06,148.21) --
+	(261.73,147.75) --
+	(261.30,147.63) --
+	(261.11,147.56) --
+	(259.93,147.06) --
+	(259.46,146.86) --
+	(258.24,146.37) --
+	(257.94,146.22) --
+	(257.79,146.15) --
+	(257.34,145.93) --
+	(255.95,145.29) --
+	(252.59,143.92) --
+	(249.60,142.66) --
+	(249.23,142.52) --
+	(248.78,142.28) --
+	(248.05,141.96) --
+	(247.36,141.73) --
+	(247.34,141.72) --
+	(245.55,140.68) --
+	(245.54,140.67) --
+	(244.41,140.23) --
+	(243.48,139.81) --
+	(242.52,139.40) --
+	(241.66,139.00) --
+	(240.75,138.64) --
+	(239.75,138.24) --
+	(239.57,138.16) --
+	(237.64,137.39) --
+	(232.73,135.16) --
+	(232.34,134.96) --
+	(232.29,134.94) --
+	(232.05,134.85) --
+	(231.37,134.57) --
+	(230.46,134.14) --
+	(229.80,133.84) --
+	(229.22,133.54) --
+	(229.07,133.47) --
+	(227.16,132.57) --
+	(226.69,132.33) --
+	(226.45,132.19) --
+	(226.35,132.15) --
+	(224.96,131.49) --
+	(220.78,129.59) --
+	(219.02,128.61) --
+	(214.75,126.43) --
+	(214.56,126.34) --
+	(209.67,123.91) --
+	(207.92,122.94) --
+	(206.30,122.24) --
+	(205.69,121.90) --
+	(205.60,121.85) --
+	(202.82,120.36) --
+	(198.25,118.05) --
+	(189.23,113.19) --
+	(182.48,109.70) --
+	(169.66,102.54) --
+	(166.44,100.78) --
+	(153.74, 94.08) --
+	(124.61, 77.55) --
+	(116.04, 72.56) --
+	(109.99, 69.23) --
+	(106.88, 67.49) --
+	(101.51, 64.29) --
+	( 93.47, 59.68) --
+	( 80.74, 52.08) --
+	( 80.61, 52.00) --
+	( 76.56, 49.55) --
+	( 69.26, 45.08) --
 	cycle;
@@
 
-\path[fill=fillColor,fill opacity=0.50] ( 57.05,159.56) --
-	( 61.80,160.25) --
-	( 66.56,160.98) --
-	( 71.31,161.86) --
-	( 76.07,162.52) --
-	( 80.82,163.37) --
-	( 85.58,164.21) --
-	( 90.34,164.90) --
-	( 95.09,165.74) --
-	( 99.85,166.75) --
-	(104.60,167.59) --
-	(109.36,168.46) --
-	(114.11,169.19) --
-	(118.87,170.16) --
-	(123.63,170.99) --
-	(128.38,171.84) --
-	(133.14,172.69) --
-	(137.89,173.59) --
-	(142.65,174.41) --
-	(147.40,175.17) --
-	(152.16,176.19) --
-	(156.92,177.17) --
-	(161.67,178.09) --
-	(166.43,178.94) --
-	(171.18,179.97) --
-	(175.94,180.98) --
-	(180.70,181.99) --
-	(185.45,182.96) --
-	(190.21,183.82) --
-	(194.96,184.88) --
-	(199.72,185.88) --
-	(204.47,186.83) --
-	(209.23,187.76) --
-	(213.99,188.99) --
-	(218.74,190.13) --
-	(223.50,191.26) --
-	(228.25,192.31) --
-	(233.01,193.53) --
-	(237.76,194.62) --
-	(242.52,195.84) --
-	(247.28,197.18) --
-	(252.03,198.48) --
-	(256.79,199.68) --
-	(261.54,201.07) --
-	(266.30,202.56) --
-	(271.05,204.06) --
-	(275.81,205.62) --
-	(280.57,207.24) --
-	(285.32,209.00) --
-	(290.08,210.51) --
-	(294.83,212.14) --
-	(299.59,213.87) --
-	(304.35,215.72) --
-	(309.10,217.52) --
-	(313.86,219.34) --
-	(318.61,221.26) --
-	(323.37,223.16) --
-	(328.12,225.10) --
-	(332.88,227.06) --
-	(337.64,228.96) --
-	(342.39,231.01) --
-	(347.15,233.07) --
-	(351.90,235.12) --
-	(356.66,237.31) --
-	(361.41,239.43) --
-	(366.17,241.62) --
-	(370.93,243.83) --
-	(375.68,246.04) --
-	(380.44,248.34) --
-	(385.19,250.61) --
-	(389.95,252.92) --
-	(394.70,255.34) --
-	(399.46,257.65) --
-	(404.22,260.08) --
-	(404.22,196.18) --
-	(399.46,195.16) --
-	(394.70,194.11) --
-	(389.95,193.22) --
-	(385.19,192.29) --
-	(380.44,191.22) --
-	(375.68,190.29) --
-	(370.93,189.27) --
-	(366.17,188.31) --
-	(361.41,187.21) --
-	(356.66,185.94) --
-	(351.90,184.86) --
-	(347.15,183.77) --
-	(342.39,182.69) --
-	(337.64,181.59) --
-	(332.88,180.34) --
-	(328.12,179.09) --
-	(323.37,177.75) --
-	(318.61,176.29) --
-	(313.86,174.79) --
-	(309.10,173.33) --
-	(304.35,171.86) --
-	(299.59,170.35) --
-	(294.83,168.77) --
-	(290.08,167.23) --
-	(285.32,165.59) --
-	(280.57,163.88) --
-	(275.81,162.14) --
-	(271.05,160.29) --
-	(266.30,158.47) --
-	(261.54,156.48) --
-	(256.79,154.63) --
-	(252.03,152.76) --
-	(247.28,150.64) --
-	(242.52,148.69) --
-	(237.76,146.57) --
-	(233.01,144.54) --
-	(228.25,142.40) --
-	(223.50,140.17) --
-	(218.74,137.98) --
-	(213.99,135.99) --
-	(209.23,133.82) --
-	(204.47,131.54) --
-	(199.72,129.37) --
-	(194.96,127.03) --
-	(190.21,124.77) --
-	(185.45,122.49) --
-	(180.70,120.16) --
-	(175.94,117.80) --
-	(171.18,115.40) --
-	(166.43,113.13) --
-	(161.67,110.68) --
-	(156.92,108.42) --
-	(152.16,105.89) --
-	(147.40,103.39) --
-	(142.65,100.83) --
-	(137.89, 98.32) --
-	(133.14, 95.77) --
-	(128.38, 93.33) --
-	(123.63, 90.81) --
-	(118.87, 88.34) --
-	(114.11, 85.90) --
-	(109.36, 83.33) --
-	(104.60, 80.84) --
-	( 99.85, 78.40) --
-	( 95.09, 75.83) --
-	( 90.34, 73.27) --
-	( 85.58, 70.75) --
-	( 80.82, 68.24) --
-	( 76.07, 65.78) --
-	( 71.31, 63.28) --
-	( 66.56, 60.67) --
-	( 61.80, 58.16) --
-	( 57.05, 55.65) --
+\path[fill=fillColor,fill opacity=0.50] ( 69.26,158.06) --
+	( 76.56,159.37) --
+	( 80.61,160.10) --
+	( 80.74,160.12) --
+	( 93.47,161.99) --
+	(101.51,163.36) --
+	(106.88,164.36) --
+	(109.99,164.97) --
+	(116.04,165.98) --
+	(124.61,167.56) --
+	(153.74,173.30) --
+	(166.44,175.73) --
+	(169.66,176.32) --
+	(182.48,179.03) --
+	(189.23,180.36) --
+	(198.25,182.33) --
+	(202.82,183.39) --
+	(205.60,184.05) --
+	(205.69,184.08) --
+	(206.30,184.21) --
+	(207.92,184.53) --
+	(209.67,184.97) --
+	(214.56,186.05) --
+	(214.75,186.10) --
+	(219.02,187.06) --
+	(220.78,187.55) --
+	(224.96,188.64) --
+	(226.35,188.99) --
+	(226.45,189.01) --
+	(226.69,189.04) --
+	(227.16,189.17) --
+	(229.07,189.76) --
+	(229.22,189.83) --
+	(229.80,189.97) --
+	(230.46,190.13) --
+	(231.37,190.40) --
+	(232.05,190.62) --
+	(232.29,190.67) --
+	(232.34,190.69) --
+	(232.73,190.81) --
+	(237.64,192.19) --
+	(239.57,192.68) --
+	(239.75,192.72) --
+	(240.75,192.97) --
+	(241.66,193.18) --
+	(242.52,193.45) --
+	(243.48,193.69) --
+	(244.41,194.00) --
+	(245.54,194.36) --
+	(245.55,194.36) --
+	(247.34,194.92) --
+	(247.36,194.92) --
+	(248.05,195.09) --
+	(248.78,195.28) --
+	(249.23,195.39) --
+	(249.60,195.46) --
+	(252.59,196.28) --
+	(255.95,197.25) --
+	(257.34,197.64) --
+	(257.79,197.74) --
+	(257.94,197.77) --
+	(258.24,197.86) --
+	(259.46,198.20) --
+	(259.93,198.33) --
+	(261.11,198.71) --
+	(261.30,198.77) --
+	(261.73,198.92) --
+	(263.06,199.31) --
+	(264.22,199.66) --
+	(266.18,200.26) --
+	(267.22,200.59) --
+	(267.29,200.62) --
+	(268.47,201.00) --
+	(269.59,201.32) --
+	(270.46,201.65) --
+	(271.09,201.82) --
+	(271.37,201.90) --
+	(271.86,202.05) --
+	(271.89,202.06) --
+	(272.02,202.07) --
+	(272.38,202.18) --
+	(272.44,202.20) --
+	(273.54,202.60) --
+	(273.54,202.61) --
+	(274.54,202.96) --
+	(274.62,202.98) --
+	(274.74,203.01) --
+	(274.93,203.06) --
+	(275.09,203.12) --
+	(275.27,203.18) --
+	(275.51,203.24) --
+	(275.85,203.34) --
+	(276.03,203.40) --
+	(276.19,203.45) --
+	(276.46,203.57) --
+	(276.61,203.62) --
+	(278.14,204.15) --
+	(278.91,204.42) --
+	(278.99,204.45) --
+	(279.48,204.60) --
+	(279.57,204.61) --
+	(279.84,204.69) --
+	(280.03,204.74) --
+	(280.82,204.98) --
+	(281.34,205.16) --
+	(281.36,205.17) --
+	(281.96,205.44) --
+	(282.46,205.62) --
+	(282.56,205.65) --
+	(283.13,205.83) --
+	(283.17,205.85) --
+	(283.65,206.01) --
+	(283.74,206.04) --
+	(285.14,206.56) --
+	(285.23,206.60) --
+	(285.29,206.62) --
+	(285.32,206.63) --
+	(285.65,206.72) --
+	(286.10,206.84) --
+	(286.16,206.85) --
+	(286.46,206.97) --
+	(286.60,207.03) --
+	(286.65,207.05) --
+	(286.71,207.07) --
+	(286.73,207.08) --
+	(286.83,207.11) --
+	(286.86,207.13) --
+	(287.36,207.33) --
+	(287.70,207.49) --
+	(287.78,207.52) --
+	(289.22,208.10) --
+	(289.39,208.18) --
+	(289.45,208.21) --
+	(289.83,208.33) --
+	(289.89,208.36) --
+	(290.32,208.55) --
+	(290.49,208.59) --
+	(290.52,208.60) --
+	(290.79,208.71) --
+	(290.84,208.71) --
+	(290.85,208.71) --
+	(290.85,208.72) --
+	(290.88,208.73) --
+	(290.92,208.74) --
+	(291.46,208.93) --
+	(291.68,209.00) --
+	(292.03,209.14) --
+	(292.66,209.32) --
+	(292.90,209.42) --
+	(293.68,209.75) --
+	(294.05,209.81) --
+	(294.33,209.92) --
+	(294.72,210.07) --
+	(294.89,210.14) --
+	(294.98,210.18) --
+	(295.14,210.26) --
+	(295.44,210.36) --
+	(295.54,210.39) --
+	(295.80,210.51) --
+	(296.23,210.69) --
+	(297.04,210.99) --
+	(297.20,211.06) --
+	(297.32,211.11) --
+	(297.39,211.13) --
+	(297.92,211.35) --
+	(298.07,211.41) --
+	(298.46,211.58) --
+	(298.47,211.58) --
+	(298.54,211.61) --
+	(298.62,211.64) --
+	(299.15,211.84) --
+	(299.26,211.88) --
+	(299.54,211.99) --
+	(299.58,212.00) --
+	(300.71,212.49) --
+	(301.41,212.70) --
+	(302.13,213.03) --
+	(302.61,213.21) --
+	(303.45,213.49) --
+	(303.55,213.52) --
+	(303.59,213.53) --
+	(303.66,213.55) --
+	(303.89,213.61) --
+	(303.92,213.61) --
+	(304.13,213.70) --
+	(304.31,213.78) --
+	(304.32,213.78) --
+	(304.63,213.91) --
+	(305.44,214.22) --
+	(306.03,214.40) --
+	(306.65,214.65) --
+	(307.10,214.83) --
+	(307.15,214.85) --
+	(307.34,214.92) --
+	(307.36,214.92) --
+	(307.48,214.98) --
+	(307.57,215.01) --
+	(307.71,215.07) --
+	(307.78,215.10) --
+	(307.86,215.13) --
+	(308.14,215.24) --
+	(308.17,215.26) --
+	(308.40,215.36) --
+	(309.29,215.75) --
+	(309.65,215.90) --
+	(309.66,215.90) --
+	(309.77,215.94) --
+	(309.85,215.96) --
+	(310.26,216.13) --
+	(310.42,216.19) --
+	(310.88,216.36) --
+	(310.97,216.39) --
+	(311.25,216.48) --
+	(312.09,216.80) --
+	(312.22,216.84) --
+	(312.41,216.92) --
+	(313.42,217.35) --
+	(313.62,217.46) --
+	(313.78,217.52) --
+	(314.05,217.62) --
+	(314.50,217.82) --
+	(314.58,217.86) --
+	(314.67,217.90) --
+	(315.27,218.11) --
+	(315.36,218.13) --
+	(315.70,218.31) --
+	(315.87,218.39) --
+	(315.98,218.43) --
+	(316.35,218.58) --
+	(316.56,218.68) --
+	(316.72,218.76) --
+	(317.21,218.94) --
+	(317.49,219.07) --
+	(317.56,219.10) --
+	(318.84,219.67) --
+	(318.87,219.68) --
+	(319.28,219.82) --
+	(319.56,219.91) --
+	(319.75,219.99) --
+	(319.97,220.10) --
+	(320.23,220.22) --
+	(320.29,220.24) --
+	(320.33,220.26) --
+	(320.94,220.45) --
+	(321.01,220.47) --
+	(321.22,220.57) --
+	(321.25,220.59) --
+	(321.36,220.64) --
+	(321.75,220.84) --
+	(323.15,221.38) --
+	(323.66,221.56) --
+	(325.17,222.18) --
+	(325.77,222.40) --
+	(325.89,222.48) --
+	(326.94,222.97) --
+	(327.01,223.01) --
+	(327.29,223.13) --
+	(328.29,223.54) --
+	(328.36,223.57) --
+	(328.82,223.76) --
+	(329.10,223.87) --
+	(329.71,224.11) --
+	(330.08,224.27) --
+	(330.10,224.28) --
+	(330.14,224.30) --
+	(330.37,224.41) --
+	(330.66,224.51) --
+	(331.19,224.72) --
+	(331.66,224.93) --
+	(331.92,225.05) --
+	(332.49,225.26) --
+	(333.01,225.49) --
+	(334.21,226.03) --
+	(334.41,226.11) --
+	(334.89,226.30) --
+	(337.42,227.37) --
+	(337.45,227.38) --
+	(337.58,227.44) --
+	(337.70,227.50) --
+	(337.71,227.50) --
+	(337.80,227.54) --
+	(339.18,228.14) --
+	(339.28,228.20) --
+	(341.35,229.04) --
+	(341.75,229.22) --
+	(342.17,229.38) --
+	(342.48,229.55) --
+	(342.53,229.57) --
+	(342.69,229.66) --
+	(342.85,229.73) --
+	(343.03,229.82) --
+	(343.17,229.89) --
+	(343.37,229.97) --
+	(343.45,230.02) --
+	(343.75,230.20) --
+	(343.88,230.27) --
+	(344.23,230.45) --
+	(345.06,230.84) --
+	(346.03,231.26) --
+	(346.49,231.43) --
+	(347.23,231.80) --
+	(347.38,231.88) --
+	(348.49,232.39) --
+	(348.58,232.43) --
+	(349.13,232.71) --
+	(349.81,233.08) --
+	(350.10,233.20) --
+	(350.24,233.26) --
+	(350.58,233.40) --
+	(351.85,233.92) --
+	(352.05,233.99) --
+	(352.77,234.32) --
+	(353.17,234.51) --
+	(353.42,234.63) --
+	(353.71,234.76) --
+	(354.71,235.15) --
+	(355.56,235.61) --
+	(357.56,236.47) --
+	(357.72,236.54) --
+	(357.97,236.65) --
+	(358.00,236.66) --
+	(358.30,236.82) --
+	(358.37,236.86) --
+	(358.57,236.95) --
+	(358.60,236.97) --
+	(358.96,237.17) --
+	(358.97,237.18) --
+	(359.44,237.44) --
+	(359.71,237.56) --
+	(359.84,237.62) --
+	(359.89,237.63) --
+	(359.95,237.66) --
+	(360.12,237.73) --
+	(360.50,237.88) --
+	(360.53,237.89) --
+	(361.15,238.15) --
+	(361.24,238.18) --
+	(361.57,238.32) --
+	(362.32,238.66) --
+	(362.86,238.92) --
+	(362.88,238.93) --
+	(362.99,238.99) --
+	(363.37,239.16) --
+	(365.15,240.02) --
+	(365.51,240.19) --
+	(365.58,240.23) --
+	(365.58,240.23) --
+	(366.24,240.61) --
+	(366.27,240.63) --
+	(366.79,240.88) --
+	(367.09,241.02) --
+	(367.28,241.13) --
+	(367.50,241.25) --
+	(367.74,241.35) --
+	(368.30,241.57) --
+	(368.30,241.57) --
+	(368.38,241.60) --
+	(368.49,241.65) --
+	(368.90,241.82) --
+	(369.46,242.09) --
+	(370.56,242.57) --
+	(370.74,242.67) --
+	(370.85,242.73) --
+	(372.47,243.56) --
+	(373.39,244.01) --
+	(373.79,244.21) --
+	(374.21,244.42) --
+	(375.70,245.15) --
+	(378.93,246.76) --
+	(380.42,247.53) --
+	(385.52,250.10) --
+	(386.08,250.38) --
+	(386.54,250.63) --
+	(386.90,250.79) --
+	(387.31,251.04) --
+	(387.53,251.17) --
+	(388.24,251.54) --
+	(388.35,251.60) --
+	(388.69,251.73) --
+	(388.71,251.74) --
+	(388.75,251.76) --
+	(388.90,251.84) --
+	(389.17,252.00) --
+	(389.73,252.28) --
+	(390.59,252.69) --
+	(391.22,253.03) --
+	(391.77,253.31) --
+	(391.82,253.33) --
+	(392.15,253.48) --
+	(392.41,253.61) --
+	(396.33,255.53) --
+	(397.13,255.92) --
+	(397.28,256.01) --
+	(404.32,259.58) --
+	(404.80,259.80) --
+	(404.80,193.63) --
+	(404.32,193.52) --
+	(397.28,192.09) --
+	(397.13,192.06) --
+	(396.33,191.92) --
+	(392.41,191.02) --
+	(392.15,190.97) --
+	(391.82,190.88) --
+	(391.77,190.87) --
+	(391.22,190.75) --
+	(390.59,190.60) --
+	(389.73,190.40) --
+	(389.17,190.27) --
+	(388.90,190.21) --
+	(388.75,190.18) --
+	(388.71,190.18) --
+	(388.69,190.17) --
+	(388.35,190.08) --
+	(388.24,190.06) --
+	(387.53,189.90) --
+	(387.31,189.87) --
+	(386.90,189.79) --
+	(386.54,189.71) --
+	(386.08,189.64) --
+	(385.52,189.44) --
+	(380.42,188.27) --
+	(378.93,187.91) --
+	(375.70,187.16) --
+	(374.21,186.81) --
+	(373.79,186.72) --
+	(373.39,186.63) --
+	(372.47,186.48) --
+	(370.85,186.09) --
+	(370.74,186.05) --
+	(370.56,185.99) --
+	(369.46,185.78) --
+	(368.90,185.66) --
+	(368.49,185.60) --
+	(368.38,185.57) --
+	(368.30,185.54) --
+	(368.30,185.54) --
+	(367.74,185.37) --
+	(367.50,185.30) --
+	(367.28,185.23) --
+	(367.09,185.20) --
+	(366.79,185.18) --
+	(366.27,185.04) --
+	(366.24,185.04) --
+	(365.58,184.87) --
+	(365.58,184.87) --
+	(365.51,184.85) --
+	(365.15,184.74) --
+	(363.37,184.26) --
+	(362.99,184.16) --
+	(362.88,184.14) --
+	(362.86,184.13) --
+	(362.32,183.99) --
+	(361.57,183.78) --
+	(361.24,183.69) --
+	(361.15,183.67) --
+	(360.53,183.58) --
+	(360.50,183.57) --
+	(360.12,183.47) --
+	(359.95,183.42) --
+	(359.89,183.40) --
+	(359.84,183.40) --
+	(359.71,183.37) --
+	(359.44,183.28) --
+	(358.97,183.13) --
+	(358.96,183.12) --
+	(358.60,182.99) --
+	(358.57,182.99) --
+	(358.37,182.96) --
+	(358.30,182.95) --
+	(358.00,182.90) --
+	(357.97,182.90) --
+	(357.72,182.84) --
+	(357.56,182.81) --
+	(355.56,182.34) --
+	(354.71,182.07) --
+	(353.71,181.78) --
+	(353.42,181.68) --
+	(353.17,181.60) --
+	(352.77,181.50) --
+	(352.05,181.35) --
+	(351.85,181.33) --
+	(350.58,181.06) --
+	(350.24,181.00) --
+	(350.10,180.98) --
+	(349.81,180.92) --
+	(349.13,180.77) --
+	(348.58,180.62) --
+	(348.49,180.60) --
+	(347.38,180.24) --
+	(347.23,180.21) --
+	(346.49,179.99) --
+	(346.03,179.86) --
+	(345.06,179.60) --
+	(344.23,179.40) --
+	(343.88,179.29) --
+	(343.75,179.26) --
+	(343.45,179.17) --
+	(343.37,179.16) --
+	(343.17,179.09) --
+	(343.03,179.05) --
+	(342.85,179.02) --
+	(342.69,178.99) --
+	(342.53,178.94) --
+	(342.48,178.93) --
+	(342.17,178.85) --
+	(341.75,178.74) --
+	(341.35,178.63) --
+	(339.28,178.08) --
+	(339.18,178.06) --
+	(337.80,177.70) --
+	(337.71,177.67) --
+	(337.70,177.67) --
+	(337.58,177.64) --
+	(337.45,177.61) --
+	(337.42,177.61) --
+	(334.89,176.97) --
+	(334.41,176.82) --
+	(334.21,176.78) --
+	(333.01,176.45) --
+	(332.49,176.29) --
+	(331.92,176.16) --
+	(331.66,176.11) --
+	(331.19,175.98) --
+	(330.66,175.82) --
+	(330.37,175.74) --
+	(330.14,175.66) --
+	(330.10,175.65) --
+	(330.08,175.64) --
+	(329.71,175.56) --
+	(329.10,175.37) --
+	(328.82,175.26) --
+	(328.36,175.14) --
+	(328.29,175.12) --
+	(327.29,174.83) --
+	(327.01,174.77) --
+	(326.94,174.76) --
+	(325.89,174.48) --
+	(325.77,174.45) --
+	(325.17,174.31) --
+	(323.66,173.93) --
+	(323.15,173.78) --
+	(321.75,173.36) --
+	(321.36,173.20) --
+	(321.25,173.15) --
+	(321.22,173.15) --
+	(321.01,173.11) --
+	(320.94,173.10) --
+	(320.33,172.92) --
+	(320.29,172.91) --
+	(320.23,172.88) --
+	(319.97,172.81) --
+	(319.75,172.74) --
+	(319.56,172.67) --
+	(319.28,172.58) --
+	(318.87,172.45) --
+	(318.84,172.44) --
+	(317.56,172.09) --
+	(317.49,172.08) --
+	(317.21,172.00) --
+	(316.72,171.83) --
+	(316.56,171.77) --
+	(316.35,171.69) --
+	(315.98,171.61) --
+	(315.87,171.59) --
+	(315.70,171.54) --
+	(315.36,171.47) --
+	(315.27,171.46) --
+	(314.67,171.26) --
+	(314.58,171.24) --
+	(314.50,171.22) --
+	(314.05,171.12) --
+	(313.78,171.03) --
+	(313.62,170.98) --
+	(313.42,170.90) --
+	(312.41,170.53) --
+	(312.22,170.46) --
+	(312.09,170.42) --
+	(311.25,170.19) --
+	(310.97,170.09) --
+	(310.88,170.07) --
+	(310.42,169.91) --
+	(310.26,169.87) --
+	(309.85,169.77) --
+	(309.77,169.74) --
+	(309.66,169.71) --
+	(309.65,169.71) --
+	(309.29,169.57) --
+	(308.40,169.24) --
+	(308.17,169.17) --
+	(308.14,169.15) --
+	(307.86,169.07) --
+	(307.78,169.05) --
+	(307.71,169.02) --
+	(307.57,168.96) --
+	(307.48,168.94) --
+	(307.36,168.90) --
+	(307.34,168.89) --
+	(307.15,168.83) --
+	(307.10,168.82) --
+	(306.65,168.65) --
+	(306.03,168.41) --
+	(305.44,168.24) --
+	(304.63,167.94) --
+	(304.32,167.86) --
+	(304.31,167.86) --
+	(304.13,167.83) --
+	(303.92,167.75) --
+	(303.89,167.74) --
+	(303.66,167.64) --
+	(303.59,167.61) --
+	(303.55,167.59) --
+	(303.45,167.57) --
+	(302.61,167.26) --
+	(302.13,167.11) --
+	(301.41,166.77) --
+	(300.71,166.59) --
+	(299.58,166.27) --
+	(299.54,166.26) --
+	(299.26,166.14) --
+	(299.15,166.11) --
+	(298.62,165.91) --
+	(298.54,165.90) --
+	(298.47,165.90) --
+	(298.46,165.89) --
+	(298.07,165.78) --
+	(297.92,165.74) --
+	(297.39,165.53) --
+	(297.32,165.52) --
+	(297.20,165.47) --
+	(297.04,165.42) --
+	(296.23,165.17) --
+	(295.80,165.04) --
+	(295.54,164.95) --
+	(295.44,164.92) --
+	(295.14,164.82) --
+	(294.98,164.77) --
+	(294.89,164.75) --
+	(294.72,164.69) --
+	(294.33,164.51) --
+	(294.05,164.40) --
+	(293.68,164.30) --
+	(292.90,164.04) --
+	(292.66,163.95) --
+	(292.03,163.71) --
+	(291.68,163.61) --
+	(291.46,163.54) --
+	(290.92,163.33) --
+	(290.88,163.31) --
+	(290.85,163.29) --
+	(290.85,163.29) --
+	(290.84,163.29) --
+	(290.79,163.29) --
+	(290.52,163.19) --
+	(290.49,163.17) --
+	(290.32,163.10) --
+	(289.89,162.93) --
+	(289.83,162.92) --
+	(289.45,162.82) --
+	(289.39,162.80) --
+	(289.22,162.75) --
+	(287.78,162.30) --
+	(287.70,162.28) --
+	(287.36,162.17) --
+	(286.86,161.98) --
+	(286.83,161.97) --
+	(286.73,161.93) --
+	(286.71,161.92) --
+	(286.65,161.89) --
+	(286.60,161.87) --
+	(286.46,161.80) --
+	(286.16,161.68) --
+	(286.10,161.65) --
+	(285.65,161.51) --
+	(285.32,161.41) --
+	(285.29,161.40) --
+	(285.23,161.39) --
+	(285.14,161.35) --
+	(283.74,160.86) --
+	(283.65,160.83) --
+	(283.17,160.65) --
+	(283.13,160.63) --
+	(282.56,160.45) --
+	(282.46,160.44) --
+	(281.96,160.22) --
+	(281.36,159.99) --
+	(281.34,159.98) --
+	(280.82,159.75) --
+	(280.03,159.42) --
+	(279.84,159.35) --
+	(279.57,159.24) --
+	(279.48,159.20) --
+	(278.99,158.99) --
+	(278.91,158.96) --
+	(278.14,158.66) --
+	(276.61,158.07) --
+	(276.46,158.02) --
+	(276.19,157.93) --
+	(276.03,157.90) --
+	(275.85,157.83) --
+	(275.51,157.70) --
+	(275.27,157.60) --
+	(275.09,157.55) --
+	(274.93,157.51) --
+	(274.74,157.44) --
+	(274.62,157.39) --
+	(274.54,157.35) --
+	(273.54,156.94) --
+	(273.54,156.94) --
+	(272.44,156.53) --
+	(272.38,156.51) --
+	(272.02,156.41) --
+	(271.89,156.36) --
+	(271.86,156.35) --
+	(271.37,156.14) --
+	(271.09,156.07) --
+	(270.46,155.83) --
+	(269.59,155.51) --
+	(268.47,155.04) --
+	(267.29,154.56) --
+	(267.22,154.54) --
+	(266.18,154.10) --
+	(264.22,153.32) --
+	(263.06,152.86) --
+	(261.73,152.31) --
+	(261.30,152.12) --
+	(261.11,152.03) --
+	(259.93,151.57) --
+	(259.46,151.36) --
+	(258.24,150.94) --
+	(257.94,150.85) --
+	(257.79,150.79) --
+	(257.34,150.60) --
+	(255.95,150.01) --
+	(252.59,148.62) --
+	(249.60,147.41) --
+	(249.23,147.23) --
+	(248.78,147.03) --
+	(248.05,146.76) --
+	(247.36,146.49) --
+	(247.34,146.48) --
+	(245.55,145.70) --
+	(245.54,145.69) --
+	(244.41,145.19) --
+	(243.48,144.81) --
+	(242.52,144.42) --
+	(241.66,144.05) --
+	(240.75,143.64) --
+	(239.75,143.12) --
+	(239.57,143.07) --
+	(237.64,142.25) --
+	(232.73,140.08) --
+	(232.34,139.90) --
+	(232.29,139.87) --
+	(232.05,139.75) --
+	(231.37,139.44) --
+	(230.46,139.01) --
+	(229.80,138.72) --
+	(229.22,138.43) --
+	(229.07,138.33) --
+	(227.16,137.42) --
+	(226.69,137.17) --
+	(226.45,137.06) --
+	(226.35,137.03) --
+	(224.96,136.50) --
+	(220.78,134.55) --
+	(219.02,133.70) --
+	(214.75,131.69) --
+	(214.56,131.61) --
+	(209.67,129.15) --
+	(207.92,128.41) --
+	(206.30,127.62) --
+	(205.69,127.37) --
+	(205.60,127.33) --
+	(202.82,125.94) --
+	(198.25,123.69) --
+	(189.23,119.35) --
+	(182.48,116.07) --
+	(169.66,109.49) --
+	(166.44,107.79) --
+	(153.74,101.09) --
+	(124.61, 85.71) --
+	(116.04, 81.15) --
+	(109.99, 77.69) --
+	(106.88, 75.97) --
+	(101.51, 73.00) --
+	( 93.47, 68.72) --
+	( 80.74, 61.97) --
+	( 80.61, 61.89) --
+	( 76.56, 59.73) --
+	( 69.26, 55.71) --
 	cycle;
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 69.26, 34.03) -- ( 69.26, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 76.56, 34.03) -- ( 76.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 80.61, 34.03) -- ( 80.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 80.74, 34.03) -- ( 80.74, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 93.47, 34.03) -- ( 93.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (101.51, 34.03) -- (101.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (106.88, 34.03) -- (106.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (109.99, 34.03) -- (109.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (116.04, 34.03) -- (116.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (124.61, 34.03) -- (124.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (153.74, 34.03) -- (153.74, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (166.44, 34.03) -- (166.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (169.66, 34.03) -- (169.66, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (182.48, 34.03) -- (182.48, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (189.23, 34.03) -- (189.23, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (198.25, 34.03) -- (198.25, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (202.82, 34.03) -- (202.82, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (205.60, 34.03) -- (205.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (205.69, 34.03) -- (205.69, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (206.30, 34.03) -- (206.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (207.92, 34.03) -- (207.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (209.67, 34.03) -- (209.67, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (214.56, 34.03) -- (214.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (214.75, 34.03) -- (214.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (219.02, 34.03) -- (219.02, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (220.78, 34.03) -- (220.78, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (224.96, 34.03) -- (224.96, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (226.35, 34.03) -- (226.35, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (226.45, 34.03) -- (226.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (226.69, 34.03) -- (226.69, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (227.16, 34.03) -- (227.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (229.07, 34.03) -- (229.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (229.22, 34.03) -- (229.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (229.80, 34.03) -- (229.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (230.46, 34.03) -- (230.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (231.37, 34.03) -- (231.37, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.05, 34.03) -- (232.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.29, 34.03) -- (232.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.34, 34.03) -- (232.34, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.73, 34.03) -- (232.73, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (237.64, 34.03) -- (237.64, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (239.57, 34.03) -- (239.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (239.75, 34.03) -- (239.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (240.75, 34.03) -- (240.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (241.66, 34.03) -- (241.66, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (242.52, 34.03) -- (242.52, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (243.48, 34.03) -- (243.48, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (244.41, 34.03) -- (244.41, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (245.54, 34.03) -- (245.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (245.55, 34.03) -- (245.55, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (247.34, 34.03) -- (247.34, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (247.36, 34.03) -- (247.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (248.05, 34.03) -- (248.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (248.78, 34.03) -- (248.78, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (249.23, 34.03) -- (249.23, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (249.60, 34.03) -- (249.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (252.59, 34.03) -- (252.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (255.95, 34.03) -- (255.95, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (257.34, 34.03) -- (257.34, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (257.79, 34.03) -- (257.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (257.94, 34.03) -- (257.94, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (258.24, 34.03) -- (258.24, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (259.46, 34.03) -- (259.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (259.93, 34.03) -- (259.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (261.11, 34.03) -- (261.11, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (261.30, 34.03) -- (261.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (261.73, 34.03) -- (261.73, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (263.06, 34.03) -- (263.06, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (264.22, 34.03) -- (264.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (266.18, 34.03) -- (266.18, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.22, 34.03) -- (267.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.29, 34.03) -- (267.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (268.47, 34.03) -- (268.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (269.59, 34.03) -- (269.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (270.46, 34.03) -- (270.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.09, 34.03) -- (271.09, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.37, 34.03) -- (271.37, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.86, 34.03) -- (271.86, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.89, 34.03) -- (271.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (272.02, 34.03) -- (272.02, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (272.38, 34.03) -- (272.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (272.44, 34.03) -- (272.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (273.54, 34.03) -- (273.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (273.54, 34.03) -- (273.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (274.54, 34.03) -- (274.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (274.62, 34.03) -- (274.62, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (274.74, 34.03) -- (274.74, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (274.93, 34.03) -- (274.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (275.09, 34.03) -- (275.09, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (275.27, 34.03) -- (275.27, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (275.51, 34.03) -- (275.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (275.85, 34.03) -- (275.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (276.03, 34.03) -- (276.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (276.19, 34.03) -- (276.19, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (276.46, 34.03) -- (276.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (276.61, 34.03) -- (276.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (278.14, 34.03) -- (278.14, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (278.91, 34.03) -- (278.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (278.99, 34.03) -- (278.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (279.48, 34.03) -- (279.48, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (279.57, 34.03) -- (279.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (279.84, 34.03) -- (279.84, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (280.03, 34.03) -- (280.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (280.82, 34.03) -- (280.82, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (281.34, 34.03) -- (281.34, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (281.36, 34.03) -- (281.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (281.96, 34.03) -- (281.96, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (282.46, 34.03) -- (282.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (282.56, 34.03) -- (282.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.13, 34.03) -- (283.13, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.17, 34.03) -- (283.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.65, 34.03) -- (283.65, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.74, 34.03) -- (283.74, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.14, 34.03) -- (285.14, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.23, 34.03) -- (285.23, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.29, 34.03) -- (285.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.32, 34.03) -- (285.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.65, 34.03) -- (285.65, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.10, 34.03) -- (286.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.16, 34.03) -- (286.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.46, 34.03) -- (286.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.60, 34.03) -- (286.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65, 34.03) -- (286.65, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.71, 34.03) -- (286.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.73, 34.03) -- (286.73, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.83, 34.03) -- (286.83, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.86, 34.03) -- (286.86, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (287.36, 34.03) -- (287.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (287.70, 34.03) -- (287.70, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (287.78, 34.03) -- (287.78, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (289.22, 34.03) -- (289.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (289.39, 34.03) -- (289.39, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (289.45, 34.03) -- (289.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (289.83, 34.03) -- (289.83, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (289.89, 34.03) -- (289.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.32, 34.03) -- (290.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.49, 34.03) -- (290.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.52, 34.03) -- (290.52, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.79, 34.03) -- (290.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.84, 34.03) -- (290.84, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.85, 34.03) -- (290.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.85, 34.03) -- (290.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.88, 34.03) -- (290.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.92, 34.03) -- (290.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (291.46, 34.03) -- (291.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (291.68, 34.03) -- (291.68, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.03, 34.03) -- (292.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.66, 34.03) -- (292.66, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.90, 34.03) -- (292.90, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (293.68, 34.03) -- (293.68, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.05, 34.03) -- (294.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.33, 34.03) -- (294.33, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.72, 34.03) -- (294.72, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.89, 34.03) -- (294.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.98, 34.03) -- (294.98, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (295.14, 34.03) -- (295.14, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (295.44, 34.03) -- (295.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (295.54, 34.03) -- (295.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (295.80, 34.03) -- (295.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (296.23, 34.03) -- (296.23, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.04, 34.03) -- (297.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.20, 34.03) -- (297.20, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.32, 34.03) -- (297.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.39, 34.03) -- (297.39, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.92, 34.03) -- (297.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.07, 34.03) -- (298.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.46, 34.03) -- (298.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.47, 34.03) -- (298.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.54, 34.03) -- (298.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.62, 34.03) -- (298.62, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.15, 34.03) -- (299.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.26, 34.03) -- (299.26, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.54, 34.03) -- (299.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.58, 34.03) -- (299.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (300.71, 34.03) -- (300.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (301.41, 34.03) -- (301.41, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.13, 34.03) -- (302.13, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.61, 34.03) -- (302.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (303.45, 34.03) -- (303.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (303.55, 34.03) -- (303.55, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (303.59, 34.03) -- (303.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (303.66, 34.03) -- (303.66, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (303.89, 34.03) -- (303.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (303.92, 34.03) -- (303.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.13, 34.03) -- (304.13, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.31, 34.03) -- (304.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.32, 34.03) -- (304.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.63, 34.03) -- (304.63, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (305.44, 34.03) -- (305.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (306.03, 34.03) -- (306.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (306.65, 34.03) -- (306.65, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.10, 34.03) -- (307.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.15, 34.03) -- (307.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.34, 34.03) -- (307.34, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.36, 34.03) -- (307.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.48, 34.03) -- (307.48, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.57, 34.03) -- (307.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.71, 34.03) -- (307.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.78, 34.03) -- (307.78, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.86, 34.03) -- (307.86, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (308.14, 34.03) -- (308.14, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (308.17, 34.03) -- (308.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (308.40, 34.03) -- (308.40, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.29, 34.03) -- (309.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.65, 34.03) -- (309.65, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.66, 34.03) -- (309.66, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.77, 34.03) -- (309.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.85, 34.03) -- (309.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.26, 34.03) -- (310.26, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.42, 34.03) -- (310.42, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.88, 34.03) -- (310.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.97, 34.03) -- (310.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.25, 34.03) -- (311.25, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (312.09, 34.03) -- (312.09, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (312.22, 34.03) -- (312.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (312.41, 34.03) -- (312.41, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (313.42, 34.03) -- (313.42, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (313.62, 34.03) -- (313.62, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (313.78, 34.03) -- (313.78, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.05, 34.03) -- (314.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.50, 34.03) -- (314.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.58, 34.03) -- (314.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.67, 34.03) -- (314.67, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.27, 34.03) -- (315.27, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.36, 34.03) -- (315.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.70, 34.03) -- (315.70, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.87, 34.03) -- (315.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.98, 34.03) -- (315.98, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.35, 34.03) -- (316.35, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.56, 34.03) -- (316.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.72, 34.03) -- (316.72, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.21, 34.03) -- (317.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.49, 34.03) -- (317.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.56, 34.03) -- (317.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (318.84, 34.03) -- (318.84, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (318.87, 34.03) -- (318.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.28, 34.03) -- (319.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.56, 34.03) -- (319.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.75, 34.03) -- (319.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.97, 34.03) -- (319.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.23, 34.03) -- (320.23, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.29, 34.03) -- (320.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.33, 34.03) -- (320.33, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.94, 34.03) -- (320.94, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.01, 34.03) -- (321.01, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.22, 34.03) -- (321.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.25, 34.03) -- (321.25, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.36, 34.03) -- (321.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.75, 34.03) -- (321.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (323.15, 34.03) -- (323.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (323.66, 34.03) -- (323.66, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (325.17, 34.03) -- (325.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (325.77, 34.03) -- (325.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (325.89, 34.03) -- (325.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (326.94, 34.03) -- (326.94, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (327.01, 34.03) -- (327.01, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (327.29, 34.03) -- (327.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (328.29, 34.03) -- (328.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (328.36, 34.03) -- (328.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (328.82, 34.03) -- (328.82, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (329.10, 34.03) -- (329.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (329.71, 34.03) -- (329.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (330.08, 34.03) -- (330.08, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (330.10, 34.03) -- (330.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (330.14, 34.03) -- (330.14, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (330.37, 34.03) -- (330.37, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (330.66, 34.03) -- (330.66, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (331.19, 34.03) -- (331.19, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (331.66, 34.03) -- (331.66, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (331.92, 34.03) -- (331.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (332.49, 34.03) -- (332.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (333.01, 34.03) -- (333.01, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (334.21, 34.03) -- (334.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (334.41, 34.03) -- (334.41, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (334.89, 34.03) -- (334.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (337.42, 34.03) -- (337.42, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (337.45, 34.03) -- (337.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (337.58, 34.03) -- (337.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (337.70, 34.03) -- (337.70, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (337.71, 34.03) -- (337.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (337.80, 34.03) -- (337.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (339.18, 34.03) -- (339.18, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (339.28, 34.03) -- (339.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (341.35, 34.03) -- (341.35, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (341.75, 34.03) -- (341.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.17, 34.03) -- (342.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.48, 34.03) -- (342.48, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.53, 34.03) -- (342.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.69, 34.03) -- (342.69, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.85, 34.03) -- (342.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (343.03, 34.03) -- (343.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (343.17, 34.03) -- (343.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (343.37, 34.03) -- (343.37, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (343.45, 34.03) -- (343.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (343.75, 34.03) -- (343.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (343.88, 34.03) -- (343.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (344.23, 34.03) -- (344.23, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (345.06, 34.03) -- (345.06, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (346.03, 34.03) -- (346.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (346.49, 34.03) -- (346.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (347.23, 34.03) -- (347.23, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (347.38, 34.03) -- (347.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.49, 34.03) -- (348.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.58, 34.03) -- (348.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (349.13, 34.03) -- (349.13, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (349.81, 34.03) -- (349.81, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (350.10, 34.03) -- (350.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (350.24, 34.03) -- (350.24, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (350.58, 34.03) -- (350.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (351.85, 34.03) -- (351.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (352.05, 34.03) -- (352.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (352.77, 34.03) -- (352.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (353.17, 34.03) -- (353.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (353.42, 34.03) -- (353.42, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (353.71, 34.03) -- (353.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (354.71, 34.03) -- (354.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (355.56, 34.03) -- (355.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (357.56, 34.03) -- (357.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (357.72, 34.03) -- (357.72, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (357.97, 34.03) -- (357.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (358.00, 34.03) -- (358.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (358.30, 34.03) -- (358.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (358.37, 34.03) -- (358.37, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (358.57, 34.03) -- (358.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (358.60, 34.03) -- (358.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (358.96, 34.03) -- (358.96, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (358.97, 34.03) -- (358.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (359.44, 34.03) -- (359.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (359.71, 34.03) -- (359.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (359.84, 34.03) -- (359.84, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (359.89, 34.03) -- (359.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (359.95, 34.03) -- (359.95, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.12, 34.03) -- (360.12, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.50, 34.03) -- (360.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.53, 34.03) -- (360.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (361.15, 34.03) -- (361.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (361.24, 34.03) -- (361.24, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (361.57, 34.03) -- (361.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (362.32, 34.03) -- (362.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (362.86, 34.03) -- (362.86, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (362.88, 34.03) -- (362.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (362.99, 34.03) -- (362.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (363.37, 34.03) -- (363.37, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (365.15, 34.03) -- (365.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (365.51, 34.03) -- (365.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (365.58, 34.03) -- (365.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (365.58, 34.03) -- (365.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (366.24, 34.03) -- (366.24, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (366.27, 34.03) -- (366.27, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (366.79, 34.03) -- (366.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (367.09, 34.03) -- (367.09, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (367.28, 34.03) -- (367.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (367.50, 34.03) -- (367.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (367.74, 34.03) -- (367.74, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (368.30, 34.03) -- (368.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (368.30, 34.03) -- (368.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (368.38, 34.03) -- (368.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (368.49, 34.03) -- (368.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (368.90, 34.03) -- (368.90, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (369.46, 34.03) -- (369.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (370.56, 34.03) -- (370.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (370.74, 34.03) -- (370.74, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (370.85, 34.03) -- (370.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (372.47, 34.03) -- (372.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (373.39, 34.03) -- (373.39, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (373.79, 34.03) -- (373.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (374.21, 34.03) -- (374.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (375.70, 34.03) -- (375.70, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (378.93, 34.03) -- (378.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (380.42, 34.03) -- (380.42, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (385.52, 34.03) -- (385.52, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (386.08, 34.03) -- (386.08, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (386.54, 34.03) -- (386.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (386.90, 34.03) -- (386.90, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (387.31, 34.03) -- (387.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (387.53, 34.03) -- (387.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (388.24, 34.03) -- (388.24, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (388.35, 34.03) -- (388.35, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (388.69, 34.03) -- (388.69, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (388.71, 34.03) -- (388.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (388.75, 34.03) -- (388.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (388.90, 34.03) -- (388.90, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.17, 34.03) -- (389.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.73, 34.03) -- (389.73, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (390.59, 34.03) -- (390.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (391.22, 34.03) -- (391.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (391.77, 34.03) -- (391.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (391.82, 34.03) -- (391.82, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (392.15, 34.03) -- (392.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (392.41, 34.03) -- (392.41, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (396.33, 34.03) -- (396.33, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (397.13, 34.03) -- (397.13, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (397.28, 34.03) -- (397.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (404.32, 34.03) -- (404.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (404.80, 34.03) -- (404.80, 41.32);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
-	( 39.69,277.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.48, 34.03) --
+	( 52.48,277.03);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,101.49) {3.8};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,183.81) {4.0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,266.13) {4.2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 45.37, 87.37) {-0.002};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 45.37,145.86) {0.000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 45.37,204.34) {0.002};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 45.37,262.83) {0.004};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.48, 34.03) --
 	(421.57, 34.03);
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 41.46, 20.31) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 89.02, 20.31) {1};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (136.58, 20.31) {2};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (184.13, 20.31) {3};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (231.69, 20.31) {4};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (279.25, 20.31) {5};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.81, 20.31) {6};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (374.36, 20.31) {7};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 53.04, 20.31) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 98.87, 20.31) {1};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (144.70, 20.31) {2};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (190.53, 20.31) {3};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (236.36, 20.31) {4};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (282.19, 20.31) {5};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (328.02, 20.31) {6};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (373.85, 20.31) {7};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (230.63,  4.82) {Ln(Min. Cap Dist.)$_{t}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (237.03,  4.82) {Ln(Min. Cap Dist.)$_{t}$};
 \end{scope}

### 2014-09-25 LaTeX/mCityCoefPlot.tex
updates to tex, and plots

@@
-% Created by tikzDevice version 0.7.0 on 2014-09-23 11:36:07
+% Created by tikzDevice version 0.7.0 on 2014-09-25 14:01:51
 % !TEX encoding = UTF-8 Unicode
@@
 \path[fill=fillColor] (124.66, 34.03) rectangle (277.04,277.03);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (201.54, 49.88) -- (209.61, 49.88);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.10, 49.88) -- (207.76, 49.88);
-
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (193.68, 76.30) -- (230.11, 76.30);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (193.96, 76.30) -- (232.45, 76.30);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (174.88,102.71) -- (189.88,102.71);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (167.42,102.71) -- (183.20,102.71);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (155.06,129.12) -- (247.73,129.12);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (143.88,129.12) -- (245.67,129.12);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (165.59,155.53) -- (195.00,155.53);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (162.34,155.53) -- (193.68,155.53);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.88,181.95) -- (202.07,181.95);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.93,181.95) -- (202.27,181.95);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (187.98,208.36) -- (225.50,208.36);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (189.78,208.36) -- (231.19,208.36);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (180.79,234.77) -- (210.45,234.77);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (174.23,234.77) -- (205.28,234.77);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (203.18,261.19) -- (216.39,261.19);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (203.17,261.19) -- (217.19,261.19);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (202.19, 49.88) -- (208.96, 49.88);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (200.72, 49.88) -- (207.15, 49.88);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (196.61, 76.30) -- (227.18, 76.30);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (197.05, 76.30) -- (229.35, 76.30);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (176.09,102.71) -- (188.68,102.71);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (168.69,102.71) -- (181.93,102.71);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (162.51,129.12) -- (240.28,129.12);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (152.06,129.12) -- (237.49,129.12);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (167.95,155.53) -- (192.63,155.53);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (164.86,155.53) -- (191.16,155.53);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (200.97,181.95) -- (201.98,181.95);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (201.04,181.95) -- (202.16,181.95);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (191.00,208.36) -- (222.48,208.36);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (193.11,208.36) -- (227.86,208.36);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (183.17,234.77) -- (208.07,234.77);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (176.73,234.77) -- (202.79,234.77);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (204.24,261.19) -- (215.33,261.19);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (204.30,261.19) -- (216.06,261.19);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.79,261.19) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (210.18,261.19) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (195.62,234.77) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.76,234.77) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (206.74,208.36) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (210.49,208.36) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.47,181.95) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.60,181.95) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.29,155.53) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.01,155.53) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.39,129.12) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.77,129.12) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.38,102.71) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.31,102.71) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (211.89, 76.30) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (213.20, 76.30) circle (  2.85);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (203.93, 49.88) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (205.57, 49.88) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.76, 48.56) --
-	(207.76, 51.20);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.61, 48.56) --
+	(209.61, 51.20);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.76, 49.88) --
-	(200.10, 49.88);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.61, 49.88) --
+	(201.54, 49.88);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (200.10, 48.56) --
-	(200.10, 51.20);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (201.54, 48.56) --
+	(201.54, 51.20);
+\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (230.11, 74.97) --
-	(230.11, 77.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (232.45, 74.97) --
+	(232.45, 77.62);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (230.11, 76.30) --
-	(193.68, 76.30);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (232.45, 76.30) --
+	(193.96, 76.30);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (193.68, 74.97) --
-	(193.68, 77.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (193.96, 74.97) --
+	(193.96, 77.62);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (189.88,101.39) --
-	(189.88,104.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (183.20,101.39) --
+	(183.20,104.03);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (189.88,102.71) --
-	(174.88,102.71);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (183.20,102.71) --
+	(167.42,102.71);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (174.88,101.39) --
-	(174.88,104.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (167.42,101.39) --
+	(167.42,104.03);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (247.73,127.80) --
-	(247.73,130.44);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (245.67,127.80) --
+	(245.67,130.44);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (247.73,129.12) --
-	(155.06,129.12);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (245.67,129.12) --
+	(143.88,129.12);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (155.06,127.80) --
-	(155.06,130.44);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (143.88,127.80) --
+	(143.88,130.44);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (195.00,154.21) --
-	(195.00,156.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (193.68,154.21) --
+	(193.68,156.86);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (195.00,155.53) --
-	(165.59,155.53);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (193.68,155.53) --
+	(162.34,155.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.59,154.21) --
-	(165.59,156.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (162.34,154.21) --
+	(162.34,156.86);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (202.07,180.63) --
-	(202.07,183.27);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.27,180.63) --
+	(202.27,183.27);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (202.07,181.95) --
-	(200.88,181.95);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.27,181.95) --
+	(200.93,181.95);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (200.88,180.63) --
-	(200.88,183.27);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (200.93,180.63) --
+	(200.93,183.27);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (225.50,207.04) --
-	(225.50,209.68);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (231.19,207.04) --
+	(231.19,209.68);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (225.50,208.36) --
-	(187.98,208.36);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (231.19,208.36) --
+	(189.78,208.36);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (187.98,207.04) --
-	(187.98,209.68);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (189.78,207.04) --
+	(189.78,209.68);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (210.45,233.45) --
-	(210.45,236.09);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.28,233.45) --
+	(205.28,236.09);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (210.45,234.77) --
-	(180.79,234.77);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.28,234.77) --
+	(174.23,234.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (180.79,233.45) --
-	(180.79,236.09);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (174.23,233.45) --
+	(174.23,236.09);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.39,259.87) --
-	(216.39,262.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (217.19,259.87) --
+	(217.19,262.51);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.39,261.19) --
-	(203.18,261.19);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (217.19,261.19) --
+	(203.17,261.19);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (203.18,259.87) --
-	(203.18,262.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (203.17,259.87) --
+	(203.17,262.51);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (131.59, 20.31) {-0.3};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (131.59, 20.31) {-0.004};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (177.76, 20.31) {-0.1};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (166.22, 20.31) {-0.002};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (223.94, 20.31) {0.1};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (200.85, 20.31) {0.000};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (270.11, 20.31) {0.3};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (235.48, 20.31) {0.002};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (270.11, 20.31) {0.004};
 \end{scope}

### 2014-09-25 LaTeX/mCitySimPlot.tex
updates to tex, and plots

@@
-% Created by tikzDevice version 0.7.0 on 2014-09-23 11:39:59
+% Created by tikzDevice version 0.7.0 on 2014-09-25 14:22:36
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 39.69, 34.03) rectangle (421.57,277.03);
+\path[clip] ( 52.48, 34.03) rectangle (421.57,277.03);
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
 
-\path[fill=fillColor] ( 39.69, 34.03) rectangle (421.57,277.03);
+\path[fill=fillColor] ( 52.48, 34.03) rectangle (421.57,277.03);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 57.05,110.46) --
-	( 62.08,112.14) --
-	( 67.11,113.83) --
-	( 72.14,115.51) --
-	( 77.17,117.20) --
-	( 82.20,118.88) --
-	( 87.23,120.57) --
-	( 92.27,122.25) --
-	( 97.30,123.94) --
-	(102.33,125.62) --
-	(107.36,127.30) --
-	(112.39,128.99) --
-	(117.42,130.67) --
-	(122.45,132.36) --
-	(127.49,134.04) --
-	(132.52,135.73) --
-	(137.55,137.41) --
-	(142.58,139.10) --
-	(147.61,140.78) --
-	(152.64,142.47) --
-	(157.67,144.15) --
-	(162.71,145.84) --
-	(167.74,147.52) --
-	(172.77,149.20) --
-	(177.80,150.89) --
-	(182.83,152.57) --
-	(187.86,154.26) --
-	(192.89,155.94) --
-	(197.93,157.63) --
-	(202.96,159.31) --
-	(207.99,161.00) --
-	(213.02,162.68) --
-	(218.05,164.37) --
-	(223.08,166.05) --
-	(228.12,167.74) --
-	(233.15,169.42) --
-	(238.18,171.11) --
-	(243.21,172.79) --
-	(248.24,174.47) --
-	(253.27,176.16) --
-	(258.30,177.84) --
-	(263.34,179.53) --
-	(268.37,181.21) --
-	(273.40,182.90) --
-	(278.43,184.58) --
-	(283.46,186.27) --
-	(288.49,187.95) --
-	(293.52,189.64) --
-	(298.56,191.32) --
-	(303.59,193.01) --
-	(308.62,194.69) --
-	(313.65,196.38) --
-	(318.68,198.06) --
-	(323.71,199.74) --
-	(328.74,201.43) --
-	(333.78,203.11) --
-	(338.81,204.80) --
-	(343.84,206.48) --
-	(348.87,208.17) --
-	(353.90,209.85) --
-	(358.93,211.54) --
-	(363.96,213.22) --
-	(369.00,214.91) --
-	(374.03,216.59) --
-	(379.06,218.28) --
-	(384.09,219.96) --
-	(389.12,221.65) --
-	(394.15,223.33) --
-	(399.18,225.01) --
-	(404.22,226.70);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 69.26,108.08) --
+	( 76.94,110.75) --
+	( 81.21,112.23) --
+	( 81.35,112.28) --
+	( 94.75,116.93) --
+	(103.21,119.87) --
+	(108.87,121.84) --
+	(112.14,122.97) --
+	(118.51,125.19) --
+	(123.77,127.01) --
+	(127.53,128.32) --
+	(130.04,129.19) --
+	(138.05,131.97) --
+	(158.20,138.97) --
+	(171.57,143.61) --
+	(171.70,143.66) --
+	(174.96,144.79) --
+	(175.86,145.11) --
+	(185.97,148.62) --
+	(188.46,149.48) --
+	(195.56,151.95) --
+	(205.05,155.24) --
+	(205.06,155.25) --
+	(209.59,156.82) --
+	(209.87,156.92) --
+	(211.41,157.45) --
+	(212.10,157.69) --
+	(212.80,157.94) --
+	(212.89,157.97) --
+	(213.53,158.19) --
+	(213.69,158.24) --
+	(215.24,158.78) --
+	(220.60,160.64) --
+	(222.23,161.21) --
+	(222.43,161.28) --
+	(224.02,161.83) --
+	(228.32,163.33) --
+	(228.78,163.49) --
+	(233.22,165.03) --
+	(235.00,165.65) --
+	(235.50,165.82) --
+	(236.76,166.26) --
+	(238.27,166.78) --
+	(238.97,167.03) --
+	(239.94,167.36) --
+	(240.65,167.61) --
+	(240.90,167.70) --
+	(240.95,167.71) --
+	(241.36,167.86) --
+	(244.68,169.01) --
+	(246.54,169.65) --
+	(247.54,170.00) --
+	(248.75,170.42) --
+	(249.31,170.62) --
+	(250.77,171.12) --
+	(251.67,171.44) --
+	(252.68,171.79) --
+	(253.66,172.13) --
+	(254.85,172.54) --
+	(254.86,172.54) --
+	(255.67,172.83) --
+	(256.23,173.02) --
+	(256.77,173.21) --
+	(257.49,173.46) --
+	(257.71,173.54) --
+	(258.26,173.73) --
+	(258.74,173.89) --
+	(259.12,174.02) --
+	(259.38,174.11) --
+	(259.99,174.33) --
+	(260.56,174.52) --
+	(260.79,174.60) --
+	(262.27,175.12) --
+	(262.38,175.16) --
+	(263.62,175.59) --
+	(263.78,175.64) --
+	(265.81,176.35) --
+	(267.16,176.82) --
+	(267.27,176.85) --
+	(267.90,177.08) --
+	(269.02,177.46) --
+	(269.24,177.54) --
+	(269.50,177.63) --
+	(270.00,177.80) --
+	(271.24,178.23) --
+	(271.44,178.30) --
+	(271.47,178.31) --
+	(271.89,178.46) --
+	(272.97,178.83) --
+	(273.00,178.84) --
+	(273.30,178.95) --
+	(274.10,179.23) --
+	(274.51,179.37) --
+	(275.15,179.59) --
+	(275.85,179.83) --
+	(276.45,180.04) --
+	(276.57,180.09) --
+	(277.67,180.47) --
+	(277.74,180.49) --
+	(278.30,180.69) --
+	(278.99,180.93) --
+	(279.37,181.06) --
+	(280.17,181.34) --
+	(281.01,181.63) --
+	(281.75,181.88) --
+	(282.04,181.99) --
+	(282.56,182.17) --
+	(282.59,182.17) --
+	(282.73,182.22) --
+	(283.17,182.38) --
+	(283.67,182.55) --
+	(284.33,182.78) --
+	(284.38,182.80) --
+	(284.78,182.94) --
+	(285.47,183.18) --
+	(285.59,183.22) --
+	(285.79,183.29) --
+	(285.93,183.34) --
+	(285.96,183.35) --
+	(286.40,183.50) --
+	(286.76,183.63) --
+	(286.94,183.69) --
+	(287.11,183.75) --
+	(287.40,183.85) --
+	(287.56,183.90) --
+	(287.64,183.93) --
+	(288.93,184.38) --
+	(289.17,184.46) --
+	(289.98,184.74) --
+	(290.06,184.77) --
+	(290.15,184.80) --
+	(290.68,184.98) --
+	(290.90,185.06) --
+	(291.07,185.12) --
+	(291.16,185.15) --
+	(291.99,185.44) --
+	(292.53,185.63) --
+	(292.56,185.64) --
+	(293.19,185.86) --
+	(293.72,186.04) --
+	(294.42,186.28) --
+	(294.46,186.30) --
+	(295.07,186.51) --
+	(295.58,186.69) --
+	(296.54,187.02) --
+	(296.64,187.06) --
+	(296.96,187.17) --
+	(297.07,187.21) --
+	(297.55,187.37) --
+	(297.61,187.39) --
+	(297.93,187.50) --
+	(298.07,187.55) --
+	(298.13,187.57) --
+	(298.19,187.59) --
+	(298.21,187.60) --
+	(298.32,187.64) --
+	(298.88,187.83) --
+	(299.55,188.07) --
+	(300.83,188.51) --
+	(301.02,188.58) --
+	(301.08,188.60) --
+	(301.48,188.74) --
+	(301.54,188.76) --
+	(301.64,188.79) --
+	(301.73,188.83) --
+	(302.00,188.92) --
+	(302.17,188.98) --
+	(302.49,189.09) --
+	(302.51,189.10) --
+	(302.54,189.11) --
+	(302.55,189.11) --
+	(302.59,189.12) --
+	(302.62,189.13) --
+	(302.72,189.17) --
+	(302.80,189.20) --
+	(302.80,189.20) --
+	(303.19,189.33) --
+	(303.42,189.41) --
+	(303.79,189.54) --
+	(304.00,189.61) --
+	(304.46,189.77) --
+	(305.92,190.28) --
+	(306.03,190.32) --
+	(306.63,190.53) --
+	(307.38,190.79) --
+	(307.50,190.83) --
+	(307.76,190.92) --
+	(308.06,191.02) --
+	(308.22,191.08) --
+	(308.71,191.25) --
+	(309.07,191.37) --
+	(309.23,191.43) --
+	(309.24,191.43) --
+	(309.36,191.48) --
+	(309.39,191.49) --
+	(309.44,191.50) --
+	(310.04,191.71) --
+	(310.57,191.90) --
+	(310.65,191.92) --
+	(310.74,191.95) --
+	(310.97,192.03) --
+	(311.29,192.15) --
+	(311.41,192.19) --
+	(312.93,192.71) --
+	(312.98,192.73) --
+	(313.47,192.90) --
+	(313.56,192.93) --
+	(314.18,193.15) --
+	(314.39,193.22) --
+	(314.46,193.25) --
+	(314.61,193.30) --
+	(314.93,193.41) --
+	(315.17,193.49) --
+	(315.66,193.66) --
+	(315.81,193.72) --
+	(315.92,193.75) --
+	(316.04,193.79) --
+	(316.27,193.88) --
+	(316.28,193.88) --
+	(316.31,193.89) --
+	(316.40,193.92) --
+	(316.53,193.97) --
+	(316.54,193.97) --
+	(316.73,194.03) --
+	(316.73,194.03) --
+	(317.05,194.15) --
+	(317.72,194.38) --
+	(317.91,194.44) --
+	(318.05,194.49) --
+	(318.31,194.58) --
+	(318.59,194.68) --
+	(318.98,194.82) --
+	(319.05,194.84) --
+	(319.19,194.89) --
+	(319.36,194.95) --
+	(319.71,195.07) --
+	(319.91,195.14) --
+	(319.93,195.15) --
+	(320.06,195.19) --
+	(320.17,195.23) --
+	(320.20,195.24) --
+	(320.30,195.27) --
+	(320.38,195.30) --
+	(320.46,195.33) --
+	(320.79,195.44) --
+	(320.87,195.47) --
+	(321.03,195.53) --
+	(321.25,195.60) --
+	(321.56,195.71) --
+	(321.69,195.76) --
+	(321.81,195.80) --
+	(321.97,195.85) --
+	(322.34,195.98) --
+	(322.35,195.99) --
+	(322.38,196.00) --
+	(322.44,196.02) --
+	(322.47,196.03) --
+	(322.55,196.06) --
+	(322.98,196.21) --
+	(323.15,196.26) --
+	(323.39,196.35) --
+	(323.51,196.39) --
+	(323.64,196.43) --
+	(323.74,196.47) --
+	(324.03,196.57) --
+	(324.31,196.67) --
+	(324.91,196.88) --
+	(326.25,197.34) --
+	(326.31,197.36) --
+	(326.44,197.41) --
+	(326.69,197.49) --
+	(326.98,197.59) --
+	(327.12,197.64) --
+	(327.38,197.73) --
+	(327.45,197.76) --
+	(327.62,197.82) --
+	(328.36,198.07) --
+	(328.71,198.20) --
+	(328.89,198.26) --
+	(329.00,198.30) --
+	(329.34,198.41) --
+	(330.21,198.72) --
+	(330.77,198.91) --
+	(330.92,198.96) --
+	(331.77,199.26) --
+	(332.05,199.35) --
+	(332.77,199.61) --
+	(333.03,199.70) --
+	(333.16,199.74) --
+	(333.59,199.89) --
+	(335.17,200.44) --
+	(335.96,200.71) --
+	(336.21,200.80) --
+	(336.98,201.07) --
+	(337.10,201.11) --
+	(337.64,201.30) --
+	(339.32,201.88) --
+	(339.85,202.06) --
+	(340.50,202.29) --
+	(340.63,202.33) --
+	(341.25,202.55) --
+	(341.62,202.68) --
+	(341.97,202.80) --
+	(342.00,202.81) --
+	(342.05,202.83) --
+	(342.45,202.97) --
+	(342.53,202.99) --
+	(343.04,203.17) --
+	(343.17,203.22) --
+	(343.85,203.45) --
+	(343.87,203.46) --
+	(343.95,203.49) --
+	(344.16,203.56) --
+	(344.46,203.67) --
+	(344.63,203.72) --
+	(344.93,203.83) --
+	(345.02,203.86) --
+	(345.07,203.88) --
+	(345.10,203.89) --
+	(345.51,204.03) --
+	(345.57,204.05) --
+	(346.09,204.23) --
+	(346.39,204.34) --
+	(347.80,204.83) --
+	(348.20,204.96) --
+	(348.41,205.04) --
+	(348.87,205.20) --
+	(348.92,205.21) --
+	(349.60,205.45) --
+	(351.33,206.05) --
+	(351.43,206.09) --
+	(351.56,206.13) --
+	(351.74,206.20) --
+	(351.87,206.24) --
+	(353.20,206.70) --
+	(353.44,206.78) --
+	(353.54,206.82) --
+	(354.59,207.18) --
+	(357.17,208.08) --
+	(357.38,208.15) --
+	(357.90,208.33) --
+	(357.93,208.34) --
+	(358.21,208.44) --
+	(358.75,208.63) --
+	(359.57,208.92) --
+	(359.62,208.93) --
+	(360.33,209.18) --
+	(360.36,209.19) --
+	(360.85,209.36) --
+	(361.40,209.55) --
+	(362.06,209.78) --
+	(362.35,209.88) --
+	(362.48,209.93) --
+	(362.58,209.96) --
+	(363.30,210.21) --
+	(363.33,210.22) --
+	(363.40,210.24) --
+	(364.54,210.64) --
+	(365.21,210.87) --
+	(366.77,211.42) --
+	(366.99,211.49) --
+	(368.17,211.90) --
+	(368.73,212.10) --
+	(372.78,213.50) --
+	(373.25,213.67) --
+	(374.25,214.01) --
+	(374.25,214.01) --
+	(374.55,214.12) --
+	(374.76,214.19) --
+	(375.05,214.29) --
+	(375.30,214.38) --
+	(375.66,214.50) --
+	(375.91,214.59) --
+	(376.54,214.81) --
+	(376.88,214.93) --
+	(377.80,215.25) --
+	(378.36,215.44) --
+	(378.50,215.49) --
+	(378.91,215.63) --
+	(379.95,215.99) --
+	(381.22,216.44) --
+	(381.23,216.44) --
+	(381.92,216.68) --
+	(381.95,216.69) --
+	(382.82,216.99) --
+	(383.24,217.14) --
+	(383.51,217.23) --
+	(384.09,217.43) --
+	(384.17,217.46) --
+	(384.29,217.50) --
+	(384.73,217.65) --
+	(386.66,218.32) --
+	(386.77,218.36) --
+	(390.32,219.59) --
+	(394.80,221.15) --
+	(396.85,221.86) --
+	(404.07,224.37) --
+	(404.80,224.62);
 \definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}
 
-\path[fill=fillColor,fill opacity=0.30] ( 57.05,174.43) --
-	( 62.08,174.80) --
-	( 67.11,175.43) --
-	( 72.14,175.95) --
-	( 77.17,176.45) --
-	( 82.20,177.01) --
-	( 87.23,177.60) --
-	( 92.27,178.07) --
-	( 97.30,178.83) --
-	(102.33,179.63) --
-	(107.36,180.19) --
-	(112.39,180.68) --
-	(117.42,181.22) --
-	(122.45,181.91) --
-	(127.49,182.61) --
-	(132.52,183.22) --
-	(137.55,183.85) --
-	(142.58,184.72) --
-	(147.61,185.27) --
-	(152.64,185.85) --
-	(157.67,186.68) --
-	(162.71,187.40) --
-	(167.74,188.19) --
-	(172.77,188.79) --
-	(177.80,189.72) --
-	(182.83,190.53) --
-	(187.86,191.58) --
-	(192.89,192.32) --
-	(197.93,193.15) --
-	(202.96,194.08) --
-	(207.99,195.20) --
-	(213.02,196.17) --
-	(218.05,197.04) --
-	(223.08,198.12) --
-	(228.12,199.15) --
-	(233.15,200.19) --
-	(238.18,201.29) --
-	(243.21,202.47) --
-	(248.24,203.82) --
-	(253.27,205.19) --
-	(258.30,206.48) --
-	(263.34,207.77) --
-	(268.37,209.20) --
-	(273.40,210.73) --
-	(278.43,212.20) --
-	(283.46,213.76) --
-	(288.49,215.30) --
-	(293.52,216.81) --
-	(298.56,218.76) --
-	(303.59,220.71) --
-	(308.62,222.73) --
-	(313.65,224.51) --
-	(318.68,226.51) --
-	(323.71,228.57) --
-	(328.74,230.64) --
-	(333.78,232.65) --
-	(338.81,234.73) --
-	(343.84,236.98) --
-	(348.87,239.31) --
-	(353.90,241.60) --
-	(358.93,243.92) --
-	(363.96,246.40) --
-	(369.00,248.74) --
-	(374.03,251.08) --
-	(379.06,253.40) --
-	(384.09,255.89) --
-	(389.12,258.42) --
-	(394.15,260.84) --
-	(399.18,263.30) --
-	(404.22,265.99) --
-	(404.22,186.70) --
-	(399.18,185.91) --
-	(394.15,185.08) --
-	(389.12,184.30) --
-	(384.09,183.58) --
-	(379.06,182.70) --
-	(374.03,181.87) --
-	(369.00,180.89) --
-	(363.96,179.93) --
-	(358.93,178.91) --
-	(353.90,178.04) --
-	(348.87,176.86) --
-	(343.84,175.89) --
-	(338.81,174.74) --
-	(333.78,173.45) --
-	(328.74,172.28) --
-	(323.71,171.02) --
-	(318.68,169.43) --
-	(313.65,167.97) --
-	(308.62,166.54) --
-	(303.59,165.18) --
-	(298.56,163.70) --
-	(293.52,162.08) --
-	(288.49,160.29) --
-	(283.46,158.60) --
-	(278.43,156.91) --
-	(273.40,155.18) --
-	(268.37,153.23) --
-	(263.34,151.42) --
-	(258.30,149.61) --
-	(253.27,147.65) --
-	(248.24,145.45) --
-	(243.21,143.23) --
-	(238.18,141.02) --
-	(233.15,138.72) --
-	(228.12,136.35) --
-	(223.08,133.80) --
-	(218.05,131.34) --
-	(213.02,128.83) --
-	(207.99,126.45) --
-	(202.96,124.00) --
-	(197.93,121.57) --
-	(192.89,119.03) --
-	(187.86,116.41) --
-	(182.83,113.90) --
-	(177.80,111.23) --
-	(172.77,108.70) --
-	(167.74,105.98) --
-	(162.71,103.34) --
-	(157.67,100.79) --
-	(152.64, 98.10) --
-	(147.61, 95.49) --
-	(142.58, 92.64) --
-	(137.55, 89.85) --
-	(132.52, 87.02) --
-	(127.49, 84.25) --
-	(122.45, 81.44) --
-	(117.42, 78.59) --
-	(112.39, 75.96) --
-	(107.36, 73.32) --
-	(102.33, 70.44) --
-	( 97.30, 67.62) --
-	( 92.27, 64.83) --
-	( 87.23, 61.80) --
-	( 82.20, 58.96) --
-	( 77.17, 56.21) --
-	( 72.14, 53.52) --
-	( 67.11, 50.65) --
-	( 62.08, 47.79) --
-	( 57.05, 45.08) --
+\path[fill=fillColor,fill opacity=0.30] ( 69.26,174.00) --
+	( 76.94,174.91) --
+	( 81.21,175.28) --
+	( 81.35,175.28) --
+	( 94.75,176.82) --
+	(103.21,177.55) --
+	(108.87,178.21) --
+	(112.14,178.55) --
+	(118.51,179.36) --
+	(123.77,179.97) --
+	(127.53,180.45) --
+	(130.04,180.72) --
+	(138.05,181.83) --
+	(158.20,184.48) --
+	(171.57,186.12) --
+	(171.70,186.12) --
+	(174.96,186.43) --
+	(175.86,186.59) --
+	(185.97,188.24) --
+	(188.46,188.71) --
+	(195.56,189.94) --
+	(205.05,191.47) --
+	(205.06,191.47) --
+	(209.59,192.51) --
+	(209.87,192.54) --
+	(211.41,192.84) --
+	(212.10,193.02) --
+	(212.80,193.13) --
+	(212.89,193.15) --
+	(213.53,193.30) --
+	(213.69,193.33) --
+	(215.24,193.64) --
+	(220.60,194.57) --
+	(222.23,194.95) --
+	(222.43,194.98) --
+	(224.02,195.30) --
+	(228.32,196.22) --
+	(228.78,196.37) --
+	(233.22,197.33) --
+	(235.00,197.73) --
+	(235.50,197.81) --
+	(236.76,198.12) --
+	(238.27,198.42) --
+	(238.97,198.51) --
+	(239.94,198.70) --
+	(240.65,198.90) --
+	(240.90,198.95) --
+	(240.95,198.96) --
+	(241.36,199.05) --
+	(244.68,199.85) --
+	(246.54,200.21) --
+	(247.54,200.41) --
+	(248.75,200.77) --
+	(249.31,200.94) --
+	(250.77,201.35) --
+	(251.67,201.62) --
+	(252.68,201.84) --
+	(253.66,202.15) --
+	(254.85,202.44) --
+	(254.86,202.44) --
+	(255.67,202.67) --
+	(256.23,202.80) --
+	(256.77,202.98) --
+	(257.49,203.17) --
+	(257.71,203.20) --
+	(258.26,203.36) --
+	(258.74,203.50) --
+	(259.12,203.66) --
+	(259.38,203.76) --
+	(259.99,203.84) --
+	(260.56,203.97) --
+	(260.79,204.00) --
+	(262.27,204.53) --
+	(262.38,204.57) --
+	(263.62,204.89) --
+	(263.78,204.92) --
+	(265.81,205.57) --
+	(267.16,205.98) --
+	(267.27,206.00) --
+	(267.90,206.19) --
+	(269.02,206.47) --
+	(269.24,206.53) --
+	(269.50,206.63) --
+	(270.00,206.83) --
+	(271.24,207.27) --
+	(271.44,207.33) --
+	(271.47,207.33) --
+	(271.89,207.39) --
+	(272.97,207.77) --
+	(273.00,207.78) --
+	(273.30,207.93) --
+	(274.10,208.20) --
+	(274.51,208.30) --
+	(275.15,208.47) --
+	(275.85,208.69) --
+	(276.45,208.85) --
+	(276.57,208.88) --
+	(277.67,209.23) --
+	(277.74,209.26) --
+	(278.30,209.41) --
+	(278.99,209.61) --
+	(279.37,209.72) --
+	(280.17,209.90) --
+	(281.01,210.17) --
+	(281.75,210.39) --
+	(282.04,210.51) --
+	(282.56,210.73) --
+	(282.59,210.74) --
+	(282.73,210.80) --
+	(283.17,210.98) --
+	(283.67,211.13) --
+	(284.33,211.34) --
+	(284.38,211.36) --
+	(284.78,211.50) --
+	(285.47,211.75) --
+	(285.59,211.80) --
+	(285.79,211.87) --
+	(285.93,211.89) --
+	(285.96,211.90) --
+	(286.40,212.01) --
+	(286.76,212.10) --
+	(286.94,212.15) --
+	(287.11,212.19) --
+	(287.40,212.28) --
+	(287.56,212.36) --
+	(287.64,212.40) --
+	(288.93,212.86) --
+	(289.17,212.95) --
+	(289.98,213.19) --
+	(290.06,213.22) --
+	(290.15,213.26) --
+	(290.68,213.45) --
+	(290.90,213.53) --
+	(291.07,213.59) --
+	(291.16,213.62) --
+	(291.99,213.93) --
+	(292.53,214.13) --
+	(292.56,214.14) --
+	(293.19,214.38) --
+	(293.72,214.62) --
+	(294.42,214.91) --
+	(294.46,214.93) --
+	(295.07,215.21) --
+	(295.58,215.42) --
+	(296.54,215.77) --
+	(296.64,215.82) --
+	(296.96,215.91) --
+	(297.07,215.95) --
+	(297.55,216.15) --
+	(297.61,216.18) --
+	(297.93,216.29) --
+	(298.07,216.34) --
+	(298.13,216.36) --
+	(298.19,216.38) --
+	(298.21,216.39) --
+	(298.32,216.43) --
+	(298.88,216.63) --
+	(299.55,216.84) --
+	(300.83,217.35) --
+	(301.02,217.42) --
+	(301.08,217.44) --
+	(301.48,217.63) --
+	(301.54,217.65) --
+	(301.64,217.68) --
+	(301.73,217.71) --
+	(302.00,217.78) --
+	(302.17,217.84) --
+	(302.49,217.96) --
+	(302.51,217.97) --
+	(302.54,217.98) --
+	(302.55,217.98) --
+	(302.59,218.00) --
+	(302.62,218.02) --
+	(302.72,218.07) --
+	(302.80,218.10) --
+	(302.80,218.10) --
+	(303.19,218.24) --
+	(303.42,218.32) --
+	(303.79,218.45) --
+	(304.00,218.54) --
+	(304.46,218.72) --
+	(305.92,219.26) --
+	(306.03,219.30) --
+	(306.63,219.55) --
+	(307.38,219.82) --
+	(307.50,219.86) --
+	(307.76,219.99) --
+	(308.06,220.05) --
+	(308.22,220.15) --
+	(308.71,220.34) --
+	(309.07,220.51) --
+	(309.23,220.58) --
+	(309.24,220.58) --
+	(309.36,220.63) --
+	(309.39,220.64) --
+	(309.44,220.65) --
+	(310.04,220.93) --
+	(310.57,221.18) --
+	(310.65,221.20) --
+	(310.74,221.23) --
+	(310.97,221.37) --
+	(311.29,221.50) --
+	(311.41,221.54) --
+	(312.93,222.17) --
+	(312.98,222.19) --
+	(313.47,222.35) --
+	(313.56,222.39) --
+	(314.18,222.61) --
+	(314.39,222.66) --
+	(314.46,222.67) --
+	(314.61,222.71) --
+	(314.93,222.88) --
+	(315.17,222.95) --
+	(315.66,223.09) --
+	(315.81,223.13) --
+	(315.92,223.16) --
+	(316.04,223.21) --
+	(316.27,223.29) --
+	(316.28,223.29) --
+	(316.31,223.29) --
+	(316.40,223.32) --
+	(316.53,223.37) --
+	(316.54,223.38) --
+	(316.73,223.47) --
+	(316.73,223.47) --
+	(317.05,223.60) --
+	(317.72,223.94) --
+	(317.91,224.00) --
+	(318.05,224.03) --
+	(318.31,224.13) --
+	(318.59,224.22) --
+	(318.98,224.34) --
+	(319.05,224.36) --
+	(319.19,224.40) --
+	(319.36,224.48) --
+	(319.71,224.64) --
+	(319.91,224.74) --
+	(319.93,224.75) --
+	(320.06,224.83) --
+	(320.17,224.87) --
+	(320.20,224.88) --
+	(320.30,224.92) --
+	(320.38,224.96) --
+	(320.46,224.99) --
+	(320.79,225.13) --
+	(320.87,225.16) --
+	(321.03,225.25) --
+	(321.25,225.37) --
+	(321.56,225.45) --
+	(321.69,225.50) --
+	(321.81,225.57) --
+	(321.97,225.64) --
+	(322.34,225.80) --
+	(322.35,225.81) --
+	(322.38,225.82) --
+	(322.44,225.86) --
+	(322.47,225.88) --
+	(322.55,225.93) --
+	(322.98,226.04) --
+	(323.15,226.10) --
+	(323.39,226.21) --
+	(323.51,226.27) --
+	(323.64,226.34) --
+	(323.74,226.38) --
+	(324.03,226.53) --
+	(324.31,226.67) --
+	(324.91,226.96) --
+	(326.25,227.49) --
+	(326.31,227.51) --
+	(326.44,227.55) --
+	(326.69,227.67) --
+	(326.98,227.78) --
+	(327.12,227.86) --
+	(327.38,228.02) --
+	(327.45,228.05) --
+	(327.62,228.10) --
+	(328.36,228.30) --
+	(328.71,228.45) --
+	(328.89,228.55) --
+	(329.00,228.61) --
+	(329.34,228.76) --
+	(330.21,229.08) --
+	(330.77,229.33) --
+	(330.92,229.40) --
+	(331.77,229.82) --
+	(332.05,229.95) --
+	(332.77,230.21) --
+	(333.03,230.32) --
+	(333.16,230.38) --
+	(333.59,230.58) --
+	(335.17,231.30) --
+	(335.96,231.66) --
+	(336.21,231.80) --
+	(336.98,232.18) --
+	(337.10,232.25) --
+	(337.64,232.45) --
+	(339.32,233.28) --
+	(339.85,233.56) --
+	(340.50,233.89) --
+	(340.63,233.96) --
+	(341.25,234.28) --
+	(341.62,234.47) --
+	(341.97,234.60) --
+	(342.00,234.62) --
+	(342.05,234.66) --
+	(342.45,234.88) --
+	(342.53,234.91) --
+	(343.04,235.11) --
+	(343.17,235.17) --
+	(343.85,235.44) --
+	(343.87,235.45) --
+	(343.95,235.48) --
+	(344.16,235.58) --
+	(344.46,235.71) --
+	(344.63,235.81) --
+	(344.93,235.95) --
+	(345.02,235.98) --
+	(345.07,236.01) --
+	(345.10,236.02) --
+	(345.51,236.18) --
+	(345.57,236.22) --
+	(346.09,236.43) --
+	(346.39,236.59) --
+	(347.80,237.20) --
+	(348.20,237.34) --
+	(348.41,237.44) --
+	(348.87,237.68) --
+	(348.92,237.70) --
+	(349.60,238.04) --
+	(351.33,238.84) --
+	(351.43,238.88) --
+	(351.56,238.95) --
+	(351.74,239.05) --
+	(351.87,239.12) --
+	(353.20,239.73) --
+	(353.44,239.87) --
+	(353.54,239.91) --
+	(354.59,240.36) --
+	(357.17,241.77) --
+	(357.38,241.84) --
+	(357.90,242.12) --
+	(357.93,242.13) --
+	(358.21,242.26) --
+	(358.75,242.53) --
+	(359.57,242.91) --
+	(359.62,242.93) --
+	(360.33,243.29) --
+	(360.36,243.30) --
+	(360.85,243.52) --
+	(361.40,243.78) --
+	(362.06,244.10) --
+	(362.35,244.25) --
+	(362.48,244.30) --
+	(362.58,244.35) --
+	(363.30,244.68) --
+	(363.33,244.70) --
+	(363.40,244.73) --
+	(364.54,245.27) --
+	(365.21,245.59) --
+	(366.77,246.33) --
+	(366.99,246.43) --
+	(368.17,246.98) --
+	(368.73,247.27) --
+	(372.78,249.35) --
+	(373.25,249.62) --
+	(374.25,250.09) --
+	(374.25,250.09) --
+	(374.55,250.26) --
+	(374.76,250.38) --
+	(375.05,250.52) --
+	(375.30,250.65) --
+	(375.66,250.84) --
+	(375.91,251.00) --
+	(376.54,251.30) --
+	(376.88,251.43) --
+	(377.80,251.88) --
+	(378.36,252.13) --
+	(378.50,252.21) --
+	(378.91,252.40) --
+	(379.95,252.87) --
+	(381.22,253.47) --
+	(381.23,253.47) --
+	(381.92,253.81) --
+	(381.95,253.82) --
+	(382.82,254.27) --
+	(383.24,254.49) --
+	(383.51,254.65) --
+	(384.09,254.97) --
+	(384.17,255.02) --
+	(384.29,255.09) --
+	(384.73,255.34) --
+	(386.66,256.33) --
+	(386.77,256.39) --
+	(390.32,258.27) --
+	(394.80,260.52) --
+	(396.85,261.63) --
+	(404.07,265.49) --
+	(404.80,265.99) --
+	(404.80,183.67) --
+	(404.07,183.52) --
+	(396.85,182.44) --
+	(394.80,181.97) --
+	(390.32,181.18) --
+	(386.77,180.54) --
+	(386.66,180.52) --
+	(384.73,180.06) --
+	(384.29,179.98) --
+	(384.17,179.97) --
+	(384.09,179.97) --
+	(383.51,179.91) --
+	(383.24,179.86) --
+	(382.82,179.77) --
+	(381.95,179.60) --
+	(381.92,179.60) --
+	(381.23,179.45) --
+	(381.22,179.45) --
+	(379.95,179.17) --
+	(378.91,178.92) --
+	(378.50,178.83) --
+	(378.36,178.78) --
+	(377.80,178.72) --
+	(376.88,178.52) --
+	(376.54,178.43) --
+	(375.91,178.35) --
+	(375.66,178.34) --
+	(375.30,178.26) --
+	(375.05,178.23) --
+	(374.76,178.17) --
+	(374.55,178.11) --
+	(374.25,178.04) --
+	(374.25,178.03) --
+	(373.25,177.72) --
+	(372.78,177.61) --
+	(368.73,176.81) --
+	(368.17,176.63) --
+	(366.99,176.37) --
+	(366.77,176.32) --
+	(365.21,176.05) --
+	(364.54,175.92) --
+	(363.40,175.69) --
+	(363.33,175.66) --
+	(363.30,175.66) --
+	(362.58,175.51) --
+	(362.48,175.51) --
+	(362.35,175.47) --
+	(362.06,175.40) --
+	(361.40,175.29) --
+	(360.85,175.14) --
+	(360.36,174.95) --
+	(360.33,174.95) --
+	(359.62,174.91) --
+	(359.57,174.90) --
+	(358.75,174.64) --
+	(358.21,174.57) --
+	(357.93,174.52) --
+	(357.90,174.51) --
+	(357.38,174.41) --
+	(357.17,174.33) --
+	(354.59,173.96) --
+	(353.54,173.77) --
+	(353.44,173.75) --
+	(353.20,173.71) --
+	(351.87,173.38) --
+	(351.74,173.35) --
+	(351.56,173.33) --
+	(351.43,173.30) --
+	(351.33,173.27) --
+	(349.60,172.85) --
+	(348.92,172.68) --
+	(348.87,172.67) --
+	(348.41,172.62) --
+	(348.20,172.56) --
+	(347.80,172.44) --
+	(346.39,172.18) --
+	(346.09,172.06) --
+	(345.57,171.89) --
+	(345.51,171.87) --
+	(345.10,171.77) --
+	(345.07,171.76) --
+	(345.02,171.75) --
+	(344.93,171.72) --
+	(344.63,171.64) --
+	(344.46,171.61) --
+	(344.16,171.57) --
+	(343.95,171.54) --
+	(343.87,171.53) --
+	(343.85,171.53) --
+	(343.17,171.40) --
+	(343.04,171.38) --
+	(342.53,171.23) --
+	(342.45,171.23) --
+	(342.05,171.18) --
+	(342.00,171.16) --
+	(341.97,171.15) --
+	(341.62,171.04) --
+	(341.25,170.97) --
+	(340.63,170.85) --
+	(340.50,170.83) --
+	(339.85,170.68) --
+	(339.32,170.51) --
+	(337.64,169.94) --
+	(337.10,169.80) --
+	(336.98,169.80) --
+	(336.21,169.64) --
+	(335.96,169.52) --
+	(335.17,169.32) --
+	(333.59,168.83) --
+	(333.16,168.72) --
+	(333.03,168.69) --
+	(332.77,168.66) --
+	(332.05,168.46) --
+	(331.77,168.38) --
+	(330.92,168.18) --
+	(330.77,168.15) --
+	(330.21,168.06) --
+	(329.34,167.81) --
+	(329.00,167.74) --
+	(328.89,167.72) --
+	(328.71,167.68) --
+	(328.36,167.60) --
+	(327.62,167.36) --
+	(327.45,167.31) --
+	(327.38,167.30) --
+	(327.12,167.23) --
+	(326.98,167.20) --
+	(326.69,167.12) --
+	(326.44,167.04) --
+	(326.31,167.00) --
+	(326.25,166.99) --
+	(324.91,166.70) --
+	(324.31,166.61) --
+	(324.03,166.54) --
+	(323.74,166.46) --
+	(323.64,166.42) --
+	(323.51,166.37) --
+	(323.39,166.35) --
+	(323.15,166.30) --
+	(322.98,166.27) --
+	(322.55,166.11) --
+	(322.47,166.08) --
+	(322.44,166.07) --
+	(322.38,166.04) --
+	(322.35,166.04) --
+	(322.34,166.04) --
+	(321.97,165.94) --
+	(321.81,165.90) --
+	(321.69,165.87) --
+	(321.56,165.83) --
+	(321.25,165.73) --
+	(321.03,165.68) --
+	(320.87,165.63) --
+	(320.79,165.58) --
+	(320.46,165.51) --
+	(320.38,165.50) --
+	(320.30,165.48) --
+	(320.20,165.46) --
+	(320.17,165.45) --
+	(320.06,165.42) --
+	(319.93,165.38) --
+	(319.91,165.37) --
+	(319.71,165.28) --
+	(319.36,165.11) --
+	(319.19,165.08) --
+	(319.05,165.05) --
+	(318.98,165.03) --
+	(318.59,164.93) --
+	(318.31,164.84) --
+	(318.05,164.78) --
+	(317.91,164.76) --
+	(317.72,164.72) --
+	(317.05,164.59) --
+	(316.73,164.53) --
+	(316.73,164.53) --
+	(316.54,164.50) --
+	(316.53,164.50) --
+	(316.40,164.47) --
+	(316.31,164.45) --
+	(316.28,164.44) --
+	(316.27,164.44) --
+	(316.04,164.36) --
+	(315.92,164.33) --
+	(315.81,164.29) --
+	(315.66,164.24) --
+	(315.17,164.10) --
+	(314.93,164.02) --
+	(314.61,163.92) --
+	(314.46,163.86) --
+	(314.39,163.83) --
+	(314.18,163.75) --
+	(313.56,163.59) --
+	(313.47,163.56) --
+	(312.98,163.44) --
+	(312.93,163.43) --
+	(311.41,163.01) --
+	(311.29,162.97) --
+	(310.97,162.86) --
+	(310.74,162.80) --
+	(310.65,162.79) --
+	(310.57,162.77) --
+	(310.04,162.61) --
+	(309.44,162.38) --
+	(309.39,162.37) --
+	(309.36,162.36) --
+	(309.24,162.34) --
+	(309.23,162.34) --
+	(309.07,162.31) --
+	(308.71,162.22) --
+	(308.22,162.06) --
+	(308.06,162.00) --
+	(307.76,161.88) --
+	(307.50,161.76) --
+	(307.38,161.70) --
+	(306.63,161.40) --
+	(306.03,161.19) --
+	(305.92,161.16) --
+	(304.46,160.70) --
+	(304.00,160.53) --
+	(303.79,160.51) --
+	(303.42,160.35) --
+	(303.19,160.23) --
+	(302.80,160.09) --
+	(302.80,160.09) --
+	(302.72,160.06) --
+	(302.62,160.03) --
+	(302.59,160.01) --
+	(302.55,160.00) --
+	(302.54,160.00) --
+	(302.51,159.98) --
+	(302.49,159.98) --
+	(302.17,159.86) --
+	(302.00,159.79) --
+	(301.73,159.71) --
+	(301.64,159.67) --
+	(301.54,159.63) --
+	(301.48,159.61) --
+	(301.08,159.53) --
+	(301.02,159.52) --
+	(300.83,159.48) --
+	(299.55,159.10) --
+	(298.88,158.93) --
+	(298.32,158.72) --
+	(298.21,158.66) --
+	(298.19,158.66) --
+	(298.13,158.62) --
+	(298.07,158.60) --
+	(297.93,158.55) --
+	(297.61,158.41) --
+	(297.55,158.38) --
+	(297.07,158.23) --
+	(296.96,158.20) --
+	(296.64,158.11) --
+	(296.54,158.10) --
+	(295.58,157.82) --
+	(295.07,157.63) --
+	(294.46,157.42) --
+	(294.42,157.41) --
+	(293.72,157.19) --
+	(293.19,157.02) --
+	(292.56,156.85) --
+	(292.53,156.84) --
+	(291.99,156.75) --
+	(291.16,156.46) --
+	(291.07,156.43) --
+	(290.90,156.37) --
+	(290.68,156.28) --
+	(290.15,156.09) --
+	(290.06,156.07) --
+	(289.98,156.04) --
+	(289.17,155.82) --
+	(288.93,155.75) --
+	(287.64,155.36) --
+	(287.56,155.32) --
+	(287.40,155.25) --
+	(287.11,155.16) --
+	(286.94,155.09) --
+	(286.76,155.04) --
+	(286.40,154.93) --
+	(285.96,154.73) --
+	(285.93,154.72) --
+	(285.79,154.65) --
+	(285.59,154.56) --
+	(285.47,154.54) --
+	(284.78,154.30) --
+	(284.38,154.16) --
+	(284.33,154.14) --
+	(283.67,153.90) --
+	(283.17,153.69) --
+	(282.73,153.53) --
+	(282.59,153.50) --
+	(282.56,153.49) --
+	(282.04,153.22) --
+	(281.75,153.16) --
+	(281.01,152.85) --
+	(280.17,152.58) --
+	(279.37,152.33) --
+	(278.99,152.24) --
+	(278.30,151.99) --
+	(277.74,151.83) --
+	(277.67,151.80) --
+	(276.57,151.29) --
+	(276.45,151.23) --
+	(275.85,150.95) --
+	(275.15,150.75) --
+	(274.51,150.62) --
+	(274.10,150.45) --
+	(273.30,150.09) --
+	(273.00,149.95) --
+	(272.97,149.94) --
+	(271.89,149.56) --
+	(271.47,149.38) --
+	(271.44,149.38) --
+	(271.24,149.28) --
+	(270.00,148.75) --
+	(269.50,148.57) --
+	(269.24,148.50) --
+	(269.02,148.44) --
+	(267.90,147.97) --
+	(267.27,147.77) --
+	(267.16,147.74) --
+	(265.81,147.22) --
+	(263.78,146.42) --
+	(263.62,146.35) --
+	(262.38,145.77) --
+	(262.27,145.73) --
+	(260.79,145.17) --
+	(260.56,145.05) --
+	(259.99,144.87) --
+	(259.38,144.57) --
+	(259.12,144.44) --
+	(258.74,144.28) --
+	(258.26,144.06) --
+	(257.71,143.89) --
+	(257.49,143.80) --
+	(256.77,143.49) --
+	(256.23,143.20) --
+	(255.67,143.00) --
+	(254.86,142.66) --
+	(254.85,142.65) --
+	(253.66,142.12) --
+	(252.68,141.77) --
+	(251.67,141.30) --
+	(250.77,140.91) --
+	(249.31,140.38) --
+	(248.75,140.16) --
+	(247.54,139.62) --
+	(246.54,139.15) --
+	(244.68,138.39) --
+	(241.36,136.98) --
+	(240.95,136.85) --
+	(240.90,136.83) --
+	(240.65,136.72) --
+	(239.94,136.44) --
+	(238.97,136.03) --
+	(238.27,135.71) --
+	(236.76,135.03) --
+	(235.50,134.47) --
+	(235.00,134.30) --
+	(233.22,133.55) --
+	(228.78,131.62) --
+	(228.32,131.44) --
+	(224.02,129.53) --
+	(222.43,128.74) --
+	(222.23,128.64) --
+	(220.60,127.76) --
+	(215.24,125.24) --
+	(213.69,124.40) --
+	(213.53,124.34) --
+	(212.89,124.01) --
+	(212.80,123.97) --
+	(212.10,123.55) --
+	(211.41,123.27) --
+	(209.87,122.48) --
+	(209.59,122.31) --
+	(205.06,119.98) --
+	(205.05,119.98) --
+	(195.56,115.19) --
+	(188.46,111.38) --
+	(185.97,110.03) --
+	(175.86,104.77) --
+	(174.96,104.36) --
+	(171.70,102.75) --
+	(171.57,102.68) --
+	(158.20, 95.45) --
+	(138.05, 84.52) --
+	(130.04, 80.01) --
+	(127.53, 78.54) --
+	(123.77, 76.37) --
+	(118.51, 73.39) --
+	(112.14, 69.76) --
+	(108.87, 67.97) --
+	(103.21, 64.72) --
+	( 94.75, 59.85) --
+	( 81.35, 52.16) --
+	( 81.21, 52.08) --
+	( 76.94, 49.62) --
+	( 69.26, 45.08) --
 	cycle;
@@
 
-\path[fill=fillColor,fill opacity=0.50] ( 57.05,165.69) --
-	( 62.08,166.26) --
-	( 67.11,166.92) --
-	( 72.14,167.65) --
-	( 77.17,168.34) --
-	( 82.20,169.03) --
-	( 87.23,169.66) --
-	( 92.27,170.38) --
-	( 97.30,171.07) --
-	(102.33,171.75) --
-	(107.36,172.44) --
-	(112.39,173.12) --
-	(117.42,173.84) --
-	(122.45,174.45) --
-	(127.49,175.12) --
-	(132.52,175.81) --
-	(137.55,176.59) --
-	(142.58,177.35) --
-	(147.61,178.25) --
-	(152.64,179.27) --
-	(157.67,180.18) --
-	(162.71,181.11) --
-	(167.74,181.96) --
-	(172.77,182.76) --
-	(177.80,183.71) --
-	(182.83,184.54) --
-	(187.86,185.47) --
-	(192.89,186.43) --
-	(197.93,187.51) --
-	(202.96,188.46) --
-	(207.99,189.58) --
-	(213.02,190.58) --
-	(218.05,191.75) --
-	(223.08,192.84) --
-	(228.12,194.00) --
-	(233.15,195.12) --
-	(238.18,196.45) --
-	(243.21,197.65) --
-	(248.24,199.02) --
-	(253.27,200.34) --
-	(258.30,201.75) --
-	(263.34,203.21) --
-	(268.37,204.61) --
-	(273.40,206.24) --
-	(278.43,207.82) --
-	(283.46,209.30) --
-	(288.49,210.93) --
-	(293.52,212.69) --
-	(298.56,214.53) --
-	(303.59,216.36) --
-	(308.62,218.21) --
-	(313.65,220.05) --
-	(318.68,222.00) --
-	(323.71,224.00) --
-	(328.74,225.95) --
-	(333.78,227.98) --
-	(338.81,230.07) --
-	(343.84,232.25) --
-	(348.87,234.41) --
-	(353.90,236.60) --
-	(358.93,238.76) --
-	(363.96,240.91) --
-	(369.00,243.13) --
-	(374.03,245.40) --
-	(379.06,247.74) --
-	(384.09,250.09) --
-	(389.12,252.61) --
-	(394.15,255.21) --
-	(399.18,257.56) --
-	(404.22,259.93) --
-	(404.22,192.89) --
-	(399.18,192.12) --
-	(394.15,191.18) --
-	(389.12,190.22) --
-	(384.09,189.28) --
-	(379.06,188.36) --
-	(374.03,187.32) --
-	(369.00,186.30) --
-	(363.96,185.20) --
-	(358.93,184.18) --
-	(353.90,182.99) --
-	(348.87,181.90) --
-	(343.84,180.64) --
-	(338.81,179.59) --
-	(333.78,178.30) --
-	(328.74,176.91) --
-	(323.71,175.49) --
-	(318.68,174.05) --
-	(313.65,172.59) --
-	(308.62,171.06) --
-	(303.59,169.50) --
-	(298.56,167.92) --
-	(293.52,166.28) --
-	(288.49,164.66) --
-	(283.46,162.97) --
-	(278.43,161.38) --
-	(273.40,159.49) --
-	(268.37,157.55) --
-	(263.34,155.74) --
-	(258.30,153.81) --
-	(253.27,151.84) --
-	(248.24,149.82) --
-	(243.21,147.69) --
-	(238.18,145.73) --
-	(233.15,143.60) --
-	(228.12,141.48) --
-	(223.08,139.15) --
-	(218.05,136.75) --
-	(213.02,134.58) --
-	(207.99,132.15) --
-	(202.96,129.81) --
-	(197.93,127.34) --
-	(192.89,124.90) --
-	(187.86,122.54) --
-	(182.83,119.97) --
-	(177.80,117.68) --
-	(172.77,115.15) --
-	(167.74,112.73) --
-	(162.71,110.22) --
-	(157.67,107.87) --
-	(152.64,105.34) --
-	(147.61,102.80) --
-	(142.58,100.16) --
-	(137.55, 97.55) --
-	(132.52, 94.94) --
-	(127.49, 92.32) --
-	(122.45, 89.72) --
-	(117.42, 87.08) --
-	(112.39, 84.45) --
-	(107.36, 81.80) --
-	(102.33, 79.16) --
-	( 97.30, 76.57) --
-	( 92.27, 74.01) --
-	( 87.23, 71.42) --
-	( 82.20, 68.63) --
-	( 77.17, 65.97) --
-	( 72.14, 63.37) --
-	( 67.11, 60.74) --
-	( 62.08, 58.05) --
-	( 57.05, 55.38) --
+\path[fill=fillColor,fill opacity=0.50] ( 69.26,162.69) --
+	( 76.94,163.86) --
+	( 81.21,164.49) --
+	( 81.35,164.51) --
+	( 94.75,166.70) --
+	(103.21,167.92) --
+	(108.87,168.87) --
+	(112.14,169.36) --
+	(118.51,170.37) --
+	(123.77,171.22) --
+	(127.53,171.70) --
+	(130.04,172.14) --
+	(138.05,173.52) --
+	(158.20,177.08) --
+	(171.57,179.46) --
+	(171.70,179.49) --
+	(174.96,180.16) --
+	(175.86,180.26) --
+	(185.97,182.09) --
+	(188.46,182.56) --
+	(195.56,184.04) --
+	(205.05,185.94) --
+	(205.06,185.94) --
+	(209.59,186.79) --
+	(209.87,186.84) --
+	(211.41,187.13) --
+	(212.10,187.25) --
+	(212.80,187.40) --
+	(212.89,187.41) --
+	(213.53,187.51) --
+	(213.69,187.55) --
+	(215.24,187.91) --
+	(220.60,189.21) --
+	(222.23,189.53) --
+	(222.43,189.58) --
+	(224.02,189.88) --
+	(228.32,190.86) --
+	(228.78,190.94) --
+	(233.22,192.19) --
+	(235.00,192.66) --
+	(235.50,192.79) --
+	(236.76,193.15) --
+	(238.27,193.50) --
+	(238.97,193.69) --
+	(239.94,193.90) --
+	(240.65,194.05) --
+	(240.90,194.11) --
+	(240.95,194.13) --
+	(241.36,194.25) --
+	(244.68,195.12) --
+	(246.54,195.56) --
+	(247.54,195.84) --
+	(248.75,196.16) --
+	(249.31,196.34) --
+	(250.77,196.74) --
+	(251.67,197.02) --
+	(252.68,197.28) --
+	(253.66,197.57) --
+	(254.85,197.95) --
+	(254.86,197.95) --
+	(255.67,198.20) --
+	(256.23,198.38) --
+	(256.77,198.52) --
+	(257.49,198.70) --
+	(257.71,198.75) --
+	(258.26,198.88) --
+	(258.74,199.00) --
+	(259.12,199.11) --
+	(259.38,199.21) --
+	(259.99,199.39) --
+	(260.56,199.55) --
+	(260.79,199.64) --
+	(262.27,200.15) --
+	(262.38,200.20) --
+	(263.62,200.57) --
+	(263.78,200.65) --
+	(265.81,201.31) --
+	(267.16,201.67) --
+	(267.27,201.70) --
+	(267.90,201.87) --
+	(269.02,202.14) --
+	(269.24,202.18) --
+	(269.50,202.25) --
+	(270.00,202.43) --
+	(271.24,202.77) --
+	(271.44,202.85) --
+	(271.47,202.86) --
+	(271.89,202.98) --
+	(272.97,203.23) --
+	(273.00,203.24) --
+	(273.30,203.29) --
+	(274.10,203.53) --
+	(274.51,203.67) --
+	(275.15,203.94) --
+	(275.85,204.13) --
+	(276.45,204.30) --
+	(276.57,204.32) --
+	(277.67,204.64) --
+	(277.74,204.66) --
+	(278.30,204.87) --
+	(278.99,205.11) --
+	(279.37,205.22) --
+	(280.17,205.50) --
+	(281.01,205.81) --
+	(281.75,206.07) --
+	(282.04,206.16) --
+	(282.56,206.35) --
+	(282.59,206.36) --
+	(282.73,206.41) --
+	(283.17,206.58) --
+	(283.67,206.75) --
+	(284.33,206.98) --
+	(284.38,207.00) --
+	(284.78,207.17) --
+	(285.47,207.40) --
+	(285.59,207.43) --
+	(285.79,207.48) --
+	(285.93,207.52) --
+	(285.96,207.53) --
+	(286.40,207.71) --
+	(286.76,207.81) --
+	(286.94,207.90) --
+	(287.11,207.95) --
+	(287.40,208.07) --
+	(287.56,208.10) --
+	(287.64,208.13) --
+	(288.93,208.48) --
+	(289.17,208.54) --
+	(289.98,208.82) --
+	(290.06,208.86) --
+	(290.15,208.88) --
+	(290.68,209.05) --
+	(290.90,209.11) --
+	(291.07,209.16) --
+	(291.16,209.18) --
+	(291.99,209.47) --
+	(292.53,209.68) --
+	(292.56,209.68) --
+	(293.19,209.95) --
+	(293.72,210.12) --
+	(294.42,210.36) --
+	(294.46,210.38) --
+	(295.07,210.61) --
+	(295.58,210.83) --
+	(296.54,211.25) --
+	(296.64,211.30) --
+	(296.96,211.44) --
+	(297.07,211.49) --
+	(297.55,211.64) --
+	(297.61,211.66) --
+	(297.93,211.79) --
+	(298.07,211.84) --
+	(298.13,211.86) --
+	(298.19,211.88) --
+	(298.21,211.88) --
+	(298.32,211.91) --
+	(298.88,212.06) --
+	(299.55,212.34) --
+	(300.83,212.79) --
+	(301.02,212.84) --
+	(301.08,212.86) --
+	(301.48,212.99) --
+	(301.54,213.01) --
+	(301.64,213.04) --
+	(301.73,213.07) --
+	(302.00,213.13) --
+	(302.17,213.19) --
+	(302.49,213.31) --
+	(302.51,213.32) --
+	(302.54,213.33) --
+	(302.55,213.33) --
+	(302.59,213.34) --
+	(302.62,213.35) --
+	(302.72,213.37) --
+	(302.80,213.40) --
+	(302.80,213.40) --
+	(303.19,213.59) --
+	(303.42,213.69) --
+	(303.79,213.78) --
+	(304.00,213.85) --
+	(304.46,214.02) --
+	(305.92,214.57) --
+	(306.03,214.62) --
+	(306.63,214.86) --
+	(307.38,215.16) --
+	(307.50,215.19) --
+	(307.76,215.29) --
+	(308.06,215.37) --
+	(308.22,215.41) --
+	(308.71,215.58) --
+	(309.07,215.76) --
+	(309.23,215.83) --
+	(309.24,215.83) --
+	(309.36,215.86) --
+	(309.39,215.87) --
+	(309.44,215.89) --
+	(310.04,216.08) --
+	(310.57,216.34) --
+	(310.65,216.38) --
+	(310.74,216.42) --
+	(310.97,216.52) --
+	(311.29,216.64) --
+	(311.41,216.70) --
+	(312.93,217.33) --
+	(312.98,217.35) --
+	(313.47,217.50) --
+	(313.56,217.54) --
+	(314.18,217.74) --
+	(314.39,217.80) --
+	(314.46,217.82) --
+	(314.61,217.89) --
+	(314.93,218.08) --
+	(315.17,218.17) --
+	(315.66,218.43) --
+	(315.81,218.48) --
+	(315.92,218.51) --
+	(316.04,218.55) --
+	(316.27,218.63) --
+	(316.28,218.63) --
+	(316.31,218.64) --
+	(316.40,218.67) --
+	(316.53,218.73) --
+	(316.54,218.74) --
+	(316.73,218.82) --
+	(316.73,218.83) --
+	(317.05,218.99) --
+	(317.72,219.22) --
+	(317.91,219.30) --
+	(318.05,219.35) --
+	(318.31,219.45) --
+	(318.59,219.60) --
+	(318.98,219.81) --
+	(319.05,219.85) --
+	(319.19,219.89) --
+	(319.36,219.93) --
+	(319.71,220.04) --
+	(319.91,220.14) --
+	(319.93,220.15) --
+	(320.06,220.21) --
+	(320.17,220.24) --
+	(320.20,220.24) --
+	(320.30,220.28) --
+	(320.38,220.31) --
+	(320.46,220.35) --
+	(320.79,220.45) --
+	(320.87,220.47) --
+	(321.03,220.52) --
+	(321.25,220.63) --
+	(321.56,220.77) --
+	(321.69,220.83) --
+	(321.81,220.87) --
+	(321.97,220.93) --
+	(322.34,221.05) --
+	(322.35,221.06) --
+	(322.38,221.06) --
+	(322.44,221.08) --
+	(322.47,221.09) --
+	(322.55,221.12) --
+	(322.98,221.32) --
+	(323.15,221.38) --
+	(323.39,221.47) --
+	(323.51,221.54) --
+	(323.64,221.60) --
+	(323.74,221.65) --
+	(324.03,221.78) --
+	(324.31,221.90) --
+	(324.91,222.19) --
+	(326.25,222.75) --
+	(326.31,222.77) --
+	(326.44,222.85) --
+	(326.69,222.97) --
+	(326.98,223.07) --
+	(327.12,223.12) --
+	(327.38,223.22) --
+	(327.45,223.25) --
+	(327.62,223.32) --
+	(328.36,223.62) --
+	(328.71,223.74) --
+	(328.89,223.84) --
+	(329.00,223.88) --
+	(329.34,224.03) --
+	(330.21,224.37) --
+	(330.77,224.65) --
+	(330.92,224.71) --
+	(331.77,224.99) --
+	(332.05,225.10) --
+	(332.77,225.35) --
+	(333.03,225.45) --
+	(333.16,225.52) --
+	(333.59,225.70) --
+	(335.17,226.36) --
+	(335.96,226.68) --
+	(336.21,226.79) --
+	(336.98,227.14) --
+	(337.10,227.18) --
+	(337.64,227.38) --
+	(339.32,228.03) --
+	(339.85,228.20) --
+	(340.50,228.45) --
+	(340.63,228.52) --
+	(341.25,228.77) --
+	(341.62,228.90) --
+	(341.97,229.05) --
+	(342.00,229.06) --
+	(342.05,229.08) --
+	(342.45,229.24) --
+	(342.53,229.28) --
+	(343.04,229.50) --
+	(343.17,229.54) --
+	(343.85,229.85) --
+	(343.87,229.86) --
+	(343.95,229.87) --
+	(344.16,229.97) --
+	(344.46,230.12) --
+	(344.63,230.20) --
+	(344.93,230.36) --
+	(345.02,230.39) --
+	(345.07,230.42) --
+	(345.10,230.43) --
+	(345.51,230.61) --
+	(345.57,230.63) --
+	(346.09,230.84) --
+	(346.39,230.97) --
+	(347.80,231.60) --
+	(348.20,231.77) --
+	(348.41,231.82) --
+	(348.87,232.01) --
+	(348.92,232.02) --
+	(349.60,232.28) --
+	(351.33,233.12) --
+	(351.43,233.18) --
+	(351.56,233.22) --
+	(351.74,233.28) --
+	(351.87,233.36) --
+	(353.20,233.97) --
+	(353.44,234.08) --
+	(353.54,234.11) --
+	(354.59,234.56) --
+	(357.17,235.70) --
+	(357.38,235.79) --
+	(357.90,235.98) --
+	(357.93,236.00) --
+	(358.21,236.08) --
+	(358.75,236.31) --
+	(359.57,236.60) --
+	(359.62,236.62) --
+	(360.33,237.04) --
+	(360.36,237.05) --
+	(360.85,237.22) --
+	(361.40,237.45) --
+	(362.06,237.74) --
+	(362.35,237.87) --
+	(362.48,237.93) --
+	(362.58,237.98) --
+	(363.30,238.32) --
+	(363.33,238.34) --
+	(363.40,238.37) --
+	(364.54,238.92) --
+	(365.21,239.23) --
+	(366.77,239.98) --
+	(366.99,240.10) --
+	(368.17,240.64) --
+	(368.73,240.88) --
+	(372.78,242.85) --
+	(373.25,243.04) --
+	(374.25,243.52) --
+	(374.25,243.53) --
+	(374.55,243.71) --
+	(374.76,243.79) --
+	(375.05,243.91) --
+	(375.30,244.01) --
+	(375.66,244.18) --
+	(375.91,244.31) --
+	(376.54,244.60) --
+	(376.88,244.76) --
+	(377.80,245.25) --
+	(378.36,245.52) --
+	(378.50,245.59) --
+	(378.91,245.79) --
+	(379.95,246.29) --
+	(381.22,246.90) --
+	(381.23,246.90) --
+	(381.92,247.24) --
+	(381.95,247.25) --
+	(382.82,247.67) --
+	(383.24,247.86) --
+	(383.51,248.01) --
+	(384.09,248.23) --
+	(384.17,248.29) --
+	(384.29,248.34) --
+	(384.73,248.57) --
+	(386.66,249.57) --
+	(386.77,249.61) --
+	(390.32,251.41) --
+	(394.80,253.54) --
+	(396.85,254.58) --
+	(404.07,257.98) --
+	(404.80,258.32) --
+	(404.80,189.64) --
+	(404.07,189.50) --
+	(396.85,188.00) --
+	(394.80,187.59) --
+	(390.32,186.83) --
+	(386.77,186.36) --
+	(386.66,186.36) --
+	(384.73,185.98) --
+	(384.29,185.90) --
+	(384.17,185.88) --
+	(384.09,185.87) --
+	(383.51,185.77) --
+	(383.24,185.74) --
+	(382.82,185.65) --
+	(381.95,185.48) --
+	(381.92,185.47) --
+	(381.23,185.34) --
+	(381.22,185.34) --
+	(379.95,185.10) --
+	(378.91,184.79) --
+	(378.50,184.70) --
+	(378.36,184.66) --
+	(377.80,184.56) --
+	(376.88,184.37) --
+	(376.54,184.29) --
+	(375.91,184.19) --
+	(375.66,184.15) --
+	(375.30,184.06) --
+	(375.05,184.03) --
+	(374.76,183.96) --
+	(374.55,183.91) --
+	(374.25,183.85) --
+	(374.25,183.85) --
+	(373.25,183.61) --
+	(372.78,183.51) --
+	(368.73,182.59) --
+	(368.17,182.50) --
+	(366.99,182.24) --
+	(366.77,182.20) --
+	(365.21,181.90) --
+	(364.54,181.78) --
+	(363.40,181.57) --
+	(363.33,181.55) --
+	(363.30,181.54) --
+	(362.58,181.32) --
+	(362.48,181.30) --
+	(362.35,181.27) --
+	(362.06,181.18) --
+	(361.40,181.08) --
+	(360.85,180.92) --
+	(360.36,180.79) --
+	(360.33,180.78) --
+	(359.62,180.60) --
+	(359.57,180.58) --
+	(358.75,180.41) --
+	(358.21,180.32) --
+	(357.93,180.28) --
+	(357.90,180.27) --
+	(357.38,180.13) --
+	(357.17,180.06) --
+	(354.59,179.48) --
+	(353.54,179.19) --
+	(353.44,179.17) --
+	(353.20,179.12) --
+	(351.87,178.72) --
+	(351.74,178.69) --
+	(351.56,178.65) --
+	(351.43,178.61) --
+	(351.33,178.58) --
+	(349.60,178.18) --
+	(348.92,177.96) --
+	(348.87,177.94) --
+	(348.41,177.84) --
+	(348.20,177.79) --
+	(347.80,177.68) --
+	(346.39,177.30) --
+	(346.09,177.23) --
+	(345.57,177.09) --
+	(345.51,177.07) --
+	(345.10,176.98) --
+	(345.07,176.97) --
+	(345.02,176.96) --
+	(344.93,176.96) --
+	(344.63,176.89) --
+	(344.46,176.83) --
+	(344.16,176.75) --
+	(343.95,176.68) --
+	(343.87,176.67) --
+	(343.85,176.67) --
+	(343.17,176.56) --
+	(343.04,176.53) --
+	(342.53,176.35) --
+	(342.45,176.33) --
+	(342.05,176.22) --
+	(342.00,176.20) --
+	(341.97,176.19) --
+	(341.62,176.12) --
+	(341.25,176.04) --
+	(340.63,175.87) --
+	(340.50,175.83) --
+	(339.85,175.63) --
+	(339.32,175.51) --
+	(337.64,175.18) --
+	(337.10,175.07) --
+	(336.98,175.03) --
+	(336.21,174.86) --
+	(335.96,174.80) --
+	(335.17,174.60) --
+	(333.59,174.17) --
+	(333.16,174.04) --
+	(333.03,174.01) --
+	(332.77,173.95) --
+	(332.05,173.81) --
+	(331.77,173.77) --
+	(330.92,173.51) --
+	(330.77,173.45) --
+	(330.21,173.33) --
+	(329.34,172.99) --
+	(329.00,172.89) --
+	(328.89,172.87) --
+	(328.71,172.79) --
+	(328.36,172.72) --
+	(327.62,172.54) --
+	(327.45,172.47) --
+	(327.38,172.46) --
+	(327.12,172.39) --
+	(326.98,172.34) --
+	(326.69,172.26) --
+	(326.44,172.25) --
+	(326.31,172.21) --
+	(326.25,172.19) --
+	(324.91,171.82) --
+	(324.31,171.68) --
+	(324.03,171.60) --
+	(323.74,171.54) --
+	(323.64,171.51) --
+	(323.51,171.46) --
+	(323.39,171.42) --
+	(323.15,171.32) --
+	(322.98,171.25) --
+	(322.55,171.10) --
+	(322.47,171.07) --
+	(322.44,171.06) --
+	(322.38,171.05) --
+	(322.35,171.04) --
+	(322.34,171.04) --
+	(321.97,170.92) --
+	(321.81,170.88) --
+	(321.69,170.84) --
+	(321.56,170.80) --
+	(321.25,170.71) --
+	(321.03,170.65) --
+	(320.87,170.61) --
+	(320.79,170.59) --
+	(320.46,170.48) --
+	(320.38,170.46) --
+	(320.30,170.44) --
+	(320.20,170.41) --
+	(320.17,170.41) --
+	(320.06,170.37) --
+	(319.93,170.32) --
+	(319.91,170.31) --
+	(319.71,170.26) --
+	(319.36,170.17) --
+	(319.19,170.11) --
+	(319.05,170.05) --
+	(318.98,170.02) --
+	(318.59,169.91) --
+	(318.31,169.82) --
+	(318.05,169.74) --
+	(317.91,169.70) --
+	(317.72,169.65) --
+	(317.05,169.42) --
+	(316.73,169.34) --
+	(316.73,169.34) --
+	(316.54,169.30) --
+	(316.53,169.30) --
+	(316.40,169.27) --
+	(316.31,169.24) --
+	(316.28,169.23) --
+	(316.27,169.22) --
+	(316.04,169.15) --
+	(315.92,169.11) --
+	(315.81,169.07) --
+	(315.66,169.02) --
+	(315.17,168.87) --
+	(314.93,168.80) --
+	(314.61,168.70) --
+	(314.46,168.64) --
+	(314.39,168.61) --
+	(314.18,168.54) --
+	(313.56,168.33) --
+	(313.47,168.29) --
+	(312.98,168.12) --
+	(312.93,168.10) --
+	(311.41,167.66) --
+	(311.29,167.62) --
+	(310.97,167.57) --
+	(310.74,167.49) --
+	(310.65,167.48) --
+	(310.57,167.46) --
+	(310.04,167.25) --
+	(309.44,167.10) --
+	(309.39,167.09) --
+	(309.36,167.07) --
+	(309.24,167.03) --
+	(309.23,167.03) --
+	(309.07,166.97) --
+	(308.71,166.82) --
+	(308.22,166.66) --
+	(308.06,166.62) --
+	(307.76,166.54) --
+	(307.50,166.45) --
+	(307.38,166.41) --
+	(306.63,166.19) --
+	(306.03,165.97) --
+	(305.92,165.94) --
+	(304.46,165.44) --
+	(304.00,165.34) --
+	(303.79,165.28) --
+	(303.42,165.16) --
+	(303.19,165.08) --
+	(302.80,164.97) --
+	(302.80,164.97) --
+	(302.72,164.95) --
+	(302.62,164.92) --
+	(302.59,164.91) --
+	(302.55,164.90) --
+	(302.54,164.90) --
+	(302.51,164.89) --
+	(302.49,164.88) --
+	(302.17,164.79) --
+	(302.00,164.74) --
+	(301.73,164.67) --
+	(301.64,164.65) --
+	(301.54,164.62) --
+	(301.48,164.61) --
+	(301.08,164.50) --
+	(301.02,164.48) --
+	(300.83,164.41) --
+	(299.55,163.99) --
+	(298.88,163.70) --
+	(298.32,163.50) --
+	(298.21,163.45) --
+	(298.19,163.45) --
+	(298.13,163.43) --
+	(298.07,163.41) --
+	(297.93,163.34) --
+	(297.61,163.23) --
+	(297.55,163.21) --
+	(297.07,163.03) --
+	(296.96,163.00) --
+	(296.64,162.91) --
+	(296.54,162.88) --
+	(295.58,162.53) --
+	(295.07,162.36) --
+	(294.46,162.18) --
+	(294.42,162.18) --
+	(293.72,161.95) --
+	(293.19,161.77) --
+	(292.56,161.53) --
+	(292.53,161.52) --
+	(291.99,161.37) --
+	(291.16,161.08) --
+	(291.07,161.06) --
+	(290.90,160.99) --
+	(290.68,160.94) --
+	(290.15,160.77) --
+	(290.06,160.74) --
+	(289.98,160.71) --
+	(289.17,160.47) --
+	(288.93,160.43) --
+	(287.64,159.98) --
+	(287.56,159.96) --
+	(287.40,159.91) --
+	(287.11,159.83) --
+	(286.94,159.78) --
+	(286.76,159.73) --
+	(286.40,159.61) --
+	(285.96,159.45) --
+	(285.93,159.44) --
+	(285.79,159.39) --
+	(285.59,159.31) --
+	(285.47,159.26) --
+	(284.78,159.01) --
+	(284.38,158.87) --
+	(284.33,158.84) --
+	(283.67,158.61) --
+	(283.17,158.41) --
+	(282.73,158.24) --
+	(282.59,158.19) --
+	(282.56,158.18) --
+	(282.04,158.00) --
+	(281.75,157.91) --
+	(281.01,157.60) --
+	(280.17,157.31) --
+	(279.37,157.02) --
+	(278.99,156.86) --
+	(278.30,156.58) --
+	(277.74,156.39) --
+	(277.67,156.37) --
+	(276.57,156.01) --
+	(276.45,155.98) --
+	(275.85,155.79) --
+	(275.15,155.49) --
+	(274.51,155.32) --
+	(274.10,155.21) --
+	(273.30,154.88) --
+	(273.00,154.78) --
+	(272.97,154.77) --
+	(271.89,154.37) --
+	(271.47,154.17) --
+	(271.44,154.15) --
+	(271.24,154.06) --
+	(270.00,153.51) --
+	(269.50,153.33) --
+	(269.24,153.19) --
+	(269.02,153.08) --
+	(267.90,152.64) --
+	(267.27,152.43) --
+	(267.16,152.39) --
+	(265.81,151.89) --
+	(263.78,151.02) --
+	(263.62,150.94) --
+	(262.38,150.41) --
+	(262.27,150.37) --
+	(260.79,149.85) --
+	(260.56,149.75) --
+	(259.99,149.51) --
+	(259.38,149.23) --
+	(259.12,149.14) --
+	(258.74,148.98) --
+	(258.26,148.80) --
+	(257.71,148.57) --
+	(257.49,148.48) --
+	(256.77,148.18) --
+	(256.23,147.96) --
+	(255.67,147.76) --
+	(254.86,147.39) --
+	(254.85,147.39) --
+	(253.66,146.86) --
+	(252.68,146.41) --
+	(251.67,146.06) --
+	(250.77,145.70) --
+	(249.31,145.09) --
+	(248.75,144.87) --
+	(247.54,144.32) --
+	(246.54,143.90) --
+	(244.68,143.00) --
+	(241.36,141.60) --
+	(240.95,141.37) --
+	(240.90,141.35) --
+	(240.65,141.25) --
+	(239.94,140.97) --
+	(238.97,140.59) --
+	(238.27,140.29) --
+	(236.76,139.59) --
+	(235.50,139.08) --
+	(235.00,138.89) --
+	(233.22,138.10) --
+	(228.78,136.06) --
+	(228.32,135.82) --
+	(224.02,133.94) --
+	(222.43,133.19) --
+	(222.23,133.10) --
+	(220.60,132.33) --
+	(215.24,129.80) --
+	(213.69,129.08) --
+	(213.53,129.01) --
+	(212.89,128.71) --
+	(212.80,128.67) --
+	(212.10,128.34) --
+	(211.41,128.11) --
+	(209.87,127.43) --
+	(209.59,127.31) --
+	(205.06,125.25) --
+	(205.05,125.25) --
+	(195.56,120.80) --
+	(188.46,117.41) --
+	(185.97,116.14) --
+	(175.86,111.07) --
+	(174.96,110.63) --
+	(171.70,108.95) --
+	(171.57,108.88) --
+	(158.20,102.11) --
+	(138.05, 91.81) --
+	(130.04, 87.70) --
+	(127.53, 86.38) --
+	(123.77, 84.36) --
+	(118.51, 81.72) --
+	(112.14, 78.35) --
+	(108.87, 76.65) --
+	(103.21, 73.60) --
+	( 94.75, 69.16) --
+	( 81.35, 62.32) --
+	( 81.21, 62.25) --
+	( 76.94, 59.97) --
+	( 69.26, 55.82) --
 	cycle;
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 69.26, 34.03) -- ( 69.26, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 76.94, 34.03) -- ( 76.94, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 81.21, 34.03) -- ( 81.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 81.35, 34.03) -- ( 81.35, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 94.75, 34.03) -- ( 94.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (103.21, 34.03) -- (103.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (108.87, 34.03) -- (108.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (112.14, 34.03) -- (112.14, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (118.51, 34.03) -- (118.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (123.77, 34.03) -- (123.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (127.53, 34.03) -- (127.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (130.04, 34.03) -- (130.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (138.05, 34.03) -- (138.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (158.20, 34.03) -- (158.20, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (171.57, 34.03) -- (171.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (171.70, 34.03) -- (171.70, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (174.96, 34.03) -- (174.96, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (175.86, 34.03) -- (175.86, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (185.97, 34.03) -- (185.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (188.46, 34.03) -- (188.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (195.56, 34.03) -- (195.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (205.05, 34.03) -- (205.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (205.06, 34.03) -- (205.06, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (209.59, 34.03) -- (209.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (209.87, 34.03) -- (209.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (211.41, 34.03) -- (211.41, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (212.10, 34.03) -- (212.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (212.80, 34.03) -- (212.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (212.89, 34.03) -- (212.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (213.53, 34.03) -- (213.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (213.69, 34.03) -- (213.69, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (215.24, 34.03) -- (215.24, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (220.60, 34.03) -- (220.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (222.23, 34.03) -- (222.23, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (222.43, 34.03) -- (222.43, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (224.02, 34.03) -- (224.02, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (228.32, 34.03) -- (228.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (228.78, 34.03) -- (228.78, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (233.22, 34.03) -- (233.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (235.00, 34.03) -- (235.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (235.50, 34.03) -- (235.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (236.76, 34.03) -- (236.76, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (238.27, 34.03) -- (238.27, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (238.97, 34.03) -- (238.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (239.94, 34.03) -- (239.94, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (240.65, 34.03) -- (240.65, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (240.90, 34.03) -- (240.90, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (240.95, 34.03) -- (240.95, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (241.36, 34.03) -- (241.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (244.68, 34.03) -- (244.68, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (246.54, 34.03) -- (246.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (247.54, 34.03) -- (247.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (248.75, 34.03) -- (248.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (249.31, 34.03) -- (249.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (250.77, 34.03) -- (250.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.67, 34.03) -- (251.67, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (252.68, 34.03) -- (252.68, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (253.66, 34.03) -- (253.66, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (254.85, 34.03) -- (254.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (254.86, 34.03) -- (254.86, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (255.67, 34.03) -- (255.67, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (256.23, 34.03) -- (256.23, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (256.77, 34.03) -- (256.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (257.49, 34.03) -- (257.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (257.71, 34.03) -- (257.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (258.26, 34.03) -- (258.26, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (258.74, 34.03) -- (258.74, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (259.12, 34.03) -- (259.12, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (259.38, 34.03) -- (259.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (259.99, 34.03) -- (259.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (260.56, 34.03) -- (260.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (260.79, 34.03) -- (260.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (262.27, 34.03) -- (262.27, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (262.38, 34.03) -- (262.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (263.62, 34.03) -- (263.62, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (263.78, 34.03) -- (263.78, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (265.81, 34.03) -- (265.81, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.16, 34.03) -- (267.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.27, 34.03) -- (267.27, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.90, 34.03) -- (267.90, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (269.02, 34.03) -- (269.02, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (269.24, 34.03) -- (269.24, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (269.50, 34.03) -- (269.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (270.00, 34.03) -- (270.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.24, 34.03) -- (271.24, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.44, 34.03) -- (271.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.47, 34.03) -- (271.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.89, 34.03) -- (271.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (272.97, 34.03) -- (272.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (273.00, 34.03) -- (273.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (273.30, 34.03) -- (273.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (274.10, 34.03) -- (274.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (274.51, 34.03) -- (274.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (275.15, 34.03) -- (275.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (275.85, 34.03) -- (275.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (276.45, 34.03) -- (276.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (276.57, 34.03) -- (276.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (277.67, 34.03) -- (277.67, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (277.74, 34.03) -- (277.74, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (278.30, 34.03) -- (278.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (278.99, 34.03) -- (278.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (279.37, 34.03) -- (279.37, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (280.17, 34.03) -- (280.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (281.01, 34.03) -- (281.01, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (281.75, 34.03) -- (281.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (282.04, 34.03) -- (282.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (282.56, 34.03) -- (282.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (282.59, 34.03) -- (282.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (282.73, 34.03) -- (282.73, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.17, 34.03) -- (283.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.67, 34.03) -- (283.67, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.33, 34.03) -- (284.33, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.38, 34.03) -- (284.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.78, 34.03) -- (284.78, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.47, 34.03) -- (285.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.59, 34.03) -- (285.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.79, 34.03) -- (285.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.93, 34.03) -- (285.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.96, 34.03) -- (285.96, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.40, 34.03) -- (286.40, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.76, 34.03) -- (286.76, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.94, 34.03) -- (286.94, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (287.11, 34.03) -- (287.11, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (287.40, 34.03) -- (287.40, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (287.56, 34.03) -- (287.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (287.64, 34.03) -- (287.64, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (288.93, 34.03) -- (288.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (289.17, 34.03) -- (289.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (289.98, 34.03) -- (289.98, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.06, 34.03) -- (290.06, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.15, 34.03) -- (290.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.68, 34.03) -- (290.68, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.90, 34.03) -- (290.90, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (291.07, 34.03) -- (291.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (291.16, 34.03) -- (291.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (291.99, 34.03) -- (291.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.53, 34.03) -- (292.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.56, 34.03) -- (292.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (293.19, 34.03) -- (293.19, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (293.72, 34.03) -- (293.72, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.42, 34.03) -- (294.42, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.46, 34.03) -- (294.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (295.07, 34.03) -- (295.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (295.58, 34.03) -- (295.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (296.54, 34.03) -- (296.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (296.64, 34.03) -- (296.64, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (296.96, 34.03) -- (296.96, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.07, 34.03) -- (297.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.55, 34.03) -- (297.55, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.61, 34.03) -- (297.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.93, 34.03) -- (297.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.07, 34.03) -- (298.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.13, 34.03) -- (298.13, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.19, 34.03) -- (298.19, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.21, 34.03) -- (298.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.32, 34.03) -- (298.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.88, 34.03) -- (298.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.55, 34.03) -- (299.55, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (300.83, 34.03) -- (300.83, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (301.02, 34.03) -- (301.02, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (301.08, 34.03) -- (301.08, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (301.48, 34.03) -- (301.48, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (301.54, 34.03) -- (301.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (301.64, 34.03) -- (301.64, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (301.73, 34.03) -- (301.73, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.00, 34.03) -- (302.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.17, 34.03) -- (302.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.49, 34.03) -- (302.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.51, 34.03) -- (302.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.54, 34.03) -- (302.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.55, 34.03) -- (302.55, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.59, 34.03) -- (302.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.62, 34.03) -- (302.62, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.72, 34.03) -- (302.72, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.80, 34.03) -- (302.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.80, 34.03) -- (302.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (303.19, 34.03) -- (303.19, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (303.42, 34.03) -- (303.42, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (303.79, 34.03) -- (303.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.00, 34.03) -- (304.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.46, 34.03) -- (304.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (305.92, 34.03) -- (305.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (306.03, 34.03) -- (306.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (306.63, 34.03) -- (306.63, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.38, 34.03) -- (307.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.50, 34.03) -- (307.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.76, 34.03) -- (307.76, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (308.06, 34.03) -- (308.06, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (308.22, 34.03) -- (308.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (308.71, 34.03) -- (308.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.07, 34.03) -- (309.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.23, 34.03) -- (309.23, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.24, 34.03) -- (309.24, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.36, 34.03) -- (309.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.39, 34.03) -- (309.39, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.44, 34.03) -- (309.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.04, 34.03) -- (310.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.57, 34.03) -- (310.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.65, 34.03) -- (310.65, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.74, 34.03) -- (310.74, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.97, 34.03) -- (310.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.29, 34.03) -- (311.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.41, 34.03) -- (311.41, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (312.93, 34.03) -- (312.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (312.98, 34.03) -- (312.98, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (313.47, 34.03) -- (313.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (313.56, 34.03) -- (313.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.18, 34.03) -- (314.18, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.39, 34.03) -- (314.39, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.46, 34.03) -- (314.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.61, 34.03) -- (314.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.93, 34.03) -- (314.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.17, 34.03) -- (315.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.66, 34.03) -- (315.66, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.81, 34.03) -- (315.81, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.92, 34.03) -- (315.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.04, 34.03) -- (316.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.27, 34.03) -- (316.27, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.28, 34.03) -- (316.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.31, 34.03) -- (316.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.40, 34.03) -- (316.40, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.53, 34.03) -- (316.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.54, 34.03) -- (316.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.73, 34.03) -- (316.73, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.73, 34.03) -- (316.73, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.05, 34.03) -- (317.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.72, 34.03) -- (317.72, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.91, 34.03) -- (317.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (318.05, 34.03) -- (318.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (318.31, 34.03) -- (318.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (318.59, 34.03) -- (318.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (318.98, 34.03) -- (318.98, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.05, 34.03) -- (319.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.19, 34.03) -- (319.19, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.36, 34.03) -- (319.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.71, 34.03) -- (319.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.91, 34.03) -- (319.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.93, 34.03) -- (319.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.06, 34.03) -- (320.06, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.17, 34.03) -- (320.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.20, 34.03) -- (320.20, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.30, 34.03) -- (320.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.38, 34.03) -- (320.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.46, 34.03) -- (320.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.79, 34.03) -- (320.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.87, 34.03) -- (320.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.03, 34.03) -- (321.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.25, 34.03) -- (321.25, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.56, 34.03) -- (321.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.69, 34.03) -- (321.69, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.81, 34.03) -- (321.81, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.97, 34.03) -- (321.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (322.34, 34.03) -- (322.34, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (322.35, 34.03) -- (322.35, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (322.38, 34.03) -- (322.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (322.44, 34.03) -- (322.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (322.47, 34.03) -- (322.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (322.55, 34.03) -- (322.55, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (322.98, 34.03) -- (322.98, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (323.15, 34.03) -- (323.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (323.39, 34.03) -- (323.39, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (323.51, 34.03) -- (323.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (323.64, 34.03) -- (323.64, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (323.74, 34.03) -- (323.74, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (324.03, 34.03) -- (324.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (324.31, 34.03) -- (324.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (324.91, 34.03) -- (324.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (326.25, 34.03) -- (326.25, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (326.31, 34.03) -- (326.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (326.44, 34.03) -- (326.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (326.69, 34.03) -- (326.69, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (326.98, 34.03) -- (326.98, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (327.12, 34.03) -- (327.12, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (327.38, 34.03) -- (327.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (327.45, 34.03) -- (327.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (327.62, 34.03) -- (327.62, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (328.36, 34.03) -- (328.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (328.71, 34.03) -- (328.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (328.89, 34.03) -- (328.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (329.00, 34.03) -- (329.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (329.34, 34.03) -- (329.34, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (330.21, 34.03) -- (330.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (330.77, 34.03) -- (330.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (330.92, 34.03) -- (330.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (331.77, 34.03) -- (331.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (332.05, 34.03) -- (332.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (332.77, 34.03) -- (332.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (333.03, 34.03) -- (333.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (333.16, 34.03) -- (333.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (333.59, 34.03) -- (333.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (335.17, 34.03) -- (335.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (335.96, 34.03) -- (335.96, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (336.21, 34.03) -- (336.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (336.98, 34.03) -- (336.98, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (337.10, 34.03) -- (337.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (337.64, 34.03) -- (337.64, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (339.32, 34.03) -- (339.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (339.85, 34.03) -- (339.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (340.50, 34.03) -- (340.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (340.63, 34.03) -- (340.63, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (341.25, 34.03) -- (341.25, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (341.62, 34.03) -- (341.62, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (341.97, 34.03) -- (341.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.00, 34.03) -- (342.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.05, 34.03) -- (342.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.45, 34.03) -- (342.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.53, 34.03) -- (342.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (343.04, 34.03) -- (343.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (343.17, 34.03) -- (343.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (343.85, 34.03) -- (343.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (343.87, 34.03) -- (343.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (343.95, 34.03) -- (343.95, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (344.16, 34.03) -- (344.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (344.46, 34.03) -- (344.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (344.63, 34.03) -- (344.63, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (344.93, 34.03) -- (344.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (345.02, 34.03) -- (345.02, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (345.07, 34.03) -- (345.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (345.10, 34.03) -- (345.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (345.51, 34.03) -- (345.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (345.57, 34.03) -- (345.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (346.09, 34.03) -- (346.09, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (346.39, 34.03) -- (346.39, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (347.80, 34.03) -- (347.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.20, 34.03) -- (348.20, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.41, 34.03) -- (348.41, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.87, 34.03) -- (348.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.92, 34.03) -- (348.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (349.60, 34.03) -- (349.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (351.33, 34.03) -- (351.33, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (351.43, 34.03) -- (351.43, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (351.56, 34.03) -- (351.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (351.74, 34.03) -- (351.74, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (351.87, 34.03) -- (351.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (353.20, 34.03) -- (353.20, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (353.44, 34.03) -- (353.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (353.54, 34.03) -- (353.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (354.59, 34.03) -- (354.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (357.17, 34.03) -- (357.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (357.38, 34.03) -- (357.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (357.90, 34.03) -- (357.90, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (357.93, 34.03) -- (357.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (358.21, 34.03) -- (358.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (358.75, 34.03) -- (358.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (359.57, 34.03) -- (359.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (359.62, 34.03) -- (359.62, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.33, 34.03) -- (360.33, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.36, 34.03) -- (360.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.85, 34.03) -- (360.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (361.40, 34.03) -- (361.40, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (362.06, 34.03) -- (362.06, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (362.35, 34.03) -- (362.35, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (362.48, 34.03) -- (362.48, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (362.58, 34.03) -- (362.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (363.30, 34.03) -- (363.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (363.33, 34.03) -- (363.33, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (363.40, 34.03) -- (363.40, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (364.54, 34.03) -- (364.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (365.21, 34.03) -- (365.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (366.77, 34.03) -- (366.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (366.99, 34.03) -- (366.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (368.17, 34.03) -- (368.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (368.73, 34.03) -- (368.73, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (372.78, 34.03) -- (372.78, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (373.25, 34.03) -- (373.25, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (374.25, 34.03) -- (374.25, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (374.25, 34.03) -- (374.25, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (374.55, 34.03) -- (374.55, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (374.76, 34.03) -- (374.76, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (375.05, 34.03) -- (375.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (375.30, 34.03) -- (375.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (375.66, 34.03) -- (375.66, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (375.91, 34.03) -- (375.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (376.54, 34.03) -- (376.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (376.88, 34.03) -- (376.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (377.80, 34.03) -- (377.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (378.36, 34.03) -- (378.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (378.50, 34.03) -- (378.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (378.91, 34.03) -- (378.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (379.95, 34.03) -- (379.95, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (381.22, 34.03) -- (381.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (381.23, 34.03) -- (381.23, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (381.92, 34.03) -- (381.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (381.95, 34.03) -- (381.95, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (382.82, 34.03) -- (382.82, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (383.24, 34.03) -- (383.24, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (383.51, 34.03) -- (383.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (384.09, 34.03) -- (384.09, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (384.17, 34.03) -- (384.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (384.29, 34.03) -- (384.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (384.73, 34.03) -- (384.73, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (386.66, 34.03) -- (386.66, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (386.77, 34.03) -- (386.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (390.32, 34.03) -- (390.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (394.80, 34.03) -- (394.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (396.85, 34.03) -- (396.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (404.07, 34.03) -- (404.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (404.80, 34.03) -- (404.80, 41.32);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 52.86) {3.7};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 96.58) {3.8};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,140.30) {3.9};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,184.02) {4.0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,227.74) {4.1};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,271.45) {4.2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 45.37, 80.71) {-0.002};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 45.37,142.88) {0.000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 45.37,205.04) {0.002};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 45.37,267.21) {0.004};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 40.56, 20.31) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 90.87, 20.31) {1};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (141.19, 20.31) {2};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (191.50, 20.31) {3};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (241.82, 20.31) {4};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (292.13, 20.31) {5};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (342.45, 20.31) {6};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (392.76, 20.31) {7};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (100.44, 20.31) {1};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (148.69, 20.31) {2};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (196.93, 20.31) {3};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (245.18, 20.31) {4};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (293.43, 20.31) {5};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (341.68, 20.31) {6};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (389.93, 20.31) {7};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (230.63,  4.82) {Ln(Min. City Dist.)$_{t}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (237.03,  4.82) {Ln(Min. City Dist.)$_{t}$};
 \end{scope}

### 2014-09-25 LaTeX/rmseInOut.tex
updates to tex, and plots

@@
-% Created by tikzDevice version 0.7.0 on 2014-09-23 12:42:48
+% Created by tikzDevice version 0.7.0 on 2014-09-25 14:01:12
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (433.62,289.08);
 \end{scope}
 \begin{scope}
-\path[clip] ( 39.69, 54.77) rectangle (229.13,264.40);
+\path[clip] ( 49.28, 54.77) rectangle (233.92,264.40);
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
 
-\path[fill=fillColor] ( 39.69, 54.77) rectangle (229.13,264.40);
+\path[fill=fillColor] ( 49.28, 54.77) rectangle (233.92,264.40);
 \definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}
 
-\path[fill=fillColor] ( 52.60, 64.30) rectangle (130.10,254.87);
+\path[fill=fillColor] ( 61.87, 64.30) rectangle (137.41,254.87);
 
-\path[fill=fillColor] (138.71, 64.30) rectangle (216.21,165.65);
+\path[fill=fillColor] (145.80, 64.30) rectangle (221.33,223.96);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 39.69, 54.77) rectangle (229.13,264.40);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.28, 54.77) rectangle (233.92,264.40);
 \end{scope}
 \begin{scope}
-\path[clip] (232.14, 54.77) rectangle (421.57,264.40);
+\path[clip] (236.94, 54.77) rectangle (421.58,264.40);
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
 
-\path[fill=fillColor] (232.14, 54.77) rectangle (421.57,264.40);
+\path[fill=fillColor] (236.94, 54.77) rectangle (421.58,264.40);
 \definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}
 
-\path[fill=fillColor] (245.05, 64.30) rectangle (322.55,254.76);
+\path[fill=fillColor] (249.52, 64.30) rectangle (325.06,254.81);
 
-\path[fill=fillColor] (331.16, 64.30) rectangle (408.66,164.41);
+\path[fill=fillColor] (333.45, 64.30) rectangle (408.99,222.46);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.14, 54.77) rectangle (421.57,264.40);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (236.94, 54.77) rectangle (421.58,264.40);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] ( 39.69,264.40) rectangle (229.13,277.04);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] ( 49.28,264.40) rectangle (233.92,277.04);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (134.41,267.41) {Ln(Min. Cap Dist.)$_{t}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (141.60,267.41) {Ln(Min. Cap Dist.)$_{t}$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (232.14,264.40) rectangle (421.57,277.04);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (236.94,264.40) rectangle (421.58,277.04);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.86,267.41) {Ln(Min. City Dist.)$_{t}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (329.26,267.41) {Ln(Min. City Dist.)$_{t}$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 60.99) {0.0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 42.17, 60.99) {0.000};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,128.89) {0.1};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 42.17,114.81) {0.001};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,196.78) {0.2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 42.17,168.63) {0.002};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 42.17,222.44) {0.003};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 91.35, 41.05) {In-Sample };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 99.64, 41.05) {In-Sample };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 91.35, 30.68) { n=375 };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 99.64, 30.68) { n=375 };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 91.35, 20.31) { N=66};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 99.64, 20.31) { N=66};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (177.46, 41.05) {Out-Sample };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (183.57, 41.05) {Out-Sample };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (177.46, 30.68) { n=186 };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (183.57, 30.68) { n=186 };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (177.46, 20.31) { N=42};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (183.57, 20.31) { N=42};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (283.80, 41.05) {In-Sample };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (287.29, 41.05) {In-Sample };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (283.80, 30.68) { n=375 };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (287.29, 30.68) { n=375 };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (283.80, 20.31) { N=66};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (287.29, 20.31) { N=66};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (369.91, 41.05) {Out-Sample };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (371.22, 41.05) {Out-Sample };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (369.91, 30.68) { n=186 };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (371.22, 30.68) { n=186 };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (369.91, 20.31) { N=42};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (371.22, 20.31) { N=42};
 \end{scope}

### 2014-09-25 R/vizResults.R

@@ -126,7 +126,8 @@ ggsimplot = function(
   if(sigma){sigma = sqrt(RSS/dfResid)} else {sigma = 0}
 
   # Set up scenario
-  vRange=seq(min(simData[,vi]), max(simData[,vi]), .1)
+  # vRange=seq(min(simData[,vi]), max(simData[,vi]), .1)
+  vRange=sort(unique(simData[,vi]))
   scenCol = length(vars); scenRow = length(vRange)
   scenario = matrix(NA, nrow=scenRow, ncol=scenCol)
   colnames(scenario) = c(vars)
@@ -157,6 +158,7 @@ ggsimplot = function(
         temp = temp + geom_errorbar(aes(x=x, ymax=Hi90, ymin=Lo90), width=0.2) 
         temp = temp + geom_errorbar(aes(x=x, ymax=Hi95, ymin=Lo95), width=.5) 
         temp = temp + geom_point(aes(x=x, y=Fit))
+        temp = temp + geom_rug(sides='b')
         if(specX){temp = temp + scale_x_discrete(limits=ggxlims, breaks=ggxbreaks)}
         }
     
@@ -165,6 +167,7 @@ ggsimplot = function(
       temp <- ggplot(ggData, aes(x=x, y=Fit, ymin=Lo95, ymax=Hi95))
       temp <- temp + geom_line() + geom_ribbon(alpha=0.3)
       temp <- temp + geom_ribbon(aes(ymin=Lo90, ymax=Hi90), alpha=0.5)
+      temp = temp + geom_rug(sides='b')
       if(specX){temp = temp + scale_x_continuous(limits=ggxlims, breaks=ggxbreaks)}
     }
   }

### 2014-09-30 LaTeX/RhodiumIntro.tex
minor comments
Minor tweaks to intro

@@
 Understanding the effects of civil conflict has become an integral part of the study of economic development \citep{serneels:verpoorten:2013}.
-From a theoretical perspective there is little consensus as to the impact that conflict has on ecomic performance.
+From a theoretical perspective there is little consensus about the impact that conflict has on economic performance.
 While neoclassical models predict that recovery from conflict should be relatively quick, others such as \citet{barro:martin:2004} and \citet{sachs:2006} argue that recovery will be extremely slow or even trapped in a low level equilibrium.
@@
 
-There are also puzzling cases of countries enmeshed in civil armed conflict that have seemingly little impact on economic growth.
+There are also puzzling cases of countries enmeshed in domestic armed conflict that have seemingly little impact on economic growth.
 Mexico, for example, has been engaged in a drug war since December 2006 and the number of deaths stemming from this civil conflict have only increased since that time.
@@
 
+% Could we say something instead like, We argue that to explain variation in economic performance between countries in the midst of civil war, it is necessary to specify the theoretical mechanism through which conflict affects growth.
+And the key mechanism is  that conflict harms growth by affecting cities.
+
+To explain this variation in economic performance between countries in the midst of civil war, it is necessary to understand how conflict affects growth.
 In this paper we argue that to explain variation in economic performance between countries in the midst of civil war, it is necessary to account for the spatial location of the conflict relative to major population and economic centers.
 Much of the extant literature has focused on examining the effect of conflict on economic growth at the national level.
-The implicit assumption of these approaches is that all civil wars are alike, whether they be occuring right outside the capital or on the fringes of the country.
-We argue that the location of conflicts to major cities and capitals will determine the effect of civil conflict on economic performance, and that conflicts only significantly dampens economic performance if they are proximate to major population and economic centers.
+The implicit assumption of these approaches is that all civil wars are alike, whether they be occurring right outside the capital or on the fringes of the country.
+We argue that the location of conflicts to major cities and capitals will determine the effect of civil conflict on economic performance, and that conflicts only significantly dampen economic performance if they are proximate to major population and economic centers.
 
-The rest of the paper proceeds as follows, we begin with a review of the literature on the relationship between economic growth and civil war.
+The rest of the paper proceeds as follows.
+We begin with a review of the literature on the relationship between economic growth and civil war.
 In section \ref{theory}, we explain the mechanisms of our hypothesis through the case of Colombia.

### 2014-09-30 LaTeX/RhodiumEmp.tex
updates to empirics

@@
 Unlike much of the extant literature in constructing our dependent variable we focus on year over change instead of a ten year average.
-We believe this approach to be superior because it allows us to estimate the direct effect of the conflict on economic performance in that year.
-A ten-year average approach might hide important variation in our dependent variable that can be explained by the proximity of conflict to economic centers.
+This allows us to estimate the direct effect of conflict on economic performance in that year.
+A ten-year average approach would hide important variation in our dependent variable that can be explained by the proximity of conflict to economic centers.
 
@@
 
-% Might want to drop this stuff about getting city data from the almanac
+A crucial part of our work here involved determining the capital and major city centers for country-years referenced in the PRIO dataset.\footnote{To gather information on capital and major cities we turned to yearly editions of The World Almanac from 1989 to 2008.} Typically, the Alamanacs listed at least three major cities for each country and year from 1989 to 2008.
+After we had gathered a yearly list of major cities by country, we determined the centroid location of each city using Google's Geocoding API.
 
-A crucial part of our work here involved determining major city centers by year.
-The only data source we found with enough geographical and temporal coverage on major cities was The World Alamanac.\footnote{To gather data from these textbooks we hired several research assistants to identify the major cities listed for each country within a yearly edition of the Almanac from 1989 to 2008.} Major cities are classified as those that have relatively large shares of a country's population and/or are economic centers.
-Typically, the Alamanacs listed at least three major cities for each country and year from 1989 to 2008.
-After we had gathered a yearly list of major cities by country, we determined the centroid location of each city using Google's Geocoding API.
+In figure \ref{fig:CityConfMap}, we show the geographic distribution of conflicts and cities.
+The centroid locations of conflicts are shown by red dots.
+Not surprisingly, we can see that in many cases conflict locations are clustered within specific parts of a country.
+In most cases, this clustering is indicative of the same conflict moving within the geographic boundaries of a country over time.
+The blue diamonds in \ref{fig:CityConfMap} denote the locations of major cities as identified in The World Alamanacs from 1989 to 2008.
+Countries shaded in grey are those for which no armed conflict took place in this period according to the PRIO dataset.
 
@@
 \FloatBarrier
-
-In figure \ref{fig:CityConfMap}, we show the geographic distribution of conflicts and cities.
-The centroid locations of conflicts are shown by red dots.
-Not surprisingly, we can see that in many cases conflict locations are clustered within specific parts of a country.
-In most cases, this clustering is indicative of the same conflict moving within the geographic boundaries of a country over time.
-The blue diamonds in \ref{fig:CityConfMap} denote the locations of major cities as identified in The World Alamanacs from 1989 to 2008.
-Countries shaded in grey are those for which no armed conflict took place in this period according to the PRIO dataset.
 
@@
 	&  \;+\; \beta_{8}(Democracy_{i,t-1}) \;+\; \beta_{9}(World \; GDP \; Growth_{t}) \\
-	& \;+\; \alpha_{i} + \mu_{i,t}
+	& \;+\; \mu_{i,t} \;+\; \epsilon_{i,t}
 \end{align*}
@@
 
-To assess the accuracy and performance of these estimates we employ a simple two-fold cross validation procedure.\footnote{Results of analysis were similar when employing a 10-fold cross validation as well, however, we limit to showing six here for the sake of space.} We use this procedure both to determine the robustness of our coefficient estimates when estimated on different subsamples of our dataset, and to assess how well the results of our model would generalize to an independent dataset.
+To assess the accuracy and performance of these estimates we employ a simple two-fold cross validation procedure.
+We use this procedure both to determine the robustness of our coefficient estimates when estimated on different subsamples of our dataset, and to assess how well the results of our model would generalize to an independent dataset.
 To begin the cross-validation, we split the 653 sanction cases in our dataset into six approximately equal subsets.

### 2014-09-30 R/Analysis/models.R

@@ -14,6 +14,7 @@ logTrans=function(x){ log( x + abs(min(x, na.rm=T)) + 1) }
 modData$lngdp_l0 = log(modData$gdp_l0)
 modData$lngdp = log(modData$gdp)
 modData$lngdpGr_l0 = (modData$lngdp_l0-modData$lngdp)/modData$lngdp_l0
+modData$lngdpGr_l0 = modData$gdpGr_l0
 
 # Transformations for conflict variables
 modData$lnminDist.min <- log(modData$minDist.min+1)
@@ -21,8 +22,10 @@ modData$lncapDist.min <- log(modData$capDist.min+1)
 modData$Int.max <- modData$Int.max-1
 
 # Transformations for other controls
+modData$lngdpCap = log(modData$gdpCap)
 modData$lninflation_l1 = logTrans(modData$inflation_l1)
 modData$democ = as.numeric(modData$polity>=6)
+modData$polity2 = modData$polity2 + 11
 ###################################################################
 
 ## MODELS FOR GDP GROWTH (ANNUAL %)
@@ -30,7 +33,8 @@ modData$democ = as.numeric(modData$polity>=6)
 modForm=function(x){
   formula( paste0('lngdpGr_l0 ~', x, '+ 
   Int.max + territorial.max + durSt1max + confAreaPropHi +
-  upperincome + lninflation_l1 + democ +
+  nconf + 
+  upperincome + lninflation_l1 + polity2 +
   gdpGr.mean_l0 + (1|ccode)' ) )
 }
 ctyForm=modForm('lnminDist.min')
@@ -40,6 +44,8 @@ mCity = lmer(ctyForm, data = modData ); summary(mCity)$'coefficients'
 mCap = lmer(capForm, data = modData ); summary(mCap)$'coefficients'
 
 # Basic model diags
+rmse=function(x){sqrt( mean( (residuals(x)^2) ) )}
+
 Reduce('-',quantile(modData$lngdpGr_l0,c(0.75,0.25),na.rm=T))
 rmse(mCity); rmse(mCap)
 ###################################################################
@@ -51,12 +57,14 @@ source('vizResults.R')
 
 vnames=c('Ln(Min. City Dist.)$_{t-1}$', 
[…]

### 2014-09-30 R/Databuilder/05 - addOtherVar.R

@@ -91,46 +91,30 @@ yData=merge(yData, polity[,c('polity2','cyear')],
 	by='cyear', all.x=T, all.y=F)
 ####################
 
-# ####################
-# # Imputation
-# # Checks for lagdata function
-# mdl=yData
-# mdl$cyear=numSM(mdl$cyear)
-# lagVars=names(mdl)[4:25]
+####################
+# Imputation
+# Impute missing value
+library('Amelia')
+names(yData)
+exclVars=c('cyear')
+test=amelia(yData[,-which(exclVars %in% names(yData))], cs='ccode', ts='year')
 
-# # Set up lags for sbgcop
-# mdl=lagDataSM(data=mdl,country_year='cyear',
-# 	country='ccode',varsTOlag=lagVars,lag=1)
-# mdl=lagDataSM(data=mdl,country_year='cyear',
-# 	country='ccode',
-# 	varsTOlag=paste0('lag1_',lagVars),lag=1)
-# mdl=lagDataSM(data=mdl,country_year='cyear',
-# 	country='ccode',
-# 	varsTOlag=paste0('lag1_lag1_',lagVars),lag=1)
-# mdl=lagDataSM(data=mdl,country_year='cyear',
-# 	country='ccode',
-# 	varsTOlag=paste0('lag1_lag1_lag1_',lagVars),lag=1)
-# mdl=lagDataSM(data=mdl,country_year='cyear',
-# 	country='ccode',
-# 	varsTOlag=paste0('lag1_lag1_lag1_lag1_',lagVars),lag=1)
-# lagVarsAll=setdiff(colnames(mdl), colnames(yData))
 
-# # Impute missing value
-# # This takes time, set it and go for a run
-# sbgcopTimeSR = system.time(
-#   sbgData <- sbgcop.mcmc(
-#   	mdl[,c('ccode','year',lagVars,lagVarsAll)],
-#   	nsamp=5000,seed=123456, verb=TRUE)
-#   )
 
-# # Clean
-# impData=data.frame(
-# 	cbind(
-# 		cyear=mdl[,'cyear'],
-# 		sbgData$Y.pmean[,c('ccode','year',lagVars)]
-# 	)
-# )
-# ####################
+sbgcopTimeSR = system.time(
+  sbgData <- sbgcop.mcmc(
+  	,
+  	nsamp=5000,seed=123456, verb=TRUE)
+  )
+
+# Clean
+impData=data.frame(
+	cbind(
[…]

### 2014-09-30 R/setup.R

@@ -47,7 +47,6 @@ require(countrycode)
 # Helpful functions
 numSM=function(x){as.numeric(as.character(x))}
 charSM=function(x){as.character(x)}
-rmse=function(x){sqrt( mean( (residuals(x)^2) ) )}
 
 # Lagging vars
 lagTS <- function(x,l){

### 2014-09-30 R/vizResults.R

@@ -158,7 +158,7 @@ ggsimplot = function(
         temp = temp + geom_errorbar(aes(x=x, ymax=Hi90, ymin=Lo90), width=0.2) 
         temp = temp + geom_errorbar(aes(x=x, ymax=Hi95, ymin=Lo95), width=.5) 
         temp = temp + geom_point(aes(x=x, y=Fit))
-        temp = temp + geom_rug(sides='b')
+        temp = temp + geom_rug(sides='b', position='jitter')
         if(specX){temp = temp + scale_x_discrete(limits=ggxlims, breaks=ggxbreaks)}
         }
     
@@ -167,7 +167,7 @@ ggsimplot = function(
       temp <- ggplot(ggData, aes(x=x, y=Fit, ymin=Lo95, ymax=Hi95))
       temp <- temp + geom_line() + geom_ribbon(alpha=0.3)
       temp <- temp + geom_ribbon(aes(ymin=Lo90, ymax=Hi90), alpha=0.5)
-      temp = temp + geom_rug(sides='b')
+      temp = temp + geom_rug(sides='b', position='jitter')
       if(specX){temp = temp + scale_x_continuous(limits=ggxlims, breaks=ggxbreaks)}
     }
   }

### 2014-09-30 LaTeX/RhodiumLit.tex
minor comments

@@
 \cite{collier:1999} identifies five avenues through which civil conflict can impede economic performance: through the \textit{destruction} of resources, through \textit{disruption} of social and economic activity, through \textit{diversion} of resources to the war effort, through \textit{dissaving}, and through \textit{portfolio substition} or divestment.
-Of course, these mechanisms are related to one another; portfolio substitution may be exacerbated by the destruction of resources or the distruption of socioeconomic activity.
+Of course, these mechanisms are related to one another; portfolio substitution may be exacerbated by the destruction of resources or the disruption of socioeconomic activity.
 Overall, Collier finds that civil wars correspond to a 2.2 percent decrease in annual economic growth.
@@
 They conclude that the long-term economic impacts of civil war are largely dependent on post-war governance and foreign assistance.
-They also find, perhaps unsuprisingly, that aggregate estimates of conflict destructiveness are negatively correlated with long-term growth.
+They also find that aggregate estimates of conflict destructiveness are negatively correlated with long-term growth.
 
@@
 
+% By brining this up I think we would need to say more about how exactly we sidestep this issue
+
 Much work has been done on the causal effects of economic performance on civil war.
 Indeed, there is likely an endogenous relationship between economic performance and civil war; each exacerbates the other.
-While our work here sidesteps this argument by focusing exclusively on observations of civil war, we will briefly review the relevant literature here.
+While our work here sidesteps this argument by focusing exclusively on observations of civil war, we will briefly review the relevant literature.
 In a report for the World Bank by \cite{collier:etal:2003}, the authors describe what they term the \textit{conflict trap}.
@@
 
-In accordance with this theory, \cite{fearon:laitin:2003} aruge that poor economic growth is the primary condition conducive for civil war.
-More specifically, they believe that strong economic growth proxies for robust governance and that states with low GDP growth likely have infrastructures that are unable to implement counterinsurgent policies.
+In accordance with this theory, \cite{fearon:laitin:2003} argue that poor economic growth is the primary condition conducive for civil war.
+More specifically, they believe that strong economic growth proxies for robust governance and that states with low GDP growth likely have infrastructures that are unable to implement counter-insurgent policies.
 In an effort to parse out the causal effect of economic growth shocks on civil war, \cite{miguel:etal:2004} instrument income growth with rainfall.
@@
 These weaker groups are only able to survive in areas more distant from capitals.
+In our analysis, we control for the strength of rebel groups to account for this confound.

### 2014-10-02 LaTeX/RhodiumIntro.tex
updates to intro

@@
 
-There are also puzzling cases of countries enmeshed in domestic armed conflict that have seemingly little impact on economic growth.
+There are also puzzling cases of countries enmeshed in domestic armed conflicts that have seemingly little impact on economic growth.
 Mexico, for example, has been engaged in a drug war since December 2006 and the number of deaths stemming from this civil conflict have only increased since that time.
-Yet, even as fatalities due to the drug war reached new peaks, Vikram Pandit of Citigroup cited Mexico in 2012 as being extremely well poised for growth and others argued that Mexico was actually beginning to catch up to its regional rival, Brazil \citep{vardi:2012}.
-This contrasts greatly with the economic fortunes of other countries in the midst of civil war where the economies have plumetted.
+Yet, even as fatalities due to the drug war reached new peaks, Vikram Pandit of Citigroup cited Mexico in 2012 as being extremely well poised for growth.
+Others have argued that Mexico is actually beginning to catch up to its regional rival, Brazil \citep{vardi:2012}.
+This contrasts greatly with the economic fortunes of other countries in the midst of civil war where economies have plumetted.
 \cite{collier:elliott:etal:2003}, for instance, describe civil war as ``development in reverse.''  ``The overall economic and political legacy from civil war,'' they write, ``is thus sufficiently adverse that rapid recovery is unlikely.''  Nevertheless, some countries appear to weather domestic conflict better than others.

### 2014-10-03 LaTeX/RhodiumEmp.tex
updates

@@
 
-To measure economic performance we use annual percent change in logged GDP collected from the World Development Indicators at the World Bank.
-We choose to focus on year over change in logged GDP because we expect conflicts proximate to major cities to lead to immediate reductions in overall growth.
+To measure economic performance we use annual percent change in GDP collected from the World Development Indicators at the World Bank.
 Unlike much of the extant literature in constructing our dependent variable we focus on year over change instead of a ten year average.
 This allows us to estimate the direct effect of conflict on economic performance in that year.
-A ten-year average approach would hide important variation in our dependent variable that can be explained by the proximity of conflict to economic centers.
+A ten or five year average approach would hide important variation in our dependent variable that can be explained by the proximity of conflict to economic centers.
 
-Our key independent variable on the location of conflicts come from the PRIO Conflict Site Dataset.
-This dataset contains geo-referenced armed conflict events from 1989 to 2008.\footnote{We only include examine the effect of internal armed conflicts.} In total this dataset provides us with almost 800 geo-referenced conflict-year cases.
-
-A crucial part of our work here involved determining the capital and major city centers for country-years referenced in the PRIO dataset.\footnote{To gather information on capital and major cities we turned to yearly editions of The World Almanac from 1989 to 2008.} Typically, the Alamanacs listed at least three major cities for each country and year from 1989 to 2008.
-After we had gathered a yearly list of major cities by country, we determined the centroid location of each city using Google's Geocoding API.
+To determine the location of conflicts we turn to the PRIO Conflict Site Dataset.
+This dataset contains geo-referenced armed conflict events from 1989 to 2008.
+In total this dataset provides us with approximately 800 geo-referenced internal conflict-year cases.
+To gather information on capital and major cities we turn to yearly editions of The World Almanac from 1989 to 2008.
+Typically, the Alamanacs list at least three major cities, including the capital, for each country and year from 1989 to 2008.
 
@@
 Meaning that for each year we determine the distance between every conflict and every major city within a state.
-For example, in figure \ref{fig:columbiaMap} we show the location of armed conflicts in Colombia, dots colored in shades of red, and the major cities therein, blue diamonds.\footnote{One armed conflict involving rebel actors and the Colombian government occurred outside of Colombia's borders.} For Colombia each of the red dots represents the same conflict but a different year, with earlier years shaded in light red and later years shaded in dark red.
+For example, in figure \ref{fig:columbiaMap} we show the location of armed conflicts in Colombia, dots colored in shades of blue, major cities, depicted as triangles, and the capital, a diamond.\footnote{One armed conflict involving rebel actors and the Colombian government occurred outside of Colombia's borders.} For Colombia each of the red dots represents the same conflict but a different year, with earlier years shaded in light blue and later years shaded in dark blue.
 Thus for every year we made six distance calculations -- one for every city.
@@
 Add in descriptors for each of these variables and expectations of their sign.
+
+A drawback with circular conflict zones is that they cover more territory than is actually affected by the conflict, including territories of neighboring countries.4 Due to the nature of armed conflict it may be impossible to gain information on the exact locations of armed encounters, occupied territories, and rebel bases.
+It might be possible to map the actual conflict-affected area with high precision for some well- reported conflicts, but it would be virtually impossible to code all conflict-years in the dataset coherently in a similar manner.
+The operationalization of conflict zones is essentially a trade-off between precision and simplicity, and in most cases a circular conflict zone will give a good indication of the core area of the conflict.
 

### 2014-10-03 R/Analysis/conflictMaps.R

@@ -13,7 +13,7 @@ prio$Conflict.territory <- toupper(countrycode(prio$Conflict.territory,"country.
 
 ######################################################################
 # Trace conflict over time
-cname="COLOMBIA"
+cname="MEXICO"
 worldmap=cshp(date=as.Date("1990-01-01"),useGW=F)
 ccode <- countrycode(cname,"country.name","cown")
 country.shape <- worldmap[worldmap$COWCODE==ccode,]
@@ -27,12 +27,35 @@ ggmap = fortify(country.shape, region = "COWCODE")
 ggmapData = data.frame("id" = unique(ggmap$id))
 ggmapData$id = as.numeric(as.character(ggmapData$id))
 
+# Trace conflict over time UGLY
+tracePrio=data.frame(matrix(NA, nrow=nrow(newprio), ncol=4, 
+	dimnames=list(NULL,c('lon1','lat1','lon2','lat2'))))
+pvars=c('Longitude', 'Latitude')
+for(ii in 1:nrow(newprio)){
+	t1 = newprio$Year[ii]; t2=t1+1; id = newprio$ID[ii]
+	toPull=newprio[which(newprio$Year==t2 & newprio$ID==id),pvars]
+	if(nrow(toPull)!=0){ tracePrio[ii,] = as.matrix(cbind(newprio[ii,pvars], toPull)) }
+}
+
 temp = ggplot(ggmapData, aes(map_id = id))
-temp = temp + geom_map(map=ggmap, fill='white', linetype=1, colour='black') + expand_limits(x = ggmap$long, y = ggmap$lat) 
-temp = temp + geom_point(aes(x=fYrCty$cleanLong[fYrCty$cname==cname], y=fYrCty$cleanLat[fYrCty$cname==cname]), pch=18,size=4,col='blue')
-temp = temp + geom_point(aes(x=newprio$Longitude, y=newprio$Latitude,color=newprio$Year),size=4)
+temp = temp + geom_map(map=ggmap, fill='white', 
+	linetype=1, colour='black') + expand_limits(x = ggmap$long, y = ggmap$lat) 
+temp = temp + geom_point(aes(
+	x=fYrCty$cleanLong[fYrCty$cname==cname & fYrCty$Capital==0], 
+	y=fYrCty$cleanLat[fYrCty$cname==cname & fYrCty$Capital==0]), 
+	pch=17,size=4,col='black')
+temp = temp + geom_point(aes(
[…]

### 2014-10-04 LaTeX/RhodiumIntro.tex
notes on urb, agg, growth

@@
 While neoclassical models predict that recovery from conflict should be relatively quick, others such as \citet{barro:martin:2004} and \citet{sachs:2006} argue that recovery will be extremely slow or even trapped in a low level equilibrium.
-Empirical analyses have borne out no clear answers either as results on the economic ramifications of civil war vary depending on the cases and time periods included \citep{kang:meernik:2005}.
+Empirical analyses have borne no clear answers either as results on the economic ramifications of civil war vary depending on the cases and time periods included \citep{kang:meernik:2005}.
 
@@
 Mexico, for example, has been engaged in a drug war since December 2006 and the number of deaths stemming from this civil conflict have only increased since that time.
-Yet, even as fatalities due to the drug war reached new peaks, Vikram Pandit of Citigroup cited Mexico in 2012 as being extremely well poised for growth.
+Yet, even as fatalities due to the drug war reached new peaks, in 2012, Vikram Pandit of Citigroup cited Mexico as being extremely well poised for growth.
 Others have argued that Mexico is actually beginning to catch up to its regional rival, Brazil \citep{vardi:2012}.
@@
 
+We argue that variation in economic performance during civil conflict is contingent on the spatial location of conflict relative to major cities.
+
+The location of production in space is a central part of the process by which economic 
+prosperity and trade is created (Krugman 1991; Martin and Sunley 1996). It is a 
+particularly noticeable feature of economic growth that the location of production in space 
+tends towards agglomeration in a few places. The resulting prominence of cities and towns 
+as a feature of the economic landscape has caused Hanson (1998:1) to remark that ‘most of 
+the United States produces very little’. The development of cities and towns and their 
+subsequent fate is therefore important for economic growth and development. Puga and 
+Venables (1999:292) recognise that ‘economic underdevelopment is a manifestation of the 
+spatial pattern of agglomeration’.
+
 To explain this variation in economic performance between countries in the midst of civil war, it is necessary to understand how conflict affects growth.
@@
 The implicit assumption of these approaches is that all civil wars are alike, whether they be occurring right outside the capital or on the fringes of the country.
-We argue that the location of conflicts to major cities and capitals will determine the effect of civil conflict on economic performance, and that conflicts only significantly dampen economic performance if they are proximate to major population and economic centers.
+We argue that the location of conflicts relative to major cities and capitals will determine the effect of civil conflict on economic performance, and that conflicts only significantly dampen economic performance if they are proximate to major population and economic centers.
 
@@
 We begin with a review of the literature on the relationship between economic growth and civil war.
-In section \ref{theory}, we explain the mechanisms of our hypothesis through the case of Colombia.
+In section \ref{theory}, we explain the mechanisms of our hypothesis through a number of descriptive cases.
 In section \ref{empirics}, we describe how we construct our measures capturing distance of conflicts between major economic and population centers and lay out our estimation approach.

### 2014-10-05 LaTeX/RhodiumIntro.tex
revisions to intro

@@
 
-There are also puzzling cases of countries enmeshed in domestic armed conflicts that have seemingly little impact on economic growth.
+Further few in the literature have sought to explain puzzling cases of domestic armed conflict having little impact on macroeconomic growth.
 Mexico, for example, has been engaged in a drug war since December 2006 and the number of deaths stemming from this civil conflict have only increased since that time.
-Yet, even as fatalities due to the drug war reached new peaks, in 2012, Vikram Pandit of Citigroup cited Mexico as being extremely well poised for growth.
-Others have argued that Mexico is actually beginning to catch up to its regional rival, Brazil \citep{vardi:2012}.
+Yet, even as fatalities due to the drug war reached new peaks, in 2012, Vikram Pandit of Citigroup cited Mexico as being extremely well poised for growth and that its economy may surpass that of its much larger regional rival, Brazil, within a decade \citep{vardi:2012}.
+In that same year, Barron's ran a headline titled, ``Is Mexico the New China?'' \citep{kapadia:2012}.
 This contrasts greatly with the economic fortunes of other countries in the midst of civil war where economies have plumetted.
-\cite{collier:elliott:etal:2003}, for instance, describe civil war as ``development in reverse.''  ``The overall economic and political legacy from civil war,'' they write, ``is thus sufficiently adverse that rapid recovery is unlikely.''  Nevertheless, some countries appear to weather domestic conflict better than others.
+\cite{collier:elliott:etal:2003}, for instance, describe civil war as ``development in reverse.'' ``The overall economic and political legacy from civil war,'' they write, ``is thus sufficiently adverse that rapid recovery is unlikely.''
 
-% Could we say something instead like, We argue that to explain variation in economic performance between countries in the midst of civil war, it is necessary to specify the theoretical mechanism through which conflict affects growth.
-And the key mechanism is  that conflict harms growth by affecting cities.
+Explaining variation in macroeconomic outcomes for countries enmeshed in internal conflict requires a better understanding of not only the spatial mechanisms through which conflict can affect growth but also the process of economic growth.
+Much of the economic development literature in the past few decades has stressed the importance of cities and towns as drivers of economic growth and development \citep{hanson:2005}.
+\citet{venables:2005} notes that the process of development and urbanization exists in virtually all countries and especially in the case of modern developing countries.
+\citet{henderson:2000} finds that even a simple correlation across countries between the level of urbanization and GDP per capita is greater than 0.8.
+The key theme in this literature on economic development is that the spatial positioning of production is a central process through which economic prosperity is created \citep{krugman:1991}.
 
-We argue that variation in economic performance during civil conflict is contingent on the spatial location of conflict relative to major cities.
-
-The location of production in space is a central part of the process by which economic 
-prosperity and trade is created (Krugman 1991; Martin and Sunley 1996). It is a 
-particularly noticeable feature of economic growth that the location of production in space 
-tends towards agglomeration in a few places. The resulting prominence of cities and towns 
-as a feature of the economic landscape has caused Hanson (1998:1) to remark that ‘most of 
-the United States produces very little’. The development of cities and towns and their 
-subsequent fate is therefore important for economic growth and development. Puga and 
-Venables (1999:292) recognise that ‘economic underdevelopment is a manifestation of the 
-spatial pattern of agglomeration’.
-
-To explain this variation in economic performance between countries in the midst of civil war, it is necessary to understand how conflict affects growth.
-In this paper we argue that to explain variation in economic performance between countries in the midst of civil war, it is necessary to account for the spatial location of the conflict relative to major population and economic centers.
+Thus what happens when cities themselves are threatened?
+In this paper, we bridge the economic development literature on the importance of cities with extant literature on the effect of armed conflict to provide a novel explanation for the paradox of high macroeconomic growth in conflict ridden countries.
+Specifically,  we argue that to explain variation in economic performance between countries in the midst of civil war, it is necessary to account for the spatial location of the conflict relative to major population and economic centers.
 Much of the extant literature has focused on examining the effect of conflict on economic growth at the national level.

### 2014-10-06 LaTeX/RhodiumEmp.tex
theory section done?

@@
 Meaning that for each year we determine the distance between every conflict and every major city within a state.
-For example, in figure \ref{fig:columbiaMap} we show the location of armed conflicts in Colombia, dots colored in shades of blue, major cities, depicted as triangles, and the capital, a diamond.\footnote{One armed conflict involving rebel actors and the Colombian government occurred outside of Colombia's borders.} For Colombia each of the red dots represents the same conflict but a different year, with earlier years shaded in light blue and later years shaded in dark blue.
+F
+
+% or example, in figure \ref{fig:columbiaMap} we show the location of armed conflicts in Colombia, dots colored in shades of blue, major cities, depicted as triangles, and the capital, a diamond.\footnote{One armed conflict involving rebel actors and the Colombian government occurred outside of Colombia's borders.} For Colombia each of the red dots represents the same conflict but a different year, with earlier years shaded in light blue and later years shaded in dark blue.
 Thus for every year we made six distance calculations -- one for every city.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=.5\textwidth]{colombiaMap-crop}
-	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008.
-Countries for which no armed conflicts are recorded are shaded in grey.}
-	\label{fig:columbiaMap}
-\end{figure}
 

### 2014-10-06 LaTeX/RhodiumLit.tex
revisions to intro
theory section done?

@@
-\subsection{Literature Review}
+\subsection{Extant Literature on Conflict and Growth}
 \label{lit}
@@
 Widespread conflicts, they argue, are more likely to result in damage to infrastructure, divestment from normal state spending, and capital flight.
-However, in subsequent simulations that account for estimation and fundamental uncertainty, the authors show that these results are uncertain and should be interpreted with caution.
+Their results suggest that widespread civil wars are five times more costly than those fought over a narrower geographic area and can reduce GDP grotwh by 1.25\% annually.
 
@@
 These weaker groups are only able to survive in areas more distant from capitals.
-In our analysis, we control for the strength of rebel groups to account for this confound.
+In our analysis, we control for the intensity and duration of conflict to account for this confound.

### 2014-10-06 LaTeX/RhodiumTheory.tex
revisions to intro
theory section done?

--- 2014-09-19 LaTeX/RhodiumTheory.tex
@@
-\section{Theory}
+\section{Spatial Distribution of Cities and Violence}
 \label{theory}
 
-% thesis: conflicts only significantly dampens economic performance if they are a threat to major population centers.
-conflicts isolated in sparsely populated territories of the country have little to no effect on the whole.
-point to the imai weinstein paper as an example of this.
+The extant literature has made important strides in explaining the relationship between economic growth and civil conflict.
+Yet, none to our knowledge have explored the effects of subnational overlaps in the spatial distribution of cities and conflicts.
+We argue that this overlap is key to explaining variation in macroeconomic performance during civil conflict.
 
-We suspect that substate factors will determine the economic impacts of civil conflict.
-In particular, citizens must be able and willing to participate in commerce.
-When major population centers are threatened by violence, residents will be less likely to engage in economically productive activities.
-Violence near major population centers not only threatens residents directly, but impedes business by threatening trade between the population center and other cities or rural areas.
+Our argument on the proximity of conflict to cities should not be confused with arguments focusing on simply the area covered by a conflict.
+Our argument explicitly differs in the hypothesized mechanism through which conflict affects economic performance.
+We do not disagree that the spread of a conflict could impact state economic prospects, but we argue that a large conflict area is not a necessary condition for poor economic performance.
+Conflict area is only one possible proxy for overall destructiveness.
+However, conflicts with smaller spatial areas can be similarly disruptive if they are centered near urban centers.
+In fact, we anticipate measures of conflict proximity relative to cities rather than spread to be more appropriate to test the macroeconomic effects of conflict.
 
-While this hypothesis may resemble those of \cite{imai:weinstein:2000}, ours differs in the hypothesized mechanism through which conflict affects economic performance.
-While we do not disagree that the spread of a conflict could impact state economic prospects, we argue that conflict area is not necessary for adverse economic performance.
-Conflict area is only one possible proxy for overall destructiveness.
-However, conflicts with smaller spatial areas can be similarly disruptive if they are centered near (and impede access to) the urban centers described above.
-In fact, we anticipate measures of proximity rather than spread to be more appropriate to test the hypothesis that conflict obstructs vital economic activity.
+% \cite[p. 137]{quigley:1998}, we should use page citations everywhere we reference long quotes or not at all
+
+That cities are central to the development of national economic performance is well supported in the long literature on the importance of urban centers to national economies.
+\citet{myrdal:sitohang:1957} were among the first to argue that once cities reach a certain size through the process of urbanization, they tend to become self-reinforcing growth centers through a process Myrdal termed as ``cumulative causation''.
+\citet{chenery:syrquin:1975} provided support for this idea by showing that sharp declines in fertility and substantial increases in growth per capita typically follow cases of urbanization.
+Jane Jacobs, a progenitor of the move towards focusing on urban centers, went farther than most in her time by arguing that cities are the primary motivators of state economies and should be given primacy over the nation state in economic analysis \citep{jacobs:1969,jacobs:1984}.
+
+In the past three decades, as the pace of urbanization has accelerated, economists have devoted even more energy to investigating the role of city-level economic drivers \citep{lucas:1988, ciccone:hall:1996, begg:1999, henderson:wang:2007}.
+Most notably, \citeauthor{krugman:1991a} in his seminal 1991 article, ``Increasing Returns and Economic Geography'', convincingly showed the importance of studying economic outcomes within a spatial context.
+A key finding of Krugman's work into economic geography has been the importance of agglomeration effects, the idea that ``activities tend to cluster where markets are large and markets become larger there where activities cluster'' \citep{krugman:1997}.
+\citet{henderson:2000} provides empirical evidence for why these agglomeration effects would manifest by showing that spatial clustering promotes economic efficiency in a variety of ways from simply enabling savings in transport costs to more efficiently functioning labor markets.
+
+In addition to agglomeration effects, there is an even simpler story, which can be traced back to \citet{marshall:1920}, that states geographic clustering of firms promotes valuable learning and exchange between actors.
+\citet{lucas:1988} provides a formal treatment of this argument and shows that the accumulation of human capital generates positive spillovers, where if even one worker acquires a new skill then spatially proximate workers would all become more productive.
+Empirical estimates of agglomeration effects indicate that a doubling of employment density correspond to a 5\% increase in labor productivity \citep{ciccone:hall:1996,ciccone:2002}.
+\citet{glaeser:etal:1992} examine this problem empirically and show that cities are important for economic growth precisely because they lead to the knowledge spillovers that are important for innovation.
+Similar empirical results have been found by many others, which has led to a growing consensus on how cities can serve as important knowledge hubs for a national economy \citep{jaffe:etal:1993, glaeser:1994, firestone:2010}.
+
+% Further \citet{quigley:1998} concludes that ``large cities have been and will continue to be an important source of economic growth.''
+
+The econometric evidence on the importance of cities has crucial implications for our understanding of the spatial structure of subnational economies.
+Namely, at the subnational level the economy can be thought of as consisting of ``lumps'' of productivity and swaths of areas that contribute little to macroeconomic growth \citep{venables:2005}.
+This implies that subnational conflicts will have heterogeneous effects on economic growth given their spatial proximity to economically relevant centers such as cities.
 
@@
 Their dense populations also tempt belligerents and maximize the impact to cost ratio of a given violent action.
-Finally, the authors point out that warfare destroys transportation infrastructure which can interfere both with commerce and with rebuilding during a conflict.
-
-That armed conflict near and within cities should impact national economic performance is not surprising given the existing body of literature that suggests a close relationship between urban agglomeration and national economies.
-\cite[p.
-137]{quigley:1998} concludes that ``large cities have been and will continue to be an important source of economic growth.''  This echoes the work of Jane Jacobs who argued that cities are the primary motivators of state economies and should be given primacy over the nation state in economic analysis \citep{jacobs:1969,jacobs:1984}.
-In the past three decades, economists have followed Jacobs' lead and investigated city-level economic drivers \citep{lucas:1988, ciccone:hall:1996, begg:1999}.
+Additionally, warfare destroys transportation infrastructure, which can interfere both with commerce and with rebuilding during a conflict.
+In particular, conflict affects citizens ability and willingness to participate in commerce.
+When major population centers are threatened by violence, residents will be less likely to engage in economically productive activities.
+Violence near major population centers not only threatens residents directly, but impedes business by threatening trade between the population center and other cities or rural areas.
 
@@
 Since urban economies are responsible for a disproportionate share of national economic performance, civil conflicts in or near these engines of commerce should likewise exert a disproportionate influence on state performance.
+
+\subsection{Descriptive Cases}
 
@@
 
+figure \ref{fig:columbiaMap}
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=.5\textwidth]{colombiaMap-crop}
+	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008.
+Countries for which no armed conflicts are recorded are shaded in grey.}
+	\label{fig:columbiaMap}
+\end{figure}
+
 Forbes magazine, reporting on peace talks between FARC guerillas and the Colombian government in 2012, wrote:
-\begin{quote}FARC's strategy and [beliefs have] always been to make economic pressure on both, multinational companies and the Colombian government.
+
+\begin{quote}
+	FARC's strategy and [beliefs have] always been to make economic pressure on both, multinational companies and the Colombian government.
 This has been done by attacking oil and natural gas infrastructure affecting companies such as Pacific Rubiales Energy, Oxy and Ecopetrol.
 For non-fuel related international companies with subsidiaries in Colombia, such as Goodyear, Nestle, Microsoft, Toyota, among others, FARC’s modus operandi was mainly racketeering, kidnappings and extortion.
-(Flannery 2012)\end{quote}
+(Flannery 2012)
+\end{quote}
+
 By targeting economic centers and resource infrastructure, FARC can strain Colombia's economy, frighten investors, and bolster support from poor and rural workers sensitive to wealth disparity in the country.
@@
 
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=.5\textwidth]{indiaMap-crop}
+	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008.
+Countries for which no armed conflicts are recorded are shaded in grey.}
+	\label{fig:indiaMap}
+\end{figure}
+
 We turn now to an empirical test of our proposition.
 Using a dataset that includes 510 country-years of civil war from 71 different countries, we seek to determine how the geography of conflict impacts state economic outcomes.
-
-%	Columbia +/- (BR), Pakistan - (SM), Philippines (BR), Israel (SM), Chad (BR), Democratic Republic of Congo (SM)
-%	(  + = Case where conflict was close to center and economy declined; - = Case where conflict far from center and no effect on econ )
-
-%End with a chart to show the distribution of econ performance among conflict-cntry-years to illustrate that there is noticeable variation in economic performance to explain.
-ending with this might help us lead into the empirics section and
-%
-%	seems like the density plot you've already made in the models.R file highlights that the gdp growth var is kind of normal centered at zero which is good for us

### 2014-10-06 R/Analysis/conflictMaps.R

@@ -13,29 +13,16 @@ prio$Conflict.territory <- toupper(countrycode(prio$Conflict.territory,"country.
 
 ######################################################################
 # Trace conflict over time
-cname="MEXICO"
+cname="COLOMBIA"
 worldmap=cshp(date=as.Date("1990-01-01"),useGW=F)
 ccode <- countrycode(cname,"country.name","cown")
 country.shape <- worldmap[worldmap$COWCODE==ccode,]
-
 newprio <- na.omit(prio[prio$Conflict.territory==cname,])
-mypal <- colorRampPalette(c("#FEE5D9",'#FB6A4A',"#99000D"))
-newprio$col= mypal(nrow(newprio))
 
 gpclibPermit()
 ggmap = fortify(country.shape, region = "COWCODE")
 ggmapData = data.frame("id" = unique(ggmap$id))
 ggmapData$id = as.numeric(as.character(ggmapData$id))
-
-# Trace conflict over time UGLY
-tracePrio=data.frame(matrix(NA, nrow=nrow(newprio), ncol=4, 
-	dimnames=list(NULL,c('lon1','lat1','lon2','lat2'))))
-pvars=c('Longitude', 'Latitude')
-for(ii in 1:nrow(newprio)){
-	t1 = newprio$Year[ii]; t2=t1+1; id = newprio$ID[ii]
-	toPull=newprio[which(newprio$Year==t2 & newprio$ID==id),pvars]
-	if(nrow(toPull)!=0){ tracePrio[ii,] = as.matrix(cbind(newprio[ii,pvars], toPull)) }
-}
 
 temp = ggplot(ggmapData, aes(map_id = id))
 temp = temp + geom_map(map=ggmap, fill='white', 
@@ -50,13 +37,9 @@ temp = temp + geom_point(aes(
 	pch=18,size=5,col='black')
 temp = temp + geom_point(aes(x=newprio$Longitude, y=newprio$Latitude,
 	color=newprio$Year),size=4)
-# temp = temp + geom_segment(
-# 	aes(x=tracePrio$lon1, xend=tracePrio$lon2, 
-# 		y=tracePrio$lat1, yend=tracePrio$lat2), 
-# 	color='black', arrow=arrow(length = unit(0.3,"cm")))
 temp = temp + scale_colour_gradient('',
 	low=brewer.pal(9,'Blues')[2],high=brewer.pal(9,'Blues')[9],
-	breaks=newprio$Year[c(1,5,10,15,20)])
[…]

### 2014-10-06 R/Analysis/models.R

@@ -35,7 +35,7 @@ modForm=function(x){
   Int.max + territorial.max + durSt1max + confAreaPropHi +
   nconf + 
   upperincome + lninflation_l1 + polity2 +
-  gdpGr.mean_l0 + (1|ccode)' ) )
+  resourceGDP + gdpGr.mean_l0 + (1|ccode)' ) )
 }
 ctyForm=modForm('lnminDist.min')
 capForm=modForm('lncapDist.min')
@@ -55,11 +55,12 @@ rmse(mCity); rmse(mCap)
 setwd(pathMain)
 source('vizResults.R')
 
-vnames=c('Ln(Min. City Dist.)$_{t-1}$', 
-  'Intensity$_{t-1}$', 'Type$_{t-1}$', 'Duration$_{t-1}$', 'Area$_{t-1}$',
-  'Number of conflicts$_{t-1}$',
+otherCovars=c('Intensity$_{t-1}$', 'Type$_{t-1}$', 'Duration$_{t-1}$', 'Area$_{t-1}$',
+  'Number of conflicts$_{t-1}$',  
   'Upper Income', 'Ln(Inflation)$_{t-1}$', 'Democracy$_{t-1}$',
-  'World GDP Growth$_{t}$')
+  'Resource Rents/GDP$_{t}$', 'World GDP Growth$_{t}$')
+
+vnames=c('Ln(Min. City Dist.)$_{t-1}$', otherCovars)
 temp <- ggcoefplot(coefData=summary(mCity)$'coefficients',
     vars=na.omit(rownames(summary(mCity)$'coefficients')[2:100]), 
     varNames=vnames, Noylabel=FALSE, coordFlip=TRUE,
@@ -72,11 +73,7 @@ setwd(pathTex)
 # temp
 # dev.off()
 
-vnames=c('Ln(Min. Capital Dist.)$_{t-1}$', 
-  'Intensity$_{t-1}$', 'Type$_{t-1}$', 'Duration$_{t-1}$', 'Area$_{t-1}$',
-  'Number of conflicts$_{t-1}$',  
-  'Upper Income', 'Ln(Inflation)$_{t-1}$', 'Democracy$_{t-1}$',
-  'World GDP Growth$_{t}$')
+vnames=c('Ln(Min. Capital Dist.)$_{t-1}$', otherCovars)
 temp <- ggcoefplot(coefData=summary(mCap)$'coefficients',
[…]

### 2014-10-06 R/Databuilder/04 - DistanceCalc.R

@@ -165,13 +165,15 @@ save(yData, file='countryYear_ConflictData.rda')
 # [95,] "NY.GDP.PCAP.KD.ZG"             "GDP per capita growth (annual %)"
 # [86,] "NY.GDP.MKTP.KD"                 "GDP (constant 2000 US$)"
 # [87,] "NY.GDP.MKTP.KD.ZG"             "GDP growth (annual %)"
+# NY.GDP.TOTL.RT.ZS             "Natual Resource Rents % of GDP"
 wbVars=c("BX.KLT.DINV.CD.WD","AG.LND.TOTL.K2", "NY.GDP.DEFL.KD.ZG",
   "NY.GDP.PCAP.KD", "NY.GDP.PCAP.KD.ZG",
-  "NY.GDP.MKTP.KD", "NY.GDP.MKTP.KD.ZG")
+  "NY.GDP.MKTP.KD", "NY.GDP.MKTP.KD.ZG", 
+  'NY.GDP.TOTL.RT.ZS')
 wbData=WDI(country='all', indicator=wbVars,
   start=1988, end=2010, extra=T)
-names(wbData)[4:10]=c('fdi', 'landArea', 'inflation', 'gdpCap',
-  'gdpCapGr', 'gdp', 'gdpGr')
+names(wbData)[4:11]=c('fdi', 'landArea', 'inflation', 'gdpCap',
+  'gdpCapGr', 'gdp', 'gdpGr', 'resourceGDP')
 setwd(pathData)
 save(wbData, file='wbData.rda')
 ##################################################################

### 2014-10-06 R/Databuilder/05 - addOtherVar.R

@@ -37,15 +37,15 @@ wbData = merge(wbData, gdpGrYr, by='year', all.x=T, all.y=F)
 
 # Merging
 wbData$cyear = paste0(wbData$ccode, wbData$year)
-yData = merge(yData, wbData[,c(4:10,20:ncol(wbData))], 
+yData = merge(yData, wbData[,c(4:11,20:ncol(wbData))], 
 	by='cyear', all.x=T, all.y=F)
 
 wbData$cyear = paste0(wbData$ccode, wbData$year-1)
-yData = merge(yData, wbData[,c(4:10,20:ncol(wbData))], 
+yData = merge(yData, wbData[,c(4:11,20:ncol(wbData))], 
 	by='cyear', all.x=T, all.y=F, suffixes=c("_l0",""))
 
 wbData$cyear = paste0(wbData$ccode, wbData$year+1)
-yData = merge(yData, wbData[,c(4:10,20:ncol(wbData))], 
+yData = merge(yData, wbData[,c(4:11,20:ncol(wbData))], 
 	by='cyear', all.x=T, all.y=F, suffixes=c("_l1",""))
 
 # Create conflict area/land area var
@@ -79,8 +79,8 @@ polity$country[polity$country=='Congo Kinshasa']='Democratic Congo'
 polity$country[polity$country=='UAE']='United Arab Emirates'
 polity$cname=toupper(countrycode(polity$country,'country.name','country.name'))
 
-polity$cname[polity$cname=="Czechoslovakia"]='CZECH REPUBLIC'
-polity$cname[polity$cname=="Yugoslavia"]="SERBIA"
+polity$cname[polity$cname=="CZECHOSLOVAKIA"]='CZECH REPUBLIC'
+polity$cname[polity$cname=="YUGOSLAVIA"]="SERBIA"
 polity$ccode=panel$ccode[match(polity$cname, panel$cname)]
 polity$cyear=paste0(polity$ccode,polity$year)
 
@@ -91,30 +91,30 @@ yData=merge(yData, polity[,c('polity2','cyear')],
 	by='cyear', all.x=T, all.y=F)
 ####################
 
-####################
-# Imputation
-# Impute missing value
-library('Amelia')
-names(yData)
-exclVars=c('cyear')
-test=amelia(yData[,-which(exclVars %in% names(yData))], cs='ccode', ts='year')
+# ####################
+# # Imputation
[…]

### 2014-10-06 R/Analysis/Legacy/Legacy - fullPanelModels.R
removing country plots, cleaning up r scriptsg

@@ -1,160 +1,0 @@
-if(Sys.info()["user"]=="janus829"){source('/Users/janus829/Desktop/Research/Rhodium/R/setup.R')}
-if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
-
-# Load conflict country year data
-setwd(pathData)
-load('combinedData.rda')
-
-###################################################################
-# CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
-
-# Correcting imp stuff
-impData$ccode=round(impData$ccode,0)
-impData$year=round(impData$year,0)
-
-# Logging conflict distance variables
-impData$lnIminDist.min = log(impData$IminDist.min+1)
-impData$lnIcapDist.min = log(impData$IcapDist.min+1)
-impData$lnIconfArea.mean = log(1/(impData$Conflict.area.mean+1))
-impData$lnIconfArea.max = log(1/(impData$Conflict.area.max+1))
-
-# Binaries
-impData$USA = impData$ccode==2
-impData$coldwar = impData$year<1991
-
-# Log of other variables
-impData$lnLandArea = log(impData$AG.LND.TOTL.K2)
-impData$lnGDPgr = log(
-	impData$NY.GDP.MKTP.KD.ZG +
-	abs(min(impData$NY.GDP.MKTP.KD.ZG)) + 1 )
-impData$lnGDPcap = log(impData$NY.GDP.PCAP.KD)
-impData$lnInflation = log(
-	impData$NY.GDP.DEFL.KD.ZG + 
-	abs(min(impData$NY.GDP.DEFL.KD.ZG)) + 1 )
-
-# Ordering
-impData = impData[order(impData$year),]
-
-# Creating lags
-lagVars=names(impData)[4:ncol(impData)]
-impData=lagDataSM(impData,'ccodeYear','ccode',lagVars,lag=1)
-###################################################################
-
-###################################################################
-# Full model
-cityMod = lmer(
-  lnGDPgr ~ 
-	lag1_lnGDPcap + lnLandArea
-	+ lag1_lnInflation
-	+ lag1_Int.mean + lag1_lnIconfArea.mean + durSt2max + nconf
-	+ lag1_lnIminDist.min
-	+ (1|ccode), data=impData)
-summary(cityMod)
-rmse(cityMod)
-
-capMod = lmer(
-  lnGDPgr ~ 
-	lag1_lnGDPcap + lnLandArea
-	+ lag1_lnInflation
[…]

### 2014-10-06 R/Analysis/conflictMaps.R

@@ -1,4 +1,5 @@
-if(Sys.info()["user"]=="janus829"){source('/Users/janus829/Desktop/Research/Rhodium/R/setup.R')}
+if(Sys.info()["user"]=="janus829"){source('~/Desktop/Research/Rhodium/R/setup.R')}
+if(Sys.info()["user"]=="s7m"){source('~/Research/Rhodium/R/setup.R')}
 if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
 
 # Load conflict country year data
@@ -30,11 +31,11 @@ temp = temp + geom_map(map=ggmap, fill='white',
 temp = temp + geom_point(aes(
 	x=fYrCty$cleanLong[fYrCty$cname==cname & fYrCty$Capital==0], 
 	y=fYrCty$cleanLat[fYrCty$cname==cname & fYrCty$Capital==0]), 
-	pch=17,size=4,col='black')
+	pch=17,size=4,col='darkgrey')
 temp = temp + geom_point(aes(
 	x=fYrCty$cleanLong[fYrCty$cname==cname & fYrCty$Capital!=0], 
 	y=fYrCty$cleanLat[fYrCty$cname==cname & fYrCty$Capital!=0]), 
-	pch=18,size=5,col='black')
+	pch=18,size=5,col='darkgrey')
 temp = temp + geom_point(aes(x=newprio$Longitude, y=newprio$Latitude,
 	color=newprio$Year),size=4)
 temp = temp + scale_colour_gradient('',
@@ -48,7 +49,15 @@ temp = temp + theme(
   panel.grid.minor=element_blank(), panel.border=element_blank())
 temp
 setwd(pathTex)
-pdf(file=paste0(tolower(cname),'Map.pdf'), width=5, height=7)
-temp
-dev.off()
+# pdf(file=paste0(tolower(cname),'Map.pdf'), width=5, height=7)
+# temp
+# dev.off()
+######################################################################
+
+######################################################################
+# Trace GDP over time
+setwd(pathData)
+load('wbData.rda')
+cwbdata=wbData[which(wbData$cname==cname & wbData$year>=min(newprio$Year) & wbData$year<=max(newprio$Year)),]
+ggplot(cwbdata, aes(x=year,y=gdpGr))+geom_line()
 ######################################################################

### 2014-10-06 R/Databuilder/04 - DistanceCalc.R

@@ -1,4 +1,5 @@
-if(Sys.info()["user"]=="janus829"){source('/Users/janus829/Desktop/Research/Rhodium/R/setup.R')}
+if(Sys.info()["user"]=="janus829"){source('~/Desktop/Research/Rhodium/R/setup.R')}
+if(Sys.info()["user"]=="s7m"){source('~/Research/Rhodium/R/setup.R')}
 if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
 
 # Load City pop data
@@ -154,26 +155,4 @@ yData=cbind(yData, prioMIN)
 # Saving aggregation of conflict data to country-year level
 setwd(pathData)
 save(yData, file='countryYear_ConflictData.rda')
-##################################################################
-
-##################################################################
-# Bring in WB data
-# [5,] "BX.KLT.DINV.CD.WD"        "Foreign direct investment, net inflows (BoP, current US$)"
-# [12,] "AG.LND.TOTL.K2"        "Land area (sq. km)"
-# [76,] "NY.GDP.DEFL.KD.ZG"             "Inflation, GDP deflator (annual %)"
-# [94,] "NY.GDP.PCAP.KD"                 "GDP per capita (constant 2000 US$)"
-# [95,] "NY.GDP.PCAP.KD.ZG"             "GDP per capita growth (annual %)"
-# [86,] "NY.GDP.MKTP.KD"                 "GDP (constant 2000 US$)"
-# [87,] "NY.GDP.MKTP.KD.ZG"             "GDP growth (annual %)"
-# NY.GDP.TOTL.RT.ZS             "Natual Resource Rents % of GDP"
-wbVars=c("BX.KLT.DINV.CD.WD","AG.LND.TOTL.K2", "NY.GDP.DEFL.KD.ZG",
-  "NY.GDP.PCAP.KD", "NY.GDP.PCAP.KD.ZG",
-  "NY.GDP.MKTP.KD", "NY.GDP.MKTP.KD.ZG", 
-  'NY.GDP.TOTL.RT.ZS')
-wbData=WDI(country='all', indicator=wbVars,
-  start=1988, end=2010, extra=T)
-names(wbData)[4:11]=c('fdi', 'landArea', 'inflation', 'gdpCap',
-  'gdpCapGr', 'gdp', 'gdpGr', 'resourceGDP')
-setwd(pathData)
-save(wbData, file='wbData.rda')
 ##################################################################

### 2014-10-06 R/Databuilder/06 - addOtherVar.R

@@ -1,6 +1,6 @@
 ####################
-if(Sys.info()["user"]=="janus829"){source('/Users/janus829/Desktop/Research/Rhodium/R/setup.R')}
-if(Sys.info()["user"]=="s7m"){source('/Users/s7m/Research/Rhodium/R/setup.R')}
+if(Sys.info()["user"]=="janus829"){source('~/Desktop/Research/Rhodium/R/setup.R')}
+if(Sys.info()["user"]=="s7m"){source('~/Research/Rhodium/R/setup.R')}
 if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
 
 # Load conflict country year and WB data

### 2014-10-06 R/Databuilder/Legacy/Legacy - addOtherVar_Full Panel.R

@@ -1,166 +1,0 @@
-####################
-if(Sys.info()["user"]=="janus829"){source('/Users/janus829/Desktop/Research/Rhodium/R/setup.R')}
-if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
-
-# Load conflict country year data
-setwd(pathData)
-load('countryYear_ConflictData.rda')
-# keeping original version for country year dataset
-conData=yData 
-####################
-
-####################
-# Bring in WB data
-# WDIsearch()
-# [5,] "BX.KLT.DINV.CD.WD"    			 "Foreign direct investment, net inflows (BoP, current US$)" 
-# [12,] "AG.LND.TOTL.K2"    			 "Land area (sq. km)"
-# [76,] "NY.GDP.DEFL.KD.ZG"              "Inflation, GDP deflator (annual %)"
-# [94,] "NY.GDP.PCAP.KD"                 "GDP per capita (constant 2000 US$)"
-# [95,] "NY.GDP.PCAP.KD.ZG"              "GDP per capita growth (annual %)"
-# [86,] "NY.GDP.MKTP.KD"                 "GDP (constant 2000 US$)"  
-# [87,] "NY.GDP.MKTP.KD.ZG"              "GDP growth (annual %)"
-
-wbVars=c("BX.KLT.DINV.CD.WD","AG.LND.TOTL.K2", 
-		"NY.GDP.DEFL.KD.ZG", 
-		"NY.GDP.PCAP.KD", "NY.GDP.PCAP.KD.ZG", 
-		"NY.GDP.MKTP.KD", "NY.GDP.MKTP.KD.ZG")
-wbData=WDI(country='all', indicator=wbVars, 
-	start=1988, end=2010, extra=T)
-
-# Add cnames
-wbData$cname = countrycode(wbData$iso2c, 'iso2c', 'country.name')
-wbData = wbData[!is.na(wbData$cname),]
-wbData$ccode = panel$ccode[match(wbData$cname, panel$cname)]
-wbData = wbData[!is.na(wbData$ccode),]
-####################
-
-####################
-# Merge into country conflict data
-# Lagging all data
-wbData$cyear = paste0(wbData$ccode, wbData$year-1)
-yData = merge(yData, wbData[,c(4:11,17,ncol(wbData))], 
-	by='cyear', all.x=T, all.y=F, suffixes=c("_l0",""))
[…]

### 2014-10-06 LaTeX/RhodiumTheory.tex
removing country plots, cleaning up r scriptsg
updated descriptive cases

@@
 % \cite[p. 137]{quigley:1998}, we should use page citations everywhere we reference long quotes or not at all
+
+\subsection{Cities and Economic Growth}
 
@@
 % Further \citet{quigley:1998} concludes that ``large cities have been and will continue to be an important source of economic growth.''
+
+\subsection{Cities and Conflict}
 
@@
 FARC advocates a number of political and economic reforms and chooses targets strategically related to these objectives.
-
-figure \ref{fig:columbiaMap}
+Figure \ref{fig:columbiaMap} shows the spatial distribution of violence in Colombia from 1989 to 2008, where Bogot\'{a} is designated by a black diamond and major cities by black triangles.
+To determine the centroid locations of conflict we use the PRIO conflict site database developed by \citet{hallberg:2012}.
 
@@
 	\includegraphics[width=.5\textwidth]{colombiaMap-crop}
-	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008.
-Countries for which no armed conflicts are recorded are shaded in grey.}
+	\caption{This map illustrates the geographic distribution of all conflicts in Colombia, according to the PRIO Conflict Site Dataset, and major cities from 1989 to 2008.}
 	\label{fig:columbiaMap}
@@
 Indeed, for much of this period, India has experienced relatively robust economic growth.
+In figure \ref{fig:indiaMap}, we show the geographic distribution of conflict in India from 1989 to 2007 again using the PRIO conflict site database.
+The story from this map is clearly quite stark from that of Colombia.
+Whereas in Colombia conflict had come right to the gates of major cities, in India conflict clearly has been centered in the peripheries.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=.5\textwidth]{indiaMap-crop}
+	\caption{This map illustrates the geographic distribution of all conflicts in India, according to the PRIO Conflict Site Dataset, and major cities from 1989 to 2007. }
+	\label{fig:indiaMap}
+\end{figure}
+
 Mexico, now nearly a decade into a violent and complicated conflict between several organized criminal enterprises and the federal government, has maintained healthy economic performance.
@@
 
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=.5\textwidth]{indiaMap-crop}
-	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008.
-Countries for which no armed conflicts are recorded are shaded in grey.}
-	\label{fig:indiaMap}
-\end{figure}
-
 We turn now to an empirical test of our proposition.

### 2014-10-06 R/Analysis/conflictMaps.R

@@ -14,7 +14,7 @@ prio$Conflict.territory <- toupper(countrycode(prio$Conflict.territory,"country.
 
 ######################################################################
 # Trace conflict over time
-cname="COLOMBIA"
+cname="INDIA"
 worldmap=cshp(date=as.Date("1990-01-01"),useGW=F)
 ccode <- countrycode(cname,"country.name","cown")
 country.shape <- worldmap[worldmap$COWCODE==ccode,]
@@ -57,7 +57,11 @@ setwd(pathTex)
 ######################################################################
 # Trace GDP over time
 setwd(pathData)
-load('wbData.rda')
-cwbdata=wbData[which(wbData$cname==cname & wbData$year>=min(newprio$Year) & wbData$year<=max(newprio$Year)),]
-ggplot(cwbdata, aes(x=year,y=gdpGr))+geom_line()
+load('combinedData.rda')
+yData$lnminDist.min <- log(yData$minDist.min+1)
+yData$lncapDist.min <- log(yData$capDist.min+1)
+
+cyData=yData[which(yData$ccode==ccode & yData$year>=min(newprio$Year) & yData$year<=max(newprio$Year)),]
+mean(cyData$gdpGr_l0)
+ggplot(cyData, aes(x=lncapDist.min,y=gdpGr_l0))+geom_line()
 ######################################################################

### 2014-10-06 LaTeX/crossValPlot.tex
updating plots

@@
-% Created by tikzDevice version 0.7.0 on 2014-09-25 14:00:56
+% Created by tikzDevice version 0.7.0 on 2014-10-06 19:49:11
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,289.08);
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
+\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
 \definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (433.62,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (505.89,289.08);
 \end{scope}
 \begin{scope}
-\path[clip] ( 53.55, 52.60) rectangle (216.77,264.40);
+\path[clip] ( 39.69, 52.60) rectangle (265.26,264.40);
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
 
-\path[fill=fillColor] ( 53.55, 52.60) rectangle (216.77,264.40);
+\path[fill=fillColor] ( 39.69, 52.60) rectangle (265.26,264.40);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 67.15, 65.03) -- ( 67.15,209.31);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 58.48, 78.70) -- ( 58.48,232.72);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 89.82, 74.37) -- ( 89.82,223.23);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 89.81, 71.45) -- ( 89.81,227.72);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (112.49, 92.67) -- (112.49,254.77);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (121.14, 91.74) -- (121.14,254.77);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (135.16, 83.37) -- (135.16,232.52);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (152.47, 95.01) -- (152.47,247.01);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (157.83, 82.70) -- (157.83,233.97);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (183.80, 99.56) -- (183.80,254.25);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (180.50, 65.59) -- (180.50,215.32);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (215.13, 73.72) -- (215.13,227.75);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (203.17, 95.32) -- (203.17,230.62);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (246.46, 85.07) -- (246.46,232.49);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 67.15, 76.63) -- ( 67.15,197.71);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 58.48, 91.09) -- ( 58.48,220.34);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 89.82, 86.34) -- ( 89.82,211.26);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 89.81, 84.01) -- ( 89.81,215.15);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (112.49,105.70) -- (112.49,241.74);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (121.14,104.85) -- (121.14,241.67);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (135.16, 95.36) -- (135.16,220.53);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (152.47,107.23) -- (152.47,234.79);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (157.83, 94.86) -- (157.83,221.81);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (183.80,111.99) -- (183.80,241.82);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (180.50, 77.62) -- (180.50,203.28);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (215.13, 86.11) -- (215.13,215.37);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (203.17,106.20) -- (203.17,219.75);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (246.46, 96.92) -- (246.46,220.64);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] ( 53.55, 62.23) -- (216.77, 62.23);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] ( 39.69, 62.52) -- (265.26, 62.52);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 67.15,137.17) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 58.48,155.71) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.82,148.80) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.81,149.58) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.49,173.72) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.14,173.26) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.16,157.94) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.47,171.01) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.83,158.33) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.80,176.91) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.50,140.45) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.13,150.74) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (203.17,162.97) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (246.46,158.78) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.02,209.31) --
-	( 68.29,209.31);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.92,232.72) --
+	( 60.05,232.72);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.15,209.31) --
-	( 67.15, 65.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 58.48,232.72) --
+	( 58.48, 78.70);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.02, 65.03) --
-	( 68.29, 65.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.92, 78.70) --
+	( 60.05, 78.70);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.69,223.23) --
-	( 90.95,223.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.25,227.72) --
+	( 91.38,227.72);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.82,223.23) --
-	( 89.82, 74.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.81,227.72) --
+	( 89.81, 71.45);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.69, 74.37) --
-	( 90.95, 74.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.25, 71.45) --
+	( 91.38, 71.45);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (111.36,254.77) --
-	(113.62,254.77);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (119.58,254.77) --
+	(122.71,254.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (112.49,254.77) --
-	(112.49, 92.67);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (121.14,254.77) --
+	(121.14, 91.74);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (111.36, 92.67) --
-	(113.62, 92.67);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (119.58, 91.74) --
+	(122.71, 91.74);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (134.03,232.52) --
-	(136.29,232.52);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.91,247.01) --
+	(154.04,247.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (135.16,232.52) --
-	(135.16, 83.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (152.47,247.01) --
+	(152.47, 95.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (134.03, 83.37) --
-	(136.29, 83.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.91, 95.01) --
+	(154.04, 95.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (156.70,233.97) --
-	(158.96,233.97);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (182.24,254.25) --
+	(185.37,254.25);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (157.83,233.97) --
-	(157.83, 82.70);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (183.80,254.25) --
+	(183.80, 99.56);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (156.70, 82.70) --
-	(158.96, 82.70);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (182.24, 99.56) --
+	(185.37, 99.56);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (179.37,215.32) --
-	(181.63,215.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (213.57,227.75) --
+	(216.70,227.75);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (180.50,215.32) --
-	(180.50, 65.59);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (215.13,227.75) --
+	(215.13, 73.72);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (179.37, 65.59) --
-	(181.63, 65.59);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (213.57, 73.72) --
+	(216.70, 73.72);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (202.04,230.62) --
-	(204.30,230.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.90,232.49) --
+	(248.03,232.49);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (203.17,230.62) --
-	(203.17, 95.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (246.46,232.49) --
+	(246.46, 85.07);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (202.04, 95.32) --
-	(204.30, 95.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.90, 85.07) --
+	(248.03, 85.07);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 53.55, 52.60) rectangle (216.77,264.40);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 39.69, 52.60) rectangle (265.26,264.40);
 \end{scope}
 \begin{scope}
-\path[clip] (258.35, 52.60) rectangle (421.58,264.40);
+\path[clip] (268.27, 52.60) rectangle (493.85,264.40);
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
 
-\path[fill=fillColor] (258.35, 52.60) rectangle (421.57,264.40);
+\path[fill=fillColor] (268.27, 52.60) rectangle (493.85,264.40);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (287.07, 67.19) -- (287.07,224.97);
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (318.40, 88.38) -- (318.40,245.63);
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (349.73, 71.61) -- (349.73,242.46);
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (381.06, 91.40) -- (381.06,250.60);
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (412.39, 88.88) -- (412.39,249.59);
 \definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (271.96, 62.23) -- (271.96,215.06);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (443.72, 62.23) -- (443.72,221.53);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (294.63, 95.75) -- (294.63,252.44);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (475.05, 77.47) -- (475.05,227.88);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (317.30, 80.30) -- (317.30,254.77);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (287.07, 79.88) -- (287.07,212.29);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (339.96, 87.24) -- (339.96,249.09);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (318.40,101.02) -- (318.40,232.99);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (362.63, 83.04) -- (362.63,245.02);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (349.73, 85.35) -- (349.73,228.72);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (381.06,104.20) -- (381.06,237.81);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (412.39,101.80) -- (412.39,236.67);
 \definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (385.30, 69.14) -- (385.30,229.47);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (443.72, 75.03) -- (443.72,208.73);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (407.97, 99.45) -- (407.97,243.12);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (475.05, 89.56) -- (475.05,215.79);
+\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
+\definecolor[named]{fillColor}{rgb}{0.00,0.00,0.00}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (268.27, 62.52) -- (493.85, 62.52);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (287.07,146.08) circle (  2.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (318.40,167.00) circle (  2.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (349.73,157.04) circle (  2.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (381.06,171.00) circle (  2.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (412.39,169.24) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (271.96, 74.51) -- (271.96,202.78);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.72,141.88) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (294.63,108.35) -- (294.63,239.84);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (475.05,152.67) circle (  2.85);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (317.30, 94.33) -- (317.30,240.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (285.50,224.97) --
+	(288.64,224.97);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (339.96,100.25) -- (339.96,236.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (287.07,224.97) --
+	(287.07, 67.19);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (362.63, 96.06) -- (362.63,232.00);
-\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
-\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
+\path[draw=drawColor,line width= 0.6pt,line join=round] (285.50, 67.19) --
+	(288.64, 67.19);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (385.30, 82.03) -- (385.30,216.58);
-\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
-\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+\path[draw=drawColor,line width= 0.6pt,line join=round] (316.83,245.63) --
+	(319.97,245.63);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (407.97,111.00) -- (407.97,231.57);
-\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
-\definecolor[named]{fillColor}{rgb}{0.00,0.00,0.00}
+\path[draw=drawColor,line width= 0.6pt,line join=round] (318.40,245.63) --
+	(318.40, 88.38);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (258.35, 69.66) -- (421.58, 69.66);
-\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
-\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
+\path[draw=drawColor,line width= 0.6pt,line join=round] (316.83, 88.38) --
+	(319.97, 88.38);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (271.96,138.64) circle (  2.85);
-\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
-\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.16,242.46) --
+	(351.30,242.46);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (294.63,174.10) circle (  2.85);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (349.73,242.46) --
+	(349.73, 71.61);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (317.30,167.54) circle (  2.85);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.16, 71.61) --
+	(351.30, 71.61);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (339.96,168.16) circle (  2.85);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (379.49,250.60) --
+	(382.62,250.60);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.63,164.03) circle (  2.85);
-\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
-\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
+\path[draw=drawColor,line width= 0.6pt,line join=round] (381.06,250.60) --
+	(381.06, 91.40);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (385.30,149.31) circle (  2.85);
-\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
-\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+\path[draw=drawColor,line width= 0.6pt,line join=round] (379.49, 91.40) --
+	(382.62, 91.40);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (407.97,171.29) circle (  2.85);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (410.82,249.59) --
+	(413.95,249.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (412.39,249.59) --
+	(412.39, 88.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (410.82, 88.88) --
+	(413.95, 88.88);
 \definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (270.82,215.06) --
-	(273.09,215.06);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (442.15,221.53) --
+	(445.28,221.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.96,215.06) --
-	(271.96, 62.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (443.72,221.53) --
+	(443.72, 62.23);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (270.82, 62.23) --
-	(273.09, 62.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (442.15, 62.23) --
+	(445.28, 62.23);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (293.49,252.44) --
-	(295.76,252.44);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (473.48,227.88) --
+	(476.61,227.88);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (294.63,252.44) --
-	(294.63, 95.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (475.05,227.88) --
+	(475.05, 77.47);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (293.49, 95.75) --
-	(295.76, 95.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (316.16,254.77) --
-	(318.43,254.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (317.30,254.77) --
-	(317.30, 80.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (316.16, 80.30) --
-	(318.43, 80.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.83,249.09) --
-	(341.10,249.09);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (339.96,249.09) --
-	(339.96, 87.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.83, 87.24) --
-	(341.10, 87.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (361.50,245.02) --
-	(363.77,245.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (362.63,245.02) --
-	(362.63, 83.04);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (361.50, 83.04) --
-	(363.77, 83.04);
-\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (384.17,229.47) --
-	(386.44,229.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (385.30,229.47) --
-	(385.30, 69.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (384.17, 69.14) --
-	(386.44, 69.14);
-\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (406.84,243.12) --
-	(409.11,243.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (407.97,243.12) --
-	(407.97, 99.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (406.84, 99.45) --
-	(409.11, 99.45);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (473.48, 77.47) --
+	(476.61, 77.47);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (258.35, 52.60) rectangle (421.57,264.40);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (268.27, 52.60) rectangle (493.85,264.40);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
+\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
@@
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] ( 53.55,264.40) rectangle (216.77,277.04);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] ( 39.69,264.40) rectangle (265.26,277.04);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (135.16,267.41) {Ln(Min. Capital Dist.)$_{t-1}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (152.47,267.41) {Ln(Min. Capital Dist.)$_{t-1}$};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
+\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
@@
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (258.35,264.40) rectangle (421.57,277.04);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (268.27,264.40) rectangle (493.85,277.04);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (339.96,267.41) {Ln(Min. City Dist.)$_{t-1}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (381.06,267.41) {Ln(Min. City Dist.)$_{t-1}$};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
+\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 46.44, 58.92) {0e+00};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 59.21) {0.0};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 46.44,111.38) {3e-04};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,108.66) {0.5};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 46.44,163.84) {6e-04};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,158.12) {1.0};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 46.44,216.30) {9e-04};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,207.57) {1.5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,257.02) {2.0};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
+\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (251.24, 66.35) {0.00000};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 63.16, 40.81) {Fold A};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (251.24,111.91) {0.00025};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 94.49, 40.81) {Fold B};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (251.24,157.46) {0.00050};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (125.82, 40.81) {Fold C};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (251.24,203.02) {0.00075};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (157.15, 40.81) {Fold D};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (251.24,248.58) {0.00100};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (188.48, 40.81) {Fold E};
+
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (219.81, 40.81) {Fold F};
+
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (251.14, 40.81) {Fold G};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
+\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 71.83, 40.81) {Fold A};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (291.74, 40.81) {Fold A};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 94.50, 40.81) {Fold B};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (323.07, 40.81) {Fold B};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.17, 40.81) {Fold C};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (354.40, 40.81) {Fold C};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (139.84, 40.81) {Fold D};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (385.73, 40.81) {Fold D};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (162.51, 40.81) {Fold E};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (417.06, 40.81) {Fold E};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (185.17, 40.81) {Fold F};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (448.39, 40.81) {Fold F};
 
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (207.84, 40.81) {Fold G};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
-\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
-
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (276.63, 40.81) {Fold A};
-
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (299.30, 40.81) {Fold B};
-
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (321.97, 40.81) {Fold C};
-
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (344.64, 40.81) {Fold D};
-
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (367.31, 40.81) {Fold E};
-
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (389.98, 40.81) {Fold F};
-
-\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (412.65, 40.81) {Fold G};
+\node[text=drawColor,rotate= 45.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (479.72, 40.81) {Fold G};
 \end{scope}

### 2014-10-06 LaTeX/distGdp.tex
updating plots

% Created by tikzDevice version 0.7.0 on 2014-10-06 19:44:25
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (505.89,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 32.22, 34.03) rectangle (261.53,264.40);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] ( 32.22, 34.03) rectangle (261.53,264.40);
\definecolor[named]{fillColor}{rgb}{0.75,0.75,0.75}

\path[fill=fillColor] ( 40.41, 44.51) rectangle ( 89.55, 93.75);

\path[fill=fillColor] ( 95.01, 44.51) rectangle (144.14,159.24);

\path[fill=fillColor] (149.60, 44.51) rectangle (198.74,204.41);

\path[fill=fillColor] (204.20, 44.51) rectangle (253.34,210.90);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.52,137.78) --
	( 70.44,137.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.98,137.78) --
	( 64.98, 49.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.52, 49.72) --
	( 70.44, 49.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.12,191.72) --
	(125.04,191.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (119.58,191.72) --
	(119.58,126.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.12,126.77) --
	(125.04,126.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (168.71,232.19) --
	(179.63,232.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] (174.17,232.19) --
	(174.17,176.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (168.71,176.63) --
	(179.63,176.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.31,230.44) --
	(234.23,230.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.77,230.44) --
	(228.77,191.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.31,191.36) --
	(234.23,191.36);
\definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 32.22, 34.03) rectangle (261.53,264.40);
\end{scope}
\begin{scope}
\path[clip] (264.54, 34.03) rectangle (493.85,264.40);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] (264.54, 34.03) rectangle (493.85,264.40);
\definecolor[named]{fillColor}{rgb}{0.75,0.75,0.75}

\path[fill=fillColor] (272.73, 44.51) rectangle (321.87, 96.35);

\path[fill=fillColor] (327.33, 44.51) rectangle (376.46,135.46);

\path[fill=fillColor] (381.92, 44.51) rectangle (431.06,203.89);

\path[fill=fillColor] (436.52, 44.51) rectangle (485.66,230.96);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] (291.84,138.07) --
	(302.76,138.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (297.30,138.07) --
	(297.30, 54.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (291.84, 54.63) --
	(302.76, 54.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (346.43,174.04) --
	(357.35,174.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (351.89,174.04) --
	(351.89, 96.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] (346.43, 96.87) --
	(357.35, 96.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] (401.03,223.16) --
	(411.95,223.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] (406.49,223.16) --
	(406.49,184.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (401.03,184.61) --
	(411.95,184.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (455.63,253.93) --
	(466.55,253.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] (461.09,253.93) --
	(461.09,208.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (455.63,208.00) --
	(466.55,208.00);
\definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (264.54, 34.03) rectangle (493.85,264.40);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
\definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
\definecolor[named]{fillColor}{rgb}{0.80,0.80,0.80}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] ( 32.22,264.40) rectangle (261.53,277.04);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (146.87,267.41) {Ln(Min. Cap Dist.)$_{t-1}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
\definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
\definecolor[named]{fillColor}{rgb}{0.80,0.80,0.80}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (264.54,264.40) rectangle (493.85,277.04);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (379.19,267.41) {Ln(Min. City Dist.)$_{t-1}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11, 41.20) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11, 82.02) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11,122.84) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11,163.67) {3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11,204.49) {4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11,245.31) {5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 64.98, 20.31) {0-25$^{th}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (119.58, 20.31) {26-50$^{th}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (174.17, 20.31) {51-75$^{th}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (228.77, 20.31) {76-100$^{th}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (297.30, 20.31) {0-25$^{th}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (351.89, 20.31) {26-50$^{th}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (406.49, 20.31) {51-75$^{th}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (461.09, 20.31) {76-100$^{th}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at ( 14.29,149.22) {\% $\Delta$ Ln(GDP)$_{t}$};
\end{scope}
\end{tikzpicture}

### 2014-10-06 LaTeX/mCapSimPlot.tex
updating plots

--- 2014-09-23 LaTeX/mCapSimPlot.tex
@@
-% Created by tikzDevice version 0.7.0 on 2014-09-23 11:40:21
+% Created by tikzDevice version 0.7.0 on 2014-10-06 19:44:45
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 39.69, 34.03) rectangle (421.57,277.03);
+\path[clip] ( 35.42, 34.03) rectangle (421.57,277.03);
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
 
-\path[fill=fillColor] ( 39.69, 34.03) rectangle (421.57,277.03);
+\path[fill=fillColor] ( 35.42, 34.03) rectangle (421.57,277.03);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 57.05,107.99) --
-	( 61.80,109.63) --
-	( 66.56,111.28) --
-	( 71.31,112.93) --
-	( 76.07,114.58) --
-	( 80.82,116.22) --
-	( 85.58,117.87) --
-	( 90.34,119.52) --
-	( 95.09,121.16) --
-	( 99.85,122.81) --
-	(104.60,124.46) --
-	(109.36,126.11) --
-	(114.11,127.75) --
-	(118.87,129.40) --
-	(123.63,131.05) --
-	(128.38,132.70) --
-	(133.14,134.34) --
-	(137.89,135.99) --
-	(142.65,137.64) --
-	(147.40,139.28) --
-	(152.16,140.93) --
-	(156.92,142.58) --
-	(161.67,144.23) --
-	(166.43,145.87) --
-	(171.18,147.52) --
-	(175.94,149.17) --
-	(180.70,150.81) --
-	(185.45,152.46) --
-	(190.21,154.11) --
-	(194.96,155.76) --
-	(199.72,157.40) --
-	(204.47,159.05) --
-	(209.23,160.70) --
-	(213.99,162.34) --
-	(218.74,163.99) --
-	(223.50,165.64) --
-	(228.25,167.29) --
-	(233.01,168.93) --
-	(237.76,170.58) --
-	(242.52,172.23) --
-	(247.28,173.88) --
-	(252.03,175.52) --
-	(256.79,177.17) --
-	(261.54,178.82) --
-	(266.30,180.46) --
-	(271.05,182.11) --
-	(275.81,183.76) --
-	(280.57,185.41) --
-	(285.32,187.05) --
-	(290.08,188.70) --
-	(294.83,190.35) --
-	(299.59,191.99) --
-	(304.35,193.64) --
-	(309.10,195.29) --
-	(313.86,196.94) --
-	(318.61,198.58) --
-	(323.37,200.23) --
-	(328.12,201.88) --
-	(332.88,203.52) --
-	(337.64,205.17) --
-	(342.39,206.82) --
-	(347.15,208.47) --
-	(351.90,210.11) --
-	(356.66,211.76) --
-	(361.41,213.41) --
-	(366.17,215.05) --
-	(370.93,216.70) --
-	(375.68,218.35) --
-	(380.44,220.00) --
-	(385.19,221.64) --
-	(389.95,223.29) --
-	(394.70,224.94) --
-	(399.46,226.59) --
-	(404.22,228.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,105.62) --
+	( 60.61,108.24) --
+	( 64.85,109.70) --
+	( 64.98,109.74) --
+	( 78.30,114.31) --
+	( 86.71,117.20) --
+	( 92.34,119.13) --
+	( 95.59,120.24) --
+	(101.92,122.42) --
+	(110.88,125.49) --
+	(154.64,140.51) --
+	(158.01,141.66) --
+	(171.43,146.26) --
+	(178.49,148.69) --
+	(187.92,151.92) --
+	(192.71,153.57) --
+	(195.62,154.56) --
+	(195.71,154.59) --
+	(196.35,154.81) --
+	(198.04,155.39) --
+	(199.87,156.02) --
+	(204.99,157.78) --
+	(205.19,157.85) --
+	(209.65,159.38) --
+	(211.50,160.01) --
+	(215.87,161.51) --
+	(217.33,162.01) --
+	(217.43,162.05) --
+	(217.68,162.13) --
+	(218.17,162.30) --
+	(220.17,162.99) --
+	(220.33,163.04) --
+	(220.93,163.25) --
+	(221.63,163.49) --
+	(222.58,163.81) --
+	(223.29,164.06) --
+	(223.54,164.14) --
+	(223.59,164.16) --
+	(224.00,164.30) --
+	(229.14,166.07) --
+	(231.15,166.76) --
+	(231.34,166.82) --
+	(232.39,167.18) --
+	(233.34,167.51) --
+	(234.25,167.82) --
+	(235.24,168.16) --
+	(236.22,168.49) --
+	(237.40,168.90) --
+	(237.41,168.90) --
+	(239.29,169.55) --
+	(239.31,169.55) --
+	(240.03,169.80) --
+	(240.80,170.06) --
+	(241.27,170.23) --
+	(241.65,170.36) --
+	(242.95,170.80) --
+	(244.78,171.43) --
+	(248.30,172.64) --
+	(249.74,173.13) --
+	(250.22,173.30) --
+	(250.38,173.35) --
+	(250.69,173.46) --
+	(251.97,173.90) --
+	(252.46,174.07) --
+	(253.69,174.49) --
+	(253.89,174.55) --
+	(254.34,174.71) --
+	(255.74,175.19) --
+	(256.94,175.60) --
+	(258.99,176.31) --
+	(260.08,176.68) --
+	(260.16,176.71) --
+	(261.39,177.13) --
+	(262.57,177.53) --
+	(263.47,177.84) --
+	(264.14,178.07) --
+	(264.43,178.17) --
+	(264.94,178.35) --
+	(265.11,178.40) --
+	(265.48,178.53) --
+	(265.54,178.55) --
+	(266.69,178.95) --
+	(266.70,178.95) --
+	(267.74,179.31) --
+	(267.83,179.34) --
+	(267.95,179.38) --
+	(268.15,179.45) --
+	(268.32,179.51) --
+	(268.51,179.57) --
+	(268.75,179.66) --
+	(269.12,179.78) --
+	(269.30,179.84) --
+	(269.75,180.00) --
+	(269.91,180.05) --
+	(271.51,180.60) --
+	(272.31,180.88) --
+	(272.40,180.91) --
+	(272.91,181.08) --
+	(273.01,181.11) --
+	(273.29,181.21) --
+	(273.48,181.28) --
+	(274.31,181.56) --
+	(274.85,181.75) --
+	(274.88,181.76) --
+	(275.50,181.97) --
+	(276.03,182.15) --
+	(276.14,182.19) --
+	(276.73,182.39) --
+	(276.77,182.41) --
+	(277.28,182.58) --
+	(277.37,182.61) --
+	(278.83,183.11) --
+	(278.93,183.15) --
+	(278.99,183.17) --
+	(279.03,183.18) --
+	(279.36,183.30) --
+	(279.83,183.46) --
+	(279.90,183.48) --
+	(280.21,183.59) --
+	(280.36,183.64) --
+	(280.41,183.66) --
+	(280.47,183.68) --
+	(280.50,183.68) --
+	(280.60,183.72) --
+	(280.63,183.73) --
+	(281.16,183.91) --
+	(281.52,184.03) --
+	(281.60,184.06) --
+	(283.10,184.58) --
+	(283.28,184.64) --
+	(283.34,184.66) --
+	(283.74,184.80) --
+	(283.80,184.82) --
+	(284.26,184.97) --
+	(284.43,185.03) --
+	(284.75,185.14) --
+	(284.80,185.16) --
+	(284.81,185.16) --
+	(284.81,185.16) --
+	(284.84,185.18) --
+	(284.88,185.19) --
+	(285.44,185.38) --
+	(285.67,185.46) --
+	(286.04,185.59) --
+	(286.70,185.81) --
+	(286.95,185.90) --
+	(287.76,186.18) --
+	(288.16,186.31) --
+	(288.45,186.41) --
+	(288.86,186.55) --
+	(289.03,186.61) --
+	(289.13,186.65) --
+	(289.30,186.70) --
+	(289.61,186.81) --
+	(289.71,186.85) --
+	(289.99,186.94) --
+	(290.44,187.10) --
+	(291.29,187.39) --
+	(291.45,187.44) --
+	(291.58,187.49) --
+	(292.20,187.70) --
+	(292.36,187.75) --
+	(292.77,187.89) --
+	(292.78,187.90) --
+	(292.85,187.92) --
+	(292.94,187.95) --
+	(293.49,188.14) --
+	(293.61,188.18) --
+	(293.90,188.28) --
+	(293.94,188.30) --
+	(295.12,188.70) --
+	(295.85,188.95) --
+	(296.61,189.21) --
+	(297.11,189.38) --
+	(297.99,189.68) --
+	(298.09,189.72) --
+	(298.13,189.74) --
+	(298.21,189.76) --
+	(298.45,189.84) --
+	(298.48,189.85) --
+	(298.71,189.93) --
+	(298.89,190.00) --
+	(299.22,190.11) --
+	(300.07,190.40) --
+	(300.69,190.61) --
+	(301.34,190.83) --
+	(301.81,191.00) --
+	(301.86,191.01) --
+	(302.06,191.08) --
+	(302.08,191.09) --
+	(302.20,191.13) --
+	(302.30,191.16) --
+	(302.45,191.22) --
+	(302.52,191.24) --
+	(302.61,191.27) --
+	(302.89,191.37) --
+	(302.93,191.38) --
+	(303.17,191.46) --
+	(304.10,191.78) --
+	(304.31,191.85) --
+	(304.47,191.91) --
+	(304.48,191.91) --
+	(304.60,191.95) --
+	(304.68,191.98) --
+	(305.11,192.13) --
+	(305.28,192.19) --
+	(305.76,192.35) --
+	(305.86,192.39) --
+	(306.15,192.49) --
+	(307.03,192.79) --
+	(307.16,192.83) --
+	(307.37,192.90) --
+	(308.42,193.27) --
+	(308.63,193.34) --
+	(308.79,193.39) --
+	(309.08,193.49) --
+	(309.55,193.65) --
+	(309.72,193.71) --
+	(310.36,193.93) --
+	(310.45,193.96) --
+	(310.80,194.08) --
+	(310.98,194.14) --
+	(311.09,194.18) --
+	(311.49,194.32) --
+	(311.71,194.39) --
+	(311.87,194.45) --
+	(312.39,194.63) --
+	(312.68,194.73) --
+	(312.75,194.75) --
+	(314.09,195.21) --
+	(314.12,195.22) --
+	(314.55,195.37) --
+	(314.84,195.47) --
+	(315.05,195.54) --
+	(315.28,195.62) --
+	(315.54,195.71) --
+	(315.61,195.73) --
+	(315.65,195.75) --
+	(316.29,195.97) --
+	(316.37,195.99) --
+	(316.58,196.06) --
+	(316.61,196.07) --
+	(316.72,196.11) --
+	(317.13,196.25) --
+	(318.60,196.76) --
+	(319.14,196.94) --
+	(320.71,197.48) --
+	(321.34,197.70) --
+	(321.47,197.74) --
+	(322.56,198.12) --
+	(322.64,198.14) --
+	(322.93,198.24) --
+	(323.98,198.60) --
+	(324.06,198.63) --
+	(324.53,198.79) --
+	(324.82,198.89) --
+	(325.46,199.11) --
+	(325.85,199.24) --
+	(325.87,199.25) --
+	(325.91,199.27) --
+	(326.16,199.35) --
+	(326.46,199.45) --
+	(327.01,199.64) --
+	(327.50,199.81) --
+	(327.78,199.91) --
+	(328.37,200.11) --
+	(328.92,200.30) --
+	(330.17,200.73) --
+	(330.38,200.80) --
+	(330.88,200.97) --
+	(333.53,201.88) --
+	(333.56,201.89) --
+	(333.69,201.94) --
+	(333.82,201.98) --
+	(333.83,201.98) --
+	(335.38,202.51) --
+	(335.47,202.55) --
+	(337.65,203.29) --
+	(338.50,203.58) --
+	(338.83,203.70) --
+	(338.87,203.71) --
+	(339.04,203.77) --
+	(339.21,203.83) --
+	(339.40,203.89) --
+	(339.55,203.94) --
+	(339.76,204.02) --
+	(339.84,204.04) --
+	(340.15,204.15) --
+	(340.28,204.20) --
+	(340.65,204.32) --
+	(341.52,204.62) --
+	(342.53,204.97) --
+	(343.79,205.40) --
+	(343.95,205.45) --
+	(345.11,205.85) --
+	(345.20,205.89) --
+	(345.78,206.08) --
+	(346.49,206.33) --
+	(346.80,206.43) --
+	(346.94,206.48) --
+	(347.30,206.60) --
+	(348.63,207.06) --
+	(348.84,207.13) --
+	(349.59,207.39) --
+	(350.01,207.53) --
+	(350.27,207.62) --
+	(350.57,207.73) --
+	(351.61,208.08) --
+	(352.50,208.39) --
+	(354.60,209.11) --
+	(354.77,209.17) --
+	(355.03,209.26) --
+	(355.06,209.27) --
+	(355.38,209.38) --
+	(355.44,209.40) --
+	(355.66,209.47) --
+	(355.69,209.48) --
+	(356.06,209.61) --
+	(356.08,209.62) --
+	(356.57,209.78) --
+	(356.86,209.88) --
+	(356.99,209.93) --
+	(357.04,209.94) --
+	(357.10,209.97) --
+	(357.28,210.03) --
+	(357.68,210.17) --
+	(357.71,210.18) --
+	(358.36,210.40) --
+	(358.45,210.43) --
+	(358.80,210.55) --
+	(359.58,210.82) --
+	(360.14,211.01) --
+	(360.17,211.02) --
+	(360.28,211.06) --
+	(360.68,211.20) --
+	(362.54,211.83) --
+	(362.92,211.96) --
+	(362.99,211.99) --
+	(362.99,211.99) --
+	(363.68,212.22) --
+	(363.71,212.23) --
+	(364.25,212.42) --
+	(364.57,212.53) --
+	(364.77,212.60) --
+	(365.00,212.68) --
+	(365.26,212.76) --
+	(365.84,212.96) --
+	(365.84,212.96) --
+	(365.92,212.99) --
+	(366.04,213.03) --
+	(366.47,213.18) --
+	(367.05,213.38) --
+	(368.20,213.78) --
+	(368.39,213.84) --
+	(368.50,213.88) --
+	(370.21,214.46) --
+	(371.17,214.79) --
+	(371.58,214.94) --
+	(372.02,215.09) --
+	(373.58,215.62) --
+	(376.96,216.78) --
+	(378.52,217.32) --
+	(383.85,219.15) --
+	(384.44,219.35) --
+	(384.92,219.51) --
+	(385.30,219.64) --
+	(385.73,219.79) --
+	(385.96,219.87) --
+	(386.70,220.12) --
+	(386.81,220.16) --
+	(387.17,220.28) --
+	(387.19,220.29) --
+	(387.24,220.31) --
+	(387.39,220.36) --
+	(387.67,220.46) --
+	(388.26,220.66) --
+	(389.16,220.97) --
+	(389.82,221.19) --
+	(390.40,221.39) --
+	(390.44,221.41) --
+	(390.79,221.53) --
+	(391.07,221.62) --
+	(395.16,223.02) --
+	(396.00,223.31) --
+	(396.15,223.37) --
+	(403.52,225.89) --
+	(404.02,226.07);
 \definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}
 
-\path[fill=fillColor,fill opacity=0.30] ( 57.05,170.30) --
-	( 61.80,170.75) --
-	( 66.56,171.43) --
-	( 71.31,172.00) --
-	( 76.07,172.73) --
-	( 80.82,173.39) --
-	( 85.58,174.13) --
-	( 90.34,174.65) --
-	( 95.09,175.20) --
-	( 99.85,175.83) --
-	(104.60,176.50) --
-	(109.36,177.16) --
-	(114.11,177.80) --
-	(118.87,178.59) --
-	(123.63,179.29) --
-	(128.38,179.81) --
-	(133.14,180.41) --
-	(137.89,181.20) --
-	(142.65,181.89) --
-	(147.40,182.78) --
-	(152.16,183.41) --
-	(156.92,183.93) --
-	(161.67,184.69) --
-	(166.43,185.42) --
-	(171.18,186.20) --
-	(175.94,187.05) --
-	(180.70,188.02) --
-	(185.45,188.60) --
-	(190.21,189.50) --
-	(194.96,190.46) --
-	(199.72,191.24) --
-	(204.47,192.15) --
-	(209.23,193.07) --
-	(213.99,194.11) --
-	(218.74,195.08) --
-	(223.50,196.00) --
-	(228.25,196.95) --
-	(233.01,198.08) --
-	(237.76,199.37) --
-	(242.52,200.49) --
-	(247.28,201.79) --
-	(252.03,203.07) --
-	(256.79,204.30) --
-	(261.54,205.54) --
-	(266.30,207.04) --
-	(271.05,208.33) --
-	(275.81,209.80) --
-	(280.57,211.29) --
-	(285.32,212.83) --
-	(290.08,214.53) --
-	(294.83,216.23) --
-	(299.59,217.85) --
-	(304.35,219.60) --
-	(309.10,221.58) --
-	(313.86,223.41) --
-	(318.61,225.32) --
-	(323.37,227.31) --
-	(328.12,229.50) --
-	(332.88,231.70) --
-	(337.64,233.85) --
-	(342.39,235.89) --
-	(347.15,238.03) --
-	(351.90,240.17) --
-	(356.66,242.38) --
-	(361.41,244.58) --
-	(366.17,246.95) --
-	(370.93,249.06) --
-	(375.68,251.34) --
-	(380.44,253.72) --
-	(385.19,255.97) --
-	(389.95,258.60) --
-	(394.70,261.10) --
-	(399.46,263.65) --
-	(404.22,265.99) --
-	(404.22,189.23) --
-	(399.46,188.51) --
-	(394.70,187.90) --
-	(389.95,187.02) --
-	(385.19,186.13) --
-	(380.44,185.09) --
-	(375.68,184.39) --
-	(370.93,183.61) --
-	(366.17,182.69) --
-	(361.41,181.83) --
-	(356.66,180.81) --
-	(351.90,179.77) --
-	(347.15,178.57) --
-	(342.39,177.44) --
-	(337.64,176.32) --
-	(332.88,175.29) --
-	(328.12,174.08) --
-	(323.37,172.90) --
-	(318.61,171.57) --
-	(313.86,170.24) --
-	(309.10,168.76) --
-	(304.35,167.31) --
-	(299.59,165.82) --
-	(294.83,164.52) --
-	(290.08,162.91) --
-	(285.32,161.16) --
-	(280.57,159.46) --
-	(275.81,157.79) --
-	(271.05,155.95) --
-	(266.30,154.07) --
-	(261.54,152.24) --
-	(256.79,150.23) --
-	(252.03,148.25) --
-	(247.28,146.22) --
-	(242.52,143.99) --
-	(237.76,141.83) --
-	(233.01,139.84) --
-	(228.25,137.63) --
-	(223.50,135.49) --
-	(218.74,133.10) --
-	(213.99,130.62) --
-	(209.23,128.31) --
-	(204.47,125.87) --
-	(199.72,123.59) --
-	(194.96,121.22) --
-	(190.21,118.75) --
-	(185.45,116.43) --
-	(180.70,114.03) --
-	(175.94,111.47) --
-	(171.18,108.99) --
-	(166.43,106.38) --
-	(161.67,103.74) --
-	(156.92,101.22) --
-	(152.16, 98.74) --
-	(147.40, 96.24) --
-	(142.65, 93.73) --
-	(137.89, 91.21) --
-	(133.14, 88.50) --
-	(128.38, 85.77) --
-	(123.63, 83.16) --
-	(118.87, 80.48) --
-	(114.11, 77.79) --
-	(109.36, 75.08) --
-	(104.60, 72.30) --
-	( 99.85, 69.52) --
-	( 95.09, 66.86) --
-	( 90.34, 64.14) --
-	( 85.58, 61.43) --
-	( 80.82, 58.71) --
-	( 76.07, 55.94) --
-	( 71.31, 53.21) --
-	( 66.56, 50.50) --
-	( 61.80, 47.80) --
-	( 57.05, 45.08) --
+\path[fill=fillColor,fill opacity=0.30] ( 52.97,165.20) --
+	( 60.61,166.06) --
+	( 64.85,166.50) --
+	( 64.98,166.52) --
+	( 78.30,168.34) --
+	( 86.71,169.62) --
+	( 92.34,170.49) --
+	( 95.59,171.09) --
+	(101.92,171.91) --
+	(110.88,173.03) --
+	(154.64,179.87) --
+	(158.01,180.61) --
+	(171.43,182.79) --
+	(178.49,184.14) --
+	(187.92,186.16) --
+	(192.71,186.96) --
+	(195.62,187.49) --
+	(195.71,187.52) --
+	(196.35,187.67) --
+	(198.04,187.95) --
+	(199.87,188.32) --
+	(204.99,189.26) --
+	(205.19,189.29) --
+	(209.65,190.35) --
+	(211.50,190.74) --
+	(215.87,191.88) --
+	(217.33,192.18) --
+	(217.43,192.18) --
+	(217.68,192.24) --
+	(218.17,192.39) --
+	(220.17,192.85) --
+	(220.33,192.86) --
+	(220.93,193.03) --
+	(221.63,193.24) --
+	(222.58,193.40) --
+	(223.29,193.54) --
+	(223.54,193.60) --
+	(223.59,193.62) --
+	(224.00,193.67) --
+	(229.14,194.98) --
+	(231.15,195.48) --
+	(231.34,195.52) --
+	(232.39,195.71) --
+	(233.34,195.91) --
+	(234.25,196.12) --
+	(235.24,196.41) --
+	(236.22,196.59) --
+	(237.40,196.88) --
+	(237.41,196.88) --
+	(239.29,197.35) --
+	(239.31,197.35) --
+	(240.03,197.54) --
+	(240.80,197.71) --
+	(241.27,197.83) --
+	(241.65,197.94) --
+	(242.95,198.33) --
+	(244.78,198.83) --
+	(248.30,199.74) --
+	(249.74,200.06) --
+	(250.22,200.25) --
+	(250.38,200.30) --
+	(250.69,200.38) --
+	(251.97,200.79) --
+	(252.46,200.89) --
+	(253.69,201.25) --
+	(253.89,201.30) --
+	(254.34,201.47) --
+	(255.74,201.84) --
+	(256.94,202.18) --
+	(258.99,202.81) --
+	(260.08,203.21) --
+	(260.16,203.23) --
+	(261.39,203.62) --
+	(262.57,204.01) --
+	(263.47,204.17) --
+	(264.14,204.36) --
+	(264.43,204.44) --
+	(264.94,204.64) --
+	(265.11,204.71) --
+	(265.48,204.84) --
+	(265.54,204.86) --
+	(266.69,205.27) --
+	(266.70,205.27) --
+	(267.74,205.67) --
+	(267.83,205.69) --
+	(267.95,205.73) --
+	(268.15,205.80) --
+	(268.32,205.86) --
+	(268.51,205.91) --
+	(268.75,206.03) --
+	(269.12,206.13) --
+	(269.30,206.19) --
+	(269.75,206.29) --
+	(269.91,206.34) --
+	(271.51,206.93) --
+	(272.31,207.26) --
+	(272.40,207.29) --
+	(272.91,207.46) --
+	(273.01,207.49) --
+	(273.29,207.60) --
+	(273.48,207.63) --
+	(274.31,207.88) --
+	(274.85,208.05) --
+	(274.88,208.05) --
+	(275.50,208.31) --
+	(276.03,208.51) --
+	(276.14,208.54) --
+	(276.73,208.71) --
+	(276.77,208.72) --
+	(277.28,208.92) --
+	(277.37,208.95) --
+	(278.83,209.44) --
+	(278.93,209.48) --
+	(278.99,209.50) --
+	(279.03,209.51) --
+	(279.36,209.57) --
+	(279.83,209.71) --
+	(279.90,209.72) --
+	(280.21,209.80) --
+	(280.36,209.87) --
+	(280.41,209.89) --
+	(280.47,209.91) --
+	(280.50,209.92) --
+	(280.60,209.95) --
+	(280.63,209.96) --
+	(281.16,210.14) --
+	(281.52,210.28) --
+	(281.60,210.32) --
+	(283.10,210.87) --
+	(283.28,210.96) --
+	(283.34,210.98) --
+	(283.74,211.11) --
+	(283.80,211.13) --
+	(284.26,211.28) --
+	(284.43,211.32) --
+	(284.75,211.44) --
+	(284.80,211.46) --
+	(284.81,211.46) --
+	(284.81,211.46) --
+	(284.84,211.48) --
+	(284.88,211.49) --
+	(285.44,211.69) --
+	(285.67,211.76) --
+	(286.04,211.88) --
+	(286.70,212.11) --
+	(286.95,212.19) --
+	(287.76,212.60) --
+	(288.16,212.75) --
+	(288.45,212.88) --
+	(288.86,212.98) --
+	(289.03,213.01) --
+	(289.13,213.03) --
+	(289.30,213.12) --
+	(289.61,213.30) --
+	(289.71,213.32) --
+	(289.99,213.40) --
+	(290.44,213.53) --
+	(291.29,213.87) --
+	(291.45,213.92) --
+	(291.58,213.96) --
+	(292.20,214.19) --
+	(292.36,214.26) --
+	(292.77,214.38) --
+	(292.78,214.39) --
+	(292.85,214.43) --
+	(292.94,214.45) --
+	(293.49,214.66) --
+	(293.61,214.72) --
+	(293.90,214.85) --
+	(293.94,214.86) --
+	(295.12,215.33) --
+	(295.85,215.63) --
+	(296.61,215.90) --
+	(297.11,216.10) --
+	(297.99,216.47) --
+	(298.09,216.52) --
+	(298.13,216.53) --
+	(298.21,216.57) --
+	(298.45,216.67) --
+	(298.48,216.68) --
+	(298.71,216.78) --
+	(298.89,216.86) --
+	(299.22,217.00) --
+	(300.07,217.37) --
+	(300.69,217.67) --
+	(301.34,217.95) --
+	(301.81,218.15) --
+	(301.86,218.17) --
+	(302.06,218.25) --
+	(302.08,218.25) --
+	(302.20,218.30) --
+	(302.30,218.33) --
+	(302.45,218.39) --
+	(302.52,218.41) --
+	(302.61,218.44) --
+	(302.89,218.54) --
+	(302.93,218.56) --
+	(303.17,218.62) --
+	(304.10,218.98) --
+	(304.31,219.07) --
+	(304.47,219.12) --
+	(304.48,219.12) --
+	(304.60,219.15) --
+	(304.68,219.18) --
+	(305.11,219.34) --
+	(305.28,219.40) --
+	(305.76,219.62) --
+	(305.86,219.66) --
+	(306.15,219.79) --
+	(307.03,220.15) --
+	(307.16,220.21) --
+	(307.37,220.28) --
+	(308.42,220.71) --
+	(308.63,220.77) --
+	(308.79,220.81) --
+	(309.08,220.91) --
+	(309.55,221.07) --
+	(309.72,221.11) --
+	(310.36,221.34) --
+	(310.45,221.38) --
+	(310.80,221.53) --
+	(310.98,221.58) --
+	(311.09,221.61) --
+	(311.49,221.78) --
+	(311.71,221.89) --
+	(311.87,221.97) --
+	(312.39,222.22) --
+	(312.68,222.34) --
+	(312.75,222.36) --
+	(314.09,222.97) --
+	(314.12,222.98) --
+	(314.55,223.10) --
+	(314.84,223.21) --
+	(315.05,223.29) --
+	(315.28,223.38) --
+	(315.54,223.48) --
+	(315.61,223.51) --
+	(315.65,223.53) --
+	(316.29,223.77) --
+	(316.37,223.80) --
+	(316.58,223.88) --
+	(316.61,223.90) --
+	(316.72,223.94) --
+	(317.13,224.10) --
+	(318.60,224.77) --
+	(319.14,224.99) --
+	(320.71,225.74) --
+	(321.34,226.00) --
+	(321.47,226.05) --
+	(322.56,226.60) --
+	(322.64,226.65) --
+	(322.93,226.81) --
+	(323.98,227.18) --
+	(324.06,227.23) --
+	(324.53,227.46) --
+	(324.82,227.58) --
+	(325.46,227.82) --
+	(325.85,227.92) --
+	(325.87,227.93) --
+	(325.91,227.95) --
+	(326.16,228.06) --
+	(326.46,228.20) --
+	(327.01,228.46) --
+	(327.50,228.65) --
+	(327.78,228.76) --
+	(328.37,229.01) --
+	(328.92,229.25) --
+	(330.17,229.78) --
+	(330.38,229.89) --
+	(330.88,230.12) --
+	(333.53,231.30) --
+	(333.56,231.31) --
+	(333.69,231.37) --
+	(333.82,231.43) --
+	(333.83,231.43) --
+	(335.38,232.11) --
+	(335.47,232.16) --
+	(337.65,233.11) --
+	(338.50,233.49) --
+	(338.83,233.64) --
+	(338.87,233.66) --
+	(339.04,233.73) --
+	(339.21,233.80) --
+	(339.40,233.89) --
+	(339.55,233.95) --
+	(339.76,234.05) --
+	(339.84,234.09) --
+	(340.15,234.23) --
+	(340.28,234.29) --
+	(340.65,234.46) --
+	(341.52,234.87) --
+	(342.53,235.38) --
+	(343.79,235.96) --
+	(343.95,236.03) --
+	(345.11,236.65) --
+	(345.20,236.70) --
+	(345.78,236.95) --
+	(346.49,237.30) --
+	(346.80,237.45) --
+	(346.94,237.52) --
+	(347.30,237.70) --
+	(348.63,238.33) --
+	(348.84,238.43) --
+	(349.59,238.82) --
+	(350.01,239.02) --
+	(350.27,239.13) --
+	(350.57,239.26) --
+	(351.61,239.72) --
+	(352.50,240.14) --
+	(354.60,241.18) --
+	(354.77,241.25) --
+	(355.03,241.37) --
+	(355.06,241.39) --
+	(355.38,241.55) --
+	(355.44,241.59) --
+	(355.66,241.70) --
+	(355.69,241.71) --
+	(356.06,241.93) --
+	(356.08,241.93) --
+	(356.57,242.19) --
+	(356.86,242.34) --
+	(356.99,242.41) --
+	(357.04,242.44) --
+	(357.10,242.47) --
+	(357.28,242.56) --
+	(357.68,242.77) --
+	(357.71,242.78) --
+	(358.36,243.06) --
+	(358.45,243.11) --
+	(358.80,243.27) --
+	(359.58,243.64) --
+	(360.14,243.89) --
+	(360.17,243.90) --
+	(360.28,243.94) --
+	(360.68,244.14) --
+	(362.54,245.11) --
+	(362.92,245.32) --
+	(362.99,245.36) --
+	(362.99,245.36) --
+	(363.68,245.73) --
+	(363.71,245.75) --
+	(364.25,246.04) --
+	(364.57,246.19) --
+	(364.77,246.29) --
+	(365.00,246.40) --
+	(365.26,246.54) --
+	(365.84,246.88) --
+	(365.84,246.88) --
+	(365.92,246.92) --
+	(366.04,246.98) --
+	(366.47,247.19) --
+	(367.05,247.46) --
+	(368.20,247.96) --
+	(368.39,248.07) --
+	(368.50,248.14) --
+	(370.21,248.93) --
+	(371.17,249.41) --
+	(371.58,249.67) --
+	(372.02,249.86) --
+	(373.58,250.61) --
+	(376.96,252.31) --
+	(378.52,252.97) --
+	(383.85,255.72) --
+	(384.44,256.00) --
+	(384.92,256.23) --
+	(385.30,256.42) --
+	(385.73,256.63) --
+	(385.96,256.74) --
+	(386.70,257.14) --
+	(386.81,257.19) --
+	(387.17,257.37) --
+	(387.19,257.37) --
+	(387.24,257.39) --
+	(387.39,257.47) --
+	(387.67,257.63) --
+	(388.26,257.95) --
+	(389.16,258.36) --
+	(389.82,258.71) --
+	(390.40,258.98) --
+	(390.44,259.01) --
+	(390.79,259.17) --
+	(391.07,259.30) --
+	(395.16,261.28) --
+	(396.00,261.69) --
+	(396.15,261.76) --
+	(403.52,265.67) --
+	(404.02,265.99) --
+	(404.02,186.16) --
+	(403.52,186.07) --
+	(396.15,184.62) --
+	(396.00,184.56) --
+	(395.16,184.43) --
+	(391.07,183.78) --
+	(390.79,183.76) --
+	(390.44,183.72) --
+	(390.40,183.71) --
+	(389.82,183.64) --
+	(389.16,183.56) --
+	(388.26,183.43) --
+	(387.67,183.32) --
+	(387.39,183.25) --
+	(387.24,183.21) --
+	(387.19,183.20) --
+	(387.17,183.20) --
+	(386.81,183.11) --
+	(386.70,183.09) --
+	(385.96,182.98) --
+	(385.73,182.95) --
+	(385.30,182.87) --
+	(384.92,182.82) --
+	(384.44,182.79) --
+	(383.85,182.69) --
+	(378.52,181.63) --
+	(376.96,181.35) --
+	(373.58,180.87) --
+	(372.02,180.66) --
+	(371.58,180.64) --
+	(371.17,180.60) --
+	(370.21,180.44) --
+	(368.50,180.16) --
+	(368.39,180.14) --
+	(368.20,180.08) --
+	(367.05,179.83) --
+	(366.47,179.68) --
+	(366.04,179.56) --
+	(365.92,179.53) --
+	(365.84,179.51) --
+	(365.84,179.51) --
+	(365.26,179.35) --
+	(365.00,179.28) --
+	(364.77,179.25) --
+	(364.57,179.24) --
+	(364.25,179.17) --
+	(363.71,179.04) --
+	(363.68,179.03) --
+	(362.99,178.85) --
+	(362.99,178.85) --
+	(362.92,178.84) --
+	(362.54,178.74) --
+	(360.68,178.40) --
+	(360.28,178.30) --
+	(360.17,178.31) --
+	(360.14,178.31) --
+	(359.58,178.27) --
+	(358.80,178.08) --
+	(358.45,178.01) --
+	(358.36,177.98) --
+	(357.71,177.80) --
+	(357.68,177.80) --
+	(357.28,177.74) --
+	(357.10,177.72) --
+	(357.04,177.72) --
+	(356.99,177.71) --
+	(356.86,177.70) --
+	(356.57,177.64) --
+	(356.08,177.49) --
+	(356.06,177.49) --
+	(355.69,177.37) --
+	(355.66,177.36) --
+	(355.44,177.32) --
+	(355.38,177.31) --
+	(355.06,177.26) --
+	(355.03,177.25) --
+	(354.77,177.22) --
+	(354.60,177.19) --
+	(352.50,176.92) --
+	(351.61,176.70) --
+	(350.57,176.49) --
+	(350.27,176.47) --
+	(350.01,176.37) --
+	(349.59,176.23) --
+	(348.84,176.03) --
+	(348.63,175.98) --
+	(347.30,175.74) --
+	(346.94,175.67) --
+	(346.80,175.64) --
+	(346.49,175.53) --
+	(345.78,175.33) --
+	(345.20,175.23) --
+	(345.11,175.20) --
+	(343.95,174.89) --
+	(343.79,174.84) --
+	(342.53,174.62) --
+	(341.52,174.45) --
+	(340.65,174.27) --
+	(340.28,174.16) --
+	(340.15,174.10) --
+	(339.84,174.03) --
+	(339.76,174.02) --
+	(339.55,173.99) --
+	(339.40,173.93) --
+	(339.21,173.87) --
+	(339.04,173.82) --
+	(338.87,173.77) --
+	(338.83,173.76) --
+	(338.50,173.69) --
+	(337.65,173.44) --
+	(335.47,172.96) --
+	(335.38,172.95) --
+	(333.83,172.52) --
+	(333.82,172.52) --
+	(333.69,172.48) --
+	(333.56,172.45) --
+	(333.53,172.44) --
+	(330.88,171.81) --
+	(330.38,171.72) --
+	(330.17,171.68) --
+	(328.92,171.37) --
+	(328.37,171.15) --
+	(327.78,170.98) --
+	(327.50,170.92) --
+	(327.01,170.77) --
+	(326.46,170.62) --
+	(326.16,170.57) --
+	(325.91,170.51) --
+	(325.87,170.51) --
+	(325.85,170.51) --
+	(325.46,170.40) --
+	(324.82,170.21) --
+	(324.53,170.21) --
+	(324.06,170.15) --
+	(323.98,170.13) --
+	(322.93,169.85) --
+	(322.64,169.82) --
+	(322.56,169.82) --
+	(321.47,169.46) --
+	(321.34,169.40) --
+	(320.71,169.24) --
+	(319.14,168.74) --
+	(318.60,168.64) --
+	(317.13,168.18) --
+	(316.72,168.05) --
+	(316.61,168.01) --
+	(316.58,168.00) --
+	(316.37,167.93) --
+	(316.29,167.90) --
+	(315.65,167.68) --
+	(315.61,167.67) --
+	(315.54,167.65) --
+	(315.28,167.58) --
+	(315.05,167.51) --
+	(314.84,167.42) --
+	(314.55,167.33) --
+	(314.12,167.22) --
+	(314.09,167.21) --
+	(312.75,166.87) --
+	(312.68,166.86) --
+	(312.39,166.79) --
+	(311.87,166.57) --
+	(311.71,166.51) --
+	(311.49,166.45) --
+	(311.09,166.35) --
+	(310.98,166.33) --
+	(310.80,166.29) --
+	(310.45,166.23) --
+	(310.36,166.21) --
+	(309.72,166.00) --
+	(309.55,165.96) --
+	(309.08,165.82) --
+	(308.79,165.72) --
+	(308.63,165.67) --
+	(308.42,165.62) --
+	(307.37,165.33) --
+	(307.16,165.25) --
+	(307.03,165.22) --
+	(306.15,165.04) --
+	(305.86,164.98) --
+	(305.76,164.96) --
+	(305.28,164.84) --
+	(305.11,164.79) --
+	(304.68,164.71) --
+	(304.60,164.69) --
+	(304.48,164.65) --
+	(304.47,164.64) --
+	(304.31,164.58) --
+	(304.10,164.53) --
+	(303.17,164.22) --
+	(302.93,164.15) --
+	(302.89,164.14) --
+	(302.61,164.07) --
+	(302.52,164.04) --
+	(302.45,164.03) --
+	(302.30,164.00) --
+	(302.20,163.98) --
+	(302.08,163.95) --
+	(302.06,163.95) --
+	(301.86,163.90) --
+	(301.81,163.89) --
+	(301.34,163.78) --
+	(300.69,163.54) --
+	(300.07,163.35) --
+	(299.22,163.00) --
+	(298.89,162.91) --
+	(298.71,162.85) --
+	(298.48,162.77) --
+	(298.45,162.76) --
+	(298.21,162.69) --
+	(298.13,162.66) --
+	(298.09,162.65) --
+	(297.99,162.62) --
+	(297.11,162.35) --
+	(296.61,162.22) --
+	(295.85,161.97) --
+	(295.12,161.73) --
+	(293.94,161.38) --
+	(293.90,161.37) --
+	(293.61,161.27) --
+	(293.49,161.22) --
+	(292.94,161.03) --
+	(292.85,161.01) --
+	(292.78,160.99) --
+	(292.77,160.98) --
+	(292.36,160.87) --
+	(292.20,160.82) --
+	(291.58,160.61) --
+	(291.45,160.57) --
+	(291.29,160.52) --
+	(290.44,160.26) --
+	(289.99,160.13) --
+	(289.71,160.04) --
+	(289.61,160.00) --
+	(289.30,159.87) --
+	(289.13,159.80) --
+	(289.03,159.75) --
+	(288.86,159.69) --
+	(288.45,159.56) --
+	(288.16,159.43) --
+	(287.76,159.26) --
+	(286.95,158.94) --
+	(286.70,158.84) --
+	(286.04,158.62) --
+	(285.67,158.49) --
+	(285.44,158.44) --
+	(284.88,158.24) --
+	(284.84,158.23) --
+	(284.81,158.22) --
+	(284.81,158.22) --
+	(284.80,158.21) --
+	(284.75,158.20) --
+	(284.43,158.12) --
+	(284.26,158.06) --
+	(283.80,157.92) --
+	(283.74,157.91) --
+	(283.34,157.81) --
+	(283.28,157.79) --
+	(283.10,157.72) --
+	(281.60,157.19) --
+	(281.52,157.15) --
+	(281.16,157.04) --
+	(280.63,156.85) --
+	(280.60,156.83) --
+	(280.50,156.79) --
+	(280.47,156.78) --
+	(280.41,156.75) --
+	(280.36,156.73) --
+	(280.21,156.68) --
+	(279.90,156.59) --
+	(279.83,156.58) --
+	(279.36,156.45) --
+	(279.03,156.32) --
+	(278.99,156.30) --
+	(278.93,156.27) --
+	(278.83,156.20) --
+	(277.37,155.69) --
+	(277.28,155.66) --
+	(276.77,155.47) --
+	(276.73,155.45) --
+	(276.14,155.25) --
+	(276.03,155.23) --
+	(275.50,155.09) --
+	(274.88,154.85) --
+	(274.85,154.84) --
+	(274.31,154.63) --
+	(273.48,154.33) --
+	(273.29,154.26) --
+	(273.01,154.14) --
+	(272.91,154.08) --
+	(272.40,153.94) --
+	(272.31,153.91) --
+	(271.51,153.68) --
+	(269.91,153.18) --
+	(269.75,153.12) --
+	(269.30,153.01) --
+	(269.12,152.95) --
+	(268.75,152.83) --
+	(268.51,152.72) --
+	(268.32,152.61) --
+	(268.15,152.54) --
+	(267.95,152.45) --
+	(267.83,152.40) --
+	(267.74,152.36) --
+	(266.70,151.94) --
+	(266.69,151.93) --
+	(265.54,151.50) --
+	(265.48,151.48) --
+	(265.11,151.39) --
+	(264.94,151.31) --
+	(264.43,151.11) --
+	(264.14,151.03) --
+	(263.47,150.81) --
+	(262.57,150.47) --
+	(261.39,150.00) --
+	(260.16,149.54) --
+	(260.08,149.51) --
+	(258.99,149.05) --
+	(256.94,148.31) --
+	(255.74,147.96) --
+	(254.34,147.35) --
+	(253.89,147.15) --
+	(253.69,147.06) --
+	(252.46,146.62) --
+	(251.97,146.47) --
+	(250.69,145.91) --
+	(250.38,145.79) --
+	(250.22,145.74) --
+	(249.74,145.63) --
+	(248.30,145.02) --
+	(244.78,143.52) --
+	(242.95,142.71) --
+	(241.65,142.20) --
+	(241.27,142.05) --
+	(240.80,141.82) --
+	(240.03,141.56) --
+	(239.31,141.28) --
+	(239.29,141.27) --
+	(237.41,140.47) --
+	(237.40,140.46) --
+	(236.22,140.02) --
+	(235.24,139.60) --
+	(234.25,139.14) --
+	(233.34,138.79) --
+	(232.39,138.25) --
+	(231.34,137.82) --
+	(231.15,137.77) --
+	(229.14,136.99) --
+	(224.00,134.73) --
+	(223.59,134.56) --
+	(223.54,134.54) --
+	(223.29,134.42) --
+	(222.58,134.07) --
+	(221.63,133.64) --
+	(220.93,133.31) --
+	(220.33,132.98) --
+	(220.17,132.91) --
+	(218.17,132.08) --
+	(217.68,131.82) --
+	(217.43,131.70) --
+	(217.33,131.66) --
+	(215.87,130.99) --
+	(211.50,128.79) --
+	(209.65,127.84) --
+	(205.19,125.79) --
+	(204.99,125.71) --
+	(199.87,123.16) --
+	(198.04,122.29) --
+	(196.35,121.40) --
+	(195.71,121.10) --
+	(195.62,121.07) --
+	(192.71,119.57) --
+	(187.92,117.14) --
+	(178.49,112.49) --
+	(171.43,108.90) --
+	(158.01,101.95) --
+	(154.64,100.20) --
+	(110.88, 76.90) --
+	(101.92, 72.02) --
+	( 95.59, 68.42) --
+	( 92.34, 66.68) --
+	( 86.71, 63.70) --
+	( 78.30, 59.08) --
+	( 64.98, 51.79) --
+	( 64.85, 51.71) --
+	( 60.61, 49.49) --
+	( 52.97, 45.08) --
 	cycle;
@@
 
-\path[fill=fillColor,fill opacity=0.50] ( 57.05,159.56) --
-	( 61.80,160.25) --
-	( 66.56,160.98) --
-	( 71.31,161.86) --
-	( 76.07,162.52) --
-	( 80.82,163.37) --
-	( 85.58,164.21) --
-	( 90.34,164.90) --
-	( 95.09,165.74) --
-	( 99.85,166.75) --
-	(104.60,167.59) --
-	(109.36,168.46) --
-	(114.11,169.19) --
-	(118.87,170.16) --
-	(123.63,170.99) --
-	(128.38,171.84) --
-	(133.14,172.69) --
-	(137.89,173.59) --
-	(142.65,174.41) --
-	(147.40,175.17) --
-	(152.16,176.19) --
-	(156.92,177.17) --
-	(161.67,178.09) --
-	(166.43,178.94) --
-	(171.18,179.97) --
-	(175.94,180.98) --
-	(180.70,181.99) --
-	(185.45,182.96) --
-	(190.21,183.82) --
-	(194.96,184.88) --
-	(199.72,185.88) --
-	(204.47,186.83) --
-	(209.23,187.76) --
-	(213.99,188.99) --
-	(218.74,190.13) --
-	(223.50,191.26) --
-	(228.25,192.31) --
-	(233.01,193.53) --
-	(237.76,194.62) --
-	(242.52,195.84) --
-	(247.28,197.18) --
-	(252.03,198.48) --
-	(256.79,199.68) --
-	(261.54,201.07) --
-	(266.30,202.56) --
-	(271.05,204.06) --
-	(275.81,205.62) --
-	(280.57,207.24) --
-	(285.32,209.00) --
-	(290.08,210.51) --
-	(294.83,212.14) --
-	(299.59,213.87) --
-	(304.35,215.72) --
-	(309.10,217.52) --
-	(313.86,219.34) --
-	(318.61,221.26) --
-	(323.37,223.16) --
-	(328.12,225.10) --
-	(332.88,227.06) --
-	(337.64,228.96) --
-	(342.39,231.01) --
-	(347.15,233.07) --
-	(351.90,235.12) --
-	(356.66,237.31) --
-	(361.41,239.43) --
-	(366.17,241.62) --
-	(370.93,243.83) --
-	(375.68,246.04) --
-	(380.44,248.34) --
-	(385.19,250.61) --
-	(389.95,252.92) --
-	(394.70,255.34) --
-	(399.46,257.65) --
-	(404.22,260.08) --
-	(404.22,196.18) --
-	(399.46,195.16) --
-	(394.70,194.11) --
-	(389.95,193.22) --
-	(385.19,192.29) --
-	(380.44,191.22) --
-	(375.68,190.29) --
-	(370.93,189.27) --
-	(366.17,188.31) --
-	(361.41,187.21) --
-	(356.66,185.94) --
-	(351.90,184.86) --
-	(347.15,183.77) --
-	(342.39,182.69) --
-	(337.64,181.59) --
-	(332.88,180.34) --
-	(328.12,179.09) --
-	(323.37,177.75) --
-	(318.61,176.29) --
-	(313.86,174.79) --
-	(309.10,173.33) --
-	(304.35,171.86) --
-	(299.59,170.35) --
-	(294.83,168.77) --
-	(290.08,167.23) --
-	(285.32,165.59) --
-	(280.57,163.88) --
-	(275.81,162.14) --
-	(271.05,160.29) --
-	(266.30,158.47) --
-	(261.54,156.48) --
-	(256.79,154.63) --
-	(252.03,152.76) --
-	(247.28,150.64) --
-	(242.52,148.69) --
-	(237.76,146.57) --
-	(233.01,144.54) --
-	(228.25,142.40) --
-	(223.50,140.17) --
-	(218.74,137.98) --
-	(213.99,135.99) --
-	(209.23,133.82) --
-	(204.47,131.54) --
-	(199.72,129.37) --
-	(194.96,127.03) --
-	(190.21,124.77) --
-	(185.45,122.49) --
-	(180.70,120.16) --
-	(175.94,117.80) --
-	(171.18,115.40) --
-	(166.43,113.13) --
-	(161.67,110.68) --
-	(156.92,108.42) --
-	(152.16,105.89) --
-	(147.40,103.39) --
-	(142.65,100.83) --
-	(137.89, 98.32) --
-	(133.14, 95.77) --
-	(128.38, 93.33) --
-	(123.63, 90.81) --
-	(118.87, 88.34) --
-	(114.11, 85.90) --
-	(109.36, 83.33) --
-	(104.60, 80.84) --
-	( 99.85, 78.40) --
-	( 95.09, 75.83) --
-	( 90.34, 73.27) --
-	( 85.58, 70.75) --
-	( 80.82, 68.24) --
-	( 76.07, 65.78) --
-	( 71.31, 63.28) --
-	( 66.56, 60.67) --
-	( 61.80, 58.16) --
-	( 57.05, 55.65) --
+\path[fill=fillColor,fill opacity=0.50] ( 52.97,155.78) --
+	( 60.61,157.02) --
+	( 64.85,157.72) --
+	( 64.98,157.76) --
+	( 78.30,159.89) --
+	( 86.71,161.16) --
+	( 92.34,162.02) --
+	( 95.59,162.58) --
+	(101.92,163.75) --
+	(110.88,165.37) --
+	(154.64,173.25) --
+	(158.01,173.83) --
+	(171.43,176.44) --
+	(178.49,177.89) --
+	(187.92,179.93) --
+	(192.71,180.94) --
+	(195.62,181.57) --
+	(195.71,181.60) --
+	(196.35,181.78) --
+	(198.04,182.20) --
+	(199.87,182.59) --
+	(204.99,183.69) --
+	(205.19,183.74) --
+	(209.65,184.88) --
+	(211.50,185.32) --
+	(215.87,186.31) --
+	(217.33,186.70) --
+	(217.43,186.73) --
+	(217.68,186.79) --
+	(218.17,186.95) --
+	(220.17,187.43) --
+	(220.33,187.47) --
+	(220.93,187.59) --
+	(221.63,187.78) --
+	(222.58,188.03) --
+	(223.29,188.16) --
+	(223.54,188.25) --
+	(223.59,188.27) --
+	(224.00,188.40) --
+	(229.14,189.71) --
+	(231.15,190.26) --
+	(231.34,190.31) --
+	(232.39,190.62) --
+	(233.34,190.89) --
+	(234.25,191.19) --
+	(235.24,191.47) --
+	(236.22,191.82) --
+	(237.40,192.18) --
+	(237.41,192.18) --
+	(239.29,192.72) --
+	(239.31,192.73) --
+	(240.03,192.94) --
+	(240.80,193.15) --
+	(241.27,193.33) --
+	(241.65,193.46) --
+	(242.95,193.75) --
+	(244.78,194.25) --
+	(248.30,195.33) --
+	(249.74,195.76) --
+	(250.22,195.94) --
+	(250.38,196.01) --
+	(250.69,196.16) --
+	(251.97,196.55) --
+	(252.46,196.68) --
+	(253.69,197.01) --
+	(253.89,197.07) --
+	(254.34,197.22) --
+	(255.74,197.69) --
+	(256.94,198.07) --
+	(258.99,198.62) --
+	(260.08,198.96) --
+	(260.16,198.98) --
+	(261.39,199.44) --
+	(262.57,199.78) --
+	(263.47,200.03) --
+	(264.14,200.24) --
+	(264.43,200.36) --
+	(264.94,200.54) --
+	(265.11,200.57) --
+	(265.48,200.70) --
+	(265.54,200.72) --
+	(266.69,201.09) --
+	(266.70,201.09) --
+	(267.74,201.45) --
+	(267.83,201.46) --
+	(267.95,201.52) --
+	(268.15,201.60) --
+	(268.32,201.64) --
+	(268.51,201.73) --
+	(268.75,201.81) --
+	(269.12,201.95) --
+	(269.30,202.00) --
+	(269.75,202.18) --
+	(269.91,202.21) --
+	(271.51,202.79) --
+	(272.31,203.06) --
+	(272.40,203.09) --
+	(272.91,203.23) --
+	(273.01,203.25) --
+	(273.29,203.34) --
+	(273.48,203.41) --
+	(274.31,203.68) --
+	(274.85,203.89) --
+	(274.88,203.90) --
+	(275.50,204.08) --
+	(276.03,204.23) --
+	(276.14,204.27) --
+	(276.73,204.46) --
+	(276.77,204.47) --
+	(277.28,204.64) --
+	(277.37,204.66) --
+	(278.83,205.17) --
+	(278.93,205.20) --
+	(278.99,205.23) --
+	(279.03,205.25) --
+	(279.36,205.31) --
+	(279.83,205.47) --
+	(279.90,205.50) --
+	(280.21,205.61) --
+	(280.36,205.65) --
+	(280.41,205.68) --
+	(280.47,205.71) --
+	(280.50,205.71) --
+	(280.60,205.74) --
+	(280.63,205.75) --
+	(281.16,205.91) --
+	(281.52,206.01) --
+	(281.60,206.03) --
+	(283.10,206.58) --
+	(283.28,206.66) --
+	(283.34,206.68) --
+	(283.74,206.84) --
+	(283.80,206.86) --
+	(284.26,207.01) --
+	(284.43,207.07) --
+	(284.75,207.16) --
+	(284.80,207.18) --
+	(284.81,207.18) --
+	(284.81,207.18) --
+	(284.84,207.19) --
+	(284.88,207.20) --
+	(285.44,207.45) --
+	(285.67,207.54) --
+	(286.04,207.68) --
+	(286.70,207.89) --
+	(286.95,207.97) --
+	(287.76,208.27) --
+	(288.16,208.43) --
+	(288.45,208.57) --
+	(288.86,208.73) --
+	(289.03,208.78) --
+	(289.13,208.82) --
+	(289.30,208.87) --
+	(289.61,208.98) --
+	(289.71,209.02) --
+	(289.99,209.12) --
+	(290.44,209.29) --
+	(291.29,209.59) --
+	(291.45,209.64) --
+	(291.58,209.68) --
+	(292.20,209.90) --
+	(292.36,209.95) --
+	(292.77,210.11) --
+	(292.78,210.12) --
+	(292.85,210.14) --
+	(292.94,210.16) --
+	(293.49,210.35) --
+	(293.61,210.39) --
+	(293.90,210.51) --
+	(293.94,210.53) --
+	(295.12,210.90) --
+	(295.85,211.14) --
+	(296.61,211.47) --
+	(297.11,211.69) --
+	(297.99,212.07) --
+	(298.09,212.10) --
+	(298.13,212.11) --
+	(298.21,212.12) --
+	(298.45,212.21) --
+	(298.48,212.23) --
+	(298.71,212.30) --
+	(298.89,212.38) --
+	(299.22,212.51) --
+	(300.07,212.87) --
+	(300.69,213.09) --
+	(301.34,213.35) --
+	(301.81,213.52) --
+	(301.86,213.54) --
+	(302.06,213.61) --
+	(302.08,213.62) --
+	(302.20,213.66) --
+	(302.30,213.71) --
+	(302.45,213.79) --
+	(302.52,213.81) --
+	(302.61,213.85) --
+	(302.89,213.96) --
+	(302.93,213.97) --
+	(303.17,214.04) --
+	(304.10,214.40) --
+	(304.31,214.48) --
+	(304.47,214.53) --
+	(304.48,214.53) --
+	(304.60,214.58) --
+	(304.68,214.61) --
+	(305.11,214.78) --
+	(305.28,214.85) --
+	(305.76,215.07) --
+	(305.86,215.12) --
+	(306.15,215.24) --
+	(307.03,215.53) --
+	(307.16,215.60) --
+	(307.37,215.70) --
+	(308.42,216.07) --
+	(308.63,216.18) --
+	(308.79,216.26) --
+	(309.08,216.38) --
+	(309.55,216.59) --
+	(309.72,216.66) --
+	(310.36,216.92) --
+	(310.45,216.96) --
+	(310.80,217.15) --
+	(310.98,217.23) --
+	(311.09,217.27) --
+	(311.49,217.42) --
+	(311.71,217.50) --
+	(311.87,217.56) --
+	(312.39,217.84) --
+	(312.68,217.99) --
+	(312.75,218.02) --
+	(314.09,218.56) --
+	(314.12,218.57) --
+	(314.55,218.71) --
+	(314.84,218.84) --
+	(315.05,218.90) --
+	(315.28,218.98) --
+	(315.54,219.09) --
+	(315.61,219.12) --
+	(315.65,219.13) --
+	(316.29,219.37) --
+	(316.37,219.39) --
+	(316.58,219.47) --
+	(316.61,219.48) --
+	(316.72,219.52) --
+	(317.13,219.68) --
+	(318.60,220.33) --
+	(319.14,220.56) --
+	(320.71,221.16) --
+	(321.34,221.42) --
+	(321.47,221.48) --
+	(322.56,221.95) --
+	(322.64,221.98) --
+	(322.93,222.10) --
+	(323.98,222.52) --
+	(324.06,222.56) --
+	(324.53,222.78) --
+	(324.82,222.91) --
+	(325.46,223.17) --
+	(325.85,223.33) --
+	(325.87,223.34) --
+	(325.91,223.34) --
+	(326.16,223.46) --
+	(326.46,223.57) --
+	(327.01,223.82) --
+	(327.50,224.06) --
+	(327.78,224.16) --
+	(328.37,224.39) --
+	(328.92,224.61) --
+	(330.17,225.15) --
+	(330.38,225.24) --
+	(330.88,225.42) --
+	(333.53,226.62) --
+	(333.56,226.63) --
+	(333.69,226.70) --
+	(333.82,226.78) --
+	(333.83,226.78) --
+	(335.38,227.53) --
+	(335.47,227.58) --
+	(337.65,228.52) --
+	(338.50,228.87) --
+	(338.83,228.96) --
+	(338.87,228.99) --
+	(339.04,229.08) --
+	(339.21,229.15) --
+	(339.40,229.23) --
+	(339.55,229.29) --
+	(339.76,229.37) --
+	(339.84,229.40) --
+	(340.15,229.53) --
+	(340.28,229.58) --
+	(340.65,229.71) --
+	(341.52,230.07) --
+	(342.53,230.56) --
+	(343.79,231.08) --
+	(343.95,231.15) --
+	(345.11,231.69) --
+	(345.20,231.73) --
+	(345.78,231.99) --
+	(346.49,232.31) --
+	(346.80,232.47) --
+	(346.94,232.52) --
+	(347.30,232.67) --
+	(348.63,233.25) --
+	(348.84,233.35) --
+	(349.59,233.76) --
+	(350.01,233.97) --
+	(350.27,234.09) --
+	(350.57,234.23) --
+	(351.61,234.73) --
+	(352.50,235.16) --
+	(354.60,236.10) --
+	(354.77,236.18) --
+	(355.03,236.30) --
+	(355.06,236.31) --
+	(355.38,236.46) --
+	(355.44,236.49) --
+	(355.66,236.61) --
+	(355.69,236.61) --
+	(356.06,236.78) --
+	(356.08,236.79) --
+	(356.57,237.02) --
+	(356.86,237.14) --
+	(356.99,237.20) --
+	(357.04,237.22) --
+	(357.10,237.25) --
+	(357.28,237.33) --
+	(357.68,237.52) --
+	(357.71,237.53) --
+	(358.36,237.85) --
+	(358.45,237.89) --
+	(358.80,238.04) --
+	(359.58,238.38) --
+	(360.14,238.61) --
+	(360.17,238.62) --
+	(360.28,238.68) --
+	(360.68,238.85) --
+	(362.54,239.69) --
+	(362.92,239.87) --
+	(362.99,239.91) --
+	(362.99,239.91) --
+	(363.68,240.21) --
+	(363.71,240.22) --
+	(364.25,240.52) --
+	(364.57,240.68) --
+	(364.77,240.77) --
+	(365.00,240.87) --
+	(365.26,241.04) --
+	(365.84,241.33) --
+	(365.84,241.33) --
+	(365.92,241.37) --
+	(366.04,241.42) --
+	(366.47,241.62) --
+	(367.05,241.89) --
+	(368.20,242.45) --
+	(368.39,242.54) --
+	(368.50,242.59) --
+	(370.21,243.39) --
+	(371.17,243.81) --
+	(371.58,244.00) --
+	(372.02,244.21) --
+	(373.58,244.87) --
+	(376.96,246.54) --
+	(378.52,247.26) --
+	(383.85,249.83) --
+	(384.44,250.15) --
+	(384.92,250.40) --
+	(385.30,250.56) --
+	(385.73,250.74) --
+	(385.96,250.84) --
+	(386.70,251.22) --
+	(386.81,251.27) --
+	(387.17,251.44) --
+	(387.19,251.44) --
+	(387.24,251.46) --
+	(387.39,251.54) --
+	(387.67,251.67) --
+	(388.26,251.97) --
+	(389.16,252.36) --
+	(389.82,252.64) --
+	(390.40,252.95) --
+	(390.44,252.98) --
+	(390.79,253.21) --
+	(391.07,253.39) --
+	(395.16,255.52) --
+	(396.00,255.92) --
+	(396.15,255.99) --
+	(403.52,259.54) --
+	(404.02,259.83) --
+	(404.02,193.21) --
+	(403.52,193.10) --
+	(396.15,191.59) --
+	(396.00,191.58) --
+	(395.16,191.49) --
+	(391.07,190.75) --
+	(390.79,190.69) --
+	(390.44,190.64) --
+	(390.40,190.63) --
+	(389.82,190.53) --
+	(389.16,190.43) --
+	(388.26,190.20) --
+	(387.67,190.10) --
+	(387.39,190.05) --
+	(387.24,190.01) --
+	(387.19,190.01) --
+	(387.17,190.00) --
+	(386.81,189.94) --
+	(386.70,189.92) --
+	(385.96,189.70) --
+	(385.73,189.67) --
+	(385.30,189.58) --
+	(384.92,189.52) --
+	(384.44,189.44) --
+	(383.85,189.36) --
+	(378.52,187.97) --
+	(376.96,187.68) --
+	(373.58,186.94) --
+	(372.02,186.66) --
+	(371.58,186.58) --
+	(371.17,186.48) --
+	(370.21,186.18) --
+	(368.50,185.79) --
+	(368.39,185.78) --
+	(368.20,185.73) --
+	(367.05,185.54) --
+	(366.47,185.42) --
+	(366.04,185.30) --
+	(365.92,185.27) --
+	(365.84,185.25) --
+	(365.84,185.25) --
+	(365.26,185.12) --
+	(365.00,185.06) --
+	(364.77,185.00) --
+	(364.57,184.94) --
+	(364.25,184.87) --
+	(363.71,184.72) --
+	(363.68,184.71) --
+	(362.99,184.56) --
+	(362.99,184.56) --
+	(362.92,184.54) --
+	(362.54,184.46) --
+	(360.68,184.05) --
+	(360.28,183.92) --
+	(360.17,183.88) --
+	(360.14,183.88) --
+	(359.58,183.76) --
+	(358.80,183.59) --
+	(358.45,183.50) --
+	(358.36,183.48) --
+	(357.71,183.31) --
+	(357.68,183.31) --
+	(357.28,183.23) --
+	(357.10,183.18) --
+	(357.04,183.16) --
+	(356.99,183.15) --
+	(356.86,183.10) --
+	(356.57,183.03) --
+	(356.08,182.90) --
+	(356.06,182.90) --
+	(355.69,182.80) --
+	(355.66,182.80) --
+	(355.44,182.75) --
+	(355.38,182.73) --
+	(355.06,182.65) --
+	(355.03,182.64) --
+	(354.77,182.59) --
+	(354.60,182.56) --
+	(352.50,182.02) --
+	(351.61,181.81) --
+	(350.57,181.53) --
+	(350.27,181.44) --
+	(350.01,181.39) --
+	(349.59,181.29) --
+	(348.84,181.08) --
+	(348.63,181.04) --
+	(347.30,180.74) --
+	(346.94,180.63) --
+	(346.80,180.60) --
+	(346.49,180.52) --
+	(345.78,180.31) --
+	(345.20,180.18) --
+	(345.11,180.16) --
+	(343.95,179.88) --
+	(343.79,179.84) --
+	(342.53,179.55) --
+	(341.52,179.33) --
+	(340.65,179.17) --
+	(340.28,179.02) --
+	(340.15,178.96) --
+	(339.84,178.86) --
+	(339.76,178.82) --
+	(339.55,178.78) --
+	(339.40,178.76) --
+	(339.21,178.74) --
+	(339.04,178.70) --
+	(338.87,178.68) --
+	(338.83,178.66) --
+	(338.50,178.58) --
+	(337.65,178.29) --
+	(335.47,177.71) --
+	(335.38,177.68) --
+	(333.83,177.24) --
+	(333.82,177.24) --
+	(333.69,177.20) --
+	(333.56,177.17) --
+	(333.53,177.16) --
+	(330.88,176.48) --
+	(330.38,176.35) --
+	(330.17,176.29) --
+	(328.92,176.00) --
+	(328.37,175.84) --
+	(327.78,175.64) --
+	(327.50,175.55) --
+	(327.01,175.42) --
+	(326.46,175.32) --
+	(326.16,175.25) --
+	(325.91,175.20) --
+	(325.87,175.20) --
+	(325.85,175.19) --
+	(325.46,175.13) --
+	(324.82,174.98) --
+	(324.53,174.93) --
+	(324.06,174.82) --
+	(323.98,174.80) --
+	(322.93,174.54) --
+	(322.64,174.46) --
+	(322.56,174.44) --
+	(321.47,174.10) --
+	(321.34,174.07) --
+	(320.71,173.87) --
+	(319.14,173.48) --
+	(318.60,173.34) --
+	(317.13,172.94) --
+	(316.72,172.82) --
+	(316.61,172.81) --
+	(316.58,172.80) --
+	(316.37,172.74) --
+	(316.29,172.72) --
+	(315.65,172.55) --
+	(315.61,172.53) --
+	(315.54,172.52) --
+	(315.28,172.44) --
+	(315.05,172.37) --
+	(314.84,172.32) --
+	(314.55,172.24) --
+	(314.12,172.13) --
+	(314.09,172.13) --
+	(312.75,171.77) --
+	(312.68,171.75) --
+	(312.39,171.66) --
+	(311.87,171.50) --
+	(311.71,171.46) --
+	(311.49,171.39) --
+	(311.09,171.28) --
+	(310.98,171.25) --
+	(310.80,171.20) --
+	(310.45,171.10) --
+	(310.36,171.07) --
+	(309.72,170.92) --
+	(309.55,170.87) --
+	(309.08,170.76) --
+	(308.79,170.69) --
+	(308.63,170.64) --
+	(308.42,170.58) --
+	(307.37,170.23) --
+	(307.16,170.16) --
+	(307.03,170.09) --
+	(306.15,169.83) --
+	(305.86,169.74) --
+	(305.76,169.71) --
+	(305.28,169.58) --
+	(305.11,169.54) --
+	(304.68,169.40) --
+	(304.60,169.37) --
+	(304.48,169.34) --
+	(304.47,169.33) --
+	(304.31,169.29) --
+	(304.10,169.23) --
+	(303.17,168.95) --
+	(302.93,168.88) --
+	(302.89,168.88) --
+	(302.61,168.80) --
+	(302.52,168.79) --
+	(302.45,168.78) --
+	(302.30,168.73) --
+	(302.20,168.71) --
+	(302.08,168.67) --
+	(302.06,168.66) --
+	(301.86,168.62) --
+	(301.81,168.60) --
+	(301.34,168.41) --
+	(300.69,168.22) --
+	(300.07,168.01) --
+	(299.22,167.81) --
+	(298.89,167.74) --
+	(298.71,167.68) --
+	(298.48,167.60) --
+	(298.45,167.59) --
+	(298.21,167.50) --
+	(298.13,167.47) --
+	(298.09,167.46) --
+	(297.99,167.43) --
+	(297.11,167.14) --
+	(296.61,167.00) --
+	(295.85,166.72) --
+	(295.12,166.43) --
+	(293.94,166.08) --
+	(293.90,166.07) --
+	(293.61,165.97) --
+	(293.49,165.93) --
+	(292.94,165.77) --
+	(292.85,165.76) --
+	(292.78,165.72) --
+	(292.77,165.72) --
+	(292.36,165.59) --
+	(292.20,165.54) --
+	(291.58,165.36) --
+	(291.45,165.31) --
+	(291.29,165.25) --
+	(290.44,164.93) --
+	(289.99,164.78) --
+	(289.71,164.71) --
+	(289.61,164.68) --
+	(289.30,164.60) --
+	(289.13,164.54) --
+	(289.03,164.51) --
+	(288.86,164.44) --
+	(288.45,164.32) --
+	(288.16,164.21) --
+	(287.76,164.11) --
+	(286.95,163.86) --
+	(286.70,163.79) --
+	(286.04,163.59) --
+	(285.67,163.45) --
+	(285.44,163.36) --
+	(284.88,163.17) --
+	(284.84,163.16) --
+	(284.81,163.14) --
+	(284.81,163.14) --
+	(284.80,163.14) --
+	(284.75,163.11) --
+	(284.43,163.01) --
+	(284.26,162.95) --
+	(283.80,162.82) --
+	(283.74,162.80) --
+	(283.34,162.65) --
+	(283.28,162.64) --
+	(283.10,162.60) --
+	(281.60,162.07) --
+	(281.52,162.04) --
+	(281.16,161.89) --
+	(280.63,161.70) --
+	(280.60,161.69) --
+	(280.50,161.65) --
+	(280.47,161.64) --
+	(280.41,161.61) --
+	(280.36,161.59) --
+	(280.21,161.53) --
+	(279.90,161.42) --
+	(279.83,161.40) --
+	(279.36,161.22) --
+	(279.03,161.12) --
+	(278.99,161.10) --
+	(278.93,161.08) --
+	(278.83,161.05) --
+	(277.37,160.51) --
+	(277.28,160.48) --
+	(276.77,160.29) --
+	(276.73,160.28) --
+	(276.14,160.03) --
+	(276.03,159.99) --
+	(275.50,159.78) --
+	(274.88,159.56) --
+	(274.85,159.55) --
+	(274.31,159.34) --
+	(273.48,159.10) --
+	(273.29,159.00) --
+	(273.01,158.91) --
+	(272.91,158.87) --
+	(272.40,158.63) --
+	(272.31,158.61) --
+	(271.51,158.38) --
+	(269.91,157.84) --
+	(269.75,157.78) --
+	(269.30,157.63) --
+	(269.12,157.57) --
+	(268.75,157.44) --
+	(268.51,157.36) --
+	(268.32,157.28) --
+	(268.15,157.20) --
+	(267.95,157.14) --
+	(267.83,157.09) --
+	(267.74,157.07) --
+	(266.70,156.71) --
+	(266.69,156.71) --
+	(265.54,156.24) --
+	(265.48,156.21) --
+	(265.11,156.07) --
+	(264.94,156.00) --
+	(264.43,155.81) --
+	(264.14,155.71) --
+	(263.47,155.47) --
+	(262.57,155.16) --
+	(261.39,154.71) --
+	(260.16,154.24) --
+	(260.08,154.22) --
+	(258.99,153.78) --
+	(256.94,152.92) --
+	(255.74,152.43) --
+	(254.34,151.90) --
+	(253.89,151.74) --
+	(253.69,151.68) --
+	(252.46,151.14) --
+	(251.97,150.97) --
+	(250.69,150.46) --
+	(250.38,150.35) --
+	(250.22,150.29) --
+	(249.74,150.09) --
+	(248.30,149.50) --
+	(244.78,148.02) --
+	(242.95,147.32) --
+	(241.65,146.80) --
+	(241.27,146.62) --
+	(240.80,146.42) --
+	(240.03,146.15) --
+	(239.31,145.84) --
+	(239.29,145.83) --
+	(237.41,145.07) --
+	(237.40,145.07) --
+	(236.22,144.55) --
+	(235.24,144.17) --
+	(234.25,143.77) --
+	(233.34,143.45) --
+	(232.39,143.03) --
+	(231.34,142.62) --
+	(231.15,142.56) --
+	(229.14,141.64) --
+	(224.00,139.28) --
+	(223.59,139.09) --
+	(223.54,139.07) --
+	(223.29,138.97) --
+	(222.58,138.65) --
+	(221.63,138.25) --
+	(220.93,137.97) --
+	(220.33,137.73) --
+	(220.17,137.66) --
+	(218.17,136.81) --
+	(217.68,136.58) --
+	(217.43,136.47) --
+	(217.33,136.42) --
+	(215.87,135.77) --
+	(211.50,133.87) --
+	(209.65,133.08) --
+	(205.19,130.98) --
+	(204.99,130.88) --
+	(199.87,128.62) --
+	(198.04,127.77) --
+	(196.35,126.93) --
+	(195.71,126.63) --
+	(195.62,126.59) --
+	(192.71,125.33) --
+	(187.92,123.15) --
+	(178.49,118.78) --
+	(171.43,115.43) --
+	(158.01,108.85) --
+	(154.64,107.17) --
+	(110.88, 85.07) --
+	(101.92, 80.39) --
+	( 95.59, 77.11) --
+	( 92.34, 75.32) --
+	( 86.71, 72.24) --
+	( 78.30, 67.94) --
+	( 64.98, 61.14) --
+	( 64.85, 61.07) --
+	( 60.61, 58.89) --
+	( 52.97, 54.98) --
 	cycle;
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 52.97, 34.03) -- ( 52.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 60.61, 34.03) -- ( 60.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 64.85, 34.03) -- ( 64.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 64.98, 34.03) -- ( 64.98, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 78.30, 34.03) -- ( 78.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 86.71, 34.03) -- ( 86.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 92.34, 34.03) -- ( 92.34, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 95.59, 34.03) -- ( 95.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (101.92, 34.03) -- (101.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (110.88, 34.03) -- (110.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (154.64, 34.03) -- (154.64, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (158.01, 34.03) -- (158.01, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (171.43, 34.03) -- (171.43, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (178.49, 34.03) -- (178.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (187.92, 34.03) -- (187.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (192.71, 34.03) -- (192.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (195.62, 34.03) -- (195.62, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (195.71, 34.03) -- (195.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (196.35, 34.03) -- (196.35, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (198.04, 34.03) -- (198.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (199.87, 34.03) -- (199.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (204.99, 34.03) -- (204.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (205.19, 34.03) -- (205.19, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (209.65, 34.03) -- (209.65, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (211.50, 34.03) -- (211.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (215.87, 34.03) -- (215.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (217.33, 34.03) -- (217.33, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (217.43, 34.03) -- (217.43, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (217.68, 34.03) -- (217.68, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (218.17, 34.03) -- (218.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (220.17, 34.03) -- (220.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (220.33, 34.03) -- (220.33, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (220.93, 34.03) -- (220.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (221.63, 34.03) -- (221.63, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (222.58, 34.03) -- (222.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (223.29, 34.03) -- (223.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (223.54, 34.03) -- (223.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (223.59, 34.03) -- (223.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (224.00, 34.03) -- (224.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (229.14, 34.03) -- (229.14, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (231.15, 34.03) -- (231.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (231.34, 34.03) -- (231.34, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.39, 34.03) -- (232.39, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (233.34, 34.03) -- (233.34, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (234.25, 34.03) -- (234.25, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (235.24, 34.03) -- (235.24, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (236.22, 34.03) -- (236.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (237.40, 34.03) -- (237.40, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (237.41, 34.03) -- (237.41, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (239.29, 34.03) -- (239.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (239.31, 34.03) -- (239.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (240.03, 34.03) -- (240.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (240.80, 34.03) -- (240.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (241.27, 34.03) -- (241.27, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (241.65, 34.03) -- (241.65, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (242.95, 34.03) -- (242.95, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (244.78, 34.03) -- (244.78, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (248.30, 34.03) -- (248.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (249.74, 34.03) -- (249.74, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (250.22, 34.03) -- (250.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (250.38, 34.03) -- (250.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (250.69, 34.03) -- (250.69, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.97, 34.03) -- (251.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (252.46, 34.03) -- (252.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (253.69, 34.03) -- (253.69, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (253.89, 34.03) -- (253.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (254.34, 34.03) -- (254.34, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (255.74, 34.03) -- (255.74, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (256.94, 34.03) -- (256.94, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (258.99, 34.03) -- (258.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (260.08, 34.03) -- (260.08, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (260.16, 34.03) -- (260.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (261.39, 34.03) -- (261.39, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (262.57, 34.03) -- (262.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (263.47, 34.03) -- (263.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (264.14, 34.03) -- (264.14, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (264.43, 34.03) -- (264.43, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (264.94, 34.03) -- (264.94, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (265.11, 34.03) -- (265.11, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (265.48, 34.03) -- (265.48, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (265.54, 34.03) -- (265.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (266.69, 34.03) -- (266.69, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (266.70, 34.03) -- (266.70, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.75, 34.03) -- (267.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.83, 34.03) -- (267.83, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.95, 34.03) -- (267.95, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (268.15, 34.03) -- (268.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (268.31, 34.03) -- (268.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (268.51, 34.03) -- (268.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (268.75, 34.03) -- (268.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (269.12, 34.03) -- (269.12, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (269.30, 34.03) -- (269.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (269.75, 34.03) -- (269.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (269.91, 34.03) -- (269.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.51, 34.03) -- (271.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (272.31, 34.03) -- (272.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (272.40, 34.03) -- (272.40, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (272.91, 34.03) -- (272.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (273.01, 34.03) -- (273.01, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (273.29, 34.03) -- (273.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (273.48, 34.03) -- (273.48, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (274.31, 34.03) -- (274.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (274.85, 34.03) -- (274.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (274.88, 34.03) -- (274.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (275.50, 34.03) -- (275.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (276.03, 34.03) -- (276.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (276.14, 34.03) -- (276.14, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (276.73, 34.03) -- (276.73, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (276.77, 34.03) -- (276.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (277.28, 34.03) -- (277.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (277.37, 34.03) -- (277.37, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (278.83, 34.03) -- (278.83, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (278.93, 34.03) -- (278.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (278.99, 34.03) -- (278.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (279.03, 34.03) -- (279.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (279.36, 34.03) -- (279.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (279.83, 34.03) -- (279.83, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (279.90, 34.03) -- (279.90, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (280.21, 34.03) -- (280.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (280.36, 34.03) -- (280.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (280.41, 34.03) -- (280.41, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (280.47, 34.03) -- (280.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (280.50, 34.03) -- (280.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (280.60, 34.03) -- (280.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (280.63, 34.03) -- (280.63, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (281.16, 34.03) -- (281.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (281.52, 34.03) -- (281.52, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (281.60, 34.03) -- (281.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.10, 34.03) -- (283.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.28, 34.03) -- (283.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.34, 34.03) -- (283.34, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.74, 34.03) -- (283.74, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.80, 34.03) -- (283.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.26, 34.03) -- (284.26, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.43, 34.03) -- (284.43, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.75, 34.03) -- (284.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.80, 34.03) -- (284.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.81, 34.03) -- (284.81, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.81, 34.03) -- (284.81, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.84, 34.03) -- (284.84, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.88, 34.03) -- (284.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.44, 34.03) -- (285.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.67, 34.03) -- (285.67, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.04, 34.03) -- (286.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.70, 34.03) -- (286.70, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.95, 34.03) -- (286.95, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (287.76, 34.03) -- (287.76, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (288.16, 34.03) -- (288.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (288.45, 34.03) -- (288.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (288.86, 34.03) -- (288.86, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (289.03, 34.03) -- (289.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (289.13, 34.03) -- (289.13, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (289.30, 34.03) -- (289.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (289.61, 34.03) -- (289.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (289.71, 34.03) -- (289.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (289.99, 34.03) -- (289.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.44, 34.03) -- (290.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (291.29, 34.03) -- (291.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (291.45, 34.03) -- (291.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (291.58, 34.03) -- (291.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.20, 34.03) -- (292.20, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.36, 34.03) -- (292.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.77, 34.03) -- (292.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.78, 34.03) -- (292.78, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.85, 34.03) -- (292.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.94, 34.03) -- (292.94, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (293.49, 34.03) -- (293.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (293.61, 34.03) -- (293.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (293.90, 34.03) -- (293.90, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (293.94, 34.03) -- (293.94, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (295.12, 34.03) -- (295.12, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (295.85, 34.03) -- (295.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (296.61, 34.03) -- (296.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.11, 34.03) -- (297.11, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.99, 34.03) -- (297.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.09, 34.03) -- (298.09, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.14, 34.03) -- (298.14, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.21, 34.03) -- (298.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.45, 34.03) -- (298.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.48, 34.03) -- (298.48, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.71, 34.03) -- (298.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.89, 34.03) -- (298.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.22, 34.03) -- (299.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (300.07, 34.03) -- (300.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (300.69, 34.03) -- (300.69, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (301.34, 34.03) -- (301.34, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (301.81, 34.03) -- (301.81, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (301.86, 34.03) -- (301.86, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.06, 34.03) -- (302.06, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.08, 34.03) -- (302.08, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.20, 34.03) -- (302.20, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.30, 34.03) -- (302.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.45, 34.03) -- (302.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.52, 34.03) -- (302.52, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.61, 34.03) -- (302.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.89, 34.03) -- (302.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.93, 34.03) -- (302.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (303.17, 34.03) -- (303.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.10, 34.03) -- (304.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.31, 34.03) -- (304.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.47, 34.03) -- (304.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.48, 34.03) -- (304.48, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.60, 34.03) -- (304.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.68, 34.03) -- (304.68, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (305.11, 34.03) -- (305.11, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (305.28, 34.03) -- (305.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (305.76, 34.03) -- (305.76, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (305.86, 34.03) -- (305.86, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (306.15, 34.03) -- (306.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.03, 34.03) -- (307.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.16, 34.03) -- (307.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.37, 34.03) -- (307.37, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (308.42, 34.03) -- (308.42, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (308.63, 34.03) -- (308.63, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (308.79, 34.03) -- (308.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.08, 34.03) -- (309.08, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.55, 34.03) -- (309.55, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.72, 34.03) -- (309.72, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.36, 34.03) -- (310.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.45, 34.03) -- (310.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.80, 34.03) -- (310.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.98, 34.03) -- (310.98, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.09, 34.03) -- (311.09, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.49, 34.03) -- (311.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.71, 34.03) -- (311.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.87, 34.03) -- (311.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (312.39, 34.03) -- (312.39, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (312.68, 34.03) -- (312.68, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (312.75, 34.03) -- (312.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.09, 34.03) -- (314.09, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.12, 34.03) -- (314.12, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.55, 34.03) -- (314.55, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.84, 34.03) -- (314.84, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.05, 34.03) -- (315.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.28, 34.03) -- (315.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.54, 34.03) -- (315.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.61, 34.03) -- (315.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.65, 34.03) -- (315.65, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.29, 34.03) -- (316.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.37, 34.03) -- (316.37, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.58, 34.03) -- (316.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.61, 34.03) -- (316.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.72, 34.03) -- (316.72, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.13, 34.03) -- (317.13, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (318.60, 34.03) -- (318.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.14, 34.03) -- (319.14, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.71, 34.03) -- (320.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.34, 34.03) -- (321.34, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.47, 34.03) -- (321.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (322.56, 34.03) -- (322.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (322.64, 34.03) -- (322.64, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (322.93, 34.03) -- (322.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (323.97, 34.03) -- (323.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (324.06, 34.03) -- (324.06, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (324.53, 34.03) -- (324.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (324.82, 34.03) -- (324.82, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (325.46, 34.03) -- (325.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (325.85, 34.03) -- (325.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (325.87, 34.03) -- (325.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (325.91, 34.03) -- (325.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (326.16, 34.03) -- (326.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (326.46, 34.03) -- (326.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (327.01, 34.03) -- (327.01, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (327.50, 34.03) -- (327.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (327.78, 34.03) -- (327.78, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (328.37, 34.03) -- (328.37, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (328.92, 34.03) -- (328.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (330.17, 34.03) -- (330.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (330.38, 34.03) -- (330.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (330.88, 34.03) -- (330.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (333.53, 34.03) -- (333.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (333.56, 34.03) -- (333.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (333.69, 34.03) -- (333.69, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (333.82, 34.03) -- (333.82, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (333.83, 34.03) -- (333.83, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (335.38, 34.03) -- (335.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (335.47, 34.03) -- (335.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (337.65, 34.03) -- (337.65, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.50, 34.03) -- (338.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.83, 34.03) -- (338.83, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.87, 34.03) -- (338.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (339.04, 34.03) -- (339.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (339.21, 34.03) -- (339.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (339.40, 34.03) -- (339.40, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (339.55, 34.03) -- (339.55, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (339.76, 34.03) -- (339.76, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (339.84, 34.03) -- (339.84, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (340.15, 34.03) -- (340.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (340.28, 34.03) -- (340.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (340.65, 34.03) -- (340.65, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (341.52, 34.03) -- (341.52, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.53, 34.03) -- (342.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (343.79, 34.03) -- (343.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (343.95, 34.03) -- (343.95, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (345.11, 34.03) -- (345.11, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (345.20, 34.03) -- (345.20, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (345.78, 34.03) -- (345.78, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (346.49, 34.03) -- (346.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (346.80, 34.03) -- (346.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (346.94, 34.03) -- (346.94, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (347.30, 34.03) -- (347.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.63, 34.03) -- (348.63, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.84, 34.03) -- (348.84, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (349.59, 34.03) -- (349.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (350.01, 34.03) -- (350.01, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (350.27, 34.03) -- (350.27, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (350.57, 34.03) -- (350.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (351.61, 34.03) -- (351.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (352.51, 34.03) -- (352.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (354.60, 34.03) -- (354.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (354.77, 34.03) -- (354.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (355.03, 34.03) -- (355.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (355.06, 34.03) -- (355.06, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (355.38, 34.03) -- (355.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (355.44, 34.03) -- (355.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (355.66, 34.03) -- (355.66, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (355.69, 34.03) -- (355.69, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (356.06, 34.03) -- (356.06, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (356.08, 34.03) -- (356.08, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (356.57, 34.03) -- (356.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (356.86, 34.03) -- (356.86, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (356.99, 34.03) -- (356.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (357.04, 34.03) -- (357.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (357.10, 34.03) -- (357.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (357.28, 34.03) -- (357.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (357.68, 34.03) -- (357.68, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (357.71, 34.03) -- (357.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (358.36, 34.03) -- (358.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (358.45, 34.03) -- (358.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (358.80, 34.03) -- (358.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (359.58, 34.03) -- (359.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.14, 34.03) -- (360.14, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.17, 34.03) -- (360.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.28, 34.03) -- (360.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.68, 34.03) -- (360.68, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (362.54, 34.03) -- (362.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (362.92, 34.03) -- (362.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (362.99, 34.03) -- (362.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (362.99, 34.03) -- (362.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (363.68, 34.03) -- (363.68, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (363.71, 34.03) -- (363.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (364.25, 34.03) -- (364.25, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (364.57, 34.03) -- (364.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (364.77, 34.03) -- (364.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (365.00, 34.03) -- (365.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (365.26, 34.03) -- (365.26, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (365.84, 34.03) -- (365.84, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (365.84, 34.03) -- (365.84, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (365.92, 34.03) -- (365.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (366.04, 34.03) -- (366.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (366.47, 34.03) -- (366.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (367.05, 34.03) -- (367.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (368.20, 34.03) -- (368.20, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (368.39, 34.03) -- (368.39, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (368.50, 34.03) -- (368.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (370.21, 34.03) -- (370.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (371.17, 34.03) -- (371.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (371.58, 34.03) -- (371.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (372.02, 34.03) -- (372.02, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (373.58, 34.03) -- (373.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (376.96, 34.03) -- (376.96, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (378.52, 34.03) -- (378.52, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (383.85, 34.03) -- (383.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (384.44, 34.03) -- (384.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (384.92, 34.03) -- (384.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (385.30, 34.03) -- (385.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (385.73, 34.03) -- (385.73, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (385.96, 34.03) -- (385.96, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (386.70, 34.03) -- (386.70, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (386.81, 34.03) -- (386.81, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (387.17, 34.03) -- (387.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (387.19, 34.03) -- (387.19, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (387.24, 34.03) -- (387.24, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (387.39, 34.03) -- (387.39, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (387.67, 34.03) -- (387.67, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (388.26, 34.03) -- (388.26, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.16, 34.03) -- (389.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.82, 34.03) -- (389.82, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (390.40, 34.03) -- (390.40, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (390.45, 34.03) -- (390.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (390.79, 34.03) -- (390.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (391.07, 34.03) -- (391.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (395.16, 34.03) -- (395.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (396.00, 34.03) -- (396.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (396.15, 34.03) -- (396.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (403.52, 34.03) -- (403.52, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (404.02, 34.03) -- (404.02, 41.32);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
-	( 39.69,277.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.42, 34.03) --
+	( 35.42,277.03);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,101.49) {3.8};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,183.81) {4.0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,266.13) {4.2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31, 54.28) {-5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,133.28) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,212.28) {5};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.42, 34.03) --
 	(421.57, 34.03);
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 41.46, 20.31) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 89.02, 20.31) {1};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (136.58, 20.31) {2};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (184.13, 20.31) {3};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (231.69, 20.31) {4};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (279.25, 20.31) {5};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.81, 20.31) {6};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (374.36, 20.31) {7};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 36.01, 20.31) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 83.96, 20.31) {1};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (131.90, 20.31) {2};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (179.85, 20.31) {3};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (227.80, 20.31) {4};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (275.75, 20.31) {5};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (323.69, 20.31) {6};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (371.64, 20.31) {7};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (230.63,  4.82) {Ln(Min. Cap Dist.)$_{t}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (228.50,  4.82) {Ln(Min. Cap Dist.)$_{t}$};
 \end{scope}

### 2014-10-06 LaTeX/mCitySimPlot.tex
updating plots

--- 2014-09-23 LaTeX/mCitySimPlot.tex
@@
-% Created by tikzDevice version 0.7.0 on 2014-09-23 11:39:59
+% Created by tikzDevice version 0.7.0 on 2014-10-06 19:44:41
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 39.69, 34.03) rectangle (421.57,277.03);
+\path[clip] ( 35.42, 34.03) rectangle (421.57,277.03);
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
 
-\path[fill=fillColor] ( 39.69, 34.03) rectangle (421.57,277.03);
+\path[fill=fillColor] ( 35.42, 34.03) rectangle (421.57,277.03);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 57.05,110.46) --
-	( 62.08,112.14) --
-	( 67.11,113.83) --
-	( 72.14,115.51) --
-	( 77.17,117.20) --
-	( 82.20,118.88) --
-	( 87.23,120.57) --
-	( 92.27,122.25) --
-	( 97.30,123.94) --
-	(102.33,125.62) --
-	(107.36,127.30) --
-	(112.39,128.99) --
-	(117.42,130.67) --
-	(122.45,132.36) --
-	(127.49,134.04) --
-	(132.52,135.73) --
-	(137.55,137.41) --
-	(142.58,139.10) --
-	(147.61,140.78) --
-	(152.64,142.47) --
-	(157.67,144.15) --
-	(162.71,145.84) --
-	(167.74,147.52) --
-	(172.77,149.20) --
-	(177.80,150.89) --
-	(182.83,152.57) --
-	(187.86,154.26) --
-	(192.89,155.94) --
-	(197.93,157.63) --
-	(202.96,159.31) --
-	(207.99,161.00) --
-	(213.02,162.68) --
-	(218.05,164.37) --
-	(223.08,166.05) --
-	(228.12,167.74) --
-	(233.15,169.42) --
-	(238.18,171.11) --
-	(243.21,172.79) --
-	(248.24,174.47) --
-	(253.27,176.16) --
-	(258.30,177.84) --
-	(263.34,179.53) --
-	(268.37,181.21) --
-	(273.40,182.90) --
-	(278.43,184.58) --
-	(283.46,186.27) --
-	(288.49,187.95) --
-	(293.52,189.64) --
-	(298.56,191.32) --
-	(303.59,193.01) --
-	(308.62,194.69) --
-	(313.65,196.38) --
-	(318.68,198.06) --
-	(323.71,199.74) --
-	(328.74,201.43) --
-	(333.78,203.11) --
-	(338.81,204.80) --
-	(343.84,206.48) --
-	(348.87,208.17) --
-	(353.90,209.85) --
-	(358.93,211.54) --
-	(363.96,213.22) --
-	(369.00,214.91) --
-	(374.03,216.59) --
-	(379.06,218.28) --
-	(384.09,219.96) --
-	(389.12,221.65) --
-	(394.15,223.33) --
-	(399.18,225.01) --
-	(404.22,226.70);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,106.37) --
+	( 61.01,109.04) --
+	( 65.48,110.52) --
+	( 65.62,110.57) --
+	( 79.64,115.23) --
+	( 88.50,118.17) --
+	( 94.41,120.14) --
+	( 97.84,121.27) --
+	(104.50,123.49) --
+	(110.01,125.32) --
+	(113.94,126.62) --
+	(116.56,127.49) --
+	(124.94,130.28) --
+	(160.01,141.93) --
+	(160.15,141.97) --
+	(163.56,143.10) --
+	(164.50,143.42) --
+	(175.08,146.93) --
+	(177.68,147.80) --
+	(185.12,150.27) --
+	(195.04,153.56) --
+	(195.05,153.57) --
+	(199.79,155.14) --
+	(200.09,155.24) --
+	(201.70,155.77) --
+	(202.42,156.01) --
+	(203.15,156.26) --
+	(203.24,156.29) --
+	(203.92,156.51) --
+	(204.08,156.56) --
+	(205.70,157.10) --
+	(211.30,158.97) --
+	(213.02,159.54) --
+	(213.22,159.60) --
+	(213.28,159.62) --
+	(214.88,160.15) --
+	(219.39,161.65) --
+	(219.87,161.81) --
+	(224.51,163.35) --
+	(226.38,163.97) --
+	(226.89,164.14) --
+	(228.22,164.58) --
+	(229.80,165.11) --
+	(230.53,165.35) --
+	(231.54,165.69) --
+	(232.29,165.94) --
+	(232.55,166.02) --
+	(232.60,166.04) --
+	(233.03,166.18) --
+	(236.50,167.34) --
+	(238.44,167.98) --
+	(239.50,168.33) --
+	(240.76,168.75) --
+	(242.87,169.45) --
+	(243.82,169.77) --
+	(244.87,170.11) --
+	(245.90,170.46) --
+	(247.14,170.87) --
+	(247.15,170.87) --
+	(248.00,171.16) --
+	(248.59,171.35) --
+	(249.15,171.54) --
+	(249.91,171.79) --
+	(250.14,171.87) --
+	(250.71,172.06) --
+	(251.21,172.22) --
+	(251.61,172.35) --
+	(251.88,172.44) --
+	(252.52,172.66) --
+	(252.98,172.81) --
+	(253.12,172.85) --
+	(253.36,172.94) --
+	(254.91,173.45) --
+	(255.02,173.49) --
+	(256.32,173.92) --
+	(258.61,174.68) --
+	(260.03,175.15) --
+	(260.14,175.19) --
+	(260.80,175.41) --
+	(261.97,175.79) --
+	(262.19,175.87) --
+	(262.48,175.96) --
+	(262.99,176.14) --
+	(264.29,176.57) --
+	(264.50,176.64) --
+	(264.53,176.65) --
+	(264.97,176.79) --
+	(266.10,177.17) --
+	(266.13,177.18) --
+	(266.44,177.28) --
+	(267.28,177.56) --
+	(267.71,177.70) --
+	(268.38,177.92) --
+	(269.11,178.17) --
+	(269.74,178.38) --
+	(269.87,178.42) --
+	(271.02,178.80) --
+	(271.10,178.83) --
+	(271.68,179.02) --
+	(272.40,179.26) --
+	(272.79,179.39) --
+	(273.63,179.67) --
+	(274.52,179.96) --
+	(275.28,180.22) --
+	(275.59,180.32) --
+	(276.13,180.50) --
+	(276.31,180.56) --
+	(276.77,180.71) --
+	(277.30,180.89) --
+	(277.98,181.12) --
+	(278.04,181.13) --
+	(278.45,181.27) --
+	(279.17,181.51) --
+	(279.30,181.55) --
+	(279.52,181.62) --
+	(279.66,181.67) --
+	(279.69,181.68) --
+	(280.15,181.83) --
+	(280.53,181.96) --
+	(280.72,182.02) --
+	(281.20,182.18) --
+	(281.36,182.24) --
+	(281.45,182.27) --
+	(282.80,182.71) --
+	(283.05,182.80) --
+	(283.89,183.08) --
+	(283.98,183.11) --
+	(284.07,183.14) --
+	(284.62,183.32) --
+	(284.86,183.40) --
+	(285.03,183.46) --
+	(285.13,183.49) --
+	(286.00,183.78) --
+	(286.57,183.97) --
+	(286.59,183.98) --
+	(287.25,184.19) --
+	(287.81,184.38) --
+	(288.54,184.62) --
+	(288.59,184.64) --
+	(289.22,184.85) --
+	(289.76,185.03) --
+	(290.76,185.36) --
+	(290.86,185.39) --
+	(291.20,185.51) --
+	(291.32,185.54) --
+	(291.81,185.71) --
+	(291.88,185.73) --
+	(292.21,185.84) --
+	(292.36,185.89) --
+	(292.42,185.91) --
+	(292.49,185.93) --
+	(292.51,185.94) --
+	(292.62,185.98) --
+	(293.21,186.17) --
+	(293.91,186.41) --
+	(295.25,186.85) --
+	(295.45,186.92) --
+	(295.51,186.94) --
+	(295.93,187.08) --
+	(295.99,187.10) --
+	(296.10,187.13) --
+	(296.47,187.26) --
+	(296.65,187.32) --
+	(296.99,187.43) --
+	(297.01,187.43) --
+	(297.04,187.45) --
+	(297.05,187.45) --
+	(297.09,187.46) --
+	(297.13,187.47) --
+	(297.22,187.51) --
+	(297.31,187.53) --
+	(297.31,187.53) --
+	(297.71,187.67) --
+	(297.96,187.75) --
+	(298.34,187.88) --
+	(298.57,187.95) --
+	(299.04,188.11) --
+	(300.58,188.62) --
+	(300.69,188.66) --
+	(301.32,188.87) --
+	(302.10,189.13) --
+	(302.23,189.17) --
+	(302.50,189.26) --
+	(302.82,189.36) --
+	(302.98,189.42) --
+	(303.49,189.59) --
+	(303.87,189.71) --
+	(304.04,189.77) --
+	(304.05,189.77) --
+	(304.17,189.82) --
+	(304.21,189.83) --
+	(304.88,190.05) --
+	(305.44,190.24) --
+	(305.52,190.26) --
+	(305.61,190.29) --
+	(305.86,190.37) --
+	(306.19,190.49) --
+	(306.32,190.53) --
+	(307.91,191.06) --
+	(307.96,191.07) --
+	(308.47,191.24) --
+	(308.57,191.27) --
+	(309.22,191.49) --
+	(309.44,191.56) --
+	(309.51,191.59) --
+	(309.67,191.64) --
+	(310.00,191.75) --
+	(310.25,191.83) --
+	(310.76,192.00) --
+	(310.92,192.06) --
+	(311.04,192.09) --
+	(311.16,192.14) --
+	(311.41,192.22) --
+	(311.41,192.22) --
+	(311.44,192.23) --
+	(311.54,192.26) --
+	(311.68,192.31) --
+	(311.68,192.31) --
+	(311.88,192.38) --
+	(312.22,192.49) --
+	(312.92,192.72) --
+	(313.12,192.79) --
+	(313.27,192.84) --
+	(313.53,192.93) --
+	(313.83,193.02) --
+	(314.24,193.16) --
+	(314.31,193.18) --
+	(314.45,193.23) --
+	(314.63,193.29) --
+	(315.00,193.41) --
+	(315.21,193.48) --
+	(315.23,193.49) --
+	(315.37,193.53) --
+	(315.48,193.57) --
+	(315.51,193.58) --
+	(315.62,193.62) --
+	(315.70,193.64) --
+	(315.79,193.67) --
+	(316.13,193.79) --
+	(316.22,193.82) --
+	(316.38,193.87) --
+	(316.61,193.95) --
+	(316.93,194.05) --
+	(317.07,194.10) --
+	(317.20,194.14) --
+	(317.36,194.20) --
+	(317.75,194.33) --
+	(317.76,194.33) --
+	(317.79,194.34) --
+	(317.86,194.36) --
+	(317.89,194.37) --
+	(317.98,194.40) --
+	(318.43,194.55) --
+	(318.60,194.61) --
+	(318.85,194.69) --
+	(319.11,194.78) --
+	(319.21,194.81) --
+	(319.52,194.91) --
+	(319.81,195.01) --
+	(320.44,195.22) --
+	(321.85,195.69) --
+	(321.91,195.71) --
+	(322.04,195.75) --
+	(322.30,195.84) --
+	(322.60,195.94) --
+	(322.75,195.99) --
+	(323.02,196.08) --
+	(323.10,196.10) --
+	(323.28,196.16) --
+	(324.05,196.42) --
+	(324.42,196.54) --
+	(324.61,196.60) --
+	(324.72,196.64) --
+	(325.08,196.76) --
+	(325.99,197.06) --
+	(326.58,197.26) --
+	(326.72,197.31) --
+	(327.61,197.60) --
+	(327.91,197.70) --
+	(328.67,197.95) --
+	(328.94,198.04) --
+	(329.07,198.09) --
+	(329.52,198.24) --
+	(331.17,198.78) --
+	(332.00,199.06) --
+	(332.27,199.15) --
+	(333.07,199.42) --
+	(333.19,199.45) --
+	(333.76,199.64) --
+	(335.51,200.23) --
+	(336.07,200.41) --
+	(336.75,200.64) --
+	(336.88,200.68) --
+	(337.54,200.90) --
+	(337.92,201.03) --
+	(338.29,201.15) --
+	(338.32,201.16) --
+	(338.37,201.17) --
+	(338.79,201.32) --
+	(338.87,201.34) --
+	(339.41,201.52) --
+	(339.54,201.56) --
+	(340.26,201.80) --
+	(340.28,201.81) --
+	(340.36,201.84) --
+	(340.58,201.91) --
+	(340.90,202.02) --
+	(341.07,202.07) --
+	(341.38,202.18) --
+	(341.48,202.21) --
+	(341.53,202.23) --
+	(341.57,202.24) --
+	(342.00,202.38) --
+	(342.06,202.40) --
+	(342.60,202.58) --
+	(342.92,202.69) --
+	(344.39,203.18) --
+	(344.81,203.31) --
+	(345.03,203.39) --
+	(345.51,203.55) --
+	(345.56,203.56) --
+	(346.27,203.80) --
+	(348.09,204.40) --
+	(348.19,204.44) --
+	(348.32,204.48) --
+	(348.52,204.55) --
+	(348.65,204.59) --
+	(350.04,205.05) --
+	(350.29,205.13) --
+	(350.39,205.17) --
+	(351.49,205.53) --
+	(354.19,206.43) --
+	(354.41,206.50) --
+	(354.96,206.69) --
+	(354.99,206.69) --
+	(355.28,206.79) --
+	(355.84,206.98) --
+	(356.71,207.27) --
+	(356.75,207.28) --
+	(357.50,207.53) --
+	(357.53,207.54) --
+	(358.04,207.71) --
+	(358.62,207.90) --
+	(359.31,208.13) --
+	(359.62,208.23) --
+	(359.75,208.28) --
+	(359.85,208.31) --
+	(360.61,208.56) --
+	(360.64,208.57) --
+	(360.71,208.60) --
+	(361.91,208.99) --
+	(362.60,209.22) --
+	(364.24,209.77) --
+	(364.46,209.84) --
+	(365.70,210.25) --
+	(366.29,210.45) --
+	(370.53,211.86) --
+	(371.02,212.02) --
+	(372.06,212.37) --
+	(372.07,212.37) --
+	(372.38,212.47) --
+	(372.60,212.54) --
+	(372.90,212.65) --
+	(373.16,212.73) --
+	(373.53,212.86) --
+	(373.80,212.94) --
+	(374.46,213.16) --
+	(374.81,213.28) --
+	(375.77,213.60) --
+	(376.36,213.80) --
+	(376.51,213.85) --
+	(376.93,213.98) --
+	(378.03,214.35) --
+	(379.36,214.79) --
+	(379.36,214.79) --
+	(380.09,215.03) --
+	(380.12,215.04) --
+	(381.03,215.35) --
+	(381.47,215.49) --
+	(381.75,215.58) --
+	(382.36,215.79) --
+	(382.44,215.82) --
+	(382.57,215.86) --
+	(383.02,216.01) --
+	(385.04,216.68) --
+	(385.16,216.72) --
+	(388.87,217.95) --
+	(393.56,219.51) --
+	(395.71,220.22) --
+	(403.26,222.73) --
+	(404.02,222.98);
 \definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}
 
-\path[fill=fillColor,fill opacity=0.30] ( 57.05,174.43) --
-	( 62.08,174.80) --
-	( 67.11,175.43) --
-	( 72.14,175.95) --
-	( 77.17,176.45) --
-	( 82.20,177.01) --
-	( 87.23,177.60) --
-	( 92.27,178.07) --
-	( 97.30,178.83) --
-	(102.33,179.63) --
-	(107.36,180.19) --
-	(112.39,180.68) --
-	(117.42,181.22) --
-	(122.45,181.91) --
-	(127.49,182.61) --
-	(132.52,183.22) --
-	(137.55,183.85) --
-	(142.58,184.72) --
-	(147.61,185.27) --
-	(152.64,185.85) --
-	(157.67,186.68) --
-	(162.71,187.40) --
-	(167.74,188.19) --
-	(172.77,188.79) --
-	(177.80,189.72) --
-	(182.83,190.53) --
-	(187.86,191.58) --
-	(192.89,192.32) --
-	(197.93,193.15) --
-	(202.96,194.08) --
-	(207.99,195.20) --
-	(213.02,196.17) --
-	(218.05,197.04) --
-	(223.08,198.12) --
-	(228.12,199.15) --
-	(233.15,200.19) --
-	(238.18,201.29) --
-	(243.21,202.47) --
-	(248.24,203.82) --
-	(253.27,205.19) --
-	(258.30,206.48) --
-	(263.34,207.77) --
-	(268.37,209.20) --
-	(273.40,210.73) --
-	(278.43,212.20) --
-	(283.46,213.76) --
-	(288.49,215.30) --
-	(293.52,216.81) --
-	(298.56,218.76) --
-	(303.59,220.71) --
-	(308.62,222.73) --
-	(313.65,224.51) --
-	(318.68,226.51) --
-	(323.71,228.57) --
-	(328.74,230.64) --
-	(333.78,232.65) --
-	(338.81,234.73) --
-	(343.84,236.98) --
-	(348.87,239.31) --
-	(353.90,241.60) --
-	(358.93,243.92) --
-	(363.96,246.40) --
-	(369.00,248.74) --
-	(374.03,251.08) --
-	(379.06,253.40) --
-	(384.09,255.89) --
-	(389.12,258.42) --
-	(394.15,260.84) --
-	(399.18,263.30) --
-	(404.22,265.99) --
-	(404.22,186.70) --
-	(399.18,185.91) --
-	(394.15,185.08) --
-	(389.12,184.30) --
-	(384.09,183.58) --
-	(379.06,182.70) --
-	(374.03,181.87) --
-	(369.00,180.89) --
-	(363.96,179.93) --
-	(358.93,178.91) --
-	(353.90,178.04) --
-	(348.87,176.86) --
-	(343.84,175.89) --
-	(338.81,174.74) --
-	(333.78,173.45) --
-	(328.74,172.28) --
-	(323.71,171.02) --
-	(318.68,169.43) --
-	(313.65,167.97) --
-	(308.62,166.54) --
-	(303.59,165.18) --
-	(298.56,163.70) --
-	(293.52,162.08) --
-	(288.49,160.29) --
-	(283.46,158.60) --
-	(278.43,156.91) --
-	(273.40,155.18) --
-	(268.37,153.23) --
-	(263.34,151.42) --
-	(258.30,149.61) --
-	(253.27,147.65) --
-	(248.24,145.45) --
-	(243.21,143.23) --
-	(238.18,141.02) --
-	(233.15,138.72) --
-	(228.12,136.35) --
-	(223.08,133.80) --
-	(218.05,131.34) --
-	(213.02,128.83) --
-	(207.99,126.45) --
-	(202.96,124.00) --
-	(197.93,121.57) --
-	(192.89,119.03) --
-	(187.86,116.41) --
-	(182.83,113.90) --
-	(177.80,111.23) --
-	(172.77,108.70) --
-	(167.74,105.98) --
-	(162.71,103.34) --
-	(157.67,100.79) --
-	(152.64, 98.10) --
-	(147.61, 95.49) --
-	(142.58, 92.64) --
-	(137.55, 89.85) --
-	(132.52, 87.02) --
-	(127.49, 84.25) --
-	(122.45, 81.44) --
-	(117.42, 78.59) --
-	(112.39, 75.96) --
-	(107.36, 73.32) --
-	(102.33, 70.44) --
-	( 97.30, 67.62) --
-	( 92.27, 64.83) --
-	( 87.23, 61.80) --
-	( 82.20, 58.96) --
-	( 77.17, 56.21) --
-	( 72.14, 53.52) --
-	( 67.11, 50.65) --
-	( 62.08, 47.79) --
-	( 57.05, 45.08) --
+\path[fill=fillColor,fill opacity=0.30] ( 52.97,167.36) --
+	( 61.01,168.41) --
+	( 65.48,168.80) --
+	( 65.62,168.81) --
+	( 79.64,170.79) --
+	( 88.50,171.79) --
+	( 94.41,172.49) --
+	( 97.84,173.06) --
+	(104.50,173.98) --
+	(110.01,174.56) --
+	(113.94,175.03) --
+	(116.56,175.36) --
+	(124.94,176.30) --
+	(160.01,181.27) --
+	(160.15,181.30) --
+	(163.56,181.70) --
+	(164.50,181.78) --
+	(175.08,183.35) --
+	(177.68,183.86) --
+	(185.12,185.40) --
+	(195.04,187.30) --
+	(195.05,187.30) --
+	(199.79,188.52) --
+	(200.09,188.60) --
+	(201.70,188.94) --
+	(202.42,189.05) --
+	(203.15,189.18) --
+	(203.24,189.19) --
+	(203.92,189.29) --
+	(204.08,189.32) --
+	(205.70,189.71) --
+	(211.30,190.89) --
+	(213.02,191.21) --
+	(213.22,191.26) --
+	(213.28,191.27) --
+	(214.88,191.68) --
+	(219.39,192.70) --
+	(219.87,192.77) --
+	(224.51,193.76) --
+	(226.38,194.26) --
+	(226.89,194.38) --
+	(228.22,194.75) --
+	(229.80,195.15) --
+	(230.53,195.25) --
+	(231.54,195.47) --
+	(232.29,195.59) --
+	(232.55,195.66) --
+	(232.60,195.67) --
+	(233.03,195.77) --
+	(236.50,196.61) --
+	(238.44,197.03) --
+	(239.50,197.27) --
+	(240.76,197.54) --
+	(242.87,198.03) --
+	(243.82,198.26) --
+	(244.87,198.51) --
+	(245.90,198.81) --
+	(247.14,199.15) --
+	(247.15,199.15) --
+	(248.00,199.39) --
+	(248.59,199.55) --
+	(249.15,199.72) --
+	(249.91,199.94) --
+	(250.14,200.00) --
+	(250.71,200.16) --
+	(251.21,200.29) --
+	(251.61,200.40) --
+	(251.88,200.46) --
+	(252.52,200.69) --
+	(252.98,200.84) --
+	(253.12,200.86) --
+	(253.36,200.89) --
+	(254.91,201.29) --
+	(255.02,201.32) --
+	(256.32,201.72) --
+	(258.61,202.38) --
+	(260.03,202.80) --
+	(260.14,202.84) --
+	(260.80,203.04) --
+	(261.97,203.27) --
+	(262.19,203.35) --
+	(262.48,203.44) --
+	(262.99,203.62) --
+	(264.29,204.03) --
+	(264.50,204.10) --
+	(264.53,204.11) --
+	(264.97,204.25) --
+	(266.10,204.54) --
+	(266.13,204.55) --
+	(266.44,204.61) --
+	(267.28,204.93) --
+	(267.71,205.05) --
+	(268.38,205.26) --
+	(269.11,205.45) --
+	(269.74,205.69) --
+	(269.87,205.74) --
+	(271.02,206.18) --
+	(271.10,206.22) --
+	(271.68,206.47) --
+	(272.40,206.66) --
+	(272.79,206.78) --
+	(273.63,207.07) --
+	(274.52,207.40) --
+	(275.28,207.68) --
+	(275.59,207.78) --
+	(276.13,207.95) --
+	(276.31,207.99) --
+	(276.77,208.14) --
+	(277.30,208.37) --
+	(277.98,208.66) --
+	(278.04,208.68) --
+	(278.45,208.79) --
+	(279.17,208.98) --
+	(279.30,209.02) --
+	(279.52,209.08) --
+	(279.66,209.14) --
+	(279.69,209.14) --
+	(280.15,209.31) --
+	(280.53,209.48) --
+	(280.72,209.56) --
+	(281.20,209.75) --
+	(281.36,209.82) --
+	(281.45,209.85) --
+	(282.80,210.34) --
+	(283.05,210.37) --
+	(283.89,210.70) --
+	(283.98,210.74) --
+	(284.07,210.78) --
+	(284.62,210.98) --
+	(284.86,211.08) --
+	(285.03,211.13) --
+	(285.13,211.16) --
+	(286.00,211.42) --
+	(286.57,211.61) --
+	(286.59,211.61) --
+	(287.25,211.79) --
+	(287.81,211.98) --
+	(288.54,212.28) --
+	(288.59,212.29) --
+	(289.22,212.44) --
+	(289.76,212.64) --
+	(290.76,213.08) --
+	(290.86,213.13) --
+	(291.20,213.21) --
+	(291.32,213.21) --
+	(291.81,213.42) --
+	(291.88,213.46) --
+	(292.21,213.58) --
+	(292.36,213.65) --
+	(292.42,213.69) --
+	(292.49,213.72) --
+	(292.51,213.74) --
+	(292.62,213.79) --
+	(293.21,213.98) --
+	(293.91,214.28) --
+	(295.25,214.70) --
+	(295.45,214.78) --
+	(295.51,214.81) --
+	(295.93,215.00) --
+	(295.99,215.02) --
+	(296.10,215.06) --
+	(296.47,215.21) --
+	(296.65,215.26) --
+	(296.99,215.30) --
+	(297.01,215.30) --
+	(297.04,215.31) --
+	(297.05,215.31) --
+	(297.09,215.32) --
+	(297.13,215.34) --
+	(297.22,215.39) --
+	(297.31,215.44) --
+	(297.31,215.44) --
+	(297.71,215.55) --
+	(297.96,215.64) --
+	(298.34,215.77) --
+	(298.57,215.86) --
+	(299.04,216.04) --
+	(300.58,216.50) --
+	(300.69,216.54) --
+	(301.32,216.72) --
+	(302.10,216.99) --
+	(302.23,217.04) --
+	(302.50,217.16) --
+	(302.82,217.32) --
+	(302.98,217.40) --
+	(303.49,217.63) --
+	(303.87,217.81) --
+	(304.04,217.89) --
+	(304.05,217.89) --
+	(304.17,217.95) --
+	(304.21,217.97) --
+	(304.88,218.27) --
+	(305.44,218.51) --
+	(305.52,218.55) --
+	(305.61,218.58) --
+	(305.86,218.68) --
+	(306.19,218.81) --
+	(306.32,218.86) --
+	(307.91,219.57) --
+	(307.96,219.60) --
+	(308.47,219.81) --
+	(308.57,219.85) --
+	(309.22,220.10) --
+	(309.44,220.18) --
+	(309.51,220.20) --
+	(309.67,220.25) --
+	(310.00,220.39) --
+	(310.25,220.47) --
+	(310.76,220.68) --
+	(310.92,220.74) --
+	(311.04,220.77) --
+	(311.16,220.82) --
+	(311.41,220.90) --
+	(311.41,220.90) --
+	(311.44,220.91) --
+	(311.54,220.94) --
+	(311.68,220.98) --
+	(311.68,220.99) --
+	(311.88,221.05) --
+	(312.22,221.19) --
+	(312.92,221.49) --
+	(313.12,221.57) --
+	(313.27,221.65) --
+	(313.53,221.73) --
+	(313.83,221.83) --
+	(314.24,222.00) --
+	(314.31,222.04) --
+	(314.45,222.11) --
+	(314.63,222.16) --
+	(315.00,222.37) --
+	(315.21,222.46) --
+	(315.23,222.47) --
+	(315.37,222.52) --
+	(315.48,222.56) --
+	(315.51,222.58) --
+	(315.62,222.62) --
+	(315.70,222.64) --
+	(315.79,222.66) --
+	(316.13,222.81) --
+	(316.22,222.83) --
+	(316.38,222.87) --
+	(316.61,222.95) --
+	(316.93,223.12) --
+	(317.07,223.18) --
+	(317.20,223.26) --
+	(317.36,223.33) --
+	(317.75,223.47) --
+	(317.76,223.47) --
+	(317.79,223.49) --
+	(317.86,223.53) --
+	(317.89,223.54) --
+	(317.98,223.58) --
+	(318.43,223.78) --
+	(318.60,223.85) --
+	(318.85,224.00) --
+	(319.11,224.09) --
+	(319.21,224.11) --
+	(319.52,224.25) --
+	(319.81,224.40) --
+	(320.44,224.64) --
+	(321.85,225.23) --
+	(321.91,225.27) --
+	(322.04,225.35) --
+	(322.30,225.47) --
+	(322.60,225.60) --
+	(322.75,225.66) --
+	(323.02,225.77) --
+	(323.10,225.80) --
+	(323.28,225.87) --
+	(324.05,226.17) --
+	(324.42,226.34) --
+	(324.61,226.43) --
+	(324.72,226.50) --
+	(325.08,226.65) --
+	(325.99,227.12) --
+	(326.58,227.38) --
+	(326.72,227.44) --
+	(327.61,227.83) --
+	(327.91,227.96) --
+	(328.67,228.25) --
+	(328.94,228.38) --
+	(329.07,228.46) --
+	(329.52,228.70) --
+	(331.17,229.50) --
+	(332.00,229.87) --
+	(332.27,230.00) --
+	(333.07,230.25) --
+	(333.19,230.29) --
+	(333.76,230.52) --
+	(335.51,231.36) --
+	(336.07,231.68) --
+	(336.75,232.03) --
+	(336.88,232.07) --
+	(337.54,232.34) --
+	(337.92,232.47) --
+	(338.29,232.66) --
+	(338.32,232.68) --
+	(338.37,232.70) --
+	(338.79,232.94) --
+	(338.87,232.97) --
+	(339.41,233.19) --
+	(339.54,233.26) --
+	(340.26,233.63) --
+	(340.28,233.64) --
+	(340.36,233.69) --
+	(340.58,233.82) --
+	(340.90,234.00) --
+	(341.07,234.09) --
+	(341.38,234.25) --
+	(341.48,234.29) --
+	(341.53,234.32) --
+	(341.57,234.33) --
+	(342.00,234.53) --
+	(342.06,234.56) --
+	(342.60,234.82) --
+	(342.92,234.94) --
+	(344.39,235.59) --
+	(344.81,235.76) --
+	(345.03,235.85) --
+	(345.51,236.00) --
+	(345.56,236.01) --
+	(346.27,236.21) --
+	(348.09,237.11) --
+	(348.19,237.16) --
+	(348.32,237.23) --
+	(348.52,237.32) --
+	(348.65,237.36) --
+	(350.04,238.11) --
+	(350.29,238.22) --
+	(350.39,238.27) --
+	(351.49,238.86) --
+	(354.19,240.24) --
+	(354.41,240.37) --
+	(354.96,240.65) --
+	(354.99,240.67) --
+	(355.28,240.79) --
+	(355.84,241.02) --
+	(356.71,241.48) --
+	(356.75,241.51) --
+	(357.50,241.86) --
+	(357.53,241.87) --
+	(358.04,242.13) --
+	(358.62,242.42) --
+	(359.31,242.81) --
+	(359.62,242.94) --
+	(359.75,243.03) --
+	(359.85,243.09) --
+	(360.61,243.54) --
+	(360.64,243.55) --
+	(360.71,243.59) --
+	(361.91,244.20) --
+	(362.60,244.50) --
+	(364.24,245.24) --
+	(364.46,245.35) --
+	(365.70,245.99) --
+	(366.29,246.26) --
+	(370.53,248.44) --
+	(371.02,248.71) --
+	(372.06,249.22) --
+	(372.07,249.22) --
+	(372.38,249.33) --
+	(372.60,249.45) --
+	(372.90,249.61) --
+	(373.16,249.73) --
+	(373.53,249.89) --
+	(373.80,250.04) --
+	(374.46,250.35) --
+	(374.81,250.52) --
+	(375.77,251.03) --
+	(376.36,251.34) --
+	(376.51,251.43) --
+	(376.93,251.64) --
+	(378.03,252.22) --
+	(379.36,252.85) --
+	(379.36,252.86) --
+	(380.09,253.22) --
+	(380.12,253.24) --
+	(381.03,253.71) --
+	(381.47,253.91) --
+	(381.75,254.05) --
+	(382.36,254.37) --
+	(382.44,254.41) --
+	(382.57,254.46) --
+	(383.02,254.69) --
+	(385.04,255.76) --
+	(385.16,255.82) --
+	(388.87,257.82) --
+	(393.56,260.29) --
+	(395.71,261.42) --
+	(403.26,265.59) --
+	(404.02,265.99) --
+	(404.02,182.27) --
+	(403.26,182.16) --
+	(395.71,180.94) --
+	(393.56,180.61) --
+	(388.87,179.73) --
+	(385.16,179.04) --
+	(385.04,179.03) --
+	(383.02,178.81) --
+	(382.57,178.70) --
+	(382.44,178.65) --
+	(382.36,178.61) --
+	(381.75,178.55) --
+	(381.47,178.49) --
+	(381.03,178.47) --
+	(380.12,178.30) --
+	(380.09,178.30) --
+	(379.36,178.16) --
+	(379.36,178.16) --
+	(378.03,177.94) --
+	(376.93,177.72) --
+	(376.51,177.66) --
+	(376.36,177.65) --
+	(375.77,177.59) --
+	(374.81,177.41) --
+	(374.46,177.37) --
+	(373.80,177.19) --
+	(373.53,177.12) --
+	(373.16,177.03) --
+	(372.90,176.96) --
+	(372.60,176.88) --
+	(372.38,176.82) --
+	(372.07,176.74) --
+	(372.06,176.74) --
+	(371.02,176.61) --
+	(370.53,176.50) --
+	(366.29,175.56) --
+	(365.70,175.48) --
+	(364.46,175.26) --
+	(364.24,175.21) --
+	(362.60,174.88) --
+	(361.91,174.73) --
+	(360.71,174.46) --
+	(360.64,174.43) --
+	(360.61,174.42) --
+	(359.85,174.28) --
+	(359.75,174.26) --
+	(359.62,174.24) --
+	(359.31,174.18) --
+	(358.62,174.10) --
+	(358.04,174.00) --
+	(357.53,173.89) --
+	(357.50,173.88) --
+	(356.75,173.74) --
+	(356.71,173.73) --
+	(355.84,173.55) --
+	(355.28,173.44) --
+	(354.99,173.38) --
+	(354.96,173.38) --
+	(354.41,173.27) --
+	(354.19,173.22) --
+	(351.49,172.56) --
+	(350.39,172.25) --
+	(350.29,172.22) --
+	(350.04,172.22) --
+	(348.65,172.01) --
+	(348.52,171.96) --
+	(348.32,171.89) --
+	(348.19,171.87) --
+	(348.09,171.85) --
+	(346.27,171.41) --
+	(345.56,171.26) --
+	(345.51,171.26) --
+	(345.03,171.14) --
+	(344.81,171.13) --
+	(344.39,171.04) --
+	(342.92,170.73) --
+	(342.60,170.68) --
+	(342.06,170.59) --
+	(342.00,170.58) --
+	(341.57,170.51) --
+	(341.53,170.50) --
+	(341.48,170.48) --
+	(341.38,170.46) --
+	(341.07,170.41) --
+	(340.90,170.35) --
+	(340.58,170.27) --
+	(340.36,170.25) --
+	(340.28,170.24) --
+	(340.26,170.24) --
+	(339.54,170.08) --
+	(339.41,170.03) --
+	(338.87,169.90) --
+	(338.79,169.88) --
+	(338.37,169.75) --
+	(338.32,169.74) --
+	(338.29,169.73) --
+	(337.92,169.66) --
+	(337.54,169.63) --
+	(336.88,169.52) --
+	(336.75,169.49) --
+	(336.07,169.33) --
+	(335.51,169.18) --
+	(333.76,168.91) --
+	(333.19,168.80) --
+	(333.07,168.78) --
+	(332.27,168.47) --
+	(332.00,168.39) --
+	(331.17,168.19) --
+	(329.52,167.74) --
+	(329.07,167.64) --
+	(328.94,167.62) --
+	(328.67,167.52) --
+	(327.91,167.32) --
+	(327.61,167.25) --
+	(326.72,167.12) --
+	(326.58,167.07) --
+	(325.99,166.89) --
+	(325.08,166.68) --
+	(324.72,166.60) --
+	(324.61,166.57) --
+	(324.42,166.53) --
+	(324.05,166.45) --
+	(323.28,166.24) --
+	(323.10,166.20) --
+	(323.02,166.19) --
+	(322.75,166.13) --
+	(322.60,166.08) --
+	(322.30,166.02) --
+	(322.04,165.95) --
+	(321.91,165.91) --
+	(321.85,165.90) --
+	(320.44,165.54) --
+	(319.81,165.48) --
+	(319.52,165.41) --
+	(319.21,165.35) --
+	(319.11,165.31) --
+	(318.85,165.22) --
+	(318.60,165.15) --
+	(318.43,165.12) --
+	(317.98,165.00) --
+	(317.89,164.98) --
+	(317.86,164.98) --
+	(317.79,164.97) --
+	(317.76,164.96) --
+	(317.75,164.96) --
+	(317.36,164.87) --
+	(317.20,164.84) --
+	(317.07,164.81) --
+	(316.93,164.77) --
+	(316.61,164.69) --
+	(316.38,164.64) --
+	(316.22,164.63) --
+	(316.13,164.63) --
+	(315.79,164.58) --
+	(315.70,164.56) --
+	(315.62,164.55) --
+	(315.51,164.53) --
+	(315.48,164.52) --
+	(315.37,164.49) --
+	(315.23,164.45) --
+	(315.21,164.44) --
+	(315.00,164.38) --
+	(314.63,164.28) --
+	(314.45,164.23) --
+	(314.31,164.17) --
+	(314.24,164.15) --
+	(313.83,164.06) --
+	(313.53,163.97) --
+	(313.27,163.89) --
+	(313.12,163.80) --
+	(312.92,163.72) --
+	(312.22,163.58) --
+	(311.88,163.47) --
+	(311.68,163.41) --
+	(311.68,163.41) --
+	(311.54,163.36) --
+	(311.44,163.32) --
+	(311.41,163.32) --
+	(311.41,163.32) --
+	(311.16,163.25) --
+	(311.04,163.22) --
+	(310.92,163.20) --
+	(310.76,163.15) --
+	(310.25,163.05) --
+	(310.00,162.99) --
+	(309.67,162.92) --
+	(309.51,162.86) --
+	(309.44,162.83) --
+	(309.22,162.77) --
+	(308.57,162.62) --
+	(308.47,162.60) --
+	(307.96,162.44) --
+	(307.91,162.43) --
+	(306.32,161.94) --
+	(306.19,161.90) --
+	(305.86,161.80) --
+	(305.61,161.73) --
+	(305.52,161.70) --
+	(305.44,161.68) --
+	(304.88,161.50) --
+	(304.21,161.34) --
+	(304.17,161.33) --
+	(304.05,161.30) --
+	(304.04,161.30) --
+	(303.87,161.27) --
+	(303.49,161.16) --
+	(302.98,161.00) --
+	(302.82,160.95) --
+	(302.50,160.89) --
+	(302.23,160.84) --
+	(302.10,160.82) --
+	(301.32,160.64) --
+	(300.69,160.55) --
+	(300.58,160.54) --
+	(299.04,160.13) --
+	(298.57,160.04) --
+	(298.34,159.99) --
+	(297.96,159.86) --
+	(297.71,159.79) --
+	(297.31,159.71) --
+	(297.31,159.71) --
+	(297.22,159.67) --
+	(297.13,159.62) --
+	(297.09,159.60) --
+	(297.05,159.58) --
+	(297.04,159.58) --
+	(297.01,159.57) --
+	(296.99,159.56) --
+	(296.65,159.45) --
+	(296.47,159.35) --
+	(296.10,159.26) --
+	(295.99,159.24) --
+	(295.93,159.23) --
+	(295.51,159.10) --
+	(295.45,159.08) --
+	(295.25,159.01) --
+	(293.91,158.66) --
+	(293.21,158.46) --
+	(292.62,158.25) --
+	(292.51,158.22) --
+	(292.49,158.21) --
+	(292.42,158.20) --
+	(292.36,158.18) --
+	(292.21,158.15) --
+	(291.88,158.09) --
+	(291.81,158.08) --
+	(291.32,157.93) --
+	(291.20,157.93) --
+	(290.86,157.83) --
+	(290.76,157.78) --
+	(289.76,157.50) --
+	(289.22,157.31) --
+	(288.59,157.10) --
+	(288.54,157.09) --
+	(287.81,156.93) --
+	(287.25,156.69) --
+	(286.59,156.44) --
+	(286.57,156.44) --
+	(286.00,156.29) --
+	(285.13,156.04) --
+	(285.03,156.02) --
+	(284.86,155.95) --
+	(284.62,155.87) --
+	(284.07,155.70) --
+	(283.98,155.67) --
+	(283.89,155.63) --
+	(283.05,155.39) --
+	(282.80,155.29) --
+	(281.45,154.91) --
+	(281.36,154.89) --
+	(281.20,154.85) --
+	(280.72,154.72) --
+	(280.53,154.68) --
+	(280.15,154.56) --
+	(279.69,154.48) --
+	(279.66,154.48) --
+	(279.52,154.44) --
+	(279.30,154.38) --
+	(279.17,154.34) --
+	(278.45,154.06) --
+	(278.04,153.95) --
+	(277.98,153.93) --
+	(277.30,153.70) --
+	(276.77,153.46) --
+	(276.31,153.28) --
+	(276.13,153.22) --
+	(275.59,153.06) --
+	(275.28,152.95) --
+	(274.52,152.77) --
+	(273.63,152.39) --
+	(272.79,152.07) --
+	(272.40,151.94) --
+	(271.68,151.70) --
+	(271.10,151.43) --
+	(271.02,151.41) --
+	(269.87,151.00) --
+	(269.74,150.96) --
+	(269.11,150.78) --
+	(268.38,150.50) --
+	(267.71,150.29) --
+	(267.28,150.15) --
+	(266.44,149.85) --
+	(266.13,149.74) --
+	(266.10,149.73) --
+	(264.97,149.27) --
+	(264.53,149.09) --
+	(264.50,149.08) --
+	(264.29,149.03) --
+	(262.99,148.54) --
+	(262.48,148.27) --
+	(262.19,148.19) --
+	(261.97,148.12) --
+	(260.80,147.75) --
+	(260.14,147.55) --
+	(260.03,147.49) --
+	(258.61,146.90) --
+	(256.32,145.98) --
+	(255.02,145.42) --
+	(254.91,145.38) --
+	(253.36,144.78) --
+	(253.12,144.70) --
+	(252.98,144.64) --
+	(252.52,144.47) --
+	(251.88,144.26) --
+	(251.61,144.16) --
+	(251.21,144.00) --
+	(250.71,143.81) --
+	(250.14,143.57) --
+	(249.91,143.49) --
+	(249.15,143.20) --
+	(248.59,142.98) --
+	(248.00,142.78) --
+	(247.15,142.45) --
+	(247.14,142.44) --
+	(245.90,142.02) --
+	(244.87,141.53) --
+	(243.82,141.15) --
+	(242.87,140.79) --
+	(240.76,139.96) --
+	(239.50,139.44) --
+	(238.44,139.02) --
+	(236.50,138.27) --
+	(233.03,136.65) --
+	(232.60,136.47) --
+	(232.55,136.45) --
+	(232.29,136.34) --
+	(231.54,136.09) --
+	(230.53,135.66) --
+	(229.80,135.35) --
+	(228.22,134.60) --
+	(226.89,134.03) --
+	(226.38,133.85) --
+	(224.51,133.07) --
+	(219.87,130.96) --
+	(219.39,130.73) --
+	(214.88,128.51) --
+	(213.28,127.81) --
+	(213.22,127.78) --
+	(213.02,127.70) --
+	(211.30,126.92) --
+	(205.70,124.51) --
+	(204.08,123.77) --
+	(203.92,123.68) --
+	(203.24,123.35) --
+	(203.15,123.31) --
+	(202.42,123.02) --
+	(201.70,122.67) --
+	(200.09,121.90) --
+	(199.79,121.73) --
+	(195.05,119.42) --
+	(195.04,119.41) --
+	(185.12,114.89) --
+	(177.68,111.26) --
+	(175.08,110.08) --
+	(164.50,104.62) --
+	(163.56,104.15) --
+	(160.15,102.47) --
+	(160.01,102.40) --
+	(124.94, 84.29) --
+	(116.56, 79.63) --
+	(113.94, 78.09) --
+	(110.01, 75.93) --
+	(104.50, 73.31) --
+	( 97.84, 69.48) --
+	( 94.41, 67.75) --
+	( 88.50, 64.75) --
+	( 79.64, 59.82) --
+	( 65.62, 51.87) --
+	( 65.48, 51.79) --
+	( 61.01, 49.34) --
+	( 52.97, 45.08) --
 	cycle;
@@
 
-\path[fill=fillColor,fill opacity=0.50] ( 57.05,165.69) --
-	( 62.08,166.26) --
-	( 67.11,166.92) --
-	( 72.14,167.65) --
-	( 77.17,168.34) --
-	( 82.20,169.03) --
-	( 87.23,169.66) --
-	( 92.27,170.38) --
-	( 97.30,171.07) --
-	(102.33,171.75) --
-	(107.36,172.44) --
-	(112.39,173.12) --
-	(117.42,173.84) --
-	(122.45,174.45) --
-	(127.49,175.12) --
-	(132.52,175.81) --
-	(137.55,176.59) --
-	(142.58,177.35) --
-	(147.61,178.25) --
-	(152.64,179.27) --
-	(157.67,180.18) --
-	(162.71,181.11) --
-	(167.74,181.96) --
-	(172.77,182.76) --
-	(177.80,183.71) --
-	(182.83,184.54) --
-	(187.86,185.47) --
-	(192.89,186.43) --
-	(197.93,187.51) --
-	(202.96,188.46) --
-	(207.99,189.58) --
-	(213.02,190.58) --
-	(218.05,191.75) --
-	(223.08,192.84) --
-	(228.12,194.00) --
-	(233.15,195.12) --
-	(238.18,196.45) --
-	(243.21,197.65) --
-	(248.24,199.02) --
-	(253.27,200.34) --
-	(258.30,201.75) --
-	(263.34,203.21) --
-	(268.37,204.61) --
-	(273.40,206.24) --
-	(278.43,207.82) --
-	(283.46,209.30) --
-	(288.49,210.93) --
-	(293.52,212.69) --
-	(298.56,214.53) --
-	(303.59,216.36) --
-	(308.62,218.21) --
-	(313.65,220.05) --
-	(318.68,222.00) --
-	(323.71,224.00) --
-	(328.74,225.95) --
-	(333.78,227.98) --
-	(338.81,230.07) --
-	(343.84,232.25) --
-	(348.87,234.41) --
-	(353.90,236.60) --
-	(358.93,238.76) --
-	(363.96,240.91) --
-	(369.00,243.13) --
-	(374.03,245.40) --
-	(379.06,247.74) --
-	(384.09,250.09) --
-	(389.12,252.61) --
-	(394.15,255.21) --
-	(399.18,257.56) --
-	(404.22,259.93) --
-	(404.22,192.89) --
-	(399.18,192.12) --
-	(394.15,191.18) --
-	(389.12,190.22) --
-	(384.09,189.28) --
-	(379.06,188.36) --
-	(374.03,187.32) --
-	(369.00,186.30) --
-	(363.96,185.20) --
-	(358.93,184.18) --
-	(353.90,182.99) --
-	(348.87,181.90) --
-	(343.84,180.64) --
-	(338.81,179.59) --
-	(333.78,178.30) --
-	(328.74,176.91) --
-	(323.71,175.49) --
-	(318.68,174.05) --
-	(313.65,172.59) --
-	(308.62,171.06) --
-	(303.59,169.50) --
-	(298.56,167.92) --
-	(293.52,166.28) --
-	(288.49,164.66) --
-	(283.46,162.97) --
-	(278.43,161.38) --
-	(273.40,159.49) --
-	(268.37,157.55) --
-	(263.34,155.74) --
-	(258.30,153.81) --
-	(253.27,151.84) --
-	(248.24,149.82) --
-	(243.21,147.69) --
-	(238.18,145.73) --
-	(233.15,143.60) --
-	(228.12,141.48) --
-	(223.08,139.15) --
-	(218.05,136.75) --
-	(213.02,134.58) --
-	(207.99,132.15) --
-	(202.96,129.81) --
-	(197.93,127.34) --
-	(192.89,124.90) --
-	(187.86,122.54) --
-	(182.83,119.97) --
-	(177.80,117.68) --
-	(172.77,115.15) --
-	(167.74,112.73) --
-	(162.71,110.22) --
-	(157.67,107.87) --
-	(152.64,105.34) --
-	(147.61,102.80) --
-	(142.58,100.16) --
-	(137.55, 97.55) --
-	(132.52, 94.94) --
-	(127.49, 92.32) --
-	(122.45, 89.72) --
-	(117.42, 87.08) --
-	(112.39, 84.45) --
-	(107.36, 81.80) --
-	(102.33, 79.16) --
-	( 97.30, 76.57) --
-	( 92.27, 74.01) --
-	( 87.23, 71.42) --
-	( 82.20, 68.63) --
-	( 77.17, 65.97) --
-	( 72.14, 63.37) --
-	( 67.11, 60.74) --
-	( 62.08, 58.05) --
-	( 57.05, 55.38) --
+\path[fill=fillColor,fill opacity=0.50] ( 52.97,157.52) --
+	( 61.01,158.71) --
+	( 65.48,159.33) --
+	( 65.62,159.35) --
+	( 79.64,161.53) --
+	( 88.50,163.05) --
+	( 94.41,164.05) --
+	( 97.84,164.63) --
+	(104.50,165.72) --
+	(110.01,166.51) --
+	(113.94,167.24) --
+	(116.56,167.79) --
+	(124.94,169.05) --
+	(160.01,175.04) --
+	(160.15,175.05) --
+	(163.56,175.67) --
+	(164.50,175.82) --
+	(175.08,178.09) --
+	(177.68,178.61) --
+	(185.12,180.03) --
+	(195.04,182.20) --
+	(195.05,182.20) --
+	(199.79,183.10) --
+	(200.09,183.15) --
+	(201.70,183.53) --
+	(202.42,183.68) --
+	(203.15,183.82) --
+	(203.24,183.84) --
+	(203.92,183.98) --
+	(204.08,184.00) --
+	(205.70,184.39) --
+	(211.30,185.68) --
+	(213.02,186.07) --
+	(213.22,186.12) --
+	(213.28,186.14) --
+	(214.88,186.52) --
+	(219.39,187.64) --
+	(219.87,187.75) --
+	(224.51,188.92) --
+	(226.38,189.39) --
+	(226.89,189.48) --
+	(228.22,189.88) --
+	(229.80,190.26) --
+	(230.53,190.49) --
+	(231.54,190.73) --
+	(232.29,190.94) --
+	(232.55,191.02) --
+	(232.60,191.04) --
+	(233.03,191.16) --
+	(236.50,192.03) --
+	(238.44,192.60) --
+	(239.50,192.87) --
+	(240.76,193.23) --
+	(242.87,193.80) --
+	(243.82,193.97) --
+	(244.87,194.22) --
+	(245.90,194.45) --
+	(247.14,194.78) --
+	(247.15,194.78) --
+	(248.00,195.06) --
+	(248.59,195.19) --
+	(249.15,195.38) --
+	(249.91,195.68) --
+	(250.14,195.72) --
+	(250.71,195.90) --
+	(251.21,196.07) --
+	(251.61,196.16) --
+	(251.88,196.25) --
+	(252.52,196.37) --
+	(252.98,196.48) --
+	(253.12,196.53) --
+	(253.36,196.58) --
+	(254.91,197.00) --
+	(255.02,197.02) --
+	(256.32,197.42) --
+	(258.61,198.09) --
+	(260.03,198.53) --
+	(260.14,198.54) --
+	(260.80,198.76) --
+	(261.97,199.13) --
+	(262.19,199.18) --
+	(262.48,199.25) --
+	(262.99,199.41) --
+	(264.29,199.74) --
+	(264.50,199.84) --
+	(264.53,199.86) --
+	(264.97,199.98) --
+	(266.10,200.32) --
+	(266.13,200.33) --
+	(266.44,200.43) --
+	(267.28,200.69) --
+	(267.71,200.79) --
+	(268.38,200.99) --
+	(269.11,201.16) --
+	(269.74,201.38) --
+	(269.87,201.40) --
+	(271.02,201.80) --
+	(271.10,201.83) --
+	(271.68,202.00) --
+	(272.40,202.28) --
+	(272.79,202.41) --
+	(273.63,202.69) --
+	(274.52,202.98) --
+	(275.28,203.20) --
+	(275.59,203.27) --
+	(276.13,203.43) --
+	(276.31,203.47) --
+	(276.77,203.63) --
+	(277.30,203.79) --
+	(277.98,204.00) --
+	(278.04,204.00) --
+	(278.45,204.12) --
+	(279.17,204.40) --
+	(279.30,204.44) --
+	(279.52,204.50) --
+	(279.66,204.55) --
+	(279.69,204.56) --
+	(280.15,204.72) --
+	(280.53,204.89) --
+	(280.72,204.98) --
+	(281.20,205.18) --
+	(281.36,205.23) --
+	(281.45,205.24) --
+	(282.80,205.79) --
+	(283.05,205.89) --
+	(283.89,206.20) --
+	(283.98,206.21) --
+	(284.07,206.25) --
+	(284.62,206.45) --
+	(284.86,206.51) --
+	(285.03,206.59) --
+	(285.13,206.64) --
+	(286.00,206.89) --
+	(286.57,207.08) --
+	(286.59,207.10) --
+	(287.25,207.30) --
+	(287.81,207.46) --
+	(288.54,207.69) --
+	(288.59,207.71) --
+	(289.22,207.96) --
+	(289.76,208.14) --
+	(290.76,208.49) --
+	(290.86,208.52) --
+	(291.20,208.64) --
+	(291.32,208.69) --
+	(291.81,208.87) --
+	(291.88,208.91) --
+	(292.21,209.05) --
+	(292.36,209.11) --
+	(292.42,209.13) --
+	(292.49,209.15) --
+	(292.51,209.16) --
+	(292.62,209.22) --
+	(293.21,209.38) --
+	(293.91,209.64) --
+	(295.25,210.12) --
+	(295.45,210.17) --
+	(295.51,210.19) --
+	(295.93,210.34) --
+	(295.99,210.37) --
+	(296.10,210.42) --
+	(296.47,210.53) --
+	(296.65,210.60) --
+	(296.99,210.70) --
+	(297.01,210.71) --
+	(297.04,210.72) --
+	(297.05,210.72) --
+	(297.09,210.73) --
+	(297.13,210.74) --
+	(297.22,210.77) --
+	(297.31,210.80) --
+	(297.31,210.80) --
+	(297.71,210.96) --
+	(297.96,211.07) --
+	(298.34,211.23) --
+	(298.57,211.33) --
+	(299.04,211.48) --
+	(300.58,212.07) --
+	(300.69,212.11) --
+	(301.32,212.32) --
+	(302.10,212.65) --
+	(302.23,212.71) --
+	(302.50,212.86) --
+	(302.82,212.96) --
+	(302.98,213.02) --
+	(303.49,213.24) --
+	(303.87,213.38) --
+	(304.04,213.46) --
+	(304.05,213.46) --
+	(304.17,213.52) --
+	(304.21,213.54) --
+	(304.88,213.80) --
+	(305.44,214.06) --
+	(305.52,214.08) --
+	(305.61,214.12) --
+	(305.86,214.20) --
+	(306.19,214.32) --
+	(306.32,214.36) --
+	(307.91,214.96) --
+	(307.96,214.99) --
+	(308.47,215.19) --
+	(308.57,215.23) --
+	(309.22,215.49) --
+	(309.44,215.58) --
+	(309.51,215.60) --
+	(309.67,215.66) --
+	(310.00,215.78) --
+	(310.25,215.88) --
+	(310.76,216.10) --
+	(310.92,216.15) --
+	(311.04,216.19) --
+	(311.16,216.24) --
+	(311.41,216.35) --
+	(311.41,216.36) --
+	(311.44,216.37) --
+	(311.54,216.40) --
+	(311.68,216.46) --
+	(311.68,216.46) --
+	(311.88,216.53) --
+	(312.22,216.64) --
+	(312.92,216.90) --
+	(313.12,216.98) --
+	(313.27,217.05) --
+	(313.53,217.12) --
+	(313.83,217.24) --
+	(314.24,217.40) --
+	(314.31,217.42) --
+	(314.45,217.49) --
+	(314.63,217.59) --
+	(315.00,217.69) --
+	(315.21,217.81) --
+	(315.23,217.82) --
+	(315.37,217.86) --
+	(315.48,217.91) --
+	(315.51,217.92) --
+	(315.62,217.95) --
+	(315.70,217.98) --
+	(315.79,218.02) --
+	(316.13,218.15) --
+	(316.22,218.18) --
+	(316.38,218.25) --
+	(316.61,218.33) --
+	(316.93,218.48) --
+	(317.07,218.54) --
+	(317.20,218.60) --
+	(317.36,218.68) --
+	(317.75,218.86) --
+	(317.76,218.87) --
+	(317.79,218.88) --
+	(317.86,218.90) --
+	(317.89,218.91) --
+	(317.98,218.95) --
+	(318.43,219.10) --
+	(318.60,219.15) --
+	(318.85,219.23) --
+	(319.11,219.34) --
+	(319.21,219.36) --
+	(319.52,219.46) --
+	(319.81,219.61) --
+	(320.44,219.87) --
+	(321.85,220.46) --
+	(321.91,220.48) --
+	(322.04,220.54) --
+	(322.30,220.65) --
+	(322.60,220.80) --
+	(322.75,220.85) --
+	(323.02,220.98) --
+	(323.10,221.01) --
+	(323.28,221.10) --
+	(324.05,221.40) --
+	(324.42,221.57) --
+	(324.61,221.63) --
+	(324.72,221.66) --
+	(325.08,221.77) --
+	(325.99,222.17) --
+	(326.58,222.47) --
+	(326.72,222.50) --
+	(327.61,222.87) --
+	(327.91,223.02) --
+	(328.67,223.32) --
+	(328.94,223.47) --
+	(329.07,223.53) --
+	(329.52,223.68) --
+	(331.17,224.41) --
+	(332.00,224.77) --
+	(332.27,224.86) --
+	(333.07,225.24) --
+	(333.19,225.28) --
+	(333.76,225.52) --
+	(335.51,226.18) --
+	(336.07,226.42) --
+	(336.75,226.75) --
+	(336.88,226.82) --
+	(337.54,227.09) --
+	(337.92,227.27) --
+	(338.29,227.44) --
+	(338.32,227.46) --
+	(338.37,227.49) --
+	(338.79,227.66) --
+	(338.87,227.69) --
+	(339.41,227.95) --
+	(339.54,228.00) --
+	(340.26,228.35) --
+	(340.28,228.35) --
+	(340.36,228.38) --
+	(340.58,228.46) --
+	(340.90,228.61) --
+	(341.07,228.67) --
+	(341.38,228.80) --
+	(341.48,228.85) --
+	(341.53,228.88) --
+	(341.57,228.90) --
+	(342.00,229.08) --
+	(342.06,229.11) --
+	(342.60,229.32) --
+	(342.92,229.41) --
+	(344.39,230.06) --
+	(344.81,230.26) --
+	(345.03,230.35) --
+	(345.51,230.53) --
+	(345.56,230.55) --
+	(346.27,230.84) --
+	(348.09,231.63) --
+	(348.19,231.66) --
+	(348.32,231.71) --
+	(348.52,231.79) --
+	(348.65,231.84) --
+	(350.04,232.48) --
+	(350.29,232.58) --
+	(350.39,232.61) --
+	(351.49,233.03) --
+	(354.19,234.20) --
+	(354.41,234.28) --
+	(354.96,234.53) --
+	(354.99,234.54) --
+	(355.28,234.70) --
+	(355.84,234.97) --
+	(356.71,235.37) --
+	(356.75,235.39) --
+	(357.50,235.70) --
+	(357.53,235.71) --
+	(358.04,235.90) --
+	(358.62,236.15) --
+	(359.31,236.46) --
+	(359.62,236.61) --
+	(359.75,236.69) --
+	(359.85,236.75) --
+	(360.61,237.12) --
+	(360.64,237.13) --
+	(360.71,237.18) --
+	(361.91,237.72) --
+	(362.60,238.04) --
+	(364.24,238.88) --
+	(364.46,239.00) --
+	(365.70,239.62) --
+	(366.29,239.93) --
+	(370.53,241.73) --
+	(371.02,241.94) --
+	(372.06,242.43) --
+	(372.07,242.43) --
+	(372.38,242.60) --
+	(372.60,242.71) --
+	(372.90,242.85) --
+	(373.16,243.00) --
+	(373.53,243.19) --
+	(373.80,243.33) --
+	(374.46,243.64) --
+	(374.81,243.78) --
+	(375.77,244.22) --
+	(376.36,244.50) --
+	(376.51,244.59) --
+	(376.93,244.79) --
+	(378.03,245.25) --
+	(379.36,245.80) --
+	(379.36,245.80) --
+	(380.09,246.17) --
+	(380.12,246.18) --
+	(381.03,246.59) --
+	(381.47,246.80) --
+	(381.75,246.94) --
+	(382.36,247.23) --
+	(382.44,247.28) --
+	(382.57,247.34) --
+	(383.02,247.55) --
+	(385.04,248.44) --
+	(385.16,248.51) --
+	(388.87,250.32) --
+	(393.56,252.71) --
+	(395.71,253.79) --
+	(403.26,257.56) --
+	(404.02,257.95) --
+	(404.02,188.48) --
+	(403.26,188.33) --
+	(395.71,186.92) --
+	(393.56,186.56) --
+	(388.87,185.69) --
+	(385.16,184.82) --
+	(385.04,184.80) --
+	(383.02,184.39) --
+	(382.57,184.31) --
+	(382.44,184.30) --
+	(382.36,184.29) --
+	(381.75,184.16) --
+	(381.47,184.11) --
+	(381.03,184.04) --
+	(380.12,183.81) --
+	(380.09,183.80) --
+	(379.36,183.64) --
+	(379.36,183.64) --
+	(378.03,183.40) --
+	(376.93,183.15) --
+	(376.51,183.06) --
+	(376.36,183.05) --
+	(375.77,182.97) --
+	(374.81,182.77) --
+	(374.46,182.70) --
+	(373.80,182.52) --
+	(373.53,182.49) --
+	(373.16,182.43) --
+	(372.90,182.36) --
+	(372.60,182.28) --
+	(372.38,182.23) --
+	(372.07,182.19) --
+	(372.06,182.19) --
+	(371.02,182.00) --
+	(370.53,181.89) --
+	(366.29,181.14) --
+	(365.70,181.03) --
+	(364.46,180.67) --
+	(364.24,180.65) --
+	(362.60,180.37) --
+	(361.91,180.21) --
+	(360.71,179.92) --
+	(360.64,179.91) --
+	(360.61,179.91) --
+	(359.85,179.80) --
+	(359.75,179.78) --
+	(359.62,179.75) --
+	(359.31,179.68) --
+	(358.62,179.58) --
+	(358.04,179.52) --
+	(357.53,179.41) --
+	(357.50,179.40) --
+	(356.75,179.23) --
+	(356.71,179.22) --
+	(355.84,179.05) --
+	(355.28,178.90) --
+	(354.99,178.79) --
+	(354.96,178.78) --
+	(354.41,178.64) --
+	(354.19,178.60) --
+	(351.49,177.92) --
+	(350.39,177.61) --
+	(350.29,177.59) --
+	(350.04,177.51) --
+	(348.65,177.21) --
+	(348.52,177.18) --
+	(348.32,177.15) --
+	(348.19,177.12) --
+	(348.09,177.09) --
+	(346.27,176.71) --
+	(345.56,176.53) --
+	(345.51,176.51) --
+	(345.03,176.39) --
+	(344.81,176.34) --
+	(344.39,176.25) --
+	(342.92,175.94) --
+	(342.60,175.88) --
+	(342.06,175.75) --
+	(342.00,175.73) --
+	(341.57,175.65) --
+	(341.53,175.64) --
+	(341.48,175.64) --
+	(341.38,175.62) --
+	(341.07,175.54) --
+	(340.90,175.51) --
+	(340.58,175.45) --
+	(340.36,175.41) --
+	(340.28,175.40) --
+	(340.26,175.39) --
+	(339.54,175.25) --
+	(339.41,175.22) --
+	(338.87,175.11) --
+	(338.79,175.10) --
+	(338.37,175.01) --
+	(338.32,174.99) --
+	(338.29,174.98) --
+	(337.92,174.87) --
+	(337.54,174.80) --
+	(336.88,174.67) --
+	(336.75,174.64) --
+	(336.07,174.44) --
+	(335.51,174.32) --
+	(333.76,173.87) --
+	(333.19,173.78) --
+	(333.07,173.75) --
+	(332.27,173.58) --
+	(332.00,173.51) --
+	(331.17,173.30) --
+	(329.52,172.87) --
+	(329.07,172.77) --
+	(328.94,172.73) --
+	(328.67,172.67) --
+	(327.91,172.46) --
+	(327.61,172.39) --
+	(326.72,172.17) --
+	(326.58,172.14) --
+	(325.99,172.00) --
+	(325.08,171.78) --
+	(324.72,171.70) --
+	(324.61,171.67) --
+	(324.42,171.61) --
+	(324.05,171.49) --
+	(323.28,171.35) --
+	(323.10,171.31) --
+	(323.02,171.29) --
+	(322.75,171.18) --
+	(322.60,171.15) --
+	(322.30,171.10) --
+	(322.04,171.03) --
+	(321.91,171.01) --
+	(321.85,171.00) --
+	(320.44,170.69) --
+	(319.81,170.53) --
+	(319.52,170.45) --
+	(319.21,170.37) --
+	(319.11,170.34) --
+	(318.85,170.26) --
+	(318.60,170.22) --
+	(318.43,170.18) --
+	(317.98,170.05) --
+	(317.89,170.02) --
+	(317.86,170.01) --
+	(317.79,169.99) --
+	(317.76,169.99) --
+	(317.75,169.99) --
+	(317.36,169.90) --
+	(317.20,169.85) --
+	(317.07,169.82) --
+	(316.93,169.79) --
+	(316.61,169.68) --
+	(316.38,169.60) --
+	(316.22,169.57) --
+	(316.13,169.55) --
+	(315.79,169.46) --
+	(315.70,169.44) --
+	(315.62,169.41) --
+	(315.51,169.37) --
+	(315.48,169.36) --
+	(315.37,169.32) --
+	(315.23,169.28) --
+	(315.21,169.27) --
+	(315.00,169.20) --
+	(314.63,169.05) --
+	(314.45,168.98) --
+	(314.31,168.94) --
+	(314.24,168.90) --
+	(313.83,168.77) --
+	(313.53,168.69) --
+	(313.27,168.63) --
+	(313.12,168.61) --
+	(312.92,168.58) --
+	(312.22,168.40) --
+	(311.88,168.29) --
+	(311.68,168.25) --
+	(311.68,168.25) --
+	(311.54,168.22) --
+	(311.44,168.18) --
+	(311.41,168.17) --
+	(311.41,168.17) --
+	(311.16,168.09) --
+	(311.04,168.07) --
+	(310.92,168.05) --
+	(310.76,168.02) --
+	(310.25,167.88) --
+	(310.00,167.83) --
+	(309.67,167.75) --
+	(309.51,167.72) --
+	(309.44,167.71) --
+	(309.22,167.66) --
+	(308.57,167.46) --
+	(308.47,167.44) --
+	(307.96,167.34) --
+	(307.91,167.34) --
+	(306.32,166.93) --
+	(306.19,166.90) --
+	(305.86,166.81) --
+	(305.61,166.74) --
+	(305.52,166.71) --
+	(305.44,166.69) --
+	(304.88,166.51) --
+	(304.21,166.30) --
+	(304.17,166.30) --
+	(304.05,166.26) --
+	(304.04,166.26) --
+	(303.87,166.21) --
+	(303.49,166.10) --
+	(302.98,165.93) --
+	(302.82,165.89) --
+	(302.50,165.78) --
+	(302.23,165.67) --
+	(302.10,165.62) --
+	(301.32,165.40) --
+	(300.69,165.24) --
+	(300.58,165.20) --
+	(299.04,164.69) --
+	(298.57,164.54) --
+	(298.34,164.48) --
+	(297.96,164.38) --
+	(297.71,164.30) --
+	(297.31,164.13) --
+	(297.31,164.13) --
+	(297.22,164.10) --
+	(297.13,164.08) --
+	(297.09,164.07) --
+	(297.05,164.05) --
+	(297.04,164.05) --
+	(297.01,164.04) --
+	(296.99,164.03) --
+	(296.65,163.91) --
+	(296.47,163.85) --
+	(296.10,163.73) --
+	(295.99,163.69) --
+	(295.93,163.67) --
+	(295.51,163.54) --
+	(295.45,163.52) --
+	(295.25,163.45) --
+	(293.91,163.09) --
+	(293.21,162.89) --
+	(292.62,162.68) --
+	(292.51,162.66) --
+	(292.49,162.65) --
+	(292.42,162.63) --
+	(292.36,162.61) --
+	(292.21,162.56) --
+	(291.88,162.48) --
+	(291.81,162.46) --
+	(291.32,162.32) --
+	(291.20,162.27) --
+	(290.86,162.16) --
+	(290.76,162.12) --
+	(289.76,161.73) --
+	(289.22,161.57) --
+	(288.59,161.34) --
+	(288.54,161.32) --
+	(287.81,161.08) --
+	(287.25,160.92) --
+	(286.59,160.70) --
+	(286.57,160.70) --
+	(286.00,160.52) --
+	(285.13,160.28) --
+	(285.03,160.25) --
+	(284.86,160.19) --
+	(284.62,160.11) --
+	(284.07,159.94) --
+	(283.98,159.91) --
+	(283.89,159.89) --
+	(283.05,159.64) --
+	(282.80,159.57) --
+	(281.45,159.12) --
+	(281.36,159.08) --
+	(281.20,159.03) --
+	(280.72,158.84) --
+	(280.53,158.80) --
+	(280.15,158.71) --
+	(279.69,158.55) --
+	(279.66,158.54) --
+	(279.52,158.48) --
+	(279.30,158.40) --
+	(279.17,158.36) --
+	(278.45,158.13) --
+	(278.04,157.99) --
+	(277.98,157.96) --
+	(277.30,157.71) --
+	(276.77,157.53) --
+	(276.31,157.40) --
+	(276.13,157.34) --
+	(275.59,157.16) --
+	(275.28,157.07) --
+	(274.52,156.81) --
+	(273.63,156.52) --
+	(272.79,156.25) --
+	(272.40,156.11) --
+	(271.68,155.88) --
+	(271.10,155.68) --
+	(271.02,155.65) --
+	(269.87,155.20) --
+	(269.74,155.17) --
+	(269.11,154.96) --
+	(268.38,154.71) --
+	(267.71,154.49) --
+	(267.28,154.34) --
+	(266.44,154.07) --
+	(266.13,153.97) --
+	(266.10,153.96) --
+	(264.97,153.64) --
+	(264.53,153.52) --
+	(264.50,153.51) --
+	(264.29,153.45) --
+	(262.99,153.00) --
+	(262.48,152.85) --
+	(262.19,152.74) --
+	(261.97,152.68) --
+	(260.80,152.32) --
+	(260.14,152.06) --
+	(260.03,152.03) --
+	(258.61,151.54) --
+	(256.32,150.72) --
+	(255.02,150.28) --
+	(254.91,150.24) --
+	(253.36,149.63) --
+	(253.12,149.55) --
+	(252.98,149.50) --
+	(252.52,149.32) --
+	(251.88,149.06) --
+	(251.61,148.94) --
+	(251.21,148.84) --
+	(250.71,148.65) --
+	(250.14,148.41) --
+	(249.91,148.31) --
+	(249.15,148.07) --
+	(248.59,147.93) --
+	(248.00,147.70) --
+	(247.15,147.40) --
+	(247.14,147.39) --
+	(245.90,146.93) --
+	(244.87,146.49) --
+	(243.82,146.09) --
+	(242.87,145.70) --
+	(240.76,144.79) --
+	(239.50,144.28) --
+	(238.44,143.86) --
+	(236.50,143.12) --
+	(233.03,141.67) --
+	(232.60,141.48) --
+	(232.55,141.46) --
+	(232.29,141.37) --
+	(231.54,141.09) --
+	(230.53,140.70) --
+	(229.80,140.39) --
+	(228.22,139.75) --
+	(226.89,139.17) --
+	(226.38,138.96) --
+	(224.51,138.27) --
+	(219.87,136.46) --
+	(219.39,136.25) --
+	(214.88,134.34) --
+	(213.28,133.63) --
+	(213.22,133.61) --
+	(213.02,133.50) --
+	(211.30,132.78) --
+	(205.70,130.38) --
+	(204.08,129.58) --
+	(203.92,129.52) --
+	(203.24,129.24) --
+	(203.15,129.19) --
+	(202.42,128.83) --
+	(201.70,128.52) --
+	(200.09,127.78) --
+	(199.79,127.65) --
+	(195.05,125.74) --
+	(195.04,125.74) --
+	(185.12,121.11) --
+	(177.68,117.77) --
+	(175.08,116.58) --
+	(164.50,111.49) --
+	(163.56,111.05) --
+	(160.15,109.37) --
+	(160.01,109.30) --
+	(124.94, 91.80) --
+	(116.56, 87.52) --
+	(113.94, 86.20) --
+	(110.01, 84.11) --
+	(104.50, 81.25) --
+	( 97.84, 77.97) --
+	( 94.41, 76.21) --
+	( 88.50, 73.15) --
+	( 79.64, 68.59) --
+	( 65.62, 61.16) --
+	( 65.48, 61.09) --
+	( 61.01, 58.86) --
+	( 52.97, 54.68) --
 	cycle;
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 52.97, 34.03) -- ( 52.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 61.01, 34.03) -- ( 61.01, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 65.48, 34.03) -- ( 65.48, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 65.62, 34.03) -- ( 65.62, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 79.64, 34.03) -- ( 79.64, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 88.50, 34.03) -- ( 88.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 94.41, 34.03) -- ( 94.41, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 97.84, 34.03) -- ( 97.84, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (104.50, 34.03) -- (104.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (110.01, 34.03) -- (110.01, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (113.94, 34.03) -- (113.94, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (116.56, 34.03) -- (116.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (124.94, 34.03) -- (124.94, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (160.01, 34.03) -- (160.01, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (160.15, 34.03) -- (160.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (163.56, 34.03) -- (163.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (164.50, 34.03) -- (164.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (175.08, 34.03) -- (175.08, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (177.68, 34.03) -- (177.68, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (185.12, 34.03) -- (185.12, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (195.04, 34.03) -- (195.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (195.05, 34.03) -- (195.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (199.79, 34.03) -- (199.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (200.09, 34.03) -- (200.09, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (201.70, 34.03) -- (201.70, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (202.42, 34.03) -- (202.42, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (203.15, 34.03) -- (203.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (203.24, 34.03) -- (203.24, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (203.92, 34.03) -- (203.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (204.08, 34.03) -- (204.08, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (205.70, 34.03) -- (205.70, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (211.30, 34.03) -- (211.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (213.02, 34.03) -- (213.02, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (213.22, 34.03) -- (213.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (213.28, 34.03) -- (213.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (214.88, 34.03) -- (214.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (219.39, 34.03) -- (219.39, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (219.87, 34.03) -- (219.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (224.51, 34.03) -- (224.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (226.38, 34.03) -- (226.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (226.89, 34.03) -- (226.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (228.22, 34.03) -- (228.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (229.80, 34.03) -- (229.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (230.53, 34.03) -- (230.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (231.54, 34.03) -- (231.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.29, 34.03) -- (232.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.55, 34.03) -- (232.55, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.60, 34.03) -- (232.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (233.03, 34.03) -- (233.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (236.50, 34.03) -- (236.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (238.44, 34.03) -- (238.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (239.49, 34.03) -- (239.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (240.76, 34.03) -- (240.76, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (242.87, 34.03) -- (242.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (243.82, 34.03) -- (243.82, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (244.87, 34.03) -- (244.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (245.90, 34.03) -- (245.90, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (247.14, 34.03) -- (247.14, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (247.15, 34.03) -- (247.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (248.00, 34.03) -- (248.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (248.59, 34.03) -- (248.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (249.15, 34.03) -- (249.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (249.91, 34.03) -- (249.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (250.14, 34.03) -- (250.14, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (250.71, 34.03) -- (250.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.21, 34.03) -- (251.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.61, 34.03) -- (251.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.88, 34.03) -- (251.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (252.52, 34.03) -- (252.52, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (252.98, 34.03) -- (252.98, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (253.12, 34.03) -- (253.12, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (253.36, 34.03) -- (253.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (254.91, 34.03) -- (254.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (255.02, 34.03) -- (255.02, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (256.32, 34.03) -- (256.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (258.61, 34.03) -- (258.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (260.03, 34.03) -- (260.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (260.14, 34.03) -- (260.14, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (260.80, 34.03) -- (260.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (261.97, 34.03) -- (261.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (262.19, 34.03) -- (262.19, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (262.47, 34.03) -- (262.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (262.99, 34.03) -- (262.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (264.29, 34.03) -- (264.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (264.50, 34.03) -- (264.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (264.53, 34.03) -- (264.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (264.97, 34.03) -- (264.97, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (266.10, 34.03) -- (266.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (266.13, 34.03) -- (266.13, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (266.44, 34.03) -- (266.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.28, 34.03) -- (267.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.71, 34.03) -- (267.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (268.38, 34.03) -- (268.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (269.11, 34.03) -- (269.11, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (269.74, 34.03) -- (269.74, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (269.87, 34.03) -- (269.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.02, 34.03) -- (271.02, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.10, 34.03) -- (271.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.68, 34.03) -- (271.68, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (272.40, 34.03) -- (272.40, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (272.79, 34.03) -- (272.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (273.63, 34.03) -- (273.63, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (274.52, 34.03) -- (274.52, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (275.28, 34.03) -- (275.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (275.59, 34.03) -- (275.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (276.13, 34.03) -- (276.13, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (276.31, 34.03) -- (276.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (276.77, 34.03) -- (276.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (277.30, 34.03) -- (277.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (277.98, 34.03) -- (277.98, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (278.04, 34.03) -- (278.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (278.45, 34.03) -- (278.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (279.17, 34.03) -- (279.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (279.30, 34.03) -- (279.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (279.52, 34.03) -- (279.52, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (279.66, 34.03) -- (279.66, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (279.69, 34.03) -- (279.69, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (280.15, 34.03) -- (280.15, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (280.53, 34.03) -- (280.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (280.72, 34.03) -- (280.72, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (281.20, 34.03) -- (281.20, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (281.36, 34.03) -- (281.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (281.45, 34.03) -- (281.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (282.79, 34.03) -- (282.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.05, 34.03) -- (283.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.89, 34.03) -- (283.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.98, 34.03) -- (283.98, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.07, 34.03) -- (284.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.63, 34.03) -- (284.63, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.86, 34.03) -- (284.86, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.03, 34.03) -- (285.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.13, 34.03) -- (285.13, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.00, 34.03) -- (286.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.57, 34.03) -- (286.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.59, 34.03) -- (286.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (287.25, 34.03) -- (287.25, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (287.81, 34.03) -- (287.81, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (288.54, 34.03) -- (288.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (288.59, 34.03) -- (288.59, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (289.22, 34.03) -- (289.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (289.76, 34.03) -- (289.76, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.76, 34.03) -- (290.76, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.86, 34.03) -- (290.86, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (291.20, 34.03) -- (291.20, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (291.32, 34.03) -- (291.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (291.81, 34.03) -- (291.81, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (291.88, 34.03) -- (291.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.21, 34.03) -- (292.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.36, 34.03) -- (292.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.42, 34.03) -- (292.42, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.49, 34.03) -- (292.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.51, 34.03) -- (292.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.62, 34.03) -- (292.62, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (293.21, 34.03) -- (293.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (293.91, 34.03) -- (293.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (295.25, 34.03) -- (295.25, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (295.45, 34.03) -- (295.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (295.51, 34.03) -- (295.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (295.93, 34.03) -- (295.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (295.99, 34.03) -- (295.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (296.10, 34.03) -- (296.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (296.47, 34.03) -- (296.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (296.65, 34.03) -- (296.65, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (296.99, 34.03) -- (296.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.01, 34.03) -- (297.01, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.04, 34.03) -- (297.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.05, 34.03) -- (297.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.08, 34.03) -- (297.08, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.12, 34.03) -- (297.12, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.22, 34.03) -- (297.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.31, 34.03) -- (297.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.31, 34.03) -- (297.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.71, 34.03) -- (297.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.96, 34.03) -- (297.96, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.34, 34.03) -- (298.34, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.57, 34.03) -- (298.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.04, 34.03) -- (299.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (300.58, 34.03) -- (300.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (300.69, 34.03) -- (300.69, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (301.32, 34.03) -- (301.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.10, 34.03) -- (302.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.23, 34.03) -- (302.23, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.50, 34.03) -- (302.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.82, 34.03) -- (302.82, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.98, 34.03) -- (302.98, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (303.49, 34.03) -- (303.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (303.87, 34.03) -- (303.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.04, 34.03) -- (304.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.05, 34.03) -- (304.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.17, 34.03) -- (304.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.21, 34.03) -- (304.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.88, 34.03) -- (304.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (305.44, 34.03) -- (305.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (305.52, 34.03) -- (305.52, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (305.61, 34.03) -- (305.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (305.86, 34.03) -- (305.86, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (306.19, 34.03) -- (306.19, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (306.32, 34.03) -- (306.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.91, 34.03) -- (307.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (307.96, 34.03) -- (307.96, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (308.47, 34.03) -- (308.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (308.57, 34.03) -- (308.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.22, 34.03) -- (309.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.44, 34.03) -- (309.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.51, 34.03) -- (309.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.67, 34.03) -- (309.67, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.00, 34.03) -- (310.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.25, 34.03) -- (310.25, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.76, 34.03) -- (310.76, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.92, 34.03) -- (310.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.04, 34.03) -- (311.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.16, 34.03) -- (311.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.41, 34.03) -- (311.41, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.41, 34.03) -- (311.41, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.44, 34.03) -- (311.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.54, 34.03) -- (311.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.68, 34.03) -- (311.68, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.68, 34.03) -- (311.68, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (311.88, 34.03) -- (311.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (312.22, 34.03) -- (312.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (312.92, 34.03) -- (312.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (313.12, 34.03) -- (313.12, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (313.27, 34.03) -- (313.27, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (313.53, 34.03) -- (313.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (313.83, 34.03) -- (313.83, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.24, 34.03) -- (314.24, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.31, 34.03) -- (314.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.45, 34.03) -- (314.45, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.63, 34.03) -- (314.63, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.00, 34.03) -- (315.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.21, 34.03) -- (315.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.23, 34.03) -- (315.23, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.37, 34.03) -- (315.37, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.48, 34.03) -- (315.48, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.51, 34.03) -- (315.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.62, 34.03) -- (315.62, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.70, 34.03) -- (315.70, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.79, 34.03) -- (315.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.13, 34.03) -- (316.13, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.22, 34.03) -- (316.22, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.38, 34.03) -- (316.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.61, 34.03) -- (316.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.93, 34.03) -- (316.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.07, 34.03) -- (317.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.20, 34.03) -- (317.20, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.36, 34.03) -- (317.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.75, 34.03) -- (317.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.76, 34.03) -- (317.76, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.79, 34.03) -- (317.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.86, 34.03) -- (317.86, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.89, 34.03) -- (317.89, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.98, 34.03) -- (317.98, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (318.43, 34.03) -- (318.43, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (318.60, 34.03) -- (318.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (318.85, 34.03) -- (318.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.11, 34.03) -- (319.11, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.21, 34.03) -- (319.21, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.52, 34.03) -- (319.52, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.81, 34.03) -- (319.81, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.44, 34.03) -- (320.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.85, 34.03) -- (321.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.91, 34.03) -- (321.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (322.04, 34.03) -- (322.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (322.30, 34.03) -- (322.30, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (322.60, 34.03) -- (322.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (322.75, 34.03) -- (322.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (323.02, 34.03) -- (323.02, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (323.10, 34.03) -- (323.10, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (323.28, 34.03) -- (323.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (324.05, 34.03) -- (324.05, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (324.42, 34.03) -- (324.42, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (324.61, 34.03) -- (324.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (324.72, 34.03) -- (324.72, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (325.08, 34.03) -- (325.08, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (325.99, 34.03) -- (325.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (326.58, 34.03) -- (326.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (326.72, 34.03) -- (326.72, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (327.61, 34.03) -- (327.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (327.91, 34.03) -- (327.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (328.67, 34.03) -- (328.67, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (328.94, 34.03) -- (328.94, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (329.07, 34.03) -- (329.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (329.52, 34.03) -- (329.52, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (331.17, 34.03) -- (331.17, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (332.00, 34.03) -- (332.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (332.27, 34.03) -- (332.27, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (333.07, 34.03) -- (333.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (333.19, 34.03) -- (333.19, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (333.76, 34.03) -- (333.76, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (335.51, 34.03) -- (335.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (336.07, 34.03) -- (336.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (336.75, 34.03) -- (336.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (336.88, 34.03) -- (336.88, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (337.54, 34.03) -- (337.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (337.92, 34.03) -- (337.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.29, 34.03) -- (338.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.32, 34.03) -- (338.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.37, 34.03) -- (338.37, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.79, 34.03) -- (338.79, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.87, 34.03) -- (338.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (339.41, 34.03) -- (339.41, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (339.54, 34.03) -- (339.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (340.26, 34.03) -- (340.26, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (340.28, 34.03) -- (340.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (340.36, 34.03) -- (340.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (340.58, 34.03) -- (340.58, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (340.90, 34.03) -- (340.90, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (341.07, 34.03) -- (341.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (341.38, 34.03) -- (341.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (341.48, 34.03) -- (341.48, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (341.54, 34.03) -- (341.54, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (341.57, 34.03) -- (341.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.00, 34.03) -- (342.00, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.06, 34.03) -- (342.06, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.60, 34.03) -- (342.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.92, 34.03) -- (342.92, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (344.39, 34.03) -- (344.39, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (344.81, 34.03) -- (344.81, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (345.03, 34.03) -- (345.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (345.51, 34.03) -- (345.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (345.56, 34.03) -- (345.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (346.27, 34.03) -- (346.27, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.09, 34.03) -- (348.09, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.19, 34.03) -- (348.19, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.32, 34.03) -- (348.32, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.52, 34.03) -- (348.52, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.65, 34.03) -- (348.65, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (350.04, 34.03) -- (350.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (350.29, 34.03) -- (350.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (350.39, 34.03) -- (350.39, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (351.49, 34.03) -- (351.49, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (354.19, 34.03) -- (354.19, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (354.41, 34.03) -- (354.41, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (354.96, 34.03) -- (354.96, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (354.99, 34.03) -- (354.99, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (355.28, 34.03) -- (355.28, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (355.84, 34.03) -- (355.84, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (356.71, 34.03) -- (356.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (356.75, 34.03) -- (356.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (357.50, 34.03) -- (357.50, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (357.53, 34.03) -- (357.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (358.04, 34.03) -- (358.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (358.62, 34.03) -- (358.62, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (359.31, 34.03) -- (359.31, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (359.62, 34.03) -- (359.62, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (359.75, 34.03) -- (359.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (359.85, 34.03) -- (359.85, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.61, 34.03) -- (360.61, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.64, 34.03) -- (360.64, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.71, 34.03) -- (360.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (361.91, 34.03) -- (361.91, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (362.60, 34.03) -- (362.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (364.24, 34.03) -- (364.24, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (364.46, 34.03) -- (364.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (365.70, 34.03) -- (365.70, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (366.29, 34.03) -- (366.29, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (370.53, 34.03) -- (370.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (371.02, 34.03) -- (371.02, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (372.06, 34.03) -- (372.06, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (372.07, 34.03) -- (372.07, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (372.38, 34.03) -- (372.38, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (372.60, 34.03) -- (372.60, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (372.90, 34.03) -- (372.90, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (373.16, 34.03) -- (373.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (373.53, 34.03) -- (373.53, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (373.80, 34.03) -- (373.80, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (374.46, 34.03) -- (374.46, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (374.81, 34.03) -- (374.81, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (375.77, 34.03) -- (375.77, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (376.36, 34.03) -- (376.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (376.51, 34.03) -- (376.51, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (376.93, 34.03) -- (376.93, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (378.03, 34.03) -- (378.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (379.36, 34.03) -- (379.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (379.36, 34.03) -- (379.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (380.09, 34.03) -- (380.09, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (380.12, 34.03) -- (380.12, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (381.03, 34.03) -- (381.03, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (381.47, 34.03) -- (381.47, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (381.75, 34.03) -- (381.75, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (382.36, 34.03) -- (382.36, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (382.44, 34.03) -- (382.44, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (382.57, 34.03) -- (382.57, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (383.02, 34.03) -- (383.02, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (385.04, 34.03) -- (385.04, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (385.16, 34.03) -- (385.16, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (388.87, 34.03) -- (388.87, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.56, 34.03) -- (393.56, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (395.71, 34.03) -- (395.71, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (403.26, 34.03) -- (403.26, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (404.02, 34.03) -- (404.02, 41.32);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 52.86) {3.7};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 96.58) {3.8};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,140.30) {3.9};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,184.02) {4.0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,227.74) {4.1};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,271.45) {4.2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31, 44.90) {-5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,128.11) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,211.32) {5};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 40.56, 20.31) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 90.87, 20.31) {1};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (141.19, 20.31) {2};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (191.50, 20.31) {3};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (241.82, 20.31) {4};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (292.13, 20.31) {5};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (342.45, 20.31) {6};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (392.76, 20.31) {7};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 85.59, 20.31) {1};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (136.07, 20.31) {2};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (186.55, 20.31) {3};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (237.03, 20.31) {4};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (287.51, 20.31) {5};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (337.99, 20.31) {6};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (388.47, 20.31) {7};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (230.63,  4.82) {Ln(Min. City Dist.)$_{t}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (228.50,  4.82) {Ln(Min. City Dist.)$_{t}$};
 \end{scope}

### 2014-10-06 LaTeX/rmseInOut.tex
updating plots

--- 2014-09-23 LaTeX/rmseInOut.tex
@@
-% Created by tikzDevice version 0.7.0 on 2014-09-23 12:42:48
+% Created by tikzDevice version 0.7.0 on 2014-10-06 19:44:46
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (505.89,289.08);
 \end{scope}
 \begin{scope}
-\path[clip] ( 39.69, 54.77) rectangle (229.13,264.40);
+\path[clip] ( 32.22, 54.77) rectangle (261.53,264.40);
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
 
-\path[fill=fillColor] ( 39.69, 54.77) rectangle (229.13,264.40);
+\path[fill=fillColor] ( 32.22, 54.77) rectangle (261.53,264.40);
 \definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}
 
-\path[fill=fillColor] ( 52.60, 64.30) rectangle (130.10,254.87);
+\path[fill=fillColor] ( 47.86, 64.30) rectangle (141.66,254.87);
 
-\path[fill=fillColor] (138.71, 64.30) rectangle (216.21,165.65);
+\path[fill=fillColor] (152.09, 64.30) rectangle (245.89,242.43);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 39.69, 54.77) rectangle (229.13,264.40);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 32.22, 54.77) rectangle (261.53,264.40);
 \end{scope}
 \begin{scope}
-\path[clip] (232.14, 54.77) rectangle (421.57,264.40);
+\path[clip] (264.54, 54.77) rectangle (493.85,264.40);
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
 
-\path[fill=fillColor] (232.14, 54.77) rectangle (421.57,264.40);
+\path[fill=fillColor] (264.54, 54.77) rectangle (493.85,264.40);
 \definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}
 
-\path[fill=fillColor] (245.05, 64.30) rectangle (322.55,254.76);
+\path[fill=fillColor] (280.17, 64.30) rectangle (373.98,254.37);
 
-\path[fill=fillColor] (331.16, 64.30) rectangle (408.66,164.41);
+\path[fill=fillColor] (384.40, 64.30) rectangle (478.21,239.82);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.14, 54.77) rectangle (421.57,264.40);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (264.54, 54.77) rectangle (493.85,264.40);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
+\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
@@
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] ( 39.69,264.40) rectangle (229.13,277.04);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] ( 32.22,264.40) rectangle (261.53,277.04);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (134.41,267.41) {Ln(Min. Cap Dist.)$_{t}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (146.87,267.41) {Ln(Min. Cap Dist.)$_{t}$};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
+\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
@@
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (232.14,264.40) rectangle (421.57,277.04);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (264.54,264.40) rectangle (493.85,277.04);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.86,267.41) {Ln(Min. City Dist.)$_{t}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (379.19,267.41) {Ln(Min. City Dist.)$_{t}$};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
+\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 60.99) {0.0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11, 60.99) {0};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,128.89) {0.1};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11,120.76) {2};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,196.78) {0.2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11,180.52) {4};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11,240.28) {6};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
+\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 91.35, 41.05) {In-Sample };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 94.76, 41.05) {In-Sample };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 91.35, 30.68) { n=375 };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 94.76, 30.68) { n=375 };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 91.35, 20.31) { N=66};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 94.76, 20.31) { N=66};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (177.46, 41.05) {Out-Sample };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (198.99, 41.05) {Out-Sample };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (177.46, 30.68) { n=186 };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (198.99, 30.68) { n=186 };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (177.46, 20.31) { N=42};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (198.99, 20.31) { N=42};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
+\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (283.80, 41.05) {In-Sample };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (327.08, 41.05) {In-Sample };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (283.80, 30.68) { n=375 };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (327.08, 30.68) { n=375 };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (283.80, 20.31) { N=66};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (327.08, 20.31) { N=66};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (369.91, 41.05) {Out-Sample };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (431.31, 41.05) {Out-Sample };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (369.91, 30.68) { n=186 };
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (431.31, 30.68) { n=186 };
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (369.91, 20.31) { N=42};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (431.31, 20.31) { N=42};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
+\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at ( 17.30,159.59) {RMSE};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at ( 14.29,159.59) {RMSE};
 \end{scope}

### 2014-10-06 R/Analysis/conflictMaps.R

@@ -6,22 +6,25 @@ if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
 setwd(pathData)
 load('combinedData.rda')
 load("cityTotPopLatLongvFinal.rda")
-prio <- read.csv("PRIO - Conflict Site Data/ConflictSite 4-2010_v3 Dataset.csv",stringsAsFactors=F)
+prio = read.csv("PRIO - Conflict Site Data/ConflictSite 4-2010_v3 Dataset.csv",
+	stringsAsFactors=F)
 source(paste0(pathMain,"/geodistance.R"))
 
-fYrCty$cname <- toupper(countrycode(fYrCty$cname,"country.name","country.name"))
-prio$Conflict.territory <- toupper(countrycode(prio$Conflict.territory,"country.name","country.name"))
+fYrCty$cname = toupper( countrycode(
+	fYrCty$cname,"country.name","country.name") )
+prio$Conflict.territory = toupper( countrycode(
+	prio$Conflict.territory,"country.name","country.name") )
 
 ######################################################################
 # Trace conflict over time
 cname="INDIA"
 worldmap=cshp(date=as.Date("1990-01-01"),useGW=F)
-ccode <- countrycode(cname,"country.name","cown")
-country.shape <- worldmap[worldmap$COWCODE==ccode,]
-newprio <- na.omit(prio[prio$Conflict.territory==cname,])
+ccode = countrycode(cname,"country.name","cown")
+cntryShape = worldmap[worldmap$COWCODE==ccode,]
+newprio = na.omit(prio[prio$Conflict.territory==cname,])
 
 gpclibPermit()
-ggmap = fortify(country.shape, region = "COWCODE")
+ggmap = fortify(cntryShape, region = "COWCODE")
 ggmapData = data.frame("id" = unique(ggmap$id))
 ggmapData$id = as.numeric(as.character(ggmapData$id))
 
@@ -55,13 +58,41 @@ setwd(pathTex)
 ######################################################################
 
 ######################################################################
-# Trace GDP over time
+# Aggregate GDP Growth and Distance
 setwd(pathData)
 load('combinedData.rda')
[…]

### 2014-10-06 R/Analysis/models.R

@@ -96,11 +96,12 @@ temp = ggsimplot(modelResults=mCity, sims=10000, simData=modData,
   ylabel="\\% $\\Delta$ Ln(GDP)$_{t}$", xlabel="Ln(Min. City Dist.)$_{t}$",
   specX=TRUE, ggxbreaks=seq(-1,7,1), plotType='ribbon'
   )
+temp + theme(axis.title.y=element_text(vjust=1))
 temp
 setwd(pathTex)
-# tikz(file='mCitySimPlot.tex', width=6, height=4, standAlone=F)
-# temp
-# dev.off()
+tikz(file='mCitySimPlot.tex', width=6, height=4, standAlone=F)
+temp
+dev.off()
 
 temp = ggsimplot(modelResults=mCap, sims=10000, simData=modData, 
   vars=na.omit(rownames(summary(mCap)$'coefficients')[2:100]),
@@ -108,11 +109,12 @@ temp = ggsimplot(modelResults=mCap, sims=10000, simData=modData,
   ylabel="\\% $\\Delta$ Ln(GDP)$_{t}$", xlabel="Ln(Min. Cap Dist.)$_{t}$",
   specX=TRUE, ggxbreaks=seq(-1,7,1), plotType='ribbon'
   )
+temp + theme(axis.title.y=element_text(vjust=1))
 temp
 setwd(pathTex)
-# tikz(file='mCapSimPlot.tex', width=6, height=4, standAlone=F)
-# temp
-# dev.off()
+tikz(file='mCapSimPlot.tex', width=6, height=4, standAlone=F)
+temp
+dev.off()
 ###################################################################
 
 
@@ -155,14 +157,15 @@ ggRMSE$stat=numSM(ggRMSE$stat)
 temp=ggplot(ggRMSE, aes(x=type, y=stat))
 temp=temp + geom_bar(stat='identity') + ylab('RMSE') + xlab('')
 temp=temp + facet_wrap(~var)
-temp=temp + theme(legend.position='none', legend.title=element_blank(),
-      axis.ticks=element_blank(), panel.grid.major=element_blank(),
-      panel.grid.minor=element_blank())
+temp=temp + theme(axis.title.y=element_text(vjust=1),
+  legend.position='none', legend.title=element_blank(),
+  axis.ticks=element_blank(), panel.grid.major=element_blank(),
+  panel.grid.minor=element_blank())
 temp
 setwd(pathTex)
-# tikz(file='rmseInOut.tex', width=6, height=4, standAlone=F)
-# temp
[…]

### 2014-10-09 LaTeX/RhodiumEmp.tex
ugh

@@
 
-\subsection{Conflict and City Data}
+Our theoretical framework centers around the argument that variation in macroeconomic growth amongst countries in the midst of civil war can be explained by the spatial proximity between civil conflicts and urban centers.
+In constructing our dataset, we thus restrict our unit of observation to conflict-country years.
+This enables us to directly explore whether variation in growth amongst countries experiencing internal conflict can be explained by the proximity of conflict to cities.
+To measure macroeconomic performance, we focus on annual percent change in GDP from the World Development Indicators.
+We adopt this parameterization of our dependent variable because we expect that conflicts proximate to urban centers will generate abrupt changes in macroeconomic growth.
+Much of the extant literature linking internal armed conflict and economic growth has approached this instead using five or ten year averages of GDP growth.
+However, averaging over an arbitrary set of years may obfuscate meaningful variation in GDP growth over short temporal spans.
 
-To measure economic performance we use annual percent change in GDP collected from the World Development Indicators at the World Bank.
-Unlike much of the extant literature in constructing our dependent variable we focus on year over change instead of a ten year average.
-This allows us to estimate the direct effect of conflict on economic performance in that year.
-A ten or five year average approach would hide important variation in our dependent variable that can be explained by the proximity of conflict to economic centers.
+To determine the spatial proximity of conflict to urban centers, we collect information on the location of conflicts from the PRIO Conflict Site Dataset \citep{hallberg:2012}.
+This dataset contains information on the geographical centers of  armed conflict events and the area covered by each conflict at a yearly level from 1989 to 2008.
+To construct a time-series cross-sectional database of urban centers, we turn to yearly editions of The World Almanac from 1989 to 2008.
+Typically, the Almanacs list at least three major cities, including the capital, for each country and year from 1989 to 2008.
+To determine proximity, we calculate the great-circle distance in kilometers between the centroid of each of the conflicts with the centroids of city locations.
+Meaning that for each year we determine the distance between every conflict and every major city within a state.
 
-To determine the location of conflicts we turn to the PRIO Conflict Site Dataset.
-This dataset contains geo-referenced armed conflict events from 1989 to 2008.
-In total this dataset provides us with approximately 800 geo-referenced internal conflict-year cases.
-To gather information on capital and major cities we turn to yearly editions of The World Almanac from 1989 to 2008.
-Typically, the Alamanacs list at least three major cities, including the capital, for each country and year from 1989 to 2008.
+\begin{figure}
+	\centering
+	\resizebox{.8\textwidth}{!}{\input{distGdp}}
+	\caption{Average relationship between city and capital distance from conflict and GDP growth.}
+	\label{fig:distGdp}
+\end{figure}
 
@@
 \FloatBarrier
-
-Our analysis focuses on exploring variations in economic growth in countries undergoing conflict by the proximity of those conflicts to major cities, thus we restrict our sample to only those countries that are listed as having conflicts in the PRIO dataset.
-To determine proximity, we calculate the distance in kilometers between the centroid of each of the conflicts with the centroids of city locations.
-Meaning that for each year we determine the distance between every conflict and every major city within a state.
-F
-
-% or example, in figure \ref{fig:columbiaMap} we show the location of armed conflicts in Colombia, dots colored in shades of blue, major cities, depicted as triangles, and the capital, a diamond.\footnote{One armed conflict involving rebel actors and the Colombian government occurred outside of Colombia's borders.} For Colombia each of the red dots represents the same conflict but a different year, with earlier years shaded in light blue and later years shaded in dark blue.
-Thus for every year we made six distance calculations -- one for every city.
 
@@
 
+Using a dataset that includes 497 country-years of civil war from 68 different countries during the period of 1989 to 2007.
+
 To estimate the model we use random effects clustered on countries. The model we estimate is shown below:
@@
 	& \;+\; \beta_{6}(Upper \; Income_{i,t}) \;+\; \beta_{7}(Inflation_{i,t-1}) \\
-	&  \;+\; \beta_{8}(Democracy_{i,t-1}) \;+\; \beta_{9}(World \; GDP \; Growth_{t}) \\
-	& \;+\; \mu_{i,t} \;+\; \epsilon_{i,t}
+	&  \;+\; \beta_{8}(Democracy_{i,t-1}) \;+\; \beta_{9}(Resource \; Rents/GDP_{t}) \\
+	& \;+\; \beta_{10}(World \; GDP \; Growth_{t}) \;+\; \mu_{i,t} \;+\; \epsilon_{i,t}
 \end{align*}

### 2014-10-09 LaTeX/RhodiumTheory.tex
updating plots
ugh

@@
 
-% \cite[p. 137]{quigley:1998}, we should use page citations everywhere we reference long quotes or not at all
-
 \subsection{Cities and Economic Growth}
 
-That cities are central to the development of national economic performance is well supported in the long literature on the importance of urban centers to national economies.
+That cities are central to the development of national economic performance is well supported in literature on the role urban centers play in national economies.
 \citet{myrdal:sitohang:1957} were among the first to argue that once cities reach a certain size through the process of urbanization, they tend to become self-reinforcing growth centers through a process Myrdal termed as ``cumulative causation''.
@@
 
-% Further \citet{quigley:1998} concludes that ``large cities have been and will continue to be an important source of economic growth.''
+% Further \citet{quigley:1998} concludes that ``large cities have been and will continue to be an important source of economic growth.'' good quote but i didnt know where to put it
 
@@
 Their dense populations also tempt belligerents and maximize the impact to cost ratio of a given violent action.
+
 Additionally, warfare destroys transportation infrastructure, which can interfere both with commerce and with rebuilding during a conflict.
@@
 
-We extend this line of research by conceptualizing civil wars not as homogeneous national phenomenon, but as a diverse class of violent conflict with properties that distinguish the effects of one conflict from another.
+We extend this line of research by conceptualizing civil war not as a homogeneous national phenomenon, but as a diverse class of violent conflict with properties that distinguish the effects of one conflict from another.
 Since urban economies are responsible for a disproportionate share of national economic performance, civil conflicts in or near these engines of commerce should likewise exert a disproportionate influence on state performance.
@@
 For much of this time, the cartel violence generally occurred in rural areas along drug trafficking routes and not within major cities.
-\cite{beittel:2011} writes in 2011 that ``drug trafficking-related killings remain concentrated in a relatively few cities,'' but notes that the violence was beginning to expand in geographic range by 2010.
-
-We turn now to an empirical test of our proposition.
-Using a dataset that includes 510 country-years of civil war from 71 different countries, we seek to determine how the geography of conflict impacts state economic outcomes.
+\cite{beittel:2011} writes in 2011 that ``drug trafficking-related killings remain concentrated in a relatively few cities.''

### 2014-10-09 LaTeX/distGdp.tex
ugh

@@
-% Created by tikzDevice version 0.7.0 on 2014-10-06 19:44:25
+% Created by tikzDevice version 0.7.0 on 2014-10-06 20:06:20
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (146.87,267.41) {Ln(Min. Cap Dist.)$_{t-1}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (146.87,267.41) {Min. Capital Dist.$_{t-1}$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (379.19,267.41) {Ln(Min. City Dist.)$_{t-1}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (379.19,267.41) {Min. City Dist.$_{t-1}$};
 \end{scope}

### 2014-10-09 LaTeX/mCapCoefPlot.tex
ugh

--- 2014-09-23 LaTeX/mCapCoefPlot.tex
@@
-% Created by tikzDevice version 0.7.0 on 2014-09-23 11:36:12
+% Created by tikzDevice version 0.7.0 on 2014-10-06 20:08:18
 % !TEX encoding = UTF-8 Unicode
@@
 \path[fill=fillColor] (137.46, 34.03) rectangle (277.03,277.03);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (208.13, 47.05) -- (219.24, 47.05);
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (208.14, 68.75) -- (209.77, 68.75);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (206.43, 49.88) -- (213.45, 49.88);
-
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (198.47, 76.30) -- (231.75, 76.30);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (206.20, 90.45) -- (210.40, 90.45);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (183.03,102.71) -- (196.68,102.71);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (159.27,112.14) -- (179.64,112.14);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (165.42,129.12) -- (249.46,129.12);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (143.80,133.84) -- (270.69,133.84);
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (205.01,155.53) -- (236.69,155.53);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (175.86,155.53) -- (202.88,155.53);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (156.71,177.23) -- (198.91,177.23);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (207.28,181.95) -- (208.37,181.95);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (208.28,198.93) -- (210.01,198.93);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (194.89,208.36) -- (229.18,208.36);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (197.99,220.62) -- (253.62,220.62);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (189.15,234.77) -- (216.25,234.77);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (171.25,242.32) -- (211.92,242.32);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (209.85,261.19) -- (221.60,261.19);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (211.83,264.02) -- (229.44,264.02);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (209.03, 47.05) -- (218.35, 47.05);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (208.27, 68.75) -- (209.64, 68.75);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (206.99, 49.88) -- (212.88, 49.88);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (201.15, 76.30) -- (229.08, 76.30);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (206.54, 90.45) -- (210.06, 90.45);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (184.13,102.71) -- (195.58,102.71);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (160.90,112.14) -- (178.00,112.14);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (172.18,129.12) -- (242.71,129.12);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (154.00,133.84) -- (260.49,133.84);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (207.55,155.53) -- (234.14,155.53);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (178.04,155.53) -- (200.70,155.53);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (160.10,177.23) -- (195.52,177.23);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (207.37,181.95) -- (208.28,181.95);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (208.42,198.93) -- (209.87,198.93);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (197.65,208.36) -- (226.42,208.36);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (202.46,220.62) -- (249.15,220.62);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (191.33,234.77) -- (214.07,234.77);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (174.52,242.32) -- (208.65,242.32);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (210.79,261.19) -- (220.66,261.19);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (213.24,264.02) -- (228.03,264.02);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (207.25, 34.03) -- (207.25,277.03);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (207.86, 34.03) -- (207.86,277.03);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.73,261.19) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (220.63,264.02) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (202.70,234.77) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (191.58,242.32) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (212.04,208.36) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (225.80,220.62) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.82,181.95) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.15,198.93) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.37,155.53) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.81,177.23) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.44,129.12) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (220.85,155.53) circle (  2.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.25,133.84) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.85,102.71) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.45,112.14) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.11, 76.30) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.30, 90.45) circle (  2.85);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.94, 49.88) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.96, 68.75) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.45, 48.56) --
-	(213.45, 51.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (213.69, 47.05) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.45, 49.88) --
-	(206.43, 49.88);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (219.24, 45.97) --
+	(219.24, 48.14);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (206.43, 48.56) --
-	(206.43, 51.20);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (219.24, 47.05) --
+	(208.13, 47.05);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (231.75, 74.97) --
-	(231.75, 77.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (208.13, 45.97) --
+	(208.13, 48.14);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (231.75, 76.30) --
-	(198.47, 76.30);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.77, 67.66) --
+	(209.77, 69.83);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (198.47, 74.97) --
-	(198.47, 77.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.77, 68.75) --
+	(208.14, 68.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (208.14, 67.66) --
+	(208.14, 69.83);
+\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (210.40, 89.36) --
+	(210.40, 91.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (210.40, 90.45) --
+	(206.20, 90.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (206.20, 89.36) --
+	(206.20, 91.53);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (196.68,101.39) --
-	(196.68,104.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (179.64,111.06) --
+	(179.64,113.23);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (196.68,102.71) --
-	(183.03,102.71);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (179.64,112.14) --
+	(159.27,112.14);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (183.03,101.39) --
-	(183.03,104.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.27,111.06) --
+	(159.27,113.23);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (249.46,127.80) --
-	(249.46,130.44);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (270.69,132.75) --
+	(270.69,134.92);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (249.46,129.12) --
-	(165.42,129.12);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (270.69,133.84) --
+	(143.80,133.84);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.42,127.80) --
-	(165.42,130.44);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (143.80,132.75) --
+	(143.80,134.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (236.69,154.45) --
+	(236.69,156.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (236.69,155.53) --
+	(205.01,155.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.01,154.45) --
+	(205.01,156.62);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (202.88,154.21) --
-	(202.88,156.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (198.91,176.15) --
+	(198.91,178.32);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (202.88,155.53) --
-	(175.86,155.53);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (198.91,177.23) --
+	(156.71,177.23);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (175.86,154.21) --
-	(175.86,156.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.71,176.15) --
+	(156.71,178.32);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (208.37,180.63) --
-	(208.37,183.27);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (210.01,197.84) --
+	(210.01,200.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (208.37,181.95) --
-	(207.28,181.95);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (210.01,198.93) --
+	(208.28,198.93);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.28,180.63) --
-	(207.28,183.27);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (208.28,197.84) --
+	(208.28,200.01);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (229.18,207.04) --
-	(229.18,209.68);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (253.62,219.54) --
+	(253.62,221.71);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (229.18,208.36) --
-	(194.89,208.36);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (253.62,220.62) --
+	(197.99,220.62);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (194.89,207.04) --
-	(194.89,209.68);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (197.99,219.54) --
+	(197.99,221.71);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.25,233.45) --
-	(216.25,236.09);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (211.92,241.24) --
+	(211.92,243.41);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.25,234.77) --
-	(189.15,234.77);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (211.92,242.32) --
+	(171.25,242.32);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (189.15,233.45) --
-	(189.15,236.09);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (171.25,241.24) --
+	(171.25,243.41);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (221.60,259.87) --
-	(221.60,262.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.44,262.93) --
+	(229.44,265.10);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (221.60,261.19) --
-	(209.85,261.19);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.44,264.02) --
+	(211.83,264.02);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.85,259.87) --
-	(209.85,262.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (211.83,262.93) --
+	(211.83,265.10);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 46.58) {World GDP Growth$_{t}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 43.75) {World GDP Growth$_{t}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 72.99) {Democracy$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 65.44) {Resource Rents/GDP$_{t}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 99.40) {Ln(Inflation)$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 87.14) {Democracy$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,125.82) {Upper Income};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,108.84) {Ln(Inflation)$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,152.23) {Area$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,130.53) {Upper Income};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,178.64) {Duration$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,152.23) {Number of conflicts$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,205.06) {Type$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,173.93) {Area$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,231.47) {Intensity$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,195.62) {Duration$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,257.88) {Ln(Min. Capital Dist.)$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,217.32) {Type$_{t-1}$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,239.01) {Intensity$_{t-1}$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,260.71) {Ln(Min. Capital Dist.)$_{t-1}$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (143.80, 20.31) {-0.3};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (171.21, 20.31) {-3};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (186.10, 20.31) {-0.1};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (207.86, 20.31) {0};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (228.40, 20.31) {0.1};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (270.69, 20.31) {0.3};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (244.52, 20.31) {3};
 \end{scope}

### 2014-10-09 LaTeX/mCapSimPlot.tex
ugh

@@
-% Created by tikzDevice version 0.7.0 on 2014-10-06 19:44:45
+% Created by tikzDevice version 0.7.0 on 2014-10-06 20:10:12
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,105.62) --
-	( 60.61,108.24) --
-	( 64.85,109.70) --
-	( 64.98,109.74) --
-	( 78.30,114.31) --
-	( 86.71,117.20) --
-	( 92.34,119.13) --
-	( 95.59,120.24) --
-	(101.92,122.42) --
-	(110.88,125.49) --
-	(154.64,140.51) --
-	(158.01,141.66) --
-	(171.43,146.26) --
-	(178.49,148.69) --
-	(187.92,151.92) --
-	(192.71,153.57) --
-	(195.62,154.56) --
-	(195.71,154.59) --
-	(196.35,154.81) --
-	(198.04,155.39) --
-	(199.87,156.02) --
-	(204.99,157.78) --
-	(205.19,157.85) --
-	(209.65,159.38) --
-	(211.50,160.01) --
-	(215.87,161.51) --
-	(217.33,162.01) --
-	(217.43,162.05) --
-	(217.68,162.13) --
-	(218.17,162.30) --
-	(220.17,162.99) --
-	(220.33,163.04) --
-	(220.93,163.25) --
-	(221.63,163.49) --
-	(222.58,163.81) --
-	(223.29,164.06) --
-	(223.54,164.14) --
-	(223.59,164.16) --
-	(224.00,164.30) --
-	(229.14,166.07) --
-	(231.15,166.76) --
-	(231.34,166.82) --
-	(232.39,167.18) --
-	(233.34,167.51) --
-	(234.25,167.82) --
-	(235.24,168.16) --
-	(236.22,168.49) --
-	(237.40,168.90) --
-	(237.41,168.90) --
-	(239.29,169.55) --
-	(239.31,169.55) --
-	(240.03,169.80) --
-	(240.80,170.06) --
-	(241.27,170.23) --
-	(241.65,170.36) --
-	(242.95,170.80) --
-	(244.78,171.43) --
-	(248.30,172.64) --
-	(249.74,173.13) --
-	(250.22,173.30) --
-	(250.38,173.35) --
-	(250.69,173.46) --
-	(251.97,173.90) --
-	(252.46,174.07) --
-	(253.69,174.49) --
-	(253.89,174.55) --
-	(254.34,174.71) --
-	(255.74,175.19) --
-	(256.94,175.60) --
-	(258.99,176.31) --
-	(260.08,176.68) --
-	(260.16,176.71) --
-	(261.39,177.13) --
-	(262.57,177.53) --
-	(263.47,177.84) --
-	(264.14,178.07) --
-	(264.43,178.17) --
-	(264.94,178.35) --
-	(265.11,178.40) --
-	(265.48,178.53) --
-	(265.54,178.55) --
-	(266.69,178.95) --
-	(266.70,178.95) --
-	(267.74,179.31) --
-	(267.83,179.34) --
-	(267.95,179.38) --
-	(268.15,179.45) --
-	(268.32,179.51) --
-	(268.51,179.57) --
-	(268.75,179.66) --
-	(269.12,179.78) --
-	(269.30,179.84) --
-	(269.75,180.00) --
-	(269.91,180.05) --
-	(271.51,180.60) --
-	(272.31,180.88) --
-	(272.40,180.91) --
-	(272.91,181.08) --
-	(273.01,181.11) --
-	(273.29,181.21) --
-	(273.48,181.28) --
-	(274.31,181.56) --
-	(274.85,181.75) --
-	(274.88,181.76) --
-	(275.50,181.97) --
-	(276.03,182.15) --
-	(276.14,182.19) --
-	(276.73,182.39) --
-	(276.77,182.41) --
-	(277.28,182.58) --
-	(277.37,182.61) --
-	(278.83,183.11) --
-	(278.93,183.15) --
-	(278.99,183.17) --
-	(279.03,183.18) --
-	(279.36,183.30) --
-	(279.83,183.46) --
-	(279.90,183.48) --
-	(280.21,183.59) --
-	(280.36,183.64) --
-	(280.41,183.66) --
-	(280.47,183.68) --
-	(280.50,183.68) --
-	(280.60,183.72) --
-	(280.63,183.73) --
-	(281.16,183.91) --
-	(281.52,184.03) --
-	(281.60,184.06) --
-	(283.10,184.58) --
-	(283.28,184.64) --
-	(283.34,184.66) --
-	(283.74,184.80) --
-	(283.80,184.82) --
-	(284.26,184.97) --
-	(284.43,185.03) --
-	(284.75,185.14) --
-	(284.80,185.16) --
-	(284.81,185.16) --
-	(284.81,185.16) --
-	(284.84,185.18) --
-	(284.88,185.19) --
-	(285.44,185.38) --
-	(285.67,185.46) --
-	(286.04,185.59) --
-	(286.70,185.81) --
-	(286.95,185.90) --
-	(287.76,186.18) --
-	(288.16,186.31) --
-	(288.45,186.41) --
-	(288.86,186.55) --
-	(289.03,186.61) --
-	(289.13,186.65) --
-	(289.30,186.70) --
-	(289.61,186.81) --
-	(289.71,186.85) --
-	(289.99,186.94) --
-	(290.44,187.10) --
-	(291.29,187.39) --
-	(291.45,187.44) --
-	(291.58,187.49) --
-	(292.20,187.70) --
-	(292.36,187.75) --
-	(292.77,187.89) --
-	(292.78,187.90) --
-	(292.85,187.92) --
-	(292.94,187.95) --
-	(293.49,188.14) --
-	(293.61,188.18) --
-	(293.90,188.28) --
-	(293.94,188.30) --
-	(295.12,188.70) --
-	(295.85,188.95) --
-	(296.61,189.21) --
-	(297.11,189.38) --
-	(297.99,189.68) --
-	(298.09,189.72) --
-	(298.13,189.74) --
-	(298.21,189.76) --
-	(298.45,189.84) --
-	(298.48,189.85) --
-	(298.71,189.93) --
-	(298.89,190.00) --
-	(299.22,190.11) --
-	(300.07,190.40) --
-	(300.69,190.61) --
-	(301.34,190.83) --
-	(301.81,191.00) --
-	(301.86,191.01) --
-	(302.06,191.08) --
-	(302.08,191.09) --
-	(302.20,191.13) --
-	(302.30,191.16) --
-	(302.45,191.22) --
-	(302.52,191.24) --
-	(302.61,191.27) --
-	(302.89,191.37) --
-	(302.93,191.38) --
-	(303.17,191.46) --
-	(304.10,191.78) --
-	(304.31,191.85) --
-	(304.47,191.91) --
-	(304.48,191.91) --
-	(304.60,191.95) --
-	(304.68,191.98) --
-	(305.11,192.13) --
-	(305.28,192.19) --
-	(305.76,192.35) --
-	(305.86,192.39) --
-	(306.15,192.49) --
-	(307.03,192.79) --
-	(307.16,192.83) --
-	(307.37,192.90) --
-	(308.42,193.27) --
-	(308.63,193.34) --
-	(308.79,193.39) --
-	(309.08,193.49) --
-	(309.55,193.65) --
-	(309.72,193.71) --
-	(310.36,193.93) --
-	(310.45,193.96) --
-	(310.80,194.08) --
-	(310.98,194.14) --
-	(311.09,194.18) --
-	(311.49,194.32) --
-	(311.71,194.39) --
-	(311.87,194.45) --
-	(312.39,194.63) --
-	(312.68,194.73) --
-	(312.75,194.75) --
-	(314.09,195.21) --
-	(314.12,195.22) --
-	(314.55,195.37) --
-	(314.84,195.47) --
-	(315.05,195.54) --
-	(315.28,195.62) --
-	(315.54,195.71) --
-	(315.61,195.73) --
-	(315.65,195.75) --
-	(316.29,195.97) --
-	(316.37,195.99) --
-	(316.58,196.06) --
-	(316.61,196.07) --
-	(316.72,196.11) --
-	(317.13,196.25) --
-	(318.60,196.76) --
-	(319.14,196.94) --
-	(320.71,197.48) --
-	(321.34,197.70) --
-	(321.47,197.74) --
-	(322.56,198.12) --
-	(322.64,198.14) --
-	(322.93,198.24) --
-	(323.98,198.60) --
-	(324.06,198.63) --
-	(324.53,198.79) --
-	(324.82,198.89) --
-	(325.46,199.11) --
-	(325.85,199.24) --
-	(325.87,199.25) --
-	(325.91,199.27) --
-	(326.16,199.35) --
-	(326.46,199.45) --
-	(327.01,199.64) --
-	(327.50,199.81) --
-	(327.78,199.91) --
-	(328.37,200.11) --
-	(328.92,200.30) --
-	(330.17,200.73) --
-	(330.38,200.80) --
-	(330.88,200.97) --
-	(333.53,201.88) --
-	(333.56,201.89) --
-	(333.69,201.94) --
-	(333.82,201.98) --
-	(333.83,201.98) --
-	(335.38,202.51) --
-	(335.47,202.55) --
-	(337.65,203.29) --
-	(338.50,203.58) --
-	(338.83,203.70) --
-	(338.87,203.71) --
-	(339.04,203.77) --
-	(339.21,203.83) --
-	(339.40,203.89) --
-	(339.55,203.94) --
-	(339.76,204.02) --
-	(339.84,204.04) --
-	(340.15,204.15) --
-	(340.28,204.20) --
-	(340.65,204.32) --
-	(341.52,204.62) --
-	(342.53,204.97) --
-	(343.79,205.40) --
-	(343.95,205.45) --
-	(345.11,205.85) --
-	(345.20,205.89) --
-	(345.78,206.08) --
-	(346.49,206.33) --
-	(346.80,206.43) --
-	(346.94,206.48) --
-	(347.30,206.60) --
-	(348.63,207.06) --
-	(348.84,207.13) --
-	(349.59,207.39) --
-	(350.01,207.53) --
-	(350.27,207.62) --
-	(350.57,207.73) --
-	(351.61,208.08) --
-	(352.50,208.39) --
-	(354.60,209.11) --
-	(354.77,209.17) --
-	(355.03,209.26) --
-	(355.06,209.27) --
-	(355.38,209.38) --
-	(355.44,209.40) --
-	(355.66,209.47) --
-	(355.69,209.48) --
-	(356.06,209.61) --
-	(356.08,209.62) --
-	(356.57,209.78) --
-	(356.86,209.88) --
-	(356.99,209.93) --
-	(357.04,209.94) --
-	(357.10,209.97) --
-	(357.28,210.03) --
-	(357.68,210.17) --
-	(357.71,210.18) --
-	(358.36,210.40) --
-	(358.45,210.43) --
-	(358.80,210.55) --
-	(359.58,210.82) --
-	(360.14,211.01) --
-	(360.17,211.02) --
-	(360.28,211.06) --
-	(360.68,211.20) --
-	(362.54,211.83) --
-	(362.92,211.96) --
-	(362.99,211.99) --
-	(362.99,211.99) --
-	(363.68,212.22) --
-	(363.71,212.23) --
-	(364.25,212.42) --
-	(364.57,212.53) --
-	(364.77,212.60) --
-	(365.00,212.68) --
-	(365.26,212.76) --
-	(365.84,212.96) --
-	(365.84,212.96) --
-	(365.92,212.99) --
-	(366.04,213.03) --
-	(366.47,213.18) --
-	(367.05,213.38) --
-	(368.20,213.78) --
-	(368.39,213.84) --
-	(368.50,213.88) --
-	(370.21,214.46) --
-	(371.17,214.79) --
-	(371.58,214.94) --
-	(372.02,215.09) --
-	(373.58,215.62) --
-	(376.96,216.78) --
-	(378.52,217.32) --
-	(383.85,219.15) --
-	(384.44,219.35) --
-	(384.92,219.51) --
-	(385.30,219.64) --
-	(385.73,219.79) --
-	(385.96,219.87) --
-	(386.70,220.12) --
-	(386.81,220.16) --
-	(387.17,220.28) --
-	(387.19,220.29) --
-	(387.24,220.31) --
-	(387.39,220.36) --
-	(387.67,220.46) --
-	(388.26,220.66) --
-	(389.16,220.97) --
-	(389.82,221.19) --
-	(390.40,221.39) --
-	(390.44,221.41) --
-	(390.79,221.53) --
-	(391.07,221.62) --
-	(395.16,223.02) --
-	(396.00,223.31) --
-	(396.15,223.37) --
-	(403.52,225.89) --
-	(404.02,226.07);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,105.17) --
+	( 60.61,107.79) --
+	( 64.85,109.25) --
+	( 64.98,109.30) --
+	( 78.30,113.88) --
+	( 86.71,116.78) --
+	( 92.34,118.71) --
+	( 95.59,119.83) --
+	(101.92,122.01) --
+	(110.88,125.09) --
+	(154.64,140.15) --
+	(158.01,141.31) --
+	(171.43,145.93) --
+	(178.49,148.35) --
+	(187.92,151.60) --
+	(192.71,153.25) --
+	(195.62,154.25) --
+	(195.71,154.28) --
+	(196.35,154.50) --
+	(198.04,155.08) --
+	(199.87,155.71) --
+	(204.99,157.47) --
+	(205.19,157.54) --
+	(209.65,159.08) --
+	(211.50,159.71) --
+	(215.87,161.22) --
+	(217.33,161.72) --
+	(217.43,161.75) --
+	(217.68,161.84) --
+	(218.17,162.01) --
+	(220.17,162.70) --
+	(220.33,162.75) --
+	(220.93,162.96) --
+	(221.63,163.20) --
+	(222.58,163.53) --
+	(223.29,163.77) --
+	(223.54,163.86) --
+	(223.59,163.87) --
+	(224.00,164.02) --
+	(229.14,165.78) --
+	(231.15,166.48) --
+	(231.34,166.54) --
+	(232.39,166.90) --
+	(233.34,167.23) --
+	(234.24,167.54) --
+	(235.24,167.88) --
+	(236.22,168.22) --
+	(237.40,168.63) --
+	(237.41,168.63) --
+	(239.29,169.28) --
+	(239.31,169.28) --
+	(240.03,169.53) --
+	(240.80,169.79) --
+	(241.27,169.96) --
+	(241.65,170.09) --
+	(242.95,170.54) --
+	(244.78,171.17) --
+	(248.30,172.38) --
+	(249.74,172.87) --
+	(250.22,173.04) --
+	(250.38,173.09) --
+	(250.69,173.20) --
+	(251.97,173.64) --
+	(252.46,173.81) --
+	(253.69,174.23) --
+	(253.89,174.30) --
+	(254.34,174.45) --
+	(255.73,174.94) --
+	(256.94,175.35) --
+	(258.99,176.06) --
+	(260.08,176.43) --
+	(260.16,176.46) --
+	(261.39,176.88) --
+	(262.57,177.29) --
+	(263.47,177.60) --
+	(264.14,177.83) --
+	(264.43,177.93) --
+	(264.94,178.10) --
+	(265.11,178.16) --
+	(265.48,178.29) --
+	(265.54,178.31) --
+	(266.69,178.71) --
+	(266.70,178.71) --
+	(267.74,179.07) --
+	(267.83,179.10) --
+	(267.95,179.14) --
+	(268.15,179.21) --
+	(268.32,179.26) --
+	(268.51,179.33) --
+	(268.75,179.41) --
+	(269.12,179.54) --
+	(269.30,179.60) --
+	(269.75,179.76) --
+	(269.91,179.81) --
+	(271.51,180.36) --
+	(272.31,180.64) --
+	(272.40,180.67) --
+	(272.91,180.84) --
+	(273.01,180.88) --
+	(273.29,180.98) --
+	(273.48,181.04) --
+	(274.31,181.33) --
+	(274.85,181.51) --
+	(274.88,181.52) --
+	(275.50,181.74) --
+	(276.03,181.92) --
+	(276.14,181.95) --
+	(276.73,182.16) --
+	(276.77,182.17) --
+	(277.28,182.35) --
+	(277.37,182.38) --
+	(278.83,182.88) --
+	(278.93,182.92) --
+	(278.99,182.94) --
+	(279.03,182.95) --
+	(279.36,183.06) --
+	(279.83,183.23) --
+	(279.90,183.25) --
+	(280.21,183.36) --
+	(280.36,183.41) --
+	(280.41,183.43) --
+	(280.47,183.45) --
+	(280.50,183.46) --
+	(280.60,183.49) --
+	(280.63,183.50) --
+	(281.16,183.68) --
+	(281.52,183.81) --
+	(281.60,183.84) --
+	(283.10,184.35) --
+	(283.28,184.41) --
+	(283.34,184.44) --
+	(283.74,184.57) --
+	(283.80,184.59) --
+	(284.26,184.75) --
+	(284.43,184.81) --
+	(284.75,184.92) --
+	(284.80,184.94) --
+	(284.81,184.94) --
+	(284.81,184.94) --
+	(284.84,184.95) --
+	(284.88,184.96) --
+	(285.44,185.16) --
+	(285.67,185.24) --
+	(286.04,185.36) --
+	(286.70,185.59) --
+	(286.95,185.68) --
+	(287.76,185.96) --
+	(288.16,186.09) --
+	(288.45,186.19) --
+	(288.86,186.33) --
+	(289.03,186.39) --
+	(289.13,186.43) --
+	(289.30,186.48) --
+	(289.61,186.59) --
+	(289.71,186.63) --
+	(289.99,186.72) --
+	(290.44,186.88) --
+	(291.29,187.17) --
+	(291.45,187.22) --
+	(291.58,187.27) --
+	(292.20,187.48) --
+	(292.36,187.54) --
+	(292.77,187.68) --
+	(292.78,187.68) --
+	(292.85,187.71) --
+	(292.94,187.74) --
+	(293.49,187.93) --
+	(293.61,187.97) --
+	(293.90,188.07) --
+	(293.94,188.08) --
+	(295.12,188.49) --
+	(295.85,188.74) --
+	(296.61,189.00) --
+	(297.11,189.17) --
+	(297.99,189.47) --
+	(298.09,189.51) --
+	(298.13,189.52) --
+	(298.21,189.55) --
+	(298.45,189.63) --
+	(298.48,189.64) --
+	(298.71,189.72) --
+	(298.89,189.79) --
+	(299.22,189.90) --
+	(300.07,190.19) --
+	(300.69,190.40) --
+	(301.34,190.63) --
+	(301.81,190.79) --
+	(301.86,190.81) --
+	(302.06,190.87) --
+	(302.08,190.88) --
+	(302.20,190.93) --
+	(302.30,190.96) --
+	(302.45,191.01) --
+	(302.52,191.03) --
+	(302.61,191.06) --
+	(302.89,191.16) --
+	(302.93,191.17) --
+	(303.17,191.26) --
+	(304.10,191.58) --
+	(304.31,191.65) --
+	(304.47,191.71) --
+	(304.48,191.71) --
+	(304.60,191.75) --
+	(304.68,191.78) --
+	(305.11,191.93) --
+	(305.28,191.98) --
+	(305.76,192.15) --
+	(305.86,192.18) --
+	(306.15,192.28) --
+	(307.03,192.59) --
+	(307.16,192.63) --
+	(307.37,192.70) --
+	(308.42,193.06) --
+	(308.63,193.14) --
+	(308.79,193.19) --
+	(309.08,193.29) --
+	(309.55,193.45) --
+	(309.72,193.51) --
+	(310.36,193.73) --
+	(310.45,193.76) --
+	(310.80,193.88) --
+	(310.98,193.95) --
+	(311.09,193.98) --
+	(311.49,194.12) --
+	(311.71,194.20) --
+	(311.87,194.25) --
+	(312.39,194.43) --
+	(312.68,194.53) --
+	(312.75,194.55) --
+	(314.09,195.02) --
+	(314.12,195.02) --
+	(314.55,195.17) --
+	(314.84,195.27) --
+	(315.05,195.34) --
+	(315.28,195.42) --
+	(315.54,195.51) --
+	(315.61,195.54) --
+	(315.65,195.55) --
+	(316.29,195.77) --
+	(316.37,195.80) --
+	(316.58,195.87) --
+	(316.61,195.88) --
+	(316.72,195.92) --
+	(317.13,196.06) --
+	(318.60,196.57) --
+	(319.14,196.75) --
+	(320.71,197.29) --
+	(321.34,197.51) --
+	(321.47,197.55) --
+	(322.56,197.93) --
+	(322.64,197.96) --
+	(322.93,198.06) --
+	(323.98,198.42) --
+	(324.06,198.44) --
+	(324.53,198.61) --
+	(324.82,198.71) --
+	(325.46,198.93) --
+	(325.85,199.06) --
+	(325.87,199.07) --
+	(325.91,199.08) --
+	(326.16,199.17) --
+	(326.46,199.27) --
+	(327.01,199.46) --
+	(327.50,199.63) --
+	(327.78,199.72) --
+	(328.37,199.93) --
+	(328.92,200.12) --
+	(330.17,200.55) --
+	(330.38,200.62) --
+	(330.88,200.79) --
+	(333.53,201.71) --
+	(333.56,201.71) --
+	(333.69,201.76) --
+	(333.82,201.80) --
+	(333.83,201.81) --
+	(335.38,202.34) --
+	(335.47,202.37) --
+	(337.65,203.12) --
+	(338.50,203.41) --
+	(338.83,203.53) --
+	(338.87,203.54) --
+	(339.04,203.60) --
+	(339.21,203.66) --
+	(339.40,203.72) --
+	(339.55,203.77) --
+	(339.76,203.85) --
+	(339.84,203.88) --
+	(340.15,203.98) --
+	(340.28,204.03) --
+	(340.65,204.15) --
+	(341.52,204.45) --
+	(342.53,204.80) --
+	(343.79,205.23) --
+	(343.95,205.29) --
+	(345.11,205.69) --
+	(345.20,205.72) --
+	(345.78,205.92) --
+	(346.49,206.16) --
+	(346.80,206.27) --
+	(346.94,206.32) --
+	(347.30,206.44) --
+	(348.63,206.90) --
+	(348.84,206.97) --
+	(349.59,207.23) --
+	(350.01,207.38) --
+	(350.27,207.46) --
+	(350.57,207.57) --
+	(351.61,207.93) --
+	(352.50,208.23) --
+	(354.60,208.95) --
+	(354.77,209.01) --
+	(355.03,209.10) --
+	(355.06,209.11) --
+	(355.38,209.22) --
+	(355.44,209.24) --
+	(355.66,209.32) --
+	(355.69,209.33) --
+	(356.06,209.46) --
+	(356.08,209.46) --
+	(356.57,209.63) --
+	(356.86,209.73) --
+	(356.99,209.78) --
+	(357.04,209.79) --
+	(357.10,209.81) --
+	(357.28,209.88) --
+	(357.68,210.01) --
+	(357.71,210.02) --
+	(358.36,210.25) --
+	(358.45,210.28) --
+	(358.80,210.40) --
+	(359.58,210.67) --
+	(360.14,210.86) --
+	(360.17,210.87) --
+	(360.28,210.91) --
+	(360.68,211.05) --
+	(362.54,211.69) --
+	(362.92,211.82) --
+	(362.99,211.84) --
+	(362.99,211.84) --
+	(363.68,212.08) --
+	(363.71,212.09) --
+	(364.25,212.28) --
+	(364.57,212.39) --
+	(364.77,212.45) --
+	(365.00,212.53) --
+	(365.26,212.62) --
+	(365.84,212.82) --
+	(365.84,212.82) --
+	(365.92,212.85) --
+	(366.04,212.89) --
+	(366.47,213.04) --
+	(367.05,213.24) --
+	(368.20,213.63) --
+	(368.39,213.70) --
+	(368.50,213.74) --
+	(370.21,214.32) --
+	(371.17,214.65) --
+	(371.58,214.80) --
+	(372.02,214.95) --
+	(373.58,215.48) --
+	(376.96,216.65) --
+	(378.52,217.19) --
+	(383.85,219.02) --
+	(384.44,219.22) --
+	(384.92,219.39) --
+	(385.30,219.52) --
+	(385.73,219.66) --
+	(385.96,219.74) --
+	(386.70,220.00) --
+	(386.81,220.04) --
+	(387.17,220.16) --
+	(387.19,220.17) --
+	(387.24,220.18) --
+	(387.39,220.24) --
+	(387.67,220.34) --
+	(388.26,220.54) --
+	(389.16,220.85) --
+	(389.82,221.07) --
+	(390.40,221.27) --
+	(390.44,221.29) --
+	(390.79,221.41) --
+	(391.07,221.50) --
+	(395.16,222.91) --
+	(396.00,223.20) --
+	(396.15,223.25) --
+	(403.52,225.79) --
+	(404.02,225.96);
 \definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}
 
-\path[fill=fillColor,fill opacity=0.30] ( 52.97,165.20) --
-	( 60.61,166.06) --
-	( 64.85,166.50) --
-	( 64.98,166.52) --
-	( 78.30,168.34) --
-	( 86.71,169.62) --
-	( 92.34,170.49) --
-	( 95.59,171.09) --
-	(101.92,171.91) --
-	(110.88,173.03) --
-	(154.64,179.87) --
-	(158.01,180.61) --
-	(171.43,182.79) --
-	(178.49,184.14) --
-	(187.92,186.16) --
-	(192.71,186.96) --
-	(195.62,187.49) --
-	(195.71,187.52) --
-	(196.35,187.67) --
-	(198.04,187.95) --
-	(199.87,188.32) --
-	(204.99,189.26) --
-	(205.19,189.29) --
-	(209.65,190.35) --
-	(211.50,190.74) --
-	(215.87,191.88) --
-	(217.33,192.18) --
-	(217.43,192.18) --
-	(217.68,192.24) --
-	(218.17,192.39) --
-	(220.17,192.85) --
-	(220.33,192.86) --
-	(220.93,193.03) --
-	(221.63,193.24) --
-	(222.58,193.40) --
-	(223.29,193.54) --
-	(223.54,193.60) --
-	(223.59,193.62) --
-	(224.00,193.67) --
-	(229.14,194.98) --
-	(231.15,195.48) --
-	(231.34,195.52) --
-	(232.39,195.71) --
-	(233.34,195.91) --
-	(234.25,196.12) --
-	(235.24,196.41) --
-	(236.22,196.59) --
-	(237.40,196.88) --
-	(237.41,196.88) --
-	(239.29,197.35) --
-	(239.31,197.35) --
-	(240.03,197.54) --
-	(240.80,197.71) --
-	(241.27,197.83) --
-	(241.65,197.94) --
-	(242.95,198.33) --
-	(244.78,198.83) --
-	(248.30,199.74) --
-	(249.74,200.06) --
-	(250.22,200.25) --
-	(250.38,200.30) --
-	(250.69,200.38) --
-	(251.97,200.79) --
-	(252.46,200.89) --
-	(253.69,201.25) --
-	(253.89,201.30) --
-	(254.34,201.47) --
-	(255.74,201.84) --
-	(256.94,202.18) --
-	(258.99,202.81) --
-	(260.08,203.21) --
-	(260.16,203.23) --
-	(261.39,203.62) --
-	(262.57,204.01) --
-	(263.47,204.17) --
-	(264.14,204.36) --
-	(264.43,204.44) --
-	(264.94,204.64) --
-	(265.11,204.71) --
-	(265.48,204.84) --
-	(265.54,204.86) --
-	(266.69,205.27) --
-	(266.70,205.27) --
-	(267.74,205.67) --
-	(267.83,205.69) --
-	(267.95,205.73) --
-	(268.15,205.80) --
-	(268.32,205.86) --
-	(268.51,205.91) --
-	(268.75,206.03) --
-	(269.12,206.13) --
-	(269.30,206.19) --
-	(269.75,206.29) --
-	(269.91,206.34) --
-	(271.51,206.93) --
-	(272.31,207.26) --
-	(272.40,207.29) --
-	(272.91,207.46) --
-	(273.01,207.49) --
-	(273.29,207.60) --
-	(273.48,207.63) --
-	(274.31,207.88) --
-	(274.85,208.05) --
-	(274.88,208.05) --
-	(275.50,208.31) --
-	(276.03,208.51) --
-	(276.14,208.54) --
-	(276.73,208.71) --
-	(276.77,208.72) --
-	(277.28,208.92) --
-	(277.37,208.95) --
-	(278.83,209.44) --
-	(278.93,209.48) --
-	(278.99,209.50) --
-	(279.03,209.51) --
-	(279.36,209.57) --
-	(279.83,209.71) --
-	(279.90,209.72) --
-	(280.21,209.80) --
-	(280.36,209.87) --
-	(280.41,209.89) --
-	(280.47,209.91) --
-	(280.50,209.92) --
-	(280.60,209.95) --
-	(280.63,209.96) --
-	(281.16,210.14) --
-	(281.52,210.28) --
-	(281.60,210.32) --
-	(283.10,210.87) --
-	(283.28,210.96) --
-	(283.34,210.98) --
-	(283.74,211.11) --
-	(283.80,211.13) --
-	(284.26,211.28) --
-	(284.43,211.32) --
-	(284.75,211.44) --
-	(284.80,211.46) --
-	(284.81,211.46) --
-	(284.81,211.46) --
-	(284.84,211.48) --
-	(284.88,211.49) --
-	(285.44,211.69) --
-	(285.67,211.76) --
-	(286.04,211.88) --
-	(286.70,212.11) --
-	(286.95,212.19) --
-	(287.76,212.60) --
-	(288.16,212.75) --
-	(288.45,212.88) --
-	(288.86,212.98) --
-	(289.03,213.01) --
-	(289.13,213.03) --
-	(289.30,213.12) --
-	(289.61,213.30) --
-	(289.71,213.32) --
-	(289.99,213.40) --
-	(290.44,213.53) --
-	(291.29,213.87) --
-	(291.45,213.92) --
-	(291.58,213.96) --
-	(292.20,214.19) --
-	(292.36,214.26) --
-	(292.77,214.38) --
-	(292.78,214.39) --
-	(292.85,214.43) --
-	(292.94,214.45) --
-	(293.49,214.66) --
-	(293.61,214.72) --
-	(293.90,214.85) --
-	(293.94,214.86) --
-	(295.12,215.33) --
-	(295.85,215.63) --
-	(296.61,215.90) --
-	(297.11,216.10) --
-	(297.99,216.47) --
-	(298.09,216.52) --
-	(298.13,216.53) --
-	(298.21,216.57) --
-	(298.45,216.67) --
-	(298.48,216.68) --
-	(298.71,216.78) --
-	(298.89,216.86) --
-	(299.22,217.00) --
-	(300.07,217.37) --
-	(300.69,217.67) --
-	(301.34,217.95) --
-	(301.81,218.15) --
-	(301.86,218.17) --
-	(302.06,218.25) --
-	(302.08,218.25) --
-	(302.20,218.30) --
-	(302.30,218.33) --
-	(302.45,218.39) --
-	(302.52,218.41) --
-	(302.61,218.44) --
-	(302.89,218.54) --
-	(302.93,218.56) --
-	(303.17,218.62) --
-	(304.10,218.98) --
-	(304.31,219.07) --
-	(304.47,219.12) --
-	(304.48,219.12) --
-	(304.60,219.15) --
-	(304.68,219.18) --
-	(305.11,219.34) --
-	(305.28,219.40) --
-	(305.76,219.62) --
-	(305.86,219.66) --
-	(306.15,219.79) --
-	(307.03,220.15) --
-	(307.16,220.21) --
-	(307.37,220.28) --
-	(308.42,220.71) --
-	(308.63,220.77) --
-	(308.79,220.81) --
-	(309.08,220.91) --
-	(309.55,221.07) --
-	(309.72,221.11) --
-	(310.36,221.34) --
-	(310.45,221.38) --
-	(310.80,221.53) --
-	(310.98,221.58) --
-	(311.09,221.61) --
-	(311.49,221.78) --
-	(311.71,221.89) --
-	(311.87,221.97) --
-	(312.39,222.22) --
-	(312.68,222.34) --
-	(312.75,222.36) --
-	(314.09,222.97) --
-	(314.12,222.98) --
-	(314.55,223.10) --
-	(314.84,223.21) --
-	(315.05,223.29) --
-	(315.28,223.38) --
-	(315.54,223.48) --
-	(315.61,223.51) --
-	(315.65,223.53) --
-	(316.29,223.77) --
-	(316.37,223.80) --
-	(316.58,223.88) --
-	(316.61,223.90) --
-	(316.72,223.94) --
-	(317.13,224.10) --
-	(318.60,224.77) --
-	(319.14,224.99) --
-	(320.71,225.74) --
-	(321.34,226.00) --
-	(321.47,226.05) --
-	(322.56,226.60) --
-	(322.64,226.65) --
-	(322.93,226.81) --
-	(323.98,227.18) --
-	(324.06,227.23) --
-	(324.53,227.46) --
-	(324.82,227.58) --
-	(325.46,227.82) --
-	(325.85,227.92) --
-	(325.87,227.93) --
-	(325.91,227.95) --
-	(326.16,228.06) --
-	(326.46,228.20) --
-	(327.01,228.46) --
-	(327.50,228.65) --
-	(327.78,228.76) --
-	(328.37,229.01) --
-	(328.92,229.25) --
-	(330.17,229.78) --
-	(330.38,229.89) --
-	(330.88,230.12) --
-	(333.53,231.30) --
-	(333.56,231.31) --
-	(333.69,231.37) --
-	(333.82,231.43) --
-	(333.83,231.43) --
-	(335.38,232.11) --
-	(335.47,232.16) --
-	(337.65,233.11) --
-	(338.50,233.49) --
-	(338.83,233.64) --
-	(338.87,233.66) --
-	(339.04,233.73) --
-	(339.21,233.80) --
-	(339.40,233.89) --
-	(339.55,233.95) --
-	(339.76,234.05) --
-	(339.84,234.09) --
-	(340.15,234.23) --
-	(340.28,234.29) --
-	(340.65,234.46) --
-	(341.52,234.87) --
-	(342.53,235.38) --
-	(343.79,235.96) --
-	(343.95,236.03) --
-	(345.11,236.65) --
-	(345.20,236.70) --
-	(345.78,236.95) --
-	(346.49,237.30) --
-	(346.80,237.45) --
-	(346.94,237.52) --
-	(347.30,237.70) --
-	(348.63,238.33) --
-	(348.84,238.43) --
-	(349.59,238.82) --
-	(350.01,239.02) --
-	(350.27,239.13) --
-	(350.57,239.26) --
-	(351.61,239.72) --
-	(352.50,240.14) --
-	(354.60,241.18) --
-	(354.77,241.25) --
-	(355.03,241.37) --
-	(355.06,241.39) --
-	(355.38,241.55) --
-	(355.44,241.59) --
-	(355.66,241.70) --
-	(355.69,241.71) --
-	(356.06,241.93) --
-	(356.08,241.93) --
-	(356.57,242.19) --
-	(356.86,242.34) --
-	(356.99,242.41) --
-	(357.04,242.44) --
-	(357.10,242.47) --
-	(357.28,242.56) --
-	(357.68,242.77) --
-	(357.71,242.78) --
-	(358.36,243.06) --
-	(358.45,243.11) --
-	(358.80,243.27) --
-	(359.58,243.64) --
-	(360.14,243.89) --
-	(360.17,243.90) --
-	(360.28,243.94) --
-	(360.68,244.14) --
-	(362.54,245.11) --
-	(362.92,245.32) --
-	(362.99,245.36) --
-	(362.99,245.36) --
-	(363.68,245.73) --
-	(363.71,245.75) --
-	(364.25,246.04) --
-	(364.57,246.19) --
-	(364.77,246.29) --
-	(365.00,246.40) --
-	(365.26,246.54) --
-	(365.84,246.88) --
-	(365.84,246.88) --
-	(365.92,246.92) --
-	(366.04,246.98) --
-	(366.47,247.19) --
-	(367.05,247.46) --
-	(368.20,247.96) --
-	(368.39,248.07) --
-	(368.50,248.14) --
-	(370.21,248.93) --
-	(371.17,249.41) --
-	(371.58,249.67) --
-	(372.02,249.86) --
-	(373.58,250.61) --
-	(376.96,252.31) --
-	(378.52,252.97) --
-	(383.85,255.72) --
-	(384.44,256.00) --
-	(384.92,256.23) --
-	(385.30,256.42) --
-	(385.73,256.63) --
-	(385.96,256.74) --
-	(386.70,257.14) --
-	(386.81,257.19) --
-	(387.17,257.37) --
-	(387.19,257.37) --
-	(387.24,257.39) --
-	(387.39,257.47) --
-	(387.67,257.63) --
-	(388.26,257.95) --
-	(389.16,258.36) --
-	(389.82,258.71) --
-	(390.40,258.98) --
-	(390.44,259.01) --
-	(390.79,259.17) --
-	(391.07,259.30) --
-	(395.16,261.28) --
-	(396.00,261.69) --
-	(396.15,261.76) --
-	(403.52,265.67) --
+\path[fill=fillColor,fill opacity=0.30] ( 52.97,165.07) --
+	( 60.61,166.03) --
+	( 64.85,166.51) --
+	( 64.98,166.54) --
+	( 78.30,168.33) --
+	( 86.71,169.61) --
+	( 92.34,170.44) --
+	( 95.59,171.03) --
+	(101.92,171.81) --
+	(110.88,172.89) --
+	(154.64,180.05) --
+	(158.01,180.45) --
+	(171.43,182.73) --
+	(178.49,184.08) --
+	(187.92,185.93) --
+	(192.71,186.77) --
+	(195.62,187.27) --
+	(195.71,187.28) --
+	(196.35,187.38) --
+	(198.04,187.65) --
+	(199.87,188.05) --
+	(204.99,189.01) --
+	(205.19,189.03) --
+	(209.65,190.06) --
+	(211.50,190.52) --
+	(215.87,191.59) --
+	(217.33,191.90) --
+	(217.43,191.93) --
+	(217.68,191.97) --
+	(218.17,192.07) --
+	(220.17,192.44) --
+	(220.33,192.49) --
+	(220.93,192.59) --
+	(221.63,192.75) --
+	(222.58,192.98) --
+	(223.29,193.13) --
+	(223.54,193.18) --
+	(223.59,193.19) --
+	(224.00,193.30) --
+	(229.14,194.56) --
+	(231.15,194.97) --
+	(231.34,194.99) --
+	(232.39,195.37) --
+	(233.34,195.60) --
+	(234.24,195.69) --
+	(235.24,195.85) --
+	(236.22,196.18) --
+	(237.40,196.49) --
+	(237.41,196.49) --
+	(239.29,197.05) --
+	(239.31,197.06) --
+	(240.03,197.23) --
+	(240.80,197.39) --
+	(241.27,197.46) --
+	(241.65,197.55) --
+	(242.95,197.83) --
+	(244.78,198.38) --
+	(248.30,199.35) --
+	(249.74,199.77) --
+	(250.22,199.91) --
+	(250.38,199.94) --
+	(250.69,200.06) --
+	(251.97,200.42) --
+	(252.46,200.53) --
+	(253.69,200.79) --
+	(253.89,200.86) --
+	(254.34,200.96) --
+	(255.73,201.43) --
+	(256.94,201.82) --
+	(258.99,202.54) --
+	(260.08,202.88) --
+	(260.16,202.90) --
+	(261.39,203.25) --
+	(262.57,203.64) --
+	(263.47,203.91) --
+	(264.14,204.11) --
+	(264.43,204.22) --
+	(264.94,204.38) --
+	(265.11,204.45) --
+	(265.48,204.57) --
+	(265.54,204.59) --
+	(266.69,205.01) --
+	(266.70,205.01) --
+	(267.74,205.35) --
+	(267.83,205.37) --
+	(267.95,205.45) --
+	(268.15,205.52) --
+	(268.32,205.56) --
+	(268.51,205.63) --
+	(268.75,205.74) --
+	(269.12,205.89) --
+	(269.30,205.97) --
+	(269.75,206.12) --
+	(269.91,206.17) --
+	(271.51,206.69) --
+	(272.31,207.01) --
+	(272.40,207.06) --
+	(272.91,207.29) --
+	(273.01,207.33) --
+	(273.29,207.43) --
+	(273.48,207.49) --
+	(274.31,207.72) --
+	(274.85,207.89) --
+	(274.88,207.90) --
+	(275.50,208.11) --
+	(276.03,208.30) --
+	(276.14,208.34) --
+	(276.73,208.55) --
+	(276.77,208.57) --
+	(277.28,208.75) --
+	(277.37,208.78) --
+	(278.83,209.26) --
+	(278.93,209.30) --
+	(278.99,209.33) --
+	(279.03,209.34) --
+	(279.36,209.43) --
+	(279.83,209.54) --
+	(279.90,209.57) --
+	(280.21,209.70) --
+	(280.36,209.75) --
+	(280.41,209.78) --
+	(280.47,209.80) --
+	(280.50,209.81) --
+	(280.60,209.85) --
+	(280.63,209.85) --
+	(281.16,210.05) --
+	(281.52,210.20) --
+	(281.60,210.24) --
+	(283.10,210.77) --
+	(283.28,210.82) --
+	(283.34,210.83) --
+	(283.74,210.94) --
+	(283.80,210.97) --
+	(284.26,211.19) --
+	(284.43,211.24) --
+	(284.75,211.33) --
+	(284.80,211.34) --
+	(284.81,211.34) --
+	(284.81,211.34) --
+	(284.84,211.35) --
+	(284.88,211.37) --
+	(285.44,211.54) --
+	(285.67,211.63) --
+	(286.04,211.78) --
+	(286.70,212.02) --
+	(286.95,212.12) --
+	(287.76,212.51) --
+	(288.16,212.63) --
+	(288.45,212.70) --
+	(288.86,212.81) --
+	(289.03,212.87) --
+	(289.13,212.93) --
+	(289.30,212.99) --
+	(289.61,213.12) --
+	(289.71,213.16) --
+	(289.99,213.26) --
+	(290.44,213.43) --
+	(291.29,213.72) --
+	(291.45,213.79) --
+	(291.58,213.85) --
+	(292.20,214.08) --
+	(292.36,214.13) --
+	(292.77,214.30) --
+	(292.78,214.30) --
+	(292.85,214.32) --
+	(292.94,214.36) --
+	(293.49,214.59) --
+	(293.61,214.64) --
+	(293.90,214.77) --
+	(293.94,214.79) --
+	(295.12,215.21) --
+	(295.85,215.51) --
+	(296.61,215.83) --
+	(297.11,216.04) --
+	(297.99,216.40) --
+	(298.09,216.45) --
+	(298.13,216.47) --
+	(298.21,216.50) --
+	(298.45,216.60) --
+	(298.48,216.61) --
+	(298.71,216.72) --
+	(298.89,216.80) --
+	(299.22,216.90) --
+	(300.07,217.25) --
+	(300.69,217.51) --
+	(301.34,217.77) --
+	(301.81,217.95) --
+	(301.86,217.97) --
+	(302.06,218.06) --
+	(302.08,218.06) --
+	(302.20,218.12) --
+	(302.30,218.16) --
+	(302.45,218.22) --
+	(302.52,218.25) --
+	(302.61,218.29) --
+	(302.89,218.40) --
+	(302.93,218.42) --
+	(303.17,218.52) --
+	(304.10,218.84) --
+	(304.31,218.92) --
+	(304.47,218.97) --
+	(304.48,218.97) --
+	(304.60,219.01) --
+	(304.68,219.04) --
+	(305.11,219.23) --
+	(305.28,219.30) --
+	(305.76,219.46) --
+	(305.86,219.49) --
+	(306.15,219.58) --
+	(307.03,219.96) --
+	(307.16,220.02) --
+	(307.37,220.07) --
+	(308.42,220.47) --
+	(308.63,220.55) --
+	(308.79,220.61) --
+	(309.08,220.73) --
+	(309.55,220.92) --
+	(309.72,220.98) --
+	(310.36,221.22) --
+	(310.45,221.25) --
+	(310.80,221.37) --
+	(310.98,221.46) --
+	(311.09,221.48) --
+	(311.49,221.66) --
+	(311.71,221.78) --
+	(311.87,221.84) --
+	(312.39,222.06) --
+	(312.68,222.19) --
+	(312.75,222.21) --
+	(314.09,222.81) --
+	(314.12,222.82) --
+	(314.55,223.00) --
+	(314.84,223.11) --
+	(315.05,223.18) --
+	(315.28,223.25) --
+	(315.54,223.34) --
+	(315.61,223.36) --
+	(315.65,223.37) --
+	(316.29,223.65) --
+	(316.37,223.69) --
+	(316.58,223.78) --
+	(316.61,223.79) --
+	(316.72,223.82) --
+	(317.13,223.99) --
+	(318.60,224.64) --
+	(319.14,224.92) --
+	(320.71,225.62) --
+	(321.34,225.89) --
+	(321.47,225.94) --
+	(322.56,226.40) --
+	(322.64,226.44) --
+	(322.93,226.57) --
+	(323.98,227.03) --
+	(324.06,227.07) --
+	(324.53,227.28) --
+	(324.82,227.40) --
+	(325.46,227.67) --
+	(325.85,227.84) --
+	(325.87,227.86) --
+	(325.91,227.88) --
+	(326.16,227.97) --
+	(326.46,228.10) --
+	(327.01,228.35) --
+	(327.50,228.52) --
+	(327.78,228.67) --
+	(328.37,228.96) --
+	(328.92,229.20) --
+	(330.17,229.74) --
+	(330.38,229.85) --
+	(330.88,230.08) --
+	(333.53,231.22) --
+	(333.56,231.23) --
+	(333.69,231.29) --
+	(333.82,231.35) --
+	(333.83,231.35) --
+	(335.38,232.05) --
+	(335.47,232.09) --
+	(337.65,233.08) --
+	(338.50,233.45) --
+	(338.83,233.59) --
+	(338.87,233.61) --
+	(339.04,233.68) --
+	(339.21,233.75) --
+	(339.40,233.82) --
+	(339.55,233.88) --
+	(339.76,233.97) --
+	(339.84,234.00) --
+	(340.15,234.13) --
+	(340.28,234.18) --
+	(340.65,234.38) --
+	(341.52,234.84) --
+	(342.53,235.30) --
+	(343.79,235.93) --
+	(343.95,236.02) --
+	(345.11,236.58) --
+	(345.20,236.63) --
+	(345.78,236.90) --
+	(346.49,237.20) --
+	(346.80,237.34) --
+	(346.94,237.42) --
+	(347.30,237.59) --
+	(348.63,238.22) --
+	(348.84,238.32) --
+	(349.59,238.65) --
+	(350.01,238.84) --
+	(350.27,238.96) --
+	(350.57,239.10) --
+	(351.61,239.64) --
+	(352.50,240.05) --
+	(354.60,241.08) --
+	(354.77,241.16) --
+	(355.03,241.32) --
+	(355.06,241.34) --
+	(355.38,241.48) --
+	(355.44,241.51) --
+	(355.66,241.60) --
+	(355.69,241.61) --
+	(356.06,241.77) --
+	(356.08,241.77) --
+	(356.57,242.01) --
+	(356.86,242.17) --
+	(356.99,242.24) --
+	(357.04,242.27) --
+	(357.10,242.29) --
+	(357.28,242.37) --
+	(357.68,242.57) --
+	(357.71,242.59) --
+	(358.36,242.94) --
+	(358.45,242.99) --
+	(358.80,243.19) --
+	(359.58,243.57) --
+	(360.14,243.86) --
+	(360.17,243.87) --
+	(360.28,243.93) --
+	(360.68,244.11) --
+	(362.54,244.96) --
+	(362.92,245.17) --
+	(362.99,245.21) --
+	(362.99,245.21) --
+	(363.68,245.56) --
+	(363.71,245.57) --
+	(364.25,245.86) --
+	(364.57,246.01) --
+	(364.77,246.11) --
+	(365.00,246.26) --
+	(365.26,246.42) --
+	(365.84,246.74) --
+	(365.84,246.74) --
+	(365.92,246.77) --
+	(366.04,246.82) --
+	(366.47,247.02) --
+	(367.05,247.32) --
+	(368.20,247.89) --
+	(368.39,247.96) --
+	(368.50,248.02) --
+	(370.21,248.86) --
+	(371.17,249.37) --
+	(371.58,249.56) --
+	(372.02,249.77) --
+	(373.58,250.63) --
+	(376.96,252.21) --
+	(378.52,252.92) --
+	(383.85,255.70) --
+	(384.44,256.07) --
+	(384.92,256.30) --
+	(385.30,256.48) --
+	(385.73,256.69) --
+	(385.96,256.80) --
+	(386.70,257.17) --
+	(386.81,257.23) --
+	(387.17,257.43) --
+	(387.19,257.44) --
+	(387.24,257.46) --
+	(387.39,257.54) --
+	(387.67,257.70) --
+	(388.26,258.02) --
+	(389.16,258.43) --
+	(389.82,258.73) --
+	(390.40,259.04) --
+	(390.44,259.06) --
+	(390.79,259.24) --
+	(391.07,259.36) --
+	(395.16,261.33) --
+	(396.00,261.76) --
+	(396.15,261.83) --
+	(403.52,265.76) --
 	(404.02,265.99) --
-	(404.02,186.16) --
-	(403.52,186.07) --
-	(396.15,184.62) --
-	(396.00,184.56) --
-	(395.16,184.43) --
-	(391.07,183.78) --
-	(390.79,183.76) --
-	(390.44,183.72) --
-	(390.40,183.71) --
-	(389.82,183.64) --
-	(389.16,183.56) --
+	(404.02,186.34) --
+	(403.52,186.23) --
+	(396.15,184.68) --
+	(396.00,184.66) --
+	(395.16,184.56) --
+	(391.07,183.90) --
+	(390.79,183.85) --
+	(390.44,183.80) --
+	(390.40,183.79) --
+	(389.82,183.70) --
+	(389.16,183.57) --
 	(388.26,183.43) --
-	(387.67,183.32) --
-	(387.39,183.25) --
-	(387.24,183.21) --
-	(387.19,183.20) --
-	(387.17,183.20) --
-	(386.81,183.11) --
-	(386.70,183.09) --
-	(385.96,182.98) --
-	(385.73,182.95) --
-	(385.30,182.87) --
-	(384.92,182.82) --
-	(384.44,182.79) --
-	(383.85,182.69) --
-	(378.52,181.63) --
-	(376.96,181.35) --
-	(373.58,180.87) --
-	(372.02,180.66) --
-	(371.58,180.64) --
-	(371.17,180.60) --
-	(370.21,180.44) --
-	(368.50,180.16) --
-	(368.39,180.14) --
-	(368.20,180.08) --
-	(367.05,179.83) --
-	(366.47,179.68) --
-	(366.04,179.56) --
+	(387.67,183.36) --
+	(387.39,183.28) --
+	(387.24,183.25) --
+	(387.19,183.24) --
+	(387.17,183.24) --
+	(386.81,183.18) --
+	(386.70,183.16) --
+	(385.96,183.06) --
+	(385.73,183.03) --
+	(385.30,182.96) --
+	(384.92,182.88) --
+	(384.44,182.77) --
+	(383.85,182.65) --
+	(378.52,181.64) --
+	(376.96,181.44) --
+	(373.58,180.91) --
+	(372.02,180.68) --
+	(371.58,180.65) --
+	(371.17,180.59) --
+	(370.21,180.45) --
+	(368.50,180.08) --
+	(368.39,180.06) --
+	(368.20,180.02) --
+	(367.05,179.77) --
+	(366.47,179.65) --
+	(366.04,179.54) --
 	(365.92,179.53) --
-	(365.84,179.51) --
-	(365.84,179.51) --
-	(365.26,179.35) --
-	(365.00,179.28) --
-	(364.77,179.25) --
-	(364.57,179.24) --
-	(364.25,179.17) --
-	(363.71,179.04) --
-	(363.68,179.03) --
-	(362.99,178.85) --
-	(362.99,178.85) --
-	(362.92,178.84) --
-	(362.54,178.74) --
+	(365.84,179.52) --
+	(365.84,179.52) --
+	(365.26,179.44) --
+	(365.00,179.39) --
+	(364.77,179.33) --
+	(364.57,179.26) --
+	(364.25,179.16) --
+	(363.71,179.01) --
+	(363.68,179.01) --
+	(362.99,178.88) --
+	(362.99,178.88) --
+	(362.92,178.86) --
+	(362.54,178.77) --
 	(360.68,178.40) --
-	(360.28,178.30) --
-	(360.17,178.31) --
-	(360.14,178.31) --
-	(359.58,178.27) --
-	(358.80,178.08) --
-	(358.45,178.01) --
-	(358.36,177.98) --
-	(357.71,177.80) --
-	(357.68,177.80) --
-	(357.28,177.74) --
-	(357.10,177.72) --
-	(357.04,177.72) --
-	(356.99,177.71) --
-	(356.86,177.70) --
-	(356.57,177.64) --
-	(356.08,177.49) --
-	(356.06,177.49) --
-	(355.69,177.37) --
-	(355.66,177.36) --
-	(355.44,177.32) --
-	(355.38,177.31) --
-	(355.06,177.26) --
-	(355.03,177.25) --
-	(354.77,177.22) --
-	(354.60,177.19) --
-	(352.50,176.92) --
-	(351.61,176.70) --
-	(350.57,176.49) --
-	(350.27,176.47) --
-	(350.01,176.37) --
-	(349.59,176.23) --
-	(348.84,176.03) --
-	(348.63,175.98) --
-	(347.30,175.74) --
-	(346.94,175.67) --
-	(346.80,175.64) --
-	(346.49,175.53) --
-	(345.78,175.33) --
-	(345.20,175.23) --
-	(345.11,175.20) --
-	(343.95,174.89) --
-	(343.79,174.84) --
-	(342.53,174.62) --
-	(341.52,174.45) --
-	(340.65,174.27) --
-	(340.28,174.16) --
-	(340.15,174.10) --
-	(339.84,174.03) --
-	(339.76,174.02) --
-	(339.55,173.99) --
-	(339.40,173.93) --
-	(339.21,173.87) --
-	(339.04,173.82) --
-	(338.87,173.77) --
-	(338.83,173.76) --
-	(338.50,173.69) --
-	(337.65,173.44) --
-	(335.47,172.96) --
-	(335.38,172.95) --
-	(333.83,172.52) --
-	(333.82,172.52) --
-	(333.69,172.48) --
-	(333.56,172.45) --
-	(333.53,172.44) --
-	(330.88,171.81) --
-	(330.38,171.72) --
-	(330.17,171.68) --
-	(328.92,171.37) --
-	(328.37,171.15) --
-	(327.78,170.98) --
-	(327.50,170.92) --
-	(327.01,170.77) --
-	(326.46,170.62) --
-	(326.16,170.57) --
-	(325.91,170.51) --
-	(325.87,170.51) --
-	(325.85,170.51) --
-	(325.46,170.40) --
-	(324.82,170.21) --
-	(324.53,170.21) --
-	(324.06,170.15) --
-	(323.98,170.13) --
-	(322.93,169.85) --
-	(322.64,169.82) --
-	(322.56,169.82) --
-	(321.47,169.46) --
-	(321.34,169.40) --
-	(320.71,169.24) --
-	(319.14,168.74) --
-	(318.60,168.64) --
-	(317.13,168.18) --
-	(316.72,168.05) --
-	(316.61,168.01) --
-	(316.58,168.00) --
-	(316.37,167.93) --
-	(316.29,167.90) --
-	(315.65,167.68) --
-	(315.61,167.67) --
-	(315.54,167.65) --
-	(315.28,167.58) --
-	(315.05,167.51) --
-	(314.84,167.42) --
-	(314.55,167.33) --
-	(314.12,167.22) --
-	(314.09,167.21) --
-	(312.75,166.87) --
-	(312.68,166.86) --
-	(312.39,166.79) --
-	(311.87,166.57) --
-	(311.71,166.51) --
-	(311.49,166.45) --
-	(311.09,166.35) --
-	(310.98,166.33) --
-	(310.80,166.29) --
-	(310.45,166.23) --
-	(310.36,166.21) --
-	(309.72,166.00) --
-	(309.55,165.96) --
-	(309.08,165.82) --
-	(308.79,165.72) --
-	(308.63,165.67) --
-	(308.42,165.62) --
-	(307.37,165.33) --
-	(307.16,165.25) --
-	(307.03,165.22) --
-	(306.15,165.04) --
-	(305.86,164.98) --
-	(305.76,164.96) --
-	(305.28,164.84) --
-	(305.11,164.79) --
-	(304.68,164.71) --
-	(304.60,164.69) --
-	(304.48,164.65) --
-	(304.47,164.64) --
-	(304.31,164.58) --
-	(304.10,164.53) --
-	(303.17,164.22) --
-	(302.93,164.15) --
-	(302.89,164.14) --
-	(302.61,164.07) --
-	(302.52,164.04) --
-	(302.45,164.03) --
-	(302.30,164.00) --
-	(302.20,163.98) --
-	(302.08,163.95) --
-	(302.06,163.95) --
-	(301.86,163.90) --
-	(301.81,163.89) --
-	(301.34,163.78) --
-	(300.69,163.54) --
-	(300.07,163.35) --
-	(299.22,163.00) --
-	(298.89,162.91) --
-	(298.71,162.85) --
-	(298.48,162.77) --
-	(298.45,162.76) --
-	(298.21,162.69) --
-	(298.13,162.66) --
-	(298.09,162.65) --
-	(297.99,162.62) --
-	(297.11,162.35) --
-	(296.61,162.22) --
-	(295.85,161.97) --
-	(295.12,161.73) --
-	(293.94,161.38) --
-	(293.90,161.37) --
-	(293.61,161.27) --
-	(293.49,161.22) --
-	(292.94,161.03) --
-	(292.85,161.01) --
-	(292.78,160.99) --
-	(292.77,160.98) --
-	(292.36,160.87) --
-	(292.20,160.82) --
-	(291.58,160.61) --
-	(291.45,160.57) --
-	(291.29,160.52) --
-	(290.44,160.26) --
-	(289.99,160.13) --
-	(289.71,160.04) --
-	(289.61,160.00) --
-	(289.30,159.87) --
-	(289.13,159.80) --
-	(289.03,159.75) --
-	(288.86,159.69) --
-	(288.45,159.56) --
-	(288.16,159.43) --
-	(287.76,159.26) --
-	(286.95,158.94) --
-	(286.70,158.84) --
-	(286.04,158.62) --
-	(285.67,158.49) --
-	(285.44,158.44) --
-	(284.88,158.24) --
-	(284.84,158.23) --
-	(284.81,158.22) --
-	(284.81,158.22) --
-	(284.80,158.21) --
-	(284.75,158.20) --
-	(284.43,158.12) --
-	(284.26,158.06) --
-	(283.80,157.92) --
-	(283.74,157.91) --
-	(283.34,157.81) --
-	(283.28,157.79) --
-	(283.10,157.72) --
-	(281.60,157.19) --
-	(281.52,157.15) --
-	(281.16,157.04) --
-	(280.63,156.85) --
-	(280.60,156.83) --
-	(280.50,156.79) --
-	(280.47,156.78) --
-	(280.41,156.75) --
-	(280.36,156.73) --
-	(280.21,156.68) --
-	(279.90,156.59) --
-	(279.83,156.58) --
-	(279.36,156.45) --
-	(279.03,156.32) --
-	(278.99,156.30) --
-	(278.93,156.27) --
-	(278.83,156.20) --
-	(277.37,155.69) --
-	(277.28,155.66) --
-	(276.77,155.47) --
-	(276.73,155.45) --
-	(276.14,155.25) --
-	(276.03,155.23) --
-	(275.50,155.09) --
-	(274.88,154.85) --
-	(274.85,154.84) --
-	(274.31,154.63) --
-	(273.48,154.33) --
-	(273.29,154.26) --
-	(273.01,154.14) --
-	(272.91,154.08) --
-	(272.40,153.94) --
-	(272.31,153.91) --
-	(271.51,153.68) --
-	(269.91,153.18) --
-	(269.75,153.12) --
-	(269.30,153.01) --
-	(269.12,152.95) --
-	(268.75,152.83) --
-	(268.51,152.72) --
-	(268.32,152.61) --
-	(268.15,152.54) --
-	(267.95,152.45) --
-	(267.83,152.40) --
-	(267.74,152.36) --
-	(266.70,151.94) --
-	(266.69,151.93) --
-	(265.54,151.50) --
-	(265.48,151.48) --
-	(265.11,151.39) --
-	(264.94,151.31) --
-	(264.43,151.11) --
-	(264.14,151.03) --
-	(263.47,150.81) --
-	(262.57,150.47) --
-	(261.39,150.00) --
-	(260.16,149.54) --
-	(260.08,149.51) --
-	(258.99,149.05) --
-	(256.94,148.31) --
-	(255.74,147.96) --
-	(254.34,147.35) --
-	(253.89,147.15) --
-	(253.69,147.06) --
-	(252.46,146.62) --
-	(251.97,146.47) --
-	(250.69,145.91) --
-	(250.38,145.79) --
-	(250.22,145.74) --
-	(249.74,145.63) --
-	(248.30,145.02) --
-	(244.78,143.52) --
-	(242.95,142.71) --
-	(241.65,142.20) --
-	(241.27,142.05) --
-	(240.80,141.82) --
-	(240.03,141.56) --
-	(239.31,141.28) --
-	(239.29,141.27) --
-	(237.41,140.47) --
-	(237.40,140.46) --
-	(236.22,140.02) --
-	(235.24,139.60) --
-	(234.25,139.14) --
-	(233.34,138.79) --
-	(232.39,138.25) --
-	(231.34,137.82) --
-	(231.15,137.77) --
-	(229.14,136.99) --
-	(224.00,134.73) --
-	(223.59,134.56) --
-	(223.54,134.54) --
-	(223.29,134.42) --
-	(222.58,134.07) --
-	(221.63,133.64) --
-	(220.93,133.31) --
-	(220.33,132.98) --
-	(220.17,132.91) --
-	(218.17,132.08) --
-	(217.68,131.82) --
-	(217.43,131.70) --
-	(217.33,131.66) --
-	(215.87,130.99) --
-	(211.50,128.79) --
-	(209.65,127.84) --
-	(205.19,125.79) --
-	(204.99,125.71) --
-	(199.87,123.16) --
-	(198.04,122.29) --
-	(196.35,121.40) --
-	(195.71,121.10) --
-	(195.62,121.07) --
-	(192.71,119.57) --
-	(187.92,117.14) --
-	(178.49,112.49) --
-	(171.43,108.90) --
-	(158.01,101.95) --
-	(154.64,100.20) --
-	(110.88, 76.90) --
-	(101.92, 72.02) --
-	( 95.59, 68.42) --
-	( 92.34, 66.68) --
-	( 86.71, 63.70) --
-	( 78.30, 59.08) --
-	( 64.98, 51.79) --
-	( 64.85, 51.71) --
-	( 60.61, 49.49) --
+	(360.28,178.34) --
+	(360.17,178.33) --
+	(360.14,178.33) --
+	(359.58,178.20) --
+	(358.80,177.96) --
+	(358.45,177.91) --
+	(358.36,177.90) --
+	(357.71,177.77) --
+	(357.68,177.77) --
+	(357.28,177.69) --
+	(357.10,177.64) --
+	(357.04,177.62) --
+	(356.99,177.60) --
+	(356.86,177.57) --
+	(356.57,177.50) --
+	(356.08,177.44) --
+	(356.06,177.44) --
+	(355.69,177.39) --
+	(355.66,177.39) --
+	(355.44,177.35) --
+	(355.38,177.33) --
+	(355.06,177.25) --
+	(355.03,177.24) --
+	(354.77,177.18) --
+	(354.60,177.14) --
+	(352.50,176.83) --
+	(351.61,176.61) --
+	(350.57,176.40) --
+	(350.27,176.31) --
+	(350.01,176.25) --
+	(349.59,176.10) --
+	(348.84,175.91) --
+	(348.63,175.90) --
+	(347.30,175.60) --
+	(346.94,175.50) --
+	(346.80,175.46) --
+	(346.49,175.36) --
+	(345.78,175.18) --
+	(345.20,175.07) --
+	(345.11,175.06) --
+	(343.95,174.79) --
+	(343.79,174.78) --
+	(342.53,174.52) --
+	(341.52,174.36) --
+	(340.65,174.13) --
+	(340.28,174.04) --
+	(340.15,174.01) --
+	(339.84,173.92) --
+	(339.76,173.90) --
+	(339.55,173.83) --
+	(339.40,173.79) --
+	(339.21,173.73) --
+	(339.04,173.70) --
+	(338.87,173.64) --
+	(338.83,173.63) --
+	(338.50,173.54) --
+	(337.65,173.34) --
+	(335.47,172.82) --
+	(335.38,172.79) --
+	(333.83,172.41) --
+	(333.82,172.41) --
+	(333.69,172.37) --
+	(333.56,172.35) --
+	(333.53,172.35) --
+	(330.88,171.78) --
+	(330.38,171.66) --
+	(330.17,171.61) --
+	(328.92,171.27) --
+	(328.37,171.13) --
+	(327.78,170.94) --
+	(327.50,170.85) --
+	(327.01,170.66) --
+	(326.46,170.48) --
+	(326.16,170.42) --
+	(325.91,170.35) --
+	(325.87,170.35) --
+	(325.85,170.34) --
+	(325.46,170.28) --
+	(324.82,170.17) --
+	(324.53,170.12) --
+	(324.06,170.03) --
+	(323.98,170.02) --
+	(322.93,169.78) --
+	(322.64,169.70) --
+	(322.56,169.67) --
+	(321.47,169.34) --
+	(321.34,169.32) --
+	(320.71,169.14) --
+	(319.14,168.58) --
+	(318.60,168.45) --
+	(317.13,168.04) --
+	(316.72,167.88) --
+	(316.61,167.84) --
+	(316.58,167.83) --
+	(316.37,167.76) --
+	(316.29,167.72) --
+	(315.65,167.51) --
+	(315.61,167.51) --
+	(315.54,167.50) --
+	(315.28,167.39) --
+	(315.05,167.32) --
+	(314.84,167.28) --
+	(314.55,167.23) --
+	(314.12,167.07) --
+	(314.09,167.07) --
+	(312.75,166.67) --
+	(312.68,166.66) --
+	(312.39,166.57) --
+	(311.87,166.38) --
+	(311.71,166.32) --
+	(311.49,166.25) --
+	(311.09,166.15) --
+	(310.98,166.13) --
+	(310.80,166.08) --
+	(310.45,166.02) --
+	(310.36,166.01) --
+	(309.72,165.79) --
+	(309.55,165.75) --
+	(309.08,165.61) --
+	(308.79,165.54) --
+	(308.63,165.48) --
+	(308.42,165.44) --
+	(307.37,165.12) --
+	(307.16,165.08) --
+	(307.03,165.02) --
+	(306.15,164.82) --
+	(305.86,164.72) --
+	(305.76,164.70) --
+	(305.28,164.59) --
+	(305.11,164.57) --
+	(304.68,164.44) --
+	(304.60,164.42) --
+	(304.48,164.39) --
+	(304.47,164.39) --
+	(304.31,164.34) --
+	(304.10,164.27) --
+	(303.17,163.99) --
+	(302.93,163.92) --
+	(302.89,163.90) --
+	(302.61,163.82) --
+	(302.52,163.80) --
+	(302.45,163.78) --
+	(302.30,163.73) --
+	(302.20,163.70) --
+	(302.08,163.66) --
+	(302.06,163.66) --
+	(301.86,163.61) --
+	(301.81,163.60) --
+	(301.34,163.43) --
+	(300.69,163.25) --
+	(300.07,163.04) --
+	(299.22,162.75) --
+	(298.89,162.65) --
+	(298.71,162.61) --
+	(298.48,162.53) --
+	(298.45,162.52) --
+	(298.21,162.43) --
+	(298.13,162.41) --
+	(298.09,162.40) --
+	(297.99,162.37) --
+	(297.11,162.13) --
+	(296.61,161.93) --
+	(295.85,161.71) --
+	(295.12,161.51) --
+	(293.94,161.16) --
+	(293.90,161.15) --
+	(293.61,161.05) --
+	(293.49,161.00) --
+	(292.94,160.81) --
+	(292.85,160.79) --
+	(292.78,160.77) --
+	(292.77,160.76) --
+	(292.36,160.65) --
+	(292.20,160.60) --
+	(291.58,160.39) --
+	(291.45,160.35) --
+	(291.29,160.30) --
+	(290.44,160.04) --
+	(289.99,159.91) --
+	(289.71,159.82) --
+	(289.61,159.78) --
+	(289.30,159.65) --
+	(289.13,159.58) --
+	(289.03,159.53) --
+	(288.86,159.47) --
+	(288.45,159.34) --
+	(288.16,159.21) --
+	(287.76,159.03) --
+	(286.95,158.71) --
+	(286.70,158.61) --
+	(286.04,158.39) --
+	(285.67,158.25) --
+	(285.44,158.18) --
+	(284.88,157.97) --
+	(284.84,157.96) --
+	(284.81,157.95) --
+	(284.81,157.95) --
+	(284.80,157.95) --
+	(284.75,157.94) --
+	(284.43,157.86) --
+	(284.26,157.81) --
+	(283.80,157.65) --
+	(283.74,157.63) --
+	(283.34,157.47) --
+	(283.28,157.45) --
+	(283.10,157.38) --
+	(281.60,156.86) --
+	(281.52,156.84) --
+	(281.16,156.72) --
+	(280.63,156.53) --
+	(280.60,156.52) --
+	(280.50,156.49) --
+	(280.47,156.48) --
+	(280.41,156.46) --
+	(280.36,156.44) --
+	(280.21,156.38) --
+	(279.90,156.27) --
+	(279.83,156.25) --
+	(279.36,156.10) --
+	(279.03,155.99) --
+	(278.99,155.97) --
+	(278.93,155.95) --
+	(278.83,155.92) --
+	(277.37,155.41) --
+	(277.28,155.37) --
+	(276.77,155.18) --
+	(276.73,155.17) --
+	(276.14,154.91) --
+	(276.03,154.89) --
+	(275.50,154.75) --
+	(274.88,154.53) --
+	(274.85,154.52) --
+	(274.31,154.33) --
+	(273.48,153.97) --
+	(273.29,153.90) --
+	(273.01,153.83) --
+	(272.91,153.80) --
+	(272.40,153.63) --
+	(272.31,153.60) --
+	(271.51,153.32) --
+	(269.91,152.88) --
+	(269.75,152.84) --
+	(269.30,152.67) --
+	(269.12,152.60) --
+	(268.75,152.46) --
+	(268.51,152.38) --
+	(268.32,152.31) --
+	(268.15,152.25) --
+	(267.95,152.15) --
+	(267.83,152.10) --
+	(267.74,152.07) --
+	(266.70,151.65) --
+	(266.69,151.65) --
+	(265.54,151.21) --
+	(265.48,151.19) --
+	(265.11,151.03) --
+	(264.94,150.97) --
+	(264.43,150.80) --
+	(264.14,150.73) --
+	(263.47,150.51) --
+	(262.57,150.18) --
+	(261.39,149.72) --
+	(260.16,149.25) --
+	(260.08,149.22) --
+	(258.99,148.77) --
+	(256.94,147.97) --
+	(255.73,147.55) --
+	(254.34,147.05) --
+	(253.89,146.87) --
+	(253.69,146.77) --
+	(252.46,146.32) --
+	(251.97,146.14) --
+	(250.69,145.55) --
+	(250.38,145.47) --
+	(250.22,145.41) --
+	(249.74,145.23) --
+	(248.30,144.72) --
+	(244.78,143.23) --
+	(242.95,142.41) --
+	(241.65,141.90) --
+	(241.27,141.77) --
+	(240.80,141.53) --
+	(240.03,141.24) --
+	(239.31,140.92) --
+	(239.29,140.91) --
+	(237.41,140.17) --
+	(237.40,140.16) --
+	(236.22,139.67) --
+	(235.24,139.19) --
+	(234.24,138.83) --
+	(233.34,138.46) --
+	(232.39,137.97) --
+	(231.34,137.53) --
+	(231.15,137.48) --
+	(229.14,136.70) --
+	(224.00,134.47) --
+	(223.59,134.28) --
+	(223.54,134.27) --
+	(223.29,134.18) --
+	(222.58,133.90) --
+	(221.63,133.38) --
+	(220.93,133.02) --
+	(220.33,132.73) --
+	(220.17,132.66) --
+	(218.17,131.78) --
+	(217.68,131.60) --
+	(217.43,131.51) --
+	(217.33,131.46) --
+	(215.87,130.73) --
+	(211.50,128.68) --
+	(209.65,127.80) --
+	(205.19,125.59) --
+	(204.99,125.51) --
+	(199.87,122.96) --
+	(198.04,122.14) --
+	(196.35,121.30) --
+	(195.71,120.97) --
+	(195.62,120.92) --
+	(192.71,119.45) --
+	(187.92,116.99) --
+	(178.49,112.56) --
+	(171.43,108.91) --
+	(158.01,101.79) --
+	(154.64,100.08) --
+	(110.88, 76.82) --
+	(101.92, 71.87) --
+	( 95.59, 68.45) --
+	( 92.34, 66.61) --
+	( 86.71, 63.49) --
+	( 78.30, 58.97) --
+	( 64.98, 51.78) --
+	( 64.85, 51.70) --
+	( 60.61, 49.34) --
 	( 52.97, 45.08) --
@@
 
-\path[fill=fillColor,fill opacity=0.50] ( 52.97,155.78) --
-	( 60.61,157.02) --
-	( 64.85,157.72) --
-	( 64.98,157.76) --
-	( 78.30,159.89) --
-	( 86.71,161.16) --
-	( 92.34,162.02) --
-	( 95.59,162.58) --
-	(101.92,163.75) --
-	(110.88,165.37) --
-	(154.64,173.25) --
-	(158.01,173.83) --
-	(171.43,176.44) --
-	(178.49,177.89) --
-	(187.92,179.93) --
-	(192.71,180.94) --
-	(195.62,181.57) --
-	(195.71,181.60) --
-	(196.35,181.78) --
-	(198.04,182.20) --
-	(199.87,182.59) --
-	(204.99,183.69) --
-	(205.19,183.74) --
-	(209.65,184.88) --
-	(211.50,185.32) --
-	(215.87,186.31) --
-	(217.33,186.70) --
-	(217.43,186.73) --
-	(217.68,186.79) --
-	(218.17,186.95) --
-	(220.17,187.43) --
-	(220.33,187.47) --
-	(220.93,187.59) --
-	(221.63,187.78) --
-	(222.58,188.03) --
-	(223.29,188.16) --
-	(223.54,188.25) --
-	(223.59,188.27) --
-	(224.00,188.40) --
-	(229.14,189.71) --
-	(231.15,190.26) --
-	(231.34,190.31) --
-	(232.39,190.62) --
-	(233.34,190.89) --
-	(234.25,191.19) --
-	(235.24,191.47) --
-	(236.22,191.82) --
-	(237.40,192.18) --
-	(237.41,192.18) --
-	(239.29,192.72) --
-	(239.31,192.73) --
-	(240.03,192.94) --
-	(240.80,193.15) --
-	(241.27,193.33) --
-	(241.65,193.46) --
-	(242.95,193.75) --
-	(244.78,194.25) --
-	(248.30,195.33) --
-	(249.74,195.76) --
-	(250.22,195.94) --
-	(250.38,196.01) --
-	(250.69,196.16) --
-	(251.97,196.55) --
-	(252.46,196.68) --
-	(253.69,197.01) --
-	(253.89,197.07) --
-	(254.34,197.22) --
-	(255.74,197.69) --
-	(256.94,198.07) --
-	(258.99,198.62) --
-	(260.08,198.96) --
-	(260.16,198.98) --
-	(261.39,199.44) --
-	(262.57,199.78) --
-	(263.47,200.03) --
-	(264.14,200.24) --
-	(264.43,200.36) --
-	(264.94,200.54) --
-	(265.11,200.57) --
-	(265.48,200.70) --
-	(265.54,200.72) --
-	(266.69,201.09) --
-	(266.70,201.09) --
-	(267.74,201.45) --
-	(267.83,201.46) --
-	(267.95,201.52) --
-	(268.15,201.60) --
-	(268.32,201.64) --
-	(268.51,201.73) --
-	(268.75,201.81) --
-	(269.12,201.95) --
-	(269.30,202.00) --
-	(269.75,202.18) --
-	(269.91,202.21) --
-	(271.51,202.79) --
-	(272.31,203.06) --
-	(272.40,203.09) --
-	(272.91,203.23) --
-	(273.01,203.25) --
-	(273.29,203.34) --
-	(273.48,203.41) --
-	(274.31,203.68) --
-	(274.85,203.89) --
-	(274.88,203.90) --
-	(275.50,204.08) --
-	(276.03,204.23) --
-	(276.14,204.27) --
-	(276.73,204.46) --
-	(276.77,204.47) --
-	(277.28,204.64) --
-	(277.37,204.66) --
-	(278.83,205.17) --
-	(278.93,205.20) --
-	(278.99,205.23) --
-	(279.03,205.25) --
-	(279.36,205.31) --
-	(279.83,205.47) --
-	(279.90,205.50) --
-	(280.21,205.61) --
-	(280.36,205.65) --
-	(280.41,205.68) --
-	(280.47,205.71) --
-	(280.50,205.71) --
-	(280.60,205.74) --
-	(280.63,205.75) --
-	(281.16,205.91) --
-	(281.52,206.01) --
-	(281.60,206.03) --
-	(283.10,206.58) --
-	(283.28,206.66) --
-	(283.34,206.68) --
-	(283.74,206.84) --
-	(283.80,206.86) --
-	(284.26,207.01) --
-	(284.43,207.07) --
-	(284.75,207.16) --
-	(284.80,207.18) --
-	(284.81,207.18) --
-	(284.81,207.18) --
-	(284.84,207.19) --
-	(284.88,207.20) --
-	(285.44,207.45) --
-	(285.67,207.54) --
-	(286.04,207.68) --
-	(286.70,207.89) --
-	(286.95,207.97) --
-	(287.76,208.27) --
-	(288.16,208.43) --
-	(288.45,208.57) --
-	(288.86,208.73) --
-	(289.03,208.78) --
-	(289.13,208.82) --
-	(289.30,208.87) --
-	(289.61,208.98) --
-	(289.71,209.02) --
-	(289.99,209.12) --
-	(290.44,209.29) --
-	(291.29,209.59) --
-	(291.45,209.64) --
-	(291.58,209.68) --
-	(292.20,209.90) --
-	(292.36,209.95) --
-	(292.77,210.11) --
-	(292.78,210.12) --
-	(292.85,210.14) --
-	(292.94,210.16) --
-	(293.49,210.35) --
-	(293.61,210.39) --
-	(293.90,210.51) --
-	(293.94,210.53) --
-	(295.12,210.90) --
-	(295.85,211.14) --
-	(296.61,211.47) --
-	(297.11,211.69) --
-	(297.99,212.07) --
-	(298.09,212.10) --
-	(298.13,212.11) --
-	(298.21,212.12) --
-	(298.45,212.21) --
-	(298.48,212.23) --
-	(298.71,212.30) --
-	(298.89,212.38) --
-	(299.22,212.51) --
-	(300.07,212.87) --
-	(300.69,213.09) --
-	(301.34,213.35) --
-	(301.81,213.52) --
-	(301.86,213.54) --
-	(302.06,213.61) --
-	(302.08,213.62) --
-	(302.20,213.66) --
-	(302.30,213.71) --
-	(302.45,213.79) --
-	(302.52,213.81) --
-	(302.61,213.85) --
-	(302.89,213.96) --
-	(302.93,213.97) --
-	(303.17,214.04) --
-	(304.10,214.40) --
-	(304.31,214.48) --
-	(304.47,214.53) --
-	(304.48,214.53) --
-	(304.60,214.58) --
-	(304.68,214.61) --
-	(305.11,214.78) --
-	(305.28,214.85) --
-	(305.76,215.07) --
-	(305.86,215.12) --
-	(306.15,215.24) --
-	(307.03,215.53) --
-	(307.16,215.60) --
-	(307.37,215.70) --
-	(308.42,216.07) --
-	(308.63,216.18) --
-	(308.79,216.26) --
-	(309.08,216.38) --
-	(309.55,216.59) --
-	(309.72,216.66) --
-	(310.36,216.92) --
-	(310.45,216.96) --
-	(310.80,217.15) --
-	(310.98,217.23) --
-	(311.09,217.27) --
-	(311.49,217.42) --
-	(311.71,217.50) --
-	(311.87,217.56) --
-	(312.39,217.84) --
-	(312.68,217.99) --
-	(312.75,218.02) --
-	(314.09,218.56) --
-	(314.12,218.57) --
-	(314.55,218.71) --
-	(314.84,218.84) --
-	(315.05,218.90) --
-	(315.28,218.98) --
-	(315.54,219.09) --
-	(315.61,219.12) --
-	(315.65,219.13) --
-	(316.29,219.37) --
-	(316.37,219.39) --
-	(316.58,219.47) --
-	(316.61,219.48) --
-	(316.72,219.52) --
-	(317.13,219.68) --
-	(318.60,220.33) --
-	(319.14,220.56) --
-	(320.71,221.16) --
-	(321.34,221.42) --
-	(321.47,221.48) --
-	(322.56,221.95) --
-	(322.64,221.98) --
-	(322.93,222.10) --
-	(323.98,222.52) --
-	(324.06,222.56) --
-	(324.53,222.78) --
-	(324.82,222.91) --
-	(325.46,223.17) --
-	(325.85,223.33) --
-	(325.87,223.34) --
-	(325.91,223.34) --
-	(326.16,223.46) --
-	(326.46,223.57) --
-	(327.01,223.82) --
-	(327.50,224.06) --
-	(327.78,224.16) --
-	(328.37,224.39) --
-	(328.92,224.61) --
-	(330.17,225.15) --
-	(330.38,225.24) --
-	(330.88,225.42) --
-	(333.53,226.62) --
-	(333.56,226.63) --
-	(333.69,226.70) --
-	(333.82,226.78) --
-	(333.83,226.78) --
-	(335.38,227.53) --
-	(335.47,227.58) --
-	(337.65,228.52) --
-	(338.50,228.87) --
-	(338.83,228.96) --
-	(338.87,228.99) --
-	(339.04,229.08) --
-	(339.21,229.15) --
-	(339.40,229.23) --
-	(339.55,229.29) --
-	(339.76,229.37) --
-	(339.84,229.40) --
-	(340.15,229.53) --
-	(340.28,229.58) --
-	(340.65,229.71) --
-	(341.52,230.07) --
-	(342.53,230.56) --
-	(343.79,231.08) --
-	(343.95,231.15) --
-	(345.11,231.69) --
-	(345.20,231.73) --
-	(345.78,231.99) --
-	(346.49,232.31) --
-	(346.80,232.47) --
-	(346.94,232.52) --
-	(347.30,232.67) --
-	(348.63,233.25) --
-	(348.84,233.35) --
-	(349.59,233.76) --
-	(350.01,233.97) --
-	(350.27,234.09) --
-	(350.57,234.23) --
-	(351.61,234.73) --
-	(352.50,235.16) --
-	(354.60,236.10) --
-	(354.77,236.18) --
-	(355.03,236.30) --
-	(355.06,236.31) --
-	(355.38,236.46) --
-	(355.44,236.49) --
-	(355.66,236.61) --
-	(355.69,236.61) --
-	(356.06,236.78) --
-	(356.08,236.79) --
-	(356.57,237.02) --
-	(356.86,237.14) --
-	(356.99,237.20) --
-	(357.04,237.22) --
-	(357.10,237.25) --
-	(357.28,237.33) --
-	(357.68,237.52) --
-	(357.71,237.53) --
-	(358.36,237.85) --
-	(358.45,237.89) --
-	(358.80,238.04) --
-	(359.58,238.38) --
-	(360.14,238.61) --
-	(360.17,238.62) --
-	(360.28,238.68) --
-	(360.68,238.85) --
-	(362.54,239.69) --
-	(362.92,239.87) --
-	(362.99,239.91) --
-	(362.99,239.91) --
-	(363.68,240.21) --
-	(363.71,240.22) --
-	(364.25,240.52) --
-	(364.57,240.68) --
-	(364.77,240.77) --
-	(365.00,240.87) --
-	(365.26,241.04) --
-	(365.84,241.33) --
-	(365.84,241.33) --
-	(365.92,241.37) --
-	(366.04,241.42) --
-	(366.47,241.62) --
-	(367.05,241.89) --
-	(368.20,242.45) --
-	(368.39,242.54) --
-	(368.50,242.59) --
-	(370.21,243.39) --
-	(371.17,243.81) --
-	(371.58,244.00) --
-	(372.02,244.21) --
-	(373.58,244.87) --
-	(376.96,246.54) --
-	(378.52,247.26) --
-	(383.85,249.83) --
-	(384.44,250.15) --
-	(384.92,250.40) --
-	(385.30,250.56) --
-	(385.73,250.74) --
-	(385.96,250.84) --
-	(386.70,251.22) --
-	(386.81,251.27) --
-	(387.17,251.44) --
-	(387.19,251.44) --
-	(387.24,251.46) --
-	(387.39,251.54) --
-	(387.67,251.67) --
-	(388.26,251.97) --
-	(389.16,252.36) --
-	(389.82,252.64) --
-	(390.40,252.95) --
-	(390.44,252.98) --
-	(390.79,253.21) --
+\path[fill=fillColor,fill opacity=0.50] ( 52.97,155.19) --
+	( 60.61,156.53) --
+	( 64.85,157.27) --
+	( 64.98,157.28) --
+	( 78.30,159.47) --
+	( 86.71,160.71) --
+	( 92.34,161.58) --
+	( 95.59,162.05) --
+	(101.92,163.22) --
+	(110.88,164.79) --
+	(154.64,172.89) --
+	(158.01,173.52) --
+	(171.43,176.11) --
+	(178.49,177.51) --
+	(187.92,179.51) --
+	(192.71,180.54) --
+	(195.62,181.28) --
+	(195.71,181.30) --
+	(196.35,181.45) --
+	(198.04,181.86) --
+	(199.87,182.28) --
+	(204.99,183.41) --
+	(205.19,183.47) --
+	(209.65,184.61) --
+	(211.50,185.09) --
+	(215.87,186.10) --
+	(217.33,186.45) --
+	(217.43,186.49) --
+	(217.68,186.54) --
+	(218.17,186.65) --
+	(220.17,187.17) --
+	(220.33,187.22) --
+	(220.93,187.38) --
+	(221.63,187.54) --
+	(222.58,187.83) --
+	(223.29,188.00) --
+	(223.54,188.05) --
+	(223.59,188.07) --
+	(224.00,188.19) --
+	(229.14,189.51) --
+	(231.15,190.06) --
+	(231.34,190.12) --
+	(232.39,190.40) --
+	(233.34,190.68) --
+	(234.24,191.01) --
+	(235.24,191.26) --
+	(236.22,191.57) --
+	(237.40,191.97) --
+	(237.41,191.97) --
+	(239.29,192.53) --
+	(239.31,192.53) --
+	(240.03,192.72) --
+	(240.80,192.93) --
+	(241.27,193.06) --
+	(241.65,193.15) --
+	(242.95,193.53) --
+	(244.78,194.03) --
+	(248.30,195.14) --
+	(249.74,195.57) --
+	(250.22,195.74) --
+	(250.38,195.79) --
+	(250.69,195.89) --
+	(251.97,196.35) --
+	(252.46,196.50) --
+	(253.69,196.89) --
+	(253.89,196.94) --
+	(254.34,197.06) --
+	(255.73,197.56) --
+	(256.94,197.95) --
+	(258.99,198.48) --
+	(260.08,198.81) --
+	(260.16,198.84) --
+	(261.39,199.27) --
+	(262.57,199.62) --
+	(263.47,199.90) --
+	(264.14,200.12) --
+	(264.43,200.22) --
+	(264.94,200.38) --
+	(265.11,200.45) --
+	(265.48,200.56) --
+	(265.54,200.57) --
+	(266.69,200.88) --
+	(266.70,200.88) --
+	(267.74,201.28) --
+	(267.83,201.30) --
+	(267.95,201.35) --
+	(268.15,201.41) --
+	(268.32,201.47) --
+	(268.51,201.54) --
+	(268.75,201.61) --
+	(269.12,201.74) --
+	(269.30,201.81) --
+	(269.75,201.95) --
+	(269.91,202.03) --
+	(271.51,202.58) --
+	(272.31,202.84) --
+	(272.40,202.88) --
+	(272.91,203.02) --
+	(273.01,203.06) --
+	(273.29,203.17) --
+	(273.48,203.20) --
+	(274.31,203.44) --
+	(274.85,203.62) --
+	(274.88,203.63) --
+	(275.50,203.81) --
+	(276.03,203.99) --
+	(276.14,204.04) --
+	(276.73,204.19) --
+	(276.77,204.20) --
+	(277.28,204.39) --
+	(277.37,204.42) --
+	(278.83,204.90) --
+	(278.93,204.94) --
+	(278.99,204.95) --
+	(279.03,204.97) --
+	(279.36,205.12) --
+	(279.83,205.26) --
+	(279.90,205.28) --
+	(280.21,205.37) --
+	(280.36,205.42) --
+	(280.41,205.43) --
+	(280.47,205.44) --
+	(280.50,205.45) --
+	(280.60,205.49) --
+	(280.63,205.50) --
+	(281.16,205.65) --
+	(281.52,205.76) --
+	(281.60,205.78) --
+	(283.10,206.25) --
+	(283.28,206.33) --
+	(283.34,206.35) --
+	(283.74,206.50) --
+	(283.80,206.52) --
+	(284.26,206.69) --
+	(284.43,206.76) --
+	(284.75,206.88) --
+	(284.80,206.90) --
+	(284.81,206.91) --
+	(284.81,206.91) --
+	(284.84,206.92) --
+	(284.88,206.93) --
+	(285.44,207.14) --
+	(285.67,207.22) --
+	(286.04,207.36) --
+	(286.70,207.63) --
+	(286.95,207.73) --
+	(287.76,208.02) --
+	(288.16,208.16) --
+	(288.45,208.28) --
+	(288.86,208.45) --
+	(289.03,208.52) --
+	(289.13,208.56) --
+	(289.30,208.64) --
+	(289.61,208.76) --
+	(289.71,208.80) --
+	(289.99,208.88) --
+	(290.44,209.04) --
+	(291.29,209.36) --
+	(291.45,209.42) --
+	(291.58,209.46) --
+	(292.20,209.69) --
+	(292.36,209.73) --
+	(292.77,209.90) --
+	(292.78,209.91) --
+	(292.85,209.93) --
+	(292.94,209.95) --
+	(293.49,210.13) --
+	(293.61,210.18) --
+	(293.90,210.31) --
+	(293.94,210.32) --
+	(295.12,210.69) --
+	(295.85,210.96) --
+	(296.61,211.26) --
+	(297.11,211.43) --
+	(297.99,211.77) --
+	(298.09,211.82) --
+	(298.13,211.84) --
+	(298.21,211.88) --
+	(298.45,211.97) --
+	(298.48,211.98) --
+	(298.71,212.08) --
+	(298.89,212.18) --
+	(299.22,212.26) --
+	(300.07,212.54) --
+	(300.69,212.82) --
+	(301.34,213.11) --
+	(301.81,213.30) --
+	(301.86,213.32) --
+	(302.06,213.44) --
+	(302.08,213.45) --
+	(302.20,213.50) --
+	(302.30,213.52) --
+	(302.45,213.59) --
+	(302.52,213.63) --
+	(302.61,213.67) --
+	(302.89,213.80) --
+	(302.93,213.81) --
+	(303.17,213.89) --
+	(304.10,214.24) --
+	(304.31,214.32) --
+	(304.47,214.39) --
+	(304.48,214.39) --
+	(304.60,214.44) --
+	(304.68,214.47) --
+	(305.11,214.62) --
+	(305.28,214.68) --
+	(305.76,214.84) --
+	(305.86,214.87) --
+	(306.15,214.99) --
+	(307.03,215.33) --
+	(307.16,215.39) --
+	(307.37,215.47) --
+	(308.42,215.91) --
+	(308.63,216.00) --
+	(308.79,216.07) --
+	(309.08,216.15) --
+	(309.55,216.36) --
+	(309.72,216.43) --
+	(310.36,216.68) --
+	(310.45,216.72) --
+	(310.80,216.85) --
+	(310.98,216.92) --
+	(311.09,216.97) --
+	(311.49,217.14) --
+	(311.71,217.26) --
+	(311.87,217.33) --
+	(312.39,217.54) --
+	(312.68,217.63) --
+	(312.75,217.66) --
+	(314.09,218.31) --
+	(314.12,218.32) --
+	(314.55,218.48) --
+	(314.84,218.60) --
+	(315.05,218.68) --
+	(315.28,218.77) --
+	(315.54,218.83) --
+	(315.61,218.85) --
+	(315.65,218.87) --
+	(316.29,219.12) --
+	(316.37,219.15) --
+	(316.58,219.26) --
+	(316.61,219.28) --
+	(316.72,219.32) --
+	(317.13,219.49) --
+	(318.60,220.09) --
+	(319.14,220.29) --
+	(320.71,220.94) --
+	(321.34,221.16) --
+	(321.47,221.23) --
+	(322.56,221.66) --
+	(322.64,221.71) --
+	(322.93,221.87) --
+	(323.98,222.34) --
+	(324.06,222.38) --
+	(324.53,222.58) --
+	(324.82,222.69) --
+	(325.46,222.96) --
+	(325.85,223.17) --
+	(325.87,223.18) --
+	(325.91,223.20) --
+	(326.16,223.30) --
+	(326.46,223.44) --
+	(327.01,223.67) --
+	(327.50,223.87) --
+	(327.78,223.98) --
+	(328.37,224.21) --
+	(328.92,224.41) --
+	(330.17,224.96) --
+	(330.38,225.06) --
+	(330.88,225.26) --
+	(333.53,226.46) --
+	(333.56,226.47) --
+	(333.69,226.53) --
+	(333.82,226.59) --
+	(333.83,226.59) --
+	(335.38,227.23) --
+	(335.47,227.26) --
+	(337.65,228.26) --
+	(338.50,228.58) --
+	(338.83,228.72) --
+	(338.87,228.74) --
+	(339.04,228.81) --
+	(339.21,228.91) --
+	(339.40,228.99) --
+	(339.55,229.06) --
+	(339.76,229.11) --
+	(339.84,229.13) --
+	(340.15,229.30) --
+	(340.28,229.35) --
+	(340.65,229.49) --
+	(341.52,229.90) --
+	(342.53,230.36) --
+	(343.79,230.93) --
+	(343.95,231.01) --
+	(345.11,231.48) --
+	(345.20,231.51) --
+	(345.78,231.75) --
+	(346.49,232.11) --
+	(346.80,232.22) --
+	(346.94,232.30) --
+	(347.30,232.45) --
+	(348.63,233.08) --
+	(348.84,233.17) --
+	(349.59,233.49) --
+	(350.01,233.69) --
+	(350.27,233.84) --
+	(350.57,233.99) --
+	(351.61,234.45) --
+	(352.50,234.88) --
+	(354.60,235.89) --
+	(354.77,235.97) --
+	(355.03,236.10) --
+	(355.06,236.11) --
+	(355.38,236.26) --
+	(355.44,236.29) --
+	(355.66,236.39) --
+	(355.69,236.41) --
+	(356.06,236.58) --
+	(356.08,236.59) --
+	(356.57,236.82) --
+	(356.86,236.97) --
+	(356.99,237.03) --
+	(357.04,237.05) --
+	(357.10,237.08) --
+	(357.28,237.18) --
+	(357.68,237.39) --
+	(357.71,237.41) --
+	(358.36,237.73) --
+	(358.45,237.77) --
+	(358.80,237.91) --
+	(359.58,238.25) --
+	(360.14,238.49) --
+	(360.17,238.49) --
+	(360.28,238.54) --
+	(360.68,238.74) --
+	(362.54,239.57) --
+	(362.92,239.73) --
+	(362.99,239.76) --
+	(362.99,239.76) --
+	(363.68,240.09) --
+	(363.71,240.11) --
+	(364.25,240.39) --
+	(364.57,240.53) --
+	(364.77,240.61) --
+	(365.00,240.72) --
+	(365.26,240.83) --
+	(365.84,241.13) --
+	(365.84,241.13) --
+	(365.92,241.18) --
+	(366.04,241.25) --
+	(366.47,241.48) --
+	(367.05,241.72) --
+	(368.20,242.22) --
+	(368.39,242.31) --
+	(368.50,242.36) --
+	(370.21,243.12) --
+	(371.17,243.56) --
+	(371.58,243.77) --
+	(372.02,244.00) --
+	(373.58,244.77) --
+	(376.96,246.43) --
+	(378.52,247.22) --
+	(383.85,249.72) --
+	(384.44,250.00) --
+	(384.92,250.25) --
+	(385.30,250.43) --
+	(385.73,250.63) --
+	(385.96,250.75) --
+	(386.70,251.19) --
+	(386.81,251.26) --
+	(387.17,251.47) --
+	(387.19,251.47) --
+	(387.24,251.49) --
+	(387.39,251.56) --
+	(387.67,251.69) --
+	(388.26,251.93) --
+	(389.16,252.31) --
+	(389.82,252.63) --
+	(390.40,252.99) --
+	(390.44,253.01) --
+	(390.79,253.23) --
 	(391.07,253.39) --
-	(395.16,255.52) --
-	(396.00,255.92) --
-	(396.15,255.99) --
-	(403.52,259.54) --
-	(404.02,259.83) --
-	(404.02,193.21) --
-	(403.52,193.10) --
-	(396.15,191.59) --
-	(396.00,191.58) --
-	(395.16,191.49) --
-	(391.07,190.75) --
-	(390.79,190.69) --
-	(390.44,190.64) --
-	(390.40,190.63) --
+	(395.16,255.39) --
+	(396.00,255.83) --
+	(396.15,255.90) --
+	(403.52,259.58) --
+	(404.02,259.80) --
+	(404.02,193.19) --
+	(403.52,193.11) --
+	(396.15,191.61) --
+	(396.00,191.61) --
+	(395.16,191.48) --
+	(391.07,190.82) --
+	(390.79,190.75) --
+	(390.44,190.67) --
+	(390.40,190.66) --
 	(389.82,190.53) --
-	(389.16,190.43) --
-	(388.26,190.20) --
+	(389.16,190.35) --
+	(388.26,190.22) --
 	(387.67,190.10) --
 	(387.39,190.05) --
-	(387.24,190.01) --
-	(387.19,190.01) --
+	(387.24,190.02) --
+	(387.19,190.00) --
 	(387.17,190.00) --
-	(386.81,189.94) --
-	(386.70,189.92) --
-	(385.96,189.70) --
-	(385.73,189.67) --
-	(385.30,189.58) --
-	(384.92,189.52) --
-	(384.44,189.44) --
-	(383.85,189.36) --
-	(378.52,187.97) --
-	(376.96,187.68) --
-	(373.58,186.94) --
-	(372.02,186.66) --
-	(371.58,186.58) --
-	(371.17,186.48) --
-	(370.21,186.18) --
-	(368.50,185.79) --
-	(368.39,185.78) --
-	(368.20,185.73) --
-	(367.05,185.54) --
-	(366.47,185.42) --
-	(366.04,185.30) --
-	(365.92,185.27) --
-	(365.84,185.25) --
-	(365.84,185.25) --
-	(365.26,185.12) --
-	(365.00,185.06) --
-	(364.77,185.00) --
-	(364.57,184.94) --
-	(364.25,184.87) --
-	(363.71,184.72) --
-	(363.68,184.71) --
-	(362.99,184.56) --
-	(362.99,184.56) --
-	(362.92,184.54) --
-	(362.54,184.46) --
-	(360.68,184.05) --
-	(360.28,183.92) --
-	(360.17,183.88) --
-	(360.14,183.88) --
-	(359.58,183.76) --
-	(358.80,183.59) --
-	(358.45,183.50) --
-	(358.36,183.48) --
-	(357.71,183.31) --
-	(357.68,183.31) --
-	(357.28,183.23) --
-	(357.10,183.18) --
-	(357.04,183.16) --
-	(356.99,183.15) --
-	(356.86,183.10) --
-	(356.57,183.03) --
-	(356.08,182.90) --
-	(356.06,182.90) --
-	(355.69,182.80) --
-	(355.66,182.80) --
-	(355.44,182.75) --
-	(355.38,182.73) --
-	(355.06,182.65) --
-	(355.03,182.64) --
-	(354.77,182.59) --
-	(354.60,182.56) --
-	(352.50,182.02) --
-	(351.61,181.81) --
-	(350.57,181.53) --
-	(350.27,181.44) --
-	(350.01,181.39) --
-	(349.59,181.29) --
-	(348.84,181.08) --
-	(348.63,181.04) --
-	(347.30,180.74) --
-	(346.94,180.63) --
-	(346.80,180.60) --
-	(346.49,180.52) --
-	(345.78,180.31) --
-	(345.20,180.18) --
-	(345.11,180.16) --
-	(343.95,179.88) --
-	(343.79,179.84) --
-	(342.53,179.55) --
-	(341.52,179.33) --
-	(340.65,179.17) --
-	(340.28,179.02) --
-	(340.15,178.96) --
-	(339.84,178.86) --
+	(386.81,189.88) --
+	(386.70,189.84) --
+	(385.96,189.65) --
+	(385.73,189.61) --
+	(385.30,189.54) --
+	(384.92,189.44) --
+	(384.44,189.37) --
+	(383.85,189.24) --
+	(378.52,187.98) --
+	(376.96,187.66) --
+	(373.58,186.93) --
+	(372.02,186.65) --
+	(371.58,186.49) --
+	(371.17,186.38) --
+	(370.21,186.10) --
+	(368.50,185.76) --
+	(368.39,185.75) --
+	(368.20,185.70) --
+	(367.05,185.49) --
+	(366.47,185.33) --
+	(366.04,185.27) --
+	(365.92,185.25) --
+	(365.84,185.23) --
+	(365.84,185.23) --
+	(365.26,185.08) --
+	(365.00,185.01) --
+	(364.77,184.98) --
+	(364.57,184.96) --
+	(364.25,184.88) --
+	(363.71,184.76) --
+	(363.68,184.76) --
+	(362.99,184.59) --
+	(362.99,184.59) --
+	(362.92,184.58) --
+	(362.54,184.47) --
+	(360.68,184.03) --
+	(360.28,183.93) --
+	(360.17,183.89) --
+	(360.14,183.89) --
+	(359.58,183.75) --
+	(358.80,183.55) --
+	(358.45,183.44) --
+	(358.36,183.41) --
+	(357.71,183.25) --
+	(357.68,183.25) --
+	(357.28,183.16) --
+	(357.10,183.11) --
+	(357.04,183.09) --
+	(356.99,183.08) --
+	(356.86,183.03) --
+	(356.57,182.97) --
+	(356.08,182.88) --
+	(356.06,182.87) --
+	(355.69,182.77) --
+	(355.66,182.76) --
+	(355.44,182.71) --
+	(355.38,182.69) --
+	(355.06,182.60) --
+	(355.03,182.58) --
+	(354.77,182.52) --
+	(354.60,182.49) --
+	(352.50,182.01) --
+	(351.61,181.76) --
+	(350.57,181.44) --
+	(350.27,181.37) --
+	(350.01,181.30) --
+	(349.59,181.21) --
+	(348.84,181.06) --
+	(348.63,181.03) --
+	(347.30,180.67) --
+	(346.94,180.58) --
+	(346.80,180.53) --
+	(346.49,180.45) --
+	(345.78,180.29) --
+	(345.20,180.15) --
+	(345.11,180.12) --
+	(343.95,179.83) --
+	(343.79,179.81) --
+	(342.53,179.51) --
+	(341.52,179.27) --
+	(340.65,179.03) --
+	(340.28,178.93) --
+	(340.15,178.90) --
+	(339.84,178.84) --
 	(339.76,178.82) --
-	(339.55,178.78) --
-	(339.40,178.76) --
-	(339.21,178.74) --
-	(339.04,178.70) --
-	(338.87,178.68) --
-	(338.83,178.66) --
-	(338.50,178.58) --
-	(337.65,178.29) --
-	(335.47,177.71) --
-	(335.38,177.68) --
-	(333.83,177.24) --
-	(333.82,177.24) --
-	(333.69,177.20) --
-	(333.56,177.17) --
-	(333.53,177.16) --
-	(330.88,176.48) --
-	(330.38,176.35) --
-	(330.17,176.29) --
-	(328.92,176.00) --
-	(328.37,175.84) --
-	(327.78,175.64) --
-	(327.50,175.55) --
-	(327.01,175.42) --
-	(326.46,175.32) --
-	(326.16,175.25) --
-	(325.91,175.20) --
-	(325.87,175.20) --
-	(325.85,175.19) --
-	(325.46,175.13) --
-	(324.82,174.98) --
-	(324.53,174.93) --
-	(324.06,174.82) --
-	(323.98,174.80) --
-	(322.93,174.54) --
-	(322.64,174.46) --
-	(322.56,174.44) --
-	(321.47,174.10) --
-	(321.34,174.07) --
-	(320.71,173.87) --
-	(319.14,173.48) --
-	(318.60,173.34) --
-	(317.13,172.94) --
-	(316.72,172.82) --
-	(316.61,172.81) --
-	(316.58,172.80) --
-	(316.37,172.74) --
-	(316.29,172.72) --
-	(315.65,172.55) --
-	(315.61,172.53) --
-	(315.54,172.52) --
-	(315.28,172.44) --
-	(315.05,172.37) --
-	(314.84,172.32) --
-	(314.55,172.24) --
-	(314.12,172.13) --
-	(314.09,172.13) --
-	(312.75,171.77) --
-	(312.68,171.75) --
-	(312.39,171.66) --
-	(311.87,171.50) --
-	(311.71,171.46) --
-	(311.49,171.39) --
-	(311.09,171.28) --
-	(310.98,171.25) --
-	(310.80,171.20) --
-	(310.45,171.10) --
-	(310.36,171.07) --
-	(309.72,170.92) --
-	(309.55,170.87) --
-	(309.08,170.76) --
-	(308.79,170.69) --
-	(308.63,170.64) --
-	(308.42,170.58) --
-	(307.37,170.23) --
-	(307.16,170.16) --
-	(307.03,170.09) --
-	(306.15,169.83) --
-	(305.86,169.74) --
-	(305.76,169.71) --
-	(305.28,169.58) --
-	(305.11,169.54) --
-	(304.68,169.40) --
-	(304.60,169.37) --
-	(304.48,169.34) --
-	(304.47,169.33) --
-	(304.31,169.29) --
-	(304.10,169.23) --
-	(303.17,168.95) --
-	(302.93,168.88) --
-	(302.89,168.88) --
-	(302.61,168.80) --
-	(302.52,168.79) --
-	(302.45,168.78) --
-	(302.30,168.73) --
-	(302.20,168.71) --
-	(302.08,168.67) --
-	(302.06,168.66) --
-	(301.86,168.62) --
-	(301.81,168.60) --
-	(301.34,168.41) --
-	(300.69,168.22) --
-	(300.07,168.01) --
-	(299.22,167.81) --
-	(298.89,167.74) --
-	(298.71,167.68) --
-	(298.48,167.60) --
-	(298.45,167.59) --
-	(298.21,167.50) --
-	(298.13,167.47) --
-	(298.09,167.46) --
-	(297.99,167.43) --
-	(297.11,167.14) --
-	(296.61,167.00) --
-	(295.85,166.72) --
-	(295.12,166.43) --
-	(293.94,166.08) --
-	(293.90,166.07) --
-	(293.61,165.97) --
-	(293.49,165.93) --
-	(292.94,165.77) --
-	(292.85,165.76) --
-	(292.78,165.72) --
-	(292.77,165.72) --
-	(292.36,165.59) --
-	(292.20,165.54) --
-	(291.58,165.36) --
-	(291.45,165.31) --
-	(291.29,165.25) --
-	(290.44,164.93) --
-	(289.99,164.78) --
-	(289.71,164.71) --
-	(289.61,164.68) --
-	(289.30,164.60) --
-	(289.13,164.54) --
-	(289.03,164.51) --
-	(288.86,164.44) --
-	(288.45,164.32) --
-	(288.16,164.21) --
-	(287.76,164.11) --
-	(286.95,163.86) --
-	(286.70,163.79) --
-	(286.04,163.59) --
-	(285.67,163.45) --
-	(285.44,163.36) --
-	(284.88,163.17) --
-	(284.84,163.16) --
-	(284.81,163.14) --
-	(284.81,163.14) --
-	(284.80,163.14) --
-	(284.75,163.11) --
-	(284.43,163.01) --
-	(284.26,162.95) --
-	(283.80,162.82) --
-	(283.74,162.80) --
-	(283.34,162.65) --
-	(283.28,162.64) --
-	(283.10,162.60) --
-	(281.60,162.07) --
-	(281.52,162.04) --
-	(281.16,161.89) --
-	(280.63,161.70) --
-	(280.60,161.69) --
-	(280.50,161.65) --
-	(280.47,161.64) --
-	(280.41,161.61) --
-	(280.36,161.59) --
-	(280.21,161.53) --
-	(279.90,161.42) --
-	(279.83,161.40) --
-	(279.36,161.22) --
-	(279.03,161.12) --
-	(278.99,161.10) --
-	(278.93,161.08) --
-	(278.83,161.05) --
-	(277.37,160.51) --
-	(277.28,160.48) --
-	(276.77,160.29) --
-	(276.73,160.28) --
-	(276.14,160.03) --
-	(276.03,159.99) --
-	(275.50,159.78) --
-	(274.88,159.56) --
-	(274.85,159.55) --
-	(274.31,159.34) --
-	(273.48,159.10) --
-	(273.29,159.00) --
-	(273.01,158.91) --
-	(272.91,158.87) --
-	(272.40,158.63) --
-	(272.31,158.61) --
-	(271.51,158.38) --
-	(269.91,157.84) --
-	(269.75,157.78) --
-	(269.30,157.63) --
-	(269.12,157.57) --
-	(268.75,157.44) --
-	(268.51,157.36) --
-	(268.32,157.28) --
-	(268.15,157.20) --
-	(267.95,157.14) --
-	(267.83,157.09) --
-	(267.74,157.07) --
-	(266.70,156.71) --
-	(266.69,156.71) --
-	(265.54,156.24) --
-	(265.48,156.21) --
-	(265.11,156.07) --
-	(264.94,156.00) --
-	(264.43,155.81) --
-	(264.14,155.71) --
-	(263.47,155.47) --
-	(262.57,155.16) --
-	(261.39,154.71) --
-	(260.16,154.24) --
-	(260.08,154.22) --
-	(258.99,153.78) --
-	(256.94,152.92) --
-	(255.74,152.43) --
-	(254.34,151.90) --
-	(253.89,151.74) --
-	(253.69,151.68) --
-	(252.46,151.14) --
-	(251.97,150.97) --
-	(250.69,150.46) --
-	(250.38,150.35) --
-	(250.22,150.29) --
-	(249.74,150.09) --
-	(248.30,149.50) --
-	(244.78,148.02) --
-	(242.95,147.32) --
-	(241.65,146.80) --
-	(241.27,146.62) --
-	(240.80,146.42) --
-	(240.03,146.15) --
-	(239.31,145.84) --
-	(239.29,145.83) --
-	(237.41,145.07) --
-	(237.40,145.07) --
-	(236.22,144.55) --
-	(235.24,144.17) --
-	(234.25,143.77) --
-	(233.34,143.45) --
-	(232.39,143.03) --
-	(231.34,142.62) --
-	(231.15,142.56) --
-	(229.14,141.64) --
-	(224.00,139.28) --
-	(223.59,139.09) --
-	(223.54,139.07) --
-	(223.29,138.97) --
-	(222.58,138.65) --
-	(221.63,138.25) --
-	(220.93,137.97) --
-	(220.33,137.73) --
-	(220.17,137.66) --
-	(218.17,136.81) --
-	(217.68,136.58) --
-	(217.43,136.47) --
-	(217.33,136.42) --
-	(215.87,135.77) --
-	(211.50,133.87) --
-	(209.65,133.08) --
-	(205.19,130.98) --
-	(204.99,130.88) --
-	(199.87,128.62) --
-	(198.04,127.77) --
-	(196.35,126.93) --
-	(195.71,126.63) --
-	(195.62,126.59) --
-	(192.71,125.33) --
-	(187.92,123.15) --
-	(178.49,118.78) --
-	(171.43,115.43) --
-	(158.01,108.85) --
-	(154.64,107.17) --
-	(110.88, 85.07) --
-	(101.92, 80.39) --
-	( 95.59, 77.11) --
-	( 92.34, 75.32) --
-	( 86.71, 72.24) --
-	( 78.30, 67.94) --
-	( 64.98, 61.14) --
-	( 64.85, 61.07) --
-	( 60.61, 58.89) --
-	( 52.97, 54.98) --
+	(339.55,178.77) --
+	(339.40,178.72) --
+	(339.21,178.67) --
+	(339.04,178.66) --
+	(338.87,178.60) --
+	(338.83,178.60) --
+	(338.50,178.51) --
+	(337.65,178.32) --
+	(335.47,177.66) --
+	(335.38,177.66) --
+	(333.83,177.22) --
+	(333.82,177.21) --
+	(333.69,177.18) --
+	(333.56,177.16) --
+	(333.53,177.15) --
+	(330.88,176.40) --
+	(330.38,176.27) --
+	(330.17,176.19) --
+	(328.92,175.83) --
+	(328.37,175.67) --
+	(327.78,175.48) --
+	(327.50,175.42) --
+	(327.01,175.27) --
+	(326.46,175.15) --
+	(326.16,175.09) --
+	(325.91,175.03) --
+	(325.87,175.02) --
+	(325.85,175.02) --
+	(325.46,174.98) --
+	(324.82,174.87) --
+	(324.53,174.78) --
+	(324.06,174.68) --
+	(323.98,174.67) --
+	(322.93,174.38) --
+	(322.64,174.29) --
+	(322.56,174.27) --
+	(321.47,173.96) --
+	(321.34,173.91) --
+	(320.71,173.74) --
+	(319.14,173.37) --
+	(318.60,173.23) --
+	(317.13,172.83) --
+	(316.72,172.72) --
+	(316.61,172.69) --
+	(316.58,172.68) --
+	(316.37,172.62) --
+	(316.29,172.61) --
+	(315.65,172.41) --
+	(315.61,172.39) --
+	(315.54,172.36) --
+	(315.28,172.26) --
+	(315.05,172.19) --
+	(314.84,172.14) --
+	(314.55,172.06) --
+	(314.12,171.98) --
+	(314.09,171.97) --
+	(312.75,171.61) --
+	(312.68,171.61) --
+	(312.39,171.50) --
+	(311.87,171.35) --
+	(311.71,171.29) --
+	(311.49,171.25) --
+	(311.09,171.16) --
+	(310.98,171.13) --
+	(310.80,171.04) --
+	(310.45,170.94) --
+	(310.36,170.92) --
+	(309.72,170.76) --
+	(309.55,170.73) --
+	(309.08,170.61) --
+	(308.79,170.53) --
+	(308.63,170.50) --
+	(308.42,170.44) --
+	(307.37,170.08) --
+	(307.16,169.99) --
+	(307.03,169.96) --
+	(306.15,169.70) --
+	(305.86,169.60) --
+	(305.76,169.57) --
+	(305.28,169.43) --
+	(305.11,169.37) --
+	(304.68,169.29) --
+	(304.60,169.26) --
+	(304.48,169.24) --
+	(304.47,169.24) --
+	(304.31,169.20) --
+	(304.10,169.14) --
+	(303.17,168.86) --
+	(302.93,168.78) --
+	(302.89,168.77) --
+	(302.61,168.67) --
+	(302.52,168.64) --
+	(302.45,168.62) --
+	(302.30,168.58) --
+	(302.20,168.55) --
+	(302.08,168.52) --
+	(302.06,168.52) --
+	(301.86,168.48) --
+	(301.81,168.46) --
+	(301.34,168.30) --
+	(300.69,168.09) --
+	(300.07,167.93) --
+	(299.22,167.66) --
+	(298.89,167.58) --
+	(298.71,167.52) --
+	(298.48,167.45) --
+	(298.45,167.44) --
+	(298.21,167.36) --
+	(298.13,167.33) --
+	(298.09,167.31) --
+	(297.99,167.28) --
+	(297.11,166.97) --
+	(296.61,166.83) --
+	(295.85,166.56) --
+	(295.12,166.33) --
+	(293.94,165.91) --
+	(293.90,165.90) --
+	(293.61,165.83) --
+	(293.49,165.80) --
+	(292.94,165.62) --
+	(292.85,165.60) --
+	(292.78,165.59) --
+	(292.77,165.59) --
+	(292.36,165.45) --
+	(292.20,165.42) --
+	(291.58,165.18) --
+	(291.45,165.14) --
+	(291.29,165.09) --
+	(290.44,164.80) --
+	(289.99,164.65) --
+	(289.71,164.55) --
+	(289.61,164.51) --
+	(289.30,164.42) --
+	(289.13,164.37) --
+	(289.03,164.34) --
+	(288.86,164.30) --
+	(288.45,164.13) --
+	(288.16,164.03) --
+	(287.76,163.91) --
+	(286.95,163.73) --
+	(286.70,163.63) --
+	(286.04,163.40) --
+	(285.67,163.30) --
+	(285.44,163.21) --
+	(284.88,162.98) --
+	(284.84,162.95) --
+	(284.81,162.93) --
+	(284.81,162.93) --
+	(284.80,162.93) --
+	(284.75,162.91) --
+	(284.43,162.81) --
+	(284.26,162.77) --
+	(283.80,162.62) --
+	(283.74,162.59) --
+	(283.34,162.46) --
+	(283.28,162.45) --
+	(283.10,162.38) --
+	(281.60,161.86) --
+	(281.52,161.82) --
+	(281.16,161.69) --
+	(280.63,161.49) --
+	(280.60,161.48) --
+	(280.50,161.44) --
+	(280.47,161.43) --
+	(280.41,161.41) --
+	(280.36,161.39) --
+	(280.21,161.34) --
+	(279.90,161.21) --
+	(279.83,161.18) --
+	(279.36,161.02) --
+	(279.03,160.90) --
+	(278.99,160.89) --
+	(278.93,160.88) --
+	(278.83,160.85) --
+	(277.37,160.31) --
+	(277.28,160.26) --
+	(276.77,160.09) --
+	(276.73,160.07) --
+	(276.14,159.87) --
+	(276.03,159.84) --
+	(275.50,159.62) --
+	(274.88,159.38) --
+	(274.85,159.37) --
+	(274.31,159.22) --
+	(273.48,158.96) --
+	(273.29,158.86) --
+	(273.01,158.72) --
+	(272.91,158.70) --
+	(272.40,158.57) --
+	(272.31,158.54) --
+	(271.51,158.23) --
+	(269.91,157.66) --
+	(269.75,157.60) --
+	(269.30,157.43) --
+	(269.12,157.37) --
+	(268.75,157.24) --
+	(268.51,157.16) --
+	(268.32,157.08) --
+	(268.15,157.04) --
+	(267.95,156.96) --
+	(267.83,156.90) --
+	(267.74,156.87) --
+	(266.70,156.51) --
+	(266.69,156.51) --
+	(265.54,156.06) --
+	(265.48,156.04) --
+	(265.11,155.87) --
+	(264.94,155.82) --
+	(264.43,155.64) --
+	(264.14,155.54) --
+	(263.47,155.27) --
+	(262.57,154.94) --
+	(261.39,154.51) --
+	(260.16,154.01) --
+	(260.08,153.99) --
+	(258.99,153.54) --
+	(256.94,152.72) --
+	(255.73,152.25) --
+	(254.34,151.68) --
+	(253.89,151.52) --
+	(253.69,151.45) --
+	(252.46,150.93) --
+	(251.97,150.72) --
+	(250.69,150.23) --
+	(250.38,150.10) --
+	(250.22,150.06) --
+	(249.74,149.87) --
+	(248.30,149.31) --
+	(244.78,147.88) --
+	(242.95,147.21) --
+	(241.65,146.64) --
+	(241.27,146.46) --
+	(240.80,146.27) --
+	(240.03,145.97) --
+	(239.31,145.69) --
+	(239.29,145.68) --
+	(237.41,144.89) --
+	(237.40,144.88) --
+	(236.22,144.44) --
+	(235.24,144.03) --
+	(234.24,143.66) --
+	(233.34,143.28) --
+	(232.39,142.91) --
+	(231.34,142.45) --
+	(231.15,142.37) --
+	(229.14,141.49) --
+	(224.00,139.16) --
+	(223.59,138.95) --
+	(223.54,138.94) --
+	(223.29,138.82) --
+	(222.58,138.54) --
+	(221.63,138.11) --
+	(220.93,137.81) --
+	(220.33,137.57) --
+	(220.17,137.50) --
+	(218.17,136.61) --
+	(217.68,136.38) --
+	(217.43,136.24) --
+	(217.33,136.19) --
+	(215.87,135.57) --
+	(211.50,133.70) --
+	(209.65,132.94) --
+	(205.19,130.92) --
+	(204.99,130.83) --
+	(199.87,128.59) --
+	(198.04,127.74) --
+	(196.35,126.88) --
+	(195.71,126.55) --
+	(195.62,126.51) --
+	(192.71,125.09) --
+	(187.92,122.99) --
+	(178.49,118.59) --
+	(171.43,115.31) --
+	(158.01,108.67) --
+	(154.64,106.95) --
+	(110.88, 84.87) --
+	(101.92, 80.24) --
+	( 95.59, 76.90) --
+	( 92.34, 75.13) --
+	( 86.71, 72.15) --
+	( 78.30, 67.89) --
+	( 64.98, 61.01) --
+	( 64.85, 60.94) --
+	( 60.61, 58.72) --
+	( 52.97, 54.81) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (274.31, 34.03) -- (274.31, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (274.32, 34.03) -- (274.32, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (291.58, 34.03) -- (291.58, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (291.57, 34.03) -- (291.57, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.14, 34.03) -- (298.14, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.13, 34.03) -- (298.13, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.50, 34.03) -- (338.50, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.49, 34.03) -- (338.49, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (365.00, 34.03) -- (365.00, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (364.99, 34.03) -- (364.99, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (370.21, 34.03) -- (370.21, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (370.20, 34.03) -- (370.20, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (390.45, 34.03) -- (390.45, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (390.44, 34.03) -- (390.44, 41.32);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31, 54.28) {-5};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,133.28) {0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,212.28) {5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31, 53.75) {-5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,132.99) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,212.23) {5};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (228.50,  4.82) {Ln(Min. Cap Dist.)$_{t}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (228.50,  4.82) {Ln(Min. Capital Dist.)$_{t}$};
 \end{scope}

### 2014-10-09 LaTeX/mCityCoefPlot.tex
ugh

--- 2014-09-23 LaTeX/mCityCoefPlot.tex
@@
-% Created by tikzDevice version 0.7.0 on 2014-09-23 11:36:07
+% Created by tikzDevice version 0.7.0 on 2014-10-06 20:01:15
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] (124.66, 34.03) rectangle (277.03,277.03);
+\path[clip] (124.66, 27.42) rectangle (277.03,277.03);
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
 
-\path[fill=fillColor] (124.66, 34.03) rectangle (277.04,277.03);
+\path[fill=fillColor] (124.66, 27.42) rectangle (277.04,277.03);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.93, 40.79) -- (213.04, 40.79);
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.64, 63.08) -- (202.41, 63.08);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.10, 49.88) -- (207.76, 49.88);
-
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (193.68, 76.30) -- (230.11, 76.30);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (198.74, 85.37) -- (203.35, 85.37);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (174.88,102.71) -- (189.88,102.71);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (148.07,107.66) -- (170.40,107.66);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (155.06,129.12) -- (247.73,129.12);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (131.59,129.94) -- (270.11,129.94);
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (196.74,152.23) -- (231.20,152.23);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (165.59,155.53) -- (195.00,155.53);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (143.41,174.52) -- (189.28,174.52);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.88,181.95) -- (202.07,181.95);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.75,196.80) -- (202.64,196.80);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (187.98,208.36) -- (225.50,208.36);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (190.64,219.09) -- (251.11,219.09);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (180.79,234.77) -- (210.45,234.77);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (160.16,241.38) -- (204.59,241.38);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (203.18,261.19) -- (216.39,261.19);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (203.83,263.66) -- (223.65,263.66);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (201.90, 40.79) -- (212.07, 40.79);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (200.78, 63.08) -- (202.27, 63.08);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (200.72, 49.88) -- (207.15, 49.88);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (196.61, 76.30) -- (227.18, 76.30);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (199.11, 85.37) -- (202.98, 85.37);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (176.09,102.71) -- (188.68,102.71);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (149.87,107.66) -- (168.61,107.66);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (162.51,129.12) -- (240.28,129.12);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (142.72,129.94) -- (258.97,129.94);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (199.51,152.23) -- (228.43,152.23);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (167.95,155.53) -- (192.63,155.53);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (147.09,174.52) -- (185.60,174.52);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (200.97,181.95) -- (201.98,181.95);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (200.90,196.80) -- (202.49,196.80);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (191.00,208.36) -- (222.48,208.36);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (195.50,219.09) -- (246.25,219.09);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (183.17,234.77) -- (208.07,234.77);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (163.73,241.38) -- (201.02,241.38);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (204.24,261.19) -- (215.33,261.19);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (205.42,263.66) -- (222.05,263.66);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (200.85, 34.03) -- (200.85,277.03);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (200.31, 27.42) -- (200.31,277.03);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.79,261.19) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (213.74,263.66) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (195.62,234.77) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.37,241.38) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (206.74,208.36) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (220.87,219.09) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.47,181.95) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.69,196.80) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.29,155.53) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.35,174.52) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.39,129.12) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (213.97,152.23) circle (  2.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (200.85,129.94) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.38,102.71) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.24,107.66) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (211.89, 76.30) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.04, 85.37) circle (  2.85);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (203.93, 49.88) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.52, 63.08) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.76, 48.56) --
-	(207.76, 51.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (206.98, 40.79) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.76, 49.88) --
-	(200.10, 49.88);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (213.04, 39.68) --
+	(213.04, 41.91);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (200.10, 48.56) --
-	(200.10, 51.20);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (213.04, 40.79) --
+	(200.93, 40.79);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (230.11, 74.97) --
-	(230.11, 77.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (200.93, 39.68) --
+	(200.93, 41.91);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (230.11, 76.30) --
-	(193.68, 76.30);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.41, 61.97) --
+	(202.41, 64.20);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (193.68, 74.97) --
-	(193.68, 77.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.41, 63.08) --
+	(200.64, 63.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (200.64, 61.97) --
+	(200.64, 64.20);
+\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (203.35, 84.25) --
+	(203.35, 86.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (203.35, 85.37) --
+	(198.74, 85.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (198.74, 84.25) --
+	(198.74, 86.48);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (189.88,101.39) --
-	(189.88,104.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (170.40,106.54) --
+	(170.40,108.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (189.88,102.71) --
-	(174.88,102.71);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (170.40,107.66) --
+	(148.07,107.66);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (174.88,101.39) --
-	(174.88,104.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (148.07,106.54) --
+	(148.07,108.77);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (247.73,127.80) --
-	(247.73,130.44);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (270.11,128.83) --
+	(270.11,131.06);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (247.73,129.12) --
-	(155.06,129.12);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (270.11,129.94) --
+	(131.59,129.94);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (155.06,127.80) --
-	(155.06,130.44);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (131.59,128.83) --
+	(131.59,131.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (231.20,151.11) --
+	(231.20,153.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (231.20,152.23) --
+	(196.74,152.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (196.74,151.11) --
+	(196.74,153.34);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (195.00,154.21) --
-	(195.00,156.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (189.28,173.40) --
+	(189.28,175.63);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (195.00,155.53) --
-	(165.59,155.53);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (189.28,174.52) --
+	(143.41,174.52);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.59,154.21) --
-	(165.59,156.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (143.41,173.40) --
+	(143.41,175.63);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (202.07,180.63) --
-	(202.07,183.27);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.64,195.69) --
+	(202.64,197.92);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (202.07,181.95) --
-	(200.88,181.95);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.64,196.80) --
+	(200.75,196.80);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (200.88,180.63) --
-	(200.88,183.27);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (200.75,195.69) --
+	(200.75,197.92);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (225.50,207.04) --
-	(225.50,209.68);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (251.11,217.97) --
+	(251.11,220.20);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (225.50,208.36) --
-	(187.98,208.36);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (251.11,219.09) --
+	(190.64,219.09);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (187.98,207.04) --
-	(187.98,209.68);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (190.64,217.97) --
+	(190.64,220.20);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (210.45,233.45) --
-	(210.45,236.09);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (204.59,240.26) --
+	(204.59,242.49);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (210.45,234.77) --
-	(180.79,234.77);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (204.59,241.38) --
+	(160.16,241.38);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (180.79,233.45) --
-	(180.79,236.09);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (160.16,240.26) --
+	(160.16,242.49);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.39,259.87) --
-	(216.39,262.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (223.65,262.55) --
+	(223.65,264.78);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.39,261.19) --
-	(203.18,261.19);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (223.65,263.66) --
+	(203.83,263.66);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (203.18,259.87) --
-	(203.18,262.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (203.83,262.55) --
+	(203.83,264.78);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (124.66, 34.03) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (124.66, 27.42) --
 	(124.66,277.03);
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55, 46.58) {World GDP Growth$_{t}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55, 37.49) {World GDP Growth$_{t}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55, 72.99) {Democracy$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55, 59.78) {Resource Rents/GDP$_{t}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55, 99.40) {Ln(Inflation)$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55, 82.06) {Democracy$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,125.82) {Upper Income};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,104.35) {Ln(Inflation)$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,152.23) {Area$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,126.64) {Upper Income};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,178.64) {Duration$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,148.92) {Number of conflicts$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,205.06) {Type$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,171.21) {Area$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,231.47) {Intensity$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,193.50) {Duration$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,257.88) {Ln(Min. City Dist.)$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,215.78) {Type$_{t-1}$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,238.07) {Intensity$_{t-1}$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,260.36) {Ln(Min. City Dist.)$_{t-1}$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (124.66, 34.03) --
-	(277.03, 34.03);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
-\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (131.59, 20.31) {-0.3};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (177.76, 20.31) {-0.1};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (223.94, 20.31) {0.1};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (270.11, 20.31) {0.3};
+\path[draw=drawColor,line width= 0.6pt,line join=round] (124.66, 27.42) --
+	(277.03, 27.42);
 \end{scope}

### 2014-10-09 LaTeX/mCitySimPlot.tex
ugh

@@
-% Created by tikzDevice version 0.7.0 on 2014-10-06 19:44:41
+% Created by tikzDevice version 0.7.0 on 2014-10-06 20:01:25
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,106.37) --
-	( 61.01,109.04) --
-	( 65.48,110.52) --
-	( 65.62,110.57) --
-	( 79.64,115.23) --
-	( 88.50,118.17) --
-	( 94.41,120.14) --
-	( 97.84,121.27) --
-	(104.50,123.49) --
-	(110.01,125.32) --
-	(113.94,126.62) --
-	(116.56,127.49) --
-	(124.94,130.28) --
-	(160.01,141.93) --
-	(160.15,141.97) --
-	(163.56,143.10) --
-	(164.50,143.42) --
-	(175.08,146.93) --
-	(177.68,147.80) --
-	(185.12,150.27) --
-	(195.04,153.56) --
-	(195.05,153.57) --
-	(199.79,155.14) --
-	(200.09,155.24) --
-	(201.70,155.77) --
-	(202.42,156.01) --
-	(203.15,156.26) --
-	(203.24,156.29) --
-	(203.92,156.51) --
-	(204.08,156.56) --
-	(205.70,157.10) --
-	(211.30,158.97) --
-	(213.02,159.54) --
-	(213.22,159.60) --
-	(213.28,159.62) --
-	(214.88,160.15) --
-	(219.39,161.65) --
-	(219.87,161.81) --
-	(224.51,163.35) --
-	(226.38,163.97) --
-	(226.89,164.14) --
-	(228.22,164.58) --
-	(229.80,165.11) --
-	(230.53,165.35) --
-	(231.54,165.69) --
-	(232.29,165.94) --
-	(232.55,166.02) --
-	(232.60,166.04) --
-	(233.03,166.18) --
-	(236.50,167.34) --
-	(238.44,167.98) --
-	(239.50,168.33) --
-	(240.76,168.75) --
-	(242.87,169.45) --
-	(243.82,169.77) --
-	(244.87,170.11) --
-	(245.90,170.46) --
-	(247.14,170.87) --
-	(247.15,170.87) --
-	(248.00,171.16) --
-	(248.59,171.35) --
-	(249.15,171.54) --
-	(249.91,171.79) --
-	(250.14,171.87) --
-	(250.71,172.06) --
-	(251.21,172.22) --
-	(251.61,172.35) --
-	(251.88,172.44) --
-	(252.52,172.66) --
-	(252.98,172.81) --
-	(253.12,172.85) --
-	(253.36,172.94) --
-	(254.91,173.45) --
-	(255.02,173.49) --
-	(256.32,173.92) --
-	(258.61,174.68) --
-	(260.03,175.15) --
-	(260.14,175.19) --
-	(260.80,175.41) --
-	(261.97,175.79) --
-	(262.19,175.87) --
-	(262.48,175.96) --
-	(262.99,176.14) --
-	(264.29,176.57) --
-	(264.50,176.64) --
-	(264.53,176.65) --
-	(264.97,176.79) --
-	(266.10,177.17) --
-	(266.13,177.18) --
-	(266.44,177.28) --
-	(267.28,177.56) --
-	(267.71,177.70) --
-	(268.38,177.92) --
-	(269.11,178.17) --
-	(269.74,178.38) --
-	(269.87,178.42) --
-	(271.02,178.80) --
-	(271.10,178.83) --
-	(271.68,179.02) --
-	(272.40,179.26) --
-	(272.79,179.39) --
-	(273.63,179.67) --
-	(274.52,179.96) --
-	(275.28,180.22) --
-	(275.59,180.32) --
-	(276.13,180.50) --
-	(276.31,180.56) --
-	(276.77,180.71) --
-	(277.30,180.89) --
-	(277.98,181.12) --
-	(278.04,181.13) --
-	(278.45,181.27) --
-	(279.17,181.51) --
-	(279.30,181.55) --
-	(279.52,181.62) --
-	(279.66,181.67) --
-	(279.69,181.68) --
-	(280.15,181.83) --
-	(280.53,181.96) --
-	(280.72,182.02) --
-	(281.20,182.18) --
-	(281.36,182.24) --
-	(281.45,182.27) --
-	(282.80,182.71) --
-	(283.05,182.80) --
-	(283.89,183.08) --
-	(283.98,183.11) --
-	(284.07,183.14) --
-	(284.62,183.32) --
-	(284.86,183.40) --
-	(285.03,183.46) --
-	(285.13,183.49) --
-	(286.00,183.78) --
-	(286.57,183.97) --
-	(286.59,183.98) --
-	(287.25,184.19) --
-	(287.81,184.38) --
-	(288.54,184.62) --
-	(288.59,184.64) --
-	(289.22,184.85) --
-	(289.76,185.03) --
-	(290.76,185.36) --
-	(290.86,185.39) --
-	(291.20,185.51) --
-	(291.32,185.54) --
-	(291.81,185.71) --
-	(291.88,185.73) --
-	(292.21,185.84) --
-	(292.36,185.89) --
-	(292.42,185.91) --
-	(292.49,185.93) --
-	(292.51,185.94) --
-	(292.62,185.98) --
-	(293.21,186.17) --
-	(293.91,186.41) --
-	(295.25,186.85) --
-	(295.45,186.92) --
-	(295.51,186.94) --
-	(295.93,187.08) --
-	(295.99,187.10) --
-	(296.10,187.13) --
-	(296.47,187.26) --
-	(296.65,187.32) --
-	(296.99,187.43) --
-	(297.01,187.43) --
-	(297.04,187.45) --
-	(297.05,187.45) --
-	(297.09,187.46) --
-	(297.13,187.47) --
-	(297.22,187.51) --
-	(297.31,187.53) --
-	(297.31,187.53) --
-	(297.71,187.67) --
-	(297.96,187.75) --
-	(298.34,187.88) --
-	(298.57,187.95) --
-	(299.04,188.11) --
-	(300.58,188.62) --
-	(300.69,188.66) --
-	(301.32,188.87) --
-	(302.10,189.13) --
-	(302.23,189.17) --
-	(302.50,189.26) --
-	(302.82,189.36) --
-	(302.98,189.42) --
-	(303.49,189.59) --
-	(303.87,189.71) --
-	(304.04,189.77) --
-	(304.05,189.77) --
-	(304.17,189.82) --
-	(304.21,189.83) --
-	(304.88,190.05) --
-	(305.44,190.24) --
-	(305.52,190.26) --
-	(305.61,190.29) --
-	(305.86,190.37) --
-	(306.19,190.49) --
-	(306.32,190.53) --
-	(307.91,191.06) --
-	(307.96,191.07) --
-	(308.47,191.24) --
-	(308.57,191.27) --
-	(309.22,191.49) --
-	(309.44,191.56) --
-	(309.51,191.59) --
-	(309.67,191.64) --
-	(310.00,191.75) --
-	(310.25,191.83) --
-	(310.76,192.00) --
-	(310.92,192.06) --
-	(311.04,192.09) --
-	(311.16,192.14) --
-	(311.41,192.22) --
-	(311.41,192.22) --
-	(311.44,192.23) --
-	(311.54,192.26) --
-	(311.68,192.31) --
-	(311.68,192.31) --
-	(311.88,192.38) --
-	(312.22,192.49) --
-	(312.92,192.72) --
-	(313.12,192.79) --
-	(313.27,192.84) --
-	(313.53,192.93) --
-	(313.83,193.02) --
-	(314.24,193.16) --
-	(314.31,193.18) --
-	(314.45,193.23) --
-	(314.63,193.29) --
-	(315.00,193.41) --
-	(315.21,193.48) --
-	(315.23,193.49) --
-	(315.37,193.53) --
-	(315.48,193.57) --
-	(315.51,193.58) --
-	(315.62,193.62) --
-	(315.70,193.64) --
-	(315.79,193.67) --
-	(316.13,193.79) --
-	(316.22,193.82) --
-	(316.38,193.87) --
-	(316.61,193.95) --
-	(316.93,194.05) --
-	(317.07,194.10) --
-	(317.20,194.14) --
-	(317.36,194.20) --
-	(317.75,194.33) --
-	(317.76,194.33) --
-	(317.79,194.34) --
-	(317.86,194.36) --
-	(317.89,194.37) --
-	(317.98,194.40) --
-	(318.43,194.55) --
-	(318.60,194.61) --
-	(318.85,194.69) --
-	(319.11,194.78) --
-	(319.21,194.81) --
-	(319.52,194.91) --
-	(319.81,195.01) --
-	(320.44,195.22) --
-	(321.85,195.69) --
-	(321.91,195.71) --
-	(322.04,195.75) --
-	(322.30,195.84) --
-	(322.60,195.94) --
-	(322.75,195.99) --
-	(323.02,196.08) --
-	(323.10,196.10) --
-	(323.28,196.16) --
-	(324.05,196.42) --
-	(324.42,196.54) --
-	(324.61,196.60) --
-	(324.72,196.64) --
-	(325.08,196.76) --
-	(325.99,197.06) --
-	(326.58,197.26) --
-	(326.72,197.31) --
-	(327.61,197.60) --
-	(327.91,197.70) --
-	(328.67,197.95) --
-	(328.94,198.04) --
-	(329.07,198.09) --
-	(329.52,198.24) --
-	(331.17,198.78) --
-	(332.00,199.06) --
-	(332.27,199.15) --
-	(333.07,199.42) --
-	(333.19,199.45) --
-	(333.76,199.64) --
-	(335.51,200.23) --
-	(336.07,200.41) --
-	(336.75,200.64) --
-	(336.88,200.68) --
-	(337.54,200.90) --
-	(337.92,201.03) --
-	(338.29,201.15) --
-	(338.32,201.16) --
-	(338.37,201.17) --
-	(338.79,201.32) --
-	(338.87,201.34) --
-	(339.41,201.52) --
-	(339.54,201.56) --
-	(340.26,201.80) --
-	(340.28,201.81) --
-	(340.36,201.84) --
-	(340.58,201.91) --
-	(340.90,202.02) --
-	(341.07,202.07) --
-	(341.38,202.18) --
-	(341.48,202.21) --
-	(341.53,202.23) --
-	(341.57,202.24) --
-	(342.00,202.38) --
-	(342.06,202.40) --
-	(342.60,202.58) --
-	(342.92,202.69) --
-	(344.39,203.18) --
-	(344.81,203.31) --
-	(345.03,203.39) --
-	(345.51,203.55) --
-	(345.56,203.56) --
-	(346.27,203.80) --
-	(348.09,204.40) --
-	(348.19,204.44) --
-	(348.32,204.48) --
-	(348.52,204.55) --
-	(348.65,204.59) --
-	(350.04,205.05) --
-	(350.29,205.13) --
-	(350.39,205.17) --
-	(351.49,205.53) --
-	(354.19,206.43) --
-	(354.41,206.50) --
-	(354.96,206.69) --
-	(354.99,206.69) --
-	(355.28,206.79) --
-	(355.84,206.98) --
-	(356.71,207.27) --
-	(356.75,207.28) --
-	(357.50,207.53) --
-	(357.53,207.54) --
-	(358.04,207.71) --
-	(358.62,207.90) --
-	(359.31,208.13) --
-	(359.62,208.23) --
-	(359.75,208.28) --
-	(359.85,208.31) --
-	(360.61,208.56) --
-	(360.64,208.57) --
-	(360.71,208.60) --
-	(361.91,208.99) --
-	(362.60,209.22) --
-	(364.24,209.77) --
-	(364.46,209.84) --
-	(365.70,210.25) --
-	(366.29,210.45) --
-	(370.53,211.86) --
-	(371.02,212.02) --
-	(372.06,212.37) --
-	(372.07,212.37) --
-	(372.38,212.47) --
-	(372.60,212.54) --
-	(372.90,212.65) --
-	(373.16,212.73) --
-	(373.53,212.86) --
-	(373.80,212.94) --
-	(374.46,213.16) --
-	(374.81,213.28) --
-	(375.77,213.60) --
-	(376.36,213.80) --
-	(376.51,213.85) --
-	(376.93,213.98) --
-	(378.03,214.35) --
-	(379.36,214.79) --
-	(379.36,214.79) --
-	(380.09,215.03) --
-	(380.12,215.04) --
-	(381.03,215.35) --
-	(381.47,215.49) --
-	(381.75,215.58) --
-	(382.36,215.79) --
-	(382.44,215.82) --
-	(382.57,215.86) --
-	(383.02,216.01) --
-	(385.04,216.68) --
-	(385.16,216.72) --
-	(388.87,217.95) --
-	(393.56,219.51) --
-	(395.71,220.22) --
-	(403.26,222.73) --
-	(404.02,222.98);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,107.25) --
+	( 61.01,109.92) --
+	( 65.48,111.40) --
+	( 65.62,111.44) --
+	( 79.64,116.10) --
+	( 88.50,119.04) --
+	( 94.41,121.00) --
+	( 97.84,122.14) --
+	(104.50,124.35) --
+	(110.01,126.18) --
+	(113.94,127.48) --
+	(116.56,128.35) --
+	(124.94,131.13) --
+	(160.01,142.77) --
+	(160.15,142.82) --
+	(163.56,143.95) --
+	(164.50,144.26) --
+	(175.08,147.77) --
+	(177.68,148.64) --
+	(185.12,151.10) --
+	(195.04,154.40) --
+	(195.05,154.40) --
+	(199.79,155.97) --
+	(200.09,156.07) --
+	(201.70,156.61) --
+	(202.42,156.85) --
+	(203.15,157.09) --
+	(203.24,157.12) --
+	(203.92,157.34) --
+	(204.08,157.39) --
+	(205.70,157.93) --
+	(211.30,159.79) --
+	(213.02,160.36) --
+	(213.22,160.43) --
+	(213.28,160.45) --
+	(214.88,160.98) --
+	(219.39,162.48) --
+	(219.87,162.64) --
+	(224.51,164.18) --
+	(226.38,164.80) --
+	(226.89,164.97) --
+	(228.22,165.41) --
+	(229.80,165.93) --
+	(230.53,166.18) --
+	(231.54,166.51) --
+	(232.29,166.76) --
+	(232.55,166.84) --
+	(232.60,166.86) --
+	(233.03,167.01) --
+	(236.50,168.16) --
+	(238.44,168.80) --
+	(239.50,169.15) --
+	(240.76,169.57) --
+	(242.87,170.27) --
+	(243.82,170.58) --
+	(244.87,170.93) --
+	(245.90,171.27) --
+	(247.14,171.69) --
+	(247.15,171.69) --
+	(248.00,171.97) --
+	(248.59,172.17) --
+	(249.15,172.35) --
+	(249.91,172.60) --
+	(250.14,172.68) --
+	(250.71,172.87) --
+	(251.21,173.04) --
+	(251.61,173.17) --
+	(251.88,173.26) --
+	(252.52,173.47) --
+	(252.98,173.63) --
+	(253.12,173.67) --
+	(253.36,173.75) --
+	(254.91,174.27) --
+	(255.02,174.30) --
+	(256.32,174.73) --
+	(258.61,175.49) --
+	(260.03,175.96) --
+	(260.14,176.00) --
+	(260.80,176.22) --
+	(261.97,176.61) --
+	(262.19,176.68) --
+	(262.48,176.78) --
+	(262.99,176.95) --
+	(264.29,177.38) --
+	(264.50,177.45) --
+	(264.53,177.46) --
+	(264.97,177.60) --
+	(266.10,177.98) --
+	(266.13,177.99) --
+	(266.44,178.09) --
+	(267.28,178.37) --
+	(267.71,178.51) --
+	(268.38,178.73) --
+	(269.11,178.98) --
+	(269.74,179.19) --
+	(269.87,179.23) --
+	(271.02,179.61) --
+	(271.10,179.64) --
+	(271.68,179.83) --
+	(272.40,180.07) --
+	(272.79,180.20) --
+	(273.63,180.48) --
+	(274.52,180.77) --
+	(275.28,181.03) --
+	(275.59,181.13) --
+	(276.13,181.31) --
+	(276.31,181.37) --
+	(276.77,181.52) --
+	(277.30,181.69) --
+	(277.98,181.92) --
+	(278.04,181.94) --
+	(278.45,182.08) --
+	(279.17,182.32) --
+	(279.30,182.36) --
+	(279.52,182.43) --
+	(279.66,182.48) --
+	(279.69,182.49) --
+	(280.15,182.64) --
+	(280.53,182.77) --
+	(280.72,182.83) --
+	(281.20,182.99) --
+	(281.36,183.04) --
+	(281.45,183.07) --
+	(282.80,183.52) --
+	(283.05,183.60) --
+	(283.89,183.88) --
+	(283.98,183.91) --
+	(284.07,183.94) --
+	(284.62,184.13) --
+	(284.86,184.21) --
+	(285.04,184.26) --
+	(285.13,184.29) --
+	(286.00,184.58) --
+	(286.57,184.77) --
+	(286.59,184.78) --
+	(287.25,185.00) --
+	(287.81,185.18) --
+	(288.54,185.43) --
+	(288.59,185.44) --
+	(289.22,185.65) --
+	(289.76,185.83) --
+	(290.76,186.16) --
+	(290.86,186.20) --
+	(291.20,186.31) --
+	(291.32,186.35) --
+	(291.81,186.51) --
+	(291.88,186.53) --
+	(292.21,186.64) --
+	(292.36,186.70) --
+	(292.42,186.71) --
+	(292.49,186.74) --
+	(292.51,186.74) --
+	(292.62,186.78) --
+	(293.21,186.98) --
+	(293.91,187.21) --
+	(295.25,187.65) --
+	(295.45,187.72) --
+	(295.51,187.74) --
+	(295.93,187.88) --
+	(295.99,187.90) --
+	(296.10,187.93) --
+	(296.47,188.06) --
+	(296.65,188.12) --
+	(296.99,188.23) --
+	(297.01,188.24) --
+	(297.04,188.25) --
+	(297.05,188.25) --
+	(297.09,188.26) --
+	(297.13,188.28) --
+	(297.22,188.31) --
+	(297.31,188.34) --
+	(297.31,188.34) --
+	(297.71,188.47) --
+	(297.96,188.55) --
+	(298.34,188.68) --
+	(298.57,188.75) --
+	(299.05,188.91) --
+	(300.58,189.42) --
+	(300.69,189.46) --
+	(301.32,189.67) --
+	(302.10,189.93) --
+	(302.23,189.97) --
+	(302.50,190.06) --
+	(302.82,190.16) --
+	(302.98,190.22) --
+	(303.49,190.39) --
+	(303.87,190.51) --
+	(304.04,190.57) --
+	(304.05,190.57) --
+	(304.17,190.61) --
+	(304.21,190.63) --
+	(304.88,190.85) --
+	(305.44,191.04) --
+	(305.52,191.06) --
+	(305.61,191.09) --
+	(305.86,191.17) --
+	(306.19,191.28) --
+	(306.32,191.33) --
+	(307.91,191.85) --
+	(307.96,191.87) --
+	(308.47,192.04) --
+	(308.57,192.07) --
+	(309.22,192.29) --
+	(309.44,192.36) --
+	(309.51,192.38) --
+	(309.67,192.44) --
+	(310.00,192.55) --
+	(310.25,192.63) --
+	(310.76,192.80) --
+	(310.92,192.85) --
+	(311.04,192.89) --
+	(311.16,192.93) --
+	(311.41,193.01) --
+	(311.41,193.02) --
+	(311.44,193.03) --
+	(311.54,193.06) --
+	(311.68,193.10) --
+	(311.68,193.11) --
+	(311.88,193.17) --
+	(312.22,193.29) --
+	(312.92,193.52) --
+	(313.12,193.58) --
+	(313.27,193.63) --
+	(313.53,193.72) --
+	(313.83,193.82) --
+	(314.24,193.95) --
+	(314.31,193.98) --
+	(314.45,194.03) --
+	(314.63,194.09) --
+	(315.00,194.21) --
+	(315.21,194.28) --
+	(315.23,194.28) --
+	(315.37,194.33) --
+	(315.48,194.37) --
+	(315.51,194.38) --
+	(315.62,194.41) --
+	(315.70,194.44) --
+	(315.79,194.47) --
+	(316.13,194.58) --
+	(316.22,194.61) --
+	(316.38,194.67) --
+	(316.61,194.74) --
+	(316.93,194.85) --
+	(317.07,194.89) --
+	(317.20,194.94) --
+	(317.36,194.99) --
+	(317.75,195.12) --
+	(317.76,195.12) --
+	(317.79,195.13) --
+	(317.86,195.16) --
+	(317.89,195.17) --
+	(317.98,195.20) --
+	(318.43,195.34) --
+	(318.60,195.40) --
+	(318.85,195.48) --
+	(319.11,195.57) --
+	(319.21,195.61) --
+	(319.52,195.71) --
+	(319.81,195.80) --
+	(320.44,196.01) --
+	(321.85,196.48) --
+	(321.91,196.50) --
+	(322.04,196.54) --
+	(322.30,196.63) --
+	(322.60,196.73) --
+	(322.75,196.78) --
+	(323.02,196.87) --
+	(323.10,196.90) --
+	(323.28,196.96) --
+	(324.05,197.21) --
+	(324.42,197.33) --
+	(324.61,197.40) --
+	(324.72,197.43) --
+	(325.08,197.55) --
+	(325.99,197.85) --
+	(326.58,198.05) --
+	(326.72,198.10) --
+	(327.61,198.39) --
+	(327.91,198.49) --
+	(328.67,198.74) --
+	(328.94,198.83) --
+	(329.07,198.88) --
+	(329.52,199.03) --
+	(331.17,199.57) --
+	(332.00,199.85) --
+	(332.27,199.94) --
+	(333.07,200.21) --
+	(333.19,200.24) --
+	(333.76,200.43) --
+	(335.51,201.02) --
+	(336.07,201.20) --
+	(336.75,201.43) --
+	(336.88,201.47) --
+	(337.54,201.69) --
+	(337.92,201.81) --
+	(338.29,201.94) --
+	(338.32,201.95) --
+	(338.37,201.96) --
+	(338.79,202.10) --
+	(338.87,202.13) --
+	(339.41,202.31) --
+	(339.54,202.35) --
+	(340.26,202.59) --
+	(340.28,202.60) --
+	(340.36,202.62) --
+	(340.58,202.70) --
+	(340.90,202.80) --
+	(341.07,202.86) --
+	(341.38,202.96) --
+	(341.48,203.00) --
+	(341.53,203.01) --
+	(341.57,203.03) --
+	(342.00,203.17) --
+	(342.06,203.19) --
+	(342.60,203.37) --
+	(342.92,203.47) --
+	(344.39,203.96) --
+	(344.81,204.10) --
+	(345.03,204.17) --
+	(345.51,204.33) --
+	(345.56,204.35) --
+	(346.27,204.59) --
+	(348.09,205.19) --
+	(348.19,205.22) --
+	(348.32,205.27) --
+	(348.52,205.33) --
+	(348.65,205.38) --
+	(350.04,205.84) --
+	(350.29,205.92) --
+	(350.39,205.95) --
+	(351.49,206.32) --
+	(354.19,207.21) --
+	(354.41,207.29) --
+	(354.96,207.47) --
+	(354.99,207.48) --
+	(355.28,207.58) --
+	(355.84,207.76) --
+	(356.71,208.05) --
+	(356.75,208.06) --
+	(357.50,208.31) --
+	(357.53,208.32) --
+	(358.04,208.49) --
+	(358.62,208.68) --
+	(359.31,208.91) --
+	(359.62,209.01) --
+	(359.75,209.06) --
+	(359.85,209.09) --
+	(360.61,209.34) --
+	(360.64,209.35) --
+	(360.71,209.38) --
+	(361.91,209.77) --
+	(362.60,210.01) --
+	(364.24,210.55) --
+	(364.46,210.62) --
+	(365.70,211.03) --
+	(366.29,211.23) --
+	(370.53,212.64) --
+	(371.02,212.80) --
+	(372.06,213.14) --
+	(372.07,213.15) --
+	(372.38,213.25) --
+	(372.60,213.32) --
+	(372.90,213.42) --
+	(373.16,213.51) --
+	(373.53,213.63) --
+	(373.80,213.72) --
+	(374.46,213.94) --
+	(374.81,214.06) --
+	(375.77,214.38) --
+	(376.36,214.57) --
+	(376.51,214.62) --
+	(376.93,214.76) --
+	(378.03,215.12) --
+	(379.36,215.57) --
+	(379.36,215.57) --
+	(380.09,215.81) --
+	(380.12,215.82) --
+	(381.03,216.12) --
+	(381.47,216.27) --
+	(381.75,216.36) --
+	(382.36,216.56) --
+	(382.44,216.59) --
+	(382.57,216.63) --
+	(383.02,216.78) --
+	(385.04,217.45) --
+	(385.16,217.49) --
+	(388.87,218.72) --
+	(393.56,220.28) --
+	(395.71,220.99) --
+	(403.26,223.50) --
+	(404.02,223.75);
 \definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}
 
-\path[fill=fillColor,fill opacity=0.30] ( 52.97,167.36) --
-	( 61.01,168.41) --
-	( 65.48,168.80) --
-	( 65.62,168.81) --
-	( 79.64,170.79) --
-	( 88.50,171.79) --
-	( 94.41,172.49) --
-	( 97.84,173.06) --
-	(104.50,173.98) --
-	(110.01,174.56) --
-	(113.94,175.03) --
-	(116.56,175.36) --
-	(124.94,176.30) --
-	(160.01,181.27) --
-	(160.15,181.30) --
-	(163.56,181.70) --
-	(164.50,181.78) --
-	(175.08,183.35) --
-	(177.68,183.86) --
-	(185.12,185.40) --
-	(195.04,187.30) --
-	(195.05,187.30) --
-	(199.79,188.52) --
-	(200.09,188.60) --
-	(201.70,188.94) --
-	(202.42,189.05) --
-	(203.15,189.18) --
-	(203.24,189.19) --
-	(203.92,189.29) --
-	(204.08,189.32) --
-	(205.70,189.71) --
-	(211.30,190.89) --
-	(213.02,191.21) --
-	(213.22,191.26) --
-	(213.28,191.27) --
-	(214.88,191.68) --
-	(219.39,192.70) --
-	(219.87,192.77) --
-	(224.51,193.76) --
-	(226.38,194.26) --
-	(226.89,194.38) --
-	(228.22,194.75) --
-	(229.80,195.15) --
-	(230.53,195.25) --
-	(231.54,195.47) --
-	(232.29,195.59) --
-	(232.55,195.66) --
-	(232.60,195.67) --
-	(233.03,195.77) --
-	(236.50,196.61) --
-	(238.44,197.03) --
-	(239.50,197.27) --
-	(240.76,197.54) --
-	(242.87,198.03) --
-	(243.82,198.26) --
-	(244.87,198.51) --
-	(245.90,198.81) --
-	(247.14,199.15) --
-	(247.15,199.15) --
-	(248.00,199.39) --
-	(248.59,199.55) --
-	(249.15,199.72) --
-	(249.91,199.94) --
-	(250.14,200.00) --
-	(250.71,200.16) --
-	(251.21,200.29) --
-	(251.61,200.40) --
-	(251.88,200.46) --
-	(252.52,200.69) --
-	(252.98,200.84) --
-	(253.12,200.86) --
-	(253.36,200.89) --
-	(254.91,201.29) --
-	(255.02,201.32) --
-	(256.32,201.72) --
-	(258.61,202.38) --
-	(260.03,202.80) --
-	(260.14,202.84) --
-	(260.80,203.04) --
-	(261.97,203.27) --
-	(262.19,203.35) --
-	(262.48,203.44) --
-	(262.99,203.62) --
-	(264.29,204.03) --
-	(264.50,204.10) --
-	(264.53,204.11) --
-	(264.97,204.25) --
-	(266.10,204.54) --
-	(266.13,204.55) --
-	(266.44,204.61) --
-	(267.28,204.93) --
-	(267.71,205.05) --
-	(268.38,205.26) --
-	(269.11,205.45) --
-	(269.74,205.69) --
-	(269.87,205.74) --
-	(271.02,206.18) --
-	(271.10,206.22) --
-	(271.68,206.47) --
-	(272.40,206.66) --
-	(272.79,206.78) --
-	(273.63,207.07) --
-	(274.52,207.40) --
-	(275.28,207.68) --
-	(275.59,207.78) --
-	(276.13,207.95) --
-	(276.31,207.99) --
-	(276.77,208.14) --
-	(277.30,208.37) --
-	(277.98,208.66) --
-	(278.04,208.68) --
-	(278.45,208.79) --
-	(279.17,208.98) --
-	(279.30,209.02) --
-	(279.52,209.08) --
-	(279.66,209.14) --
-	(279.69,209.14) --
-	(280.15,209.31) --
-	(280.53,209.48) --
-	(280.72,209.56) --
-	(281.20,209.75) --
-	(281.36,209.82) --
-	(281.45,209.85) --
-	(282.80,210.34) --
-	(283.05,210.37) --
-	(283.89,210.70) --
-	(283.98,210.74) --
-	(284.07,210.78) --
-	(284.62,210.98) --
-	(284.86,211.08) --
-	(285.03,211.13) --
-	(285.13,211.16) --
-	(286.00,211.42) --
-	(286.57,211.61) --
-	(286.59,211.61) --
-	(287.25,211.79) --
-	(287.81,211.98) --
-	(288.54,212.28) --
-	(288.59,212.29) --
-	(289.22,212.44) --
-	(289.76,212.64) --
-	(290.76,213.08) --
-	(290.86,213.13) --
-	(291.20,213.21) --
-	(291.32,213.21) --
-	(291.81,213.42) --
-	(291.88,213.46) --
-	(292.21,213.58) --
-	(292.36,213.65) --
-	(292.42,213.69) --
-	(292.49,213.72) --
-	(292.51,213.74) --
-	(292.62,213.79) --
-	(293.21,213.98) --
-	(293.91,214.28) --
-	(295.25,214.70) --
-	(295.45,214.78) --
-	(295.51,214.81) --
-	(295.93,215.00) --
-	(295.99,215.02) --
-	(296.10,215.06) --
-	(296.47,215.21) --
-	(296.65,215.26) --
-	(296.99,215.30) --
-	(297.01,215.30) --
-	(297.04,215.31) --
-	(297.05,215.31) --
-	(297.09,215.32) --
-	(297.13,215.34) --
-	(297.22,215.39) --
-	(297.31,215.44) --
-	(297.31,215.44) --
-	(297.71,215.55) --
-	(297.96,215.64) --
-	(298.34,215.77) --
-	(298.57,215.86) --
-	(299.04,216.04) --
-	(300.58,216.50) --
-	(300.69,216.54) --
-	(301.32,216.72) --
-	(302.10,216.99) --
-	(302.23,217.04) --
-	(302.50,217.16) --
-	(302.82,217.32) --
-	(302.98,217.40) --
-	(303.49,217.63) --
-	(303.87,217.81) --
-	(304.04,217.89) --
-	(304.05,217.89) --
-	(304.17,217.95) --
-	(304.21,217.97) --
-	(304.88,218.27) --
-	(305.44,218.51) --
-	(305.52,218.55) --
-	(305.61,218.58) --
-	(305.86,218.68) --
-	(306.19,218.81) --
-	(306.32,218.86) --
-	(307.91,219.57) --
-	(307.96,219.60) --
-	(308.47,219.81) --
-	(308.57,219.85) --
-	(309.22,220.10) --
-	(309.44,220.18) --
-	(309.51,220.20) --
-	(309.67,220.25) --
-	(310.00,220.39) --
-	(310.25,220.47) --
-	(310.76,220.68) --
-	(310.92,220.74) --
-	(311.04,220.77) --
-	(311.16,220.82) --
-	(311.41,220.90) --
-	(311.41,220.90) --
-	(311.44,220.91) --
-	(311.54,220.94) --
-	(311.68,220.98) --
-	(311.68,220.99) --
-	(311.88,221.05) --
-	(312.22,221.19) --
-	(312.92,221.49) --
-	(313.12,221.57) --
-	(313.27,221.65) --
-	(313.53,221.73) --
-	(313.83,221.83) --
-	(314.24,222.00) --
-	(314.31,222.04) --
-	(314.45,222.11) --
-	(314.63,222.16) --
-	(315.00,222.37) --
-	(315.21,222.46) --
-	(315.23,222.47) --
-	(315.37,222.52) --
-	(315.48,222.56) --
-	(315.51,222.58) --
-	(315.62,222.62) --
-	(315.70,222.64) --
-	(315.79,222.66) --
-	(316.13,222.81) --
-	(316.22,222.83) --
-	(316.38,222.87) --
-	(316.61,222.95) --
-	(316.93,223.12) --
-	(317.07,223.18) --
-	(317.20,223.26) --
-	(317.36,223.33) --
-	(317.75,223.47) --
-	(317.76,223.47) --
-	(317.79,223.49) --
-	(317.86,223.53) --
-	(317.89,223.54) --
-	(317.98,223.58) --
-	(318.43,223.78) --
-	(318.60,223.85) --
-	(318.85,224.00) --
-	(319.11,224.09) --
-	(319.21,224.11) --
-	(319.52,224.25) --
-	(319.81,224.40) --
-	(320.44,224.64) --
-	(321.85,225.23) --
-	(321.91,225.27) --
-	(322.04,225.35) --
-	(322.30,225.47) --
-	(322.60,225.60) --
-	(322.75,225.66) --
-	(323.02,225.77) --
-	(323.10,225.80) --
-	(323.28,225.87) --
-	(324.05,226.17) --
-	(324.42,226.34) --
-	(324.61,226.43) --
-	(324.72,226.50) --
-	(325.08,226.65) --
-	(325.99,227.12) --
-	(326.58,227.38) --
-	(326.72,227.44) --
-	(327.61,227.83) --
-	(327.91,227.96) --
-	(328.67,228.25) --
-	(328.94,228.38) --
-	(329.07,228.46) --
-	(329.52,228.70) --
-	(331.17,229.50) --
-	(332.00,229.87) --
-	(332.27,230.00) --
-	(333.07,230.25) --
-	(333.19,230.29) --
-	(333.76,230.52) --
-	(335.51,231.36) --
-	(336.07,231.68) --
-	(336.75,232.03) --
-	(336.88,232.07) --
-	(337.54,232.34) --
-	(337.92,232.47) --
-	(338.29,232.66) --
-	(338.32,232.68) --
-	(338.37,232.70) --
-	(338.79,232.94) --
-	(338.87,232.97) --
-	(339.41,233.19) --
-	(339.54,233.26) --
-	(340.26,233.63) --
-	(340.28,233.64) --
-	(340.36,233.69) --
-	(340.58,233.82) --
-	(340.90,234.00) --
-	(341.07,234.09) --
-	(341.38,234.25) --
-	(341.48,234.29) --
-	(341.53,234.32) --
-	(341.57,234.33) --
-	(342.00,234.53) --
-	(342.06,234.56) --
-	(342.60,234.82) --
-	(342.92,234.94) --
-	(344.39,235.59) --
-	(344.81,235.76) --
-	(345.03,235.85) --
-	(345.51,236.00) --
-	(345.56,236.01) --
-	(346.27,236.21) --
-	(348.09,237.11) --
-	(348.19,237.16) --
-	(348.32,237.23) --
-	(348.52,237.32) --
-	(348.65,237.36) --
-	(350.04,238.11) --
-	(350.29,238.22) --
-	(350.39,238.27) --
-	(351.49,238.86) --
-	(354.19,240.24) --
-	(354.41,240.37) --
-	(354.96,240.65) --
-	(354.99,240.67) --
-	(355.28,240.79) --
-	(355.84,241.02) --
-	(356.71,241.48) --
-	(356.75,241.51) --
-	(357.50,241.86) --
-	(357.53,241.87) --
-	(358.04,242.13) --
-	(358.62,242.42) --
-	(359.31,242.81) --
-	(359.62,242.94) --
-	(359.75,243.03) --
-	(359.85,243.09) --
-	(360.61,243.54) --
-	(360.64,243.55) --
-	(360.71,243.59) --
-	(361.91,244.20) --
-	(362.60,244.50) --
-	(364.24,245.24) --
-	(364.46,245.35) --
-	(365.70,245.99) --
-	(366.29,246.26) --
-	(370.53,248.44) --
-	(371.02,248.71) --
-	(372.06,249.22) --
-	(372.07,249.22) --
-	(372.38,249.33) --
-	(372.60,249.45) --
-	(372.90,249.61) --
-	(373.16,249.73) --
-	(373.53,249.89) --
-	(373.80,250.04) --
-	(374.46,250.35) --
-	(374.81,250.52) --
-	(375.77,251.03) --
-	(376.36,251.34) --
-	(376.51,251.43) --
-	(376.93,251.64) --
-	(378.03,252.22) --
-	(379.36,252.85) --
-	(379.36,252.86) --
-	(380.09,253.22) --
-	(380.12,253.24) --
-	(381.03,253.71) --
-	(381.47,253.91) --
-	(381.75,254.05) --
-	(382.36,254.37) --
-	(382.44,254.41) --
-	(382.57,254.46) --
-	(383.02,254.69) --
-	(385.04,255.76) --
-	(385.16,255.82) --
-	(388.87,257.82) --
-	(393.56,260.29) --
-	(395.71,261.42) --
+\path[fill=fillColor,fill opacity=0.30] ( 52.97,170.47) --
+	( 61.01,171.42) --
+	( 65.48,171.92) --
+	( 65.62,171.94) --
+	( 79.64,173.62) --
+	( 88.50,174.72) --
+	( 94.41,175.36) --
+	( 97.84,175.84) --
+	(104.50,176.60) --
+	(110.01,177.24) --
+	(113.94,177.93) --
+	(116.56,178.20) --
+	(124.94,179.24) --
+	(160.01,184.17) --
+	(160.15,184.18) --
+	(163.56,184.51) --
+	(164.50,184.59) --
+	(175.08,186.23) --
+	(177.68,186.60) --
+	(185.12,187.82) --
+	(195.04,189.45) --
+	(195.05,189.45) --
+	(199.79,190.58) --
+	(200.09,190.62) --
+	(201.70,190.93) --
+	(202.42,191.10) --
+	(203.15,191.25) --
+	(203.24,191.25) --
+	(203.92,191.30) --
+	(204.08,191.31) --
+	(205.70,191.75) --
+	(211.30,192.92) --
+	(213.02,193.28) --
+	(213.22,193.33) --
+	(213.28,193.35) --
+	(214.88,193.63) --
+	(219.39,194.53) --
+	(219.87,194.68) --
+	(224.51,195.65) --
+	(226.38,196.05) --
+	(226.89,196.15) --
+	(228.22,196.41) --
+	(229.80,196.85) --
+	(230.53,197.01) --
+	(231.54,197.24) --
+	(232.29,197.36) --
+	(232.55,197.40) --
+	(232.60,197.41) --
+	(233.03,197.50) --
+	(236.50,198.30) --
+	(238.44,198.81) --
+	(239.50,199.08) --
+	(240.76,199.42) --
+	(242.87,200.00) --
+	(243.82,200.19) --
+	(244.87,200.39) --
+	(245.90,200.62) --
+	(247.14,200.93) --
+	(247.15,200.93) --
+	(248.00,201.17) --
+	(248.59,201.32) --
+	(249.15,201.48) --
+	(249.91,201.67) --
+	(250.14,201.73) --
+	(250.71,201.90) --
+	(251.21,202.02) --
+	(251.61,202.16) --
+	(251.88,202.27) --
+	(252.52,202.50) --
+	(252.98,202.60) --
+	(253.12,202.63) --
+	(253.36,202.70) --
+	(254.91,203.17) --
+	(255.02,203.20) --
+	(256.32,203.41) --
+	(258.61,204.14) --
+	(260.03,204.46) --
+	(260.14,204.50) --
+	(260.80,204.66) --
+	(261.97,205.06) --
+	(262.19,205.14) --
+	(262.48,205.20) --
+	(262.99,205.39) --
+	(264.29,205.73) --
+	(264.50,205.78) --
+	(264.53,205.79) --
+	(264.97,205.90) --
+	(266.10,206.25) --
+	(266.13,206.27) --
+	(266.44,206.39) --
+	(267.28,206.57) --
+	(267.71,206.73) --
+	(268.38,206.99) --
+	(269.11,207.18) --
+	(269.74,207.29) --
+	(269.87,207.31) --
+	(271.02,207.71) --
+	(271.10,207.73) --
+	(271.68,207.94) --
+	(272.40,208.09) --
+	(272.79,208.15) --
+	(273.63,208.42) --
+	(274.52,208.72) --
+	(275.28,208.98) --
+	(275.59,209.10) --
+	(276.13,209.32) --
+	(276.31,209.37) --
+	(276.77,209.50) --
+	(277.30,209.67) --
+	(277.98,209.90) --
+	(278.04,209.92) --
+	(278.45,210.08) --
+	(279.17,210.31) --
+	(279.30,210.34) --
+	(279.52,210.40) --
+	(279.66,210.45) --
+	(279.69,210.46) --
+	(280.15,210.58) --
+	(280.53,210.74) --
+	(280.72,210.81) --
+	(281.20,210.99) --
+	(281.36,211.04) --
+	(281.45,211.05) --
+	(282.80,211.51) --
+	(283.05,211.59) --
+	(283.89,211.98) --
+	(283.98,212.01) --
+	(284.07,212.04) --
+	(284.62,212.16) --
+	(284.86,212.24) --
+	(285.04,212.27) --
+	(285.13,212.29) --
+	(286.00,212.55) --
+	(286.57,212.69) --
+	(286.59,212.70) --
+	(287.25,212.92) --
+	(287.81,213.15) --
+	(288.54,213.43) --
+	(288.59,213.45) --
+	(289.22,213.66) --
+	(289.76,213.90) --
+	(290.76,214.26) --
+	(290.86,214.30) --
+	(291.20,214.44) --
+	(291.32,214.50) --
+	(291.81,214.76) --
+	(291.88,214.79) --
+	(292.21,214.88) --
+	(292.36,214.93) --
+	(292.42,214.94) --
+	(292.49,214.96) --
+	(292.51,214.97) --
+	(292.62,215.01) --
+	(293.21,215.25) --
+	(293.91,215.52) --
+	(295.25,215.94) --
+	(295.45,215.99) --
+	(295.51,216.01) --
+	(295.93,216.15) --
+	(295.99,216.18) --
+	(296.10,216.23) --
+	(296.47,216.40) --
+	(296.65,216.46) --
+	(296.99,216.55) --
+	(297.01,216.56) --
+	(297.04,216.58) --
+	(297.05,216.58) --
+	(297.09,216.61) --
+	(297.13,216.63) --
+	(297.22,216.69) --
+	(297.31,216.73) --
+	(297.31,216.73) --
+	(297.71,216.87) --
+	(297.96,216.95) --
+	(298.34,217.07) --
+	(298.57,217.15) --
+	(299.05,217.32) --
+	(300.58,217.91) --
+	(300.69,217.95) --
+	(301.32,218.15) --
+	(302.10,218.48) --
+	(302.23,218.52) --
+	(302.50,218.58) --
+	(302.82,218.68) --
+	(302.98,218.74) --
+	(303.49,218.99) --
+	(303.87,219.11) --
+	(304.04,219.19) --
+	(304.05,219.19) --
+	(304.17,219.25) --
+	(304.21,219.25) --
+	(304.88,219.55) --
+	(305.44,219.84) --
+	(305.52,219.87) --
+	(305.61,219.90) --
+	(305.86,219.96) --
+	(306.19,220.13) --
+	(306.32,220.15) --
+	(307.91,220.71) --
+	(307.96,220.73) --
+	(308.47,220.90) --
+	(308.57,220.93) --
+	(309.22,221.23) --
+	(309.44,221.32) --
+	(309.51,221.37) --
+	(309.67,221.40) --
+	(310.00,221.57) --
+	(310.25,221.71) --
+	(310.76,221.86) --
+	(310.92,221.92) --
+	(311.04,221.97) --
+	(311.16,222.02) --
+	(311.41,222.13) --
+	(311.41,222.13) --
+	(311.44,222.14) --
+	(311.54,222.18) --
+	(311.68,222.24) --
+	(311.68,222.24) --
+	(311.88,222.33) --
+	(312.22,222.47) --
+	(312.92,222.75) --
+	(313.12,222.83) --
+	(313.27,222.87) --
+	(313.53,222.95) --
+	(313.83,223.10) --
+	(314.24,223.23) --
+	(314.31,223.26) --
+	(314.45,223.33) --
+	(314.63,223.41) --
+	(315.00,223.57) --
+	(315.21,223.65) --
+	(315.23,223.66) --
+	(315.37,223.70) --
+	(315.48,223.72) --
+	(315.51,223.72) --
+	(315.62,223.77) --
+	(315.70,223.81) --
+	(315.79,223.85) --
+	(316.13,224.06) --
+	(316.22,224.13) --
+	(316.38,224.22) --
+	(316.61,224.27) --
+	(316.93,224.41) --
+	(317.07,224.44) --
+	(317.20,224.49) --
+	(317.36,224.54) --
+	(317.75,224.75) --
+	(317.76,224.76) --
+	(317.79,224.77) --
+	(317.86,224.78) --
+	(317.89,224.79) --
+	(317.98,224.81) --
+	(318.43,224.96) --
+	(318.60,225.02) --
+	(318.85,225.15) --
+	(319.11,225.26) --
+	(319.21,225.29) --
+	(319.52,225.41) --
+	(319.81,225.55) --
+	(320.44,225.84) --
+	(321.85,226.35) --
+	(321.91,226.39) --
+	(322.04,226.46) --
+	(322.30,226.62) --
+	(322.60,226.79) --
+	(322.75,226.88) --
+	(323.02,227.04) --
+	(323.10,227.08) --
+	(323.28,227.19) --
+	(324.05,227.52) --
+	(324.42,227.66) --
+	(324.61,227.72) --
+	(324.72,227.76) --
+	(325.08,227.86) --
+	(325.99,228.30) --
+	(326.58,228.58) --
+	(326.72,228.65) --
+	(327.61,229.10) --
+	(327.91,229.23) --
+	(328.67,229.53) --
+	(328.94,229.64) --
+	(329.07,229.70) --
+	(329.52,229.91) --
+	(331.17,230.54) --
+	(332.00,230.87) --
+	(332.27,230.97) --
+	(333.07,231.28) --
+	(333.19,231.32) --
+	(333.76,231.57) --
+	(335.51,232.30) --
+	(336.07,232.58) --
+	(336.75,232.91) --
+	(336.88,232.96) --
+	(337.54,233.20) --
+	(337.92,233.41) --
+	(338.29,233.66) --
+	(338.32,233.68) --
+	(338.37,233.71) --
+	(338.79,233.92) --
+	(338.87,233.95) --
+	(339.41,234.15) --
+	(339.54,234.20) --
+	(340.26,234.46) --
+	(340.28,234.46) --
+	(340.36,234.50) --
+	(340.58,234.59) --
+	(340.90,234.71) --
+	(341.07,234.78) --
+	(341.38,234.92) --
+	(341.48,234.98) --
+	(341.53,235.00) --
+	(341.57,235.03) --
+	(342.00,235.27) --
+	(342.06,235.30) --
+	(342.60,235.57) --
+	(342.92,235.69) --
+	(344.39,236.26) --
+	(344.81,236.45) --
+	(345.03,236.56) --
+	(345.51,236.76) --
+	(345.56,236.78) --
+	(346.27,237.20) --
+	(348.09,238.13) --
+	(348.19,238.20) --
+	(348.32,238.28) --
+	(348.52,238.35) --
+	(348.65,238.39) --
+	(350.04,239.05) --
+	(350.29,239.17) --
+	(350.39,239.24) --
+	(351.49,239.80) --
+	(354.19,240.95) --
+	(354.41,241.02) --
+	(354.96,241.26) --
+	(354.99,241.28) --
+	(355.28,241.43) --
+	(355.84,241.70) --
+	(356.71,242.13) --
+	(356.75,242.15) --
+	(357.50,242.49) --
+	(357.53,242.50) --
+	(358.04,242.80) --
+	(358.62,243.06) --
+	(359.31,243.37) --
+	(359.62,243.47) --
+	(359.75,243.52) --
+	(359.85,243.55) --
+	(360.61,243.94) --
+	(360.64,243.96) --
+	(360.71,244.00) --
+	(361.91,244.47) --
+	(362.60,244.81) --
+	(364.24,245.62) --
+	(364.46,245.74) --
+	(365.70,246.32) --
+	(366.29,246.62) --
+	(370.53,248.75) --
+	(371.02,248.94) --
+	(372.06,249.52) --
+	(372.07,249.52) --
+	(372.38,249.70) --
+	(372.60,249.79) --
+	(372.90,249.94) --
+	(373.16,250.08) --
+	(373.53,250.23) --
+	(373.80,250.37) --
+	(374.46,250.74) --
+	(374.81,250.92) --
+	(375.77,251.40) --
+	(376.36,251.70) --
+	(376.51,251.79) --
+	(376.93,252.03) --
+	(378.03,252.55) --
+	(379.36,253.32) --
+	(379.36,253.33) --
+	(380.09,253.71) --
+	(380.12,253.73) --
+	(381.03,254.16) --
+	(381.47,254.34) --
+	(381.75,254.50) --
+	(382.36,254.82) --
+	(382.44,254.87) --
+	(382.57,254.96) --
+	(383.02,255.16) --
+	(385.04,256.33) --
+	(385.16,256.40) --
+	(388.87,257.98) --
+	(393.56,260.47) --
+	(395.71,261.52) --
 	(403.26,265.59) --
 	(404.02,265.99) --
-	(404.02,182.27) --
-	(403.26,182.16) --
-	(395.71,180.94) --
-	(393.56,180.61) --
-	(388.87,179.73) --
-	(385.16,179.04) --
-	(385.04,179.03) --
-	(383.02,178.81) --
-	(382.57,178.70) --
-	(382.44,178.65) --
-	(382.36,178.61) --
-	(381.75,178.55) --
-	(381.47,178.49) --
-	(381.03,178.47) --
-	(380.12,178.30) --
-	(380.09,178.30) --
-	(379.36,178.16) --
-	(379.36,178.16) --
-	(378.03,177.94) --
-	(376.93,177.72) --
-	(376.51,177.66) --
-	(376.36,177.65) --
-	(375.77,177.59) --
-	(374.81,177.41) --
-	(374.46,177.37) --
-	(373.80,177.19) --
-	(373.53,177.12) --
-	(373.16,177.03) --
-	(372.90,176.96) --
-	(372.60,176.88) --
-	(372.38,176.82) --
-	(372.07,176.74) --
-	(372.06,176.74) --
-	(371.02,176.61) --
-	(370.53,176.50) --
-	(366.29,175.56) --
-	(365.70,175.48) --
-	(364.46,175.26) --
-	(364.24,175.21) --
-	(362.60,174.88) --
-	(361.91,174.73) --
-	(360.71,174.46) --
-	(360.64,174.43) --
-	(360.61,174.42) --
-	(359.85,174.28) --
-	(359.75,174.26) --
-	(359.62,174.24) --
-	(359.31,174.18) --
-	(358.62,174.10) --
-	(358.04,174.00) --
-	(357.53,173.89) --
-	(357.50,173.88) --
-	(356.75,173.74) --
-	(356.71,173.73) --
-	(355.84,173.55) --
-	(355.28,173.44) --
-	(354.99,173.38) --
-	(354.96,173.38) --
-	(354.41,173.27) --
-	(354.19,173.22) --
-	(351.49,172.56) --
-	(350.39,172.25) --
-	(350.29,172.22) --
-	(350.04,172.22) --
-	(348.65,172.01) --
-	(348.52,171.96) --
-	(348.32,171.89) --
-	(348.19,171.87) --
-	(348.09,171.85) --
-	(346.27,171.41) --
-	(345.56,171.26) --
-	(345.51,171.26) --
-	(345.03,171.14) --
-	(344.81,171.13) --
-	(344.39,171.04) --
-	(342.92,170.73) --
-	(342.60,170.68) --
-	(342.06,170.59) --
-	(342.00,170.58) --
-	(341.57,170.51) --
-	(341.53,170.50) --
-	(341.48,170.48) --
-	(341.38,170.46) --
-	(341.07,170.41) --
-	(340.90,170.35) --
-	(340.58,170.27) --
-	(340.36,170.25) --
-	(340.28,170.24) --
-	(340.26,170.24) --
-	(339.54,170.08) --
-	(339.41,170.03) --
-	(338.87,169.90) --
-	(338.79,169.88) --
-	(338.37,169.75) --
-	(338.32,169.74) --
-	(338.29,169.73) --
-	(337.92,169.66) --
-	(337.54,169.63) --
-	(336.88,169.52) --
-	(336.75,169.49) --
-	(336.07,169.33) --
-	(335.51,169.18) --
-	(333.76,168.91) --
-	(333.19,168.80) --
-	(333.07,168.78) --
-	(332.27,168.47) --
-	(332.00,168.39) --
-	(331.17,168.19) --
-	(329.52,167.74) --
-	(329.07,167.64) --
-	(328.94,167.62) --
-	(328.67,167.52) --
-	(327.91,167.32) --
-	(327.61,167.25) --
-	(326.72,167.12) --
-	(326.58,167.07) --
-	(325.99,166.89) --
-	(325.08,166.68) --
-	(324.72,166.60) --
-	(324.61,166.57) --
-	(324.42,166.53) --
-	(324.05,166.45) --
-	(323.28,166.24) --
-	(323.10,166.20) --
-	(323.02,166.19) --
-	(322.75,166.13) --
-	(322.60,166.08) --
-	(322.30,166.02) --
-	(322.04,165.95) --
-	(321.91,165.91) --
-	(321.85,165.90) --
-	(320.44,165.54) --
-	(319.81,165.48) --
-	(319.52,165.41) --
-	(319.21,165.35) --
-	(319.11,165.31) --
-	(318.85,165.22) --
-	(318.60,165.15) --
-	(318.43,165.12) --
-	(317.98,165.00) --
-	(317.89,164.98) --
-	(317.86,164.98) --
-	(317.79,164.97) --
-	(317.76,164.96) --
-	(317.75,164.96) --
-	(317.36,164.87) --
-	(317.20,164.84) --
-	(317.07,164.81) --
-	(316.93,164.77) --
-	(316.61,164.69) --
-	(316.38,164.64) --
-	(316.22,164.63) --
-	(316.13,164.63) --
-	(315.79,164.58) --
-	(315.70,164.56) --
-	(315.62,164.55) --
-	(315.51,164.53) --
-	(315.48,164.52) --
-	(315.37,164.49) --
-	(315.23,164.45) --
-	(315.21,164.44) --
-	(315.00,164.38) --
-	(314.63,164.28) --
-	(314.45,164.23) --
-	(314.31,164.17) --
-	(314.24,164.15) --
-	(313.83,164.06) --
-	(313.53,163.97) --
-	(313.27,163.89) --
-	(313.12,163.80) --
-	(312.92,163.72) --
-	(312.22,163.58) --
-	(311.88,163.47) --
-	(311.68,163.41) --
-	(311.68,163.41) --
-	(311.54,163.36) --
-	(311.44,163.32) --
-	(311.41,163.32) --
-	(311.41,163.32) --
-	(311.16,163.25) --
-	(311.04,163.22) --
-	(310.92,163.20) --
-	(310.76,163.15) --
-	(310.25,163.05) --
-	(310.00,162.99) --
-	(309.67,162.92) --
-	(309.51,162.86) --
-	(309.44,162.83) --
-	(309.22,162.77) --
-	(308.57,162.62) --
-	(308.47,162.60) --
-	(307.96,162.44) --
-	(307.91,162.43) --
-	(306.32,161.94) --
-	(306.19,161.90) --
-	(305.86,161.80) --
-	(305.61,161.73) --
-	(305.52,161.70) --
-	(305.44,161.68) --
-	(304.88,161.50) --
-	(304.21,161.34) --
-	(304.17,161.33) --
-	(304.05,161.30) --
-	(304.04,161.30) --
-	(303.87,161.27) --
-	(303.49,161.16) --
-	(302.98,161.00) --
-	(302.82,160.95) --
-	(302.50,160.89) --
-	(302.23,160.84) --
-	(302.10,160.82) --
-	(301.32,160.64) --
-	(300.69,160.55) --
-	(300.58,160.54) --
-	(299.04,160.13) --
-	(298.57,160.04) --
-	(298.34,159.99) --
-	(297.96,159.86) --
-	(297.71,159.79) --
-	(297.31,159.71) --
-	(297.31,159.71) --
-	(297.22,159.67) --
-	(297.13,159.62) --
-	(297.09,159.60) --
-	(297.05,159.58) --
-	(297.04,159.58) --
-	(297.01,159.57) --
-	(296.99,159.56) --
-	(296.65,159.45) --
-	(296.47,159.35) --
-	(296.10,159.26) --
-	(295.99,159.24) --
-	(295.93,159.23) --
-	(295.51,159.10) --
-	(295.45,159.08) --
-	(295.25,159.01) --
-	(293.91,158.66) --
-	(293.21,158.46) --
-	(292.62,158.25) --
-	(292.51,158.22) --
-	(292.49,158.21) --
-	(292.42,158.20) --
-	(292.36,158.18) --
-	(292.21,158.15) --
-	(291.88,158.09) --
-	(291.81,158.08) --
-	(291.32,157.93) --
-	(291.20,157.93) --
-	(290.86,157.83) --
-	(290.76,157.78) --
-	(289.76,157.50) --
-	(289.22,157.31) --
-	(288.59,157.10) --
-	(288.54,157.09) --
-	(287.81,156.93) --
-	(287.25,156.69) --
-	(286.59,156.44) --
-	(286.57,156.44) --
-	(286.00,156.29) --
-	(285.13,156.04) --
-	(285.03,156.02) --
-	(284.86,155.95) --
-	(284.62,155.87) --
-	(284.07,155.70) --
-	(283.98,155.67) --
-	(283.89,155.63) --
-	(283.05,155.39) --
-	(282.80,155.29) --
-	(281.45,154.91) --
-	(281.36,154.89) --
-	(281.20,154.85) --
-	(280.72,154.72) --
-	(280.53,154.68) --
-	(280.15,154.56) --
-	(279.69,154.48) --
-	(279.66,154.48) --
-	(279.52,154.44) --
-	(279.30,154.38) --
-	(279.17,154.34) --
-	(278.45,154.06) --
-	(278.04,153.95) --
-	(277.98,153.93) --
-	(277.30,153.70) --
-	(276.77,153.46) --
-	(276.31,153.28) --
-	(276.13,153.22) --
-	(275.59,153.06) --
-	(275.28,152.95) --
-	(274.52,152.77) --
-	(273.63,152.39) --
-	(272.79,152.07) --
-	(272.40,151.94) --
-	(271.68,151.70) --
-	(271.10,151.43) --
-	(271.02,151.41) --
-	(269.87,151.00) --
-	(269.74,150.96) --
-	(269.11,150.78) --
-	(268.38,150.50) --
-	(267.71,150.29) --
-	(267.28,150.15) --
-	(266.44,149.85) --
-	(266.13,149.74) --
-	(266.10,149.73) --
-	(264.97,149.27) --
-	(264.53,149.09) --
-	(264.50,149.08) --
-	(264.29,149.03) --
-	(262.99,148.54) --
-	(262.48,148.27) --
-	(262.19,148.19) --
-	(261.97,148.12) --
-	(260.80,147.75) --
-	(260.14,147.55) --
-	(260.03,147.49) --
-	(258.61,146.90) --
-	(256.32,145.98) --
-	(255.02,145.42) --
-	(254.91,145.38) --
-	(253.36,144.78) --
-	(253.12,144.70) --
-	(252.98,144.64) --
-	(252.52,144.47) --
-	(251.88,144.26) --
-	(251.61,144.16) --
-	(251.21,144.00) --
-	(250.71,143.81) --
-	(250.14,143.57) --
-	(249.91,143.49) --
-	(249.15,143.20) --
-	(248.59,142.98) --
-	(248.00,142.78) --
-	(247.15,142.45) --
-	(247.14,142.44) --
-	(245.90,142.02) --
-	(244.87,141.53) --
-	(243.82,141.15) --
-	(242.87,140.79) --
-	(240.76,139.96) --
-	(239.50,139.44) --
-	(238.44,139.02) --
-	(236.50,138.27) --
-	(233.03,136.65) --
-	(232.60,136.47) --
-	(232.55,136.45) --
-	(232.29,136.34) --
-	(231.54,136.09) --
-	(230.53,135.66) --
-	(229.80,135.35) --
-	(228.22,134.60) --
-	(226.89,134.03) --
-	(226.38,133.85) --
-	(224.51,133.07) --
-	(219.87,130.96) --
-	(219.39,130.73) --
-	(214.88,128.51) --
-	(213.28,127.81) --
-	(213.22,127.78) --
-	(213.02,127.70) --
-	(211.30,126.92) --
-	(205.70,124.51) --
-	(204.08,123.77) --
-	(203.92,123.68) --
-	(203.24,123.35) --
-	(203.15,123.31) --
-	(202.42,123.02) --
-	(201.70,122.67) --
-	(200.09,121.90) --
-	(199.79,121.73) --
-	(195.05,119.42) --
-	(195.04,119.41) --
-	(185.12,114.89) --
-	(177.68,111.26) --
-	(175.08,110.08) --
-	(164.50,104.62) --
-	(163.56,104.15) --
-	(160.15,102.47) --
-	(160.01,102.40) --
-	(124.94, 84.29) --
-	(116.56, 79.63) --
-	(113.94, 78.09) --
-	(110.01, 75.93) --
-	(104.50, 73.31) --
-	( 97.84, 69.48) --
-	( 94.41, 67.75) --
-	( 88.50, 64.75) --
-	( 79.64, 59.82) --
-	( 65.62, 51.87) --
-	( 65.48, 51.79) --
-	( 61.01, 49.34) --
+	(404.02,182.81) --
+	(403.26,182.73) --
+	(395.71,181.79) --
+	(393.56,181.46) --
+	(388.87,180.68) --
+	(385.16,180.00) --
+	(385.04,179.96) --
+	(383.02,179.75) --
+	(382.57,179.67) --
+	(382.44,179.66) --
+	(382.36,179.64) --
+	(381.75,179.59) --
+	(381.47,179.52) --
+	(381.03,179.41) --
+	(380.12,179.26) --
+	(380.09,179.26) --
+	(379.36,179.10) --
+	(379.36,179.10) --
+	(378.03,178.84) --
+	(376.93,178.70) --
+	(376.51,178.67) --
+	(376.36,178.66) --
+	(375.77,178.52) --
+	(374.81,178.34) --
+	(374.46,178.30) --
+	(373.80,178.15) --
+	(373.53,178.09) --
+	(373.16,178.02) --
+	(372.90,177.97) --
+	(372.60,177.93) --
+	(372.38,177.89) --
+	(372.07,177.86) --
+	(372.06,177.86) --
+	(371.02,177.63) --
+	(370.53,177.50) --
+	(366.29,176.69) --
+	(365.70,176.59) --
+	(364.46,176.36) --
+	(364.24,176.31) --
+	(362.60,175.96) --
+	(361.91,175.81) --
+	(360.71,175.55) --
+	(360.64,175.55) --
+	(360.61,175.54) --
+	(359.85,175.40) --
+	(359.75,175.38) --
+	(359.62,175.36) --
+	(359.31,175.29) --
+	(358.62,175.15) --
+	(358.04,175.03) --
+	(357.53,174.93) --
+	(357.50,174.92) --
+	(356.75,174.77) --
+	(356.71,174.76) --
+	(355.84,174.61) --
+	(355.28,174.53) --
+	(354.99,174.45) --
+	(354.96,174.44) --
+	(354.41,174.32) --
+	(354.19,174.27) --
+	(351.49,173.63) --
+	(350.39,173.47) --
+	(350.29,173.45) --
+	(350.04,173.40) --
+	(348.65,173.12) --
+	(348.52,173.09) --
+	(348.32,173.07) --
+	(348.19,173.04) --
+	(348.09,173.02) --
+	(346.27,172.69) --
+	(345.56,172.63) --
+	(345.51,172.62) --
+	(345.03,172.50) --
+	(344.81,172.46) --
+	(344.39,172.37) --
+	(342.92,172.08) --
+	(342.60,171.98) --
+	(342.06,171.86) --
+	(342.00,171.85) --
+	(341.57,171.77) --
+	(341.53,171.76) --
+	(341.48,171.75) --
+	(341.38,171.73) --
+	(341.07,171.67) --
+	(340.90,171.64) --
+	(340.58,171.55) --
+	(340.36,171.51) --
+	(340.28,171.49) --
+	(340.26,171.48) --
+	(339.54,171.28) --
+	(339.41,171.24) --
+	(338.87,171.08) --
+	(338.79,171.06) --
+	(338.37,170.94) --
+	(338.32,170.93) --
+	(338.29,170.92) --
+	(337.92,170.81) --
+	(337.54,170.77) --
+	(336.88,170.59) --
+	(336.75,170.55) --
+	(336.07,170.33) --
+	(335.51,170.22) --
+	(333.76,169.79) --
+	(333.19,169.68) --
+	(333.07,169.68) --
+	(332.27,169.47) --
+	(332.00,169.41) --
+	(331.17,169.20) --
+	(329.52,168.69) --
+	(329.07,168.59) --
+	(328.94,168.56) --
+	(328.67,168.48) --
+	(327.91,168.38) --
+	(327.61,168.29) --
+	(326.72,168.13) --
+	(326.58,168.12) --
+	(325.99,168.06) --
+	(325.08,167.81) --
+	(324.72,167.72) --
+	(324.61,167.68) --
+	(324.42,167.61) --
+	(324.05,167.47) --
+	(323.28,167.37) --
+	(323.10,167.31) --
+	(323.02,167.30) --
+	(322.75,167.20) --
+	(322.60,167.17) --
+	(322.30,167.12) --
+	(322.04,167.03) --
+	(321.91,167.02) --
+	(321.85,167.01) --
+	(320.44,166.60) --
+	(319.81,166.49) --
+	(319.52,166.44) --
+	(319.21,166.38) --
+	(319.11,166.36) --
+	(318.85,166.30) --
+	(318.60,166.26) --
+	(318.43,166.24) --
+	(317.98,166.17) --
+	(317.89,166.14) --
+	(317.86,166.13) --
+	(317.79,166.12) --
+	(317.76,166.11) --
+	(317.75,166.11) --
+	(317.36,166.04) --
+	(317.20,165.97) --
+	(317.07,165.93) --
+	(316.93,165.90) --
+	(316.61,165.79) --
+	(316.38,165.72) --
+	(316.22,165.65) --
+	(316.13,165.64) --
+	(315.79,165.57) --
+	(315.70,165.57) --
+	(315.62,165.54) --
+	(315.51,165.53) --
+	(315.48,165.53) --
+	(315.37,165.51) --
+	(315.23,165.50) --
+	(315.21,165.50) --
+	(315.00,165.43) --
+	(314.63,165.31) --
+	(314.45,165.25) --
+	(314.31,165.20) --
+	(314.24,165.17) --
+	(313.83,165.06) --
+	(313.53,164.99) --
+	(313.27,164.87) --
+	(313.12,164.81) --
+	(312.92,164.74) --
+	(312.22,164.53) --
+	(311.88,164.43) --
+	(311.68,164.35) --
+	(311.68,164.35) --
+	(311.54,164.30) --
+	(311.44,164.29) --
+	(311.41,164.29) --
+	(311.41,164.29) --
+	(311.16,164.26) --
+	(311.04,164.22) --
+	(310.92,164.18) --
+	(310.76,164.12) --
+	(310.25,163.95) --
+	(310.00,163.87) --
+	(309.67,163.76) --
+	(309.51,163.70) --
+	(309.44,163.67) --
+	(309.22,163.60) --
+	(308.57,163.38) --
+	(308.47,163.35) --
+	(307.96,163.16) --
+	(307.91,163.14) --
+	(306.32,162.74) --
+	(306.19,162.69) --
+	(305.86,162.59) --
+	(305.61,162.52) --
+	(305.52,162.49) --
+	(305.44,162.46) --
+	(304.88,162.30) --
+	(304.21,162.10) --
+	(304.17,162.08) --
+	(304.05,162.05) --
+	(304.04,162.04) --
+	(303.87,162.00) --
+	(303.49,161.95) --
+	(302.98,161.79) --
+	(302.82,161.75) --
+	(302.50,161.60) --
+	(302.23,161.57) --
+	(302.10,161.55) --
+	(301.32,161.31) --
+	(300.69,161.08) --
+	(300.58,161.05) --
+	(299.05,160.72) --
+	(298.57,160.58) --
+	(298.34,160.51) --
+	(297.96,160.38) --
+	(297.71,160.30) --
+	(297.31,160.19) --
+	(297.31,160.19) --
+	(297.22,160.17) --
+	(297.13,160.15) --
+	(297.09,160.14) --
+	(297.05,160.13) --
+	(297.04,160.13) --
+	(297.01,160.12) --
+	(296.99,160.11) --
+	(296.65,160.04) --
+	(296.47,160.00) --
+	(296.10,159.87) --
+	(295.99,159.83) --
+	(295.93,159.82) --
+	(295.51,159.67) --
+	(295.45,159.65) --
+	(295.25,159.59) --
+	(293.91,159.27) --
+	(293.21,158.98) --
+	(292.62,158.85) --
+	(292.51,158.82) --
+	(292.49,158.81) --
+	(292.42,158.79) --
+	(292.36,158.76) --
+	(292.21,158.73) --
+	(291.88,158.60) --
+	(291.81,158.58) --
+	(291.32,158.39) --
+	(291.20,158.36) --
+	(290.86,158.25) --
+	(290.76,158.21) --
+	(289.76,157.85) --
+	(289.22,157.64) --
+	(288.59,157.49) --
+	(288.54,157.48) --
+	(287.81,157.20) --
+	(287.25,157.08) --
+	(286.59,156.84) --
+	(286.57,156.83) --
+	(286.00,156.63) --
+	(285.13,156.33) --
+	(285.04,156.28) --
+	(284.86,156.20) --
+	(284.62,156.11) --
+	(284.07,155.96) --
+	(283.98,155.93) --
+	(283.89,155.89) --
+	(283.05,155.58) --
+	(282.80,155.54) --
+	(281.45,155.14) --
+	(281.36,155.11) --
+	(281.20,155.07) --
+	(280.72,154.94) --
+	(280.53,154.88) --
+	(280.15,154.75) --
+	(279.69,154.60) --
+	(279.66,154.59) --
+	(279.52,154.55) --
+	(279.30,154.46) --
+	(279.17,154.42) --
+	(278.45,154.23) --
+	(278.04,154.06) --
+	(277.98,154.03) --
+	(277.30,153.77) --
+	(276.77,153.59) --
+	(276.31,153.43) --
+	(276.13,153.37) --
+	(275.59,153.18) --
+	(275.28,153.08) --
+	(274.52,152.92) --
+	(273.63,152.60) --
+	(272.79,152.35) --
+	(272.40,152.29) --
+	(271.68,152.02) --
+	(271.10,151.79) --
+	(271.02,151.75) --
+	(269.87,151.37) --
+	(269.74,151.31) --
+	(269.11,151.10) --
+	(268.38,150.82) --
+	(267.71,150.63) --
+	(267.28,150.49) --
+	(266.44,150.19) --
+	(266.13,150.09) --
+	(266.10,150.08) --
+	(264.97,149.73) --
+	(264.53,149.58) --
+	(264.50,149.57) --
+	(264.29,149.50) --
+	(262.99,148.98) --
+	(262.48,148.79) --
+	(262.19,148.70) --
+	(261.97,148.61) --
+	(260.80,148.23) --
+	(260.14,147.97) --
+	(260.03,147.91) --
+	(258.61,147.39) --
+	(256.32,146.54) --
+	(255.02,146.07) --
+	(254.91,146.03) --
+	(253.36,145.49) --
+	(253.12,145.41) --
+	(252.98,145.36) --
+	(252.52,145.15) --
+	(251.88,144.89) --
+	(251.61,144.78) --
+	(251.21,144.61) --
+	(250.71,144.40) --
+	(250.14,144.19) --
+	(249.91,144.08) --
+	(249.15,143.82) --
+	(248.59,143.55) --
+	(248.00,143.31) --
+	(247.15,143.00) --
+	(247.14,142.99) --
+	(245.90,142.54) --
+	(244.87,142.05) --
+	(243.82,141.66) --
+	(242.87,141.28) --
+	(240.76,140.36) --
+	(239.50,139.84) --
+	(238.44,139.43) --
+	(236.50,138.65) --
+	(233.03,137.25) --
+	(232.60,137.08) --
+	(232.55,137.06) --
+	(232.29,136.94) --
+	(231.54,136.62) --
+	(230.53,136.14) --
+	(229.80,135.84) --
+	(228.22,135.16) --
+	(226.89,134.52) --
+	(226.38,134.30) --
+	(224.51,133.47) --
+	(219.87,131.27) --
+	(219.39,131.04) --
+	(214.88,129.12) --
+	(213.28,128.37) --
+	(213.22,128.34) --
+	(213.02,128.24) --
+	(211.30,127.42) --
+	(205.70,125.04) --
+	(204.08,124.36) --
+	(203.92,124.31) --
+	(203.24,124.02) --
+	(203.15,123.98) --
+	(202.42,123.65) --
+	(201.70,123.29) --
+	(200.09,122.49) --
+	(199.79,122.31) --
+	(195.05,119.88) --
+	(195.04,119.88) --
+	(185.12,115.12) --
+	(177.68,111.43) --
+	(175.08,110.16) --
+	(164.50,105.01) --
+	(163.56,104.57) --
+	(160.15,102.91) --
+	(160.01,102.85) --
+	(124.94, 84.46) --
+	(116.56, 79.86) --
+	(113.94, 78.49) --
+	(110.01, 76.18) --
+	(104.50, 73.14) --
+	( 97.84, 69.47) --
+	( 94.41, 67.70) --
+	( 88.50, 64.37) --
+	( 79.64, 59.56) --
+	( 65.62, 51.98) --
+	( 65.48, 51.89) --
+	( 61.01, 49.61) --
 	( 52.97, 45.08) --
@@
 
-\path[fill=fillColor,fill opacity=0.50] ( 52.97,157.52) --
-	( 61.01,158.71) --
-	( 65.48,159.33) --
-	( 65.62,159.35) --
-	( 79.64,161.53) --
-	( 88.50,163.05) --
-	( 94.41,164.05) --
-	( 97.84,164.63) --
-	(104.50,165.72) --
-	(110.01,166.51) --
-	(113.94,167.24) --
-	(116.56,167.79) --
-	(124.94,169.05) --
-	(160.01,175.04) --
-	(160.15,175.05) --
-	(163.56,175.67) --
-	(164.50,175.82) --
-	(175.08,178.09) --
-	(177.68,178.61) --
-	(185.12,180.03) --
-	(195.04,182.20) --
-	(195.05,182.20) --
-	(199.79,183.10) --
-	(200.09,183.15) --
-	(201.70,183.53) --
-	(202.42,183.68) --
-	(203.15,183.82) --
-	(203.24,183.84) --
-	(203.92,183.98) --
-	(204.08,184.00) --
-	(205.70,184.39) --
-	(211.30,185.68) --
-	(213.02,186.07) --
-	(213.22,186.12) --
-	(213.28,186.14) --
-	(214.88,186.52) --
-	(219.39,187.64) --
-	(219.87,187.75) --
-	(224.51,188.92) --
-	(226.38,189.39) --
-	(226.89,189.48) --
-	(228.22,189.88) --
-	(229.80,190.26) --
-	(230.53,190.49) --
-	(231.54,190.73) --
-	(232.29,190.94) --
-	(232.55,191.02) --
-	(232.60,191.04) --
-	(233.03,191.16) --
-	(236.50,192.03) --
-	(238.44,192.60) --
-	(239.50,192.87) --
-	(240.76,193.23) --
-	(242.87,193.80) --
-	(243.82,193.97) --
-	(244.87,194.22) --
-	(245.90,194.45) --
-	(247.14,194.78) --
-	(247.15,194.78) --
-	(248.00,195.06) --
-	(248.59,195.19) --
-	(249.15,195.38) --
-	(249.91,195.68) --
-	(250.14,195.72) --
-	(250.71,195.90) --
-	(251.21,196.07) --
-	(251.61,196.16) --
-	(251.88,196.25) --
-	(252.52,196.37) --
-	(252.98,196.48) --
-	(253.12,196.53) --
-	(253.36,196.58) --
-	(254.91,197.00) --
-	(255.02,197.02) --
-	(256.32,197.42) --
-	(258.61,198.09) --
-	(260.03,198.53) --
-	(260.14,198.54) --
-	(260.80,198.76) --
-	(261.97,199.13) --
-	(262.19,199.18) --
-	(262.48,199.25) --
-	(262.99,199.41) --
-	(264.29,199.74) --
-	(264.50,199.84) --
-	(264.53,199.86) --
-	(264.97,199.98) --
-	(266.10,200.32) --
-	(266.13,200.33) --
-	(266.44,200.43) --
-	(267.28,200.69) --
-	(267.71,200.79) --
-	(268.38,200.99) --
-	(269.11,201.16) --
-	(269.74,201.38) --
-	(269.87,201.40) --
-	(271.02,201.80) --
-	(271.10,201.83) --
-	(271.68,202.00) --
-	(272.40,202.28) --
-	(272.79,202.41) --
-	(273.63,202.69) --
-	(274.52,202.98) --
-	(275.28,203.20) --
-	(275.59,203.27) --
-	(276.13,203.43) --
-	(276.31,203.47) --
-	(276.77,203.63) --
-	(277.30,203.79) --
-	(277.98,204.00) --
-	(278.04,204.00) --
-	(278.45,204.12) --
-	(279.17,204.40) --
-	(279.30,204.44) --
-	(279.52,204.50) --
-	(279.66,204.55) --
-	(279.69,204.56) --
-	(280.15,204.72) --
-	(280.53,204.89) --
-	(280.72,204.98) --
-	(281.20,205.18) --
-	(281.36,205.23) --
-	(281.45,205.24) --
-	(282.80,205.79) --
-	(283.05,205.89) --
-	(283.89,206.20) --
-	(283.98,206.21) --
-	(284.07,206.25) --
-	(284.62,206.45) --
-	(284.86,206.51) --
-	(285.03,206.59) --
-	(285.13,206.64) --
-	(286.00,206.89) --
-	(286.57,207.08) --
-	(286.59,207.10) --
-	(287.25,207.30) --
-	(287.81,207.46) --
-	(288.54,207.69) --
-	(288.59,207.71) --
-	(289.22,207.96) --
-	(289.76,208.14) --
-	(290.76,208.49) --
-	(290.86,208.52) --
-	(291.20,208.64) --
-	(291.32,208.69) --
-	(291.81,208.87) --
-	(291.88,208.91) --
-	(292.21,209.05) --
-	(292.36,209.11) --
-	(292.42,209.13) --
-	(292.49,209.15) --
-	(292.51,209.16) --
-	(292.62,209.22) --
-	(293.21,209.38) --
-	(293.91,209.64) --
-	(295.25,210.12) --
-	(295.45,210.17) --
-	(295.51,210.19) --
-	(295.93,210.34) --
-	(295.99,210.37) --
-	(296.10,210.42) --
-	(296.47,210.53) --
-	(296.65,210.60) --
-	(296.99,210.70) --
-	(297.01,210.71) --
-	(297.04,210.72) --
-	(297.05,210.72) --
-	(297.09,210.73) --
-	(297.13,210.74) --
-	(297.22,210.77) --
-	(297.31,210.80) --
-	(297.31,210.80) --
-	(297.71,210.96) --
-	(297.96,211.07) --
-	(298.34,211.23) --
-	(298.57,211.33) --
-	(299.04,211.48) --
-	(300.58,212.07) --
-	(300.69,212.11) --
-	(301.32,212.32) --
-	(302.10,212.65) --
-	(302.23,212.71) --
-	(302.50,212.86) --
-	(302.82,212.96) --
-	(302.98,213.02) --
-	(303.49,213.24) --
-	(303.87,213.38) --
-	(304.04,213.46) --
-	(304.05,213.46) --
-	(304.17,213.52) --
-	(304.21,213.54) --
-	(304.88,213.80) --
-	(305.44,214.06) --
-	(305.52,214.08) --
-	(305.61,214.12) --
-	(305.86,214.20) --
-	(306.19,214.32) --
-	(306.32,214.36) --
-	(307.91,214.96) --
-	(307.96,214.99) --
-	(308.47,215.19) --
-	(308.57,215.23) --
-	(309.22,215.49) --
-	(309.44,215.58) --
-	(309.51,215.60) --
-	(309.67,215.66) --
-	(310.00,215.78) --
-	(310.25,215.88) --
-	(310.76,216.10) --
-	(310.92,216.15) --
-	(311.04,216.19) --
-	(311.16,216.24) --
-	(311.41,216.35) --
-	(311.41,216.36) --
-	(311.44,216.37) --
-	(311.54,216.40) --
-	(311.68,216.46) --
-	(311.68,216.46) --
-	(311.88,216.53) --
-	(312.22,216.64) --
-	(312.92,216.90) --
-	(313.12,216.98) --
-	(313.27,217.05) --
-	(313.53,217.12) --
-	(313.83,217.24) --
-	(314.24,217.40) --
-	(314.31,217.42) --
-	(314.45,217.49) --
-	(314.63,217.59) --
-	(315.00,217.69) --
-	(315.21,217.81) --
-	(315.23,217.82) --
-	(315.37,217.86) --
-	(315.48,217.91) --
-	(315.51,217.92) --
-	(315.62,217.95) --
-	(315.70,217.98) --
-	(315.79,218.02) --
-	(316.13,218.15) --
-	(316.22,218.18) --
-	(316.38,218.25) --
-	(316.61,218.33) --
-	(316.93,218.48) --
-	(317.07,218.54) --
-	(317.20,218.60) --
-	(317.36,218.68) --
-	(317.75,218.86) --
-	(317.76,218.87) --
-	(317.79,218.88) --
-	(317.86,218.90) --
-	(317.89,218.91) --
-	(317.98,218.95) --
-	(318.43,219.10) --
-	(318.60,219.15) --
-	(318.85,219.23) --
-	(319.11,219.34) --
-	(319.21,219.36) --
-	(319.52,219.46) --
-	(319.81,219.61) --
-	(320.44,219.87) --
-	(321.85,220.46) --
-	(321.91,220.48) --
-	(322.04,220.54) --
-	(322.30,220.65) --
-	(322.60,220.80) --
-	(322.75,220.85) --
-	(323.02,220.98) --
-	(323.10,221.01) --
-	(323.28,221.10) --
-	(324.05,221.40) --
-	(324.42,221.57) --
-	(324.61,221.63) --
-	(324.72,221.66) --
-	(325.08,221.77) --
-	(325.99,222.17) --
-	(326.58,222.47) --
-	(326.72,222.50) --
-	(327.61,222.87) --
-	(327.91,223.02) --
-	(328.67,223.32) --
-	(328.94,223.47) --
-	(329.07,223.53) --
-	(329.52,223.68) --
-	(331.17,224.41) --
-	(332.00,224.77) --
-	(332.27,224.86) --
-	(333.07,225.24) --
-	(333.19,225.28) --
-	(333.76,225.52) --
-	(335.51,226.18) --
-	(336.07,226.42) --
-	(336.75,226.75) --
-	(336.88,226.82) --
-	(337.54,227.09) --
-	(337.92,227.27) --
-	(338.29,227.44) --
-	(338.32,227.46) --
-	(338.37,227.49) --
-	(338.79,227.66) --
-	(338.87,227.69) --
-	(339.41,227.95) --
-	(339.54,228.00) --
-	(340.26,228.35) --
-	(340.28,228.35) --
-	(340.36,228.38) --
-	(340.58,228.46) --
-	(340.90,228.61) --
-	(341.07,228.67) --
-	(341.38,228.80) --
-	(341.48,228.85) --
-	(341.53,228.88) --
-	(341.57,228.90) --
-	(342.00,229.08) --
-	(342.06,229.11) --
-	(342.60,229.32) --
-	(342.92,229.41) --
-	(344.39,230.06) --
-	(344.81,230.26) --
-	(345.03,230.35) --
-	(345.51,230.53) --
-	(345.56,230.55) --
-	(346.27,230.84) --
-	(348.09,231.63) --
-	(348.19,231.66) --
-	(348.32,231.71) --
-	(348.52,231.79) --
-	(348.65,231.84) --
-	(350.04,232.48) --
-	(350.29,232.58) --
-	(350.39,232.61) --
-	(351.49,233.03) --
-	(354.19,234.20) --
-	(354.41,234.28) --
-	(354.96,234.53) --
-	(354.99,234.54) --
-	(355.28,234.70) --
-	(355.84,234.97) --
-	(356.71,235.37) --
-	(356.75,235.39) --
-	(357.50,235.70) --
-	(357.53,235.71) --
-	(358.04,235.90) --
-	(358.62,236.15) --
-	(359.31,236.46) --
-	(359.62,236.61) --
-	(359.75,236.69) --
-	(359.85,236.75) --
-	(360.61,237.12) --
-	(360.64,237.13) --
-	(360.71,237.18) --
-	(361.91,237.72) --
-	(362.60,238.04) --
-	(364.24,238.88) --
-	(364.46,239.00) --
-	(365.70,239.62) --
-	(366.29,239.93) --
-	(370.53,241.73) --
-	(371.02,241.94) --
-	(372.06,242.43) --
-	(372.07,242.43) --
-	(372.38,242.60) --
-	(372.60,242.71) --
-	(372.90,242.85) --
-	(373.16,243.00) --
-	(373.53,243.19) --
-	(373.80,243.33) --
-	(374.46,243.64) --
-	(374.81,243.78) --
-	(375.77,244.22) --
-	(376.36,244.50) --
-	(376.51,244.59) --
-	(376.93,244.79) --
-	(378.03,245.25) --
-	(379.36,245.80) --
-	(379.36,245.80) --
-	(380.09,246.17) --
-	(380.12,246.18) --
-	(381.03,246.59) --
-	(381.47,246.80) --
-	(381.75,246.94) --
-	(382.36,247.23) --
-	(382.44,247.28) --
-	(382.57,247.34) --
-	(383.02,247.55) --
-	(385.04,248.44) --
-	(385.16,248.51) --
-	(388.87,250.32) --
-	(393.56,252.71) --
-	(395.71,253.79) --
-	(403.26,257.56) --
-	(404.02,257.95) --
-	(404.02,188.48) --
-	(403.26,188.33) --
-	(395.71,186.92) --
-	(393.56,186.56) --
-	(388.87,185.69) --
-	(385.16,184.82) --
-	(385.04,184.80) --
-	(383.02,184.39) --
-	(382.57,184.31) --
-	(382.44,184.30) --
-	(382.36,184.29) --
-	(381.75,184.16) --
-	(381.47,184.11) --
-	(381.03,184.04) --
-	(380.12,183.81) --
-	(380.09,183.80) --
-	(379.36,183.64) --
-	(379.36,183.64) --
-	(378.03,183.40) --
-	(376.93,183.15) --
-	(376.51,183.06) --
-	(376.36,183.05) --
-	(375.77,182.97) --
-	(374.81,182.77) --
-	(374.46,182.70) --
-	(373.80,182.52) --
-	(373.53,182.49) --
-	(373.16,182.43) --
-	(372.90,182.36) --
-	(372.60,182.28) --
-	(372.38,182.23) --
-	(372.07,182.19) --
-	(372.06,182.19) --
-	(371.02,182.00) --
-	(370.53,181.89) --
-	(366.29,181.14) --
-	(365.70,181.03) --
-	(364.46,180.67) --
-	(364.24,180.65) --
-	(362.60,180.37) --
-	(361.91,180.21) --
-	(360.71,179.92) --
-	(360.64,179.91) --
-	(360.61,179.91) --
-	(359.85,179.80) --
-	(359.75,179.78) --
-	(359.62,179.75) --
-	(359.31,179.68) --
-	(358.62,179.58) --
-	(358.04,179.52) --
-	(357.53,179.41) --
-	(357.50,179.40) --
-	(356.75,179.23) --
-	(356.71,179.22) --
-	(355.84,179.05) --
-	(355.28,178.90) --
-	(354.99,178.79) --
-	(354.96,178.78) --
-	(354.41,178.64) --
-	(354.19,178.60) --
-	(351.49,177.92) --
-	(350.39,177.61) --
-	(350.29,177.59) --
-	(350.04,177.51) --
-	(348.65,177.21) --
-	(348.52,177.18) --
-	(348.32,177.15) --
-	(348.19,177.12) --
-	(348.09,177.09) --
-	(346.27,176.71) --
-	(345.56,176.53) --
-	(345.51,176.51) --
-	(345.03,176.39) --
-	(344.81,176.34) --
-	(344.39,176.25) --
-	(342.92,175.94) --
-	(342.60,175.88) --
-	(342.06,175.75) --
-	(342.00,175.73) --
-	(341.57,175.65) --
-	(341.53,175.64) --
-	(341.48,175.64) --
-	(341.38,175.62) --
-	(341.07,175.54) --
-	(340.90,175.51) --
-	(340.58,175.45) --
-	(340.36,175.41) --
-	(340.28,175.40) --
-	(340.26,175.39) --
-	(339.54,175.25) --
-	(339.41,175.22) --
-	(338.87,175.11) --
-	(338.79,175.10) --
-	(338.37,175.01) --
-	(338.32,174.99) --
-	(338.29,174.98) --
-	(337.92,174.87) --
-	(337.54,174.80) --
-	(336.88,174.67) --
-	(336.75,174.64) --
-	(336.07,174.44) --
-	(335.51,174.32) --
-	(333.76,173.87) --
-	(333.19,173.78) --
-	(333.07,173.75) --
-	(332.27,173.58) --
-	(332.00,173.51) --
-	(331.17,173.30) --
-	(329.52,172.87) --
-	(329.07,172.77) --
-	(328.94,172.73) --
-	(328.67,172.67) --
-	(327.91,172.46) --
-	(327.61,172.39) --
-	(326.72,172.17) --
-	(326.58,172.14) --
-	(325.99,172.00) --
-	(325.08,171.78) --
-	(324.72,171.70) --
-	(324.61,171.67) --
-	(324.42,171.61) --
-	(324.05,171.49) --
-	(323.28,171.35) --
-	(323.10,171.31) --
-	(323.02,171.29) --
-	(322.75,171.18) --
-	(322.60,171.15) --
-	(322.30,171.10) --
-	(322.04,171.03) --
-	(321.91,171.01) --
-	(321.85,171.00) --
-	(320.44,170.69) --
-	(319.81,170.53) --
-	(319.52,170.45) --
-	(319.21,170.37) --
-	(319.11,170.34) --
-	(318.85,170.26) --
-	(318.60,170.22) --
-	(318.43,170.18) --
-	(317.98,170.05) --
-	(317.89,170.02) --
-	(317.86,170.01) --
-	(317.79,169.99) --
-	(317.76,169.99) --
-	(317.75,169.99) --
-	(317.36,169.90) --
-	(317.20,169.85) --
-	(317.07,169.82) --
-	(316.93,169.79) --
-	(316.61,169.68) --
-	(316.38,169.60) --
-	(316.22,169.57) --
-	(316.13,169.55) --
-	(315.79,169.46) --
-	(315.70,169.44) --
-	(315.62,169.41) --
-	(315.51,169.37) --
-	(315.48,169.36) --
-	(315.37,169.32) --
-	(315.23,169.28) --
-	(315.21,169.27) --
-	(315.00,169.20) --
-	(314.63,169.05) --
-	(314.45,168.98) --
-	(314.31,168.94) --
-	(314.24,168.90) --
-	(313.83,168.77) --
-	(313.53,168.69) --
-	(313.27,168.63) --
-	(313.12,168.61) --
-	(312.92,168.58) --
-	(312.22,168.40) --
-	(311.88,168.29) --
-	(311.68,168.25) --
-	(311.68,168.25) --
-	(311.54,168.22) --
-	(311.44,168.18) --
-	(311.41,168.17) --
-	(311.41,168.17) --
-	(311.16,168.09) --
-	(311.04,168.07) --
-	(310.92,168.05) --
-	(310.76,168.02) --
-	(310.25,167.88) --
-	(310.00,167.83) --
-	(309.67,167.75) --
-	(309.51,167.72) --
-	(309.44,167.71) --
-	(309.22,167.66) --
-	(308.57,167.46) --
-	(308.47,167.44) --
-	(307.96,167.34) --
-	(307.91,167.34) --
-	(306.32,166.93) --
-	(306.19,166.90) --
-	(305.86,166.81) --
-	(305.61,166.74) --
-	(305.52,166.71) --
-	(305.44,166.69) --
-	(304.88,166.51) --
-	(304.21,166.30) --
-	(304.17,166.30) --
-	(304.05,166.26) --
-	(304.04,166.26) --
-	(303.87,166.21) --
-	(303.49,166.10) --
-	(302.98,165.93) --
-	(302.82,165.89) --
-	(302.50,165.78) --
-	(302.23,165.67) --
-	(302.10,165.62) --
-	(301.32,165.40) --
-	(300.69,165.24) --
-	(300.58,165.20) --
-	(299.04,164.69) --
-	(298.57,164.54) --
-	(298.34,164.48) --
-	(297.96,164.38) --
-	(297.71,164.30) --
-	(297.31,164.13) --
-	(297.31,164.13) --
-	(297.22,164.10) --
-	(297.13,164.08) --
-	(297.09,164.07) --
-	(297.05,164.05) --
-	(297.04,164.05) --
-	(297.01,164.04) --
-	(296.99,164.03) --
-	(296.65,163.91) --
-	(296.47,163.85) --
-	(296.10,163.73) --
-	(295.99,163.69) --
-	(295.93,163.67) --
-	(295.51,163.54) --
-	(295.45,163.52) --
-	(295.25,163.45) --
-	(293.91,163.09) --
-	(293.21,162.89) --
-	(292.62,162.68) --
-	(292.51,162.66) --
-	(292.49,162.65) --
-	(292.42,162.63) --
-	(292.36,162.61) --
-	(292.21,162.56) --
-	(291.88,162.48) --
-	(291.81,162.46) --
-	(291.32,162.32) --
-	(291.20,162.27) --
-	(290.86,162.16) --
-	(290.76,162.12) --
-	(289.76,161.73) --
-	(289.22,161.57) --
-	(288.59,161.34) --
-	(288.54,161.32) --
-	(287.81,161.08) --
-	(287.25,160.92) --
-	(286.59,160.70) --
-	(286.57,160.70) --
-	(286.00,160.52) --
-	(285.13,160.28) --
-	(285.03,160.25) --
-	(284.86,160.19) --
-	(284.62,160.11) --
-	(284.07,159.94) --
-	(283.98,159.91) --
-	(283.89,159.89) --
-	(283.05,159.64) --
-	(282.80,159.57) --
-	(281.45,159.12) --
-	(281.36,159.08) --
-	(281.20,159.03) --
-	(280.72,158.84) --
-	(280.53,158.80) --
-	(280.15,158.71) --
-	(279.69,158.55) --
-	(279.66,158.54) --
-	(279.52,158.48) --
-	(279.30,158.40) --
-	(279.17,158.36) --
-	(278.45,158.13) --
-	(278.04,157.99) --
-	(277.98,157.96) --
-	(277.30,157.71) --
-	(276.77,157.53) --
-	(276.31,157.40) --
-	(276.13,157.34) --
-	(275.59,157.16) --
-	(275.28,157.07) --
-	(274.52,156.81) --
-	(273.63,156.52) --
-	(272.79,156.25) --
-	(272.40,156.11) --
-	(271.68,155.88) --
-	(271.10,155.68) --
-	(271.02,155.65) --
-	(269.87,155.20) --
-	(269.74,155.17) --
-	(269.11,154.96) --
-	(268.38,154.71) --
-	(267.71,154.49) --
-	(267.28,154.34) --
-	(266.44,154.07) --
-	(266.13,153.97) --
-	(266.10,153.96) --
-	(264.97,153.64) --
-	(264.53,153.52) --
-	(264.50,153.51) --
-	(264.29,153.45) --
-	(262.99,153.00) --
-	(262.48,152.85) --
-	(262.19,152.74) --
-	(261.97,152.68) --
-	(260.80,152.32) --
-	(260.14,152.06) --
-	(260.03,152.03) --
-	(258.61,151.54) --
-	(256.32,150.72) --
-	(255.02,150.28) --
-	(254.91,150.24) --
-	(253.36,149.63) --
-	(253.12,149.55) --
-	(252.98,149.50) --
-	(252.52,149.32) --
-	(251.88,149.06) --
-	(251.61,148.94) --
-	(251.21,148.84) --
-	(250.71,148.65) --
-	(250.14,148.41) --
-	(249.91,148.31) --
-	(249.15,148.07) --
-	(248.59,147.93) --
-	(248.00,147.70) --
-	(247.15,147.40) --
-	(247.14,147.39) --
-	(245.90,146.93) --
-	(244.87,146.49) --
-	(243.82,146.09) --
-	(242.87,145.70) --
-	(240.76,144.79) --
-	(239.50,144.28) --
-	(238.44,143.86) --
-	(236.50,143.12) --
-	(233.03,141.67) --
-	(232.60,141.48) --
-	(232.55,141.46) --
-	(232.29,141.37) --
-	(231.54,141.09) --
-	(230.53,140.70) --
-	(229.80,140.39) --
-	(228.22,139.75) --
-	(226.89,139.17) --
-	(226.38,138.96) --
-	(224.51,138.27) --
-	(219.87,136.46) --
-	(219.39,136.25) --
-	(214.88,134.34) --
-	(213.28,133.63) --
-	(213.22,133.61) --
-	(213.02,133.50) --
-	(211.30,132.78) --
-	(205.70,130.38) --
-	(204.08,129.58) --
-	(203.92,129.52) --
-	(203.24,129.24) --
-	(203.15,129.19) --
-	(202.42,128.83) --
-	(201.70,128.52) --
-	(200.09,127.78) --
-	(199.79,127.65) --
-	(195.05,125.74) --
-	(195.04,125.74) --
-	(185.12,121.11) --
-	(177.68,117.77) --
-	(175.08,116.58) --
-	(164.50,111.49) --
-	(163.56,111.05) --
-	(160.15,109.37) --
-	(160.01,109.30) --
-	(124.94, 91.80) --
-	(116.56, 87.52) --
-	(113.94, 86.20) --
-	(110.01, 84.11) --
-	(104.50, 81.25) --
-	( 97.84, 77.97) --
-	( 94.41, 76.21) --
-	( 88.50, 73.15) --
-	( 79.64, 68.59) --
-	( 65.62, 61.16) --
-	( 65.48, 61.09) --
-	( 61.01, 58.86) --
-	( 52.97, 54.68) --
+\path[fill=fillColor,fill opacity=0.50] ( 52.97,159.47) --
+	( 61.01,160.59) --
+	( 65.48,161.23) --
+	( 65.62,161.26) --
+	( 79.64,163.39) --
+	( 88.50,164.57) --
+	( 94.41,165.69) --
+	( 97.84,166.20) --
+	(104.50,167.06) --
+	(110.01,168.00) --
+	(113.94,168.69) --
+	(116.56,169.17) --
+	(124.94,170.52) --
+	(160.01,176.92) --
+	(160.15,176.94) --
+	(163.56,177.51) --
+	(164.50,177.71) --
+	(175.08,179.80) --
+	(177.68,180.16) --
+	(185.12,181.57) --
+	(195.04,183.80) --
+	(195.05,183.80) --
+	(199.79,184.69) --
+	(200.09,184.75) --
+	(201.70,185.11) --
+	(202.42,185.27) --
+	(203.15,185.46) --
+	(203.24,185.48) --
+	(203.92,185.62) --
+	(204.08,185.66) --
+	(205.70,185.99) --
+	(211.30,187.30) --
+	(213.02,187.66) --
+	(213.22,187.71) --
+	(213.28,187.73) --
+	(214.88,188.04) --
+	(219.39,189.00) --
+	(219.87,189.14) --
+	(224.51,190.27) --
+	(226.38,190.71) --
+	(226.89,190.77) --
+	(228.22,191.06) --
+	(229.80,191.48) --
+	(230.53,191.63) --
+	(231.54,191.83) --
+	(232.29,192.09) --
+	(232.55,192.17) --
+	(232.60,192.19) --
+	(233.03,192.29) --
+	(236.50,193.20) --
+	(238.44,193.74) --
+	(239.50,193.98) --
+	(240.76,194.31) --
+	(242.87,194.91) --
+	(243.82,195.16) --
+	(244.87,195.48) --
+	(245.90,195.82) --
+	(247.14,196.17) --
+	(247.15,196.18) --
+	(248.00,196.50) --
+	(248.59,196.63) --
+	(249.15,196.79) --
+	(249.91,197.01) --
+	(250.14,197.09) --
+	(250.71,197.23) --
+	(251.21,197.34) --
+	(251.61,197.49) --
+	(251.88,197.55) --
+	(252.52,197.67) --
+	(252.98,197.76) --
+	(253.12,197.80) --
+	(253.36,197.88) --
+	(254.91,198.29) --
+	(255.02,198.30) --
+	(256.32,198.66) --
+	(258.61,199.32) --
+	(260.03,199.67) --
+	(260.14,199.69) --
+	(260.80,199.89) --
+	(261.97,200.20) --
+	(262.19,200.28) --
+	(262.48,200.35) --
+	(262.99,200.50) --
+	(264.29,200.85) --
+	(264.50,200.95) --
+	(264.53,200.97) --
+	(264.97,201.14) --
+	(266.10,201.49) --
+	(266.13,201.51) --
+	(266.44,201.63) --
+	(267.28,201.85) --
+	(267.71,202.01) --
+	(268.38,202.15) --
+	(269.11,202.33) --
+	(269.74,202.52) --
+	(269.87,202.56) --
+	(271.02,202.98) --
+	(271.10,203.00) --
+	(271.68,203.15) --
+	(272.40,203.42) --
+	(272.79,203.55) --
+	(273.63,203.81) --
+	(274.52,204.12) --
+	(275.28,204.39) --
+	(275.59,204.51) --
+	(276.13,204.65) --
+	(276.31,204.70) --
+	(276.77,204.86) --
+	(277.30,204.96) --
+	(277.98,205.21) --
+	(278.04,205.24) --
+	(278.45,205.38) --
+	(279.17,205.57) --
+	(279.30,205.61) --
+	(279.52,205.68) --
+	(279.66,205.73) --
+	(279.69,205.73) --
+	(280.15,205.88) --
+	(280.53,206.00) --
+	(280.72,206.07) --
+	(281.20,206.23) --
+	(281.36,206.28) --
+	(281.45,206.31) --
+	(282.80,206.75) --
+	(283.05,206.86) --
+	(283.89,207.18) --
+	(283.98,207.21) --
+	(284.07,207.24) --
+	(284.62,207.46) --
+	(284.86,207.55) --
+	(285.04,207.61) --
+	(285.13,207.65) --
+	(286.00,207.95) --
+	(286.57,208.14) --
+	(286.59,208.15) --
+	(287.25,208.36) --
+	(287.81,208.58) --
+	(288.54,208.78) --
+	(288.59,208.79) --
+	(289.22,208.99) --
+	(289.76,209.13) --
+	(290.76,209.50) --
+	(290.86,209.53) --
+	(291.20,209.68) --
+	(291.32,209.73) --
+	(291.81,209.89) --
+	(291.88,209.92) --
+	(292.21,210.06) --
+	(292.36,210.13) --
+	(292.42,210.16) --
+	(292.49,210.17) --
+	(292.51,210.18) --
+	(292.62,210.20) --
+	(293.21,210.39) --
+	(293.91,210.61) --
+	(295.25,211.13) --
+	(295.45,211.21) --
+	(295.51,211.24) --
+	(295.93,211.39) --
+	(295.99,211.41) --
+	(296.10,211.45) --
+	(296.47,211.59) --
+	(296.65,211.64) --
+	(296.99,211.74) --
+	(297.01,211.75) --
+	(297.04,211.76) --
+	(297.05,211.76) --
+	(297.09,211.78) --
+	(297.13,211.81) --
+	(297.22,211.85) --
+	(297.31,211.88) --
+	(297.31,211.88) --
+	(297.71,212.06) --
+	(297.96,212.13) --
+	(298.34,212.29) --
+	(298.57,212.42) --
+	(299.05,212.60) --
+	(300.58,213.21) --
+	(300.69,213.25) --
+	(301.32,213.49) --
+	(302.10,213.78) --
+	(302.23,213.83) --
+	(302.50,213.93) --
+	(302.82,214.09) --
+	(302.98,214.15) --
+	(303.49,214.33) --
+	(303.87,214.46) --
+	(304.04,214.52) --
+	(304.05,214.53) --
+	(304.17,214.56) --
+	(304.21,214.57) --
+	(304.88,214.80) --
+	(305.44,215.00) --
+	(305.52,215.03) --
+	(305.61,215.07) --
+	(305.86,215.17) --
+	(306.19,215.29) --
+	(306.32,215.33) --
+	(307.91,215.92) --
+	(307.96,215.93) --
+	(308.47,216.11) --
+	(308.57,216.15) --
+	(309.22,216.41) --
+	(309.44,216.48) --
+	(309.51,216.51) --
+	(309.67,216.58) --
+	(310.00,216.73) --
+	(310.25,216.84) --
+	(310.76,217.04) --
+	(310.92,217.08) --
+	(311.04,217.15) --
+	(311.16,217.18) --
+	(311.41,217.26) --
+	(311.41,217.26) --
+	(311.44,217.27) --
+	(311.54,217.31) --
+	(311.68,217.37) --
+	(311.68,217.37) --
+	(311.88,217.45) --
+	(312.22,217.58) --
+	(312.92,217.88) --
+	(313.12,217.96) --
+	(313.27,218.01) --
+	(313.53,218.11) --
+	(313.83,218.21) --
+	(314.24,218.39) --
+	(314.31,218.42) --
+	(314.45,218.47) --
+	(314.63,218.54) --
+	(315.00,218.69) --
+	(315.21,218.76) --
+	(315.23,218.77) --
+	(315.37,218.83) --
+	(315.48,218.87) --
+	(315.51,218.88) --
+	(315.62,218.94) --
+	(315.70,218.97) --
+	(315.79,219.01) --
+	(316.13,219.13) --
+	(316.22,219.18) --
+	(316.38,219.25) --
+	(316.61,219.34) --
+	(316.93,219.46) --
+	(317.07,219.50) --
+	(317.20,219.56) --
+	(317.36,219.63) --
+	(317.75,219.81) --
+	(317.76,219.81) --
+	(317.79,219.82) --
+	(317.86,219.85) --
+	(317.89,219.87) --
+	(317.98,219.89) --
+	(318.43,220.06) --
+	(318.60,220.13) --
+	(318.85,220.21) --
+	(319.11,220.33) --
+	(319.21,220.36) --
+	(319.52,220.49) --
+	(319.81,220.61) --
+	(320.44,220.89) --
+	(321.85,221.43) --
+	(321.91,221.45) --
+	(322.04,221.50) --
+	(322.30,221.59) --
+	(322.60,221.73) --
+	(322.75,221.78) --
+	(323.02,221.89) --
+	(323.10,221.92) --
+	(323.28,221.97) --
+	(324.05,222.30) --
+	(324.42,222.44) --
+	(324.61,222.53) --
+	(324.72,222.58) --
+	(325.08,222.73) --
+	(325.99,223.18) --
+	(326.58,223.43) --
+	(326.72,223.49) --
+	(327.61,223.81) --
+	(327.91,223.95) --
+	(328.67,224.23) --
+	(328.94,224.34) --
+	(329.07,224.39) --
+	(329.52,224.58) --
+	(331.17,225.26) --
+	(332.00,225.59) --
+	(332.27,225.71) --
+	(333.07,226.08) --
+	(333.19,226.13) --
+	(333.76,226.44) --
+	(335.51,227.21) --
+	(336.07,227.44) --
+	(336.75,227.74) --
+	(336.88,227.79) --
+	(337.54,228.09) --
+	(337.92,228.27) --
+	(338.29,228.43) --
+	(338.32,228.44) --
+	(338.37,228.47) --
+	(338.79,228.65) --
+	(338.87,228.69) --
+	(339.41,228.95) --
+	(339.54,229.03) --
+	(340.26,229.31) --
+	(340.28,229.33) --
+	(340.36,229.36) --
+	(340.58,229.46) --
+	(340.90,229.60) --
+	(341.07,229.67) --
+	(341.38,229.82) --
+	(341.48,229.87) --
+	(341.53,229.89) --
+	(341.57,229.91) --
+	(342.00,230.08) --
+	(342.06,230.11) --
+	(342.60,230.32) --
+	(342.92,230.44) --
+	(344.39,231.06) --
+	(344.81,231.24) --
+	(345.03,231.34) --
+	(345.51,231.53) --
+	(345.56,231.55) --
+	(346.27,231.84) --
+	(348.09,232.60) --
+	(348.19,232.65) --
+	(348.32,232.69) --
+	(348.52,232.77) --
+	(348.65,232.83) --
+	(350.04,233.41) --
+	(350.29,233.53) --
+	(350.39,233.57) --
+	(351.49,234.02) --
+	(354.19,235.25) --
+	(354.41,235.35) --
+	(354.96,235.62) --
+	(354.99,235.64) --
+	(355.28,235.76) --
+	(355.84,236.01) --
+	(356.71,236.45) --
+	(356.75,236.48) --
+	(357.50,236.93) --
+	(357.53,236.94) --
+	(358.04,237.18) --
+	(358.62,237.46) --
+	(359.31,237.76) --
+	(359.62,237.90) --
+	(359.75,237.96) --
+	(359.85,238.02) --
+	(360.61,238.35) --
+	(360.64,238.36) --
+	(360.71,238.39) --
+	(361.91,238.92) --
+	(362.60,239.27) --
+	(364.24,240.07) --
+	(364.46,240.16) --
+	(365.70,240.71) --
+	(366.29,241.00) --
+	(370.53,242.95) --
+	(371.02,243.20) --
+	(372.06,243.72) --
+	(372.07,243.72) --
+	(372.38,243.88) --
+	(372.60,244.00) --
+	(372.90,244.15) --
+	(373.16,244.28) --
+	(373.53,244.45) --
+	(373.80,244.56) --
+	(374.46,244.87) --
+	(374.81,245.06) --
+	(375.77,245.55) --
+	(376.36,245.83) --
+	(376.51,245.90) --
+	(376.93,246.11) --
+	(378.03,246.60) --
+	(379.36,247.20) --
+	(379.36,247.20) --
+	(380.09,247.56) --
+	(380.12,247.58) --
+	(381.03,247.95) --
+	(381.47,248.18) --
+	(381.75,248.28) --
+	(382.36,248.58) --
+	(382.44,248.63) --
+	(382.57,248.68) --
+	(383.02,248.88) --
+	(385.04,249.84) --
+	(385.16,249.90) --
+	(388.87,251.64) --
+	(393.56,253.73) --
+	(395.71,254.78) --
+	(403.26,258.41) --
+	(404.02,258.78) --
+	(404.02,189.12) --
+	(403.26,189.00) --
+	(395.71,187.56) --
+	(393.56,187.20) --
+	(388.87,186.37) --
+	(385.16,185.62) --
+	(385.04,185.60) --
+	(383.02,185.20) --
+	(382.57,185.13) --
+	(382.44,185.10) --
+	(382.36,185.07) --
+	(381.75,184.98) --
+	(381.47,184.90) --
+	(381.03,184.85) --
+	(380.12,184.68) --
+	(380.09,184.68) --
+	(379.36,184.57) --
+	(379.36,184.57) --
+	(378.03,184.35) --
+	(376.93,184.17) --
+	(376.51,184.09) --
+	(376.36,184.06) --
+	(375.77,183.96) --
+	(374.81,183.76) --
+	(374.46,183.67) --
+	(373.80,183.49) --
+	(373.53,183.44) --
+	(373.16,183.39) --
+	(372.90,183.34) --
+	(372.60,183.30) --
+	(372.38,183.28) --
+	(372.07,183.23) --
+	(372.06,183.23) --
+	(371.02,183.00) --
+	(370.53,182.90) --
+	(366.29,182.01) --
+	(365.70,181.91) --
+	(364.46,181.68) --
+	(364.24,181.61) --
+	(362.60,181.33) --
+	(361.91,181.20) --
+	(360.71,180.94) --
+	(360.64,180.93) --
+	(360.61,180.92) --
+	(359.85,180.78) --
+	(359.75,180.74) --
+	(359.62,180.70) --
+	(359.31,180.61) --
+	(358.62,180.42) --
+	(358.04,180.29) --
+	(357.53,180.20) --
+	(357.50,180.20) --
+	(356.75,180.11) --
+	(356.71,180.09) --
+	(355.84,179.88) --
+	(355.28,179.78) --
+	(354.99,179.71) --
+	(354.96,179.70) --
+	(354.41,179.60) --
+	(354.19,179.57) --
+	(351.49,178.95) --
+	(350.39,178.69) --
+	(350.29,178.67) --
+	(350.04,178.64) --
+	(348.65,178.28) --
+	(348.52,178.24) --
+	(348.32,178.21) --
+	(348.19,178.18) --
+	(348.09,178.15) --
+	(346.27,177.73) --
+	(345.56,177.59) --
+	(345.51,177.59) --
+	(345.03,177.50) --
+	(344.81,177.45) --
+	(344.39,177.37) --
+	(342.92,177.09) --
+	(342.60,176.99) --
+	(342.06,176.84) --
+	(342.00,176.81) --
+	(341.57,176.73) --
+	(341.53,176.72) --
+	(341.48,176.71) --
+	(341.38,176.70) --
+	(341.07,176.63) --
+	(340.90,176.58) --
+	(340.58,176.50) --
+	(340.36,176.44) --
+	(340.28,176.41) --
+	(340.26,176.40) --
+	(339.54,176.24) --
+	(339.41,176.20) --
+	(338.87,176.07) --
+	(338.79,176.05) --
+	(338.37,175.97) --
+	(338.32,175.96) --
+	(338.29,175.95) --
+	(337.92,175.84) --
+	(337.54,175.76) --
+	(336.88,175.64) --
+	(336.75,175.61) --
+	(336.07,175.46) --
+	(335.51,175.33) --
+	(333.76,174.95) --
+	(333.19,174.78) --
+	(333.07,174.75) --
+	(332.27,174.53) --
+	(332.00,174.48) --
+	(331.17,174.26) --
+	(329.52,173.83) --
+	(329.07,173.73) --
+	(328.94,173.70) --
+	(328.67,173.61) --
+	(327.91,173.43) --
+	(327.61,173.34) --
+	(326.72,173.08) --
+	(326.58,173.04) --
+	(325.99,172.91) --
+	(325.08,172.70) --
+	(324.72,172.63) --
+	(324.61,172.62) --
+	(324.42,172.57) --
+	(324.05,172.46) --
+	(323.28,172.27) --
+	(323.10,172.22) --
+	(323.02,172.20) --
+	(322.75,172.14) --
+	(322.60,172.09) --
+	(322.30,172.02) --
+	(322.04,171.94) --
+	(321.91,171.92) --
+	(321.85,171.91) --
+	(320.44,171.52) --
+	(319.81,171.28) --
+	(319.52,171.22) --
+	(319.21,171.14) --
+	(319.11,171.10) --
+	(318.85,170.99) --
+	(318.60,170.95) --
+	(318.43,170.89) --
+	(317.98,170.75) --
+	(317.89,170.72) --
+	(317.86,170.71) --
+	(317.79,170.71) --
+	(317.76,170.70) --
+	(317.75,170.70) --
+	(317.36,170.64) --
+	(317.20,170.61) --
+	(317.07,170.58) --
+	(316.93,170.55) --
+	(316.61,170.45) --
+	(316.38,170.41) --
+	(316.22,170.39) --
+	(316.13,170.36) --
+	(315.79,170.31) --
+	(315.70,170.29) --
+	(315.62,170.27) --
+	(315.51,170.25) --
+	(315.48,170.24) --
+	(315.37,170.22) --
+	(315.23,170.19) --
+	(315.21,170.18) --
+	(315.00,170.14) --
+	(314.63,170.04) --
+	(314.45,169.99) --
+	(314.31,169.95) --
+	(314.24,169.93) --
+	(313.83,169.83) --
+	(313.53,169.75) --
+	(313.27,169.68) --
+	(313.12,169.64) --
+	(312.92,169.59) --
+	(312.22,169.43) --
+	(311.88,169.36) --
+	(311.68,169.32) --
+	(311.68,169.32) --
+	(311.54,169.27) --
+	(311.44,169.24) --
+	(311.41,169.23) --
+	(311.41,169.23) --
+	(311.16,169.18) --
+	(311.04,169.16) --
+	(310.92,169.13) --
+	(310.76,169.07) --
+	(310.25,168.92) --
+	(310.00,168.83) --
+	(309.67,168.76) --
+	(309.51,168.72) --
+	(309.44,168.70) --
+	(309.22,168.66) --
+	(308.57,168.53) --
+	(308.47,168.52) --
+	(307.96,168.35) --
+	(307.91,168.33) --
+	(306.32,167.83) --
+	(306.19,167.78) --
+	(305.86,167.65) --
+	(305.61,167.56) --
+	(305.52,167.54) --
+	(305.44,167.51) --
+	(304.88,167.36) --
+	(304.21,167.16) --
+	(304.17,167.15) --
+	(304.05,167.13) --
+	(304.04,167.12) --
+	(303.87,167.09) --
+	(303.49,166.97) --
+	(302.98,166.82) --
+	(302.82,166.77) --
+	(302.50,166.68) --
+	(302.23,166.59) --
+	(302.10,166.55) --
+	(301.32,166.30) --
+	(300.69,166.08) --
+	(300.58,166.04) --
+	(299.05,165.49) --
+	(298.57,165.30) --
+	(298.34,165.21) --
+	(297.96,165.07) --
+	(297.71,165.02) --
+	(297.31,164.88) --
+	(297.31,164.88) --
+	(297.22,164.85) --
+	(297.13,164.81) --
+	(297.09,164.80) --
+	(297.05,164.79) --
+	(297.04,164.79) --
+	(297.01,164.78) --
+	(296.99,164.78) --
+	(296.65,164.70) --
+	(296.47,164.63) --
+	(296.10,164.50) --
+	(295.99,164.48) --
+	(295.93,164.47) --
+	(295.51,164.37) --
+	(295.45,164.35) --
+	(295.25,164.28) --
+	(293.91,163.93) --
+	(293.21,163.71) --
+	(292.62,163.48) --
+	(292.51,163.45) --
+	(292.49,163.44) --
+	(292.42,163.42) --
+	(292.36,163.39) --
+	(292.21,163.34) --
+	(291.88,163.28) --
+	(291.81,163.25) --
+	(291.32,163.09) --
+	(291.20,163.06) --
+	(290.86,162.93) --
+	(290.76,162.90) --
+	(289.76,162.58) --
+	(289.22,162.41) --
+	(288.59,162.24) --
+	(288.54,162.22) --
+	(287.81,161.98) --
+	(287.25,161.77) --
+	(286.59,161.56) --
+	(286.57,161.55) --
+	(286.00,161.34) --
+	(285.13,161.02) --
+	(285.04,160.98) --
+	(284.86,160.92) --
+	(284.62,160.82) --
+	(284.07,160.64) --
+	(283.98,160.62) --
+	(283.89,160.59) --
+	(283.05,160.27) --
+	(282.80,160.20) --
+	(281.45,159.74) --
+	(281.36,159.72) --
+	(281.20,159.66) --
+	(280.72,159.52) --
+	(280.53,159.44) --
+	(280.15,159.32) --
+	(279.69,159.16) --
+	(279.66,159.15) --
+	(279.52,159.10) --
+	(279.30,159.03) --
+	(279.17,159.01) --
+	(278.45,158.83) --
+	(278.04,158.67) --
+	(277.98,158.65) --
+	(277.30,158.39) --
+	(276.77,158.21) --
+	(276.31,158.02) --
+	(276.13,157.96) --
+	(275.59,157.78) --
+	(275.28,157.68) --
+	(274.52,157.44) --
+	(273.63,157.14) --
+	(272.79,156.90) --
+	(272.40,156.80) --
+	(271.68,156.52) --
+	(271.10,156.29) --
+	(271.02,156.28) --
+	(269.87,155.91) --
+	(269.74,155.86) --
+	(269.11,155.66) --
+	(268.38,155.37) --
+	(267.71,155.15) --
+	(267.28,155.00) --
+	(266.44,154.66) --
+	(266.13,154.57) --
+	(266.10,154.55) --
+	(264.97,154.19) --
+	(264.53,154.04) --
+	(264.50,154.03) --
+	(264.29,153.96) --
+	(262.99,153.57) --
+	(262.48,153.41) --
+	(262.19,153.29) --
+	(261.97,153.18) --
+	(260.80,152.79) --
+	(260.14,152.50) --
+	(260.03,152.48) --
+	(258.61,151.94) --
+	(256.32,151.04) --
+	(255.02,150.67) --
+	(254.91,150.65) --
+	(253.36,150.08) --
+	(253.12,149.99) --
+	(252.98,149.94) --
+	(252.52,149.83) --
+	(251.88,149.57) --
+	(251.61,149.49) --
+	(251.21,149.34) --
+	(250.71,149.16) --
+	(250.14,148.92) --
+	(249.91,148.82) --
+	(249.15,148.56) --
+	(248.59,148.38) --
+	(248.00,148.19) --
+	(247.15,147.89) --
+	(247.14,147.88) --
+	(245.90,147.34) --
+	(244.87,146.93) --
+	(243.82,146.50) --
+	(242.87,146.14) --
+	(240.76,145.44) --
+	(239.50,145.01) --
+	(238.44,144.54) --
+	(236.50,143.73) --
+	(233.03,142.41) --
+	(232.60,142.21) --
+	(232.55,142.19) --
+	(232.29,142.09) --
+	(231.54,141.79) --
+	(230.53,141.39) --
+	(229.80,141.08) --
+	(228.22,140.35) --
+	(226.89,139.79) --
+	(226.38,139.59) --
+	(224.51,138.88) --
+	(219.87,136.94) --
+	(219.39,136.76) --
+	(214.88,134.81) --
+	(213.28,134.08) --
+	(213.22,134.04) --
+	(213.02,133.96) --
+	(211.30,133.22) --
+	(205.70,130.66) --
+	(204.08,129.95) --
+	(203.92,129.87) --
+	(203.24,129.55) --
+	(203.15,129.52) --
+	(202.42,129.19) --
+	(201.70,128.88) --
+	(200.09,128.20) --
+	(199.79,128.09) --
+	(195.05,125.93) --
+	(195.04,125.93) --
+	(185.12,121.41) --
+	(177.68,117.89) --
+	(175.08,116.76) --
+	(164.50,111.80) --
+	(163.56,111.33) --
+	(160.15,109.66) --
+	(160.01,109.60) --
+	(124.94, 92.19) --
+	(116.56, 87.81) --
+	(113.94, 86.49) --
+	(110.01, 84.50) --
+	(104.50, 81.76) --
+	( 97.84, 78.33) --
+	( 94.41, 76.61) --
+	( 88.50, 73.60) --
+	( 79.64, 69.03) --
+	( 65.62, 61.78) --
+	( 65.48, 61.68) --
+	( 61.01, 59.42) --
+	( 52.97, 55.16) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (239.49, 34.03) -- (239.49, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (239.50, 34.03) -- (239.50, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (262.47, 34.03) -- (262.47, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (262.48, 34.03) -- (262.48, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (273.63, 34.03) -- (273.63, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (273.64, 34.03) -- (273.64, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (282.79, 34.03) -- (282.79, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (282.80, 34.03) -- (282.80, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.03, 34.03) -- (285.03, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (285.04, 34.03) -- (285.04, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.08, 34.03) -- (297.08, 41.32);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.12, 34.03) -- (297.12, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.09, 34.03) -- (297.09, 41.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.13, 34.03) -- (297.13, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (341.54, 34.03) -- (341.54, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (341.53, 34.03) -- (341.53, 41.32);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31, 44.90) {-5};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,128.11) {0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,211.32) {5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31, 45.41) {-5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,128.66) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,211.91) {5};
 \end{scope}

### 2014-10-09 R/Analysis/conflictMaps.R

@@ -56,43 +56,3 @@ setwd(pathTex)
 # temp
 # dev.off()
 ######################################################################
-
-######################################################################
-# Aggregate GDP Growth and Distance
-setwd(pathData)
-load('combinedData.rda')
-yData$lnminDist.min = log(yData$minDist.min+1)
-yData$lncapDist.min = log(yData$capDist.min+1)
-
-# Create bucketed version of mindist and find averag GDP gr
-yData$cityDistCat=contToCat(yData$lnminDist.min, .25)
-yData$capDistCat=contToCat(yData$lncapDist.min, .25)
-
-# Conf intervals using summarySE:
-gdpByCityDist=na.omit( summarySE(data=yData, measurevar='gdpGr_l0', 
-	groupvars='cityDistCat', na.rm=TRUE) )
-gdpByCapDist=na.omit( summarySE(data=yData, measurevar='gdpGr_l0', 
-	groupvars='capDistCat', na.rm=TRUE) )
-
-names(gdpByCityDist)[1]='distCat'; names(gdpByCapDist)[1]='distCat'
-ggData=cbind(
-	rbind(gdpByCityDist, gdpByCapDist),
-	type=c(rep('Ln(Min. City Dist.)$_{t-1}$',nrow(gdpByCityDist)),
-		rep('Ln(Min. Cap Dist.)$_{t-1}$',nrow(gdpByCapDist)) ),
-	cut=rep( c('0-25$^{th}$','26-50$^{th}$','51-75$^{th}$','76-100$^{th}$'), 2 )
-	)
-
-tmp=ggplot(ggData, aes(x=cut, y=gdpGr_l0))
-tmp=tmp + geom_bar(stat='identity', fill='grey')
-tmp=tmp + geom_errorbar(aes(ymin=gdpGr_l0-se, ymax=gdpGr_l0+se),width=.2)
-tmp=tmp + ylab("\\% $\\Delta$ Ln(GDP)$_{t}$")+xlab('')
-tmp=tmp + facet_wrap(~type)
-tmp=tmp + theme( axis.title.y=element_text(vjust=1),
-  axis.ticks=element_blank(),legend.position='none',
-  panel.grid.major=element_blank(), panel.grid.minor=element_blank() )
-tmp
-setwd(pathTex)
-tikz(file='distGdp.tex', width=7, height=4, standAlone=FALSE)
-tmp
-dev.off()
-######################################################################

### 2014-10-09 R/Analysis/models.R

@@ -33,8 +33,7 @@ modData$polity2 = modData$polity2 + 11
 modForm=function(x){
   formula( paste0('lngdpGr_l0 ~', x, '+ 
   Int.max + territorial.max + durSt1max + confAreaPropHi +
-  nconf + 
-  upperincome + lninflation_l1 + polity2 +
+  nconf + upperincome + lninflation_l1 + polity2 +
   resourceGDP + gdpGr.mean_l0 + (1|ccode)' ) )
 }
 ctyForm=modForm('lnminDist.min')
@@ -64,21 +63,17 @@ vnames=c('Ln(Min. City Dist.)$_{t-1}$', otherCovars)
 temp <- ggcoefplot(coefData=summary(mCity)$'coefficients',
     vars=na.omit(rownames(summary(mCity)$'coefficients')[2:100]), 
     varNames=vnames, Noylabel=FALSE, coordFlip=TRUE,
-    specY=TRUE, 
-    # ggylims=c(-.004,.004), ggybreaks=seq(-.004,.004,.002),
     colorGrey=FALSE, grSTA=0.5, grEND=0.1)
 temp
 setwd(pathTex)
-# tikz(file='mCityCoefPlot.tex', width=4, height=4, standAlone=F)
-# temp
-# dev.off()
+tikz(file='mCityCoefPlot.tex', width=4, height=4, standAlone=F)
+temp
+dev.off()
 
 vnames=c('Ln(Min. Capital Dist.)$_{t-1}$', otherCovars)
 temp <- ggcoefplot(coefData=summary(mCap)$'coefficients',
     vars=na.omit(rownames(summary(mCap)$'coefficients')[2:100]), 
     varNames=vnames, Noylabel=FALSE, coordFlip=TRUE,
-    specY=TRUE, 
-    # ggylims=c(-.004,.004), ggybreaks=seq(-.004,.004,.002),
     colorGrey=FALSE, grSTA=0.5, grEND=0.1)
 temp
 setwd(pathTex)
@@ -99,22 +94,22 @@ temp = ggsimplot(modelResults=mCity, sims=10000, simData=modData,
 temp + theme(axis.title.y=element_text(vjust=1))
 temp
 setwd(pathTex)
-tikz(file='mCitySimPlot.tex', width=6, height=4, standAlone=F)
-temp
-dev.off()
+# tikz(file='mCitySimPlot.tex', width=6, height=4, standAlone=F)
+# temp
+# dev.off()
 
[…]

### 2014-10-09 LaTeX/RhodiumEmp.tex
more ugh

@@
 
+\subsection{Measuring Spatial Proximity of Conflict to Urban Centers}
+
 Our theoretical framework centers around the argument that variation in macroeconomic growth amongst countries in the midst of civil war can be explained by the spatial proximity between civil conflicts and urban centers.
-In constructing our dataset, we thus restrict our unit of observation to conflict-country years.
+In constructing our dataset, we thus restrict the cases we include to only those country-years in which there was an internal armed conflict.
+Additionally, the unit of observation for this analysis is the country-year.
 This enables us to directly explore whether variation in growth amongst countries experiencing internal conflict can be explained by the proximity of conflict to cities.
+
 To measure macroeconomic performance, we focus on annual percent change in GDP from the World Development Indicators.
@@
 
-To determine the spatial proximity of conflict to urban centers, we collect information on the location of conflicts from the PRIO Conflict Site Dataset \citep{hallberg:2012}.
+We collect information on the location of conflicts from the PRIO Conflict Site Dataset \citep{hallberg:2012}.
 This dataset contains information on the geographical centers of armed conflict events and the area covered by each conflict at a yearly level from 1989 to 2008.
+In recent years, other geo-referenced datasets have been developed that go beyond just providing information on conflict centroids and area to providing an actual spatial grid structure through which to conduct analysis (e.g., \citealt{tollefsen:etal:2012}).
+For the purpose of this analysis, however, we deliberately avoid using these datasets since our primary interest is in examining variation in changes to GDP growth due to the proximity of conflict to urban centers.
+
+% Note to Ben: Does that sound convincing?
+Probably not.
+The point that I'm trying to get across is that using the gridded data is not at the appropriate level of analysis.
+We need to say something here about this so if you can think of something better that'd be great.
+
 To construct a time-series cross-sectional database of urban centers, we turn to yearly editions of The World Almanac from 1989 to 2008.
+More refined subnational data listing urban centers by their contribution to economic output would be the most direct way to test our hypothesis, however, cross-national data such as this over the time period of our analysis, especially for developing countries, is simply not available.
+The World Alamanac lists the major cities in a country by population, thus providing us with a second best approximation of the urban centers that are most relevant for a particular national economy.
 Typically, the Almanacs list at least three major cities, including the capital, for each country and year from 1989 to 2008.
-To determine proximity, we calculate the great-circle distance in kilometers between the centroid of each of the conflicts with the centroids of city locations.
-Meaning that for each year we determine the distance between every conflict and every major city within a state.
+We use the top five major cities listed for each country and then determine their geographical centers.
+
+% Again if you could add anything to why The World Alamanac data is the right choice that would be great.
+
+Using our geo-referenced conflict and urban center data, we proceed to compute the proximity of every civil armed conflict in a country-year from every urban center listed in that year.\footnote{Distances between centroid locations were computed using an iterative method of distance calculation proposed by \citet{vincenty:1975}.} Since our unit of analysis is the country-year, we aggregate the distance between conflicts and major cities by calculating the  minimum logged distance any conflict is from a major city.
+For example, if a country faces, four conflicts in a year, the datapoint for that country-year level would be the minimum distance any conflict centroid is from any city centroid.
+This choice of aggregation is what conforms closest to our theoretical claims about macroeconomic activity only being severely disrupted in cases of conflicts being proximate to major cities.
 
@@
 
-Our dependent variable is at the country-year and our key independent variable, distance between conflicts and major cities, is at the conflict-country-year level.
-To deal with this, we aggregate up to the country-year level by calculating the minimum logged distance any conflict is from a major city.
-Thus if a country faced, for example, four conflicts in one year, the datapoint that we would aggregate up to the country-year level would be for the conflict that was closest to a major city.
-This obviously is somewhat problematic as we end up discarding the information from the other conflicts.
-At the same time, we argue that this choice of aggregation is what conforms closest to our theoretical claims about economic activity only being severely disrupted in cases of conflicts being proximate to major cities.
+\subsection{Control Variables}
+
 From the PRIO dataset we also bring in additional information about that conflict, specifically its intensity, the area of conflict, whether the conflict involves a territorial dispute, and its duration.

### 2014-10-09 LaTeX/RhodiumConcl.tex
Updated bib.
revisions to intro
handing it back to ben

@@
 
-Our project seeks to explain observed discrepencies in the economic impact of civil conflict.
+This piece of research has sought to explain observed discrepencies in the economic impact of civil conflict.
 Violent intrastate conflicts have occured in one third of countries in just the past several decades.
@@
 Resources and population centers that are near the border between a peaceful state and a civil war state may be impacted in the same way that resources and cities within the conflict state are.
-This may help to explain the disparate regional economic effects of civil war observed by \cite{murdoch:sandler:2002}.
+This may help to explain the disparate regional economic effects of civil war observed by \cite{murdoch:sandler:2002b}.

### 2014-10-09 LaTeX/RhodiumEmp.tex
handing it back to ben

@@
 
-\subsection{Measuring Spatial Proximity of Conflict to Urban Centers}
+\subsection{Measuring Spatial Proximity}
 
@@
 
-% Again if you could add anything to why The World Alamanac data is the right choice that would be great.
-
-Using our geo-referenced conflict and urban center data, we proceed to compute the proximity of every civil armed conflict in a country-year from every urban center listed in that year.\footnote{Distances between centroid locations were computed using an iterative method of distance calculation proposed by \citet{vincenty:1975}.} Since our unit of analysis is the country-year, we aggregate the distance between conflicts and major cities by calculating the  minimum logged distance any conflict is from a major city.
-For example, if a country faces, four conflicts in a year, the datapoint for that country-year level would be the minimum distance any conflict centroid is from any city centroid.
-This choice of aggregation is what conforms closest to our theoretical claims about macroeconomic activity only being severely disrupted in cases of conflicts being proximate to major cities.
-
-\begin{figure}
-	\centering
-	\resizebox{.8\textwidth}{!}{\input{distGdp}}
-	\caption{Average relationship between city and capital distance from conflict and GDP growth.}
-	\label{fig:distGdp}
-\end{figure}
+% Note to Ben: Again if you could add anything to why The World Alamanac data is the right choice that would be great.
 
@@
 The centroid locations of conflicts are shown by red dots.
-Not surprisingly, we can see that in many cases conflict locations are clustered within specific parts of a country.
+Not surprisingly, in many cases conflict locations are clustered within specific parts of a country.
 In most cases, this clustering is indicative of the same conflict moving within the geographic boundaries of a country over time.
-The blue diamonds in \ref{fig:CityConfMap} denote the locations of major cities as identified in The World Alamanacs from 1989 to 2008.
+The blue diamonds in \ref{fig:CityConfMap} denote the locations of major cities from 1989 to 2008.
 Countries shaded in grey are those for which no armed conflict took place in this period according to the PRIO dataset.
@@
 	\includegraphics[width=1\textwidth]{CityConfMap-crop}
-	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008.
-Countries for which no armed conflicts are recorded are shaded in grey.}
+	\caption{This map illustrates the geographic distribution of all internal armed conflicts and major cities from 1989 to 2008. Countries for which no armed conflicts are recorded are shaded in grey.}
 	\label{fig:CityConfMap}
@@
 
-\subsection{Control Variables}
+Using our geo-referenced conflict and urban center data, we proceed to compute the proximity of every civil armed conflict in a country-year from every urban center listed in that year.\footnote{Distances between centroid locations were computed using an iterative method of distance calculation proposed by \citet{vincenty:1975}.} Since our unit of analysis is the country-year, we aggregate the distance between conflicts and major cities by calculating the minimum logged distance any conflict is from a major city.
+For example, if a country faces, four conflicts in a year, the datapoint for that country-year would be the minimum distance any conflict centroid is from any city centroid.
+In addition, to identifying the minimum distance a conflict is from any city, we also create a variable measures that measures minimum distance of any conflict from the capital of the country.
+Given the importance of cities as drivers of macroeconomic growth the proximity of conflict to even one city should have at least a noticeable short-term impact on growth.
+Thus this choice of aggregation conforms clostest to our theoretical claims about how macroeconomic growth can be severely disrupted in cases where conflicts are proximate to major cities.
 
-From the PRIO dataset we also bring in additional information about that conflict, specifically its intensity, the area of conflict, whether the conflict involves a territorial dispute, and its duration.
+Figure \ref{fig:distGdp} provides a cursory illustration of the relationship between GDP growth and our spatial proximity variables.
+Each bar on the rightmost panel represents the average GDP growth rate across country-years for which the minimum distance between the centroid of the conflict and capital city fell within a certain quartile range across our full sample.
+Clearly, as the minimum distance from a conflict to capital city declines, there is a sharp decline in average growth rates for the following year.
+On the rightmost panel of this figure, the same relationship holds when we test the effect of the minimum distance of conflict from any major urban center.
 
-Last, we include a number of additional control measures.
-First, we control for a country's total, logged land area to differentiate between the proximity effects of conflicts within large and small countries.
-We also control for a couple of macroeconomic variables that could affect year over year changes in GDP, specifically, lagged inflation and whether or not the state is an upper income country, as defined by the World Bank.
+\begin{figure}
+	\centering
+	\resizebox{.8\textwidth}{!}{\input{distGdp}}
+	\caption{Average percent change in GDP growth at time $t$ by distance from conflict to capital city on rightmost panel at time $t-1$, and from conflict to any city on the leftmost.
+The error bars represent the 95\% confidence interval around the mean.}
+	\label{fig:distGdp}
+\end{figure}
 
-Add in descriptors for each of these variables and expectations of their sign.
+\subsection{Empirical Model}
 
-A drawback with circular conflict zones is that they cover more territory than is actually affected by the conflict, including territories of neighboring countries.4 Due to the nature of armed conflict it may be impossible to gain information on the exact locations of armed encounters, occupied territories, and rebel bases.
-It might be possible to map the actual conflict-affected area with high precision for some well- reported conflicts, but it would be virtually impossible to code all conflict-years in the dataset coherently in a similar manner.
-The operationalization of conflict zones is essentially a trade-off between precision and simplicity, and in most cases a circular conflict zone will give a good indication of the core area of the conflict.
+% Note to Ben: Does empirical model sound weird?
 
-Using a dataset that includes 497 country-years of civil war from 68 different countries during the period of 1989 to 2007.
+Next, we move beyond this cursory illustration and explicate our full modeling strategy.
+Given how we constructed our spatial proximity of conflict variables, it would make little sense to include both within one model.
+The obvious problem we would run into is that there would be cases for which the minimum distance of a conflict to any city would be the same as the minimum distance to the capital.
+Thus we estimate two separate models, one where we include the minimum distance from a conflict to the capital and the other where we include the minimum distance to any urban center.
+In addition, to the inclusion of our spatial proximity covariates we include a number of control measures to account for extant explanations of how civil war dynamics affect GDP growth and to mitigate against omitted variable bias.
 
-To estimate the model we use random effects clustered on countries. The model we estimate is shown below:
+From the PRIO Armed Conflict dataset we bring in additional information about conflict intensity, duration, the area covered by the conflict, and the number of conflicts \citep{themner:wallensteen:2014}.
+Conflict intensity is a binary that distinguishes between minor armed conflicts and wars, and we set this equal to one if any of the conflicts in a country year were classified as a war and zero if not.
+In aggregating conflict duration to the country year level, we bring in the duration (measured in years) of the longest lasting conflict by a certain country-year.
+Conflict area measures the conflict zone in square kilometers.
+To include this in our country-year model, we sum up the area covered by each conflict being fought and divide by the total land area of the country.
+From this we then create a binary measure that is one if greater than 50\% of a country's total land area is immersed in conflict and zero otherwise.
+Finally, the number of conflicts is simply a count of the number of ongoing internal armed conflicts in a country-year according to the PRIO dataset.
+
+Aggregating each of the PRIO conflict descriptive measures in this way is to help account for those countries in which conflicts are especially intense, cover large areas, have been long-lasting, and multiple conflicts are occurring.
+Given the findings in the extant literature, our expectation is that each of these measures should have a negative effect on economic growth.
+Though we also expect that the substantive implications of any one of these measures will matter less than the adverse effect to economic growth by the spatial proximity of conflict to urban centers.
+
+We also include a number of variables that help to capture structural and institutional aspects of the country itself.
+First, we include a binary for whether the country is classified as upper income by the World Bank and for the level of inflation in the country.
+Second, we also control for the level of democracy in the country using the polity index \citep{marshall:etal:2013}.
+We also control for the proportion of a country's GDP that is made up of natural resource rents.
+This is a particularly important variable to control for as countries that draw a large share of their GDP from natural resource rents likely rely less on urban centers to serve as drivers of growth.
+Finally, given that the timeframe of our sample overlaps with the occurence of two major global crises, we add a control for the average GDP growth across all countries in the world.
+
+% Note to Ben: Anything else to add about why including polity would be important in the model?
+
+To estimate variation in growth rates, we use a random effects model clustered on countries.
+A random effects specification is preferred to using fixed effects here as we are not interested in estimating the change in GDP within units over time, rather our purpose is to explain variation between units.
+The total number of observations we have for this analysis are 497 country-year cases of civil war from 68 different countries during the period of 1989 to 2008.
+The estimation model is shown below, where $Ln(Min.
+\; Conflict \; Dist.)_{i,t-1}$ is a placeholder for $Ln(Min.
+\; Capital \; Dist.)_{i,t-1}$ and $Ln(Min.
+\; City \; Dist.)_{i,t-1}$:
 
 \begin{align*}
-	\% \Delta Log(GDP_{i,t}) &= \beta_{1}(Ln(Min. \; Conflict \; Dist.)_{i,t}) \\
-	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t}) \;+\; \beta_{3}(Conflict \; Type_{i,t}) \\
-	& \;+\; \beta_{4}(Conflict \; Duration_{i,t}) \;+\; \beta_{5}(Ln(Conflict \; Area)_{i,t}) \\	
-	& \;+\; \beta_{6}(Upper \; Income_{i,t}) \;+\; \beta_{7}(Inflation_{i,t-1}) \\
-	&  \;+\; \beta_{8}(Democracy_{i,t-1}) \;+\; \beta_{9}(Resource \; Rents/GDP_{t}) \\
-	& \;+\; \beta_{10}(World \; GDP \; Growth_{t}) \;+\; \mu_{i,t} \;+\; \epsilon_{i,t}
+	\% \Delta GDP_{i,t} &= \beta_{1}(Ln(Min. \; Conflict \; Dist.)_{i,t-1}) \\
+	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t-1}) \;+\; \beta_{3}(Conflict \; Duration_{i,t-1}) \\
+	& \;+\; \beta_{4}(Ln(Conflict \; Area)_{i,t-1}) \;+\; \beta_{5}(Upper \; Income_{i,t}) \\	
+	& \;+\; \beta_{6}(Inflation_{i,t-1}) \;+\; \beta_{7}(Democracy_{i,t-1}) \\
+	& \;+\; \beta_{8}(Resource \; Rents/GDP_{t-1}) \;+\; \beta_{9}(World \; GDP \; Growth_{t}) \\
+	& \;+\; \mu_{i,t} \;+\; \epsilon_{i,t}
 \end{align*}
@@
 
-We depict the results of our model in figure \ref{fig:coefPlot}.
-Most of the findings here are in line with our theoretical expectations.
-We find that higher levels of conflict intensity are associated with lower levels of GDP growth.
-The effect of conflict type is positive, indicating that non-territorial disputes are related to lower levels of GDP growth as well.
-Surprisingly, conflicts that are of a longer duration are, on average, not having a negative effect on GDP growth.
+We depict the results of our models in figures \ref{fig:capCoef} and \ref{fig:cityCoef}.
+The results across the two models are broadly consistent, so we will discuss them in tandem.
+The intensity of a conflict aligns in the direction that we would expect though its effect is marginal.
+Additionally, the effect of having a high proportion of a country's land area immersed in conflict is sharply negative and aligns with the findings in the extant literature.
+Surprisingly, conflict duration and the number of conflicts a country is facing do not relate to GDP growth in the direction that we expected.
+As expected, inflation has a sharp negative effect on GDP growth.
+Countries deriving greater shares of their GDP from natural resource rents see slighlty higher levels of growth, and, not surprisingly, the average of world GDP growth is positively related to our dependent variable.
 
-Most importantly, we find strong support for our key hypothesis relating the proximity of a conflict to lower levels of GDP growth.
-The fact that the logged, minimum conflict distance variable is positive indicates that conflicts closer to major cities have an adverse effect on economic growth.
+% Note to Ben: Anything you think we should say about the two surprising findings above
+
+Turning to our hypothesis, we find strong support for the argument that spatial proximity of conflict to either a capital city or any major urban center is associated with lower levels of GDP growth.
+The positive coefficient on the logged, minimum conflict distance variables indicates that conflicts closer to major cities has an adverse effect on economic growth.
 
@@
 
-To assess the substantive effect of the minimum conflict distance variable we conduct a number of simulations.
-We set up scenarios where we hold all variables to their median except for the logged, minimum conflict distance, which we range from its minimum to maximum value.
+To ensure that our parameter estimates are robust to changes in our sample, we run a six-fold cross-validation.
+This analysis helps us to understand whether some of the subsets in our dataset follow a different pattern than what is in the broader set \citep{beck2008time}.
+To conduct the cross-validation, we randomly split the 68 country observations in our dataset into six approximately equal subsets.
+Each subset ends up containing a minimum of approximately 65 cases.
+We then run each model shown in figure \ref{fig:coefplot} seven times, where in each iteration we left out one subsample.
+The results of this analysis are depicted in \ref{fig:crossPlot}, and we can clearly see that the parameter estimates for our two spatial proximity variables remain consistent across the exclusion of any of the folds.
+
+\begin{figure}
+	\centering
+	\resizebox{.8\textwidth}{!}{\input{crossValPlot}}
+	\caption{Each line here in the left panel shows the coefficient estimate of $Ln(Min.
+\; Capital \; Dist.)_{i,t-1}$ from rerunning the model on six random subsamples within the dataset.
+The panel on the right shows the same for $Ln(Min.
+\; City \; Dist.)_{i,t-1}$.
+All the covariates used in the initial model shown in figure \ref{fig:coefplot} were included as well.}
+	\label{fig:crossPlot}
+\end{figure}
+
+% Note from Ben: I think we should leave the rmse plot out because we cant hope to actually predict gdp growth with this model setup.
+But we've done plenty of other important things with checking that our parameter estimates are somewhat substantive and stable, so I'm happy.
+That's why I've commented it out for now.
+If you want to put it back in feel free.
+If you do though, you do have to say something about the RMSE still being pretty damn high.
+
+% \begin{figure}
+% 	\centering
+% 	\resizebox{.8\textwidth}{!}{\input{rmseInOut}}
+% 	\caption{In and out of sample performance.}
+% 	\label{fig:rmsePlot}
+% \end{figure}
+
+To assess the substantive effect of these results, we conduct a number of simulations.
+We set up scenarios where we hold all variables to their median except for logged, minimum conflict distance, which we range from its minimum to maximum value.
 Next, we conduct 1,000 random draws from a multivariate normal to obtain distributions for the point estimates of each of the regression coefficients.
 After obtaining these distributions, we calculate the predicted value of GDP growth based on the conditions set by the scenarios.
-We plot the results of this analyis in figure \ref{fig:simsPlot}.
+We plot the results of this analyis in figures \ref{fig:capSim} and \ref{fig:citySim}.
 
@@
 		\subfloat[SubFigure 1][Capital City]{
-			\resizebox{.45\textwidth}{!}{\input{mCapSimPlot}}
-		\label{fig:capCoef}} &
+			\resizebox{.7\textwidth}{!}{\input{mCapSimPlot}}
+		\label{fig:capSim}} \\
 		\subfloat[SubFigure 2][Any City]{
-			\resizebox{.45\textwidth}{!}{\input{mCitySimPlot}}
-		\label{fig:cityCoef}}
+			\resizebox{.7\textwidth}{!}{\input{mCitySimPlot}}
+		\label{fig:citySim}}
 	\end{tabular}
@@
 
-Here we can clearly see that conflicts located farther away from major cities have almost no adverse impact on economic growth.
-On average, countries for which conflicts are farther away see almost no declines in economic growth and, in fact, are likely to still see positive growth.
-Where we see more variation, however, is on the effect of conflicts near to major cities.
-Although on average our model estimates that these more proximate conflicts are associated with negative levels of economic growth our estimate of this effect is highly uncertain.
-This just indicates to us that more work needs to be done in parsing out possible variation in economic growth levels for those countries that are experiencing conflicts proximate to their major cities.
-Nonetheless, overall our results are quite in line with our theoretical expectations.
-
-\subsection{Model Performance}
-
-To assess the accuracy and performance of these estimates we employ a simple two-fold cross validation procedure.
-We use this procedure both to determine the robustness of our coefficient estimates when estimated on different subsamples of our dataset, and to assess how well the results of our model would generalize to an independent dataset.
-To begin the cross-validation, we split the 653 sanction cases in our dataset into six approximately equal subsets.
-We then run each model shown in Table \ref{tab:regResults} six times, where in each iteration we left out one subsample to use as a test set.
-This allows us to compare the prediction accuracy of each model, thereby helping us to determine the gains from incorporating the reciprocity covariates that are key to our argument.
-
-\begin{figure}
-	\centering
-	\resizebox{.8\textwidth}{!}{\input{rmseInOut}}
-	\caption{In and out of sample performance.}
-	\label{fig:rmsePlot}
-\end{figure}
-
-First, however, we show the results for our reciprocity covariates when we rerun our survival analysis on each of the six folds from the cross-validation.
-This analysis helps us to understand whether some of the subsets in our dataset follow a different pattern than what is in the broader set.\footnote{\cite{beck2008time}} Figure \ref{fig:crossval} shows that this is not the case for the analysis we present here, the coefficient estimates for compliance and sanction reciprocity remain consistent across each of these subsamples.\footnote{The parameter estimates for the other covariates also remain consistent across each of the six folds but we leave them out here due to space constraints.}
-
-\begin{figure}
-	\centering
-	\resizebox{.8\textwidth}{!}{\input{crossValPlot}}
-	\caption{Each row here shows the coefficient estimate of distance from rerunning the model on eight random subsamples within the dataset.
-All the covariates used in the initial models were included as well.}
-	\label{fig:crossPlot}
-\end{figure}
+The simulation results for both $Ln(Min.
+\; Capital \; Dist.)_{i,t-1}$ and $Ln(Min.
+\; City \; Dist.)_{i,t-1}$ are quite similar.
+In both cases, conflicts located farther away from major cities have almost no adverse impact on economic growth, and, in fact, are likely to still see positive growth.
+As the proximity of conflicts to urban centers increases, however, we can clearly see substantive declines in growth rates start to emerge.
+Thus, through utilizing these spatial proximity measures we can start to explain why there is such meaningful variation in economic performance amongst countries facing internal armed conflict.

### 2014-10-09 LaTeX/crossValPlot.tex
ugh
handing it back to ben

@@
-% Created by tikzDevice version 0.7.0 on 2014-10-06 19:49:11
+% Created by tikzDevice version 0.7.0 on 2014-10-09 04:34:25
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 58.48, 78.70) -- ( 58.48,232.72);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 58.48, 96.37) -- ( 58.48,236.07);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 89.81, 71.45) -- ( 89.81,227.72);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] ( 89.81, 89.61) -- ( 89.81,229.43);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (121.14, 91.74) -- (121.14,254.77);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (121.14,108.07) -- (121.14,254.77);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (152.47, 95.01) -- (152.47,247.01);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (152.47,102.39) -- (152.47,239.32);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (183.80, 99.56) -- (183.80,254.25);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (183.80,109.03) -- (183.80,248.22);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (215.13, 73.72) -- (215.13,227.75);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (215.13, 85.27) -- (215.13,225.67);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (246.46, 85.07) -- (246.46,232.49);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (246.46, 99.29) -- (246.46,233.41);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 58.48, 91.09) -- ( 58.48,220.34);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 58.48,107.60) -- ( 58.48,224.84);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 89.81, 84.01) -- ( 89.81,215.15);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] ( 89.81,100.85) -- ( 89.81,218.19);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (121.14,104.85) -- (121.14,241.67);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (121.14,119.86) -- (121.14,242.98);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (152.47,107.23) -- (152.47,234.79);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (152.47,113.40) -- (152.47,228.31);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (183.80,111.99) -- (183.80,241.82);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (183.80,120.22) -- (183.80,237.03);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (215.13, 86.11) -- (215.13,215.37);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (215.13, 96.56) -- (215.13,214.39);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (246.46, 96.92) -- (246.46,220.64);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (246.46,110.07) -- (246.46,222.63);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] ( 39.69, 62.52) -- (265.26, 62.52);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] ( 39.69, 62.23) -- (265.26, 62.23);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 58.48,155.71) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 58.48,166.22) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.81,149.58) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.81,159.52) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.14,173.26) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.14,181.42) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.47,171.01) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.47,170.85) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.80,176.91) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.80,178.62) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.13,150.74) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.13,155.47) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (246.46,158.78) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (246.46,166.35) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.92,232.72) --
-	( 60.05,232.72);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.92,236.07) --
+	( 60.05,236.07);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 58.48,232.72) --
-	( 58.48, 78.70);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 58.48,236.07) --
+	( 58.48, 96.37);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.92, 78.70) --
-	( 60.05, 78.70);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.92, 96.37) --
+	( 60.05, 96.37);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.25,227.72) --
-	( 91.38,227.72);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.25,229.43) --
+	( 91.38,229.43);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.81,227.72) --
-	( 89.81, 71.45);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.81,229.43) --
+	( 89.81, 89.61);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.25, 71.45) --
-	( 91.38, 71.45);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.25, 89.61) --
+	( 91.38, 89.61);
 
@@
 \path[draw=drawColor,line width= 0.6pt,line join=round] (121.14,254.77) --
-	(121.14, 91.74);
+	(121.14,108.07);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (119.58, 91.74) --
-	(122.71, 91.74);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (119.58,108.07) --
+	(122.71,108.07);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (150.91,247.01) --
-	(154.04,247.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.91,239.32) --
+	(154.04,239.32);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (152.47,247.01) --
-	(152.47, 95.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (152.47,239.32) --
+	(152.47,102.39);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (150.91, 95.01) --
-	(154.04, 95.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.91,102.39) --
+	(154.04,102.39);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (182.24,254.25) --
-	(185.37,254.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (182.24,248.22) --
+	(185.37,248.22);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (183.80,254.25) --
-	(183.80, 99.56);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (183.80,248.22) --
+	(183.80,109.03);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (182.24, 99.56) --
-	(185.37, 99.56);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (182.24,109.03) --
+	(185.37,109.03);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.57,227.75) --
-	(216.70,227.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (213.57,225.67) --
+	(216.70,225.67);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (215.13,227.75) --
-	(215.13, 73.72);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (215.13,225.67) --
+	(215.13, 85.27);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.57, 73.72) --
-	(216.70, 73.72);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (213.57, 85.27) --
+	(216.70, 85.27);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (244.90,232.49) --
-	(248.03,232.49);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.90,233.41) --
+	(248.03,233.41);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (246.46,232.49) --
-	(246.46, 85.07);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (246.46,233.41) --
+	(246.46, 99.29);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (244.90, 85.07) --
-	(248.03, 85.07);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.90, 99.29) --
+	(248.03, 99.29);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (287.07, 67.19) -- (287.07,224.97);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (287.07, 86.92) -- (287.07,229.97);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (318.40, 88.38) -- (318.40,245.63);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (318.40,100.36) -- (318.40,245.14);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (349.73, 71.61) -- (349.73,242.46);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (349.73, 91.30) -- (349.73,245.39);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (381.06, 91.40) -- (381.06,250.60);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (381.06, 98.14) -- (381.06,243.75);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (412.39, 88.88) -- (412.39,249.59);
-\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
-\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (412.39, 99.88) -- (412.39,244.40);
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (443.72, 62.23) -- (443.72,221.53);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (443.72, 74.08) -- (443.72,220.21);
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (475.05, 95.45) -- (475.05,230.77);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (475.05, 77.47) -- (475.05,227.88);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (287.07, 98.41) -- (287.07,218.47);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (318.40,112.00) -- (318.40,233.50);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (349.73,103.69) -- (349.73,233.00);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (381.06,109.85) -- (381.06,232.04);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (412.39,111.49) -- (412.39,232.78);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (443.72, 85.83) -- (443.72,208.46);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (475.05,106.33) -- (475.05,219.89);
+\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
+\definecolor[named]{fillColor}{rgb}{0.00,0.00,0.00}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (268.27, 62.23) -- (493.85, 62.23);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (287.07, 79.88) -- (287.07,212.29);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (287.07,158.44) circle (  2.85);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (318.40,101.02) -- (318.40,232.99);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (318.40,172.75) circle (  2.85);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (349.73, 85.35) -- (349.73,228.72);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (349.73,168.35) circle (  2.85);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (381.06,104.20) -- (381.06,237.81);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (381.06,170.94) circle (  2.85);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (412.39,101.80) -- (412.39,236.67);
-\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
-\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (412.39,172.14) circle (  2.85);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (443.72, 75.03) -- (443.72,208.73);
-\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
-\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.72,147.14) circle (  2.85);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (475.05, 89.56) -- (475.05,215.79);
-\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
-\definecolor[named]{fillColor}{rgb}{0.00,0.00,0.00}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (475.05,163.11) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (268.27, 62.52) -- (493.85, 62.52);
-\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
-\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+\path[draw=drawColor,line width= 0.6pt,line join=round] (285.50,229.97) --
+	(288.64,229.97);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (287.07,146.08) circle (  2.85);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (287.07,229.97) --
+	(287.07, 86.92);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (318.40,167.00) circle (  2.85);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (285.50, 86.92) --
+	(288.64, 86.92);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (349.73,157.04) circle (  2.85);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (316.83,245.14) --
+	(319.97,245.14);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (381.06,171.00) circle (  2.85);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (318.40,245.14) --
+	(318.40,100.36);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (412.39,169.24) circle (  2.85);
-\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
-\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}
+\path[draw=drawColor,line width= 0.6pt,line join=round] (316.83,100.36) --
+	(319.97,100.36);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.72,141.88) circle (  2.85);
-\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
-\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.16,245.39) --
+	(351.30,245.39);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (475.05,152.67) circle (  2.85);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (349.73,245.39) --
+	(349.73, 91.30);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (285.50,224.97) --
-	(288.64,224.97);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.16, 91.30) --
+	(351.30, 91.30);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (287.07,224.97) --
-	(287.07, 67.19);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (379.49,243.75) --
+	(382.62,243.75);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (285.50, 67.19) --
-	(288.64, 67.19);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (381.06,243.75) --
+	(381.06, 98.14);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (316.83,245.63) --
-	(319.97,245.63);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (379.49, 98.14) --
+	(382.62, 98.14);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (318.40,245.63) --
-	(318.40, 88.38);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (410.82,244.40) --
+	(413.95,244.40);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (316.83, 88.38) --
-	(319.97, 88.38);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (412.39,244.40) --
+	(412.39, 99.88);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (348.16,242.46) --
-	(351.30,242.46);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (410.82, 99.88) --
+	(413.95, 99.88);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (349.73,242.46) --
-	(349.73, 71.61);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (442.15,220.21) --
+	(445.28,220.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (348.16, 71.61) --
-	(351.30, 71.61);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (443.72,220.21) --
+	(443.72, 74.08);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (379.49,250.60) --
-	(382.62,250.60);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (442.15, 74.08) --
+	(445.28, 74.08);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (381.06,250.60) --
-	(381.06, 91.40);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (473.48,230.77) --
+	(476.61,230.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (379.49, 91.40) --
-	(382.62, 91.40);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (475.05,230.77) --
+	(475.05, 95.45);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (410.82,249.59) --
-	(413.95,249.59);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (412.39,249.59) --
-	(412.39, 88.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (410.82, 88.88) --
-	(413.95, 88.88);
-\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (442.15,221.53) --
-	(445.28,221.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (443.72,221.53) --
-	(443.72, 62.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (442.15, 62.23) --
-	(445.28, 62.23);
-\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (473.48,227.88) --
-	(476.61,227.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (475.05,227.88) --
-	(475.05, 77.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (473.48, 77.47) --
-	(476.61, 77.47);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (473.48, 95.45) --
+	(476.61, 95.45);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 59.21) {0.0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 58.92) {0.0};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,108.66) {0.5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,105.28) {0.5};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,158.12) {1.0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,151.64) {1.0};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,207.57) {1.5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,198.00) {1.5};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,257.02) {2.0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,244.36) {2.0};
 \end{scope}

### 2014-10-09 LaTeX/mCapCoefPlot.tex
handing it back to ben

--- 2014-09-23 LaTeX/mCapCoefPlot.tex
@@
-% Created by tikzDevice version 0.7.0 on 2014-09-23 11:36:12
+% Created by tikzDevice version 0.7.0 on 2014-10-09 04:51:34
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,433.62);
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
 \definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (289.08,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (289.08,433.62);
 \end{scope}
 \begin{scope}
-\path[clip] (137.46, 34.03) rectangle (277.03,277.03);
+\path[clip] (137.46, 34.03) rectangle (277.03,421.57);
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
 
-\path[fill=fillColor] (137.46, 34.03) rectangle (277.03,277.03);
+\path[fill=fillColor] (137.46, 34.03) rectangle (277.03,421.57);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.46, 56.83) -- (211.86, 56.83);
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.17, 94.83) -- (201.83, 94.83);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (206.43, 49.88) -- (213.45, 49.88);
-
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (198.47, 76.30) -- (231.75, 76.30);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (198.50,132.82) -- (202.73,132.82);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (183.03,102.71) -- (196.68,102.71);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (150.09,170.81) -- (171.00,170.81);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (165.42,129.12) -- (249.46,129.12);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (143.80,208.81) -- (270.69,208.81);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.68,246.80) -- (231.65,246.80);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (175.86,155.53) -- (202.88,155.53);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (146.25,284.80) -- (189.36,284.80);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (207.28,181.95) -- (208.37,181.95);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.30,322.79) -- (202.08,322.79);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (194.89,208.36) -- (229.18,208.36);
-
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (189.15,234.77) -- (216.25,234.77);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (162.26,360.78) -- (204.09,360.78);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (209.85,261.19) -- (221.60,261.19);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (205.85,398.78) -- (223.31,398.78);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (201.38, 56.83) -- (210.95, 56.83);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (200.30, 94.83) -- (201.70, 94.83);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (206.99, 49.88) -- (212.88, 49.88);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (201.15, 76.30) -- (229.08, 76.30);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (198.84,132.82) -- (202.39,132.82);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (184.13,102.71) -- (195.58,102.71);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (151.77,170.81) -- (169.32,170.81);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (172.18,129.12) -- (242.71,129.12);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (154.00,208.81) -- (260.49,208.81);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (203.17,246.80) -- (229.16,246.80);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (178.04,155.53) -- (200.70,155.53);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (149.72,284.80) -- (185.89,284.80);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (207.37,181.95) -- (208.28,181.95);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (200.45,322.79) -- (201.93,322.79);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (197.65,208.36) -- (226.42,208.36);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (191.33,234.77) -- (214.07,234.77);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (165.62,360.78) -- (200.73,360.78);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (210.79,261.19) -- (220.66,261.19);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (207.25,398.78) -- (221.91,398.78);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (207.25, 34.03) -- (207.25,277.03);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (199.91, 34.03) -- (199.91,421.57);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.73,261.19) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (214.58,398.78) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (202.70,234.77) circle (  2.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (212.04,208.36) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.18,360.78) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.82,181.95) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.19,322.79) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.37,155.53) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.80,284.80) circle (  2.85);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (216.16,246.80) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.44,129.12) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.25,208.81) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.85,102.71) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.54,170.81) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.11, 76.30) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (200.61,132.82) circle (  2.85);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.94, 49.88) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.00, 94.83) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.45, 48.56) --
-	(213.45, 51.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (206.16, 56.83) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.45, 49.88) --
-	(206.43, 49.88);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (211.86, 54.93) --
+	(211.86, 58.73);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (206.43, 48.56) --
-	(206.43, 51.20);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (211.86, 56.83) --
+	(200.46, 56.83);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (231.75, 74.97) --
-	(231.75, 77.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (200.46, 54.93) --
+	(200.46, 58.73);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (231.75, 76.30) --
-	(198.47, 76.30);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (201.83, 92.93) --
+	(201.83, 96.72);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (198.47, 74.97) --
-	(198.47, 77.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (201.83, 94.83) --
+	(200.17, 94.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (200.17, 92.93) --
+	(200.17, 96.72);
+\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.73,130.92) --
+	(202.73,134.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.73,132.82) --
+	(198.50,132.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (198.50,130.92) --
+	(198.50,134.72);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (196.68,101.39) --
-	(196.68,104.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (171.00,168.91) --
+	(171.00,172.71);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (196.68,102.71) --
-	(183.03,102.71);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (171.00,170.81) --
+	(150.09,170.81);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (183.03,101.39) --
-	(183.03,104.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.09,168.91) --
+	(150.09,172.71);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (249.46,127.80) --
-	(249.46,130.44);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (270.69,206.91) --
+	(270.69,210.71);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (249.46,129.12) --
-	(165.42,129.12);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (270.69,208.81) --
+	(143.80,208.81);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.42,127.80) --
-	(165.42,130.44);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (143.80,206.91) --
+	(143.80,210.71);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (231.65,244.90) --
+	(231.65,248.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (231.65,246.80) --
+	(200.68,246.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (200.68,244.90) --
+	(200.68,248.70);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (202.88,154.21) --
-	(202.88,156.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (189.36,282.90) --
+	(189.36,286.70);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (202.88,155.53) --
-	(175.86,155.53);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (189.36,284.80) --
+	(146.25,284.80);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (175.86,154.21) --
-	(175.86,156.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (146.25,282.90) --
+	(146.25,286.70);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (208.37,180.63) --
-	(208.37,183.27);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.08,320.89) --
+	(202.08,324.69);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (208.37,181.95) --
-	(207.28,181.95);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.08,322.79) --
+	(200.30,322.79);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.28,180.63) --
-	(207.28,183.27);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (200.30,320.89) --
+	(200.30,324.69);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (229.18,207.04) --
-	(229.18,209.68);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (204.09,358.88) --
+	(204.09,362.68);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (229.18,208.36) --
-	(194.89,208.36);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (204.09,360.78) --
+	(162.26,360.78);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (194.89,207.04) --
-	(194.89,209.68);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.25,233.45) --
-	(216.25,236.09);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.25,234.77) --
-	(189.15,234.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (189.15,233.45) --
-	(189.15,236.09);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (162.26,358.88) --
+	(162.26,362.68);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (221.60,259.87) --
-	(221.60,262.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (223.31,396.88) --
+	(223.31,400.68);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (221.60,261.19) --
-	(209.85,261.19);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (223.31,398.78) --
+	(205.85,398.78);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.85,259.87) --
-	(209.85,262.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.85,396.88) --
+	(205.85,400.68);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
@@
 \path[draw=drawColor,line width= 0.6pt,line join=round] (137.46, 34.03) --
-	(137.46,277.03);
+	(137.46,421.57);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 46.58) {World GDP Growth$_{t}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 53.53) {World GDP Growth$_{t}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 72.99) {Democracy$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 91.52) {Resource Rents/GDP$_{t}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 99.40) {Ln(Inflation)$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,129.51) {Democracy$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,125.82) {Upper Income};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,167.51) {Ln(Inflation)$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,152.23) {Area$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,205.50) {Upper Income};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,178.64) {Duration$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,243.50) {Number of conflicts$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,205.06) {Type$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,281.49) {Area$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,231.47) {Intensity$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,319.48) {Duration$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,257.88) {Ln(Min. Capital Dist.)$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,357.48) {Intensity$_{t-1}$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,395.47) {Ln(Min. Capital Dist.)$_{t-1}$};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
@@
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (143.80, 20.31) {-0.3};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (168.51, 20.31) {-2.5};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (186.10, 20.31) {-0.1};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (199.91, 20.31) {0.0};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (228.40, 20.31) {0.1};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (231.31, 20.31) {2.5};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (270.69, 20.31) {0.3};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (262.71, 20.31) {5.0};
 \end{scope}

### 2014-10-09 LaTeX/mCityCoefPlot.tex
handing it back to ben

--- 2014-09-23 LaTeX/mCityCoefPlot.tex
@@
-% Created by tikzDevice version 0.7.0 on 2014-09-23 11:36:07
+% Created by tikzDevice version 0.7.0 on 2014-10-09 04:51:33
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (289.08,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (289.08,433.62);
 \end{scope}
 \begin{scope}
-\path[clip] (124.66, 34.03) rectangle (277.03,277.03);
+\path[clip] (124.66, 34.03) rectangle (277.03,421.57);
 \definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
 
-\path[fill=fillColor] (124.66, 34.03) rectangle (277.04,277.03);
+\path[fill=fillColor] (124.66, 34.03) rectangle (277.04,421.57);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (192.15, 56.83) -- (204.46, 56.83);
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (191.47, 94.83) -- (193.27, 94.83);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.10, 49.88) -- (207.76, 49.88);
-
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (193.68, 76.30) -- (230.11, 76.30);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (189.94,132.82) -- (194.54,132.82);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (174.88,102.71) -- (189.88,102.71);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (138.21,170.81) -- (160.94,170.81);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (155.06,129.12) -- (247.73,129.12);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (131.97,208.81) -- (270.11,208.81);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (191.59,246.80) -- (225.22,246.80);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (165.59,155.53) -- (195.00,155.53);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (131.59,284.80) -- (178.00,284.80);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (200.88,181.95) -- (202.07,181.95);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (191.56,322.79) -- (193.49,322.79);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (187.98,208.36) -- (225.50,208.36);
-
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (180.79,234.77) -- (210.45,234.77);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (150.17,360.78) -- (195.44,360.78);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (203.18,261.19) -- (216.39,261.19);
+\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30] (196.77,398.78) -- (216.33,398.78);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (193.14, 56.83) -- (203.47, 56.83);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (191.61, 94.83) -- (193.13, 94.83);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (200.72, 49.88) -- (207.15, 49.88);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (196.61, 76.30) -- (227.18, 76.30);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (190.31,132.82) -- (194.17,132.82);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (176.09,102.71) -- (188.68,102.71);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (140.04,170.81) -- (159.12,170.81);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (162.51,129.12) -- (240.28,129.12);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (143.08,208.81) -- (259.00,208.81);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (194.29,246.80) -- (222.52,246.80);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (167.95,155.53) -- (192.63,155.53);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (135.32,284.80) -- (174.27,284.80);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (200.97,181.95) -- (201.98,181.95);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (191.72,322.79) -- (193.33,322.79);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (191.00,208.36) -- (222.48,208.36);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (183.17,234.77) -- (208.07,234.77);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (153.81,360.78) -- (191.80,360.78);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (204.24,261.19) -- (215.33,261.19);
+\path[draw=drawColor,line width= 1.1pt,line join=round,fill=fillColor] (198.34,398.78) -- (214.76,398.78);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (200.85, 34.03) -- (200.85,277.03);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,fill=fillColor] (191.18, 34.03) -- (191.18,421.57);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.79,261.19) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (206.55,398.78) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (195.62,234.77) circle (  2.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (206.74,208.36) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.80,360.78) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.47,181.95) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.53,322.79) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.29,155.53) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.79,284.80) circle (  2.85);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.40,246.80) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.39,129.12) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.04,208.81) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.38,102.71) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.58,170.81) circle (  2.85);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (211.89, 76.30) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.24,132.82) circle (  2.85);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (203.93, 49.88) circle (  2.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.37, 94.83) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.76, 48.56) --
-	(207.76, 51.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (198.31, 56.83) circle (  2.85);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.76, 49.88) --
-	(200.10, 49.88);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (204.46, 54.93) --
+	(204.46, 58.73);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (200.10, 48.56) --
-	(200.10, 51.20);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (204.46, 56.83) --
+	(192.15, 56.83);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (230.11, 74.97) --
-	(230.11, 77.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (192.15, 54.93) --
+	(192.15, 58.73);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (230.11, 76.30) --
-	(193.68, 76.30);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (193.27, 92.93) --
+	(193.27, 96.72);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (193.68, 74.97) --
-	(193.68, 77.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (193.27, 94.83) --
+	(191.47, 94.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (191.47, 92.93) --
+	(191.47, 96.72);
+\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (194.54,130.92) --
+	(194.54,134.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (194.54,132.82) --
+	(189.94,132.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (189.94,130.92) --
+	(189.94,134.72);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (189.88,101.39) --
-	(189.88,104.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (160.94,168.91) --
+	(160.94,172.71);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (189.88,102.71) --
-	(174.88,102.71);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (160.94,170.81) --
+	(138.21,170.81);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (174.88,101.39) --
-	(174.88,104.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (138.21,168.91) --
+	(138.21,172.71);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (247.73,127.80) --
-	(247.73,130.44);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (270.11,206.91) --
+	(270.11,210.71);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (247.73,129.12) --
-	(155.06,129.12);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (270.11,208.81) --
+	(131.97,208.81);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (155.06,127.80) --
-	(155.06,130.44);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (131.97,206.91) --
+	(131.97,210.71);
+\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (225.22,244.90) --
+	(225.22,248.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (225.22,246.80) --
+	(191.59,246.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (191.59,244.90) --
+	(191.59,248.70);
 \definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (195.00,154.21) --
-	(195.00,156.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (178.00,282.90) --
+	(178.00,286.70);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (195.00,155.53) --
-	(165.59,155.53);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (178.00,284.80) --
+	(131.59,284.80);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.59,154.21) --
-	(165.59,156.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (131.59,282.90) --
+	(131.59,286.70);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (202.07,180.63) --
-	(202.07,183.27);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (193.49,320.89) --
+	(193.49,324.69);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (202.07,181.95) --
-	(200.88,181.95);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (193.49,322.79) --
+	(191.56,322.79);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (200.88,180.63) --
-	(200.88,183.27);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (191.56,320.89) --
+	(191.56,324.69);
 \definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (225.50,207.04) --
-	(225.50,209.68);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.44,358.88) --
+	(195.44,362.68);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (225.50,208.36) --
-	(187.98,208.36);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.44,360.78) --
+	(150.17,360.78);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (187.98,207.04) --
-	(187.98,209.68);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (210.45,233.45) --
-	(210.45,236.09);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (210.45,234.77) --
-	(180.79,234.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (180.79,233.45) --
-	(180.79,236.09);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.17,358.88) --
+	(150.17,362.68);
 \definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.39,259.87) --
-	(216.39,262.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (216.33,396.88) --
+	(216.33,400.68);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.39,261.19) --
-	(203.18,261.19);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (216.33,398.78) --
+	(196.77,398.78);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (203.18,259.87) --
-	(203.18,262.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (196.77,396.88) --
+	(196.77,400.68);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
@@
 \path[draw=drawColor,line width= 0.6pt,line join=round] (124.66, 34.03) --
-	(124.66,277.03);
+	(124.66,421.57);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55, 46.58) {World GDP Growth$_{t}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55, 53.53) {World GDP Growth$_{t}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55, 72.99) {Democracy$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55, 91.52) {Resource Rents/GDP$_{t}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55, 99.40) {Ln(Inflation)$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,129.51) {Democracy$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,125.82) {Upper Income};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,167.51) {Ln(Inflation)$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,152.23) {Area$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,205.50) {Upper Income};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,178.64) {Duration$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,243.50) {Number of conflicts$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,205.06) {Type$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,281.49) {Area$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,231.47) {Intensity$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,319.48) {Duration$_{t-1}$};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,257.88) {Ln(Min. City Dist.)$_{t-1}$};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,357.48) {Intensity$_{t-1}$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (117.55,395.47) {Ln(Min. City Dist.)$_{t-1}$};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
@@
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
 \definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (131.59, 20.31) {-0.3};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (157.28, 20.31) {-2.5};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (177.76, 20.31) {-0.1};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (191.18, 20.31) {0.0};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (223.94, 20.31) {0.1};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (225.07, 20.31) {2.5};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (270.11, 20.31) {0.3};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (258.97, 20.31) {5.0};
 \end{scope}

### 2014-10-09 LaTeX/mCitySimPlot.tex
handing it back to ben

--- 2014-10-06 LaTeX/mCitySimPlot.tex
@@
-% Created by tikzDevice version 0.7.0 on 2014-10-06 19:44:41
+% Created by tikzDevice version 0.7.0 on 2014-10-09 04:51:36
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (433.62,289.08);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,106.37) --
-	( 61.01,109.04) --
-	( 65.48,110.52) --
-	( 65.62,110.57) --
-	( 79.64,115.23) --
-	( 88.50,118.17) --
-	( 94.41,120.14) --
-	( 97.84,121.27) --
-	(104.50,123.49) --
-	(110.01,125.32) --
-	(113.94,126.62) --
-	(116.56,127.49) --
-	(124.94,130.28) --
-	(160.01,141.93) --
-	(160.15,141.97) --
-	(163.56,143.10) --
-	(164.50,143.42) --
-	(175.08,146.93) --
-	(177.68,147.80) --
-	(185.12,150.27) --
-	(195.04,153.56) --
-	(195.05,153.57) --
-	(199.79,155.14) --
-	(200.09,155.24) --
-	(201.70,155.77) --
-	(202.42,156.01) --
-	(203.15,156.26) --
-	(203.24,156.29) --
-	(203.92,156.51) --
-	(204.08,156.56) --
-	(205.70,157.10) --
-	(211.30,158.97) --
-	(213.02,159.54) --
-	(213.22,159.60) --
-	(213.28,159.62) --
-	(214.88,160.15) --
-	(219.39,161.65) --
-	(219.87,161.81) --
-	(224.51,163.35) --
-	(226.38,163.97) --
-	(226.89,164.14) --
-	(228.22,164.58) --
-	(229.80,165.11) --
-	(230.53,165.35) --
-	(231.54,165.69) --
-	(232.29,165.94) --
-	(232.55,166.02) --
-	(232.60,166.04) --
-	(233.03,166.18) --
-	(236.50,167.34) --
-	(238.44,167.98) --
-	(239.50,168.33) --
-	(240.76,168.75) --
-	(242.87,169.45) --
-	(243.82,169.77) --
-	(244.87,170.11) --
-	(245.90,170.46) --
-	(247.14,170.87) --
-	(247.15,170.87) --
-	(248.00,171.16) --
-	(248.59,171.35) --
-	(249.15,171.54) --
-	(249.91,171.79) --
-	(250.14,171.87) --
-	(250.71,172.06) --
-	(251.21,172.22) --
-	(251.61,172.35) --
-	(251.88,172.44) --
-	(252.52,172.66) --
-	(252.98,172.81) --
-	(253.12,172.85) --
-	(253.36,172.94) --
-	(254.91,173.45) --
-	(255.02,173.49) --
-	(256.32,173.92) --
-	(258.61,174.68) --
-	(260.03,175.15) --
-	(260.14,175.19) --
-	(260.80,175.41) --
-	(261.97,175.79) --
-	(262.19,175.87) --
-	(262.48,175.96) --
-	(262.99,176.14) --
-	(264.29,176.57) --
-	(264.50,176.64) --
-	(264.53,176.65) --
-	(264.97,176.79) --
-	(266.10,177.17) --
-	(266.13,177.18) --
-	(266.44,177.28) --
-	(267.28,177.56) --
-	(267.71,177.70) --
-	(268.38,177.92) --
-	(269.11,178.17) --
-	(269.74,178.38) --
-	(269.87,178.42) --
-	(271.02,178.80) --
-	(271.10,178.83) --
-	(271.68,179.02) --
-	(272.40,179.26) --
-	(272.79,179.39) --
-	(273.63,179.67) --
-	(274.52,179.96) --
-	(275.28,180.22) --
-	(275.59,180.32) --
-	(276.13,180.50) --
-	(276.31,180.56) --
-	(276.77,180.71) --
-	(277.30,180.89) --
-	(277.98,181.12) --
-	(278.04,181.13) --
-	(278.45,181.27) --
-	(279.17,181.51) --
-	(279.30,181.55) --
-	(279.52,181.62) --
-	(279.66,181.67) --
-	(279.69,181.68) --
-	(280.15,181.83) --
-	(280.53,181.96) --
-	(280.72,182.02) --
-	(281.20,182.18) --
-	(281.36,182.24) --
-	(281.45,182.27) --
-	(282.80,182.71) --
-	(283.05,182.80) --
-	(283.89,183.08) --
-	(283.98,183.11) --
-	(284.07,183.14) --
-	(284.62,183.32) --
-	(284.86,183.40) --
-	(285.03,183.46) --
-	(285.13,183.49) --
-	(286.00,183.78) --
-	(286.57,183.97) --
-	(286.59,183.98) --
-	(287.25,184.19) --
-	(287.81,184.38) --
-	(288.54,184.62) --
-	(288.59,184.64) --
-	(289.22,184.85) --
-	(289.76,185.03) --
-	(290.76,185.36) --
-	(290.86,185.39) --
-	(291.20,185.51) --
-	(291.32,185.54) --
-	(291.81,185.71) --
-	(291.88,185.73) --
-	(292.21,185.84) --
-	(292.36,185.89) --
-	(292.42,185.91) --
-	(292.49,185.93) --
-	(292.51,185.94) --
-	(292.62,185.98) --
-	(293.21,186.17) --
-	(293.91,186.41) --
-	(295.25,186.85) --
-	(295.45,186.92) --
-	(295.51,186.94) --
-	(295.93,187.08) --
-	(295.99,187.10) --
-	(296.10,187.13) --
-	(296.47,187.26) --
-	(296.65,187.32) --
-	(296.99,187.43) --
-	(297.01,187.43) --
-	(297.04,187.45) --
-	(297.05,187.45) --
-	(297.09,187.46) --
-	(297.13,187.47) --
-	(297.22,187.51) --
-	(297.31,187.53) --
-	(297.31,187.53) --
-	(297.71,187.67) --
-	(297.96,187.75) --
-	(298.34,187.88) --
-	(298.57,187.95) --
-	(299.04,188.11) --
-	(300.58,188.62) --
-	(300.69,188.66) --
-	(301.32,188.87) --
-	(302.10,189.13) --
-	(302.23,189.17) --
-	(302.50,189.26) --
-	(302.82,189.36) --
-	(302.98,189.42) --
-	(303.49,189.59) --
-	(303.87,189.71) --
-	(304.04,189.77) --
-	(304.05,189.77) --
-	(304.17,189.82) --
-	(304.21,189.83) --
-	(304.88,190.05) --
-	(305.44,190.24) --
-	(305.52,190.26) --
-	(305.61,190.29) --
-	(305.86,190.37) --
-	(306.19,190.49) --
-	(306.32,190.53) --
-	(307.91,191.06) --
-	(307.96,191.07) --
-	(308.47,191.24) --
-	(308.57,191.27) --
-	(309.22,191.49) --
-	(309.44,191.56) --
-	(309.51,191.59) --
-	(309.67,191.64) --
-	(310.00,191.75) --
-	(310.25,191.83) --
-	(310.76,192.00) --
-	(310.92,192.06) --
-	(311.04,192.09) --
-	(311.16,192.14) --
-	(311.41,192.22) --
-	(311.41,192.22) --
-	(311.44,192.23) --
-	(311.54,192.26) --
-	(311.68,192.31) --
-	(311.68,192.31) --
-	(311.88,192.38) --
-	(312.22,192.49) --
-	(312.92,192.72) --
-	(313.12,192.79) --
-	(313.27,192.84) --
-	(313.53,192.93) --
-	(313.83,193.02) --
-	(314.24,193.16) --
-	(314.31,193.18) --
-	(314.45,193.23) --
-	(314.63,193.29) --
-	(315.00,193.41) --
-	(315.21,193.48) --
-	(315.23,193.49) --
-	(315.37,193.53) --
-	(315.48,193.57) --
-	(315.51,193.58) --
-	(315.62,193.62) --
-	(315.70,193.64) --
-	(315.79,193.67) --
-	(316.13,193.79) --
-	(316.22,193.82) --
-	(316.38,193.87) --
-	(316.61,193.95) --
-	(316.93,194.05) --
-	(317.07,194.10) --
-	(317.20,194.14) --
-	(317.36,194.20) --
-	(317.75,194.33) --
-	(317.76,194.33) --
-	(317.79,194.34) --
-	(317.86,194.36) --
-	(317.89,194.37) --
-	(317.98,194.40) --
-	(318.43,194.55) --
-	(318.60,194.61) --
-	(318.85,194.69) --
-	(319.11,194.78) --
-	(319.21,194.81) --
-	(319.52,194.91) --
-	(319.81,195.01) --
-	(320.44,195.22) --
-	(321.85,195.69) --
-	(321.91,195.71) --
-	(322.04,195.75) --
-	(322.30,195.84) --
-	(322.60,195.94) --
-	(322.75,195.99) --
-	(323.02,196.08) --
-	(323.10,196.10) --
-	(323.28,196.16) --
-	(324.05,196.42) --
-	(324.42,196.54) --
-	(324.61,196.60) --
-	(324.72,196.64) --
-	(325.08,196.76) --
-	(325.99,197.06) --
-	(326.58,197.26) --
-	(326.72,197.31) --
-	(327.61,197.60) --
-	(327.91,197.70) --
-	(328.67,197.95) --
-	(328.94,198.04) --
-	(329.07,198.09) --
-	(329.52,198.24) --
-	(331.17,198.78) --
-	(332.00,199.06) --
-	(332.27,199.15) --
-	(333.07,199.42) --
-	(333.19,199.45) --
-	(333.76,199.64) --
-	(335.51,200.23) --
-	(336.07,200.41) --
-	(336.75,200.64) --
-	(336.88,200.68) --
-	(337.54,200.90) --
-	(337.92,201.03) --
-	(338.29,201.15) --
-	(338.32,201.16) --
-	(338.37,201.17) --
-	(338.79,201.32) --
-	(338.87,201.34) --
-	(339.41,201.52) --
-	(339.54,201.56) --
-	(340.26,201.80) --
-	(340.28,201.81) --
-	(340.36,201.84) --
-	(340.58,201.91) --
-	(340.90,202.02) --
-	(341.07,202.07) --
-	(341.38,202.18) --
-	(341.48,202.21) --
-	(341.53,202.23) --
-	(341.57,202.24) --
-	(342.00,202.38) --
-	(342.06,202.40) --
-	(342.60,202.58) --
-	(342.92,202.69) --
-	(344.39,203.18) --
-	(344.81,203.31) --
-	(345.03,203.39) --
-	(345.51,203.55) --
-	(345.56,203.56) --
-	(346.27,203.80) --
-	(348.09,204.40) --
-	(348.19,204.44) --
-	(348.32,204.48) --
-	(348.52,204.55) --
-	(348.65,204.59) --
-	(350.04,205.05) --
-	(350.29,205.13) --
-	(350.39,205.17) --
-	(351.49,205.53) --
-	(354.19,206.43) --
-	(354.41,206.50) --
-	(354.96,206.69) --
-	(354.99,206.69) --
-	(355.28,206.79) --
-	(355.84,206.98) --
-	(356.71,207.27) --
-	(356.75,207.28) --
-	(357.50,207.53) --
-	(357.53,207.54) --
-	(358.04,207.71) --
-	(358.62,207.90) --
-	(359.31,208.13) --
-	(359.62,208.23) --
-	(359.75,208.28) --
-	(359.85,208.31) --
-	(360.61,208.56) --
-	(360.64,208.57) --
-	(360.71,208.60) --
-	(361.91,208.99) --
-	(362.60,209.22) --
-	(364.24,209.77) --
-	(364.46,209.84) --
-	(365.70,210.25) --
-	(366.29,210.45) --
-	(370.53,211.86) --
-	(371.02,212.02) --
-	(372.06,212.37) --
-	(372.07,212.37) --
-	(372.38,212.47) --
-	(372.60,212.54) --
-	(372.90,212.65) --
-	(373.16,212.73) --
-	(373.53,212.86) --
-	(373.80,212.94) --
-	(374.46,213.16) --
-	(374.81,213.28) --
-	(375.77,213.60) --
-	(376.36,213.80) --
-	(376.51,213.85) --
-	(376.93,213.98) --
-	(378.03,214.35) --
-	(379.36,214.79) --
-	(379.36,214.79) --
-	(380.09,215.03) --
-	(380.12,215.04) --
-	(381.03,215.35) --
-	(381.47,215.49) --
-	(381.75,215.58) --
-	(382.36,215.79) --
-	(382.44,215.82) --
-	(382.57,215.86) --
-	(383.02,216.01) --
-	(385.04,216.68) --
-	(385.16,216.72) --
-	(388.87,217.95) --
-	(393.56,219.51) --
-	(395.71,220.22) --
-	(403.26,222.73) --
-	(404.02,222.98);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,105.13) --
+	( 61.01,108.04) --
+	( 65.48,109.65) --
+	( 65.62,109.70) --
+	( 79.64,114.78) --
+	( 88.50,117.99) --
+	( 94.41,120.13) --
+	( 97.84,121.37) --
+	(104.50,123.78) --
+	(110.01,125.77) --
+	(113.94,127.20) --
+	(116.56,128.15) --
+	(124.94,131.18) --
+	(160.01,143.88) --
+	(160.15,143.93) --
+	(163.56,145.16) --
+	(164.50,145.50) --
+	(175.08,149.33) --
+	(177.68,150.27) --
+	(185.12,152.97) --
+	(195.04,156.56) --
+	(195.05,156.56) --
+	(199.79,158.28) --
+	(200.09,158.39) --
+	(201.70,158.97) --
+	(202.42,159.23) --
+	(203.15,159.49) --
+	(203.24,159.53) --
+	(203.92,159.77) --
+	(204.08,159.83) --
+	(205.70,160.42) --
+	(211.30,162.45) --
+	(213.02,163.07) --
+	(213.22,163.14) --
+	(213.28,163.16) --
+	(214.88,163.74) --
+	(219.39,165.37) --
+	(219.87,165.55) --
+	(224.51,167.23) --
+	(226.38,167.90) --
+	(226.89,168.09) --
+	(228.22,168.57) --
+	(229.80,169.14) --
+	(230.53,169.41) --
+	(231.54,169.77) --
+	(232.29,170.04) --
+	(232.55,170.14) --
+	(232.60,170.16) --
+	(233.03,170.31) --
+	(236.50,171.57) --
+	(238.44,172.27) --
+	(239.50,172.65) --
+	(240.76,173.11) --
+	(242.87,173.87) --
+	(243.82,174.22) --
+	(244.87,174.60) --
+	(245.90,174.97) --
+	(247.14,175.42) --
+	(247.15,175.43) --
+	(248.00,175.73) --
+	(248.59,175.94) --
+	(249.15,176.15) --
+	(249.91,176.42) --
+	(250.14,176.51) --
+	(250.71,176.71) --
+	(251.21,176.89) --
+	(251.61,177.04) --
+	(251.88,177.14) --
+	(252.52,177.37) --
+	(252.98,177.54) --
+	(253.12,177.58) --
+	(253.36,177.67) --
+	(254.91,178.23) --
+	(255.02,178.27) --
+	(256.32,178.74) --
+	(258.61,179.57) --
+	(260.03,180.09) --
+	(260.14,180.13) --
+	(260.80,180.37) --
+	(261.97,180.79) --
+	(262.19,180.87) --
+	(262.47,180.97) --
+	(262.99,181.16) --
+	(264.29,181.63) --
+	(264.50,181.70) --
+	(264.53,181.72) --
+	(264.97,181.88) --
+	(266.10,182.28) --
+	(266.13,182.29) --
+	(266.44,182.41) --
+	(267.28,182.71) --
+	(267.71,182.87) --
+	(268.38,183.11) --
+	(269.11,183.37) --
+	(269.74,183.60) --
+	(269.87,183.65) --
+	(271.02,184.07) --
+	(271.10,184.09) --
+	(271.68,184.30) --
+	(272.40,184.56) --
+	(272.79,184.71) --
+	(273.63,185.01) --
+	(274.52,185.33) --
+	(275.28,185.61) --
+	(275.59,185.72) --
+	(276.13,185.92) --
+	(276.31,185.98) --
+	(276.77,186.15) --
+	(277.30,186.34) --
+	(277.98,186.59) --
+	(278.04,186.61) --
+	(278.45,186.76) --
+	(279.17,187.02) --
+	(279.30,187.06) --
+	(279.52,187.14) --
+	(279.66,187.19) --
+	(279.69,187.20) --
+	(280.15,187.37) --
+	(280.53,187.51) --
+	(280.72,187.58) --
+	(281.20,187.75) --
+	(281.36,187.81) --
+	(281.45,187.84) --
+	(282.80,188.33) --
+	(283.05,188.42) --
+	(283.89,188.73) --
+	(283.98,188.76) --
+	(284.07,188.79) --
+	(284.62,188.99) --
+	(284.86,189.08) --
+	(285.03,189.14) --
+	(285.13,189.17) --
+	(286.00,189.49) --
+	(286.57,189.69) --
+	(286.59,189.70) --
+	(287.25,189.94) --
+	(287.81,190.14) --
+	(288.54,190.41) --
+	(288.59,190.43) --
+	(289.22,190.65) --
+	(289.76,190.85) --
+	(290.76,191.21) --
+	(290.86,191.25) --
+	(291.20,191.37) --
+	(291.32,191.41) --
+	(291.81,191.59) --
+	(291.88,191.62) --
+	(292.21,191.74) --
+	(292.36,191.79) --
+	(292.42,191.81) --
+	(292.49,191.84) --
+	(292.51,191.85) --
+	(292.62,191.89) --
+	(293.21,192.10) --
+	(293.91,192.35) --
+	(295.25,192.84) --
+	(295.45,192.91) --
+	(295.51,192.93) --
+	(295.93,193.08) --
+	(295.99,193.10) --
+	(296.10,193.14) --
+	(296.47,193.28) --
+	(296.65,193.34) --
+	(296.99,193.47) --
+	(297.01,193.47) --
+	(297.04,193.49) --
+	(297.05,193.49) --
+	(297.09,193.50) --
+	(297.13,193.52) --
+	(297.22,193.55) --
+	(297.31,193.58) --
+	(297.31,193.58) --
+	(297.71,193.73) --
+	(297.96,193.82) --
+	(298.34,193.96) --
+	(298.57,194.04) --
+	(299.04,194.21) --
+	(300.58,194.77) --
+	(300.69,194.81) --
+	(301.32,195.03) --
+	(302.10,195.32) --
+	(302.23,195.36) --
+	(302.50,195.46) --
+	(302.82,195.58) --
+	(302.98,195.63) --
+	(303.49,195.82) --
+	(303.87,195.96) --
+	(304.04,196.02) --
+	(304.05,196.02) --
+	(304.17,196.07) --
+	(304.21,196.08) --
+	(304.88,196.32) --
+	(305.44,196.53) --
+	(305.52,196.56) --
+	(305.61,196.59) --
+	(305.86,196.68) --
+	(306.19,196.80) --
+	(306.32,196.84) --
+	(307.91,197.42) --
+	(307.96,197.44) --
+	(308.47,197.62) --
+	(308.57,197.66) --
+	(309.22,197.89) --
+	(309.44,197.97) --
+	(309.51,198.00) --
+	(309.67,198.06) --
+	(310.00,198.18) --
+	(310.25,198.27) --
+	(310.76,198.45) --
+	(310.92,198.51) --
+	(311.04,198.55) --
+	(311.16,198.60) --
+	(311.41,198.69) --
+	(311.41,198.69) --
+	(311.44,198.70) --
+	(311.54,198.73) --
+	(311.68,198.78) --
+	(311.68,198.79) --
+	(311.88,198.86) --
+	(312.22,198.98) --
+	(312.92,199.23) --
+	(313.12,199.31) --
+	(313.27,199.36) --
+	(313.53,199.46) --
+	(313.83,199.56) --
+	(314.24,199.71) --
+	(314.31,199.74) --
+	(314.45,199.79) --
+	(314.63,199.85) --
+	(315.00,199.99) --
+	(315.21,200.06) --
+	(315.23,200.07) --
+	(315.37,200.12) --
+	(315.48,200.16) --
+	(315.51,200.17) --
+	(315.62,200.21) --
+	(315.70,200.24) --
+	(315.79,200.27) --
+	(316.13,200.40) --
+	(316.22,200.43) --
+	(316.38,200.49) --
+	(316.61,200.57) --
+	(316.93,200.69) --
+	(317.07,200.74) --
+	(317.20,200.78) --
+	(317.36,200.84) --
+	(317.75,200.98) --
+	(317.76,200.99) --
+	(317.79,201.00) --
+	(317.86,201.02) --
+	(317.89,201.03) --
+	(317.98,201.06) --
+	(318.43,201.23) --
+	(318.60,201.29) --
+	(318.85,201.38) --
+	(319.11,201.48) --
+	(319.21,201.51) --
+	(319.52,201.62) --
+	(319.81,201.73) --
+	(320.44,201.96) --
+	(321.85,202.47) --
+	(321.91,202.49) --
+	(322.04,202.54) --
+	(322.30,202.63) --
+	(322.60,202.74) --
+	(322.75,202.79) --
+	(323.02,202.89) --
+	(323.10,202.92) --
+	(323.28,202.99) --
+	(324.05,203.26) --
+	(324.42,203.40) --
+	(324.61,203.47) --
+	(324.72,203.51) --
+	(325.08,203.64) --
+	(325.99,203.97) --
+	(326.58,204.18) --
+	(326.72,204.23) --
+	(327.61,204.55) --
+	(327.91,204.66) --
+	(328.67,204.94) --
+	(328.94,205.03) --
+	(329.07,205.08) --
+	(329.52,205.25) --
+	(331.17,205.84) --
+	(332.00,206.14) --
+	(332.27,206.24) --
+	(333.07,206.53) --
+	(333.19,206.57) --
+	(333.76,206.78) --
+	(335.51,207.41) --
+	(336.07,207.61) --
+	(336.75,207.86) --
+	(336.88,207.91) --
+	(337.54,208.15) --
+	(337.92,208.29) --
+	(338.29,208.42) --
+	(338.32,208.43) --
+	(338.37,208.45) --
+	(338.79,208.60) --
+	(338.87,208.63) --
+	(339.41,208.82) --
+	(339.54,208.87) --
+	(340.26,209.13) --
+	(340.28,209.14) --
+	(340.36,209.17) --
+	(340.58,209.25) --
+	(340.90,209.36) --
+	(341.07,209.43) --
+	(341.38,209.54) --
+	(341.48,209.58) --
+	(341.53,209.59) --
+	(341.57,209.61) --
+	(342.00,209.76) --
+	(342.06,209.78) --
+	(342.60,209.98) --
+	(342.92,210.09) --
+	(344.39,210.63) --
+	(344.81,210.78) --
+	(345.03,210.86) --
+	(345.51,211.03) --
+	(345.56,211.05) --
+	(346.27,211.31) --
+	(348.09,211.97) --
+	(348.19,212.00) --
+	(348.32,212.05) --
+	(348.52,212.12) --
+	(348.65,212.17) --
+	(350.04,212.67) --
+	(350.29,212.76) --
+	(350.39,212.80) --
+	(351.49,213.20) --
+	(354.19,214.18) --
+	(354.41,214.26) --
+	(354.96,214.45) --
+	(354.99,214.46) --
+	(355.28,214.57) --
+	(355.84,214.77) --
+	(356.71,215.09) --
+	(356.75,215.10) --
+	(357.50,215.37) --
+	(357.53,215.38) --
+	(358.04,215.57) --
+	(358.62,215.78) --
+	(359.31,216.03) --
+	(359.62,216.14) --
+	(359.75,216.19) --
+	(359.85,216.23) --
+	(360.61,216.50) --
+	(360.64,216.51) --
+	(360.71,216.54) --
+	(361.91,216.97) --
+	(362.60,217.22) --
+	(364.24,217.81) --
+	(364.46,217.89) --
+	(365.70,218.34) --
+	(366.29,218.56) --
+	(370.53,220.09) --
+	(371.02,220.27) --
+	(372.06,220.65) --
+	(372.07,220.65) --
+	(372.38,220.76) --
+	(372.60,220.84) --
+	(372.90,220.95) --
+	(373.16,221.04) --
+	(373.53,221.18) --
+	(373.80,221.27) --
+	(374.46,221.51) --
+	(374.81,221.64) --
+	(375.77,221.99) --
+	(376.36,222.20) --
+	(376.51,222.26) --
+	(376.93,222.41) --
+	(378.03,222.80) --
+	(379.36,223.29) --
+	(379.36,223.29) --
+	(380.09,223.55) --
+	(380.12,223.56) --
+	(381.03,223.89) --
+	(381.47,224.05) --
+	(381.75,224.15) --
+	(382.36,224.37) --
+	(382.44,224.40) --
+	(382.57,224.45) --
+	(383.02,224.61) --
+	(385.04,225.34) --
+	(385.16,225.39) --
+	(388.87,226.73) --
+	(393.56,228.43) --
+	(395.71,229.21) --
+	(403.26,231.94) --
+	(404.02,232.22);
 \definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}
 
-\path[fill=fillColor,fill opacity=0.30] ( 52.97,167.36) --
-	( 61.01,168.41) --
-	( 65.48,168.80) --
-	( 65.62,168.81) --
-	( 79.64,170.79) --
-	( 88.50,171.79) --
-	( 94.41,172.49) --
-	( 97.84,173.06) --
-	(104.50,173.98) --
-	(110.01,174.56) --
-	(113.94,175.03) --
-	(116.56,175.36) --
-	(124.94,176.30) --
-	(160.01,181.27) --
-	(160.15,181.30) --
-	(163.56,181.70) --
-	(164.50,181.78) --
-	(175.08,183.35) --
-	(177.68,183.86) --
-	(185.12,185.40) --
-	(195.04,187.30) --
-	(195.05,187.30) --
-	(199.79,188.52) --
-	(200.09,188.60) --
-	(201.70,188.94) --
-	(202.42,189.05) --
-	(203.15,189.18) --
-	(203.24,189.19) --
-	(203.92,189.29) --
-	(204.08,189.32) --
-	(205.70,189.71) --
-	(211.30,190.89) --
-	(213.02,191.21) --
-	(213.22,191.26) --
-	(213.28,191.27) --
-	(214.88,191.68) --
-	(219.39,192.70) --
-	(219.87,192.77) --
-	(224.51,193.76) --
-	(226.38,194.26) --
-	(226.89,194.38) --
-	(228.22,194.75) --
-	(229.80,195.15) --
-	(230.53,195.25) --
-	(231.54,195.47) --
-	(232.29,195.59) --
-	(232.55,195.66) --
-	(232.60,195.67) --
-	(233.03,195.77) --
-	(236.50,196.61) --
-	(238.44,197.03) --
-	(239.50,197.27) --
-	(240.76,197.54) --
-	(242.87,198.03) --
-	(243.82,198.26) --
-	(244.87,198.51) --
-	(245.90,198.81) --
-	(247.14,199.15) --
-	(247.15,199.15) --
-	(248.00,199.39) --
-	(248.59,199.55) --
-	(249.15,199.72) --
-	(249.91,199.94) --
-	(250.14,200.00) --
-	(250.71,200.16) --
-	(251.21,200.29) --
-	(251.61,200.40) --
-	(251.88,200.46) --
-	(252.52,200.69) --
-	(252.98,200.84) --
-	(253.12,200.86) --
-	(253.36,200.89) --
-	(254.91,201.29) --
-	(255.02,201.32) --
-	(256.32,201.72) --
-	(258.61,202.38) --
-	(260.03,202.80) --
-	(260.14,202.84) --
-	(260.80,203.04) --
-	(261.97,203.27) --
-	(262.19,203.35) --
-	(262.48,203.44) --
-	(262.99,203.62) --
-	(264.29,204.03) --
-	(264.50,204.10) --
-	(264.53,204.11) --
-	(264.97,204.25) --
-	(266.10,204.54) --
-	(266.13,204.55) --
-	(266.44,204.61) --
-	(267.28,204.93) --
-	(267.71,205.05) --
-	(268.38,205.26) --
-	(269.11,205.45) --
-	(269.74,205.69) --
-	(269.87,205.74) --
-	(271.02,206.18) --
-	(271.10,206.22) --
-	(271.68,206.47) --
-	(272.40,206.66) --
-	(272.79,206.78) --
-	(273.63,207.07) --
-	(274.52,207.40) --
-	(275.28,207.68) --
-	(275.59,207.78) --
-	(276.13,207.95) --
-	(276.31,207.99) --
-	(276.77,208.14) --
-	(277.30,208.37) --
-	(277.98,208.66) --
-	(278.04,208.68) --
-	(278.45,208.79) --
-	(279.17,208.98) --
-	(279.30,209.02) --
-	(279.52,209.08) --
-	(279.66,209.14) --
-	(279.69,209.14) --
-	(280.15,209.31) --
-	(280.53,209.48) --
-	(280.72,209.56) --
-	(281.20,209.75) --
-	(281.36,209.82) --
-	(281.45,209.85) --
-	(282.80,210.34) --
-	(283.05,210.37) --
-	(283.89,210.70) --
-	(283.98,210.74) --
-	(284.07,210.78) --
-	(284.62,210.98) --
-	(284.86,211.08) --
-	(285.03,211.13) --
-	(285.13,211.16) --
-	(286.00,211.42) --
-	(286.57,211.61) --
-	(286.59,211.61) --
-	(287.25,211.79) --
-	(287.81,211.98) --
-	(288.54,212.28) --
-	(288.59,212.29) --
-	(289.22,212.44) --
-	(289.76,212.64) --
-	(290.76,213.08) --
-	(290.86,213.13) --
-	(291.20,213.21) --
-	(291.32,213.21) --
-	(291.81,213.42) --
-	(291.88,213.46) --
-	(292.21,213.58) --
-	(292.36,213.65) --
-	(292.42,213.69) --
-	(292.49,213.72) --
-	(292.51,213.74) --
-	(292.62,213.79) --
-	(293.21,213.98) --
-	(293.91,214.28) --
-	(295.25,214.70) --
-	(295.45,214.78) --
-	(295.51,214.81) --
-	(295.93,215.00) --
-	(295.99,215.02) --
-	(296.10,215.06) --
-	(296.47,215.21) --
-	(296.65,215.26) --
-	(296.99,215.30) --
-	(297.01,215.30) --
-	(297.04,215.31) --
-	(297.05,215.31) --
-	(297.09,215.32) --
-	(297.13,215.34) --
-	(297.22,215.39) --
-	(297.31,215.44) --
-	(297.31,215.44) --
-	(297.71,215.55) --
-	(297.96,215.64) --
-	(298.34,215.77) --
-	(298.57,215.86) --
-	(299.04,216.04) --
-	(300.58,216.50) --
-	(300.69,216.54) --
-	(301.32,216.72) --
-	(302.10,216.99) --
-	(302.23,217.04) --
-	(302.50,217.16) --
-	(302.82,217.32) --
-	(302.98,217.40) --
-	(303.49,217.63) --
-	(303.87,217.81) --
-	(304.04,217.89) --
-	(304.05,217.89) --
-	(304.17,217.95) --
-	(304.21,217.97) --
-	(304.88,218.27) --
-	(305.44,218.51) --
-	(305.52,218.55) --
-	(305.61,218.58) --
-	(305.86,218.68) --
-	(306.19,218.81) --
-	(306.32,218.86) --
-	(307.91,219.57) --
-	(307.96,219.60) --
-	(308.47,219.81) --
-	(308.57,219.85) --
-	(309.22,220.10) --
-	(309.44,220.18) --
-	(309.51,220.20) --
-	(309.67,220.25) --
-	(310.00,220.39) --
-	(310.25,220.47) --
-	(310.76,220.68) --
-	(310.92,220.74) --
-	(311.04,220.77) --
-	(311.16,220.82) --
-	(311.41,220.90) --
-	(311.41,220.90) --
-	(311.44,220.91) --
-	(311.54,220.94) --
-	(311.68,220.98) --
-	(311.68,220.99) --
-	(311.88,221.05) --
-	(312.22,221.19) --
-	(312.92,221.49) --
-	(313.12,221.57) --
-	(313.27,221.65) --
-	(313.53,221.73) --
-	(313.83,221.83) --
-	(314.24,222.00) --
-	(314.31,222.04) --
-	(314.45,222.11) --
-	(314.63,222.16) --
-	(315.00,222.37) --
-	(315.21,222.46) --
-	(315.23,222.47) --
-	(315.37,222.52) --
-	(315.48,222.56) --
-	(315.51,222.58) --
-	(315.62,222.62) --
-	(315.70,222.64) --
-	(315.79,222.66) --
-	(316.13,222.81) --
-	(316.22,222.83) --
-	(316.38,222.87) --
-	(316.61,222.95) --
-	(316.93,223.12) --
-	(317.07,223.18) --
-	(317.20,223.26) --
-	(317.36,223.33) --
-	(317.75,223.47) --
-	(317.76,223.47) --
-	(317.79,223.49) --
-	(317.86,223.53) --
-	(317.89,223.54) --
-	(317.98,223.58) --
-	(318.43,223.78) --
-	(318.60,223.85) --
-	(318.85,224.00) --
-	(319.11,224.09) --
-	(319.21,224.11) --
-	(319.52,224.25) --
-	(319.81,224.40) --
-	(320.44,224.64) --
-	(321.85,225.23) --
-	(321.91,225.27) --
-	(322.04,225.35) --
-	(322.30,225.47) --
-	(322.60,225.60) --
-	(322.75,225.66) --
-	(323.02,225.77) --
-	(323.10,225.80) --
-	(323.28,225.87) --
-	(324.05,226.17) --
-	(324.42,226.34) --
-	(324.61,226.43) --
-	(324.72,226.50) --
-	(325.08,226.65) --
-	(325.99,227.12) --
-	(326.58,227.38) --
-	(326.72,227.44) --
-	(327.61,227.83) --
-	(327.91,227.96) --
-	(328.67,228.25) --
-	(328.94,228.38) --
-	(329.07,228.46) --
-	(329.52,228.70) --
-	(331.17,229.50) --
-	(332.00,229.87) --
-	(332.27,230.00) --
-	(333.07,230.25) --
-	(333.19,230.29) --
-	(333.76,230.52) --
-	(335.51,231.36) --
-	(336.07,231.68) --
-	(336.75,232.03) --
-	(336.88,232.07) --
-	(337.54,232.34) --
-	(337.92,232.47) --
-	(338.29,232.66) --
-	(338.32,232.68) --
-	(338.37,232.70) --
-	(338.79,232.94) --
-	(338.87,232.97) --
-	(339.41,233.19) --
-	(339.54,233.26) --
-	(340.26,233.63) --
-	(340.28,233.64) --
-	(340.36,233.69) --
-	(340.58,233.82) --
-	(340.90,234.00) --
-	(341.07,234.09) --
-	(341.38,234.25) --
-	(341.48,234.29) --
-	(341.53,234.32) --
-	(341.57,234.33) --
-	(342.00,234.53) --
-	(342.06,234.56) --
-	(342.60,234.82) --
-	(342.92,234.94) --
-	(344.39,235.59) --
-	(344.81,235.76) --
-	(345.03,235.85) --
-	(345.51,236.00) --
-	(345.56,236.01) --
-	(346.27,236.21) --
-	(348.09,237.11) --
-	(348.19,237.16) --
-	(348.32,237.23) --
-	(348.52,237.32) --
-	(348.65,237.36) --
-	(350.04,238.11) --
-	(350.29,238.22) --
-	(350.39,238.27) --
-	(351.49,238.86) --
-	(354.19,240.24) --
-	(354.41,240.37) --
-	(354.96,240.65) --
-	(354.99,240.67) --
-	(355.28,240.79) --
-	(355.84,241.02) --
-	(356.71,241.48) --
-	(356.75,241.51) --
-	(357.50,241.86) --
-	(357.53,241.87) --
-	(358.04,242.13) --
-	(358.62,242.42) --
-	(359.31,242.81) --
-	(359.62,242.94) --
-	(359.75,243.03) --
-	(359.85,243.09) --
-	(360.61,243.54) --
-	(360.64,243.55) --
-	(360.71,243.59) --
-	(361.91,244.20) --
-	(362.60,244.50) --
-	(364.24,245.24) --
-	(364.46,245.35) --
-	(365.70,245.99) --
-	(366.29,246.26) --
-	(370.53,248.44) --
-	(371.02,248.71) --
-	(372.06,249.22) --
-	(372.07,249.22) --
-	(372.38,249.33) --
-	(372.60,249.45) --
-	(372.90,249.61) --
-	(373.16,249.73) --
-	(373.53,249.89) --
-	(373.80,250.04) --
-	(374.46,250.35) --
-	(374.81,250.52) --
-	(375.77,251.03) --
-	(376.36,251.34) --
-	(376.51,251.43) --
-	(376.93,251.64) --
-	(378.03,252.22) --
-	(379.36,252.85) --
-	(379.36,252.86) --
-	(380.09,253.22) --
-	(380.12,253.24) --
-	(381.03,253.71) --
-	(381.47,253.91) --
-	(381.75,254.05) --
-	(382.36,254.37) --
-	(382.44,254.41) --
-	(382.57,254.46) --
-	(383.02,254.69) --
-	(385.04,255.76) --
-	(385.16,255.82) --
-	(388.87,257.82) --
-	(393.56,260.29) --
-	(395.71,261.42) --
-	(403.26,265.59) --
+\path[fill=fillColor,fill opacity=0.30] ( 52.97,166.87) --
+	( 61.01,168.28) --
+	( 65.48,168.86) --
+	( 65.62,168.88) --
+	( 79.64,170.96) --
+	( 88.50,172.39) --
+	( 94.41,173.16) --
+	( 97.84,173.62) --
+	(104.50,174.54) --
+	(110.01,175.23) --
+	(113.94,175.72) --
+	(116.56,176.32) --
+	(124.94,177.43) --
+	(160.01,182.90) --
+	(160.15,182.92) --
+	(163.56,183.58) --
+	(164.50,183.75) --
+	(175.08,185.58) --
+	(177.68,186.03) --
+	(185.12,187.31) --
+	(195.04,188.98) --
+	(195.05,188.98) --
+	(199.79,189.84) --
+	(200.09,189.94) --
+	(201.70,190.33) --
+	(202.42,190.48) --
+	(203.15,190.65) --
+	(203.24,190.66) --
+	(203.92,190.82) --
+	(204.08,190.85) --
+	(205.70,191.15) --
+	(211.30,192.32) --
+	(213.02,192.64) --
+	(213.22,192.68) --
+	(213.28,192.70) --
+	(214.88,193.02) --
+	(219.39,194.06) --
+	(219.87,194.20) --
+	(224.51,195.24) --
+	(226.38,195.65) --
+	(226.89,195.79) --
+	(228.22,196.10) --
+	(229.80,196.48) --
+	(230.53,196.69) --
+	(231.54,196.92) --
+	(232.29,197.08) --
+	(232.55,197.15) --
+	(232.60,197.16) --
+	(233.03,197.26) --
+	(236.50,198.18) --
+	(238.44,198.69) --
+	(239.50,198.96) --
+	(240.76,199.23) --
+	(242.87,199.83) --
+	(243.82,200.10) --
+	(244.87,200.43) --
+	(245.90,200.74) --
+	(247.14,201.06) --
+	(247.15,201.07) --
+	(248.00,201.30) --
+	(248.59,201.43) --
+	(249.15,201.55) --
+	(249.91,201.77) --
+	(250.14,201.82) --
+	(250.71,201.96) --
+	(251.21,202.07) --
+	(251.61,202.15) --
+	(251.88,202.21) --
+	(252.52,202.37) --
+	(252.98,202.49) --
+	(253.12,202.52) --
+	(253.36,202.58) --
+	(254.91,202.96) --
+	(255.02,202.98) --
+	(256.32,203.27) --
+	(258.61,203.82) --
+	(260.03,204.14) --
+	(260.14,204.17) --
+	(260.80,204.35) --
+	(261.97,204.65) --
+	(262.19,204.76) --
+	(262.47,204.86) --
+	(262.99,205.01) --
+	(264.29,205.28) --
+	(264.50,205.34) --
+	(264.53,205.35) --
+	(264.97,205.48) --
+	(266.10,205.84) --
+	(266.13,205.85) --
+	(266.44,205.95) --
+	(267.28,206.24) --
+	(267.71,206.41) --
+	(268.38,206.62) --
+	(269.11,206.90) --
+	(269.74,207.05) --
+	(269.87,207.08) --
+	(271.02,207.45) --
+	(271.10,207.48) --
+	(271.68,207.67) --
+	(272.40,207.84) --
+	(272.79,207.97) --
+	(273.63,208.21) --
+	(274.52,208.52) --
+	(275.28,208.71) --
+	(275.59,208.84) --
+	(276.13,209.05) --
+	(276.31,209.10) --
+	(276.77,209.23) --
+	(277.30,209.42) --
+	(277.98,209.63) --
+	(278.04,209.66) --
+	(278.45,209.79) --
+	(279.17,210.00) --
+	(279.30,210.03) --
+	(279.52,210.12) --
+	(279.66,210.17) --
+	(279.69,210.17) --
+	(280.15,210.36) --
+	(280.53,210.49) --
+	(280.72,210.53) --
+	(281.20,210.70) --
+	(281.36,210.76) --
+	(281.45,210.80) --
+	(282.80,211.27) --
+	(283.05,211.35) --
+	(283.89,211.61) --
+	(283.98,211.65) --
+	(284.07,211.68) --
+	(284.62,211.85) --
+	(284.86,211.90) --
+	(285.03,211.93) --
+	(285.13,211.96) --
+	(286.00,212.24) --
+	(286.57,212.41) --
+	(286.59,212.42) --
+	(287.25,212.62) --
+	(287.81,212.79) --
+	(288.54,213.02) --
+	(288.59,213.02) --
+	(289.22,213.26) --
+	(289.76,213.50) --
+	(290.76,213.87) --
+	(290.86,213.92) --
+	(291.20,214.07) --
+	(291.32,214.11) --
+	(291.81,214.26) --
+	(291.88,214.29) --
+	(292.21,214.39) --
+	(292.36,214.45) --
+	(292.42,214.48) --
+	(292.49,214.51) --
+	(292.51,214.52) --
+	(292.62,214.56) --
+	(293.21,214.80) --
+	(293.91,215.07) --
+	(295.25,215.52) --
+	(295.45,215.58) --
+	(295.51,215.61) --
+	(295.93,215.78) --
+	(295.99,215.79) --
+	(296.10,215.81) --
+	(296.47,215.93) --
+	(296.65,215.99) --
+	(296.99,216.12) --
+	(297.01,216.13) --
+	(297.04,216.14) --
+	(297.05,216.14) --
+	(297.09,216.16) --
+	(297.13,216.17) --
+	(297.22,216.21) --
+	(297.31,216.24) --
+	(297.31,216.24) --
+	(297.71,216.36) --
+	(297.96,216.42) --
+	(298.34,216.59) --
+	(298.57,216.66) --
+	(299.04,216.81) --
+	(300.58,217.39) --
+	(300.69,217.46) --
+	(301.32,217.75) --
+	(302.10,218.06) --
+	(302.23,218.10) --
+	(302.50,218.21) --
+	(302.82,218.31) --
+	(302.98,218.37) --
+	(303.49,218.57) --
+	(303.87,218.74) --
+	(304.04,218.82) --
+	(304.05,218.82) --
+	(304.17,218.88) --
+	(304.21,218.90) --
+	(304.88,219.13) --
+	(305.44,219.34) --
+	(305.52,219.36) --
+	(305.61,219.38) --
+	(305.86,219.46) --
+	(306.19,219.59) --
+	(306.32,219.64) --
+	(307.91,220.31) --
+	(307.96,220.32) --
+	(308.47,220.51) --
+	(308.57,220.55) --
+	(309.22,220.85) --
+	(309.44,220.94) --
+	(309.51,220.98) --
+	(309.67,221.05) --
+	(310.00,221.16) --
+	(310.25,221.23) --
+	(310.76,221.38) --
+	(310.92,221.43) --
+	(311.04,221.47) --
+	(311.16,221.52) --
+	(311.41,221.65) --
+	(311.41,221.65) --
+	(311.44,221.67) --
+	(311.54,221.72) --
+	(311.68,221.77) --
+	(311.68,221.77) --
+	(311.88,221.85) --
+	(312.22,222.04) --
+	(312.92,222.24) --
+	(313.12,222.33) --
+	(313.27,222.38) --
+	(313.53,222.47) --
+	(313.83,222.60) --
+	(314.24,222.78) --
+	(314.31,222.81) --
+	(314.45,222.86) --
+	(314.63,222.94) --
+	(315.00,223.12) --
+	(315.21,223.21) --
+	(315.23,223.22) --
+	(315.37,223.28) --
+	(315.48,223.34) --
+	(315.51,223.35) --
+	(315.62,223.40) --
+	(315.70,223.43) --
+	(315.79,223.47) --
+	(316.13,223.61) --
+	(316.22,223.64) --
+	(316.38,223.71) --
+	(316.61,223.81) --
+	(316.93,223.93) --
+	(317.07,223.98) --
+	(317.20,224.06) --
+	(317.36,224.13) --
+	(317.75,224.29) --
+	(317.76,224.29) --
+	(317.79,224.31) --
+	(317.86,224.33) --
+	(317.89,224.35) --
+	(317.98,224.38) --
+	(318.43,224.57) --
+	(318.60,224.65) --
+	(318.85,224.72) --
+	(319.11,224.84) --
+	(319.21,224.90) --
+	(319.52,225.04) --
+	(319.81,225.16) --
+	(320.44,225.41) --
+	(321.85,225.97) --
+	(321.91,226.01) --
+	(322.04,226.09) --
+	(322.30,226.20) --
+	(322.60,226.31) --
+	(322.75,226.40) --
+	(323.02,226.52) --
+	(323.10,226.55) --
+	(323.28,226.63) --
+	(324.05,226.98) --
+	(324.42,227.13) --
+	(324.61,227.20) --
+	(324.72,227.26) --
+	(325.08,227.46) --
+	(325.99,227.89) --
+	(326.58,228.15) --
+	(326.72,228.21) --
+	(327.61,228.57) --
+	(327.91,228.70) --
+	(328.67,229.06) --
+	(328.94,229.15) --
+	(329.07,229.20) --
+	(329.52,229.37) --
+	(331.17,230.08) --
+	(332.00,230.42) --
+	(332.27,230.55) --
+	(333.07,230.92) --
+	(333.19,230.97) --
+	(333.76,231.23) --
+	(335.51,232.06) --
+	(336.07,232.29) --
+	(336.75,232.63) --
+	(336.88,232.68) --
+	(337.54,232.98) --
+	(337.92,233.08) --
+	(338.29,233.22) --
+	(338.32,233.24) --
+	(338.37,233.26) --
+	(338.79,233.42) --
+	(338.87,233.45) --
+	(339.41,233.70) --
+	(339.54,233.76) --
+	(340.26,234.08) --
+	(340.28,234.09) --
+	(340.36,234.13) --
+	(340.58,234.23) --
+	(340.90,234.37) --
+	(341.07,234.45) --
+	(341.38,234.61) --
+	(341.48,234.68) --
+	(341.53,234.70) --
+	(341.57,234.71) --
+	(342.00,234.88) --
+	(342.06,234.91) --
+	(342.60,235.16) --
+	(342.92,235.29) --
+	(344.39,235.95) --
+	(344.81,236.19) --
+	(345.03,236.27) --
+	(345.51,236.50) --
+	(345.56,236.52) --
+	(346.27,236.90) --
+	(348.09,237.83) --
+	(348.19,237.89) --
+	(348.32,237.96) --
+	(348.52,238.06) --
+	(348.65,238.13) --
+	(350.04,238.80) --
+	(350.29,238.94) --
+	(350.39,238.99) --
+	(351.49,239.54) --
+	(354.19,240.78) --
+	(354.41,240.86) --
+	(354.96,241.07) --
+	(354.99,241.08) --
+	(355.28,241.21) --
+	(355.84,241.45) --
+	(356.71,241.88) --
+	(356.75,241.90) --
+	(357.50,242.25) --
+	(357.53,242.26) --
+	(358.04,242.52) --
+	(358.62,242.81) --
+	(359.31,243.15) --
+	(359.62,243.28) --
+	(359.75,243.36) --
+	(359.85,243.42) --
+	(360.61,243.76) --
+	(360.64,243.77) --
+	(360.71,243.80) --
+	(361.91,244.37) --
+	(362.60,244.70) --
+	(364.24,245.45) --
+	(364.46,245.55) --
+	(365.70,246.13) --
+	(366.29,246.37) --
+	(370.53,248.50) --
+	(371.02,248.75) --
+	(372.06,249.29) --
+	(372.07,249.30) --
+	(372.38,249.46) --
+	(372.60,249.57) --
+	(372.90,249.73) --
+	(373.16,249.86) --
+	(373.53,250.03) --
+	(373.80,250.17) --
+	(374.46,250.54) --
+	(374.81,250.70) --
+	(375.77,251.22) --
+	(376.36,251.54) --
+	(376.51,251.61) --
+	(376.93,251.81) --
+	(378.03,252.38) --
+	(379.36,252.99) --
+	(379.36,252.99) --
+	(380.09,253.42) --
+	(380.12,253.44) --
+	(381.03,253.90) --
+	(381.47,254.16) --
+	(381.75,254.27) --
+	(382.36,254.54) --
+	(382.44,254.57) --
+	(382.57,254.62) --
+	(383.02,254.85) --
+	(385.04,255.99) --
+	(385.16,256.08) --
+	(388.87,258.02) --
+	(393.56,260.64) --
+	(395.71,261.65) --
+	(403.26,265.55) --
 	(404.02,265.99) --
-	(404.02,182.27) --
-	(403.26,182.16) --
-	(395.71,180.94) --
-	(393.56,180.61) --
-	(388.87,179.73) --
-	(385.16,179.04) --
-	(385.04,179.03) --
-	(383.02,178.81) --
-	(382.57,178.70) --
-	(382.44,178.65) --
-	(382.36,178.61) --
-	(381.75,178.55) --
-	(381.47,178.49) --
-	(381.03,178.47) --
-	(380.12,178.30) --
-	(380.09,178.30) --
-	(379.36,178.16) --
-	(379.36,178.16) --
-	(378.03,177.94) --
-	(376.93,177.72) --
-	(376.51,177.66) --
-	(376.36,177.65) --
-	(375.77,177.59) --
-	(374.81,177.41) --
-	(374.46,177.37) --
-	(373.80,177.19) --
-	(373.53,177.12) --
-	(373.16,177.03) --
-	(372.90,176.96) --
-	(372.60,176.88) --
-	(372.38,176.82) --
-	(372.07,176.74) --
-	(372.06,176.74) --
-	(371.02,176.61) --
-	(370.53,176.50) --
-	(366.29,175.56) --
-	(365.70,175.48) --
-	(364.46,175.26) --
-	(364.24,175.21) --
-	(362.60,174.88) --
-	(361.91,174.73) --
-	(360.71,174.46) --
-	(360.64,174.43) --
-	(360.61,174.42) --
-	(359.85,174.28) --
-	(359.75,174.26) --
-	(359.62,174.24) --
-	(359.31,174.18) --
-	(358.62,174.10) --
-	(358.04,174.00) --
-	(357.53,173.89) --
-	(357.50,173.88) --
-	(356.75,173.74) --
-	(356.71,173.73) --
-	(355.84,173.55) --
-	(355.28,173.44) --
-	(354.99,173.38) --
-	(354.96,173.38) --
-	(354.41,173.27) --
-	(354.19,173.22) --
-	(351.49,172.56) --
-	(350.39,172.25) --
-	(350.29,172.22) --
-	(350.04,172.22) --
-	(348.65,172.01) --
-	(348.52,171.96) --
-	(348.32,171.89) --
-	(348.19,171.87) --
-	(348.09,171.85) --
-	(346.27,171.41) --
-	(345.56,171.26) --
-	(345.51,171.26) --
-	(345.03,171.14) --
-	(344.81,171.13) --
-	(344.39,171.04) --
-	(342.92,170.73) --
-	(342.60,170.68) --
-	(342.06,170.59) --
-	(342.00,170.58) --
-	(341.57,170.51) --
-	(341.53,170.50) --
-	(341.48,170.48) --
-	(341.38,170.46) --
-	(341.07,170.41) --
-	(340.90,170.35) --
-	(340.58,170.27) --
-	(340.36,170.25) --
-	(340.28,170.24) --
-	(340.26,170.24) --
-	(339.54,170.08) --
-	(339.41,170.03) --
-	(338.87,169.90) --
-	(338.79,169.88) --
-	(338.37,169.75) --
-	(338.32,169.74) --
-	(338.29,169.73) --
-	(337.92,169.66) --
-	(337.54,169.63) --
-	(336.88,169.52) --
-	(336.75,169.49) --
-	(336.07,169.33) --
-	(335.51,169.18) --
-	(333.76,168.91) --
-	(333.19,168.80) --
-	(333.07,168.78) --
-	(332.27,168.47) --
-	(332.00,168.39) --
-	(331.17,168.19) --
-	(329.52,167.74) --
-	(329.07,167.64) --
-	(328.94,167.62) --
-	(328.67,167.52) --
-	(327.91,167.32) --
-	(327.61,167.25) --
-	(326.72,167.12) --
-	(326.58,167.07) --
-	(325.99,166.89) --
-	(325.08,166.68) --
-	(324.72,166.60) --
-	(324.61,166.57) --
-	(324.42,166.53) --
-	(324.05,166.45) --
-	(323.28,166.24) --
-	(323.10,166.20) --
-	(323.02,166.19) --
-	(322.75,166.13) --
-	(322.60,166.08) --
-	(322.30,166.02) --
-	(322.04,165.95) --
-	(321.91,165.91) --
-	(321.85,165.90) --
-	(320.44,165.54) --
-	(319.81,165.48) --
-	(319.52,165.41) --
-	(319.21,165.35) --
-	(319.11,165.31) --
-	(318.85,165.22) --
-	(318.60,165.15) --
-	(318.43,165.12) --
-	(317.98,165.00) --
-	(317.89,164.98) --
-	(317.86,164.98) --
-	(317.79,164.97) --
-	(317.76,164.96) --
-	(317.75,164.96) --
-	(317.36,164.87) --
-	(317.20,164.84) --
-	(317.07,164.81) --
-	(316.93,164.77) --
-	(316.61,164.69) --
-	(316.38,164.64) --
-	(316.22,164.63) --
-	(316.13,164.63) --
-	(315.79,164.58) --
-	(315.70,164.56) --
-	(315.62,164.55) --
-	(315.51,164.53) --
-	(315.48,164.52) --
-	(315.37,164.49) --
-	(315.23,164.45) --
-	(315.21,164.44) --
-	(315.00,164.38) --
-	(314.63,164.28) --
-	(314.45,164.23) --
-	(314.31,164.17) --
-	(314.24,164.15) --
-	(313.83,164.06) --
-	(313.53,163.97) --
-	(313.27,163.89) --
-	(313.12,163.80) --
-	(312.92,163.72) --
-	(312.22,163.58) --
-	(311.88,163.47) --
-	(311.68,163.41) --
-	(311.68,163.41) --
-	(311.54,163.36) --
-	(311.44,163.32) --
-	(311.41,163.32) --
-	(311.41,163.32) --
-	(311.16,163.25) --
-	(311.04,163.22) --
-	(310.92,163.20) --
-	(310.76,163.15) --
-	(310.25,163.05) --
-	(310.00,162.99) --
-	(309.67,162.92) --
-	(309.51,162.86) --
-	(309.44,162.83) --
-	(309.22,162.77) --
-	(308.57,162.62) --
-	(308.47,162.60) --
-	(307.96,162.44) --
-	(307.91,162.43) --
-	(306.32,161.94) --
-	(306.19,161.90) --
-	(305.86,161.80) --
-	(305.61,161.73) --
-	(305.52,161.70) --
-	(305.44,161.68) --
-	(304.88,161.50) --
-	(304.21,161.34) --
-	(304.17,161.33) --
-	(304.05,161.30) --
-	(304.04,161.30) --
-	(303.87,161.27) --
-	(303.49,161.16) --
-	(302.98,161.00) --
-	(302.82,160.95) --
-	(302.50,160.89) --
-	(302.23,160.84) --
-	(302.10,160.82) --
-	(301.32,160.64) --
-	(300.69,160.55) --
-	(300.58,160.54) --
-	(299.04,160.13) --
-	(298.57,160.04) --
-	(298.34,159.99) --
-	(297.96,159.86) --
-	(297.71,159.79) --
-	(297.31,159.71) --
-	(297.31,159.71) --
-	(297.22,159.67) --
-	(297.13,159.62) --
-	(297.09,159.60) --
-	(297.05,159.58) --
-	(297.04,159.58) --
-	(297.01,159.57) --
-	(296.99,159.56) --
-	(296.65,159.45) --
-	(296.47,159.35) --
-	(296.10,159.26) --
-	(295.99,159.24) --
-	(295.93,159.23) --
-	(295.51,159.10) --
-	(295.45,159.08) --
-	(295.25,159.01) --
-	(293.91,158.66) --
-	(293.21,158.46) --
-	(292.62,158.25) --
-	(292.51,158.22) --
-	(292.49,158.21) --
-	(292.42,158.20) --
-	(292.36,158.18) --
-	(292.21,158.15) --
-	(291.88,158.09) --
-	(291.81,158.08) --
-	(291.32,157.93) --
-	(291.20,157.93) --
-	(290.86,157.83) --
-	(290.76,157.78) --
-	(289.76,157.50) --
-	(289.22,157.31) --
-	(288.59,157.10) --
-	(288.54,157.09) --
-	(287.81,156.93) --
-	(287.25,156.69) --
-	(286.59,156.44) --
-	(286.57,156.44) --
-	(286.00,156.29) --
-	(285.13,156.04) --
-	(285.03,156.02) --
-	(284.86,155.95) --
-	(284.62,155.87) --
-	(284.07,155.70) --
-	(283.98,155.67) --
-	(283.89,155.63) --
-	(283.05,155.39) --
-	(282.80,155.29) --
-	(281.45,154.91) --
-	(281.36,154.89) --
-	(281.20,154.85) --
-	(280.72,154.72) --
-	(280.53,154.68) --
-	(280.15,154.56) --
-	(279.69,154.48) --
-	(279.66,154.48) --
-	(279.52,154.44) --
-	(279.30,154.38) --
-	(279.17,154.34) --
-	(278.45,154.06) --
-	(278.04,153.95) --
-	(277.98,153.93) --
-	(277.30,153.70) --
-	(276.77,153.46) --
-	(276.31,153.28) --
-	(276.13,153.22) --
-	(275.59,153.06) --
-	(275.28,152.95) --
-	(274.52,152.77) --
-	(273.63,152.39) --
-	(272.79,152.07) --
-	(272.40,151.94) --
-	(271.68,151.70) --
-	(271.10,151.43) --
-	(271.02,151.41) --
-	(269.87,151.00) --
-	(269.74,150.96) --
-	(269.11,150.78) --
-	(268.38,150.50) --
-	(267.71,150.29) --
-	(267.28,150.15) --
-	(266.44,149.85) --
-	(266.13,149.74) --
-	(266.10,149.73) --
-	(264.97,149.27) --
-	(264.53,149.09) --
-	(264.50,149.08) --
-	(264.29,149.03) --
-	(262.99,148.54) --
-	(262.48,148.27) --
-	(262.19,148.19) --
-	(261.97,148.12) --
-	(260.80,147.75) --
-	(260.14,147.55) --
-	(260.03,147.49) --
-	(258.61,146.90) --
-	(256.32,145.98) --
-	(255.02,145.42) --
-	(254.91,145.38) --
-	(253.36,144.78) --
-	(253.12,144.70) --
-	(252.98,144.64) --
-	(252.52,144.47) --
-	(251.88,144.26) --
-	(251.61,144.16) --
-	(251.21,144.00) --
-	(250.71,143.81) --
-	(250.14,143.57) --
-	(249.91,143.49) --
-	(249.15,143.20) --
-	(248.59,142.98) --
-	(248.00,142.78) --
-	(247.15,142.45) --
-	(247.14,142.44) --
-	(245.90,142.02) --
-	(244.87,141.53) --
-	(243.82,141.15) --
-	(242.87,140.79) --
-	(240.76,139.96) --
-	(239.50,139.44) --
-	(238.44,139.02) --
-	(236.50,138.27) --
-	(233.03,136.65) --
-	(232.60,136.47) --
-	(232.55,136.45) --
-	(232.29,136.34) --
-	(231.54,136.09) --
-	(230.53,135.66) --
-	(229.80,135.35) --
-	(228.22,134.60) --
-	(226.89,134.03) --
-	(226.38,133.85) --
-	(224.51,133.07) --
-	(219.87,130.96) --
-	(219.39,130.73) --
-	(214.88,128.51) --
-	(213.28,127.81) --
-	(213.22,127.78) --
-	(213.02,127.70) --
-	(211.30,126.92) --
-	(205.70,124.51) --
-	(204.08,123.77) --
-	(203.92,123.68) --
-	(203.24,123.35) --
-	(203.15,123.31) --
-	(202.42,123.02) --
-	(201.70,122.67) --
-	(200.09,121.90) --
-	(199.79,121.73) --
-	(195.05,119.42) --
-	(195.04,119.41) --
-	(185.12,114.89) --
-	(177.68,111.26) --
-	(175.08,110.08) --
-	(164.50,104.62) --
-	(163.56,104.15) --
-	(160.15,102.47) --
-	(160.01,102.40) --
-	(124.94, 84.29) --
-	(116.56, 79.63) --
-	(113.94, 78.09) --
-	(110.01, 75.93) --
-	(104.50, 73.31) --
-	( 97.84, 69.48) --
-	( 94.41, 67.75) --
-	( 88.50, 64.75) --
-	( 79.64, 59.82) --
-	( 65.62, 51.87) --
-	( 65.48, 51.79) --
-	( 61.01, 49.34) --
+	(404.02,198.26) --
+	(403.26,198.13) --
+	(395.71,196.50) --
+	(393.56,196.20) --
+	(388.87,195.34) --
+	(385.16,194.57) --
+	(385.04,194.55) --
+	(383.02,194.19) --
+	(382.57,194.09) --
+	(382.44,194.08) --
+	(382.36,194.06) --
+	(381.75,193.95) --
+	(381.47,193.92) --
+	(381.03,193.85) --
+	(380.12,193.63) --
+	(380.09,193.62) --
+	(379.36,193.45) --
+	(379.36,193.45) --
+	(378.03,193.18) --
+	(376.93,192.91) --
+	(376.51,192.76) --
+	(376.36,192.72) --
+	(375.77,192.67) --
+	(374.81,192.43) --
+	(374.46,192.30) --
+	(373.80,192.20) --
+	(373.53,192.21) --
+	(373.16,192.11) --
+	(372.90,192.04) --
+	(372.60,191.95) --
+	(372.38,191.89) --
+	(372.07,191.81) --
+	(372.06,191.81) --
+	(371.02,191.60) --
+	(370.53,191.51) --
+	(366.29,190.47) --
+	(365.70,190.35) --
+	(364.46,190.06) --
+	(364.24,190.02) --
+	(362.60,189.68) --
+	(361.91,189.49) --
+	(360.71,189.17) --
+	(360.64,189.15) --
+	(360.61,189.14) --
+	(359.85,188.94) --
+	(359.75,188.92) --
+	(359.62,188.89) --
+	(359.31,188.83) --
+	(358.62,188.68) --
+	(358.04,188.52) --
+	(357.53,188.44) --
+	(357.50,188.44) --
+	(356.75,188.29) --
+	(356.71,188.28) --
+	(355.84,188.09) --
+	(355.28,187.90) --
+	(354.99,187.80) --
+	(354.96,187.79) --
+	(354.41,187.66) --
+	(354.19,187.62) --
+	(351.49,186.85) --
+	(350.39,186.52) --
+	(350.29,186.52) --
+	(350.04,186.50) --
+	(348.65,186.20) --
+	(348.52,186.16) --
+	(348.32,186.12) --
+	(348.19,186.09) --
+	(348.09,186.08) --
+	(346.27,185.58) --
+	(345.56,185.33) --
+	(345.51,185.32) --
+	(345.03,185.18) --
+	(344.81,185.12) --
+	(344.39,185.06) --
+	(342.92,184.59) --
+	(342.60,184.50) --
+	(342.06,184.34) --
+	(342.00,184.33) --
+	(341.57,184.21) --
+	(341.53,184.20) --
+	(341.48,184.20) --
+	(341.38,184.17) --
+	(341.07,184.06) --
+	(340.90,183.99) --
+	(340.58,183.92) --
+	(340.36,183.84) --
+	(340.28,183.82) --
+	(340.26,183.81) --
+	(339.54,183.64) --
+	(339.41,183.57) --
+	(338.87,183.46) --
+	(338.79,183.45) --
+	(338.37,183.35) --
+	(338.32,183.34) --
+	(338.29,183.33) --
+	(337.92,183.25) --
+	(337.54,183.11) --
+	(336.88,182.86) --
+	(336.75,182.84) --
+	(336.07,182.69) --
+	(335.51,182.49) --
+	(333.76,181.91) --
+	(333.19,181.74) --
+	(333.07,181.69) --
+	(332.27,181.44) --
+	(332.00,181.36) --
+	(331.17,181.15) --
+	(329.52,180.73) --
+	(329.07,180.63) --
+	(328.94,180.61) --
+	(328.67,180.56) --
+	(327.91,180.38) --
+	(327.61,180.29) --
+	(326.72,180.03) --
+	(326.58,180.01) --
+	(325.99,179.79) --
+	(325.08,179.60) --
+	(324.72,179.45) --
+	(324.61,179.40) --
+	(324.42,179.32) --
+	(324.05,179.20) --
+	(323.28,178.99) --
+	(323.10,178.92) --
+	(323.02,178.91) --
+	(322.75,178.83) --
+	(322.60,178.80) --
+	(322.30,178.69) --
+	(322.04,178.63) --
+	(321.91,178.59) --
+	(321.85,178.56) --
+	(320.44,178.09) --
+	(319.81,177.87) --
+	(319.52,177.77) --
+	(319.21,177.64) --
+	(319.11,177.60) --
+	(318.85,177.48) --
+	(318.60,177.37) --
+	(318.43,177.34) --
+	(317.98,177.24) --
+	(317.89,177.22) --
+	(317.86,177.22) --
+	(317.79,177.21) --
+	(317.76,177.20) --
+	(317.75,177.20) --
+	(317.36,177.07) --
+	(317.20,177.02) --
+	(317.07,176.97) --
+	(316.93,176.93) --
+	(316.61,176.81) --
+	(316.38,176.75) --
+	(316.22,176.70) --
+	(316.13,176.68) --
+	(315.79,176.57) --
+	(315.70,176.52) --
+	(315.62,176.51) --
+	(315.51,176.48) --
+	(315.48,176.46) --
+	(315.37,176.42) --
+	(315.23,176.38) --
+	(315.21,176.38) --
+	(315.00,176.34) --
+	(314.63,176.23) --
+	(314.45,176.18) --
+	(314.31,176.13) --
+	(314.24,176.10) --
+	(313.83,175.99) --
+	(313.53,175.90) --
+	(313.27,175.82) --
+	(313.12,175.77) --
+	(312.92,175.71) --
+	(312.22,175.52) --
+	(311.88,175.40) --
+	(311.68,175.34) --
+	(311.68,175.34) --
+	(311.54,175.30) --
+	(311.44,175.27) --
+	(311.41,175.26) --
+	(311.41,175.26) --
+	(311.16,175.18) --
+	(311.04,175.12) --
+	(310.92,175.09) --
+	(310.76,175.05) --
+	(310.25,174.90) --
+	(310.00,174.86) --
+	(309.67,174.70) --
+	(309.51,174.65) --
+	(309.44,174.62) --
+	(309.22,174.54) --
+	(308.57,174.30) --
+	(308.47,174.26) --
+	(307.96,174.12) --
+	(307.91,174.10) --
+	(306.32,173.58) --
+	(306.19,173.57) --
+	(305.86,173.44) --
+	(305.61,173.35) --
+	(305.52,173.31) --
+	(305.44,173.27) --
+	(304.88,173.07) --
+	(304.21,172.85) --
+	(304.17,172.84) --
+	(304.05,172.79) --
+	(304.04,172.79) --
+	(303.87,172.74) --
+	(303.49,172.61) --
+	(302.98,172.48) --
+	(302.82,172.43) --
+	(302.50,172.31) --
+	(302.23,172.23) --
+	(302.10,172.22) --
+	(301.32,171.99) --
+	(300.69,171.75) --
+	(300.58,171.72) --
+	(299.04,171.15) --
+	(298.57,170.97) --
+	(298.34,170.90) --
+	(297.96,170.74) --
+	(297.71,170.68) --
+	(297.31,170.54) --
+	(297.31,170.54) --
+	(297.22,170.52) --
+	(297.13,170.49) --
+	(297.09,170.48) --
+	(297.05,170.47) --
+	(297.04,170.47) --
+	(297.01,170.45) --
+	(296.99,170.45) --
+	(296.65,170.34) --
+	(296.47,170.28) --
+	(296.10,170.15) --
+	(295.99,170.12) --
+	(295.93,170.10) --
+	(295.51,169.99) --
+	(295.45,169.96) --
+	(295.25,169.87) --
+	(293.91,169.37) --
+	(293.21,169.08) --
+	(292.62,168.82) --
+	(292.51,168.78) --
+	(292.49,168.77) --
+	(292.42,168.74) --
+	(292.36,168.72) --
+	(292.21,168.66) --
+	(291.88,168.54) --
+	(291.81,168.51) --
+	(291.32,168.30) --
+	(291.20,168.25) --
+	(290.86,168.11) --
+	(290.76,168.08) --
+	(289.76,167.67) --
+	(289.22,167.47) --
+	(288.59,167.23) --
+	(288.54,167.21) --
+	(287.81,166.94) --
+	(287.25,166.69) --
+	(286.59,166.38) --
+	(286.57,166.37) --
+	(286.00,166.20) --
+	(285.13,165.91) --
+	(285.03,165.88) --
+	(284.86,165.82) --
+	(284.62,165.76) --
+	(284.07,165.53) --
+	(283.98,165.49) --
+	(283.89,165.47) --
+	(283.05,165.09) --
+	(282.80,165.00) --
+	(281.45,164.49) --
+	(281.36,164.45) --
+	(281.20,164.34) --
+	(280.72,164.18) --
+	(280.53,164.10) --
+	(280.15,163.97) --
+	(279.69,163.79) --
+	(279.66,163.78) --
+	(279.52,163.71) --
+	(279.30,163.60) --
+	(279.17,163.53) --
+	(278.45,163.26) --
+	(278.04,163.09) --
+	(277.98,163.06) --
+	(277.30,162.81) --
+	(276.77,162.57) --
+	(276.31,162.40) --
+	(276.13,162.34) --
+	(275.59,162.12) --
+	(275.28,162.02) --
+	(274.52,161.70) --
+	(273.63,161.30) --
+	(272.79,160.90) --
+	(272.40,160.72) --
+	(271.68,160.45) --
+	(271.10,160.31) --
+	(271.02,160.28) --
+	(269.87,159.84) --
+	(269.74,159.79) --
+	(269.11,159.53) --
+	(268.38,159.24) --
+	(267.71,158.97) --
+	(267.28,158.77) --
+	(266.44,158.43) --
+	(266.13,158.32) --
+	(266.10,158.31) --
+	(264.97,157.91) --
+	(264.53,157.73) --
+	(264.50,157.72) --
+	(264.29,157.64) --
+	(262.99,157.06) --
+	(262.47,156.84) --
+	(262.19,156.73) --
+	(261.97,156.63) --
+	(260.80,156.07) --
+	(260.14,155.70) --
+	(260.03,155.65) --
+	(258.61,155.04) --
+	(256.32,154.07) --
+	(255.02,153.46) --
+	(254.91,153.40) --
+	(253.36,152.64) --
+	(253.12,152.51) --
+	(252.98,152.44) --
+	(252.52,152.22) --
+	(251.88,151.93) --
+	(251.61,151.81) --
+	(251.21,151.64) --
+	(250.71,151.46) --
+	(250.14,151.18) --
+	(249.91,151.06) --
+	(249.15,150.66) --
+	(248.59,150.43) --
+	(248.00,150.23) --
+	(247.15,149.83) --
+	(247.14,149.82) --
+	(245.90,149.18) --
+	(244.87,148.74) --
+	(243.82,148.30) --
+	(242.87,147.86) --
+	(240.76,146.85) --
+	(239.50,146.31) --
+	(238.44,145.78) --
+	(236.50,144.96) --
+	(233.03,143.44) --
+	(232.60,143.26) --
+	(232.55,143.23) --
+	(232.29,143.13) --
+	(231.54,142.74) --
+	(230.53,142.23) --
+	(229.80,141.90) --
+	(228.22,141.17) --
+	(226.89,140.63) --
+	(226.38,140.39) --
+	(224.51,139.48) --
+	(219.87,137.01) --
+	(219.39,136.77) --
+	(214.88,134.39) --
+	(213.28,133.63) --
+	(213.22,133.59) --
+	(213.02,133.48) --
+	(211.30,132.54) --
+	(205.70,129.59) --
+	(204.08,128.85) --
+	(203.92,128.78) --
+	(203.24,128.44) --
+	(203.15,128.38) --
+	(202.42,128.06) --
+	(201.70,127.69) --
+	(200.09,126.90) --
+	(199.79,126.75) --
+	(195.05,124.28) --
+	(195.04,124.27) --
+	(185.12,119.09) --
+	(177.68,115.22) --
+	(175.08,113.78) --
+	(164.50,108.13) --
+	(163.56,107.61) --
+	(160.15,105.77) --
+	(160.01,105.70) --
+	(124.94, 86.30) --
+	(116.56, 81.79) --
+	(113.94, 80.30) --
+	(110.01, 78.01) --
+	(104.50, 74.95) --
+	( 97.84, 71.30) --
+	( 94.41, 69.33) --
+	( 88.50, 65.89) --
+	( 79.64, 60.65) --
+	( 65.62, 52.46) --
+	( 65.48, 52.39) --
+	( 61.01, 49.80) --
 	( 52.97, 45.08) --
@@
 
-\path[fill=fillColor,fill opacity=0.50] ( 52.97,157.52) --
-	( 61.01,158.71) --
-	( 65.48,159.33) --
-	( 65.62,159.35) --
-	( 79.64,161.53) --
-	( 88.50,163.05) --
-	( 94.41,164.05) --
-	( 97.84,164.63) --
-	(104.50,165.72) --
-	(110.01,166.51) --
-	(113.94,167.24) --
-	(116.56,167.79) --
-	(124.94,169.05) --
-	(160.01,175.04) --
-	(160.15,175.05) --
-	(163.56,175.67) --
-	(164.50,175.82) --
-	(175.08,178.09) --
-	(177.68,178.61) --
-	(185.12,180.03) --
-	(195.04,182.20) --
-	(195.05,182.20) --
-	(199.79,183.10) --
-	(200.09,183.15) --
-	(201.70,183.53) --
-	(202.42,183.68) --
-	(203.15,183.82) --
-	(203.24,183.84) --
-	(203.92,183.98) --
-	(204.08,184.00) --
-	(205.70,184.39) --
-	(211.30,185.68) --
-	(213.02,186.07) --
-	(213.22,186.12) --
-	(213.28,186.14) --
-	(214.88,186.52) --
-	(219.39,187.64) --
-	(219.87,187.75) --
-	(224.51,188.92) --
-	(226.38,189.39) --
-	(226.89,189.48) --
-	(228.22,189.88) --
-	(229.80,190.26) --
-	(230.53,190.49) --
-	(231.54,190.73) --
-	(232.29,190.94) --
-	(232.55,191.02) --
-	(232.60,191.04) --
-	(233.03,191.16) --
-	(236.50,192.03) --
-	(238.44,192.60) --
-	(239.50,192.87) --
-	(240.76,193.23) --
-	(242.87,193.80) --
-	(243.82,193.97) --
-	(244.87,194.22) --
-	(245.90,194.45) --
-	(247.14,194.78) --
-	(247.15,194.78) --
-	(248.00,195.06) --
-	(248.59,195.19) --
-	(249.15,195.38) --
-	(249.91,195.68) --
-	(250.14,195.72) --
-	(250.71,195.90) --
-	(251.21,196.07) --
-	(251.61,196.16) --
-	(251.88,196.25) --
-	(252.52,196.37) --
-	(252.98,196.48) --
-	(253.12,196.53) --
-	(253.36,196.58) --
-	(254.91,197.00) --
-	(255.02,197.02) --
-	(256.32,197.42) --
-	(258.61,198.09) --
-	(260.03,198.53) --
-	(260.14,198.54) --
-	(260.80,198.76) --
-	(261.97,199.13) --
-	(262.19,199.18) --
-	(262.48,199.25) --
-	(262.99,199.41) --
-	(264.29,199.74) --
-	(264.50,199.84) --
-	(264.53,199.86) --
-	(264.97,199.98) --
-	(266.10,200.32) --
-	(266.13,200.33) --
-	(266.44,200.43) --
-	(267.28,200.69) --
-	(267.71,200.79) --
-	(268.38,200.99) --
-	(269.11,201.16) --
-	(269.74,201.38) --
-	(269.87,201.40) --
-	(271.02,201.80) --
-	(271.10,201.83) --
-	(271.68,202.00) --
-	(272.40,202.28) --
-	(272.79,202.41) --
-	(273.63,202.69) --
-	(274.52,202.98) --
-	(275.28,203.20) --
-	(275.59,203.27) --
-	(276.13,203.43) --
-	(276.31,203.47) --
-	(276.77,203.63) --
-	(277.30,203.79) --
-	(277.98,204.00) --
-	(278.04,204.00) --
-	(278.45,204.12) --
-	(279.17,204.40) --
-	(279.30,204.44) --
-	(279.52,204.50) --
-	(279.66,204.55) --
-	(279.69,204.56) --
-	(280.15,204.72) --
-	(280.53,204.89) --
-	(280.72,204.98) --
-	(281.20,205.18) --
-	(281.36,205.23) --
-	(281.45,205.24) --
-	(282.80,205.79) --
-	(283.05,205.89) --
-	(283.89,206.20) --
-	(283.98,206.21) --
-	(284.07,206.25) --
-	(284.62,206.45) --
-	(284.86,206.51) --
-	(285.03,206.59) --
-	(285.13,206.64) --
-	(286.00,206.89) --
-	(286.57,207.08) --
-	(286.59,207.10) --
-	(287.25,207.30) --
-	(287.81,207.46) --
-	(288.54,207.69) --
-	(288.59,207.71) --
-	(289.22,207.96) --
-	(289.76,208.14) --
-	(290.76,208.49) --
-	(290.86,208.52) --
-	(291.20,208.64) --
-	(291.32,208.69) --
-	(291.81,208.87) --
-	(291.88,208.91) --
-	(292.21,209.05) --
-	(292.36,209.11) --
-	(292.42,209.13) --
-	(292.49,209.15) --
-	(292.51,209.16) --
-	(292.62,209.22) --
-	(293.21,209.38) --
-	(293.91,209.64) --
-	(295.25,210.12) --
-	(295.45,210.17) --
-	(295.51,210.19) --
-	(295.93,210.34) --
-	(295.99,210.37) --
-	(296.10,210.42) --
-	(296.47,210.53) --
-	(296.65,210.60) --
-	(296.99,210.70) --
-	(297.01,210.71) --
-	(297.04,210.72) --
-	(297.05,210.72) --
-	(297.09,210.73) --
-	(297.13,210.74) --
-	(297.22,210.77) --
-	(297.31,210.80) --
-	(297.31,210.80) --
-	(297.71,210.96) --
-	(297.96,211.07) --
-	(298.34,211.23) --
-	(298.57,211.33) --
-	(299.04,211.48) --
-	(300.58,212.07) --
-	(300.69,212.11) --
-	(301.32,212.32) --
-	(302.10,212.65) --
-	(302.23,212.71) --
-	(302.50,212.86) --
-	(302.82,212.96) --
-	(302.98,213.02) --
-	(303.49,213.24) --
-	(303.87,213.38) --
-	(304.04,213.46) --
-	(304.05,213.46) --
-	(304.17,213.52) --
-	(304.21,213.54) --
-	(304.88,213.80) --
-	(305.44,214.06) --
-	(305.52,214.08) --
-	(305.61,214.12) --
-	(305.86,214.20) --
-	(306.19,214.32) --
-	(306.32,214.36) --
-	(307.91,214.96) --
-	(307.96,214.99) --
-	(308.47,215.19) --
-	(308.57,215.23) --
-	(309.22,215.49) --
-	(309.44,215.58) --
-	(309.51,215.60) --
-	(309.67,215.66) --
-	(310.00,215.78) --
-	(310.25,215.88) --
-	(310.76,216.10) --
-	(310.92,216.15) --
-	(311.04,216.19) --
-	(311.16,216.24) --
-	(311.41,216.35) --
-	(311.41,216.36) --
-	(311.44,216.37) --
-	(311.54,216.40) --
-	(311.68,216.46) --
-	(311.68,216.46) --
-	(311.88,216.53) --
-	(312.22,216.64) --
-	(312.92,216.90) --
-	(313.12,216.98) --
-	(313.27,217.05) --
-	(313.53,217.12) --
-	(313.83,217.24) --
-	(314.24,217.40) --
-	(314.31,217.42) --
-	(314.45,217.49) --
-	(314.63,217.59) --
-	(315.00,217.69) --
-	(315.21,217.81) --
-	(315.23,217.82) --
-	(315.37,217.86) --
-	(315.48,217.91) --
-	(315.51,217.92) --
-	(315.62,217.95) --
-	(315.70,217.98) --
-	(315.79,218.02) --
-	(316.13,218.15) --
-	(316.22,218.18) --
-	(316.38,218.25) --
-	(316.61,218.33) --
-	(316.93,218.48) --
-	(317.07,218.54) --
-	(317.20,218.60) --
-	(317.36,218.68) --
-	(317.75,218.86) --
-	(317.76,218.87) --
-	(317.79,218.88) --
-	(317.86,218.90) --
-	(317.89,218.91) --
-	(317.98,218.95) --
-	(318.43,219.10) --
-	(318.60,219.15) --
-	(318.85,219.23) --
-	(319.11,219.34) --
-	(319.21,219.36) --
-	(319.52,219.46) --
-	(319.81,219.61) --
-	(320.44,219.87) --
-	(321.85,220.46) --
-	(321.91,220.48) --
-	(322.04,220.54) --
-	(322.30,220.65) --
-	(322.60,220.80) --
-	(322.75,220.85) --
-	(323.02,220.98) --
-	(323.10,221.01) --
-	(323.28,221.10) --
-	(324.05,221.40) --
-	(324.42,221.57) --
-	(324.61,221.63) --
-	(324.72,221.66) --
-	(325.08,221.77) --
-	(325.99,222.17) --
-	(326.58,222.47) --
-	(326.72,222.50) --
-	(327.61,222.87) --
-	(327.91,223.02) --
-	(328.67,223.32) --
-	(328.94,223.47) --
-	(329.07,223.53) --
-	(329.52,223.68) --
-	(331.17,224.41) --
-	(332.00,224.77) --
-	(332.27,224.86) --
-	(333.07,225.24) --
-	(333.19,225.28) --
-	(333.76,225.52) --
-	(335.51,226.18) --
-	(336.07,226.42) --
-	(336.75,226.75) --
-	(336.88,226.82) --
-	(337.54,227.09) --
-	(337.92,227.27) --
-	(338.29,227.44) --
-	(338.32,227.46) --
-	(338.37,227.49) --
-	(338.79,227.66) --
-	(338.87,227.69) --
-	(339.41,227.95) --
-	(339.54,228.00) --
-	(340.26,228.35) --
-	(340.28,228.35) --
-	(340.36,228.38) --
-	(340.58,228.46) --
-	(340.90,228.61) --
-	(341.07,228.67) --
-	(341.38,228.80) --
-	(341.48,228.85) --
-	(341.53,228.88) --
-	(341.57,228.90) --
-	(342.00,229.08) --
-	(342.06,229.11) --
-	(342.60,229.32) --
-	(342.92,229.41) --
-	(344.39,230.06) --
-	(344.81,230.26) --
-	(345.03,230.35) --
-	(345.51,230.53) --
-	(345.56,230.55) --
-	(346.27,230.84) --
-	(348.09,231.63) --
-	(348.19,231.66) --
-	(348.32,231.71) --
-	(348.52,231.79) --
-	(348.65,231.84) --
-	(350.04,232.48) --
-	(350.29,232.58) --
-	(350.39,232.61) --
-	(351.49,233.03) --
-	(354.19,234.20) --
-	(354.41,234.28) --
-	(354.96,234.53) --
-	(354.99,234.54) --
-	(355.28,234.70) --
-	(355.84,234.97) --
-	(356.71,235.37) --
-	(356.75,235.39) --
-	(357.50,235.70) --
-	(357.53,235.71) --
-	(358.04,235.90) --
-	(358.62,236.15) --
-	(359.31,236.46) --
-	(359.62,236.61) --
-	(359.75,236.69) --
-	(359.85,236.75) --
-	(360.61,237.12) --
-	(360.64,237.13) --
-	(360.71,237.18) --
-	(361.91,237.72) --
-	(362.60,238.04) --
-	(364.24,238.88) --
-	(364.46,239.00) --
-	(365.70,239.62) --
-	(366.29,239.93) --
-	(370.53,241.73) --
-	(371.02,241.94) --
-	(372.06,242.43) --
-	(372.07,242.43) --
-	(372.38,242.60) --
-	(372.60,242.71) --
-	(372.90,242.85) --
-	(373.16,243.00) --
-	(373.53,243.19) --
-	(373.80,243.33) --
-	(374.46,243.64) --
-	(374.81,243.78) --
-	(375.77,244.22) --
-	(376.36,244.50) --
-	(376.51,244.59) --
-	(376.93,244.79) --
-	(378.03,245.25) --
-	(379.36,245.80) --
-	(379.36,245.80) --
-	(380.09,246.17) --
-	(380.12,246.18) --
-	(381.03,246.59) --
-	(381.47,246.80) --
-	(381.75,246.94) --
-	(382.36,247.23) --
-	(382.44,247.28) --
-	(382.57,247.34) --
-	(383.02,247.55) --
-	(385.04,248.44) --
-	(385.16,248.51) --
-	(388.87,250.32) --
-	(393.56,252.71) --
-	(395.71,253.79) --
-	(403.26,257.56) --
-	(404.02,257.95) --
-	(404.02,188.48) --
-	(403.26,188.33) --
-	(395.71,186.92) --
-	(393.56,186.56) --
-	(388.87,185.69) --
-	(385.16,184.82) --
-	(385.04,184.80) --
-	(383.02,184.39) --
-	(382.57,184.31) --
-	(382.44,184.30) --
-	(382.36,184.29) --
-	(381.75,184.16) --
-	(381.47,184.11) --
-	(381.03,184.04) --
-	(380.12,183.81) --
-	(380.09,183.80) --
-	(379.36,183.64) --
-	(379.36,183.64) --
-	(378.03,183.40) --
-	(376.93,183.15) --
-	(376.51,183.06) --
-	(376.36,183.05) --
-	(375.77,182.97) --
-	(374.81,182.77) --
-	(374.46,182.70) --
-	(373.80,182.52) --
-	(373.53,182.49) --
-	(373.16,182.43) --
-	(372.90,182.36) --
-	(372.60,182.28) --
-	(372.38,182.23) --
-	(372.07,182.19) --
-	(372.06,182.19) --
-	(371.02,182.00) --
-	(370.53,181.89) --
-	(366.29,181.14) --
-	(365.70,181.03) --
-	(364.46,180.67) --
-	(364.24,180.65) --
-	(362.60,180.37) --
-	(361.91,180.21) --
-	(360.71,179.92) --
-	(360.64,179.91) --
-	(360.61,179.91) --
-	(359.85,179.80) --
-	(359.75,179.78) --
-	(359.62,179.75) --
-	(359.31,179.68) --
-	(358.62,179.58) --
-	(358.04,179.52) --
-	(357.53,179.41) --
-	(357.50,179.40) --
-	(356.75,179.23) --
-	(356.71,179.22) --
-	(355.84,179.05) --
-	(355.28,178.90) --
-	(354.99,178.79) --
-	(354.96,178.78) --
-	(354.41,178.64) --
-	(354.19,178.60) --
-	(351.49,177.92) --
-	(350.39,177.61) --
-	(350.29,177.59) --
-	(350.04,177.51) --
-	(348.65,177.21) --
-	(348.52,177.18) --
-	(348.32,177.15) --
-	(348.19,177.12) --
-	(348.09,177.09) --
-	(346.27,176.71) --
-	(345.56,176.53) --
-	(345.51,176.51) --
-	(345.03,176.39) --
-	(344.81,176.34) --
-	(344.39,176.25) --
-	(342.92,175.94) --
-	(342.60,175.88) --
-	(342.06,175.75) --
-	(342.00,175.73) --
-	(341.57,175.65) --
-	(341.53,175.64) --
-	(341.48,175.64) --
-	(341.38,175.62) --
-	(341.07,175.54) --
-	(340.90,175.51) --
-	(340.58,175.45) --
-	(340.36,175.41) --
-	(340.28,175.40) --
-	(340.26,175.39) --
-	(339.54,175.25) --
-	(339.41,175.22) --
-	(338.87,175.11) --
-	(338.79,175.10) --
-	(338.37,175.01) --
-	(338.32,174.99) --
-	(338.29,174.98) --
-	(337.92,174.87) --
-	(337.54,174.80) --
-	(336.88,174.67) --
-	(336.75,174.64) --
-	(336.07,174.44) --
-	(335.51,174.32) --
-	(333.76,173.87) --
-	(333.19,173.78) --
-	(333.07,173.75) --
-	(332.27,173.58) --
-	(332.00,173.51) --
-	(331.17,173.30) --
-	(329.52,172.87) --
-	(329.07,172.77) --
-	(328.94,172.73) --
-	(328.67,172.67) --
-	(327.91,172.46) --
-	(327.61,172.39) --
-	(326.72,172.17) --
-	(326.58,172.14) --
-	(325.99,172.00) --
-	(325.08,171.78) --
-	(324.72,171.70) --
-	(324.61,171.67) --
-	(324.42,171.61) --
-	(324.05,171.49) --
-	(323.28,171.35) --
-	(323.10,171.31) --
-	(323.02,171.29) --
-	(322.75,171.18) --
-	(322.60,171.15) --
-	(322.30,171.10) --
-	(322.04,171.03) --
-	(321.91,171.01) --
-	(321.85,171.00) --
-	(320.44,170.69) --
-	(319.81,170.53) --
-	(319.52,170.45) --
-	(319.21,170.37) --
-	(319.11,170.34) --
-	(318.85,170.26) --
-	(318.60,170.22) --
-	(318.43,170.18) --
-	(317.98,170.05) --
-	(317.89,170.02) --
-	(317.86,170.01) --
-	(317.79,169.99) --
-	(317.76,169.99) --
-	(317.75,169.99) --
-	(317.36,169.90) --
-	(317.20,169.85) --
-	(317.07,169.82) --
-	(316.93,169.79) --
-	(316.61,169.68) --
-	(316.38,169.60) --
-	(316.22,169.57) --
-	(316.13,169.55) --
-	(315.79,169.46) --
-	(315.70,169.44) --
-	(315.62,169.41) --
-	(315.51,169.37) --
-	(315.48,169.36) --
-	(315.37,169.32) --
-	(315.23,169.28) --
-	(315.21,169.27) --
-	(315.00,169.20) --
-	(314.63,169.05) --
-	(314.45,168.98) --
-	(314.31,168.94) --
-	(314.24,168.90) --
-	(313.83,168.77) --
-	(313.53,168.69) --
-	(313.27,168.63) --
-	(313.12,168.61) --
-	(312.92,168.58) --
-	(312.22,168.40) --
-	(311.88,168.29) --
-	(311.68,168.25) --
-	(311.68,168.25) --
-	(311.54,168.22) --
-	(311.44,168.18) --
-	(311.41,168.17) --
-	(311.41,168.17) --
-	(311.16,168.09) --
-	(311.04,168.07) --
-	(310.92,168.05) --
-	(310.76,168.02) --
-	(310.25,167.88) --
-	(310.00,167.83) --
-	(309.67,167.75) --
-	(309.51,167.72) --
-	(309.44,167.71) --
-	(309.22,167.66) --
-	(308.57,167.46) --
-	(308.47,167.44) --
-	(307.96,167.34) --
-	(307.91,167.34) --
-	(306.32,166.93) --
-	(306.19,166.90) --
-	(305.86,166.81) --
-	(305.61,166.74) --
-	(305.52,166.71) --
-	(305.44,166.69) --
-	(304.88,166.51) --
-	(304.21,166.30) --
-	(304.17,166.30) --
-	(304.05,166.26) --
-	(304.04,166.26) --
-	(303.87,166.21) --
-	(303.49,166.10) --
-	(302.98,165.93) --
-	(302.82,165.89) --
-	(302.50,165.78) --
-	(302.23,165.67) --
-	(302.10,165.62) --
-	(301.32,165.40) --
-	(300.69,165.24) --
-	(300.58,165.20) --
-	(299.04,164.69) --
-	(298.57,164.54) --
-	(298.34,164.48) --
-	(297.96,164.38) --
-	(297.71,164.30) --
-	(297.31,164.13) --
-	(297.31,164.13) --
-	(297.22,164.10) --
-	(297.13,164.08) --
-	(297.09,164.07) --
-	(297.05,164.05) --
-	(297.04,164.05) --
-	(297.01,164.04) --
-	(296.99,164.03) --
-	(296.65,163.91) --
-	(296.47,163.85) --
-	(296.10,163.73) --
-	(295.99,163.69) --
-	(295.93,163.67) --
-	(295.51,163.54) --
-	(295.45,163.52) --
-	(295.25,163.45) --
-	(293.91,163.09) --
-	(293.21,162.89) --
-	(292.62,162.68) --
-	(292.51,162.66) --
-	(292.49,162.65) --
-	(292.42,162.63) --
-	(292.36,162.61) --
-	(292.21,162.56) --
-	(291.88,162.48) --
-	(291.81,162.46) --
-	(291.32,162.32) --
-	(291.20,162.27) --
-	(290.86,162.16) --
-	(290.76,162.12) --
-	(289.76,161.73) --
-	(289.22,161.57) --
-	(288.59,161.34) --
-	(288.54,161.32) --
-	(287.81,161.08) --
-	(287.25,160.92) --
-	(286.59,160.70) --
-	(286.57,160.70) --
-	(286.00,160.52) --
-	(285.13,160.28) --
-	(285.03,160.25) --
-	(284.86,160.19) --
-	(284.62,160.11) --
-	(284.07,159.94) --
-	(283.98,159.91) --
-	(283.89,159.89) --
-	(283.05,159.64) --
-	(282.80,159.57) --
-	(281.45,159.12) --
-	(281.36,159.08) --
-	(281.20,159.03) --
-	(280.72,158.84) --
-	(280.53,158.80) --
-	(280.15,158.71) --
-	(279.69,158.55) --
-	(279.66,158.54) --
-	(279.52,158.48) --
-	(279.30,158.40) --
-	(279.17,158.36) --
-	(278.45,158.13) --
-	(278.04,157.99) --
-	(277.98,157.96) --
-	(277.30,157.71) --
-	(276.77,157.53) --
-	(276.31,157.40) --
-	(276.13,157.34) --
-	(275.59,157.16) --
-	(275.28,157.07) --
-	(274.52,156.81) --
-	(273.63,156.52) --
-	(272.79,156.25) --
-	(272.40,156.11) --
-	(271.68,155.88) --
-	(271.10,155.68) --
-	(271.02,155.65) --
-	(269.87,155.20) --
-	(269.74,155.17) --
-	(269.11,154.96) --
-	(268.38,154.71) --
-	(267.71,154.49) --
-	(267.28,154.34) --
-	(266.44,154.07) --
-	(266.13,153.97) --
-	(266.10,153.96) --
-	(264.97,153.64) --
-	(264.53,153.52) --
-	(264.50,153.51) --
-	(264.29,153.45) --
-	(262.99,153.00) --
-	(262.48,152.85) --
-	(262.19,152.74) --
-	(261.97,152.68) --
-	(260.80,152.32) --
-	(260.14,152.06) --
-	(260.03,152.03) --
-	(258.61,151.54) --
-	(256.32,150.72) --
-	(255.02,150.28) --
-	(254.91,150.24) --
-	(253.36,149.63) --
-	(253.12,149.55) --
-	(252.98,149.50) --
-	(252.52,149.32) --
-	(251.88,149.06) --
-	(251.61,148.94) --
-	(251.21,148.84) --
-	(250.71,148.65) --
-	(250.14,148.41) --
-	(249.91,148.31) --
-	(249.15,148.07) --
-	(248.59,147.93) --
-	(248.00,147.70) --
-	(247.15,147.40) --
-	(247.14,147.39) --
-	(245.90,146.93) --
-	(244.87,146.49) --
-	(243.82,146.09) --
-	(242.87,145.70) --
-	(240.76,144.79) --
-	(239.50,144.28) --
-	(238.44,143.86) --
-	(236.50,143.12) --
-	(233.03,141.67) --
-	(232.60,141.48) --
-	(232.55,141.46) --
-	(232.29,141.37) --
-	(231.54,141.09) --
-	(230.53,140.70) --
-	(229.80,140.39) --
-	(228.22,139.75) --
-	(226.89,139.17) --
-	(226.38,138.96) --
-	(224.51,138.27) --
-	(219.87,136.46) --
-	(219.39,136.25) --
-	(214.88,134.34) --
-	(213.28,133.63) --
-	(213.22,133.61) --
-	(213.02,133.50) --
-	(211.30,132.78) --
-	(205.70,130.38) --
-	(204.08,129.58) --
-	(203.92,129.52) --
-	(203.24,129.24) --
-	(203.15,129.19) --
-	(202.42,128.83) --
-	(201.70,128.52) --
-	(200.09,127.78) --
-	(199.79,127.65) --
-	(195.05,125.74) --
-	(195.04,125.74) --
-	(185.12,121.11) --
-	(177.68,117.77) --
-	(175.08,116.58) --
-	(164.50,111.49) --
-	(163.56,111.05) --
-	(160.15,109.37) --
-	(160.01,109.30) --
-	(124.94, 91.80) --
-	(116.56, 87.52) --
-	(113.94, 86.20) --
-	(110.01, 84.11) --
-	(104.50, 81.25) --
-	( 97.84, 77.97) --
-	( 94.41, 76.21) --
-	( 88.50, 73.15) --
-	( 79.64, 68.59) --
-	( 65.62, 61.16) --
-	( 65.48, 61.09) --
-	( 61.01, 58.86) --
-	( 52.97, 54.68) --
+\path[fill=fillColor,fill opacity=0.50] ( 52.97,156.39) --
+	( 61.01,157.87) --
+	( 65.48,158.70) --
+	( 65.62,158.74) --
+	( 79.64,161.31) --
+	( 88.50,162.86) --
+	( 94.41,163.99) --
+	( 97.84,164.62) --
+	(104.50,165.86) --
+	(110.01,166.89) --
+	(113.94,167.67) --
+	(116.56,168.21) --
+	(124.94,169.72) --
+	(160.01,176.65) --
+	(160.15,176.67) --
+	(163.56,177.38) --
+	(164.50,177.59) --
+	(175.08,179.88) --
+	(177.68,180.37) --
+	(185.12,181.92) --
+	(195.04,184.04) --
+	(195.05,184.04) --
+	(199.79,185.19) --
+	(200.09,185.26) --
+	(201.70,185.62) --
+	(202.42,185.77) --
+	(203.15,185.92) --
+	(203.24,185.94) --
+	(203.92,186.11) --
+	(204.08,186.14) --
+	(205.70,186.55) --
+	(211.30,187.85) --
+	(213.02,188.24) --
+	(213.22,188.28) --
+	(213.28,188.30) --
+	(214.88,188.73) --
+	(219.39,189.75) --
+	(219.87,189.87) --
+	(224.51,190.96) --
+	(226.38,191.38) --
+	(226.89,191.49) --
+	(228.22,191.78) --
+	(229.80,192.13) --
+	(230.53,192.30) --
+	(231.54,192.53) --
+	(232.29,192.73) --
+	(232.55,192.78) --
+	(232.60,192.80) --
+	(233.03,192.92) --
+	(236.50,193.82) --
+	(238.44,194.27) --
+	(239.50,194.57) --
+	(240.76,194.90) --
+	(242.87,195.46) --
+	(243.82,195.67) --
+	(244.87,195.98) --
+	(245.90,196.25) --
+	(247.14,196.59) --
+	(247.15,196.59) --
+	(248.00,196.80) --
+	(248.59,196.95) --
+	(249.15,197.11) --
+	(249.91,197.30) --
+	(250.14,197.39) --
+	(250.71,197.53) --
+	(251.21,197.68) --
+	(251.61,197.82) --
+	(251.88,197.90) --
+	(252.52,198.08) --
+	(252.98,198.21) --
+	(253.12,198.26) --
+	(253.36,198.33) --
+	(254.91,198.78) --
+	(255.02,198.82) --
+	(256.32,199.25) --
+	(258.61,199.93) --
+	(260.03,200.28) --
+	(260.14,200.31) --
+	(260.80,200.49) --
+	(261.97,200.82) --
+	(262.19,200.90) --
+	(262.47,201.00) --
+	(262.99,201.17) --
+	(264.29,201.61) --
+	(264.50,201.71) --
+	(264.53,201.73) --
+	(264.97,201.89) --
+	(266.10,202.25) --
+	(266.13,202.26) --
+	(266.44,202.33) --
+	(267.28,202.63) --
+	(267.71,202.76) --
+	(268.38,203.01) --
+	(269.11,203.20) --
+	(269.74,203.41) --
+	(269.87,203.46) --
+	(271.02,203.82) --
+	(271.10,203.84) --
+	(271.68,204.04) --
+	(272.40,204.22) --
+	(272.79,204.39) --
+	(273.63,204.66) --
+	(274.52,204.93) --
+	(275.28,205.23) --
+	(275.59,205.33) --
+	(276.13,205.54) --
+	(276.31,205.60) --
+	(276.77,205.76) --
+	(277.30,205.93) --
+	(277.98,206.16) --
+	(278.04,206.17) --
+	(278.45,206.30) --
+	(279.17,206.53) --
+	(279.30,206.56) --
+	(279.52,206.62) --
+	(279.66,206.67) --
+	(279.69,206.67) --
+	(280.15,206.81) --
+	(280.53,206.92) --
+	(280.72,206.98) --
+	(281.20,207.14) --
+	(281.36,207.19) --
+	(281.45,207.22) --
+	(282.80,207.62) --
+	(283.05,207.69) --
+	(283.89,207.98) --
+	(283.98,208.02) --
+	(284.07,208.06) --
+	(284.62,208.24) --
+	(284.86,208.32) --
+	(285.03,208.39) --
+	(285.13,208.43) --
+	(286.00,208.76) --
+	(286.57,208.94) --
+	(286.59,208.95) --
+	(287.25,209.20) --
+	(287.81,209.40) --
+	(288.54,209.65) --
+	(288.59,209.66) --
+	(289.22,209.88) --
+	(289.76,210.08) --
+	(290.76,210.47) --
+	(290.86,210.51) --
+	(291.20,210.60) --
+	(291.32,210.63) --
+	(291.81,210.79) --
+	(291.88,210.82) --
+	(292.21,210.92) --
+	(292.36,210.96) --
+	(292.42,210.98) --
+	(292.49,211.01) --
+	(292.51,211.02) --
+	(292.62,211.07) --
+	(293.21,211.33) --
+	(293.91,211.56) --
+	(295.25,212.03) --
+	(295.45,212.10) --
+	(295.51,212.13) --
+	(295.93,212.30) --
+	(295.99,212.33) --
+	(296.10,212.37) --
+	(296.47,212.48) --
+	(296.65,212.57) --
+	(296.99,212.65) --
+	(297.01,212.65) --
+	(297.04,212.66) --
+	(297.05,212.66) --
+	(297.09,212.68) --
+	(297.13,212.69) --
+	(297.22,212.72) --
+	(297.31,212.75) --
+	(297.31,212.75) --
+	(297.71,212.93) --
+	(297.96,213.02) --
+	(298.34,213.18) --
+	(298.57,213.28) --
+	(299.04,213.48) --
+	(300.58,214.09) --
+	(300.69,214.12) --
+	(301.32,214.36) --
+	(302.10,214.63) --
+	(302.23,214.68) --
+	(302.50,214.78) --
+	(302.82,214.88) --
+	(302.98,214.97) --
+	(303.49,215.16) --
+	(303.87,215.28) --
+	(304.04,215.35) --
+	(304.05,215.36) --
+	(304.17,215.40) --
+	(304.21,215.41) --
+	(304.88,215.68) --
+	(305.44,215.90) --
+	(305.52,215.94) --
+	(305.61,215.99) --
+	(305.86,216.08) --
+	(306.19,216.21) --
+	(306.32,216.27) --
+	(307.91,216.84) --
+	(307.96,216.86) --
+	(308.47,217.10) --
+	(308.57,217.12) --
+	(309.22,217.37) --
+	(309.44,217.47) --
+	(309.51,217.50) --
+	(309.67,217.57) --
+	(310.00,217.72) --
+	(310.25,217.80) --
+	(310.76,218.00) --
+	(310.92,218.07) --
+	(311.04,218.12) --
+	(311.16,218.17) --
+	(311.41,218.27) --
+	(311.41,218.27) --
+	(311.44,218.29) --
+	(311.54,218.32) --
+	(311.68,218.36) --
+	(311.68,218.36) --
+	(311.88,218.45) --
+	(312.22,218.58) --
+	(312.92,218.83) --
+	(313.12,218.91) --
+	(313.27,218.97) --
+	(313.53,219.09) --
+	(313.83,219.22) --
+	(314.24,219.36) --
+	(314.31,219.39) --
+	(314.45,219.45) --
+	(314.63,219.53) --
+	(315.00,219.67) --
+	(315.21,219.76) --
+	(315.23,219.77) --
+	(315.37,219.80) --
+	(315.48,219.86) --
+	(315.51,219.87) --
+	(315.62,219.90) --
+	(315.70,219.93) --
+	(315.79,219.95) --
+	(316.13,220.10) --
+	(316.22,220.13) --
+	(316.38,220.20) --
+	(316.61,220.29) --
+	(316.93,220.44) --
+	(317.07,220.49) --
+	(317.20,220.57) --
+	(317.36,220.62) --
+	(317.75,220.78) --
+	(317.76,220.78) --
+	(317.79,220.79) --
+	(317.86,220.81) --
+	(317.89,220.82) --
+	(317.98,220.85) --
+	(318.43,221.04) --
+	(318.60,221.09) --
+	(318.85,221.18) --
+	(319.11,221.27) --
+	(319.21,221.31) --
+	(319.52,221.44) --
+	(319.81,221.56) --
+	(320.44,221.84) --
+	(321.85,222.45) --
+	(321.91,222.48) --
+	(322.04,222.54) --
+	(322.30,222.65) --
+	(322.60,222.78) --
+	(322.75,222.84) --
+	(323.02,222.93) --
+	(323.10,222.95) --
+	(323.28,223.02) --
+	(324.05,223.31) --
+	(324.42,223.45) --
+	(324.61,223.52) --
+	(324.72,223.55) --
+	(325.08,223.72) --
+	(325.99,224.04) --
+	(326.58,224.29) --
+	(326.72,224.34) --
+	(327.61,224.71) --
+	(327.91,224.84) --
+	(328.67,225.16) --
+	(328.94,225.26) --
+	(329.07,225.33) --
+	(329.52,225.53) --
+	(331.17,226.21) --
+	(332.00,226.56) --
+	(332.27,226.67) --
+	(333.07,227.03) --
+	(333.19,227.08) --
+	(333.76,227.35) --
+	(335.51,228.12) --
+	(336.07,228.33) --
+	(336.75,228.66) --
+	(336.88,228.71) --
+	(337.54,229.01) --
+	(337.92,229.21) --
+	(338.29,229.35) --
+	(338.32,229.36) --
+	(338.37,229.38) --
+	(338.79,229.60) --
+	(338.87,229.63) --
+	(339.41,229.85) --
+	(339.54,229.90) --
+	(340.26,230.24) --
+	(340.28,230.25) --
+	(340.36,230.28) --
+	(340.58,230.38) --
+	(340.90,230.51) --
+	(341.07,230.59) --
+	(341.38,230.73) --
+	(341.48,230.78) --
+	(341.53,230.80) --
+	(341.57,230.81) --
+	(342.00,230.98) --
+	(342.06,231.02) --
+	(342.60,231.25) --
+	(342.92,231.39) --
+	(344.39,232.03) --
+	(344.81,232.21) --
+	(345.03,232.33) --
+	(345.51,232.53) --
+	(345.56,232.55) --
+	(346.27,232.86) --
+	(348.09,233.67) --
+	(348.19,233.72) --
+	(348.32,233.79) --
+	(348.52,233.88) --
+	(348.65,233.94) --
+	(350.04,234.58) --
+	(350.29,234.69) --
+	(350.39,234.75) --
+	(351.49,235.24) --
+	(354.19,236.42) --
+	(354.41,236.53) --
+	(354.96,236.78) --
+	(354.99,236.80) --
+	(355.28,236.94) --
+	(355.84,237.22) --
+	(356.71,237.65) --
+	(356.75,237.67) --
+	(357.50,237.99) --
+	(357.53,238.00) --
+	(358.04,238.25) --
+	(358.62,238.54) --
+	(359.31,238.90) --
+	(359.62,239.08) --
+	(359.75,239.15) --
+	(359.85,239.21) --
+	(360.61,239.51) --
+	(360.64,239.52) --
+	(360.71,239.55) --
+	(361.91,240.12) --
+	(362.60,240.45) --
+	(364.24,241.19) --
+	(364.46,241.30) --
+	(365.70,241.92) --
+	(366.29,242.17) --
+	(370.53,244.08) --
+	(371.02,244.33) --
+	(372.06,244.82) --
+	(372.07,244.82) --
+	(372.38,244.97) --
+	(372.60,245.07) --
+	(372.90,245.21) --
+	(373.16,245.34) --
+	(373.53,245.52) --
+	(373.80,245.66) --
+	(374.46,245.97) --
+	(374.81,246.14) --
+	(375.77,246.62) --
+	(376.36,246.89) --
+	(376.51,246.97) --
+	(376.93,247.18) --
+	(378.03,247.74) --
+	(379.36,248.35) --
+	(379.36,248.35) --
+	(380.09,248.75) --
+	(380.12,248.76) --
+	(381.03,249.21) --
+	(381.47,249.42) --
+	(381.75,249.52) --
+	(382.36,249.84) --
+	(382.44,249.89) --
+	(382.57,249.96) --
+	(383.02,250.19) --
+	(385.04,251.16) --
+	(385.16,251.20) --
+	(388.87,253.05) --
+	(393.56,255.21) --
+	(395.71,256.30) --
+	(403.26,259.98) --
+	(404.02,260.36) --
+	(404.02,203.20) --
+	(403.26,203.04) --
+	(395.71,201.44) --
+	(393.56,200.92) --
+	(388.87,199.86) --
+	(385.16,198.96) --
+	(385.04,198.94) --
+	(383.02,198.51) --
+	(382.57,198.39) --
+	(382.44,198.36) --
+	(382.36,198.33) --
+	(381.75,198.18) --
+	(381.47,198.10) --
+	(381.03,197.97) --
+	(380.12,197.74) --
+	(380.09,197.73) --
+	(379.36,197.56) --
+	(379.36,197.56) --
+	(378.03,197.26) --
+	(376.93,196.94) --
+	(376.51,196.88) --
+	(376.36,196.84) --
+	(375.77,196.70) --
+	(374.81,196.47) --
+	(374.46,196.36) --
+	(373.80,196.24) --
+	(373.53,196.20) --
+	(373.16,196.12) --
+	(372.90,196.08) --
+	(372.60,196.00) --
+	(372.38,195.93) --
+	(372.07,195.82) --
+	(372.06,195.82) --
+	(371.02,195.55) --
+	(370.53,195.42) --
+	(366.29,194.46) --
+	(365.70,194.31) --
+	(364.46,194.06) --
+	(364.24,194.03) --
+	(362.60,193.61) --
+	(361.91,193.45) --
+	(360.71,193.09) --
+	(360.64,193.06) --
+	(360.61,193.05) --
+	(359.85,192.86) --
+	(359.75,192.84) --
+	(359.62,192.80) --
+	(359.31,192.72) --
+	(358.62,192.57) --
+	(358.04,192.41) --
+	(357.53,192.34) --
+	(357.50,192.34) --
+	(356.75,192.11) --
+	(356.71,192.11) --
+	(355.84,191.93) --
+	(355.28,191.75) --
+	(354.99,191.69) --
+	(354.96,191.68) --
+	(354.41,191.53) --
+	(354.19,191.47) --
+	(351.49,190.79) --
+	(350.39,190.53) --
+	(350.29,190.50) --
+	(350.04,190.46) --
+	(348.65,190.18) --
+	(348.52,190.15) --
+	(348.32,190.10) --
+	(348.19,190.06) --
+	(348.09,190.04) --
+	(346.27,189.47) --
+	(345.56,189.31) --
+	(345.51,189.30) --
+	(345.03,189.17) --
+	(344.81,189.10) --
+	(344.39,188.99) --
+	(342.92,188.63) --
+	(342.60,188.57) --
+	(342.06,188.44) --
+	(342.00,188.42) --
+	(341.57,188.29) --
+	(341.53,188.28) --
+	(341.48,188.27) --
+	(341.38,188.23) --
+	(341.07,188.15) --
+	(340.90,188.11) --
+	(340.58,187.99) --
+	(340.36,187.91) --
+	(340.28,187.88) --
+	(340.26,187.87) --
+	(339.54,187.63) --
+	(339.41,187.59) --
+	(338.87,187.43) --
+	(338.79,187.41) --
+	(338.37,187.28) --
+	(338.32,187.27) --
+	(338.29,187.26) --
+	(337.92,187.17) --
+	(337.54,187.10) --
+	(336.88,186.93) --
+	(336.75,186.90) --
+	(336.07,186.65) --
+	(335.51,186.50) --
+	(333.76,186.05) --
+	(333.19,185.87) --
+	(333.07,185.85) --
+	(332.27,185.59) --
+	(332.00,185.50) --
+	(331.17,185.27) --
+	(329.52,184.77) --
+	(329.07,184.61) --
+	(328.94,184.57) --
+	(328.67,184.50) --
+	(327.91,184.30) --
+	(327.61,184.22) --
+	(326.72,183.98) --
+	(326.58,183.94) --
+	(325.99,183.73) --
+	(325.08,183.45) --
+	(324.72,183.35) --
+	(324.61,183.30) --
+	(324.42,183.25) --
+	(324.05,183.13) --
+	(323.28,182.88) --
+	(323.10,182.83) --
+	(323.02,182.80) --
+	(322.75,182.74) --
+	(322.60,182.69) --
+	(322.30,182.57) --
+	(322.04,182.48) --
+	(321.91,182.44) --
+	(321.85,182.42) --
+	(320.44,182.01) --
+	(319.81,181.86) --
+	(319.52,181.74) --
+	(319.21,181.63) --
+	(319.11,181.60) --
+	(318.85,181.53) --
+	(318.60,181.46) --
+	(318.43,181.38) --
+	(317.98,181.24) --
+	(317.89,181.22) --
+	(317.86,181.22) --
+	(317.79,181.21) --
+	(317.76,181.21) --
+	(317.75,181.21) --
+	(317.36,181.09) --
+	(317.20,181.04) --
+	(317.07,181.00) --
+	(316.93,180.96) --
+	(316.61,180.84) --
+	(316.38,180.76) --
+	(316.22,180.72) --
+	(316.13,180.70) --
+	(315.79,180.59) --
+	(315.70,180.56) --
+	(315.62,180.52) --
+	(315.51,180.48) --
+	(315.48,180.47) --
+	(315.37,180.44) --
+	(315.23,180.37) --
+	(315.21,180.36) --
+	(315.00,180.27) --
+	(314.63,180.18) --
+	(314.45,180.11) --
+	(314.31,180.08) --
+	(314.24,180.05) --
+	(313.83,179.93) --
+	(313.53,179.81) --
+	(313.27,179.74) --
+	(313.12,179.70) --
+	(312.92,179.64) --
+	(312.22,179.41) --
+	(311.88,179.32) --
+	(311.68,179.26) --
+	(311.68,179.26) --
+	(311.54,179.22) --
+	(311.44,179.20) --
+	(311.41,179.19) --
+	(311.41,179.19) --
+	(311.16,179.09) --
+	(311.04,179.05) --
+	(310.92,179.01) --
+	(310.76,178.96) --
+	(310.25,178.78) --
+	(310.00,178.68) --
+	(309.67,178.54) --
+	(309.51,178.48) --
+	(309.44,178.46) --
+	(309.22,178.38) --
+	(308.57,178.17) --
+	(308.47,178.15) --
+	(307.96,178.01) --
+	(307.91,177.99) --
+	(306.32,177.47) --
+	(306.19,177.43) --
+	(305.86,177.32) --
+	(305.61,177.24) --
+	(305.52,177.21) --
+	(305.44,177.19) --
+	(304.88,176.99) --
+	(304.21,176.77) --
+	(304.17,176.76) --
+	(304.05,176.73) --
+	(304.04,176.72) --
+	(303.87,176.68) --
+	(303.49,176.51) --
+	(302.98,176.31) --
+	(302.82,176.25) --
+	(302.50,176.15) --
+	(302.23,176.06) --
+	(302.10,176.01) --
+	(301.32,175.79) --
+	(300.69,175.60) --
+	(300.58,175.54) --
+	(299.04,175.05) --
+	(298.57,174.88) --
+	(298.34,174.79) --
+	(297.96,174.65) --
+	(297.71,174.57) --
+	(297.31,174.43) --
+	(297.31,174.43) --
+	(297.22,174.41) --
+	(297.13,174.37) --
+	(297.09,174.36) --
+	(297.05,174.34) --
+	(297.04,174.34) --
+	(297.01,174.32) --
+	(296.99,174.32) --
+	(296.65,174.21) --
+	(296.47,174.17) --
+	(296.10,174.03) --
+	(295.99,174.00) --
+	(295.93,173.98) --
+	(295.51,173.82) --
+	(295.45,173.79) --
+	(295.25,173.70) --
+	(293.91,173.24) --
+	(293.21,172.98) --
+	(292.62,172.73) --
+	(292.51,172.68) --
+	(292.49,172.68) --
+	(292.42,172.66) --
+	(292.36,172.64) --
+	(292.21,172.58) --
+	(291.88,172.47) --
+	(291.81,172.45) --
+	(291.32,172.24) --
+	(291.20,172.19) --
+	(290.86,172.06) --
+	(290.76,172.03) --
+	(289.76,171.70) --
+	(289.22,171.51) --
+	(288.59,171.29) --
+	(288.54,171.27) --
+	(287.81,170.95) --
+	(287.25,170.71) --
+	(286.59,170.46) --
+	(286.57,170.45) --
+	(286.00,170.22) --
+	(285.13,169.88) --
+	(285.03,169.85) --
+	(284.86,169.78) --
+	(284.62,169.68) --
+	(284.07,169.45) --
+	(283.98,169.42) --
+	(283.89,169.38) --
+	(283.05,169.06) --
+	(282.80,168.97) --
+	(281.45,168.44) --
+	(281.36,168.42) --
+	(281.20,168.37) --
+	(280.72,168.16) --
+	(280.53,168.10) --
+	(280.15,167.95) --
+	(279.69,167.75) --
+	(279.66,167.74) --
+	(279.52,167.68) --
+	(279.30,167.59) --
+	(279.17,167.54) --
+	(278.45,167.25) --
+	(278.04,167.06) --
+	(277.98,167.04) --
+	(277.30,166.72) --
+	(276.77,166.51) --
+	(276.31,166.31) --
+	(276.13,166.23) --
+	(275.59,165.99) --
+	(275.28,165.89) --
+	(274.52,165.57) --
+	(273.63,165.16) --
+	(272.79,164.87) --
+	(272.40,164.70) --
+	(271.68,164.42) --
+	(271.10,164.19) --
+	(271.02,164.16) --
+	(269.87,163.70) --
+	(269.74,163.65) --
+	(269.11,163.42) --
+	(268.38,163.06) --
+	(267.71,162.79) --
+	(267.28,162.64) --
+	(266.44,162.35) --
+	(266.13,162.23) --
+	(266.10,162.22) --
+	(264.97,161.74) --
+	(264.53,161.55) --
+	(264.50,161.55) --
+	(264.29,161.46) --
+	(262.99,160.99) --
+	(262.47,160.83) --
+	(262.19,160.71) --
+	(261.97,160.63) --
+	(260.80,160.22) --
+	(260.14,159.96) --
+	(260.03,159.92) --
+	(258.61,159.30) --
+	(256.32,158.33) --
+	(255.02,157.73) --
+	(254.91,157.71) --
+	(253.36,156.88) --
+	(253.12,156.77) --
+	(252.98,156.71) --
+	(252.52,156.53) --
+	(251.88,156.22) --
+	(251.61,156.11) --
+	(251.21,155.93) --
+	(250.71,155.72) --
+	(250.14,155.46) --
+	(249.91,155.34) --
+	(249.15,155.01) --
+	(248.59,154.77) --
+	(248.00,154.49) --
+	(247.15,154.13) --
+	(247.14,154.13) --
+	(245.90,153.64) --
+	(244.87,153.14) --
+	(243.82,152.69) --
+	(242.87,152.27) --
+	(240.76,151.34) --
+	(239.50,150.76) --
+	(238.44,150.24) --
+	(236.50,149.32) --
+	(233.03,147.65) --
+	(232.60,147.43) --
+	(232.55,147.40) --
+	(232.29,147.26) --
+	(231.54,146.88) --
+	(230.53,146.36) --
+	(229.80,146.01) --
+	(228.22,145.31) --
+	(226.89,144.70) --
+	(226.38,144.43) --
+	(224.51,143.49) --
+	(219.87,141.22) --
+	(219.39,141.01) --
+	(214.88,138.97) --
+	(213.28,138.19) --
+	(213.22,138.16) --
+	(213.02,138.10) --
+	(211.30,137.27) --
+	(205.70,134.58) --
+	(204.08,133.81) --
+	(203.92,133.75) --
+	(203.24,133.46) --
+	(203.15,133.43) --
+	(202.42,133.02) --
+	(201.70,132.64) --
+	(200.09,131.86) --
+	(199.79,131.73) --
+	(195.05,129.44) --
+	(195.04,129.43) --
+	(185.12,124.30) --
+	(177.68,120.60) --
+	(175.08,119.25) --
+	(164.50,114.05) --
+	(163.56,113.54) --
+	(160.15,111.75) --
+	(160.01,111.68) --
+	(124.94, 93.16) --
+	(116.56, 88.83) --
+	(113.94, 87.43) --
+	(110.01, 85.40) --
+	(104.50, 82.51) --
+	( 97.84, 78.99) --
+	( 94.41, 77.25) --
+	( 88.50, 74.13) --
+	( 79.64, 69.36) --
+	( 65.62, 62.12) --
+	( 65.48, 62.06) --
+	( 61.01, 59.63) --
+	( 52.97, 55.14) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (185.12, 34.03) -- (185.12, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (185.11, 34.03) -- (185.11, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.63, 34.03) -- (284.63, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (284.62, 34.03) -- (284.62, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.12, 34.03) -- (297.12, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.13, 34.03) -- (297.13, 41.32);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31, 44.90) {-5};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,128.11) {0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,211.32) {5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31, 45.50) {-5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,126.10) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,206.70) {5};
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at ( 19.11,155.53) {\% $\Delta$ Ln(GDP)$_{t}$};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at ( 14.29,155.53) {\% $\Delta$ GDP$_{t}$};
 \end{scope}

### 2014-10-09 LaTeX/rmseInOut.tex
ugh
handing it back to ben

@@
-% Created by tikzDevice version 0.7.0 on 2014-10-06 19:44:46
+% Created by tikzDevice version 0.7.0 on 2014-10-09 04:51:38
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[fill=fillColor] (152.09, 64.30) rectangle (245.89,242.43);
+\path[fill=fillColor] (152.09, 64.30) rectangle (245.89,243.43);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
@@
 
-\path[fill=fillColor] (280.17, 64.30) rectangle (373.98,254.37);
+\path[fill=fillColor] (280.17, 64.30) rectangle (373.98,254.41);
 
-\path[fill=fillColor] (384.40, 64.30) rectangle (478.21,239.82);
+\path[fill=fillColor] (384.40, 64.30) rectangle (478.21,241.39);
 \definecolor[named]{drawColor}{rgb}{0.50,0.50,0.50}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (146.87,267.41) {Ln(Min. Cap Dist.)$_{t}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (146.87,267.41) {Ln(Min. Capital Dist.)$_{t}$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11,120.76) {2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11,120.61) {2};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11,180.52) {4};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11,180.22) {4};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11,240.28) {6};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 25.11,239.83) {6};
 \end{scope}

### 2014-10-09 R/Analysis/models.R

@@ -6,6 +6,9 @@ if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
 setwd(pathData)
 load('combinedData.rda'); modData=yData
 
+# Gen tikz?
+genTikz=TRUE
+
 # CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
 ###################################################################
 logTrans=function(x){ log( x + abs(min(x, na.rm=T)) + 1) }
@@ -24,7 +27,7 @@ modData$Int.max <- modData$Int.max-1
 # Transformations for other controls
 modData$lngdpCap = log(modData$gdpCap)
 modData$lninflation_l1 = logTrans(modData$inflation_l1)
-modData$democ = as.numeric(modData$polity>=6)
+modData$democ = as.numeric(modData$polity2>=6)
 modData$polity2 = modData$polity2 + 11
 ###################################################################
 
@@ -32,7 +35,7 @@ modData$polity2 = modData$polity2 + 11
 ###################################################################
 modForm=function(x){
   formula( paste0('lngdpGr_l0 ~', x, '+ 
-  Int.max + territorial.max + durSt1max + confAreaPropHi +
+  Int.max + durSt1max + confAreaPropHi +
   nconf + upperincome + lninflation_l1 + polity2 +
   resourceGDP + gdpGr.mean_l0 + (1|ccode)' ) )
 }
@@ -54,7 +57,7 @@ rmse(mCity); rmse(mCap)
 setwd(pathMain)
 source('vizResults.R')
 
-otherCovars=c('Intensity$_{t-1}$', 'Type$_{t-1}$', 'Duration$_{t-1}$', 'Area$_{t-1}$',
+otherCovars=c('Intensity$_{t-1}$', 'Duration$_{t-1}$', 'Area$_{t-1}$',
   'Number of conflicts$_{t-1}$',  
   'Upper Income', 'Ln(Inflation)$_{t-1}$', 'Democracy$_{t-1}$',
   'Resource Rents/GDP$_{t}$', 'World GDP Growth$_{t}$')
@@ -64,22 +67,20 @@ temp <- ggcoefplot(coefData=summary(mCity)$'coefficients',
     vars=na.omit(rownames(summary(mCity)$'coefficients')[2:100]), 
     varNames=vnames, Noylabel=FALSE, coordFlip=TRUE,
[…]

### 2014-10-09 LaTeX/RhodiumConcl.tex
Several minor changes to phrasing/spelling

@@
 
-This piece of research has sought to explain observed discrepencies in the economic impact of civil conflict.
-Violent intrastate conflicts have occured in one third of countries in just the past several decades.
+This piece of research has sought to explain observed discrepancies in the economic impact of civil conflict.
+Violent intrastate conflicts have occurred in one third of countries in just the past several decades.
 While civil wars seem to primarily afflict developing states, their actual economic impacts are still subject to debate.
@@
 While there is a large literature on natural resources and conflict at the state level, little work has disaggregated this data and explored the micro-relationship between conflict and resources.
-Future iterations of this paper will explore each of these hypotheses using geospatial data on the economic assets of interest.
+Future work in this line of inquiry will explore each of these hypotheses using geospatial data on the economic assets of interest.
 

### 2014-10-09 LaTeX/RhodiumEmp.tex
Several minor changes to phrasing/spelling

@@
 
-To construct a time-series cross-sectional database of urban centers, we turn to yearly editions of The World Almanac from 1989 to 2008.
+To construct a time-series cross-sectional database of urban centers, we turn to yearly editions of \emph{The World Almanac} from 1989 to 2008.
 More refined subnational data listing urban centers by their contribution to economic output would be the most direct way to test our hypothesis, however, cross-national data such as this over the time period of our analysis, especially for developing countries, is simply not available.
@@
 Using our geo-referenced conflict and urban center data, we proceed to compute the proximity of every civil armed conflict in a country-year from every urban center listed in that year.\footnote{Distances between centroid locations were computed using an iterative method of distance calculation proposed by \citet{vincenty:1975}.} Since our unit of analysis is the country-year, we aggregate the distance between conflicts and major cities by calculating the minimum logged distance any conflict is from a major city.
-For example, if a country faces, four conflicts in a year, the datapoint for that country-year would be the minimum distance any conflict centroid is from any city centroid.
-In addition, to identifying the minimum distance a conflict is from any city, we also create a variable measures that measures minimum distance of any conflict from the capital of the country.
+For example, if a country faces four conflicts in a year, the datapoint for that country-year would be the minimum distance any conflict centroid is from any city centroid.
+In addition to identifying the minimum distance a conflict is from any city, we also create a variable that measures minimum distance of any conflict from the capital of the country.
 Given the importance of cities as drivers of macroeconomic growth the proximity of conflict to even one city should have at least a noticeable short-term impact on growth.
@@
 Thus we estimate two separate models, one where we include the minimum distance from a conflict to the capital and the other where we include the minimum distance to any urban center.
-In addition, to the inclusion of our spatial proximity covariates we include a number of control measures to account for extant explanations of how civil war dynamics affect GDP growth and to mitigate against omitted variable bias.
+In addition to the inclusion of our spatial proximity covariates we include a number of control measures to account for extant explanations of how civil war dynamics affect GDP growth and to mitigate omitted variable bias.
 
@@
 
-Aggregating each of the PRIO conflict descriptive measures in this way is to help account for those countries in which conflicts are especially intense, cover large areas, have been long-lasting, and multiple conflicts are occurring.
+Aggregating each of the PRIO conflict descriptive measures in this way is to help account for those countries in which conflicts are especially intense, cover large areas, have been long-lasting, or are one of many ongoing conflicts.
 Given the findings in the extant literature, our expectation is that each of these measures should have a negative effect on economic growth.
@@
 	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t-1}) \;+\; \beta_{3}(Conflict \; Duration_{i,t-1}) \\
-	& \;+\; \beta_{4}(Ln(Conflict \; Area)_{i,t-1}) \;+\; \beta_{5}(Upper \; Income_{i,t}) \\	
+	& \;+\; \beta_{4}(Conflict \; Area_{i,t-1}) \;+\; \beta_{5}(Upper \; Income_{i,t}) \\	
 	& \;+\; \beta_{6}(Inflation_{i,t-1}) \;+\; \beta_{7}(Democracy_{i,t-1}) \\
@@
 		\label{fig:capCoef}} &
-		\subfloat[SubFigure 2][Any City]{
+		\subfloat[SubFigure 2][Any Major City]{
 			\resizebox{.45\textwidth}{!}{\input{mCityCoefPlot}}

### 2014-10-09 LaTeX/RhodiumIntro.tex
handing it back to ben
Several minor changes to phrasing/spelling

@@
+% Note to Ben: Can you check if the plot margins in the master rhodium.tex file are correct for JCR?
+
 \section{Introduction}
@@
 
-Understanding the effects of civil conflict has become an integral part of the study of economic development \citep{serneels:verpoorten:2013}.
+Understanding the effects of civil conflict has become an integral component of the study of economic development \citep{serneels:verpoorten:2013}.
 From a theoretical perspective there is little consensus about the impact that conflict has on economic performance.
@@
 
-Further few in the literature have sought to explain puzzling cases of domestic armed conflict having little impact on macroeconomic growth.
+Furthermore, few in the literature have sought to explain puzzling cases of domestic armed conflict having little impact on macroeconomic growth.
 Mexico, for example, has been engaged in a drug war since December 2006 and the number of deaths stemming from this civil conflict have only increased since that time.
-Yet, even as fatalities due to the drug war reached new peaks, in 2012, Vikram Pandit of Citigroup cited Mexico as being extremely well poised for growth and that its economy may surpass that of its much larger regional rival, Brazil, within a decade \citep{vardi:2012}.
-In that same year, Barron's ran a headline titled, ``Is Mexico the New China?'' \citep{kapadia:2012}.
-This contrasts greatly with the economic fortunes of other countries in the midst of civil war where economies have plumetted.
+Yet, even as fatalities due to the drug war reached new peaks, in 2012, Vikram Pandit of Citigroup cited Mexico as being extremely well poised for growth and projected that its economy may surpass that of its much larger regional rival, Brazil, within a decade \citep{vardi:2012}.
+In that same year, \emph{Barron's} ran a headline titled, ``Is Mexico the New China?'' \citep{kapadia:2012}.
+This contrasts greatly with the economic fortunes of other countries in the midst of civil war where economies have plummeted.
 \cite{collier:elliott:etal:2003}, for instance, describe civil war as ``development in reverse.'' ``The overall economic and political legacy from civil war,'' they write, ``is thus sufficiently adverse that rapid recovery is unlikely.''
@@
 
-Thus what happens when cities themselves are threatened?
+What happens when cities themselves are threatened?
 In this paper, we bridge the economic development literature on the importance of cities with extant literature on the effect of armed conflict to provide a novel explanation for the paradox of high macroeconomic growth in conflict ridden countries.
@@
 Much of the extant literature has focused on examining the effect of conflict on economic growth at the national level.
-The implicit assumption of these approaches is that all civil wars are alike, whether they be occurring right outside the capital or on the fringes of the country.
+The implicit assumption of these approaches is that all civil wars are alike, whether they occur right outside the capital or on the fringes of the country.
 We argue that the location of conflicts relative to major cities and capitals will determine the effect of civil conflict on economic performance, and that conflicts only significantly dampen economic performance if they are proximate to major population and economic centers.

### 2014-10-09 LaTeX/RhodiumLit.tex
ugh
Several minor changes to phrasing/spelling

@@
 Not only do several studies link civil war to domestic economic performance, there is also evidence that civil wars have regional economic consequences.
-\cite{murdoch:sandler:2002a} find some evidence that states neighboring civil war states are more likely to experience poor short-term economic performance.
+\cite{murdoch:sandler:2002a} find evidence that states neighboring civil war states are more likely to experience poor short-term economic performance.
 They attribute this effect to the disruption of trade and uncertainty about the potential for conflict to spread across the border.
@@
 
-% By brining this up I think we would need to say more about how exactly we sidestep this issue
-
 Much work has been done on the causal effects of economic performance on civil war.
 Indeed, there is likely an endogenous relationship between economic performance and civil war; each exacerbates the other.
-While our work here sidesteps this argument by focusing exclusively on observations of civil war, we will briefly review the relevant literature.
+While our work here sidesteps this argument by focusing exclusively on instances of civil war, we will briefly review the relevant literature.
 In a report for the World Bank by \cite{collier:etal:2003}, the authors describe what they term the \textit{conflict trap}.
-States that find themselves in the \textit{conflict trap} are those that have experienced civil war with, are subsequently affected by its economic and social consequences, and are therefore more likely to experience further civil conflict.
+States that find themselves in the \textit{conflict trap} are those that have experienced civil war, are subsequently affected by its economic and social consequences, and are therefore more likely to experience further civil conflict.
 During civil wars, resources are diverted from productive economic activity to destructive activity.
@@
 They find that rainfall is strongly correlated with income in sub-Saharan Africa, a region also prone to civil conflict in recent decades.
-Using a two-stage estimation approach, they find that rainfall, their exogenous instrument for income, is positively correlated with the likelihood of civil war.
+Using a two-stage estimation approach, they conclude income is correlated with the likelihood of civil war.
 
@@
 They operationalize this measure of dependence, or ``remoteness,'' as distance from a seaport.
-Indeed, they find that conflicts are more likley to arise near seaports following an economic shock than they are further away.
+Indeed, they find that conflicts are more likely to arise near seaports following an economic shock than they are further away.
 
@@
 These weaker groups are only able to survive in areas more distant from capitals.
-In our analysis, we control for the intensity and duration of conflict to account for this confound.
+In our analysis, we control for the intensity and duration of conflict to account for this potential confound.

### 2014-10-09 LaTeX/RhodiumTheory.tex
handing it back to ben
Several minor changes to phrasing/spelling

@@
+% Note to Ben: Should we have a capital city and any city hypothesis?
+
 \section{Spatial Distribution of Cities and Violence}
@@
 Most notably, \citeauthor{krugman:1991a} in his seminal 1991 article, ``Increasing Returns and Economic Geography'', convincingly showed the importance of studying economic outcomes within a spatial context.
-A key finding of Krugman's work into economic geography has been the importance of agglomeration effects, the idea that ``activities tend to cluster where markets are large and markets become larger there where activities cluster'' \citep{krugman:1997}.
+A key finding of Krugman's work into economic geography has been the importance of agglomeration effects, the idea that ``activities tend to cluster where markets are large and markets become larger where activities cluster'' \citep{krugman:1997}.
 \citet{henderson:2000} provides empirical evidence for why these agglomeration effects would manifest by showing that spatial clustering promotes economic efficiency in a variety of ways from simply enabling savings in transport costs to more efficiently functioning labor markets.
@@
 The econometric evidence on the importance of cities has crucial implications for our understanding of the spatial structure of subnational economies.
-Namely, at the subnational level the economy can be thought of as consisting of ``lumps'' of productivity and swaths of areas that contribute little to macroeconomic growth \citep{venables:2005}.
+Specifically, at the subnational level, the economy can be thought of as consisting of ``lumps'' of productivity and swaths of areas that contribute little to macroeconomic growth \citep{venables:2005}.
 This implies that subnational conflicts will have heterogeneous effects on economic growth given their spatial proximity to economically relevant centers such as cities.
@@
 \cite{beittel:2011} writes in 2011 that ``drug trafficking-related killings remain concentrated in a relatively few cities.''
+
+% Note to Ben: If you have more to add about Mexico here that might be good

### 2014-10-10 LaTeX/RhodiumIntro.tex
Fixed citation format.

@@
 This contrasts greatly with the economic fortunes of other countries in the midst of civil war where economies have plummeted.
-\cite{collier:elliott:etal:2003}, for instance, describe civil war as ``development in reverse.'' ``The overall economic and political legacy from civil war,'' they write, ``is thus sufficiently adverse that rapid recovery is unlikely.''
+\citet{collier:elliott:etal:2003}, for instance, describe civil war as ``development in reverse.'' ``The overall economic and political legacy from civil war,'' they write, ``is thus sufficiently adverse that rapid recovery is unlikely.''
 

### 2014-10-10 LaTeX/RhodiumLit.tex
Fixed citation format.

@@
-\subsection{Extant Literature on Conflict and Growth}
+\section{Literature on Conflict and Growth}
 \label{lit}
 
-\subsubsection{Civil War $\rightarrow$ Economic Performance}
+\subsection{Civil War $\rightarrow$ Economic Performance}
 
@@
 
-Instead of disaggregating economic outcomes, \cite{imai:weinstein:2000} instead disaggregate conflict itself.
+Instead of disaggregating economic outcomes, \citet{imai:weinstein:2000} instead disaggregate conflict itself.
 They distinguish between those conflicts that cover larger or smaller geographic areas and hypothesize that larger conflicts (in terms of geographical spread) will result in worse economic performance.
@@
 That civil wars negatively impact economic performance, while in line with the ``war ruin'' hypothesis, runs counter to the ``war renewal'' hypothesis.
-Some scholars have argued that wars, international wars in particular, can spur economic development\footnote{For a review of this discussion, see \cite{rasler:thompson:1985}}.
+Some scholars have argued that wars, international wars in particular, can spur economic development\footnote{For a review of this discussion, see \citet{rasler:thompson:1985}}.
 The prevailing wisdom with regard to civil war, however, is that outcomes of this nature are the exception rather than the rule.
-In a test of economic and social determinants of post-conflict recovery in the context of civil war, \cite{kang:meernik:2005} find that these conflicts can lead, under different conditions, to either rapid or stagnant economic recovery.
+In a test of economic and social determinants of post-conflict recovery in the context of civil war, \citet{kang:meernik:2005} find that these conflicts can lead, under different conditions, to either rapid or stagnant economic recovery.
 They conclude that the long-term economic impacts of civil war are largely dependent on post-war governance and foreign assistance.
@@
 Not only do several studies link civil war to domestic economic performance, there is also evidence that civil wars have regional economic consequences.
-\cite{murdoch:sandler:2002a} find evidence that states neighboring civil war states are more likely to experience poor short-term economic performance.
+\citet{murdoch:sandler:2002a} find evidence that states neighboring civil war states are more likely to experience poor short-term economic performance.
 They attribute this effect to the disruption of trade and uncertainty about the potential for conflict to spread across the border.
-In a follow up study, \cite{murdoch:sandler:2002b} suggest that the spatial dispersion of economic effects from civil conflict differ from region to region.
+In a follow up study, \citet{murdoch:sandler:2002b} suggest that the spatial dispersion of economic effects from civil conflict differ from region to region.
 
-\subsubsection{Economic Performance $\rightarrow$ Civil War}
+\subsection{Economic Performance $\rightarrow$ Civil War}
 
@@
 While our work here sidesteps this argument by focusing exclusively on instances of civil war, we will briefly review the relevant literature.
-In a report for the World Bank by \cite{collier:etal:2003}, the authors describe what they term the \textit{conflict trap}.
+In a report for the World Bank by \citet{collier:etal:2003}, the authors describe what they term the \textit{conflict trap}.
 States that find themselves in the \textit{conflict trap} are those that have experienced civil war, are subsequently affected by its economic and social consequences, and are therefore more likely to experience further civil conflict.
@@
 
-In accordance with this theory, \cite{fearon:laitin:2003} argue that poor economic growth is the primary condition conducive for civil war.
+In accordance with this theory, \citet{fearon:laitin:2003} argue that poor economic growth is the primary condition conducive for civil war.
 More specifically, they believe that strong economic growth proxies for robust governance and that states with low GDP growth likely have infrastructures that are unable to implement counter-insurgent policies.
-In an effort to parse out the causal effect of economic growth shocks on civil war, \cite{miguel:etal:2004} instrument income growth with rainfall.
+In an effort to parse out the causal effect of economic growth shocks on civil war, \citet{miguel:etal:2004} instrument income growth with rainfall.
 They find that rainfall is strongly correlated with income in sub-Saharan Africa, a region also prone to civil conflict in recent decades.
@@
 
-\subsubsection{Disaggregating Civil Wars}
+\subsection{Disaggregating Civil Wars}
 
@@
 New data allows researchers to focus on how the geography of internal conflict varies.
-\cite{pierskalla:hollenbach:2013} use subnational data on African states to asses the role cell phone coverage plays in facilitating violent conflict.
+\citet{pierskalla:hollenbach:2013} use subnational data on African states to asses the role cell phone coverage plays in facilitating violent conflict.
 They theorize that cell phone coverage will enhance the collective action capabilities of rebel groups by improving coordination, communication, and in-group monitoring.
@@
 
-\cite{berman:couttenier:2013} explore another sub-state determinant of civil conflict.
-Recognizing that economic shocks are associated with changes to the probability of civil conflict,\footnote{For more, see \cite{miguel:etal:2004} and \cite{dube:vargas:2013}.} they seek to determine where conflict will emerge when these shocks occur.
+\citet{berman:couttenier:2013} explore another sub-state determinant of civil conflict.
+Recognizing that economic shocks are associated with changes to the probability of civil conflict,\footnote{For more, see \citet{miguel:etal:2004} and \citet{dube:vargas:2013}.} they seek to determine where conflict will emerge when these shocks occur.
 Given an external economic shock in a trading partner, Berman and Couttenier expect that states should be at an increased risk of experiencing conflict.
@@
 
-\cite{buhaug:2010} argues that the geography of conflict is a function of rebel strength.
+\citet{buhaug:2010} argues that the geography of conflict is a function of rebel strength.
 In particular, strong rebel groups are able to conduct military operations near capital cities while weak ones are not.

### 2014-10-10 LaTeX/RhodiumTheory.tex
Fixed citation format.

@@
 
-\cite{glaeser:shapiro:2002} discuss the historic role of cities in warfare and their current role with respect to terrorism.
+\citet{glaeser:shapiro:2002} discuss the historic role of cities in warfare and their current role with respect to terrorism.
 Cities, they argue, once provided safe haven in the midst of conflict; defense of a concentrated population is easier than defense of a dispersed population.
@@
 By targeting economic centers and resource infrastructure, FARC can strain Colombia's economy, frighten investors, and bolster support from poor and rural workers sensitive to wealth disparity in the country.
-\cite{rabasa:chalk:2001} identify a three-pronged strategy pursued by FARC in the 1990s: to consolidate power in coca-growing regions, to conduct military operations in economically valuable areas, and to isolate major cities from the rest of the country by limiting communication and travel between them.
+\citet{rabasa:chalk:2001} identify a three-pronged strategy pursued by FARC in the 1990s: to consolidate power in coca-growing regions, to conduct military operations in economically valuable areas, and to isolate major cities from the rest of the country by limiting communication and travel between them.
 
@@
 For much of this time, the cartel violence generally occurred in rural areas along drug trafficking routes and not within major cities.
-\cite{beittel:2011} writes in 2011 that ``drug trafficking-related killings remain concentrated in a relatively few cities.''
+\citet{beittel:2011} writes in 2011 that ``drug trafficking-related killings remain concentrated in a relatively few cities.''
 

### 2014-10-10 LaTeX/Abstract.tex
More changes.

@@
 % Version submitted to MPSA:
-Within the conflict literature there has been much disagreement about the relationship between civil wars, natural resources, and state economic performance.
-We find that this disagreement results from not accounting for the spatial disaggregation of conflict events within a country.
-Our hypothesis is that the economic impact of civil conflict is contingent on the conflict's location relative to major economic and labor resources within a state.
-We use subnational data on the spatial distribution of conflict, resources, and infrastructure to test the long-term impact of domestic conflict on state economic performance.
-To estimate the spatial distribution of conflict we use data from the PRIO Armed Conflict Location and Event Data.
-We combine the conflict location data with geospatial data on economic centers, natural resource locations, and infrastructure grids to generate spatial variables that approximate how far each conflict is from centers of interest.
-We then estimate the effect of the spatial variables on economic performance.
+Within the conflict literature there has been much disagreement about the relationship between civil wars and state economic performance.
+While civil war is often associated with poor economic performance, some states have managed to weather domestic armed conflict during periods of robust growth.
+We find that this disagreement results from not accounting for the spatial distribution of conflict within a country.
+Literature in economics has recently stressed the importance of major cities to development and economic growth.
+We hypothesize that the economic impact of civil conflict is contingent on the conflict's location relative to major urban centers within a state.
+We use subnational data on the location of conflict relative to urban areas to test the impact of domestic conflict on annual GDP growth.
+In doing so, we bridge the economic development literature on the importance of cities with extant literature on the effect of armed conflict to provide a novel explanation for the paradox of high macroeconomic growth in conflict ridden countries.
 By doing so, we are able to resolve tensions in the literature regarding the relationship between economic performance and civil wars.
+We find that the proximity of civil war to major urban centers is negatively correlated with economic growth and use simulations to show that the estimated marginal effect of civil war proximity can mean the difference between robust growth and stagnation.

### 2014-10-10 LaTeX/RhodiumEmp.tex
More changes.

@@
 This dataset contains information on the geographical centers of armed conflict events and the area covered by each conflict at a yearly level from 1989 to 2008.
-In recent years, other geo-referenced datasets have been developed that go beyond just providing information on conflict centroids and area to providing an actual spatial grid structure through which to conduct analysis (e.g., \citealt{tollefsen:etal:2012}).
-For the purpose of this analysis, however, we deliberately avoid using these datasets since our primary interest is in examining variation in changes to GDP growth due to the proximity of conflict to urban centers.
+In recent years, other geo-referenced datasets have been developed that go beyond just providing information on conflict centroids and area to providing an actual spatial grid structure through which to conduct analysis \citep{tollefsen:etal:2012}.
+However, these data are not available globally and would therefore unnecessarily limit the external validity of the current analysis.
+Other machine coded event datasets, while providing detailed coverage of events on a global scale, often approximate event locations based on descriptors in the source material or by the location of the reporting news agency itself.
+Because the location of conflict is critical for this analysis, the urban bias of disaggregated event data is unacceptable.
+For the purpose of this analysis, we deliberately avoid using these datasets since our primary interest is in examining variation in changes to GDP growth at a national level.
 
-% Note to Ben: Does that sound convincing?
-Probably not.
-The point that I'm trying to get across is that using the gridded data is not at the appropriate level of analysis.
-We need to say something here about this so if you can think of something better that'd be great.
-
-To construct a time-series cross-sectional database of urban centers, we turn to yearly editions of \emph{The World Almanac} from 1989 to 2008.
+To construct a time-series cross-sectional database of urban centers, we turn to yearly editions of \citet{worldalmanac:1989}.
 More refined subnational data listing urban centers by their contribution to economic output would be the most direct way to test our hypothesis, however, cross-national data such as this over the time period of our analysis, especially for developing countries, is simply not available.
-The World Alamanac lists the major cities in a country by population, thus providing us with a second best approximation of the urban centers that are most relevant for a particular national economy.
-Typically, the Almanacs list at least three major cities, including the capital, for each country and year from 1989 to 2008.
-We use the top five major cities listed for each country and then determine their geographical centers.
+\emph{The World Alamanac} lists the major cities in a country by population, thus providing us with a second best approximation of the urban centers that are most relevant for a particular national economy.
+Typically, the \emph{Almanacs} list at least three major cities, including the capital, for each country and year from 1989 to 2008.
+Because the \emph{Almanacs} are not perfectly consistent from year to year, we opted to code cities with a five year rolling window.
+That is, cities listed in the 1995 \emph{Almanac} are also included in our dataset for years 1993-1997.
+In doing so, we hope to minimize the effect of coding inconsistencies on the part of \emph{The World Almanac}.
 
@@
 % Note to Ben: Does empirical model sound weird?
+% Note to Shahryar: It sounds a lot better than "theory."
 
@@
 From the PRIO Armed Conflict dataset we bring in additional information about conflict intensity, duration, the area covered by the conflict, and the number of conflicts \citep{themner:wallensteen:2014}.
-Conflict intensity is a binary that distinguishes between minor armed conflicts and wars, and we set this equal to one if any of the conflicts in a country year were classified as a war and zero if not.
+Conflict intensity is a binary that distinguishes between minor armed conflicts (between 25 and 999 annual battle deaths) and wars (at least 1000 annual battle deaths), and we set this equal to one if any of the conflicts in a country year were classified as a war and zero if not.
 In aggregating conflict duration to the country year level, we bring in the duration (measured in years) of the longest lasting conflict by a certain country-year.
@@
 This is a particularly important variable to control for as countries that draw a large share of their GDP from natural resource rents likely rely less on urban centers to serve as drivers of growth.
-Finally, given that the timeframe of our sample overlaps with the occurence of two major global crises, we add a control for the average GDP growth across all countries in the world.
+Finally, given that the timeframe of our sample overlaps with the occurrence of two major global economic crises, the 1997 Asian financial crisis and the 2008 financial crisis, we add a control for the average GDP growth across all countries in the world.
 
 % Note to Ben: Anything else to add about why including polity would be important in the model?
+% Note to Shahryar: Nope.
 
@@
 	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t-1}) \;+\; \beta_{3}(Conflict \; Duration_{i,t-1}) \\
-	& \;+\; \beta_{4}(Conflict \; Area_{i,t-1}) \;+\; \beta_{5}(Upper \; Income_{i,t}) \\	
-	& \;+\; \beta_{6}(Inflation_{i,t-1}) \;+\; \beta_{7}(Democracy_{i,t-1}) \\
-	& \;+\; \beta_{8}(Resource \; Rents/GDP_{t-1}) \;+\; \beta_{9}(World \; GDP \; Growth_{t}) \\
+	& \;+\; \beta_{4}(Conflict \; Area_{i,t-1} \;/\; Land \; Area_{i,t-1}) \\
+	& \;+\; \beta_{5}(Number \; of \; Conflicts_{i,t-1}) \;+\; \beta_{6}(Upper \; Income_{i,t}) \\	
+	& \;+\; \beta_{7}(Inflation_{i,t-1}) \;+\; \beta_{8}(Democracy_{i,t-1}) \\
+	& \;+\; \beta_{9}(Resource \; Rents/GDP_{t-1}) \;+\; \beta_{10}(World \; GDP \; Growth_{t}) \\
 	& \;+\; \mu_{i,t} \;+\; \epsilon_{i,t}
@@
 This analysis helps us to understand whether some of the subsets in our dataset follow a different pattern than what is in the broader set \citep{beck2008time}.
-To conduct the cross-validation, we randomly split the 68 country observations in our dataset into six approximately equal subsets.
+To conduct the cross-validation, we randomly split the 68 country observations in our dataset into seven approximately equal subsets.
 Each subset ends up containing a minimum of approximately 65 cases.

### 2014-10-10 LaTeX/RhodiumIntro.tex
More changes.

@@
 In this paper, we bridge the economic development literature on the importance of cities with extant literature on the effect of armed conflict to provide a novel explanation for the paradox of high macroeconomic growth in conflict ridden countries.
-Specifically,  we argue that to explain variation in economic performance between countries in the midst of civil war, it is necessary to account for the spatial location of the conflict relative to major population and economic centers.
+Specifically, we argue that to explain variation in economic performance between countries in the midst of civil war, it is necessary to account for the spatial location of the conflict relative to major urban centers.
 Much of the extant literature has focused on examining the effect of conflict on economic growth at the national level.
 The implicit assumption of these approaches is that all civil wars are alike, whether they occur right outside the capital or on the fringes of the country.
-We argue that the location of conflicts relative to major cities and capitals will determine the effect of civil conflict on economic performance, and that conflicts only significantly dampen economic performance if they are proximate to major population and economic centers.
+We argue that the location of conflicts relative to major cities and capitals will determine the effect of civil conflict on economic performance, and that conflicts only significantly dampen economic performance if they are proximate to urban centers.
 

### 2014-10-11 LaTeX/RhodiumEmp.tex
Fixed Mexico description.

@@
 In doing so, we hope to minimize the effect of coding inconsistencies on the part of \emph{The World Almanac}.
+Also, as a more conservative test of our hypothesis, we replicate our models using the distance of conflict from each capital city rather than our preferred measure of minimum distance to a major urban center.
+While our hypothesis is most accurately represented by distance from any major urban centers, distance from capital cities provides an appealing and consistent alternative measure.
+Every country has a capital city in our sample, so using this alternative measure does not rely on differing population or density thresholds across countries that must be used in coding major cities.
 

### 2014-10-11 LaTeX/RhodiumTheory.tex
More changes.
Fixed Mexico description.

@@
 
-That cities are central to the development of national economic performance is well supported in literature on the role urban centers play in national economies.
+That cities are central to national economic performance is well supported in the relevant literature.
 \citet{myrdal:sitohang:1957} were among the first to argue that once cities reach a certain size through the process of urbanization, they tend to become self-reinforcing growth centers through a process Myrdal termed as ``cumulative causation''.
@@
 
+While this project is motivated, in part, by the current conflict in Mexico, it is important to note that this case does not appear in the civil war dataset chosen for this study.
+The UCDP definition of civil war requires that the conflict be fought over an ``incompatibility that concerns government and/or territory,'' a criteria not strictly met by the organized crime violence experienced by the country.
+Nonetheless, we want to reiterate that this instance of armed conflict, of the magnitude typically associated with civil war, conforms to the expectations of our theory.
 Mexico, now nearly a decade into a violent and complicated conflict between several organized criminal enterprises and the federal government, has maintained healthy economic performance.
 For much of this time, the cartel violence generally occurred in rural areas along drug trafficking routes and not within major cities.
-\citet{beittel:2011} writes in 2011 that ``drug trafficking-related killings remain concentrated in a relatively few cities.''
+\citet{beittel:2011} writes in 2011 that ``drug trafficking-related killings remain concentrated in a relatively few cities.'' Meanwhile, several majors cities including the capital, Mexico City, have experienced relatively low levels of cartel violence.
 

### 2014-10-11 LaTeX/RhodiumTheory.tex
added citation to UCDP codebook, changed mexico

@@
 While this project is motivated, in part, by the current conflict in Mexico, it is important to note that this case does not appear in the civil war dataset chosen for this study.
-The UCDP definition of civil war requires that the conflict be fought over an ``incompatibility that concerns government and/or territory,'' a criteria not strictly met by the organized crime violence experienced by the country.
+The UCDP definition of civil war requires that the conflict be fought over an ``incompatibility that concerns government and/or territory,'' a criteria not strictly met by the organized crime violence experienced by the country\citep[p.1]{themner:2014}.
 Nonetheless, we want to reiterate that this instance of armed conflict, of the magnitude typically associated with civil war, conforms to the expectations of our theory.

### 2014-10-13 R/Analysis/conflictMaps.R
fixed errors in compiler

@@ -51,7 +51,7 @@ temp = temp + theme(
   panel.grid.major=element_blank(), 
   panel.grid.minor=element_blank(), panel.border=element_blank())
 temp
-setwd(pathTex)
+setwd(pathGraphics)
 # pdf(file=paste0(tolower(cname),'Map.pdf'), width=5, height=7)
 # temp
 # dev.off()

### 2014-10-13 R/Analysis/descStats.R

@@ -35,7 +35,7 @@ tmp=tmp + theme( axis.title.y=element_text(vjust=1),
   axis.ticks=element_blank(),legend.position='none',
   panel.grid.major=element_blank(), panel.grid.minor=element_blank() )
 tmp
-setwd(pathTex)
+setwd(pathGraphics)
 # tikz(file='distGdp.tex', width=7, height=4, standAlone=FALSE)
 # tmp
 # dev.off()
@@ -63,7 +63,7 @@ noConfCntries=setdiff(Wcntries, cntries)
 mapColors=rep('white',length(Wcntries))
 mapColors[which(Wcntries %in% noConfCntries)] = 'grey'
 
-setwd(pathTex)
+setwd(pathGraphics)
 # pdf(file='CityConfMap.pdf', width=12, height=6)
 plot(worldmap, col=mapColors)
 points(fYrCty$cleanLong, fYrCty$cleanLat, col='blue', pch=18, cex=0.5)

### 2014-10-13 R/Analysis/models.R

@@ -67,7 +67,7 @@ temp <- ggcoefplot(coefData=summary(mCity)$'coefficients',
     vars=na.omit(rownames(summary(mCity)$'coefficients')[2:100]), 
     varNames=vnames, Noylabel=FALSE, coordFlip=TRUE,
     colorGrey=FALSE, grSTA=0.5, grEND=0.1)
-setwd(pathTex)
+setwd(pathGraphics)
 if(genTikz){ tikz(file='mCityCoefPlot.tex', width=4, height=6, standAlone=F)}
 temp
 if(genTikz){ dev.off() }
@@ -77,7 +77,7 @@ temp <- ggcoefplot(coefData=summary(mCap)$'coefficients',
     vars=na.omit(rownames(summary(mCap)$'coefficients')[2:100]), 
     varNames=vnames, Noylabel=FALSE, coordFlip=TRUE,
     colorGrey=FALSE, grSTA=0.5, grEND=0.1)
-setwd(pathTex)
+setwd(pathGraphics)
 if(genTikz){ tikz(file='mCapCoefPlot.tex', width=4, height=6, standAlone=F)}
 temp
 if(genTikz){ dev.off() }
@@ -93,7 +93,7 @@ temp = ggsimplot(modelResults=mCity, sims=10000, simData=modData,
   specX=TRUE, ggxbreaks=seq(-1,7,1), plotType='ribbon'
   )
 temp=temp + theme(axis.title.y=element_text(vjust=1))
-setwd(pathTex)
+setwd(pathGraphics)
 if(genTikz){ tikz(file='mCitySimPlot.tex', width=6, height=4, standAlone=F)}
 temp
 if(genTikz){ dev.off() }
@@ -105,7 +105,7 @@ temp = ggsimplot(modelResults=mCap, sims=10000, simData=modData,
   specX=TRUE, ggxbreaks=seq(-1,7,1), plotType='ribbon'
   )
 temp=temp + theme(axis.title.y=element_text(vjust=1))
-setwd(pathTex)
+setwd(pathGraphics)
 if(genTikz){ tikz(file='mCapSimPlot.tex', width=6, height=4, standAlone=F)}
 temp
 if(genTikz){ dev.off() }
@@ -155,7 +155,7 @@ temp=temp + theme(axis.title.y=element_text(vjust=1),
   legend.position='none', legend.title=element_blank(),
[…]

### 2014-10-13 R/setup.R

@@ -5,19 +5,16 @@ rm(list=ls())
 if(Sys.info()["user"]=="janus829")
 {pathMain="~/Desktop/Research/Rhodium/R";
 	pathData='~/Dropbox/Research/Rhodium/Data/';
-	pathGraphics="~/Dropbox/Research/Rhodium/Graphics";
-	pathTex="~/Desktop/Research/Rhodium/LaTeX"}
+	pathGraphics="~/Dropbox/Research/Rhodium/Graphics"}
 
 if(Sys.info()["user"]=="s7m")
 {pathMain="~/Research/Rhodium/R";
   pathData='~/Dropbox/Research/Rhodium/Data/';
-  pathGraphics="~/Dropbox/Research/Rhodium/Graphics";
-  pathTex="~/Research/Rhodium/LaTeX"}
+  pathGraphics="~/Dropbox/Research/Rhodium/Graphics"}
 
 # Setting working directory
 if(Sys.info()["user"]=="Ben")
 {pathMain="/Users/Ben/Github/Rhodium/R";
-pathTex="/Users/Ben/Github/Rhodium/LaTeX";
  pathGraphics="/Users/Ben/Dropbox/Rhodium/Graphics";
  pathData="/Users/Ben/Dropbox/Rhodium/Data"
 }

### 2014-10-28 LaTeX/RhodiumConcl.tex
Fixed citation format.
forgot to commit pre sub files

@@
 Despite this heterogeneity observed among civil war states, the individual characteristics of civil conflict that lead to disparate outcomes have only recently been subject to academic scrutiny.
-In this first step of a larger project to distinguish the geography of civil conflict, we hope to have contributed to our understanding of why some civil conflicts impact economic performance more severely than others.
-We have used a novel approach in the study of civil conflict to distinguish between spatially dissimilar events and shown that this new measure of interest, the minimum distance between conflict epicenters and major population centers, is a substantive determinant of economic growth.
+In this first step of a larger project to distinguish the geography of civil conflict, we have contributed to our understanding of why some civil conflicts impact economic performance more severely than others.
+To do this, we have used a novel approach in the study of civil conflict to distinguish between spatially dissimilar events and shown that this new measure of interest, the minimum distance between conflict epicenters and major population centers, is a substantive determinant of economic growth.
 While the proximity of conflict to major cities helps us to better understand how domestic armed conflict produces disparate economic outcomes across countries, one can imagine a number of other hypotheses that derive from this research.
@@
 Resources and population centers that are near the border between a peaceful state and a civil war state may be impacted in the same way that resources and cities within the conflict state are.
-This may help to explain the disparate regional economic effects of civil war observed by \cite{murdoch:sandler:2002b}.
+This may help to explain the disparate regional economic effects of civil war observed by \citet{murdoch:sandler:2002b}.

### 2014-10-28 LaTeX/RhodiumEmp.tex
fixed errors in compiler
forgot to commit pre sub files

@@
 
-% Note to Ben: Again if you could add anything to why The World Alamanac data is the right choice that would be great.
-
 In figure \ref{fig:CityConfMap}, we show the geographic distribution of conflicts and cities.
@@
 	\centering
-	\resizebox{.8\textwidth}{!}{\input{distGdp}}
+	\resizebox{.8\textwidth}{!}{\input{distGdp.tex}}
 	\caption{Average percent change in GDP growth at time $t$ by distance from conflict to capital city on rightmost panel at time $t-1$, and from conflict to any city on the leftmost.
@@
 \subsection{Empirical Model}
-
-% Note to Ben: Does empirical model sound weird?
-% Note to Shahryar: It sounds a lot better than "theory."
 
@@
 The results across the two models are broadly consistent, so we will discuss them in tandem.
+Surprisingly, conflict duration and the number of conflicts a country is facing do not relate to GDP growth in the direction that we expected.
 The intensity of a conflict aligns in the direction that we would expect though its effect is marginal.
 Additionally, the effect of having a high proportion of a country's land area immersed in conflict is sharply negative and aligns with the findings in the extant literature.
-Surprisingly, conflict duration and the number of conflicts a country is facing do not relate to GDP growth in the direction that we expected.
 As expected, inflation has a sharp negative effect on GDP growth.
@@
 Turning to our hypothesis, we find strong support for the argument that spatial proximity of conflict to either a capital city or any major urban center is associated with lower levels of GDP growth.
-The positive coefficient on the logged, minimum conflict distance variables indicates that conflicts closer to major cities has an adverse effect on economic growth.
+The positive coefficient on the logged, minimum conflict distance variables indicates that conflicts closer to major cities have an adverse effect on economic growth.
 
@@
 		\subfloat[SubFigure 1][Capital City]{
-			\resizebox{.45\textwidth}{!}{\input{mCapCoefPlot}}
+			\resizebox{.45\textwidth}{!}{\input{mCapCoefPlot.tex}}
 		\label{fig:capCoef}} &
 		\subfloat[SubFigure 2][Any Major City]{
-			\resizebox{.45\textwidth}{!}{\input{mCityCoefPlot}}
+			\resizebox{.45\textwidth}{!}{\input{mCityCoefPlot.tex}}
 		\label{fig:cityCoef}}
@@
 	\centering
-	\resizebox{.8\textwidth}{!}{\input{crossValPlot}}
+	\resizebox{.8\textwidth}{!}{\input{crossValPlot.tex}}
 	\caption{Each line here in the left panel shows the coefficient estimate of $Ln(Min.
@@
 \end{figure}
-
-% Note from Ben: I think we should leave the rmse plot out because we cant hope to actually predict gdp growth with this model setup.
-But we've done plenty of other important things with checking that our parameter estimates are somewhat substantive and stable, so I'm happy.
-That's why I've commented it out for now.
-If you want to put it back in feel free.
-If you do though, you do have to say something about the RMSE still being pretty damn high.
-
-% \begin{figure}
-% 	\centering
-% 	\resizebox{.8\textwidth}{!}{\input{rmseInOut}}
-% 	\caption{In and out of sample performance.}
-% 	\label{fig:rmsePlot}
-% \end{figure}
 
@@
 		\subfloat[SubFigure 1][Capital City]{
-			\resizebox{.7\textwidth}{!}{\input{mCapSimPlot}}
+			\resizebox{.7\textwidth}{!}{\input{mCapSimPlot.tex}}
 		\label{fig:capSim}} \\
 		\subfloat[SubFigure 2][Any City]{
-			\resizebox{.7\textwidth}{!}{\input{mCitySimPlot}}
+			\resizebox{.7\textwidth}{!}{\input{mCitySimPlot.tex}}
 		\label{fig:citySim}}

### 2014-10-28 LaTeX/RhodiumIntro.tex
forgot to commit pre sub files

@@
 
-Furthermore, few in the literature have sought to explain puzzling cases of domestic armed conflict having little impact on macroeconomic growth.
+Further few in the literature have sought to explain puzzling cases of domestic armed conflict having little impact on macroeconomic growth.
 Mexico, for example, has been engaged in a drug war since December 2006 and the number of deaths stemming from this civil conflict have only increased since that time.
@@
 \citet{henderson:2000} finds that even a simple correlation across countries between the level of urbanization and GDP per capita is greater than 0.8.
-The key theme in this literature on economic development is that the spatial positioning of production is a central process through which economic prosperity is created \citep{krugman:1991}.
+The key theme in this literature is that the spatial positioning of production is a central process through which economic prosperity is created \citep{krugman:1991}.
+
+% The importance of urbanization to economic growth has substantive implications for the conditions in which domestic armed conflict is likely to adversely impact macroeconomic growth.
 

### 2014-10-28 LaTeX/RhodiumLit.tex
forgot to commit pre sub files

@@
 
-\cite{collier:1999} identifies five avenues through which civil conflict can impede economic performance: through the \textit{destruction} of resources, through \textit{disruption} of social and economic activity, through \textit{diversion} of resources to the war effort, through \textit{dissaving}, and through \textit{portfolio substition} or divestment.
+\citet{collier:1999} identifies five avenues through which civil conflict can impede economic performance: through the \textit{destruction} of resources, through \textit{disruption} of social and economic activity, through \textit{diversion} of resources to the war effort, through \textit{dissaving}, and through \textit{portfolio substition} or divestment.
 Of course, these mechanisms are related to one another; portfolio substitution may be exacerbated by the destruction of resources or the disruption of socioeconomic activity.
@@
 Much work has been done on the causal effects of economic performance on civil war.
-Indeed, there is likely an endogenous relationship between economic performance and civil war; each exacerbates the other.
+Indeed, there is likely an endogenous relationship between economic performance and civil war.
 While our work here sidesteps this argument by focusing exclusively on instances of civil war, we will briefly review the relevant literature.

### 2014-10-28 LaTeX/RhodiumTheory.tex
forgot to commit pre sub files

--- 2014-10-11 LaTeX/RhodiumTheory.tex
@@
 Most notably, \citeauthor{krugman:1991a} in his seminal 1991 article, ``Increasing Returns and Economic Geography'', convincingly showed the importance of studying economic outcomes within a spatial context.
-A key finding of Krugman's work into economic geography has been the importance of agglomeration effects, the idea that ``activities tend to cluster where markets are large and markets become larger where activities cluster'' \citep{krugman:1997}.
+A key finding of Krugman's work on economic geography has been the importance of agglomeration effects, the idea that ``activities tend to cluster where markets are large and markets become larger where activities cluster'' \citep{krugman:1997}.
 \citet{henderson:2000} provides empirical evidence for why these agglomeration effects would manifest by showing that spatial clustering promotes economic efficiency in a variety of ways from simply enabling savings in transport costs to more efficiently functioning labor markets.
@@
 
-While this project is motivated, in part, by the current conflict in Mexico, it is important to note that this case does not appear in the civil war dataset chosen for this study.
-The UCDP definition of civil war requires that the conflict be fought over an ``incompatibility that concerns government and/or territory,'' a criteria not strictly met by the organized crime violence experienced by the country.
+It is important to note that Mexico does not appear in the civil war dataset chosen for this study.
+The UCDP definition of civil war requires that the conflict be fought over an ``incompatibility that concerns government and/or territory,'' a criteria not strictly met by the organized crime violence experienced by the country \citep[p.1]{themner:2014}.
 Nonetheless, we want to reiterate that this instance of armed conflict, of the magnitude typically associated with civil war, conforms to the expectations of our theory.

### 2014-10-28 LaTeX/coverLetter/coverLetter.tex
forgot to commit pre sub files

\documentclass[letterpaper]{article}
\usepackage{graphicx,fullpage}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}
\thispagestyle{empty}

  \begin{minipage}{0.64\linewidth}
Shahryar Minhas \\
Department of Political Science \\
Duke University \\
140 Science Drive, 208 Gross Hall \\
Durham, NC, 27708\\
United States
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{lr}
    Phone: & (248) 675-7345 \\
    Fax: & (919) 660-4330\\
    Email: & \href{mailto:shahryar.minhas@duke.edu}{\tt shahryar.minhas@duke.edu} 
    % Website:& \href{http://sites.google.com/site/nilsmetternich/}{\tt ucl.ac.uk/spp/people}
  \end{tabular}
\end{minipage}

\vspace{1.5in}

{Editorial Team of the Journal of Conflict Resolution via submission portal}

\vspace{0.5in}

Dear Colleagues:\\[1ex]

This letter accompanies our submission of a manuscript for your consideration. The manuscript ``Enemy at the Gates: Variation in Economic Growth from Civil Conflict'' applies a subnational spatial analysis to explain variation in macroeconomic performance amongst countries experiencing intrastate conflict. Our theoretical argument, bridges the economic development literature on the importance of cities with extant literature on the effect of armed conflict to provide a novel explanation for the paradox of high macroeconomic growth in conflict ridden countries. We think this is a very timely topic and an important contribution to an ongoing debate about the economic effects of instrastate conflict.\\[1ex]

We look forward to your evaluation of this paper.\\[1ex]

Respectfully submitted,

\vspace{.1in}

\includegraphics [scale=.8]{/Users/janus829/Dropbox/Finances/signature.png}

\vskip 0.5in
\hrule

\end{document}\bye

### 2015-04-17 LaTeX/Presentation/PreezeText.tex
preeze updates

--- 2014-04-02 LaTeX/PreezeText.tex
@@
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{frame}
+% \titlepage
+% \end{frame}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}
-\titlepage
+\frametitle{Motivating Question}
+
+High variation in economic performance between countries in the midst of internal armed conflict
+
+\begin{itemize}
+\item Mexico
+\item India
+\item Nicaragua
+\end{itemize}
+
 \end{frame}
@@
 \begin{frame}
-\frametitle{Motivating Question}
+\frametitle{Melding of Literatures}
 
-\begin{block}{Puzzle}
-High variation in economic performance between countries in the midst of internal armed conflict
 \begin{itemize}
-\item Mexico
-\item India
-\item Nicaragua
+\item Krugman 1991; Henderson 2000; Hanson 2005 - Cities are important drivers of economic growth
+\item Heterogeneity in effect of conflict on growth is due to spatial proximity of conflict relative to major urban centers
 \end{itemize}
-\end{block}
 
@@
 	\item Civil War $\rightarrow$ Economic Performance
+	\begin{itemize}
+	\item Collier (1999) - destruction, disruption, diversion, dissaving, portfolio substitution
+	\item Imai \& Weinstein (2005) - geographical spread of conflict
+	\end{itemize}
 	\item Economic Performance $\rightarrow$ Civil War
+	\begin{itemize}
+	\item Collier et al. (2003) - the conflict trap
+	\item Fearon \& Laitin (2003) - poor economic growth conducive for civil war
+	\end{itemize}
 	\item Disaggregating Civil Wars
+	\begin{itemize}
+	\item Pierskalla \& Hollenbach (2013) - cell phone coverage $\rightarrow$ rebel mobilization
+	\end{itemize}
 \end{itemize}
@@
 \begin{frame}
-\frametitle{Disaggregating Conflict and Growth}
+\frametitle{Cities, Conflict, \& Growth}
 
-\begin{block}{Our argument}
-State economic performance in countries experiencing civil conflict is conditional on the proximity of conflict from major population, economic, and resource centers
-\end{block}
+\begin{itemize}
+	\item Cities $\rightarrow$ Growth
+	\begin{itemize}
+	\item Marshall (1920) - geographic clustering promotes valuable learning and exchange between actors
+	\item Lucas (1998) \& Glaeser et al. (1992) - accumulation of human capital generates positive spillovers
+	\item Venables (2005) - economy consists of ``lumps'' of productivity and swaths of areas contributing little to growth	
+	\end{itemize}
+	\item Cities \& Conflict $\rightarrow$ Growth
+	\begin{itemize}
+	\item Conflicts have heterogeneous effects on economic growth 
+	\item Effects determined by spatial proximity to economically relevant centers such as cities
+	\end{itemize}
+\end{itemize}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}
@@
 \end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Spread of Conflict: Colombia}
+
+\vspace{-8mm}
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=.5\textwidth]{colombiaMap-crop}
+\end{figure}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Spread of Conflict: India}
+
+\vspace{-8mm}
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=.5\textwidth]{indiaMap-crop}
+\end{figure}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\vspace{-0.25cm}
+% \vspace{-0.25cm}
 \begin{figure}[ht]
   \centering
+  % \hspace{-50mm}
   \includegraphics[width=1\textwidth]{CityConfMap-crop}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}
-\frametitle{Aggregating to Country-Year}
+\frametitle{Bivariate Relationship?}
 
+\vspace{-0.25cm}
 \begin{figure}[ht]
   \centering
-	\includegraphics[width=.6\textwidth]{colombiaMap-crop}
+  \resizebox{1\textwidth}{!}{\input{distGdp.tex}}
 \end{figure}
@@
 \end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{align*}
-	\% \Delta GDP_{i,t} &= \beta_{1}(Upper \; Income_{i,t}) \\
-	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t}) \;+\; \beta_{3}(Ln(Conflict \; Area)_{i,t}) \\
-	& \;+\; \beta_{4}(Ln(Min. \; Conflict \; Dist.)_{i,t}) \;+\; \beta_{5}(Conflict \; Type_{i,t}) \\
-	& \;+\; \beta_{6}(Conflict \; Duration_{i,t}) \;+\; \beta_{7}(Inflation_{i,t-1}) \\
-	& \;+\; \beta_{8}(Ln(Land \; Area)_{i,t}) \;+\; \alpha_{i} + \gamma_{t} + \mu_{i,t}
+	\% \Delta Ln(GDP)_{i,t} &= \beta_{1}(Ln(Min. \; Conflict \; Dist.)_{i,t-1}) \\
+	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t-1}) \\
+	& \;+\; \beta_{3}(Conflict \; Duration_{i,t-1}) \\
+	& \;+\; \beta_{4}(Conflict \; Area_{i,t-1} \;/\; Land \; Area_{i,t-1} > 50\%) \\
+	& \;+\; \beta_{5}(Number \; of \; Conflicts_{i,t-1}) \\
+	& \;+\; \beta_{6}(Upper \; Income_{i,t}) \\	
+	& \;+\; \beta_{7}(Inflation_{i,t-1}) \;+\; \beta_{8}(Democracy_{i,t-1}) \\
+	& \;+\; \beta_{9}(Resource \; Rents/GDP_{t-1}) \\ 
+	& \;+\; \beta_{10}(World \; GDP \; Growth_{t}) \;+\; \mu_{i,t} \;+\; \epsilon_{i,t}
 \end{align*}
@@
 
-\begin{figure}[ht]
+\vspace{-8mm}
+\begin{figure}
 	\centering
-	\resizebox{.8\textwidth}{!}{\input{mod3CoefPlot.tex}}
+	\begin{tabular}{cc}
+	\hspace{-9mm}
+		\resizebox{.5\textwidth}{!}{\input{mCapCoefPlot.tex}} &
+		\resizebox{.5\textwidth}{!}{\input{mCityCoefPlot.tex}}
+	\end{tabular}
 \end{figure}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}
-\frametitle{Substantive Effects}
+\frametitle{Cross-Validation of Parameter Estimates}
 
@@
 	\centering
-	\resizebox{.9\textwidth}{!}{\input{mod3SimPlot.tex}}
+	\resizebox{1\textwidth}{!}{\input{crossValPlot.tex}}
 \end{figure}
@@
 \end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Substantive Effects: Capital Distance}
+
+\vspace{-6mm}
+\begin{figure}
+	\centering
+	\resizebox{1\textwidth}{!}{\input{mCapSimPlot.tex}}
+\end{figure}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{frame}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-04-17 LaTeX/Presentation/mpsa15.tex
preeze updates

%!TEX TS-program = xelatex
\documentclass[10pt, compress]{beamer}

\usetheme[usetitleprogressbar]{m}
\usepackage{booktabs}
\usepackage[scale=2]{ccicons}
\usepackage{coordsys} % for number lines
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{dcolumn}
\usepackage{caption}
\usepackage{subfig}
\usepackage{tikz}

% easy commands for number propers
\makeatletter
\def\input@path{{/Users/janus829/Dropbox/Research/Rhodium/Graphics/}}
\makeatother
\graphicspath{{/Users/janus829/Dropbox/Research/Rhodium/Graphics/}}

\title[Enemy at the Gates]{Variation in Economic Growth From Civil Conflict}
\author[Minhas \& Radford]{Shahryar Minhas \& Benjamin Radford}
\institute[Duke University]
{
{\emph{shahryar.minhas@duke.edu \& benjamin.radford@duke.edu}} \\
\medskip
Duke University 
}
\date{\today}

\begin{document}

\frame{\titlepage}

\input{PreezeText}

\plain{Thanks}

\end{document}

### 2015-04-25 LaTeX/Presentation/PreezeText.tex
r and r letter

@@
 
+\pause
 \begin{itemize}
 \item Krugman 1991; Henderson 2000; Hanson 2005 - Cities are important drivers of economic growth
+\pause
 \item Heterogeneity in effect of conflict on growth is due to spatial proximity of conflict relative to major urban centers
@@
 	\item Collier (1999) - destruction, disruption, diversion, dissaving, portfolio substitution
-	\item Imai \& Weinstein (2005) - geographical spread of conflict
+	% \item Imai \& Weinstein (2005) - geographical spread of conflict
 	\end{itemize}
+	\pause
 	\item Economic Performance $\rightarrow$ Civil War
 	\begin{itemize}
-	\item Collier et al. (2003) - the conflict trap
+	% \item Collier et al. (2003) - the conflict trap
 	\item Fearon \& Laitin (2003) - poor economic growth conducive for civil war
 	\end{itemize}
+	\pause
 	\item Disaggregating Civil Wars
@@
 	\item Marshall (1920) - geographic clustering promotes valuable learning and exchange between actors
+	\pause
 	\item Lucas (1998) \& Glaeser et al. (1992) - accumulation of human capital generates positive spillovers
+	\pause
 	\item Venables (2005) - economy consists of ``lumps'' of productivity and swaths of areas contributing little to growth	
 	\end{itemize}
+	\pause
 	\item Cities \& Conflict $\rightarrow$ Growth
@@
 
-\begin{block}{Conclusions}
 \begin{itemize}
-	\item Novel approach in the study of civil conflict to distinguish between spatially dissimilar events
-	\item Proximity of conflict to major cities explains disparate economic outcomes
-\end{itemize}
-\end{block}
-
-\begin{block}{Next Steps}
-\begin{itemize}
-\item Account for other economically important locations (e.g., oil fields)
-\item Alternative methods to address aggregation problem
+\item Account for other economically important locations (e.g., oil fields, highways connecting cities)
 \item More refined analysis within a country using subnational economic data
 \end{itemize}
-\end{block}
 

### 2015-04-25 LaTeX/Revision/reviseLetter.tex
r and r letter

\documentclass[12pt,onesided,fullpage]{amsart}

%%% PAGE DIMENSIONS
\usepackage{multirow}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry} 
%\pdfpagewidth=8.5in % for pdflatex
%\pdfpageheight=11in % for pdflatex

\usepackage{graphicx} % support the \includegraphics command and options

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim

%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array,amsmath,graphicx,psfrag,amssymb,subfigure,tabularx,booktabs}
\usepackage{mparhack}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{multicol}
\usepackage{color}
\usepackage{dcolumn}
\usepackage{hyperref}
\usepackage{stmaryrd}
\setcitestyle{authordate,round,semicolon,aysep={,},yysep={,}}
\bibpunct[:]{(}{)}{;}{a}{,}{,}

\doublespacing

\begin{document}
\singlespacing

\title[JCR-14-0358​]{JCR-14-0358​ entitled ``Enemy at the Gates: Variation in Economic Growth from Civil Conflict''}

\date{\today~~Version 0.01}
\maketitle

$\hspace{-5mm}$Dear Professor Huth, \\ [1ex]

We first would like to thank you for the opportunity to revise and resubmit our manuscript. We believe the manuscript has greatly benefitted from the Reviewers' helpful and thoughtful comments. We have thoroughly revised the manuscript, taking seriously each individual point raised by the Reviewers. The revision memo is organized by first responding to your comments and then addressing the reviewers' points. Our comments and responses are shown in \textcolor{blue}{\emph{BLUE}} below each point.

We hope you agree that the manuscript has greatly improved through this helpful process and we are looking forward to your response.\\ [1ex]

Sincerely, \\ [1ex]

The Authors.

\section{Editor}

In revising your paper you should consider the full range of questions raised by each of the reviewers as they offer thoughtful comments and suggestions for improving the paper. I want to highlight some of those points to emphasize the need for your careful attention to them as you work on revisions.

Regarding R1, there are three issues to highlight. 
\begin{enumerate}
\item  First, this reviewer would like to see your main model be run on a fixed effects setup with standard errors clustered on country. \\

\textcolor{blue}{\emph{stuff}}

\item Second, this reviewer would like to see country year observations without conflict included in the analyses instead of being excluded. I should note that R2 raises these two concerns as well which suggests that it will be critical to address these issues in your revisions. \\

\textcolor{blue}{\emph{stuff}}

\item Third, this reviewer would like to see you estimate a baseline model for the impact of conflict on growth in which GDP growth is regressed on a dummy for armed conflict in a country. After that, you can then move onto your central argument and compare your findings to this baseline set of findings. \\

\textcolor{blue}{\emph{stuff}}

\end{enumerate}

Regarding R2, there is one additional issue to highlight (points one and two overlap with R1).

\begin{enumerate}
\item The third point raised is to run a robustness check on the more disaggregated ACLED data set to see if your findings hold up. \\

\textcolor{blue}{\emph{stuff}}

\end{enumerate}

\section{Reviewer: 1}

This paper advances the hypothesis that conflict should exert larger negative impacts on GDP if it located closer to urban centers. This idea is tested using subnational data on conflict location from the PRIO Conflict Site Dataset covering the 1989-2008 period. The authors present evidence for their hypothesis using a random effects model. Robustness checks are conducted verifying the results are not driven by a particular sub-sample.

I very much like the conceptual hypothesis advanced by this paper, and the idea of using the conflict Site Dataset to test it. However, I am concerned about the empirical specification used for the analysis. Below I outline alternative approaches. If these can be implemented, I believe the paper can make a valuable contribution to the conflict literature.

\subsection{Major comments}

\begin{enumerate}
\item The random effects model is only appropriate compared to the fixed effects model if there is a compelling reason to believe that time invariant country characteristics are uncorrelated with spatial conflict location and income. The authors don’t present a Hausman test to try and make the case for random effects. Moreover, this doesn’t seem plausible because geographic factors such as roughness of terrain and climactic conditions in remote areas far from urban centers would determine the cost of launching an insurgency in urban vs. rural areas and also affect GDP. In addition, institutional features such as whether rule of law or state presence extends to rural areas would similarly act as potential omitted variables if country fixed effects are not included. A research question along these lines really should exploit variation within a country and show that as urban conflict location chances, GDP growth changes, instead of relying on comparisons across countries. As such, I would want to see the results hold with the fixed effects model as the primary model, including country and year fixed effects, and with standard errors clustered on country to control serial correlation over time.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item Currently country year observations without conflict are excluded from current specifications. They should not be because if low GDP correlates with periods of no conflict, as might arise if sufficient economic activity is required to finance internal conflicts, then this omission would lead to an upward bias on the estimates.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item It will be fairly important to benchmark the results based on distance between conflict location and urban center against the overall effect of conflict. In other words, we’d like to know if having any conflict lowers GDP, and if this effect is even stronger if its located closer to urban areas. To capture this, the authors should start with a simple specification that regresses GDP growth on a dummy for if any conflict occurred. Then they should introduce an interaction between this dummy variable and the conflict distance variable. The coefficient on the dummy in this second specification would then capture effects of 0 distance, or if conflicts occurred in cities.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item It wasn’t clear to me how 0 distance was dealt with the current specifications since logs were taken but this would eliminate the 0s. It would be very important to include these if in fact conflict in cities are represented by 0 distance in the data.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item Instead of treating conflict intensity as a control, it would be useful to re-do the specifications in point 3 above but just restricting to the incidents coded as wars and then restricting to the lower intensity effects. Then the authors can test to see if coefficients on the former are in fact larger.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item More information should be provided on how conflict events make it into the Conflict Site Dataset. For example, Figure 1 suggests too sparse picture of violent events in Colombia, given that nearly 1/3rd of the Colombian territory was war affected over this period.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item I like the use of the descriptive cases but more should be done with these if they will be included. In particular, the economic dynamic of these countries should be mentioned to clarify how the effect of conflict on GDP maps to the hypotheses advanced in the paper. I also wondered about the focus on conflict in the NE in India. Naxalite conflict has also spread rapidly and is also located in rural areas (which is consistent with the authors’ point), so this would be natural to draw upon as well.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\end{enumerate}

\section{Reviewer: 2}
The authors claim that the distance between cities (or capital) and the location of violent events during a civil conflict is a first order argument to explain the effect of conflict on economic growth. I’m fully convinced of the interest of the question to understand the legacies of civil conflict. Empirical evidence on the effect of civil conflict on growth is notably crucial for the post- recovery policies. While I find the the question very interesting, I think there is a number of issues that remain to be addressed.

\subsection{Major Comments}

\begin{enumerate}

\item  I’m convinced by the interpretation of the results but I can imagine also an alternative story. The state capacity is negatively correlated to the distance (to the capital or main cities - see Buhaug, 2010). That means that the fighting cost for a rebel group is decreasing with the distance to the capital. In other words, it is only the strongest (richest) rebel groups that are able to be close enough to the capital. The effect detected in the paper is perhaps only the effect of size groups. The biggest groups are the more violent, the more disruptive and consequently that have an higher effect on economic growth. I’m not sure how it will be possible to arbitrate between this alternative story and the story of the authors. At the end, a discussion around this alternative explanation would be profitable to the paper.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item he empirical strategy used is a major issue and the authors have to deeply improved this part. The authors mainly use a cross-country comparison using random effects and they justify the use of random effects because their purpose is to explain variation between unit. But the cross-country comparison doesn’t involve the use of random effects. The authors missed also to control for time-specific shocks that are common to all countries by including year dummies. The year dummies will absorb yearly worldwide changes such as economic shocks, global climate shocks or natural resource price shocks. I don’t believe also the explanation to avoid the use of country fixed effects. I think the authors should follow the following road map:
\begin{itemize}
\item Simple correlation between GDP growth and the distance of conflict.
\item Inclusion of the control variables.
\item Inclusion of year fixed effects.
\item Inclusion of both year and country fixed effects.
\end{itemize}

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item Sample. I’m not convinced by the sample choice. I would like to see results with a full sample of countries from 1989 to 2008, including peace countries. I expect the author to interact their measure of distance to conflict with a dummy coded 1 for country in civil conflict and 0 otherwise

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item Data on conflicts. One could imagine that the quality/quantity of reports on conflicts is negatively correlated to this distance to the capital. I would appreciate a discussion on the potential report bias and how it could influence the results. As a robustness, I expect the authors to use ACLED data that are commonly used now as data for disaggregated analysis.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item To avoid issues linked to reverse causation, I would consider the list of urban centers
at the beginning of the period.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item Definition of variables. The authors take the minimum distance to the conflict as explanatory variable. I would like to see alternative measures to ensure that the results are not sensitive to the definition of the main variable. For instance, the weighted (by the distance) sum of the number of events is a credible candidate as an alternative measure.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\end{enumerate}

\subsection{Minor Comments}

\begin{enumerate}

\item Introduction. The example on Mexico looks strange. By many aspects, the drug war in Mexico is very different to conflicts in Republic Democratic of Congo or in Uganda. In other words, it is difficult to compare conflicts with genocide, massive internal migration, ethnic cleavages with a drug war where almost all citizens support the government. The recent case of Nigeria and Cameroon with Boko Haram looks to be a better fit with the story of the authors.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item The authors claim they focus on the proximities of conflict to cities and not on the area covered by the conflict. I’m wondering whether the effect of the proximities of conflict to cities would be intensify by the area of the conflict. I expect the effect of the proximities of conflict to cities to be higher if the area of conflict is biggest. A very simple interaction term between distance and area would be appropriate to uncover this mechanism.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item Results. Conflict duration and the number of conflicts a country is facing have an unexpected effect on growth. I would see a discussion to explain this results.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item Area covered by conflict. I don’t understand why the authors use a binary measure instead of the continuous variable.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item Robustness. The strategy that consists to run a six-fold cross-validation is convincing. In the same spirit, I would like to see the same exercise when one country is left out of the sample.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item Figures have to be self contained.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item The visual presentation of the results are interesting but the classical way to present results (through tables) is a requirement.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\item The recent works on cities of Quoc-Anh Do seems to me as a complement to this paper.

\begin{itemize}
\item \textcolor{blue}{\emph{stuff}}
\end{itemize}

\end{enumerate}

\newpage\tiny
\end{document}\bye

### 2015-07-25 LaTeX/RhodiumAppendix.tex
Added ACLED

\section{Appendix}
\label{appendix}

The Armed Conflict Location and Event Dataset provides an alternative source of information on the subnational spatial distribution of armed conflict \citep{raleigh:linke:etal:2010}. This dataset is, at the time of writing, limited to Africa and therefore was not selected for the primary analysis presented in the text. It does, however, offer us a valuable opportunity to validate our results. Here, we have replicated the primary model described in Section~\ref{empirics}.

In order to match our existing data structure, it was necessary to aggregate the ACLED data to the country-year level. We did this by first subsetting ACLED to the years 1989-2008 and then selecting only conflict sites with at least 25 fatalities in each given year. The 25 fatalities threshold is intended to mirror the PRIO coding criteria and to prevent very low-fatality events from biasing our estimates of conflict location toward high-population areas. Covariates created with PRIO but unavailable in ACLED are omitted. The analysis procedure then continues as described in Section~\ref{empirics}: the minimum distance measure is calculated as the natural logarithm of the average distance in kilometers from any conflict site to the nearest major city (or capital). The results are presented in Figures~\ref{fig:acled} and \ref{fig:acledfixef}.

\begin{figure}
	\centering
	\begin{tabular}{cc}
		\subfloat[SubFigure 1][Capital City]{
			\resizebox{.45\textwidth}{!}{\input{mAcledCapCoefPlot.tex}}
		\label{fig:acled}} &
		\subfloat[SubFigure 2][Any Major City]{
			\resizebox{.45\textwidth}{!}{\input{mAcledCityCoefPlot.tex}}
		\label{fig:acledfixef}}
	\end{tabular}
	\caption{Regression results using conflict distance from capital city on the left, and the chart on the right shows regression results using minimum conflict distance from any major city. Conflict data based on ACLED. Darker colors indicates that the coefficient estimate is significantly different from zero at a 95\% CI, while lighter the same for a 90\% CI. Grey indicates that the estimate is not significantly different from zero at either of those intervals. The lagged number of conflicts within a country is also included in the models but is omitted from the plots above to enhance readability.}
	\label{fig:coefplot}
\end{figure}

### 2015-07-25 LaTeX/RhodiumEmp.tex
Added ACLED

@@
 In recent years, other geo-referenced datasets have been developed that go beyond just providing information on conflict centroids and area to providing an actual spatial grid structure through which to conduct analysis \citep{tollefsen:etal:2012}.
-However, these data are not available globally and would therefore unnecessarily limit the external validity of the current analysis.
-Other machine coded event datasets, while providing detailed coverage of events on a global scale, often approximate event locations based on descriptors in the source material or by the location of the reporting news agency itself.
+However, these data are not available globally and would therefore unnecessarily limit the external validity of the current analysis.\footnote{Nonetheless, we conduct a robustness test of our primary models using data from the Armed Conflict Location and Event Data (ACLED) Project.
+The results described here hold with the new data.
+A description of the ACLED modeling strategy and results can be found in the Appendix.} Other machine coded event datasets, while providing detailed coverage of events on a global scale, often approximate event locations based on descriptors in the source material or by the location of the reporting news agency itself.
 Because the location of conflict is critical for this analysis, the urban bias of disaggregated event data is unacceptable.
@@
 After obtaining these distributions, we calculate the predicted value of GDP growth based on the conditions set by the scenarios.
-We plot the results of this analyis in figures \ref{fig:capSim} and \ref{fig:citySim}.
+We plot the results of this analysis in figures \ref{fig:capSim} and \ref{fig:citySim}.
 

### 2015-07-25 R/Analysis/models.R

@@ -28,6 +28,8 @@ modData$lnminDist.mean <- log(modData$minDist.mean+1)
 modData$lncapDist.mean <- log(modData$capDist.mean+1)
 modData$lnminDistACLED.min <- log(modData$minDistACLED.min+1)
 modData$lnminDistACLED.mean <- log(modData$minDistACLED.mean+1)
+modData$lncapDistACLED.min <- log(modData$acledCapDist.min+1)
+modData$lncapDistACLED.mean <- log(modData$acledCapDist.mean+1)
 modData$Int.max <- modData$Int.max-1
 
 # Transformations for other controls
@@ -66,9 +68,11 @@ ctyForm=modForm(ivs=c(kivs[1], cntrls), type='random')
 capForm=modForm(ivs=c(kivs[2], cntrls), type='random')
 # We can't use the modForm() function here because Int.max, durSt1max, confAreaProp are not defined for ACLED data:
 acledForm = lngdpGr_l0 ~ lnminDistACLED.mean + nconf + upperincome + lninflation_l1 + polity2 + resourceGDP + gdpGr.mean_l0 + (1 | ccode)
+acledFormCap = lngdpGr_l0 ~ lncapDistACLED.mean + nconf + upperincome + lninflation_l1 + polity2 + resourceGDP + gdpGr.mean_l0 + (1 | ccode)
 mCity = lmer(ctyForm, data = modData ); summary(mCity)$'coefficients'
 mCap = lmer(capForm, data = modData ); summary(mCap)$'coefficients'
 mAcled = lmer(acledForm, data = modData ); summary(mAcled)$'coefficients'
+mAcledCap = lmer(acledFormCap, data=modData); summary(mAcledCap)$'coefficients'
 
 # Fixef Robustness Checks
 ctyFormFE=modForm(ivs=c(kivs[1], cntrls), type='fixed')
@@ -77,7 +81,7 @@ capFormFE=modForm(ivs=c(kivs[2], cntrls), type='fixed')
 acledFormFE = lngdpGr_l0 ~ lnminDistACLED.mean + nconf + upperincome + lninflation_l1 + polity2 + resourceGDP + gdpGr.mean_l0 + factor(ccode) -1
 mCityFixefCntry = lm(ctyFormFE, data = modData ); summary(mCityFixefCntry)$'coefficients'[1:(length(cntrls)+1),]
[…]

### 2015-07-25 R/Databuilder/04 - DistanceCalc.R

@@ -57,12 +57,19 @@ acledData$minDistACLED <- minDist(
   acledData$LATITUDE, acledData$LONGITUDE, acledData$cname, acledData$YEAR,
   fYrCty$cleanLat, fYrCty$cleanLong, fYrCty$cname, fYrCty$YearAlmanac)
 
+acledData$acledCapDist <- minDist(
+  acledData$LATITUDE, acledData$LONGITUDE, acledData$cname, acledData$YEAR,
+  fYrCty$cleanLat[fYrCty$Capital==1],
+  fYrCty$cleanLong[fYrCty$Capital==1],
+  fYrCty$cname[fYrCty$Capital==1],
+  fYrCty$YearAlmanac[fYrCty$Capital==1])
+
 plot(density(acledData$minDistACLED,na.rm=T),lty=2,frame=F,yaxt="n",xlab="Minimum Distance",ylab="",main="PRIO vs ACLED")
 lines(density(prioAC$minDist,na.rm=T),lty=1)
 legend("topright",c("PRIO","ACLED"),lty=c(1,2),bty="n")
 
-acledData <- aggregate(acledData$minDistACLED, list(acledData$cname,acledData$YEAR), FUN=function(x)min(x,na.rm=T))
-names(acledData) <- c("cname","YEAR","minDistACLED")
+acledData <- aggregate(acledData[,c("minDistACLED","acledCapDist")], list(acledData$cname,acledData$YEAR), FUN=function(x)min(x,na.rm=T))
+names(acledData) <- c("cname","YEAR","minDistACLED","acledCapDist")
 prioAC <- merge(prioAC, acledData, by=c("cname","YEAR"), all.x=T, all.y=F)
 
 # Calculate number of cities within radius of conflict
@@ -82,13 +89,14 @@ prioAC$capDist <- minDist(
 
   prioAC$capDist = rnorm(nrow(prioAC))
 }
+
 ##################################################################
 
 ##################################################################
 # Aggregate to the country-year
 prioAC$territorial <- as.numeric(prioAC$Incomp%in%c(1,3))
 prioAC <- prioAC[,c("ID","Incomp","Int","CumInt","territorial",
-  "Conflict.area","Type","Region","minDist","minDistACLED","inRadius","capDist",
+  "Conflict.area","Type","Region","minDist","minDistACLED","acledCapDist","inRadius","capDist",
[…]

### 2015-08-16 LaTeX/RhodiumIntro.tex
Mexico -> Nigeria & Cameroon
Really? Ugh.

@@
 
-Further few in the literature have sought to explain puzzling cases of domestic armed conflict having little impact on macroeconomic growth.
+Further, few in the literature have sought to explain puzzling cases of domestic armed conflicts that have little impact on macroeconomic growth.
+Nigeria and Cameroon, for instance, have both been engaged in violent conflict with Boko Haram, a group of militants determined to establish an Islamic state in West Africa.
+In Nigeria, the death toll has steadily risen since 2011; the Council on Foreign Relations estimates that the conflict had resulted in over 40,000 casualties by mid-2015 \citep{cfr:2015}.
+However, Boko Haram primarily operates in the rural and relatively less populated north-eastern regions of Nigeria and Cameroon.
+During this conflict, both countries have maintained robust economic growth.
+When Nigeria rebased its economy in 2014, it overtook South Africa as the continent's largest economy.
+
+%Further few in the literature have sought to explain puzzling cases of domestic armed conflict having little impact on macroeconomic growth.
 Mexico, for example, has been engaged in a drug war since December 2006 and the number of deaths stemming from this civil conflict have only increased since that time.

### 2015-08-16 LaTeX/RhodiumTheory.tex
Mexico -> Nigeria & Cameroon
Really? Ugh.

@@
 The story from this map is clearly quite stark from that of Colombia.
-Whereas in Colombia conflict had come right to the gates of major cities, in India conflict clearly has been centered in the peripheries.
+Whereas in Colombia conflict had come right to the gates of major cities, in India conflict clearly has been confined to the periphery.
 
@@
 
-It is important to note that Mexico does not appear in the civil war dataset chosen for this study.
+%It is important to note that Mexico does not appear in the civil war dataset chosen for this study.
 The UCDP definition of civil war requires that the conflict be fought over an ``incompatibility that concerns government and/or territory,'' a criteria not strictly met by the organized crime violence experienced by the country \citep[p.1]{themner:2014}.

### 2015-08-17 LaTeX/Revision/editor.tex
rev letter

--- 2015-04-25 LaTeX/Revision/reviseLetter.tex
@@
-\documentclass[12pt,onesided,fullpage]{amsart}
-
-%%% PAGE DIMENSIONS
-\usepackage{multirow}
-\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry} 
-%\pdfpagewidth=8.5in % for pdflatex
-%\pdfpageheight=11in % for pdflatex
-
-\usepackage{graphicx} % support the \includegraphics command and options
-
-%%% PACKAGES
-\usepackage{booktabs} % for much better looking tables
-\usepackage{array} % for better arrays (eg matrices) in maths
-\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
-\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
-
-%%% HEADERS & FOOTERS
-\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
-\pagestyle{fancy} % options: empty , plain , fancy
-\renewcommand{\headrulewidth}{0pt} % customise the layout...
-
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{array,amsmath,graphicx,psfrag,amssymb,subfigure,tabularx,booktabs}
-\usepackage{mparhack}
-\usepackage{setspace}
-\usepackage{natbib}
-\usepackage{multicol}
-\usepackage{color}
-\usepackage{dcolumn}
-\usepackage{hyperref}
-\usepackage{stmaryrd}
-\setcitestyle{authordate,round,semicolon,aysep={,},yysep={,}}
-\bibpunct[:]{(}{)}{;}{a}{,}{,}
-
-\doublespacing
-
-\begin{document}
-\singlespacing
-
-\title[JCR-14-0358​]{JCR-14-0358​ entitled ``Enemy at the Gates: Variation in Economic Growth from Civil Conflict''}
-
-\date{\today~~Version 0.01}
-\maketitle
-
-$\hspace{-5mm}$Dear Professor Huth, \\ [1ex]
-
-We first would like to thank you for the opportunity to revise and resubmit our manuscript.
-We believe the manuscript has greatly benefitted from the Reviewers' helpful and thoughtful comments.
-We have thoroughly revised the manuscript, taking seriously each individual point raised by the Reviewers.
-The revision memo is organized by first responding to your comments and then addressing the reviewers' points.
-Our comments and responses are shown in \textcolor{blue}{\emph{BLUE}} below each point.
-
-We hope you agree that the manuscript has greatly improved through this helpful process and we are looking forward to your response.\\ [1ex]
-
-Sincerely, \\ [1ex]
-
-The Authors.
-
 \section{Editor}
@@
 \end{enumerate}
-
-\section{Reviewer: 1}
-
-This paper advances the hypothesis that conflict should exert larger negative impacts on GDP if it located closer to urban centers.
-This idea is tested using subnational data on conflict location from the PRIO Conflict Site Dataset covering the 1989-2008 period.
-The authors present evidence for their hypothesis using a random effects model.
-Robustness checks are conducted verifying the results are not driven by a particular sub-sample.
-
-I very much like the conceptual hypothesis advanced by this paper, and the idea of using the conflict Site Dataset to test it.
-However, I am concerned about the empirical specification used for the analysis.
-Below I outline alternative approaches.
-If these can be implemented, I believe the paper can make a valuable contribution to the conflict literature.
-
-\subsection{Major comments}
-
-\begin{enumerate}
-\item The random effects model is only appropriate compared to the fixed effects model if there is a compelling reason to believe that time invariant country characteristics are uncorrelated with spatial conflict location and income.
-The authors don’t present a Hausman test to try and make the case for random effects.
-Moreover, this doesn’t seem plausible because geographic factors such as roughness of terrain and climactic conditions in remote areas far from urban centers would determine the cost of launching an insurgency in urban vs.
-rural areas and also affect GDP.
-In addition, institutional features such as whether rule of law or state presence extends to rural areas would similarly act as potential omitted variables if country fixed effects are not included.
-A research question along these lines really should exploit variation within a country and show that as urban conflict location chances, GDP growth changes, instead of relying on comparisons across countries.
-As such, I would want to see the results hold with the fixed effects model as the primary model, including country and year fixed effects, and with standard errors clustered on country to control serial correlation over time.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Currently country year observations without conflict are excluded from current specifications.
-They should not be because if low GDP correlates with periods of no conflict, as might arise if sufficient economic activity is required to finance internal conflicts, then this omission would lead to an upward bias on the estimates.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item It will be fairly important to benchmark the results based on distance between conflict location and urban center against the overall effect of conflict.
-In other words, we’d like to know if having any conflict lowers GDP, and if this effect is even stronger if its located closer to urban areas.
-To capture this, the authors should start with a simple specification that regresses GDP growth on a dummy for if any conflict occurred.
-Then they should introduce an interaction between this dummy variable and the conflict distance variable.
-The coefficient on the dummy in this second specification would then capture effects of 0 distance, or if conflicts occurred in cities.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item It wasn’t clear to me how 0 distance was dealt with the current specifications since logs were taken but this would eliminate the 0s.
-It would be very important to include these if in fact conflict in cities are represented by 0 distance in the data.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Instead of treating conflict intensity as a control, it would be useful to re-do the specifications in point 3 above but just restricting to the incidents coded as wars and then restricting to the lower intensity effects.
-Then the authors can test to see if coefficients on the former are in fact larger.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item More information should be provided on how conflict events make it into the Conflict Site Dataset.
-For example, Figure 1 suggests too sparse picture of violent events in Colombia, given that nearly 1/3rd of the Colombian territory was war affected over this period.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item I like the use of the descriptive cases but more should be done with these if they will be included.
-In particular, the economic dynamic of these countries should be mentioned to clarify how the effect of conflict on GDP maps to the hypotheses advanced in the paper.
-I also wondered about the focus on conflict in the NE in India.
-Naxalite conflict has also spread rapidly and is also located in rural areas (which is consistent with the authors’ point), so this would be natural to draw upon as well.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\end{enumerate}
-
-\section{Reviewer: 2}
-The authors claim that the distance between cities (or capital) and the location of violent events during a civil conflict is a first order argument to explain the effect of conflict on economic growth.
-I’m fully convinced of the interest of the question to understand the legacies of civil conflict.
-Empirical evidence on the effect of civil conflict on growth is notably crucial for the post- recovery policies.
-While I find the the question very interesting, I think there is a number of issues that remain to be addressed.
-
-\subsection{Major Comments}
-
-\begin{enumerate}
-
-\item  I’m convinced by the interpretation of the results but I can imagine also an alternative story.
-The state capacity is negatively correlated to the distance (to the capital or main cities - see Buhaug, 2010).
-That means that the fighting cost for a rebel group is decreasing with the distance to the capital.
-In other words, it is only the strongest (richest) rebel groups that are able to be close enough to the capital.
-The effect detected in the paper is perhaps only the effect of size groups.
-The biggest groups are the more violent, the more disruptive and consequently that have an higher effect on economic growth.
-I’m not sure how it will be possible to arbitrate between this alternative story and the story of the authors.
-At the end, a discussion around this alternative explanation would be profitable to the paper.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item he empirical strategy used is a major issue and the authors have to deeply improved this part.
-The authors mainly use a cross-country comparison using random effects and they justify the use of random effects because their purpose is to explain variation between unit.
-But the cross-country comparison doesn’t involve the use of random effects.
-The authors missed also to control for time-specific shocks that are common to all countries by including year dummies.
-The year dummies will absorb yearly worldwide changes such as economic shocks, global climate shocks or natural resource price shocks.
-I don’t believe also the explanation to avoid the use of country fixed effects.
-I think the authors should follow the following road map:
-\begin{itemize}
-\item Simple correlation between GDP growth and the distance of conflict.
-\item Inclusion of the control variables.
-\item Inclusion of year fixed effects.
-\item Inclusion of both year and country fixed effects.
-\end{itemize}
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Sample.
-I’m not convinced by the sample choice.
-I would like to see results with a full sample of countries from 1989 to 2008, including peace countries.
-I expect the author to interact their measure of distance to conflict with a dummy coded 1 for country in civil conflict and 0 otherwise
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Data on conflicts.
-One could imagine that the quality/quantity of reports on conflicts is negatively correlated to this distance to the capital.
-I would appreciate a discussion on the potential report bias and how it could influence the results.
-As a robustness, I expect the authors to use ACLED data that are commonly used now as data for disaggregated analysis.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item To avoid issues linked to reverse causation, I would consider the list of urban centers
-at the beginning of the period.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Definition of variables.
-The authors take the minimum distance to the conflict as explanatory variable.
-I would like to see alternative measures to ensure that the results are not sensitive to the definition of the main variable.
-For instance, the weighted (by the distance) sum of the number of events is a credible candidate as an alternative measure.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\end{enumerate}
-
-\subsection{Minor Comments}
-
-\begin{enumerate}
-
-\item Introduction.
-The example on Mexico looks strange.
-By many aspects, the drug war in Mexico is very different to conflicts in Republic Democratic of Congo or in Uganda.
-In other words, it is difficult to compare conflicts with genocide, massive internal migration, ethnic cleavages with a drug war where almost all citizens support the government.
-The recent case of Nigeria and Cameroon with Boko Haram looks to be a better fit with the story of the authors.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item The authors claim they focus on the proximities of conflict to cities and not on the area covered by the conflict.
-I’m wondering whether the effect of the proximities of conflict to cities would be intensify by the area of the conflict.
-I expect the effect of the proximities of conflict to cities to be higher if the area of conflict is biggest.
-A very simple interaction term between distance and area would be appropriate to uncover this mechanism.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Results. Conflict duration and the number of conflicts a country is facing have an unexpected effect on growth. I would see a discussion to explain this results.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Area covered by conflict. I don’t understand why the authors use a binary measure instead of the continuous variable.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Robustness. The strategy that consists to run a six-fold cross-validation is convincing. In the same spirit, I would like to see the same exercise when one country is left out of the sample.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Figures have to be self contained.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item The visual presentation of the results are interesting but the classical way to present results (through tables) is a requirement.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item The recent works on cities of Quoc-Anh Do seems to me as a complement to this paper.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\end{enumerate}
-
-\newpage\tiny
-\end{document}\bye

### 2015-08-17 LaTeX/Revision/rev1.tex
rev letter

--- 2015-04-25 LaTeX/Revision/reviseLetter.tex
@@
-\documentclass[12pt,onesided,fullpage]{amsart}
-
-%%% PAGE DIMENSIONS
-\usepackage{multirow}
-\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry} 
-%\pdfpagewidth=8.5in % for pdflatex
-%\pdfpageheight=11in % for pdflatex
-
-\usepackage{graphicx} % support the \includegraphics command and options
-
-%%% PACKAGES
-\usepackage{booktabs} % for much better looking tables
-\usepackage{array} % for better arrays (eg matrices) in maths
-\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
-\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
-
-%%% HEADERS & FOOTERS
-\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
-\pagestyle{fancy} % options: empty , plain , fancy
-\renewcommand{\headrulewidth}{0pt} % customise the layout...
-
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{array,amsmath,graphicx,psfrag,amssymb,subfigure,tabularx,booktabs}
-\usepackage{mparhack}
-\usepackage{setspace}
-\usepackage{natbib}
-\usepackage{multicol}
-\usepackage{color}
-\usepackage{dcolumn}
-\usepackage{hyperref}
-\usepackage{stmaryrd}
-\setcitestyle{authordate,round,semicolon,aysep={,},yysep={,}}
-\bibpunct[:]{(}{)}{;}{a}{,}{,}
-
-\doublespacing
-
-\begin{document}
-\singlespacing
-
-\title[JCR-14-0358​]{JCR-14-0358​ entitled ``Enemy at the Gates: Variation in Economic Growth from Civil Conflict''}
-
-\date{\today~~Version 0.01}
-\maketitle
-
-$\hspace{-5mm}$Dear Professor Huth, \\ [1ex]
-
-We first would like to thank you for the opportunity to revise and resubmit our manuscript.
-We believe the manuscript has greatly benefitted from the Reviewers' helpful and thoughtful comments.
-We have thoroughly revised the manuscript, taking seriously each individual point raised by the Reviewers.
-The revision memo is organized by first responding to your comments and then addressing the reviewers' points.
-Our comments and responses are shown in \textcolor{blue}{\emph{BLUE}} below each point.
-
-We hope you agree that the manuscript has greatly improved through this helpful process and we are looking forward to your response.\\ [1ex]
-
-Sincerely, \\ [1ex]
-
-The Authors.
-
-\section{Editor}
-
-In revising your paper you should consider the full range of questions raised by each of the reviewers as they offer thoughtful comments and suggestions for improving the paper.
-I want to highlight some of those points to emphasize the need for your careful attention to them as you work on revisions.
-
-Regarding R1, there are three issues to highlight. 
-\begin{enumerate}
-\item  First, this reviewer would like to see your main model be run on a fixed effects setup with standard errors clustered on country. \\
-
-\textcolor{blue}{\emph{stuff}}
-
-\item Second, this reviewer would like to see country year observations without conflict included in the analyses instead of being excluded.
-I should note that R2 raises these two concerns as well which suggests that it will be critical to address these issues in your revisions.
-\\
-
-\textcolor{blue}{\emph{stuff}}
-
-\item Third, this reviewer would like to see you estimate a baseline model for the impact of conflict on growth in which GDP growth is regressed on a dummy for armed conflict in a country.
-After that, you can then move onto your central argument and compare your findings to this baseline set of findings.
-\\
-
-\textcolor{blue}{\emph{stuff}}
-
-\end{enumerate}
-
-Regarding R2, there is one additional issue to highlight (points one and two overlap with R1).
-
-\begin{enumerate}
-\item The third point raised is to run a robustness check on the more disaggregated ACLED data set to see if your findings hold up. \\
-
-\textcolor{blue}{\emph{stuff}}
-
-\end{enumerate}
-
 \section{Reviewer: 1}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{
+	For the ``Capital City'' and ``Any Major City'' models we ran a Hausman test to see if fixed or random effects were appropriate for our dataset, and in both cases we do not reject the null hypothesis of the Hausman test at a 90 or 95\% confidence interval indicating that it is acceptable to use random effects.
+We have added a discussion of this analysis into our empirical section.
+}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{
+	We have run a t-test to test whether GDP is lower during times of no conflict versus conflict and we find that GDP is higher during conflict years than non-conflict years at a 95\% confidence interval.
+Thus the possibility of an upward bias on our main model estimates should not be so severe.
+}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{
+	We have run a model on our full panel dataset to calculate a benchmark on the effect of any conflict on GDP growth.
+The results of this analysis have been added to the paper.
+To make the baseline model as comparable as possible to the model that we use to test our distance hypothesis, we adopt as similar a specification as possible.
+Specifically, the dependent variable is again logged, GDP growth.
+Then our independent variables are, each lagged by one year:
+	\begin{itemize}
+		\item Civil war, this is just a binary to indicate whether a civil war took place in that year
+		\item Upperincome, this is a binary to indicate whether the country is classified as upper or lower income according to the Worldbank
+		\item Logged, inflation
+		\item Polity score
+		\item Resources as a percent of GDP
+		\item Average GDP growth across the world for that year
+	\end{itemize}
+	We do not include the conflict-specific measures (Distance, Intensity, Duration, and Area) from our distance model since they would just have a value of NA during non-conflict years.
+The key finding from this analysis is that a civil war is related to lower levels of GDP growth, however, this effect is marginal and only significant at a 90\% confidence interval.
+	In terms of including an interaction to the model, 
+}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{
+	The minimum distance of the centroid of a conflict from any major or capital city in our dataset is 0.38 UNITS so this is not an issue for our analysis.
+}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{
+	We reran the models per this specification and have included the results in the appendix.
+In both low intensity and high intensity cases we find that the distance variables remain significant and in the hypothesized direction.
+}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{
+	The PRIO Conflict Site dataset provides information on the centroid of a conflict and that is what is plotted in each of the conflict map figures.
+The PRIO Conflict Site dataset then approximates the area that is covered by the conflict.
+However, the way in which they define this area is problematic as it is not a polygon representing the actual area of conflict, instead they just provide the radius of the conflict zone.
+If we were to try and construct the distance from a city to any part of a conflict area we would have to define the conflict area as just a perfect circle with a given radius, which would not actually reflect where conflict was taking place.
+}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{
+	BEN will add stuff here. 
+}
 \end{itemize}
@@
 \end{enumerate}
-
-\section{Reviewer: 2}
-The authors claim that the distance between cities (or capital) and the location of violent events during a civil conflict is a first order argument to explain the effect of conflict on economic growth.
-I’m fully convinced of the interest of the question to understand the legacies of civil conflict.
-Empirical evidence on the effect of civil conflict on growth is notably crucial for the post- recovery policies.
-While I find the the question very interesting, I think there is a number of issues that remain to be addressed.
-
-\subsection{Major Comments}
-
-\begin{enumerate}
-
-\item  I’m convinced by the interpretation of the results but I can imagine also an alternative story.
-The state capacity is negatively correlated to the distance (to the capital or main cities - see Buhaug, 2010).
-That means that the fighting cost for a rebel group is decreasing with the distance to the capital.
-In other words, it is only the strongest (richest) rebel groups that are able to be close enough to the capital.
-The effect detected in the paper is perhaps only the effect of size groups.
-The biggest groups are the more violent, the more disruptive and consequently that have an higher effect on economic growth.
-I’m not sure how it will be possible to arbitrate between this alternative story and the story of the authors.
-At the end, a discussion around this alternative explanation would be profitable to the paper.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item he empirical strategy used is a major issue and the authors have to deeply improved this part.
-The authors mainly use a cross-country comparison using random effects and they justify the use of random effects because their purpose is to explain variation between unit.
-But the cross-country comparison doesn’t involve the use of random effects.
-The authors missed also to control for time-specific shocks that are common to all countries by including year dummies.
-The year dummies will absorb yearly worldwide changes such as economic shocks, global climate shocks or natural resource price shocks.
-I don’t believe also the explanation to avoid the use of country fixed effects.
-I think the authors should follow the following road map:
-\begin{itemize}
-\item Simple correlation between GDP growth and the distance of conflict.
-\item Inclusion of the control variables.
-\item Inclusion of year fixed effects.
-\item Inclusion of both year and country fixed effects.
-\end{itemize}
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Sample.
-I’m not convinced by the sample choice.
-I would like to see results with a full sample of countries from 1989 to 2008, including peace countries.
-I expect the author to interact their measure of distance to conflict with a dummy coded 1 for country in civil conflict and 0 otherwise
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Data on conflicts.
-One could imagine that the quality/quantity of reports on conflicts is negatively correlated to this distance to the capital.
-I would appreciate a discussion on the potential report bias and how it could influence the results.
-As a robustness, I expect the authors to use ACLED data that are commonly used now as data for disaggregated analysis.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item To avoid issues linked to reverse causation, I would consider the list of urban centers
-at the beginning of the period.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Definition of variables.
-The authors take the minimum distance to the conflict as explanatory variable.
-I would like to see alternative measures to ensure that the results are not sensitive to the definition of the main variable.
-For instance, the weighted (by the distance) sum of the number of events is a credible candidate as an alternative measure.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\end{enumerate}
-
-\subsection{Minor Comments}
-
-\begin{enumerate}
-
-\item Introduction.
-The example on Mexico looks strange.
-By many aspects, the drug war in Mexico is very different to conflicts in Republic Democratic of Congo or in Uganda.
-In other words, it is difficult to compare conflicts with genocide, massive internal migration, ethnic cleavages with a drug war where almost all citizens support the government.
-The recent case of Nigeria and Cameroon with Boko Haram looks to be a better fit with the story of the authors.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item The authors claim they focus on the proximities of conflict to cities and not on the area covered by the conflict.
-I’m wondering whether the effect of the proximities of conflict to cities would be intensify by the area of the conflict.
-I expect the effect of the proximities of conflict to cities to be higher if the area of conflict is biggest.
-A very simple interaction term between distance and area would be appropriate to uncover this mechanism.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Results. Conflict duration and the number of conflicts a country is facing have an unexpected effect on growth. I would see a discussion to explain this results.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Area covered by conflict. I don’t understand why the authors use a binary measure instead of the continuous variable.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Robustness. The strategy that consists to run a six-fold cross-validation is convincing. In the same spirit, I would like to see the same exercise when one country is left out of the sample.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Figures have to be self contained.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item The visual presentation of the results are interesting but the classical way to present results (through tables) is a requirement.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item The recent works on cities of Quoc-Anh Do seems to me as a complement to this paper.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\end{enumerate}
-
-\newpage\tiny
-\end{document}\bye

### 2015-08-17 LaTeX/Revision/rev2.tex
rev letter

--- 2015-04-25 LaTeX/Revision/reviseLetter.tex
@@
-\documentclass[12pt,onesided,fullpage]{amsart}
-
-%%% PAGE DIMENSIONS
-\usepackage{multirow}
-\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry} 
-%\pdfpagewidth=8.5in % for pdflatex
-%\pdfpageheight=11in % for pdflatex
-
-\usepackage{graphicx} % support the \includegraphics command and options
-
-%%% PACKAGES
-\usepackage{booktabs} % for much better looking tables
-\usepackage{array} % for better arrays (eg matrices) in maths
-\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
-\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
-
-%%% HEADERS & FOOTERS
-\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
-\pagestyle{fancy} % options: empty , plain , fancy
-\renewcommand{\headrulewidth}{0pt} % customise the layout...
-
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{array,amsmath,graphicx,psfrag,amssymb,subfigure,tabularx,booktabs}
-\usepackage{mparhack}
-\usepackage{setspace}
-\usepackage{natbib}
-\usepackage{multicol}
-\usepackage{color}
-\usepackage{dcolumn}
-\usepackage{hyperref}
-\usepackage{stmaryrd}
-\setcitestyle{authordate,round,semicolon,aysep={,},yysep={,}}
-\bibpunct[:]{(}{)}{;}{a}{,}{,}
-
-\doublespacing
-
-\begin{document}
-\singlespacing
-
-\title[JCR-14-0358​]{JCR-14-0358​ entitled ``Enemy at the Gates: Variation in Economic Growth from Civil Conflict''}
-
-\date{\today~~Version 0.01}
-\maketitle
-
-$\hspace{-5mm}$Dear Professor Huth, \\ [1ex]
-
-We first would like to thank you for the opportunity to revise and resubmit our manuscript.
-We believe the manuscript has greatly benefitted from the Reviewers' helpful and thoughtful comments.
-We have thoroughly revised the manuscript, taking seriously each individual point raised by the Reviewers.
-The revision memo is organized by first responding to your comments and then addressing the reviewers' points.
-Our comments and responses are shown in \textcolor{blue}{\emph{BLUE}} below each point.
-
-We hope you agree that the manuscript has greatly improved through this helpful process and we are looking forward to your response.\\ [1ex]
-
-Sincerely, \\ [1ex]
-
-The Authors.
-
-\section{Editor}
-
-In revising your paper you should consider the full range of questions raised by each of the reviewers as they offer thoughtful comments and suggestions for improving the paper.
-I want to highlight some of those points to emphasize the need for your careful attention to them as you work on revisions.
-
-Regarding R1, there are three issues to highlight. 
-\begin{enumerate}
-\item  First, this reviewer would like to see your main model be run on a fixed effects setup with standard errors clustered on country. \\
-
-\textcolor{blue}{\emph{stuff}}
-
-\item Second, this reviewer would like to see country year observations without conflict included in the analyses instead of being excluded.
-I should note that R2 raises these two concerns as well which suggests that it will be critical to address these issues in your revisions.
-\\
-
-\textcolor{blue}{\emph{stuff}}
-
-\item Third, this reviewer would like to see you estimate a baseline model for the impact of conflict on growth in which GDP growth is regressed on a dummy for armed conflict in a country.
-After that, you can then move onto your central argument and compare your findings to this baseline set of findings.
-\\
-
-\textcolor{blue}{\emph{stuff}}
-
-\end{enumerate}
-
-Regarding R2, there is one additional issue to highlight (points one and two overlap with R1).
-
-\begin{enumerate}
-\item The third point raised is to run a robustness check on the more disaggregated ACLED data set to see if your findings hold up. \\
-
-\textcolor{blue}{\emph{stuff}}
-
-\end{enumerate}
-
-\section{Reviewer: 1}
-
-This paper advances the hypothesis that conflict should exert larger negative impacts on GDP if it located closer to urban centers.
-This idea is tested using subnational data on conflict location from the PRIO Conflict Site Dataset covering the 1989-2008 period.
-The authors present evidence for their hypothesis using a random effects model.
-Robustness checks are conducted verifying the results are not driven by a particular sub-sample.
-
-I very much like the conceptual hypothesis advanced by this paper, and the idea of using the conflict Site Dataset to test it.
-However, I am concerned about the empirical specification used for the analysis.
-Below I outline alternative approaches.
-If these can be implemented, I believe the paper can make a valuable contribution to the conflict literature.
-
-\subsection{Major comments}
-
-\begin{enumerate}
-\item The random effects model is only appropriate compared to the fixed effects model if there is a compelling reason to believe that time invariant country characteristics are uncorrelated with spatial conflict location and income.
-The authors don’t present a Hausman test to try and make the case for random effects.
-Moreover, this doesn’t seem plausible because geographic factors such as roughness of terrain and climactic conditions in remote areas far from urban centers would determine the cost of launching an insurgency in urban vs.
-rural areas and also affect GDP.
-In addition, institutional features such as whether rule of law or state presence extends to rural areas would similarly act as potential omitted variables if country fixed effects are not included.
-A research question along these lines really should exploit variation within a country and show that as urban conflict location chances, GDP growth changes, instead of relying on comparisons across countries.
-As such, I would want to see the results hold with the fixed effects model as the primary model, including country and year fixed effects, and with standard errors clustered on country to control serial correlation over time.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Currently country year observations without conflict are excluded from current specifications.
-They should not be because if low GDP correlates with periods of no conflict, as might arise if sufficient economic activity is required to finance internal conflicts, then this omission would lead to an upward bias on the estimates.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item It will be fairly important to benchmark the results based on distance between conflict location and urban center against the overall effect of conflict.
-In other words, we’d like to know if having any conflict lowers GDP, and if this effect is even stronger if its located closer to urban areas.
-To capture this, the authors should start with a simple specification that regresses GDP growth on a dummy for if any conflict occurred.
-Then they should introduce an interaction between this dummy variable and the conflict distance variable.
-The coefficient on the dummy in this second specification would then capture effects of 0 distance, or if conflicts occurred in cities.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item It wasn’t clear to me how 0 distance was dealt with the current specifications since logs were taken but this would eliminate the 0s.
-It would be very important to include these if in fact conflict in cities are represented by 0 distance in the data.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Instead of treating conflict intensity as a control, it would be useful to re-do the specifications in point 3 above but just restricting to the incidents coded as wars and then restricting to the lower intensity effects.
-Then the authors can test to see if coefficients on the former are in fact larger.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item More information should be provided on how conflict events make it into the Conflict Site Dataset.
-For example, Figure 1 suggests too sparse picture of violent events in Colombia, given that nearly 1/3rd of the Colombian territory was war affected over this period.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item I like the use of the descriptive cases but more should be done with these if they will be included.
-In particular, the economic dynamic of these countries should be mentioned to clarify how the effect of conflict on GDP maps to the hypotheses advanced in the paper.
-I also wondered about the focus on conflict in the NE in India.
-Naxalite conflict has also spread rapidly and is also located in rural areas (which is consistent with the authors’ point), so this would be natural to draw upon as well.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\end{enumerate}
-
 \section{Reviewer: 2}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{
+	We provide a discussion of this alternative explanation following our empirical analysis.
+}
 \end{itemize}
 
-\item he empirical strategy used is a major issue and the authors have to deeply improved this part.
+\item The empirical strategy used is a major issue and the authors have to deeply improved this part.
 The authors mainly use a cross-country comparison using random effects and they justify the use of random effects because their purpose is to explain variation between unit.
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{
+	We retested our hypothesis using the ACLED dataset and here as well we find that our distance measure of conflict to major urban centers is significantly negative. 
+}
 \end{itemize}
@@
 \end{enumerate}
-
-\newpage\tiny
-\end{document}\bye

### 2015-08-17 LaTeX/Revision/reviseLetter.tex
rev letter

@@
 
-\section{Editor}
-
-In revising your paper you should consider the full range of questions raised by each of the reviewers as they offer thoughtful comments and suggestions for improving the paper.
-I want to highlight some of those points to emphasize the need for your careful attention to them as you work on revisions.
-
-Regarding R1, there are three issues to highlight. 
-\begin{enumerate}
-\item  First, this reviewer would like to see your main model be run on a fixed effects setup with standard errors clustered on country. \\
-
-\textcolor{blue}{\emph{stuff}}
-
-\item Second, this reviewer would like to see country year observations without conflict included in the analyses instead of being excluded.
-I should note that R2 raises these two concerns as well which suggests that it will be critical to address these issues in your revisions.
-\\
-
-\textcolor{blue}{\emph{stuff}}
-
-\item Third, this reviewer would like to see you estimate a baseline model for the impact of conflict on growth in which GDP growth is regressed on a dummy for armed conflict in a country.
-After that, you can then move onto your central argument and compare your findings to this baseline set of findings.
-\\
-
-\textcolor{blue}{\emph{stuff}}
-
-\end{enumerate}
-
-Regarding R2, there is one additional issue to highlight (points one and two overlap with R1).
-
-\begin{enumerate}
-\item The third point raised is to run a robustness check on the more disaggregated ACLED data set to see if your findings hold up. \\
-
-\textcolor{blue}{\emph{stuff}}
-
-\end{enumerate}
-
-\section{Reviewer: 1}
-
-This paper advances the hypothesis that conflict should exert larger negative impacts on GDP if it located closer to urban centers.
-This idea is tested using subnational data on conflict location from the PRIO Conflict Site Dataset covering the 1989-2008 period.
-The authors present evidence for their hypothesis using a random effects model.
-Robustness checks are conducted verifying the results are not driven by a particular sub-sample.
-
-I very much like the conceptual hypothesis advanced by this paper, and the idea of using the conflict Site Dataset to test it.
-However, I am concerned about the empirical specification used for the analysis.
-Below I outline alternative approaches.
-If these can be implemented, I believe the paper can make a valuable contribution to the conflict literature.
-
-\subsection{Major comments}
-
-\begin{enumerate}
-\item The random effects model is only appropriate compared to the fixed effects model if there is a compelling reason to believe that time invariant country characteristics are uncorrelated with spatial conflict location and income.
-The authors don’t present a Hausman test to try and make the case for random effects.
-Moreover, this doesn’t seem plausible because geographic factors such as roughness of terrain and climactic conditions in remote areas far from urban centers would determine the cost of launching an insurgency in urban vs.
-rural areas and also affect GDP.
-In addition, institutional features such as whether rule of law or state presence extends to rural areas would similarly act as potential omitted variables if country fixed effects are not included.
-A research question along these lines really should exploit variation within a country and show that as urban conflict location chances, GDP growth changes, instead of relying on comparisons across countries.
-As such, I would want to see the results hold with the fixed effects model as the primary model, including country and year fixed effects, and with standard errors clustered on country to control serial correlation over time.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Currently country year observations without conflict are excluded from current specifications.
-They should not be because if low GDP correlates with periods of no conflict, as might arise if sufficient economic activity is required to finance internal conflicts, then this omission would lead to an upward bias on the estimates.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item It will be fairly important to benchmark the results based on distance between conflict location and urban center against the overall effect of conflict.
-In other words, we’d like to know if having any conflict lowers GDP, and if this effect is even stronger if its located closer to urban areas.
-To capture this, the authors should start with a simple specification that regresses GDP growth on a dummy for if any conflict occurred.
-Then they should introduce an interaction between this dummy variable and the conflict distance variable.
-The coefficient on the dummy in this second specification would then capture effects of 0 distance, or if conflicts occurred in cities.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item It wasn’t clear to me how 0 distance was dealt with the current specifications since logs were taken but this would eliminate the 0s.
-It would be very important to include these if in fact conflict in cities are represented by 0 distance in the data.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Instead of treating conflict intensity as a control, it would be useful to re-do the specifications in point 3 above but just restricting to the incidents coded as wars and then restricting to the lower intensity effects.
-Then the authors can test to see if coefficients on the former are in fact larger.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item More information should be provided on how conflict events make it into the Conflict Site Dataset.
-For example, Figure 1 suggests too sparse picture of violent events in Colombia, given that nearly 1/3rd of the Colombian territory was war affected over this period.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item I like the use of the descriptive cases but more should be done with these if they will be included.
-In particular, the economic dynamic of these countries should be mentioned to clarify how the effect of conflict on GDP maps to the hypotheses advanced in the paper.
-I also wondered about the focus on conflict in the NE in India.
-Naxalite conflict has also spread rapidly and is also located in rural areas (which is consistent with the authors’ point), so this would be natural to draw upon as well.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\end{enumerate}
-
-\section{Reviewer: 2}
-The authors claim that the distance between cities (or capital) and the location of violent events during a civil conflict is a first order argument to explain the effect of conflict on economic growth.
-I’m fully convinced of the interest of the question to understand the legacies of civil conflict.
-Empirical evidence on the effect of civil conflict on growth is notably crucial for the post- recovery policies.
-While I find the the question very interesting, I think there is a number of issues that remain to be addressed.
-
-\subsection{Major Comments}
-
-\begin{enumerate}
-
-\item  I’m convinced by the interpretation of the results but I can imagine also an alternative story.
-The state capacity is negatively correlated to the distance (to the capital or main cities - see Buhaug, 2010).
-That means that the fighting cost for a rebel group is decreasing with the distance to the capital.
-In other words, it is only the strongest (richest) rebel groups that are able to be close enough to the capital.
-The effect detected in the paper is perhaps only the effect of size groups.
-The biggest groups are the more violent, the more disruptive and consequently that have an higher effect on economic growth.
-I’m not sure how it will be possible to arbitrate between this alternative story and the story of the authors.
-At the end, a discussion around this alternative explanation would be profitable to the paper.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item he empirical strategy used is a major issue and the authors have to deeply improved this part.
-The authors mainly use a cross-country comparison using random effects and they justify the use of random effects because their purpose is to explain variation between unit.
-But the cross-country comparison doesn’t involve the use of random effects.
-The authors missed also to control for time-specific shocks that are common to all countries by including year dummies.
-The year dummies will absorb yearly worldwide changes such as economic shocks, global climate shocks or natural resource price shocks.
-I don’t believe also the explanation to avoid the use of country fixed effects.
-I think the authors should follow the following road map:
-\begin{itemize}
-\item Simple correlation between GDP growth and the distance of conflict.
-\item Inclusion of the control variables.
-\item Inclusion of year fixed effects.
-\item Inclusion of both year and country fixed effects.
-\end{itemize}
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Sample.
-I’m not convinced by the sample choice.
-I would like to see results with a full sample of countries from 1989 to 2008, including peace countries.
-I expect the author to interact their measure of distance to conflict with a dummy coded 1 for country in civil conflict and 0 otherwise
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Data on conflicts.
-One could imagine that the quality/quantity of reports on conflicts is negatively correlated to this distance to the capital.
-I would appreciate a discussion on the potential report bias and how it could influence the results.
-As a robustness, I expect the authors to use ACLED data that are commonly used now as data for disaggregated analysis.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item To avoid issues linked to reverse causation, I would consider the list of urban centers
-at the beginning of the period.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Definition of variables.
-The authors take the minimum distance to the conflict as explanatory variable.
-I would like to see alternative measures to ensure that the results are not sensitive to the definition of the main variable.
-For instance, the weighted (by the distance) sum of the number of events is a credible candidate as an alternative measure.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\end{enumerate}
-
-\subsection{Minor Comments}
-
-\begin{enumerate}
-
-\item Introduction.
-The example on Mexico looks strange.
-By many aspects, the drug war in Mexico is very different to conflicts in Republic Democratic of Congo or in Uganda.
-In other words, it is difficult to compare conflicts with genocide, massive internal migration, ethnic cleavages with a drug war where almost all citizens support the government.
-The recent case of Nigeria and Cameroon with Boko Haram looks to be a better fit with the story of the authors.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item The authors claim they focus on the proximities of conflict to cities and not on the area covered by the conflict.
-I’m wondering whether the effect of the proximities of conflict to cities would be intensify by the area of the conflict.
-I expect the effect of the proximities of conflict to cities to be higher if the area of conflict is biggest.
-A very simple interaction term between distance and area would be appropriate to uncover this mechanism.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Results. Conflict duration and the number of conflicts a country is facing have an unexpected effect on growth. I would see a discussion to explain this results.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Area covered by conflict. I don’t understand why the authors use a binary measure instead of the continuous variable.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Robustness. The strategy that consists to run a six-fold cross-validation is convincing. In the same spirit, I would like to see the same exercise when one country is left out of the sample.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item Figures have to be self contained.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item The visual presentation of the results are interesting but the classical way to present results (through tables) is a requirement.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\item The recent works on cities of Quoc-Anh Do seems to me as a complement to this paper.
-
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
-
-\end{enumerate}
+\input{editor.tex}
+\input{rev1.tex}
+\input{rev2.tex}
 

### 2015-08-17 R/Analysis/fullPanelModel.R

@@ -34,16 +34,16 @@ for(var in distVars){
 	modData$tmp = yData[,var][match(modData$cyear, yData$cyear)]
 	names(modData)[ncol(modData)] = var
 
-	# Invert variable
-	modData[,var] = 1/modData[,var]
-
-	# Convert NAs to zero
-	modData[,var][is.na( modData[,var] )] = 0
-
 	# Log transformed version
 	lnVar = paste0('ln',var)
 	modData$tmp = log(modData[,var] + 1)
 	names(modData)[ncol(modData)] = lnVar
+
+	# Invert variable
+	modData[,lnVar] = 1/modData[,lnVar]
+
+	# Convert NAs to zero
+	modData[,lnVar][is.na( modData[,lnVar] )] = 0
 
 	# Create interaction variable
 	modData$tmp = modData$civwar * modData[,lnVar]
@@ -69,9 +69,13 @@ modForm = function(dv='lngdpGr_l0', ivs, id='ccode', type='random'){
 }
 
 dv = 'lngdpGr_l0'
+# kivs = c(
+# 	'lncapDist.min', 
+# 	'lnminDist.min'
+# 	)
 kivs = c(
-	'lncapDist.min', 
-	'lnminDist.min'
+	'civwar', 
+	'nconf'
 	)
 cntrls = c('upperincome', 'lninflation_l1',  'polity2', 'resourceGDP',  'gdpGr.mean_l0'
 	# , 'civwar'

### 2015-08-18 LaTeX/RhodiumIntro.tex

--- 2014-10-28 LaTeX/RhodiumIntro.tex
@@
 
-Further few in the literature have sought to explain puzzling cases of domestic armed conflict having little impact on macroeconomic growth.
-Mexico, for example, has been engaged in a drug war since December 2006 and the number of deaths stemming from this civil conflict have only increased since that time.
+Further, few in the literature have sought to explain puzzling cases of domestic armed conflicts that have little impact on macroeconomic growth.
+Nigeria and Cameroon, for instance, have both been engaged in violent conflict with Boko Haram, a group of militants determined to establish an Islamic state in West Africa.
+In Nigeria, the death toll has steadily risen since 2011; the Council on Foreign Relations estimates that the conflict had resulted in over 40,000 casualties by mid-2015 \citep{cfr:2015}.
+However, Boko Haram primarily operates in the rural and relatively less populated north-eastern regions of Nigeria and Cameroon.
+During this conflict, both countries have enjoyed steady economic growth.
+When Nigeria rebased its economy in 2014, it overtook South Africa as the continent's largest economy.
+
+Mexico has been engaged in a drug war since December 2006 and the number of deaths stemming from this civil conflict have only increased since that time.
 Yet, even as fatalities due to the drug war reached new peaks, in 2012, Vikram Pandit of Citigroup cited Mexico as being extremely well poised for growth and projected that its economy may surpass that of its much larger regional rival, Brazil, within a decade \citep{vardi:2012}.

### 2015-08-18 LaTeX/RhodiumLit.tex

@@
 
-\citet{collier:1999} identifies five avenues through which civil conflict can impede economic performance: through the \textit{destruction} of resources, through \textit{disruption} of social and economic activity, through \textit{diversion} of resources to the war effort, through \textit{dissaving}, and through \textit{portfolio substition} or divestment.
+\citet{collier:1999} identifies five avenues through which civil conflict can impede economic performance: through the \textit{destruction} of resources, through \textit{disruption} of social and economic activity, through \textit{diversion} of resources to the war effort, through \textit{dissaving}, and through \textit{portfolio substitution} or divestment.
 Of course, these mechanisms are related to one another; portfolio substitution may be exacerbated by the destruction of resources or the disruption of socioeconomic activity.

### 2015-08-18 LaTeX/RhodiumTheory.tex

--- 2014-10-28 LaTeX/RhodiumTheory.tex
@@
 
+Nigeria and Cameroon have battled Boko Haram in a bloody conflict in their rural northern regions for half a decade.
+For the period between 2009 and 2013, the National Consortium for the Study of Terrorism and Responses to Terrorism (START) described Boko Haram as ``among the deadliest [terrorist groups] in the world'' \citep{pate:etal:2014}.
+The groups tactics range from car and suicide bombings to direct assaults to mass kidnappings.
+Nonetheless, Nigeria and Cameroon have both maintained strong economic growth during this period.
+The African Development Bank Group (AFDB) described Nigeria's economic growth from 2004 to 2014 as ``robust'' and projected ``moderate'' growth of 5\% for 2015 \citep{afdb:nigeria:2015}.
+On Cameroon, the AFDB said ``despite the security and humanitarian crisis in the region, Cameroonian growth remains strong at above 5\%'' \citep{afdb:cameroon:2015}.
+
 It is important to note that Mexico does not appear in the civil war dataset chosen for this study.
@@
 
+The examples cited here seemingly break from the mold by prospering economically while facing high levels of internal violence.
+A common characteristic of these cases is the geographic distribution of conflict; violent armed groups operate primarily in rural areas away from major cities.
+
 % Note to Ben: If you have more to add about Mexico here that might be good

### 2015-08-18 LaTeX/RhodiumIntro.tex
recompiled with new intro
new intro is great

@@
-% Note to Ben: Can you check if the plot margins in the master rhodium.tex file are correct for JCR?
-
 \section{Introduction}
@@
 Nigeria and Cameroon, for instance, have both been engaged in violent conflict with Boko Haram, a group of militants determined to establish an Islamic state in West Africa.
-In Nigeria, the death toll has steadily risen since 2011; the Council on Foreign Relations estimates that the conflict had resulted in over 40,000 casualties by mid-2015 \citep{cfr:2015}.
+In Nigeria, the death toll has steadily risen since 2011; the Council on Foreign Relations estimates that the conflict had resulted in over 40,000 casualties by mid-2015 \citep{CFR:2015}.
 However, Boko Haram primarily operates in the rural and relatively less populated north-eastern regions of Nigeria and Cameroon.

### 2015-08-18 LaTeX/Revision/rev1.tex
recompiled with new intro
expl for why interaction wont work

@@
 \begin{itemize}
-\item \textcolor{blue}{
+\item \textcolor{blue}{\emph{
 	For the ``Capital City'' and ``Any Major City'' models we ran a Hausman test to see if fixed or random effects were appropriate for our dataset, and in both cases we do not reject the null hypothesis of the Hausman test at a 90 or 95\% confidence interval indicating that it is acceptable to use random effects.
 We have added a discussion of this analysis into our empirical section.
-}
+	However, as Clark \& Linzer (2015) show the Hausman test is by itself not a sufficient statistic to choose between fixed or random effects.
+They provide a typology for assessing whether or not to use fixed or random effects.
+Specifically they suggest to look at the ``the size of the dataset (both number of units and number of observations per unit), the level of correlation between the covariate and unit effects, and the extent of within-unit variation in the independent variable relative to the dependent variable'' (pg., 2).
+We employ their typology to further test whether our choice of random effects over fixed effects is appropriate.
+}}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{
+\item \textcolor{blue}{\emph{
 	We have run a t-test to test whether GDP is lower during times of no conflict versus conflict and we find that GDP is higher during conflict years than non-conflict years at a 95\% confidence interval.
 Thus the possibility of an upward bias on our main model estimates should not be so severe.
-}
+}}
 \end{itemize}
@@
 To capture this, the authors should start with a simple specification that regresses GDP growth on a dummy for if any conflict occurred.
-Then they should introduce an interaction between this dummy variable and the conflict distance variable.
-The coefficient on the dummy in this second specification would then capture effects of 0 distance, or if conflicts occurred in cities.
 
 \begin{itemize}
-\item \textcolor{blue}{
+\item \textcolor{blue}{\emph{
 	We have run a model on our full panel dataset to calculate a benchmark on the effect of any conflict on GDP growth.
@@
 The key finding from this analysis is that a civil war is related to lower levels of GDP growth, however, this effect is marginal and only significant at a 90\% confidence interval.
-	In terms of including an interaction to the model, 
-}
+Further the substantive effect of civil war is ...
+compared to ...
+when conflicts are very proximate to city centers.
+}}
+\end{itemize}
+
+\item Then they should introduce an interaction between this dummy variable and the conflict distance variable.
+The coefficient on the dummy in this second specification would then capture effects of 0 distance, or if conflicts occurred in cities.
+
+\begin{itemize}
+\item \textcolor{blue}{\emph{
+	Including an interaction in this way is problematic for estimating the effect of conflict distance on conflict.
+The logged, minimum distance variable ranges from approximately 0.33 to 7.31, with closer values indicating that conflict is more proximate to an urban center for that country-conflict-year.
+This variable is NA for cases in which no conflict occurred for a given country year, thus before we interact it with the civil war variable in a full panel set up we would need to introduce some values for the NAs.
+One possibility is to simply invert the distance variable and then set the NAs to zero.
+However, the choice of introducing a zero for the NAs would be arbitrary and problematic, as our variable would no longer truly be continuous.
+Instead it would be discontinous in that we would have a large lump of observations at zero and then no observations until 1/7.31.
+Beyond the problems associated with transforming the variable in this way we would also run into issues of perfect collinearity with the inverted conflict distance measure and the interaction variable.
+The collinearity would result because the binary conflict variable is zero for every case that the inverted conflict distance variable is zero and one otherwise, meaning that multiplying the two will simply result in the inverted conflict distance variable again.
+	We have spent a fair bit of time trying to think of alternative approaches to modeling this in a full panel context using mixture or hierarchical approaches, but could find no mentions to develop a model for this type of data.
+	Despite this we strongly feel that our results are illustrative of an important and meaningful finding for the conflict literature.
+There has been very little discussion of the role that the spatial distribution of conflict plays in shaping macroeconomic outcomes, and the findings that we present here are the first to begin to disentangle this relationship.
+}}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{
+\item \textcolor{blue}{\emph{
 	The minimum distance of the centroid of a conflict from any major or capital city in our dataset is 0.38 UNITS so this is not an issue for our analysis.
-}
+}}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{
+\item \textcolor{blue}{\emph{
 	We reran the models per this specification and have included the results in the appendix.
 In both low intensity and high intensity cases we find that the distance variables remain significant and in the hypothesized direction.
-}
+}}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{
+\item \textcolor{blue}{\emph{
 	The PRIO Conflict Site dataset provides information on the centroid of a conflict and that is what is plotted in each of the conflict map figures.
@@
 If we were to try and construct the distance from a city to any part of a conflict area we would have to define the conflict area as just a perfect circle with a given radius, which would not actually reflect where conflict was taking place.
-}
+}}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{
+\item \textcolor{blue}{\emph{
 	BEN will add stuff here. 
-}
+}}
 \end{itemize}

### 2015-08-18 LaTeX/Revision/rev2.tex
expl for why interaction wont work

@@
 \begin{itemize}
-\item \textcolor{blue}{
+\item \textcolor{blue}{\emph{
 	We provide a discussion of this alternative explanation following our empirical analysis.
-}
+}}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{\emph{
+	For the ``Capital City'' and ``Any Major City'' models we ran a Hausman test to see if fixed or random effects were appropriate for our dataset, and in both cases we do not reject the null hypothesis of the Hausman test at a 90 or 95\% confidence interval indicating that it is acceptable to use random effects.
+We have added a discussion of this analysis into our empirical section.
+	However, as Clark \& Linzer (2015) show the Hausman test is by itself not a sufficient statistic to choose between fixed or random effects.
+They provide a typology for assessing whether or not to use fixed or random effects.
+Specifically they suggest to look at the ``the size of the dataset (both number of units and number of observations per unit), the level of correlation between the covariate and unit effects, and the extent of within-unit variation in the independent variable relative to the dependent variable'' (pg., 2).
+We employ their typology to further test whether our choice of random effects over fixed effects is appropriate.
+}}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{\emph{
+	Including an interaction in this way is problematic for estimating the effect of conflict distance on conflict.
+The logged, minimum distance variable ranges from approximately 0.33 to 7.31, with closer values indicating that conflict is more proximate to an urban center for that country-conflict-year.
+This variable is NA for cases in which no conflict occurred for a given country year, thus before we interact it with the civil war variable in a full panel set up we would need to introduce some values for the NAs.
+One possibility is to simply invert the distance variable and then set the NAs to zero.
+However, the choice of introducing a zero for the NAs would be arbitrary and problematic, as our variable would no longer truly be continuous.
+Instead it would be discontinous in that we would have a large lump of observations at zero and then no observations until 1/7.31.
+Beyond the problems associated with transforming the variable in this way we would also run into issues of perfect collinearity with the inverted conflict distance measure and the interaction variable.
+The collinearity would result because the binary conflict variable is zero for every case that the inverted conflict distance variable is zero and one otherwise, meaning that multiplying the two will simply result in the inverted conflict distance variable again.
+	We have spent a fair bit of time trying to think of alternative approaches to modeling this in a full panel context using mixture or hierarchical approaches, but could find no mentions to develop a model for this type of data.
+	Despite this we strongly feel that our results are illustrative of an important and meaningful finding for the conflict literature.
+There has been very little discussion of the role that the spatial distribution of conflict plays in shaping macroeconomic outcomes, and the findings that we present here are the first to begin to disentangle this relationship.
+}}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{
+\item \textcolor{blue}{\emph{
 	We retested our hypothesis using the ACLED dataset and here as well we find that our distance measure of conflict to major urban centers is significantly negative. 
-}
+}}
 \end{itemize}
 
-\item To avoid issues linked to reverse causation, I would consider the list of urban centers
-at the beginning of the period.
+\item To avoid issues linked to reverse causation, I would consider the list of urban centers at the beginning of the period.
 
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{\emph{
+	When rerunning the model using the continuous variable each of the key results remain similar.
+}}
 \end{itemize}

### 2015-08-18 R/Analysis/fullPanelModel.R

@@ -1,3 +1,8 @@
+set.seed(6886)
+fakeData = data.frame(y = rnorm(100), bin=rbinom(100,1,0.5), x=0)
+fakeData$x[fakeData$bin==1] = rnorm(sum(fakeData$bin), .23, .25)
+
+
 if(Sys.info()["user"]=="janus829" | Sys.info()["user"]=="s7m"){
   source('~/Research/Rhodium/R/setup.R')}
 if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}

### 2015-08-18 LaTeX/RhodiumEmp.tex
recompiled with new intro
syncing up

@@
 
-% Note to Ben: Anything else to add about why including polity would be important in the model?
-% Note to Shahryar: Nope.
-
 To estimate variation in growth rates, we use a random effects model clustered on countries.
 A random effects specification is preferred to using fixed effects here as we are not interested in estimating the change in GDP within units over time, rather our purpose is to explain variation between units.
+However, to ensure that it is also statistically justifiable to make this choice we run a Hausman specification test \citep{greene:2008}.
+For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at either the 90 and 95\% confidence intervals, providing at least some initial evidence that we are justified in our choice.
+However, as \citet{clark:linzer:2015} note not finding a significant difference through the Hausman test does not necessarily mean ``that the random effects is `safely` free from bias, and therefore to be preferred over the fixed effects estimator'' (pg., 2).
+We utilize their more nuanced typology for further arbitrating between fixed and random effects.
+
 The total number of observations we have for this analysis are 497 country-year cases of civil war from 68 different countries during the period of 1989 to 2008.

### 2015-08-18 R/Analysis/fullPanelModel.R

@@ -1,8 +1,3 @@
-set.seed(6886)
-fakeData = data.frame(y = rnorm(100), bin=rbinom(100,1,0.5), x=0)
-fakeData$x[fakeData$bin==1] = rnorm(sum(fakeData$bin), .23, .25)
-
-
 if(Sys.info()["user"]=="janus829" | Sys.info()["user"]=="s7m"){
   source('~/Research/Rhodium/R/setup.R')}
 if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}

### 2015-08-18 R/Analysis/revLetterExtra.R

@@ -35,3 +35,11 @@ modData$polity2 = modData$polity2 + 11
 # Across full panel
 with(modData, t.test(lngdp~civwar, alternative='two.sided') )
 ###################################################################
+
+###################################################################
+# Interaction wont work
+set.seed(6886)
+fakeData = data.frame(y = rnorm(100), bin=rbinom(100,1,0.5), x=0)
+fakeData$x[fakeData$bin==1] = rnorm(sum(fakeData$bin), .23, .25)
+fakeData$i = fakeData$x*fakeData$bin
+###################################################################

### 2015-08-18 LaTeX/Revision/editor.tex
baseline model disc, sep fixefvre from paper

@@
 
-\textcolor{blue}{\emph{stuff}}
+\textcolor{blue}{\emph{
+	For the ``Capital City'' and ``Any Major City'' models we ran a Hausman test to see if fixed or random effects were appropriate for our dataset, and in both cases we do not reject the null hypothesis of the Hausman test at a 90 or 95\% confidence interval indicating that it is acceptable to use random effects.
+We have added a discussion of this analysis into our empirical section.
+	However, as Clark \& Linzer (2015) show the Hausman test is by itself not a sufficient statistic to choose between fixed or random effects.
+They provide a typology for assessing whether or not to use fixed or random effects.
+Specifically they suggest to look at the ``the size of the dataset (both number of units and number of observations per unit), the level of correlation between the covariate and unit effects, and the extent of within-unit variation in the independent variable relative to the dependent variable'' (pg., 2).
+We employ their typology to further test whether our choice of random effects over fixed effects is appropriate.
+}}
 
@@
 
-\textcolor{blue}{\emph{stuff}}
+\textcolor{blue}{\emph{
+	Including an interaction in this way is problematic for estimating the effect of conflict distance on conflict.
+The logged, minimum distance variable ranges from approximately 0.33 to 7.31, with closer values indicating that conflict is more proximate to an urban center for that country-conflict-year.
+This variable is NA for cases in which no conflict occurred for a given country year, thus before we interact it with the civil war variable in a full panel set up we would need to introduce some values for the NAs.
+One possibility is to simply invert the distance variable and then set the NAs to zero.
+However, the choice of introducing a zero for the NAs would be arbitrary and problematic, as our variable would no longer truly be continuous.
+Instead it would be discontinous in that we would have a large lump of observations at zero and then no observations until 1/7.31.
+Beyond the problems associated with transforming the variable in this way we would also run into issues of perfect collinearity with the inverted conflict distance measure and the interaction variable.
+The collinearity would result because the binary conflict variable is zero for every case that the inverted conflict distance variable is zero and one otherwise, meaning that multiplying the two will simply result in the inverted conflict distance variable again.
+	We have spent a fair bit of time trying to think of alternative approaches to modeling this in a full panel context using mixture or hierarchical approaches, but could find no mentions to develop a model for this type of data.
+	Despite this we strongly feel that our results are illustrative of an important and meaningful finding for the conflict literature.
+There has been very little discussion of the role that the spatial distribution of conflict plays in shaping macroeconomic outcomes, and the findings that we present here are the first to begin to disentangle this relationship.
+}}
 
@@
 
-\textcolor{blue}{\emph{stuff}}
+\textcolor{blue}{\emph{
+	stuff
+}}
 
@@
 
-\textcolor{blue}{\emph{stuff}}
+\textcolor{blue}{\emph{
+	We retested our hypothesis using the ACLED dataset and here as well we find that our distance measure of conflict to major urban centers is significantly negative. 
+}}
 

### 2015-08-18 LaTeX/RhodiumEmp.tex
baseline model disc, sep fixefvre from paper

@@
 However, as \citet{clark:linzer:2015} note not finding a significant difference through the Hausman test does not necessarily mean ``that the random effects is `safely` free from bias, and therefore to be preferred over the fixed effects estimator'' (pg., 2).
-We utilize their more nuanced typology for further arbitrating between fixed and random effects.
+We utilize their more nuanced typology for further arbitrating between fixed and random effects, and again we find that random effects are preferred in this case.\footnote{A lengthier discussion of the \citet{clark:linzer:2015} procedure and its application to our data can be found in the Appendix.}
 
@@
 	& \;+\; \beta_{7}(Inflation_{i,t-1}) \;+\; \beta_{8}(Democracy_{i,t-1}) \\
-	& \;+\; \beta_{9}(Resource \; Rents/GDP_{t-1}) \;+\; \beta_{10}(World \; GDP \; Growth_{t}) \\
-	& \;+\; \mu_{i,t} \;+\; \epsilon_{i,t}
+	& \;+\; \beta_{9}(Resource \; Rents/GDP_{t-1}) \;+\; \beta_{10}(World \; GDP \; Growth_{t})
 \end{align*}
+
+\subsection{Baseline Model}
+
+Before we move to discussing the results of the model specification that we have described above we estimate a simple, baseline model to assess the effect of any civil conflict on growth.
+For this model we use a specification as similar as possible to the one we explicated in the previous section, with the key difference being that this baseline model is estimated using a full country-year panel with fixed effects.\footnote{In choosing between fixed and random effects, we again followed the typology set out by \citet{clark:linzer:2015}, and, in this case, found that the fixed effects specification was preferred.} The dependent variable is again annual percent change in GDP from the World Development Indicators, and the key independent variable here is whether or not the country was engaged in a civil war in the previous year according to the PRIO Conflict dataset.
+Since we are using a full country-year panel, we have to omit the PRIO conflict specific variables (e.g., conflict intensity, conflict duration) as they are undefined for country-year observations in which no conflict was taking place.
+The rest of the independent variables are similar to the model specified in the previous section, the exact estimation model we use is shown below:
+
+\begin{align*}
+	\% \Delta GDP_{i,t} &= \beta_{1}(Civil War)_{i,t-1}) \\
+	& beta_{6}(Upper \; Income_{i,t}) \;+\; \beta_{7}(Inflation_{i,t-1}) \\	
+	& \beta_{8}(Democracy_{i,t-1}) \;+\; \beta_{9}(Resource \; Rents/GDP_{t-1}) \\
+	& \;+\; \beta_{10}(World \; GDP \; Growth_{t})
+\end{align*}
+
+The results of this model are shown below in figure~\ref{fig:civWarCoefplot}.
+We will eschew discussing the controls since the primary purpose of this analysis is to determine a baseline effect for civil war.
+
+\begin{figure}
+	\resizebox{.45\textwidth}{!}{\input{civWarCoefPlot.tex}}
+	\caption{Fixed effects regression results using full country-year panel.
+Darker colors indicates that the coefficient estimate is significantly different from zero at a 95\% CI, while lighter the same for a 90\% CI.
+Grey indicates that the estimate is not significantly different from zero at either of those intervals.}
+	\label{fig:civWarCoefplot}
+\end{figure}
 
@@
 Countries deriving greater shares of their GDP from natural resource rents see slighlty higher levels of growth, and, not surprisingly, the average of world GDP growth is positively related to our dependent variable.
-
-% Note to Ben: Anything you think we should say about the two surprising findings above
 

### 2015-08-18 R/Analysis/fixefVre.R

@@ -1,0 +1,115 @@
+if(Sys.info()["user"]=="janus829" | Sys.info()["user"]=="s7m"){ source('~/Research/Rhodium/R/setup.R')}
+if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
+library(Hmisc)
+# Load conflict country year data
+setwd(pathData)
+# load('combinedData_Orig.rda'); modData=yData
+load('combinedData.rda'); modData=yData
+# load('combinedData_loInt.rda'); modData=yData
+# load('combinedData_hiInt.rda'); modData=yData
+
+# Gen tikz?
+genTikz=FALSE
+
+# CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
+###################################################################
+logTrans=function(x){ log( x + abs(min(x, na.rm=T)) + 1) }
+
+# Log transforming DVs
+modData$lngdp_l0 = log(modData$gdp_l0)
+modData$lngdp = log(modData$gdp)
+modData$lngdpGr_l0 = (modData$lngdp_l0-modData$lngdp)/modData$lngdp_l0
+modData$lngdpGr_l0 = modData$gdpGr_l0
+
+# Transformations for conflict variables
+modData$lnminDist.min <- log(modData$minDist.min+1)
+modData$lncapDist.min <- log(modData$capDist.min+1)
+modData$lnminDist.mean <- log(modData$minDist.mean+1)
+modData$lncapDist.mean <- log(modData$capDist.mean+1)
+modData$lnminDistACLED.min <- log(modData$minDistACLED.min+1)
+modData$lnminDistACLED.mean <- log(modData$minDistACLED.mean+1)
+modData$lncapDistACLED.min <- log(modData$acledCapDist.min+1)
+modData$lncapDistACLED.mean <- log(modData$acledCapDist.mean+1)
+modData$Int.max <- modData$Int.max-1
+
+# Transformations for other controls
+modData$lngdpCap = log(modData$gdpCap)
+modData$lninflation_l1 = logTrans(modData$inflation_l1)
+modData$democ = as.numeric(modData$polity2>=6)
+modData$polity2 = modData$polity2 + 11
+
+###################################################################
+
+## MODELS FOR GDP GROWTH (ANNUAL %)
+###################################################################
+# Model parameters
[…]

### 2015-08-18 R/Analysis/fullPanelModel.R

@@ -9,7 +9,7 @@ load('combinedData.rda')
 modData = fullData
 
 # Gen tikz?
-genTikz=FALSE
+genTikz=TRUE
 
 # CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
 ###################################################################
@@ -78,38 +78,53 @@ kivs = c(
 	'nconf'
 	)
 cntrls = c('upperincome', 'lninflation_l1',  'polity2', 'resourceGDP',  'gdpGr.mean_l0'
-	# , 'civwar'
 	)
 
 # Run random effect models
 civwarForm=modForm(ivs=c(kivs[1], cntrls), type='random')
-nconfForm=modForm(ivs=c(kivs[2], cntrls), type='random')
 mCivWar = lmer(civwarForm, data = modData ); summary(mCivWar)$'coefficients'
-mNConf = lmer(nconfForm, data = modData ); summary(mNConf)$'coefficients'
 
 # Fixef Robustness Checks
 civwarFormFE=modForm(ivs=c(kivs[1], cntrls), type='fixed')
-nconfFormFE=modForm(ivs=c(kivs[2], cntrls), type='fixed')
 mCivWar = lm(civwarFormFE, data = modData ); summary(mCivWar)$'coefficients'[1:(length(cntrls)+1),]
-mNConfFixefCntry = lm(nconfFormFE, data = modData ); summary(mNConfFixefCntry)$'coefficients'[1:(length(cntrls)+1),]
 
 # Run Hausman test on city and cap models
 library(plm)
 civwarFormBase=modForm(ivs=c(kivs[1], cntrls), type='none')
-nconfFormBase=modForm(ivs=c(kivs[2], cntrls), type='none')
 
 regData = modData[,c(dv, kivs, cntrls, 'ccode', 'year')]
 plmFE = plm(civwarFormBase, data=regData, model='within', effect='individual', index=c('ccode','year'))
 plmRE = plm(civwarFormBase, data=regData, model='random', effect='individual', index=c('ccode','year'))
 phtest(plmFE, plmRE)
 
-plmFE = plm(nconfFormBase, data=regData, model='within', effect='individual', index=c('ccode','year'))
-plmRE = plm(nconfFormBase, data=regData, model='random', effect='individual', index=c('ccode','year'))
-phtest(plmFE, plmRE)
-
 # Basic model diags
[…]

### 2015-08-18 R/Analysis/models.R

@@ -37,13 +37,12 @@ modData$lngdpCap = log(modData$gdpCap)
 modData$lninflation_l1 = logTrans(modData$inflation_l1)
 modData$democ = as.numeric(modData$polity2>=6)
 modData$polity2 = modData$polity2 + 11
-
 ###################################################################
 
 ## MODELS FOR GDP GROWTH (ANNUAL %)
 ###################################################################
 # Model parameters
-modForm = function(dv='lngdpGr_l0', ivs, id='ccode', type='random'){
+modForm = function(dv='gdpGr_l0', ivs, id='ccode', type='random'){
   base = paste(dv, paste(ivs, collapse=' + '), sep=' ~ ')
   if(type=='random'){
     eff = paste0('(1 |', id, ')')
@@ -57,7 +56,7 @@ modForm = function(dv='lngdpGr_l0', ivs, id='ccode', type='random'){
   return(formula(base))
 }
 
-dv = 'lngdpGr_l0'
+dv = 'gdpGr_l0'
 kivs = c('lnminDist.mean', 'lncapDist.mean')
 cntrls = c(
   'Int.max',
@@ -74,38 +73,6 @@ mCity = lmer(ctyForm, data = modData ); summary(mCity)$'coefficients'
 mCap = lmer(capForm, data = modData ); summary(mCap)$'coefficients'
 mAcled = lmer(acledForm, data = modData ); summary(mAcled)$'coefficients'
 mAcledCap = lmer(acledFormCap, data=modData); summary(mAcledCap)$'coefficients'
-
-# Fixef Robustness Checks
-ctyFormFE=modForm(ivs=c(kivs[1], cntrls), type='fixed')
-capFormFE=modForm(ivs=c(kivs[2], cntrls), type='fixed')
-# We can't use the modForm() function here because Int.max, durSt1max, confAreaProp are not defined for ACLED data:
-acledFormFE = lngdpGr_l0 ~ lnminDistACLED.mean + nconf + upperincome + lninflation_l1 + polity2 + resourceGDP + gdpGr.mean_l0 + factor(ccode) -1
-mCityFixefCntry = lm(ctyFormFE, data = modData ); summary(mCityFixefCntry)$'coefficients'[1:(length(cntrls)+1),]
-mCapFixefCntry = lm(capFormFE, data = modData ); summary(mCapFixefCntry)$'coefficients'[1:(length(cntrls)+1),]
[…]

### 2015-08-18 R/Analysis/revLetterExtra.R

@@ -4,9 +4,10 @@ if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
 
 # Load conflict country year data
 setwd(pathData)
-load('fullData.rda')
+# load('fullData.rda')
+# modData = fullData # For full panel extensions
 load('combinedData.rda')
-modData = fullData
+modData=yData # For country-conflict-year extensions
 
 # Gen tikz?
 genTikz=FALSE
@@ -42,4 +43,34 @@ set.seed(6886)
 fakeData = data.frame(y = rnorm(100), bin=rbinom(100,1,0.5), x=0)
 fakeData$x[fakeData$bin==1] = rnorm(sum(fakeData$bin), .23, .25)
 fakeData$i = fakeData$x*fakeData$bin
+###################################################################
+
+###################################################################
+# Number of t observations by country
+# Transformations for conflict variables
+modData$lnminDist.min <- log(modData$minDist.min+1)
+modData$lncapDist.min <- log(modData$capDist.min+1)
+modData$lnminDist.mean <- log(modData$minDist.mean+1)
+modData$lncapDist.mean <- log(modData$capDist.mean+1)
+modData$lnminDistACLED.min <- log(modData$minDistACLED.min+1)
+modData$lnminDistACLED.mean <- log(modData$minDistACLED.mean+1)
+modData$lncapDistACLED.min <- log(modData$acledCapDist.min+1)
+modData$lncapDistACLED.mean <- log(modData$acledCapDist.mean+1)
+modData$Int.max <- modData$Int.max-1
+
+dv = 'lngdpGr_l0'
+kivs = c('lnminDist.mean', 'lncapDist.mean')
+cntrls = c(
+  'Int.max',
+  'durSt1max',  'confAreaProp', 'nconf', 
+  'upperincome', 'lninflation_l1',  'polity2', 'resourceGDP',  'gdpGr.mean_l0')
+
+vars = c(dv, kivs, cntrls, 'ccode', 'year')
+
+slice = na.omit( modData[,vars] )
+
+cntryCnts = table(slice$ccode)
+length(cntryCnts[cntryCnts>5]) / length(cntryCnts)
+length(cntryCnts[cntryCnts<=5]) / length(cntryCnts)
+# ~53% of data has fewer than five observations per unit
 ###################################################################

### 2015-08-18 LaTeX/RhodiumEmp.tex
more on baseline model

@@
 
+Since our primary interest here is just
+
 The results of this model are shown below in figure~\ref{fig:civWarCoefplot}.
 We will eschew discussing the controls since the primary purpose of this analysis is to determine a baseline effect for civil war.
+Additionally, for the sake of space we do not show the full results from this regression, though they are available in section \ref{baseline} of the Appendix.
+The key result pertains to the civil war variable, the $\beta$ estimate is approximately -1.011 with a standard error of 0.521.
+To assess the substantive significance of this variable we turn to a simulation based analysis.
+To to do this we set up two scenarios, one in which a civil war occurred and in the other no civil war, all the other parameters were set to their median value.
+Next, we conduct 1,000 random draws from a multivariate normal to obtain distributions for the point estimates of each of our regression coefficients.
+After obtaining these distributions, we calculate the predicted value of FDI inflows based on our two scenarios.
+The resulting distributions are shown in figure \ref{fig:civWarEffect}.
 
 \begin{figure}
-	\resizebox{.45\textwidth}{!}{\input{civWarCoefPlot.tex}}
-	\caption{Fixed effects regression results using full country-year panel.
-Darker colors indicates that the coefficient estimate is significantly different from zero at a 95\% CI, while lighter the same for a 90\% CI.
-Grey indicates that the estimate is not significantly different from zero at either of those intervals.}
-	\label{fig:civWarCoefplot}
+	\centering
+	\resizebox{.45\textwidth}{!}{\input{civWarEffect.tex}}
+	\caption{Distributions of expected values for GDP growth based on whether or not a country experienced a civil war in the previous year.
+The distribution in red designates the scenarios for which a civil war occurred and in blue if a civil war did not occur.
+The 90\% interval of each distribution is shaded in a dark blue or red color and the 95\% in a lighter color.}
+	\label{fig:civWarEffect}	
 \end{figure}

### 2015-08-18 R/Analysis/fixefVre.R

@@ -83,16 +83,9 @@ acledFormFE = lngdpGr_l0 ~ lnminDistACLED.mean + nconf + upperincome + lninflati
 mCityFixefCntry = lm(ctyFormFE, data = modData ); summary(mCityFixefCntry)$'coefficients'[1:(length(cntrls)+1),]
 mCapFixefCntry = lm(capFormFE, data = modData ); summary(mCapFixefCntry)$'coefficients'[1:(length(cntrls)+1),]
 mAcledFixefCntry = lm(acledFormFE, data = modData); summary(mAcledFixefCntry)$'coefficients'[1:6,]
+###################################################################
 
-# RE versus FE
-fixedEff <- mCityFixefCntry$effects[grepl("factor",names(mCityFixefCntry$effects))]
-library(doBy)
-ctryAvs <- summaryBy(lnminDist.min ~ ccode, data=modData, FUN=mean)
-fixedEff <- data.frame(ccode=names(fixedEff),val=fixedEff)
-fixedEff$ccode <- gsub("factor\\(ccode\\)","",fixedEff$ccode)
-ctryAvs <- merge(ctryAvs,fixedEff,by="ccode",all.x=T,all.y=F)
-cor(ctryAvs[,2:3], use="complete.obs")
-
+###################################################################
 # Run Hausman test on city and cap models
 library(plm)
 ctyFormBase=modForm(ivs=c(kivs[1], cntrls), type='none')
@@ -106,10 +99,15 @@ phtest(plmFE, plmRE)
 plmFE = plm(capFormBase, data=regData, model='within', effect='individual', index=c('ccode','year'))
 plmRE = plm(capFormBase, data=regData, model='random', effect='individual', index=c('ccode','year'))
 phtest(plmFE, plmRE)
+###################################################################
 
-# Basic model diags
-rmse=function(x){sqrt( mean( (residuals(x)^2) ) )}
-
-Reduce('-',quantile(modData$lngdpGr_l0,c(0.75,0.25),na.rm=T))
-rmse(mCity); rmse(mCap)
+###################################################################
+# RE versus FE, Clark and Linzer (2015)
+fixedEff <- mCityFixefCntry$effects[grepl("factor",names(mCityFixefCntry$effects))]
+library(doBy)
+ctryAvs <- summaryBy(lnminDist.min ~ ccode, data=modData, FUN=mean)
+fixedEff <- data.frame(ccode=names(fixedEff),val=fixedEff)
[…]

### 2015-08-18 R/Analysis/fullPanelModel.R

@@ -80,14 +80,6 @@ kivs = c(
 cntrls = c('upperincome', 'lninflation_l1',  'polity2', 'resourceGDP',  'gdpGr.mean_l0'
 	)
 
-# Run random effect models
-civwarForm=modForm(ivs=c(kivs[1], cntrls), type='random')
-mCivWar = lmer(civwarForm, data = modData ); summary(mCivWar)$'coefficients'
-
-# Fixef Robustness Checks
-civwarFormFE=modForm(ivs=c(kivs[1], cntrls), type='fixed')
-mCivWar = lm(civwarFormFE, data = modData ); summary(mCivWar)$'coefficients'[1:(length(cntrls)+1),]
-
 # Run Hausman test on city and cap models
 library(plm)
 civwarFormBase=modForm(ivs=c(kivs[1], cntrls), type='none')
@@ -97,11 +89,9 @@ plmFE = plm(civwarFormBase, data=regData, model='within', effect='individual', i
 plmRE = plm(civwarFormBase, data=regData, model='random', effect='individual', index=c('ccode','year'))
 phtest(plmFE, plmRE)
 
-# Basic model diags
-rmse=function(x){sqrt( mean( (residuals(x)^2) ) )}
-
-Reduce('-',quantile(modData$lngdpGr_l0,c(0.75,0.25),na.rm=T))
-rmse(mCivWar)
+# Fixef model
+civwarFormFE=modForm(ivs=c(kivs[1], cntrls), type='fixed')
+mCivWar = lm(civwarFormFE, data = modData ); summary(mCivWar)$'coefficients'[1:(length(cntrls)+1),]
 ###################################################################
 
 ###################################################################
@@ -127,4 +117,61 @@ if(genTikz){ dev.off() }
 ###################################################################
 # Model results: Table
 library(stargazer)
+stargazer(plmFE)
+###################################################################
+
+###################################################################
+# Substantive effects
+# Model results
+mod = mCivWar
+vars = c('factor(ccode)950', kivs[1], cntrls)
+coef = mod$'coefficients'[vars]
+varCov = vcov(mod)[vars,vars]
+
+# Set up scenario matrix
+data = na.omit( modData[,vars[2:length(vars)]] )
+scen = rbind(
[…]

### 2015-08-18 R/Analysis/models.R

@@ -57,7 +57,7 @@ modForm = function(dv='gdpGr_l0', ivs, id='ccode', type='random'){
 }
 
 dv = 'gdpGr_l0'
-kivs = c('lnminDist.mean', 'lncapDist.mean')
+kivs = c('lnminDist.min', 'lncapDist.min')
 cntrls = c(
   'Int.max',
   'durSt1max',  'confAreaProp', 'nconf', 
@@ -136,7 +136,6 @@ if(genTikz){ dev.off() }
 
 ###################################################################
 # Simulations
-
 temp = ggsimplot(modelResults=mCity, sims=10000, simData=modData, 
   vars=charSM(na.omit(rownames(summary(mCity)$'coefficients')[2:100])),
   vi='lnminDist.min', ostat=median, sigma=FALSE, intercept=TRUE,

### 2015-08-19 LaTeX/Revision/rev1.tex
more on baseline model
intensity models

@@
 To make the baseline model as comparable as possible to the model that we use to test our distance hypothesis, we adopt as similar a specification as possible.
-Specifically, the dependent variable is again logged, GDP growth.
+Specifically, the dependent variable is again GDP growth.
 Then our independent variables are, each lagged by one year:
@@
 However, the choice of introducing a zero for the NAs would be arbitrary and problematic, as our variable would no longer truly be continuous.
-Instead it would be discontinous in that we would have a large lump of observations at zero and then no observations until 1/7.31.
+Instead it would be discontinuous in that we would have a large lump of observations at zero and then no observations until 1/7.31.
 Beyond the problems associated with transforming the variable in this way we would also run into issues of perfect collinearity with the inverted conflict distance measure and the interaction variable.
@@
 \item \textcolor{blue}{\emph{
-	The minimum distance of the centroid of a conflict from any major or capital city in our dataset is 0.38 UNITS so this is not an issue for our analysis.
+	The minimum distance of the centroid of a conflict from the centroid of any major or capital city in our dataset is 0.38 kilometers, so we do not run into issues with zero distance values.
 }}

### 2015-08-19 LaTeX/Revision/rev2.tex
intensity models

@@
 	We retested our hypothesis using the ACLED dataset and here as well we find that our distance measure of conflict to major urban centers is significantly negative.
+We have included these results in the Appendix under the subsection ACLED Analysis, we have also added in a footnote in the paper indicating that our results remain robust when estimated on this alternative dataset.
 }}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{\emph{
+We reran our model on the effect of conflict proximity on GDP growth using the list of urban centers at the beginning of the period.
+The results are shown in table \ref{tab:modOrigCity} below.
+We were only able to rerun this model for minimum distance to any city because ...
+
+\input{modelsWithOrigCity.tex}
+\FloatBarrier
+}}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{\emph{
+	WOuld need to take into account distance of countries, hard to construct
+	however, we have looked at other parameterizations such as mean distance
+}}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{\emph{
+	We appreciate this suggestion and have shifted the focus to the cases of Nigeria and Cameroon. 
+}}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{\emph{
+}}
 \end{itemize}

### 2015-08-19 LaTeX/RhodiumAppendix.tex
recompiled with new intro
more on baseline model
intensity models

@@
 \label{appendix}
+
+\subsection{Estimating Models Separately for High and Low Intensity Conflicts}
+
+Here instead of treating conflict intensity as a control, we re-do our primary models estimating the effect of distance on growth, but restricting to the civil conflicts coded as wars and then a separate model for civil conflicts coded as low intensity events.
+
+\input{modelHiLoIntensity.tex}
+\FloatBarrier
+
+\newpage
+\subsection{ACLED Analysis}
+\label{acled}
 

### 2015-08-19 LaTeX/RhodiumEmp.tex
intensity models

@@
 
-To construct a time-series cross-sectional database of urban centers, we turn to yearly editions of \citet{worldalmanac:1989}.
+To construct a time-series cross-sectional database of urban centers, we turn to yearly editions of \emph{The World Alamanac}.
 More refined subnational data listing urban centers by their contribution to economic output would be the most direct way to test our hypothesis, however, cross-national data such as this over the time period of our analysis, especially for developing countries, is simply not available.
@@
 To include this in our country-year model, we sum up the area covered by each conflict being fought and divide by the total land area of the country.
-From this we then create a binary measure that is one if greater than 50\% of a country's total land area is immersed in conflict and zero otherwise.
 Finally, the number of conflicts is simply a count of the number of ongoing internal armed conflicts in a country-year according to the PRIO dataset.
+
+% From this we then create a binary measure that is one if greater than 50\% of a country's total land area is immersed in conflict and zero otherwise.
 
@@
 Before we move to discussing the results of the model specification that we have described above we estimate a simple, baseline model to assess the effect of any civil conflict on growth.
-For this model we use a specification as similar as possible to the one we explicated in the previous section, with the key difference being that this baseline model is estimated using a full country-year panel with fixed effects.\footnote{In choosing between fixed and random effects, we again followed the typology set out by \citet{clark:linzer:2015}, and, in this case, found that the fixed effects specification was preferred.} The dependent variable is again annual percent change in GDP from the World Development Indicators, and the key independent variable here is whether or not the country was engaged in a civil war in the previous year according to the PRIO Conflict dataset.
+For this model we use a specification as similar as possible to the one we explicated in the previous section, with the key difference being that this baseline model is estimated using a full country-year panel with fixed effects.\footnote{In choosing between fixed and random effects, we again followed the typology set out by \citet{clark:linzer:2015}, and, in this case, found that the fixed effects specification was preferred.} The dependent variable is again annual percent change in GDP from the World Development Indicators, and the key independent variable here is whether or not the country was engaged in a civil war in the previous year according to the PRIO Armed Conflict dataset.
 Since we are using a full country-year panel, we have to omit the PRIO conflict specific variables (e.g., conflict intensity, conflict duration) as they are undefined for country-year observations in which no conflict was taking place.
-The rest of the independent variables are similar to the model specified in the previous section, the exact estimation model we use is shown below:
+The rest of the independent variables are similar to the model specified in the previous section, specifically, we include: whether or not the country is classified as upper income, lagged version of inflation, lagged version of polity, lagged version of resource rents as a proportion of GDP, and average GDP growth across all countries in the world.
 
-\begin{align*}
-	\% \Delta GDP_{i,t} &= \beta_{1}(Civil War)_{i,t-1}) \\
-	& beta_{6}(Upper \; Income_{i,t}) \;+\; \beta_{7}(Inflation_{i,t-1}) \\	
-	& \beta_{8}(Democracy_{i,t-1}) \;+\; \beta_{9}(Resource \; Rents/GDP_{t-1}) \\
-	& \;+\; \beta_{10}(World \; GDP \; Growth_{t})
-\end{align*}
+% \begin{align*}
+% 	\% \Delta GDP_{i,t} &= \beta_{1}(Civil\;War_{i,t-1}) \\
+% 	& \;+\; \beta_{6}(Upper \; Income_{i,t}) \;+\; \beta_{7}(Inflation_{i,t-1}) \\	
+% 	& \;+\; \beta_{8}(Democracy_{i,t-1}) \;+\; \beta_{9}(Resource \; Rents/GDP_{t-1}) \\
+% 	& \;+\; \beta_{10}(World \; GDP \; Growth_{t})
+% \end{align*}
 
-Since our primary interest here is just
+We will eschew discussing the controls since the primary purpose of this analysis is to determine a baseline effect for civil war.
+Additionally, for the sake of space we do not show the full results from this regression, but they are available in section \ref{baseline} of the Appendix.
+The key result pertains to the civil war variable, the $\beta$ estimate is approximately -1.011 with a standard error of 0.521.
 
-The results of this model are shown below in figure~\ref{fig:civWarCoefplot}.
-We will eschew discussing the controls since the primary purpose of this analysis is to determine a baseline effect for civil war.
-Additionally, for the sake of space we do not show the full results from this regression, though they are available in section \ref{baseline} of the Appendix.
-The key result pertains to the civil war variable, the $\beta$ estimate is approximately -1.011 with a standard error of 0.521.
 To assess the substantive significance of this variable we turn to a simulation based analysis.
 To to do this we set up two scenarios, one in which a civil war occurred and in the other no civil war, all the other parameters were set to their median value.
-Next, we conduct 1,000 random draws from a multivariate normal to obtain distributions for the point estimates of each of our regression coefficients.
-After obtaining these distributions, we calculate the predicted value of FDI inflows based on our two scenarios.
+Next, we conduct 1,000 random draws from a multivariate normal to obtain a distribution of point estimates of each regression coefficient.
+Last, we simply matrix multiply the draws from the multivariate normal with the transposed scenario matrix to obtain expected values of GDP growth by the two scenarios.
 The resulting distributions are shown in figure \ref{fig:civWarEffect}.
@@
 \end{figure}
+
+The analysis here highlights that there is little distinguishable difference in the expected values of GDP growth by whether or not there a country was experiencing a civil war in the previous year.
 

### 2015-08-19 R/Analysis/fixefVre.R

@@ -103,8 +103,8 @@ phtest(plmFE, plmRE)
 
 ###################################################################
 # RE versus FE, Clark and Linzer (2015)
-fixedEff <- mCityFixefCntry$effects[grepl("factor",names(mCityFixefCntry$effects))]
 library(doBy)
+fixedEff <- mCityFixefCntry$effects[grepl("factor",names(mCityFixefCntry$effects))]
 ctryAvs <- summaryBy(lnminDist.min ~ ccode, data=modData, FUN=mean)
 fixedEff <- data.frame(ccode=names(fixedEff),val=fixedEff)
 fixedEff$ccode <- gsub("factor\\(ccode\\)","",fixedEff$ccode)

### 2015-08-19 R/Analysis/fullPanelModel.R

@@ -171,6 +171,7 @@ temp = temp + theme(panel.border = element_blank(),
 	axis.title.x = element_text(vjust=-0.2),
 	axis.title.y = element_text(vjust=0.2))
 temp
+setwd(pathGraphics)
 if(genTikz){ tikz(file='civWarEffect.tex', width=6, height=4, standAlone=F)}
 temp
 if(genTikz){ dev.off() }

### 2015-08-19 R/Analysis/models.R

@@ -1,12 +1,8 @@
 if(Sys.info()["user"]=="janus829" | Sys.info()["user"]=="s7m"){ source('~/Research/Rhodium/R/setup.R')}
 if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
-library(Hmisc)
 # Load conflict country year data
 setwd(pathData)
-# load('combinedData_Orig.rda'); modData=yData
 load('combinedData.rda'); modData=yData
-# load('combinedData_loInt.rda'); modData=yData
-# load('combinedData_hiInt.rda'); modData=yData
 
 # Gen tikz?
 genTikz=FALSE
@@ -79,6 +75,12 @@ rmse=function(x){sqrt( mean( (residuals(x)^2) ) )}
 
 Reduce('-',quantile(modData$lngdpGr_l0,c(0.75,0.25),na.rm=T))
 rmse(mCity); rmse(mCap)
+###################################################################
+
+###################################################################
+# Regression Tables
+library(stargazer)
+stargazer(mCity, mCap)
 ###################################################################
 
 ###################################################################

### 2015-08-19 R/Analysis/modelsInteractionArea.R

@@ -1,0 +1,77 @@
+if(Sys.info()["user"]=="janus829" | Sys.info()["user"]=="s7m"){ source('~/Research/Rhodium/R/setup.R')}
+if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
+# Load conflict country year data
+setwd(pathData)
+# load('combinedData_Orig.rda'); modData=yData
+load('combinedData.rda'); modData=yData
+# load('combinedData_loInt.rda'); modData=yData
+# load('combinedData_hiInt.rda'); modData=yData
+
+# Gen tikz?
+genTikz=FALSE
+
+# CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
+###################################################################
+logTrans=function(x){ log( x + abs(min(x, na.rm=T)) + 1) }
+
+# Log transforming DVs
+modData$lngdp_l0 = log(modData$gdp_l0)
+modData$lngdp = log(modData$gdp)
+modData$lngdpGr_l0 = (modData$lngdp_l0-modData$lngdp)/modData$lngdp_l0
+modData$lngdpGr_l0 = modData$gdpGr_l0
+
+# Transformations for conflict variables
+modData$lnminDist.min <- log(modData$minDist.min+1)
+modData$lncapDist.min <- log(modData$capDist.min+1)
+modData$Int.max <- modData$Int.max-1
+
+# Transformations for other controls
+modData$lngdpCap = log(modData$gdpCap)
+modData$lninflation_l1 = logTrans(modData$inflation_l1)
+modData$democ = as.numeric(modData$polity2>=6)
+modData$polity2 = modData$polity2 + 11
+
+# Interaction term with distance and area
+modData$minAreaSum = modData$lnminDist.min * modData$Conflict.area.sum
+modData$minAreaMean = modData$lnminDist.min * modData$Conflict.area.mean
+modData$capAreaSum = modData$lncapDist.min * modData$Conflict.area.sum
+modData$capAreaMean = modData$lncapDist.min * modData$Conflict.area.mean
+###################################################################
+
+## MODELS FOR GDP GROWTH (ANNUAL %)
+###################################################################
+# Model parameters
+modForm = function(dv='gdpGr_l0', ivs, id='ccode', type='random'){
+  base = paste(dv, paste(ivs, collapse=' + '), sep=' ~ ')
+  if(type=='random'){
+    eff = paste0('(1 |', id, ')')
[…]

### 2015-08-19 R/Analysis/modelsOrigCity.R

@@ -1,0 +1,66 @@
+if(Sys.info()["user"]=="janus829" | Sys.info()["user"]=="s7m"){ source('~/Research/Rhodium/R/setup.R')}
+if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
+# Load conflict country year data
+setwd(pathData)
+load('combinedData_Orig.rda'); modData=yData
+
+# Gen tikz?
+genTikz=FALSE
+
+# CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
+###################################################################
+logTrans=function(x){ log( x + abs(min(x, na.rm=T)) + 1) }
+
+# Log transforming DVs
+modData$lngdp_l0 = log(modData$gdp_l0)
+modData$lngdp = log(modData$gdp)
+modData$lngdpGr_l0 = (modData$lngdp_l0-modData$lngdp)/modData$lngdp_l0
+modData$lngdpGr_l0 = modData$gdpGr_l0
+
+# Transformations for conflict variables
+modData$lnminDist.min <- log(modData$minDist.min+1)
+modData$Int.max <- modData$Int.max-1
+
+# Transformations for other controls
+modData$lngdpCap = log(modData$gdpCap)
+modData$lninflation_l1 = logTrans(modData$inflation_l1)
+modData$democ = as.numeric(modData$polity2>=6)
+modData$polity2 = modData$polity2 + 11
+###################################################################
+
+
+## MODELS FOR GDP GROWTH (ANNUAL %)
+###################################################################
+# Model parameters
+modForm = function(dv='gdpGr_l0', ivs, id='ccode', type='random'){
+  base = paste(dv, paste(ivs, collapse=' + '), sep=' ~ ')
+  if(type=='random'){
+    eff = paste0('(1 |', id, ')')
+    base = paste(base, eff, sep=' + ')
+  }
+
+  if(type=='fixed'){
+    eff = paste0('factor(', id, ') - 1')
+    base = paste(base, eff, sep=' + ')
+  }
+  return(formula(base))
+}
+
+dv = 'gdpGr_l0'
+kivs = 'lnminDist.min'
+cntrls = c(
+  'Int.max',
+  'durSt1max',  'confAreaProp', 'nconf', 
+  'upperincome', 'lninflation_l1',  'polity2', 'resourceGDP',  'gdpGr.mean_l0')
+
+# Run random effect models
[…]

### 2015-08-20 LaTeX/Revision/rev1.tex
gdp gr versus mindist

@@
 	We reran the models per this specification and have included the results in the appendix.
-In both low intensity and high intensity cases we find that the distance variables remain significant and in the hypothesized direction.
+In both low intensity and high intensity cases we find that the distance variables remain significant and in the hypothesized direction, but as R1 expected the $\beta$ estimate of our distance variables was noticeably higher when using high intensity versus low intensity civil conflict cases.
 }}

### 2015-08-20 R/Analysis/gdpGr_minDist.R

@@ -1,0 +1,17 @@
+if(Sys.info()["user"]=="janus829" | Sys.info()["user"]=="s7m"){
+  source('~/Research/Rhodium/R/setup.R')}
+if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
+
+# Load conflict country year data
+setwd(pathData)
+load('fullData.rda')
+
+slice = fullData[,c('ccode','year','gdpGr', 'minDist.min')]
+slice$lnminDist.min = log(slice$minDist.min + 1)
+slice$lnminDist.min[is.na(slice$lnminDist.min)] = 0
+
+cntryData = slice[slice$ccode==100,]
+library(gridExtra)
+gdpTime = ggplot(cntryData, aes(x=year, y=gdpGr)) + geom_line()
+distTime = ggplot(cntryData, aes(x=year, y=minDist.min)) + geom_bar(stat='identity')
+grid.arrange(gdpTime, distTime)

### 2015-08-20 R/Analysis/models.R

@@ -265,6 +265,7 @@ temp <- ggcoefplot(coefData=ccityCross, vars=ccCoefs, varNames=ccNames,
   )
 temp=temp+facet_wrap(~Variable, scales='fixed')
 setwd(pathGraphics)
+temp
 if(genTikz){ tikz(efile='crossValPlot.tex', width=7, height=4, standAlone=FALSE)}
 temp
 if(genTikz){ dev.off() }

### 2015-08-20 R/Analysis/modelsInteractionArea.R

@@ -36,6 +36,9 @@ modData$minAreaSum = modData$lnminDist.min * modData$Conflict.area.sum
 modData$minAreaMean = modData$lnminDist.min * modData$Conflict.area.mean
 modData$capAreaSum = modData$lncapDist.min * modData$Conflict.area.sum
 modData$capAreaMean = modData$lncapDist.min * modData$Conflict.area.mean
+
+modData$minArea = modData$lnminDist.min * modData$confAreaProp
+modData$capArea = modData$lncapDist.min * modData$confAreaProp
 ###################################################################
 
 ## MODELS FOR GDP GROWTH (ANNUAL %)
@@ -56,7 +59,8 @@ modForm = function(dv='gdpGr_l0', ivs, id='ccode', type='random'){
 }
 
 dv = 'gdpGr_l0'
-kivs = c('lnminDist.min', 'minAreaSum', 'lncapDist.min', 'capAreaSum')
+kivs = c('lnminDist.min', 'minArea', 'lncapDist.min', 'capArea')
+# kivs = c('lnminDist.min', 'minAreaSum', 'lncapDist.min', 'capAreaSum')
 # kivs = c('lnminDist.min', 'minAreaMean', 'lncapDist.min', 'capAreaMean')
 cntrls = c(
   'Int.max',

### 2015-08-21 LaTeX/Revision/rev2.tex
edits to rev 2

@@
 \item \textcolor{blue}{\emph{
-	WOuld need to take into account distance of countries, hard to construct
-	however, we have looked at other parameterizations such as mean distance
+	We have looked at alternative parameterizations of the conflict distance measure including both the minimum and mean distances of conflicts to the respective nearest cities.
+Our results are robust across these parameterizations.
+We specifically chose not to create an aggregate conflict variable weighted by distance as we lacked theoretical justification for doing so given the argument advanced in the paper.
+If a country experiences both a rural and an urban conflict simultaneously, we do not expect the rural conflict to mitigate the economic consequences of the urban conflict.
+In the same way, we do not expect distant cities to compensate for the economic consequences felt by a city near conflict.
 }}
@@
 \item \textcolor{blue}{\emph{
+	We agree that this is an interesting hypothesis and would constitute a valuable extension to this research.
+However, we believe that this hypothesis is not a clear corollary to the arguments presented in this paper and deserves more consideration than a simple interaction term.
+Conflict area is not necessarily a proxy for conflict intensity and it is unclear to us that, controlling for intensity as we do, conflicts with larger areas that are nearer to cities will be of necessarily greater economic impact.
+In fact, one might argue that there is a dilution effect in which larger conflicts, controlling for intensity, produce less violence per square kilometer.
+Also, an interaction term like this supposes that there is a multiplicative effect such that \textnormal{conflict area} $\times$ \textnormal{conflict distance} is correlated with economic growth in a way that \textnormal{conflict area} $+$ \textnormal{conflict distance} is not.
+We reiterate that this is a very interesting avenue for further exploration but believe that we cannot address it adequately within the scope of this paper.
 }}
@@
 \item \textcolor{blue}{\emph{
-	When rerunning the model using the continuous variable each of the key results remain similar.
+	When rerunning the model using the continuous variable each of the key results remain similar. We have used the continuous version of the variable in the revised draft.
 }}

### 2015-08-21 LaTeX/RhodiumTheory.tex
recompiled with new intro
syria example?

@@
-% Note to Ben: Should we have a capital city and any city hypothesis?
-
 \section{Spatial Distribution of Cities and Violence}
@@
 
+More recently, economic productivity in Syria has ground to a halt due to its ongoing civil war.
+Fighting in Syria has been widespread with particularly bloody battles of attrition fought over some of the country's largest cities.
+Both Aleppo and Damascus have been divided neighborhood-by-neighborhood by the Assad regime and various armed groups vying for control of the cities.
+Simultaneously, Syria's economy has shrunk dramatically.
+
 While FARC seems to exploit its ability to target areas of economic importance including cities, other insurgencies tend to be more peripheral.
@@
 A common characteristic of these cases is the geographic distribution of conflict; violent armed groups operate primarily in rural areas away from major cities.
-
-% Note to Ben: If you have more to add about Mexico here that might be good

### 2015-08-22 R/Analysis/modelsInteractionArea.R
interaction model

@@ -18,8 +18,8 @@ modData$lngdpGr_l0 = (modData$lngdp_l0-modData$lngdp)/modData$lngdp_l0
 modData$lngdpGr_l0 = modData$gdpGr_l0
 
 # Transformations for conflict variables
-modData$lnminDist.min <- log(modData$minDist.min+1)
-modData$lncapDist.min <- log(modData$capDist.min+1)
+modData$lnminDist.min <- log(modData$minDist.min+1) 
+modData$lncapDist.min <- log(modData$capDist.min+1) 
 modData$Int.max <- modData$Int.max-1
 
 # Transformations for other controls

### 2015-08-24 R/Analysis/models.R
syncing up

@@ -59,12 +59,13 @@ cntrls = c(
   'durSt1max',  'confAreaProp', 'nconf', 
   'upperincome', 'lninflation_l1',  'polity2', 'resourceGDP',  'gdpGr.mean_l0')
 
-# Run random effect models
+# Model specifications
 ctyForm=modForm(ivs=c(kivs[1], cntrls), type='random')
 capForm=modForm(ivs=c(kivs[2], cntrls), type='random')
-# We can't use the modForm() function here because Int.max, durSt1max, confAreaProp are not defined for ACLED data:
-acledForm = lngdpGr_l0 ~ lnminDistACLED.mean + nconf + upperincome + lninflation_l1 + polity2 + resourceGDP + gdpGr.mean_l0 + (1 | ccode)
-acledFormCap = lngdpGr_l0 ~ lncapDistACLED.mean + nconf + upperincome + lninflation_l1 + polity2 + resourceGDP + gdpGr.mean_l0 + (1 | ccode)
+acledForm = modForm(ivs=c('lnminDistACLED.mean', cntrls[4:length(cntrls)]))
+acledFormCap = modForm(ivs=c('lncapDistACLED.mean', cntrls[4:length(cntrls)]))
+
+# Run models
 mCity = lmer(ctyForm, data = modData ); summary(mCity)$'coefficients'
 mCap = lmer(capForm, data = modData ); summary(mCap)$'coefficients'
 mAcled = lmer(acledForm, data = modData ); summary(mAcled)$'coefficients'
@@ -80,7 +81,10 @@ rmse(mCity); rmse(mCap)
 ###################################################################
 # Regression Tables
 library(stargazer)
+# Tabular depictions for PRIO city models
 stargazer(mCity, mCap)
+# Tabular depictions for ACLED city models
+stargazer(mAcled, mAcledCap)
 ###################################################################
 
 ###################################################################
@@ -215,7 +219,7 @@ if(genTikz){ dev.off() }
 
 ###################################################################
 # Crossval: Testing for heterogeneous effects across subsets
-vars=c( 'ccode','year','lngdpGr_l0',dv,kivs,cntrls)
+vars=c( 'ccode','year',dv,kivs,cntrls)
 crossData=na.omit( modData[,vars] )
 
 cntries=unique(crossData$ccode)
[…]

### 2015-08-25 LaTeX/Revision/editor.tex
intensity models
fixef v ranef, piecewise models, cleanup

@@
 \textcolor{blue}{\emph{
-	For the ``Capital City'' and ``Any Major City'' models we ran a Hausman test to see if fixed or random effects were appropriate for our dataset, and in both cases we do not reject the null hypothesis of the Hausman test at a 90 or 95\% confidence interval indicating that it is acceptable to use random effects.
-We have added a discussion of this analysis into our empirical section.
-	However, as Clark \& Linzer (2015) show the Hausman test is by itself not a sufficient statistic to choose between fixed or random effects.
-They provide a typology for assessing whether or not to use fixed or random effects.
-Specifically they suggest to look at the ``the size of the dataset (both number of units and number of observations per unit), the level of correlation between the covariate and unit effects, and the extent of within-unit variation in the independent variable relative to the dependent variable'' (pg., 2).
-We employ their typology to further test whether our choice of random effects over fixed effects is appropriate.
+	There are a number of reasons why we chose a random effects framework, however, we agree with the reviewers that these reasons were not clearly explicated in the text.
+The following discussion provides three reasons why we employ a random effects framework.
+We have added the reasoning described below to the relevant section in the actual paper as well.
+	For the ``Capital City'' and ``Any Major City'' models we ran a Hausman test to see if fixed or random effects were appropriate for our dataset, and in both cases we do not reject the null hypothesis of the Hausman test at a 90 or 95\% confidence interval indicating by at least that standard that both fixed and random effect approaches are consistent, with the latter obviously being more efficient.
+	However, as Clark \& Linzer (2015) note the Hausman test should not be the sole determination for choosing between fixed or random effects.
+They perform a series of Monte Carlo simulations to determine the conditions under which a fixed or random effects model is appropriate and provide a rough typology.
+Specifically to take into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects.
+In our case, we have over 70 countries but for over half of those we only have five conflict instances or less.
+Given such a data structure Clark \& Linzer (2015) recommend to examine the level of correlation between the regressor and unit effects to determine the appropriate modeling framework.
+For both our distance models, the level of correlation between the regressor and unit effects is less than 0.20, which accords with a random effects recommendation under the framework described by Clark \& Linzer (2015).
+	Another reason why we choose a random effects framework is because of our concerns with the unchanging and time invariant nature of where conflict is taking place relative to major urban centers.
+In Thailand, for example, the distance between conflict and urban centers in our dataset just ranges from approximately 790 to 810 kilometers, which basically indicates that conflicts are simply isolated to a specific part of the country.
+This same patterns holds for many other countries in our sample such as Mozambique (range: $\approx$ 705 - 860 km), Bangladesh (range: $\approx$ 198 - 237 km), Cambodia (range: $\approx$ 131 - 197 km), etc..
+These ranges become even further compressed when we log them for use in our regression analysis.
+If we employed a fixed effects model to test our hypothesis we would in essence be removing many of these types of countries from our sample, or as Beck \& Katz (2001) would put it ``throwing out the baby with the bathwater''.
 }}

### 2015-08-25 LaTeX/Revision/rev1.tex
fixef v ranef, piecewise models, cleanup

@@
 \item \textcolor{blue}{\emph{
-	For the ``Capital City'' and ``Any Major City'' models we ran a Hausman test to see if fixed or random effects were appropriate for our dataset, and in both cases we do not reject the null hypothesis of the Hausman test at a 90 or 95\% confidence interval indicating that it is acceptable to use random effects.
-We have added a discussion of this analysis into our empirical section.
-	However, as Clark \& Linzer (2015) show the Hausman test is by itself not a sufficient statistic to choose between fixed or random effects.
-They provide a typology for assessing whether or not to use fixed or random effects.
-Specifically they suggest to look at the ``the size of the dataset (both number of units and number of observations per unit), the level of correlation between the covariate and unit effects, and the extent of within-unit variation in the independent variable relative to the dependent variable'' (pg., 2).
-We employ their typology to further test whether our choice of random effects over fixed effects is appropriate.
+	There are a number of reasons why we chose a random effects framework, however, we agree with the reviewers that these reasons were not clearly explicated in the text.
+The following discussion provides three reasons why we employ a random effects framework.
+We have added the reasoning described below to the relevant section in the actual paper as well.
+	For the ``Capital City'' and ``Any Major City'' models we ran a Hausman test to see if fixed or random effects were appropriate for our dataset, and in both cases we do not reject the null hypothesis of the Hausman test at a 90 or 95\% confidence interval indicating by at least that standard that both fixed and random effect approaches are consistent, with the latter obviously being more efficient.
+	However, as Clark \& Linzer (2015) note the Hausman test should not be the sole determination for choosing between fixed or random effects.
+They perform a series of Monte Carlo simulations to determine the conditions under which a fixed or random effects model is appropriate and provide a rough typology.
+Specifically to take into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects.
+In our case, we have over 70 countries but for over half of those we only have five conflict instances or less.
+Given such a data structure Clark \& Linzer (2015) recommend to examine the level of correlation between the regressor and unit effects to determine the appropriate modeling framework.
+For both our distance models, the level of correlation between the regressor and unit effects is less than 0.20, which accords with a random effects recommendation under the framework described by Clark \& Linzer (2015).
+	Another reason why we choose a random effects framework is because of our concerns with the unchanging and time invariant nature of where conflict is taking place relative to major urban centers.
+In Thailand, for example, the distance between conflict and urban centers in our dataset just ranges from approximately 790 to 810 kilometers, which basically indicates that conflicts are simply isolated to a specific part of the country.
+This same patterns holds for many other countries in our sample such as Mozambique (range: $\approx$ 705 - 860 km), Bangladesh (range: $\approx$ 198 - 237 km), Cambodia (range: $\approx$ 131 - 197 km), etc..
+These ranges become even further compressed when we log them for use in our regression analysis.
+If we employed a fixed effects model to test our hypothesis we would in essence be removing many of these types of countries from our sample, or as Beck \& Katz (2001) would put it ``throwing out the baby with the bathwater''.
 }}
@@
 The key finding from this analysis is that a civil war is related to lower levels of GDP growth, however, this effect is marginal and only significant at a 90\% confidence interval.
-Further the substantive effect of civil war is ...
-compared to ...
-when conflicts are very proximate to city centers.
+To determine the substantive significance of a civil war we employ a simulation based approach, similar to what we did to assess the effect of conflict distance from urban centers on growth, and we find that there is a marginal difference but the effect is highly uncertain.
+We use this finding as a lead in to our main model describing the effect of conflict distance from urban centers on growth.
 }}
@@
 \item \textcolor{blue}{\emph{
-	BEN will add stuff here. 
+	We are not familiar enough with the Naxalite conflict to comment but we have added a lengthier discussion in the descriptive cases section to highlight the effect that we have found in our empirical analysis.
 }}

### 2015-08-25 LaTeX/Revision/rev2.tex
interaction model
syncing up
fixef v ranef, piecewise models, cleanup

@@
 \item \textcolor{blue}{\emph{
-	For the ``Capital City'' and ``Any Major City'' models we ran a Hausman test to see if fixed or random effects were appropriate for our dataset, and in both cases we do not reject the null hypothesis of the Hausman test at a 90 or 95\% confidence interval indicating that it is acceptable to use random effects.
-We have added a discussion of this analysis into our empirical section.
-	However, as Clark \& Linzer (2015) show the Hausman test is by itself not a sufficient statistic to choose between fixed or random effects.
-They provide a typology for assessing whether or not to use fixed or random effects.
-Specifically they suggest to look at the ``the size of the dataset (both number of units and number of observations per unit), the level of correlation between the covariate and unit effects, and the extent of within-unit variation in the independent variable relative to the dependent variable'' (pg., 2).
-We employ their typology to further test whether our choice of random effects over fixed effects is appropriate.
+	There are a number of reasons why we chose a random effects framework, however, we agree with the reviewers that these reasons were not clearly explicated in the text.
+The following discussion provides three reasons why we employ a random effects framework.
+We have added the reasoning described below to the relevant section in the actual paper as well.
+	For the ``Capital City'' and ``Any Major City'' models we ran a Hausman test to see if fixed or random effects were appropriate for our dataset, and in both cases we do not reject the null hypothesis of the Hausman test at a 90 or 95\% confidence interval indicating by at least that standard that both fixed and random effect approaches are consistent, with the latter obviously being more efficient.
+	However, as Clark \& Linzer (2015) note the Hausman test should not be the sole determination for choosing between fixed or random effects.
+They perform a series of Monte Carlo simulations to determine the conditions under which a fixed or random effects model is appropriate and provide a rough typology.
+Specifically to take into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects.
+In our case, we have over 70 countries but for over half of those we only have five conflict instances or less.
+Given such a data structure Clark \& Linzer (2015) recommend to examine the level of correlation between the regressor and unit effects to determine the appropriate modeling framework.
+For both our distance models, the level of correlation between the regressor and unit effects is less than 0.20, which accords with a random effects recommendation under the framework described by Clark \& Linzer (2015).
+	Another reason why we choose a random effects framework is because of our concerns with the unchanging and time invariant nature of where conflict is taking place relative to major urban centers.
+In Thailand, for example, the distance between conflict and urban centers in our dataset just ranges from approximately 790 to 810 kilometers, which basically indicates that conflicts are simply isolated to a specific part of the country.
+This same patterns holds for many other countries in our sample such as Mozambique (range: $\approx$ 705 - 860 km), Bangladesh (range: $\approx$ 198 - 237 km), Cambodia (range: $\approx$ 131 - 197 km), etc..
+These ranges become even further compressed when we log them for use in our regression analysis.
+If we employed a fixed effects model to test our hypothesis we would in essence be removing many of these types of countries from our sample, or as Beck \& Katz (2001) would put it ``throwing out the baby with the bathwater''.
+	In terms of the roadmap mentioned by the reviewer, we have added an appendix item that runs the analysis in the way reviewer suggested and reports the results in a tabular format. 
 }}
@@
 \item \textcolor{blue}{\emph{
-	We retested our hypothesis using the ACLED dataset and here as well we find that our distance measure of conflict to major urban centers is significantly negative.
+	We retested our hypothesis using the ACLED dataset and we find that our distance measure of conflict to major urban centers is significantly negative.
 We have included these results in the Appendix under the subsection ACLED Analysis, we have also added in a footnote in the paper indicating that our results remain robust when estimated on this alternative dataset.
@@
 The results are shown in table \ref{tab:modOrigCity} below.
-We were only able to rerun this model for minimum distance to any city because ...
-
+Running the same analysis using capital cities is difficult as they change over time in our sample.
 \input{modelsWithOrigCity.tex}
@@
 \item \textcolor{blue}{\emph{
-	We appreciate this suggestion and have shifted the focus to the cases of Nigeria and Cameroon. 
+	We appreciate this suggestion and have included the cases of Nigeria and Cameroon rather than profiling Mexico at the lead of this paper. 
 }}

### 2015-08-25 LaTeX/RhodiumAppendix.tex
fixef v ranef, piecewise models, cleanup

@@
 \label{appendix}
+
+\subsection{Conflict Distance Models in Tabular Format}
+
+Here we present the results of our models measuring the effect of conflict distance in a tabular format.
+The first column in each of the tables below is a simple linear model regressing the conflict distance parameter on GDP Growth, in the second we add our controls, in the third we include random effects, varying intercepts, for country, in the fourth random effects for year, and in the last random effects for both country and year.
+
+\input{capDistRegTable.tex}
+
+\input{cityDistRegTable.tex}
+
+\FloatBarrier
+\nepage
 

### 2015-08-25 R/Analysis/fixefVre.R

@@ -3,18 +3,13 @@ if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
 library(Hmisc)
 # Load conflict country year data
 setwd(pathData)
-# load('combinedData_Orig.rda'); modData=yData
 load('combinedData.rda'); modData=yData
-# load('combinedData_loInt.rda'); modData=yData
-# load('combinedData_hiInt.rda'); modData=yData
 
 # Gen tikz?
 genTikz=FALSE
 
 # CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
 ###################################################################
-logTrans=function(x){ log( x + abs(min(x, na.rm=T)) + 1) }
-
 # Log transforming DVs
 modData$lngdp_l0 = log(modData$gdp_l0)
 modData$lngdp = log(modData$gdp)
@@ -37,26 +32,31 @@ modData$lngdpCap = log(modData$gdpCap)
 modData$lninflation_l1 = logTrans(modData$inflation_l1)
 modData$democ = as.numeric(modData$polity2>=6)
 modData$polity2 = modData$polity2 + 11
+###################################################################
 
 ###################################################################
+# Number of observations per unit
+prioDistData = na.omit( modData[,c('ccode','year','lnminDist.min')] )
+acledDistData = na.omit( modData[,c('ccode','year','lnminDistACLED.min')] )
+sort( table(prioDistData$ccode) )
+sort( table(acledDistData$ccode) )
+
+# Variation in distance measures by unit (RSD)
+library(doBy)
+varDist = summaryBy(lnminDist.min ~ ccode, data=modData, FUN=c(sd, mean), na.rm=TRUE)
+varDist = na.omit( varDist )
+varDist$sdMean = varDist[,2]/varDist[,3]
+varDist[order(varDist[,4]),]
+
+# Plot by unit
+cnts = table( na.omit( modData[,c('ccode','year','minDist.min','lnminDist.min')] )$ccode )
+slice = na.omit( modData[which(modData$ccode %in% names(cnts[cnts>1])), c('ccode','year','minDist.min','lnminDist.min')] )
+ggplot(slice, aes(x=year, y=minDist.min)) + facet_wrap(~ccode, scales='free') + geom_bar(stat='identity')
+###################################################################s
 
[…]

### 2015-08-25 R/Analysis/modelByPiece.R

@@ -1,0 +1,75 @@
+if(Sys.info()["user"]=="janus829" | Sys.info()["user"]=="s7m"){ source('~/Research/Rhodium/R/setup.R')}
+if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
+# Load conflict country year data
+setwd(pathData)
+load('combinedData.rda'); modData=yData
+
+# Gen tikz?
+genTikz=FALSE
+
+# CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
+###################################################################
+# Log transforming DVs
+modData$lngdp_l0 = log(modData$gdp_l0)
+modData$lngdp = log(modData$gdp)
+modData$lngdpGr_l0 = (modData$lngdp_l0-modData$lngdp)/modData$lngdp_l0
+modData$lngdpGr_l0 = modData$gdpGr_l0
+
+# Transformations for conflict variables
+modData$lnminDist.min <- log(modData$minDist.min+1)
+modData$lncapDist.min <- log(modData$capDist.min+1)
+modData$lnminDist.mean <- log(modData$minDist.mean+1)
+modData$lncapDist.mean <- log(modData$capDist.mean+1)
+modData$lnminDistACLED.min <- log(modData$minDistACLED.min+1)
+modData$lnminDistACLED.mean <- log(modData$minDistACLED.mean+1)
+modData$lncapDistACLED.min <- log(modData$acledCapDist.min+1)
+modData$lncapDistACLED.mean <- log(modData$acledCapDist.mean+1)
+modData$Int.max <- modData$Int.max-1
+
+# Transformations for other controls
+modData$lngdpCap = log(modData$gdpCap)
+modData$lninflation_l1 = logTrans(modData$inflation_l1)
+modData$democ = as.numeric(modData$polity2>=6)
+modData$polity2 = modData$polity2 + 11
+###################################################################
+
+## MODELS FOR GDP GROWTH (ANNUAL %)
+###################################################################
+# Model parameters
+dv = 'gdpGr_l0'
+kivs = c('lnminDist.min', 'lncapDist.min')
+cntrls = c(
+  'Int.max',
+  'durSt1max',  'confAreaProp', 'nconf', 
+  'upperincome', 'lninflation_l1',  'polity2', 'resourceGDP',  'gdpGr.mean_l0')
+
+# Run dist models in pieces
+library(magrittr)
[…]

### 2015-08-25 R/Analysis/models.R

@@ -9,8 +9,6 @@ genTikz=FALSE
 
 # CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
 ###################################################################
-logTrans=function(x){ log( x + abs(min(x, na.rm=T)) + 1) }
-
 # Log transforming DVs
 modData$lngdp_l0 = log(modData$gdp_l0)
 modData$lngdp = log(modData$gdp)
@@ -38,20 +36,6 @@ modData$polity2 = modData$polity2 + 11
 ## MODELS FOR GDP GROWTH (ANNUAL %)
 ###################################################################
 # Model parameters
-modForm = function(dv='gdpGr_l0', ivs, id='ccode', type='random'){
-  base = paste(dv, paste(ivs, collapse=' + '), sep=' ~ ')
-  if(type=='random'){
-    eff = paste0('(1 |', id, ')')
-    base = paste(base, eff, sep=' + ')
-  }
-
-  if(type=='fixed'){
-    eff = paste0('factor(', id, ') - 1')
-    base = paste(base, eff, sep=' + ')
-  }
-  return(formula(base))
-}
-
 dv = 'gdpGr_l0'
 kivs = c('lnminDist.min', 'lncapDist.min')
 cntrls = c(
@@ -76,15 +60,6 @@ rmse=function(x){sqrt( mean( (residuals(x)^2) ) )}
 
 Reduce('-',quantile(modData$lngdpGr_l0,c(0.75,0.25),na.rm=T))
 rmse(mCity); rmse(mCap)
-###################################################################
-
-###################################################################
-# Regression Tables
-library(stargazer)
-# Tabular depictions for PRIO city models
-stargazer(mCity, mCap)
-# Tabular depictions for ACLED city models
-stargazer(mAcled, mAcledCap)
 ###################################################################
 
 ###################################################################

### 2015-08-25 R/Analysis/modelsIntensity.R

@@ -23,22 +23,7 @@ prepData = function(modData){
 	modData$polity2 = modData$polity2 + 11
 	return(modData)
 }
-# Model formulas
-modForm = function(dv='gdpGr_l0', ivs, id='ccode', type='random'){
-  base = paste(dv, paste(ivs, collapse=' + '), sep=' ~ ')
-  if(type=='random'){
-    eff = paste0('(1 |', id, ')')
-    base = paste(base, eff, sep=' + ')
-  }
 
-  if(type=='fixed'){
-    eff = paste0('factor(', id, ') - 1')
-    base = paste(base, eff, sep=' + ')
-  }
-  return(formula(base))
-}
-# Log transformations
-logTrans=function(x){ log( x + abs(min(x, na.rm=T)) + 1) }
 # Model specifications
 dv = 'gdpGr_l0'
 kivs = c('lnminDist.min', 'lncapDist.min')

### 2015-08-25 R/Analysis/modelsInteractionArea.R

@@ -9,8 +9,6 @@ genTikz=FALSE
 
 # CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
 ###################################################################
-logTrans=function(x){ log( x + abs(min(x, na.rm=T)) + 1) }
-
 # Log transforming DVs
 modData$lngdp_l0 = log(modData$gdp_l0)
 modData$lngdp = log(modData$gdp)
@@ -41,20 +39,6 @@ modData$capArea = modData$lncapDist.min * modData$confAreaProp
 ## MODELS FOR GDP GROWTH (ANNUAL %)
 ###################################################################
 # Model parameters
-modForm = function(dv='gdpGr_l0', ivs, id='ccode', type='random'){
-  base = paste(dv, paste(ivs, collapse=' + '), sep=' ~ ')
-  if(type=='random'){
-    eff = paste0('(1 |', id, ')')
-    base = paste(base, eff, sep=' + ')
-  }
-
-  if(type=='fixed'){
-    eff = paste0('factor(', id, ') - 1')
-    base = paste(base, eff, sep=' + ')
-  }
-  return(formula(base))
-}
-
 dv = 'gdpGr_l0'
 kivs = c('lnminDist.min', 'minArea', 'lncapDist.min', 'capArea')
 # kivs = c('lnminDist.min', 'minAreaSum', 'lncapDist.min', 'capAreaSum')

### 2015-08-25 R/Analysis/modelsOrigCity.R

@@ -9,8 +9,6 @@ genTikz=FALSE
 
 # CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
 ###################################################################
-logTrans=function(x){ log( x + abs(min(x, na.rm=T)) + 1) }
-
 # Log transforming DVs
 modData$lngdp_l0 = log(modData$gdp_l0)
 modData$lngdp = log(modData$gdp)
@@ -32,20 +30,6 @@ modData$polity2 = modData$polity2 + 11
 ## MODELS FOR GDP GROWTH (ANNUAL %)
 ###################################################################
 # Model parameters
-modForm = function(dv='gdpGr_l0', ivs, id='ccode', type='random'){
-  base = paste(dv, paste(ivs, collapse=' + '), sep=' ~ ')
-  if(type=='random'){
-    eff = paste0('(1 |', id, ')')
-    base = paste(base, eff, sep=' + ')
-  }
-
-  if(type=='fixed'){
-    eff = paste0('factor(', id, ') - 1')
-    base = paste(base, eff, sep=' + ')
-  }
-  return(formula(base))
-}
-
 dv = 'gdpGr_l0'
 kivs = 'lnminDist.min'
 cntrls = c(

### 2015-08-25 R/Analysis/opendata.R

@@ -5,7 +5,6 @@ rm(list=ls())
 if(Sys.info()["user"]=="janus829")
 {pathMain="~/Desktop/Research/Rhodium/R";
  pathGraphics="~/Dropbox/Research/Rhodium/Graphics";
- pathFunctions="~/Desktop/Prog Notes/R Functions";
  pathData="~/Dropbox/Research/Rhodium/Data"
 }
 
@@ -23,11 +22,6 @@ if(Sys.info()["user"]=="Ben")
  pathFunctions="C:/Users/Ben/Documents/Github/Rhodium/R";
  pathData="C:/Users/Ben/Dropbox/Rhodium/Data"
 }
-
-# Concatenation operator
-"+" <- function(...) UseMethod("+")
-"+.default" <- .Primitive("+")
-"+.character" <- function(...) paste(...,sep="")
 
 library(maptools)
 library(RColorBrewer)

### 2015-08-25 R/Analysis/revLetterExtra.R

@@ -14,8 +14,6 @@ genTikz=FALSE
 
 # CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
 ###################################################################
-logTrans=function(x){ log( x + abs(min(x, na.rm=T)) + 1) }
-
 # Log transforming DVs
 modData$lngdp_l0 = log(modData$gdp_l0)
 modData$lngdp = log(modData$gdp)

### 2015-08-25 R/setup.R

@@ -42,6 +42,7 @@ library(countrycode)
 numSM=function(x){as.numeric(as.character(x))}
 charSM=function(x){as.character(x)}
 contToCat=function(x,by=0.1){ cut(x, breaks=quantile(x,seq(0,1,by),na.rm=T)) }
+logTrans=function(x){ log( x + abs(min(x, na.rm=T)) + 1) }
 
 # Lagging vars
 lagTS <- function(x,l){
@@ -59,6 +60,26 @@ lagDataSM <- function(data, country_year, country, varsTOlag, lag=1)
     } )
   colnames(lagData) <- paste('lag', lag, '_', varsTOlag, sep='')
   cbind(data, lagData)
+}
+
+# Create model formula
+modForm = function(dv='gdpGr_l0', ivs, id='ccode', type='random'){
+  base = paste(dv, paste(ivs, collapse=' + '), sep=' ~ ')
+  if(type=='random'){
+    eff = paste0('(1 |', id, ')')
+    if(length(eff)>1){ eff = paste(eff, collapse='+') }
+    base = paste(base, eff, sep=' + ')
+  }
+
+  if(type=='fixed'){
+    eff = paste0('factor(', id, ')')
+    if(length(eff)>1){
+      eff = paste0( paste(eff, collapse='+'), '- 1') } else {
+        eff = paste0(eff, '- 1')
+      }    
+    base = paste(base, eff, sep=' + ')
+  }
+  return(formula(base))
 }
 
 # http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)/#Helper functions

### 2015-08-25 LaTeX/Revision/editor.tex
updates all around

@@
 \textcolor{blue}{\emph{
-	stuff
+	We have run a model on our full panel dataset to calculate a benchmark on the effect of any conflict on GDP growth.
+The results of this analysis have been added to the paper.
+To make the baseline model as comparable as possible to the model that we use to test our distance hypothesis, we adopt as similar a specification as possible.
+Specifically, the dependent variable is again GDP growth.
+Then our independent variables are, each lagged by one year:
+	\begin{itemize}
+		\item Civil war, this is just a binary to indicate whether a civil war took place in that year
+		\item Upperincome, this is a binary to indicate whether the country is classified as upper or lower income according to the Worldbank
+		\item Logged, inflation
+		\item Polity score
+		\item Resources as a percent of GDP
+		\item Average GDP growth across the world for that year
+	\end{itemize}
+	We do not include the conflict-specific measures (Distance, Intensity, Duration, and Area) from our distance model since they would just have a value of NA during non-conflict years.
+The key finding from this analysis is that a civil war is related to lower levels of GDP growth, however, this effect is marginal and only significant at a 90\% confidence interval.
+To determine the substantive significance of a civil war we employ a simulation based approach, similar to what we did to assess the effect of conflict distance from urban centers on growth, and we find that there is a marginal difference but the effect is highly uncertain.
+We use this finding as a lead in to our main model describing the effect of conflict distance from urban centers on growth.
 }}
@@
 \textcolor{blue}{\emph{
-	We retested our hypothesis using the ACLED dataset and here as well we find that our distance measure of conflict to major urban centers is significantly negative. 
+	We retested our hypothesis using the ACLED dataset and we find that our distance measure of conflict to major urban centers is significantly negative.
+We have included these results in the Appendix under the subsection ACLED Analysis, we have also added in a footnote in the paper indicating that our results remain robust when estimated on this alternative dataset.
 }}

### 2015-08-25 LaTeX/Revision/rev1.tex
updates all around

@@
 	We reran the models per this specification and have included the results in the appendix.
-In both low intensity and high intensity cases we find that the distance variables remain significant and in the hypothesized direction, but as R1 expected the $\beta$ estimate of our distance variables was noticeably higher when using high intensity versus low intensity civil conflict cases.
+In both low intensity and high intensity cases we find that the distance variables remain significant and in the hypothesized direction, but as R1 expected the $\beta$ estimate of our distance variables is noticeably higher when using high intensity versus low intensity civil conflict cases.
 }}

### 2015-08-25 LaTeX/Revision/rev2.tex
updates all around

@@
 \item \textcolor{blue}{\emph{
-	We provide a discussion of this alternative explanation following our empirical analysis.
+	We do not view this as an alternative to the story that we present, rather we see it as an interesting and valuable extension to pursue in future work.
+Our key argument is simply that conflicts which are proximate to points of economic interest, specifically, the capital and major cities, are likely to have a more deleterious impact on growth.
+If only strong rebel groups are able to initiate conflicts close to cities that does not directly challenge our argument, rather it adds another important dimension to it.
+At this point we are uncertain as to whether only strong rebel groups would be able to initiate conflict close to urban centers, but the argument suggested by the reviewer is certainly possible and we consider it a valuable future research question to pursue.
+We have added a discussion of it to the conclusion of our paper.
 }}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{\emph{
+	With respect to the duration finding our argument would be that more important to determining the effect of conflict on growth is its proximity to urban centers.
+Conflicts can be long lasting have an ambiguous effect on growth if they are simply occurring in the periphery of countries.
+We certainly would not have argued for a positive effect of conflict duration on growth prior to running the analysis, but the fact that it has occurred may open up future, interest research questions.
+	Our response to the unexpected effect of the number of conflicts a country has faced on growth is similar.
+We would again argue that it is not just that a number of conflicts our occurring that would dampen growth but where they are occurring is what matters.
+}}
 \end{itemize}
@@
 
-\item Robustness. The strategy that consists to run a six-fold cross-validation is convincing. In the same spirit, I would like to see the same exercise when one country is left out of the sample.
+% \item Robustness. The strategy that consists to run a six-fold cross-validation is convincing. In the same spirit, I would like to see the same exercise when one country is left out of the sample.
 
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
+% \begin{itemize}
+% \item \textcolor{blue}{\emph{
+
+% }}
+% \end{itemize}
 
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{\emph{
+	We have added in additional information to aid in interpreting the visual results where possible.
+However, we do have preferences for presenting additional information in the captions instead of by adding in legends.
+}}
 \end{itemize}
@@
 \begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
+\item \textcolor{blue}{\emph{
+	We have added in tabular representations of each of the key regression models. 
+}}
 \end{itemize}
 
-\item The recent works on cities of Quoc-Anh Do seems to me as a complement to this paper.
+% \item The recent works on cities of Quoc-Anh Do seems to me as a complement to this paper.
 
-\begin{itemize}
-\item \textcolor{blue}{\emph{stuff}}
-\end{itemize}
+% \begin{itemize}
+% \item \textcolor{blue}{\emph{stuff}}
+% \end{itemize}
 

### 2015-08-25 LaTeX/RhodiumAppendix.tex
updates all around

@@
 
+\subsection{Baseline Effect of Civil Conflict on Growth}
+
+In Table \ref{tab:baseline} below, we show the fixed effects regression results for the model in which we utilize a full country year panel in order to define a baseline effect of civil war on economic growth.
+
+\input{baseline.tex}
+
 \subsection{Conflict Distance Models in Tabular Format}
 
-Here we present the results of our models measuring the effect of conflict distance in a tabular format.
+Here we present the results of our models measuring the effect of conflict distance in a tabular format, results for distance from the capital city are shown in Table \ref{tab:capDistMod} and for any major city in Table \ref{tab:cityDistMod} below.
 The first column in each of the tables below is a simple linear model regressing the conflict distance parameter on GDP Growth, in the second we add our controls, in the third we include random effects, varying intercepts, for country, in the fourth random effects for year, and in the last random effects for both country and year.
@@
 Here instead of treating conflict intensity as a control, we re-do our primary models estimating the effect of distance on growth, but restricting to the civil conflicts coded as wars and then a separate model for civil conflicts coded as low intensity events.
+In both low intensity and high intensity cases we find that the conflict distance variables remain significant and in the expected direction, but the $\beta$ estimate of our distance variables is noticeably higher when using high intensity versus low intensity civil conflict cases.
+The results are presented in Table~\ref{tab:modHiLoIntensity} below.
 
@@
 The analysis procedure then continues as described in Section~\ref{empirics}: the minimum distance measure is calculated as the natural logarithm of the average distance in kilometers from any conflict site to the nearest major city (or capital).
-The results are presented in Figures~\ref{fig:acled} and \ref{fig:acledfixef}.
+The results are presented in Table~\ref{tab:acledRegResults} below.
 
-\begin{figure}
-	\centering
-	\begin{tabular}{cc}
-		\subfloat[SubFigure 1][Capital City]{
-			\resizebox{.45\textwidth}{!}{\input{mAcledCapCoefPlot.tex}}
-		\label{fig:acled}} &
-		\subfloat[SubFigure 2][Any Major City]{
-			\resizebox{.45\textwidth}{!}{\input{mAcledCityCoefPlot.tex}}
-		\label{fig:acledfixef}}
-	\end{tabular}
-	\caption{Regression results using conflict distance from capital city on the left, and the chart on the right shows regression results using minimum conflict distance from any major city.
-Conflict data based on ACLED.
-Darker colors indicates that the coefficient estimate is significantly different from zero at a 95\% CI, while lighter the same for a 90\% CI.
-Grey indicates that the estimate is not significantly different from zero at either of those intervals.
-The lagged number of conflicts within a country is also included in the models but is omitted from the plots above to enhance readability.}
-	\label{fig:coefplot}
-\end{figure}
+\input{acledModels.tex}
+\FloatBarrier

### 2015-08-25 LaTeX/RhodiumConcl.tex
recompiled with new intro
updates all around

@@
 Future work in this line of inquiry will explore each of these hypotheses using geospatial data on the economic assets of interest.
+One additional question that springs from our work here is whether only certain rebel groups are able to initiate conflicts near urban centers.
+Specifically, it could be the case that only the strongest, richest rebel groups are able to survive and initiate conflicts proximate to the capital or other major cities.
+In future research, it would certainly be interesting and valuable to determine whether there are certain rebel group characteristics that relate to the geolocation of conflicts relative to points of economic interest.
 

### 2015-08-25 LaTeX/RhodiumEmp.tex
recompiled versions
updates all around

@@
 For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at either the 90 and 95\% confidence intervals, providing at least some initial evidence that we are justified in our choice.
-However, as \citet{clark:linzer:2015} note not finding a significant difference through the Hausman test does not necessarily mean ``that the random effects is `safely` free from bias, and therefore to be preferred over the fixed effects estimator'' (pg., 2).
-We utilize their more nuanced typology for further arbitrating between fixed and random effects, and again we find that random effects are preferred in this case.\footnote{A lengthier discussion of the \citet{clark:linzer:2015} procedure and its application to our data can be found in the Appendix.}
+However, as \citet{clark:linzer:2015} note the Hausman test should not be the sole determination for choosing between fixed or random effects.
+We utilize their more nuanced typology for further arbitrating between fixed and random effects, and again we find that random effects are preferred in this case.\footnote{Specifically to take into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects.
+In our case, we have over 70 countries but for over half of those we only have five conflict instances or less.
+Given such a data structure Clark \& Linzer (2015) recommend to examine the level of correlation between the regressor and unit effects to determine the appropriate modeling framework.
+For both our distance models, the level of correlation between the regressor and unit effects is less than 0.20, which accords with a random effects recommendation under the framework described by Clark \& Linzer (2015).}
 
-The total number of observations we have for this analysis are 497 country-year cases of civil war from 68 different countries during the period of 1989 to 2008.
+The total number of observations we have for this analysis are 505 country-year cases of civil war from 68 different countries during the period of 1989 to 2008.
 The estimation model is shown below, where $Ln(Min.
@@
 
-\subsection{Baseline Model}
+\subsection{Baseline Effect of Civil Conflict on Growth}
 
 Before we move to discussing the results of the model specification that we have described above we estimate a simple, baseline model to assess the effect of any civil conflict on growth.
-For this model we use a specification as similar as possible to the one we explicated in the previous section, with the key difference being that this baseline model is estimated using a full country-year panel with fixed effects.\footnote{In choosing between fixed and random effects, we again followed the typology set out by \citet{clark:linzer:2015}, and, in this case, found that the fixed effects specification was preferred.} The dependent variable is again annual percent change in GDP from the World Development Indicators, and the key independent variable here is whether or not the country was engaged in a civil war in the previous year according to the PRIO Armed Conflict dataset.
+For this model we use a specification as similar as possible to the one we explicated in the previous section, with the key difference being that this baseline model is estimated using a full country-year panel with fixed effects.\footnote{In choosing between fixed and random effects, we again began by running a Hausman test and followed the recommendations set out in \citet{clark:linzer:2015}.
+In this case, found that the fixed effects specification was preferred.} The dependent variable is again annual percent change in GDP from the World Development Indicators, and the key independent variable here is whether or not the country was engaged in a civil war in the previous year according to the PRIO Armed Conflict dataset.
 Since we are using a full country-year panel, we have to omit the PRIO conflict specific variables (e.g., conflict intensity, conflict duration) as they are undefined for country-year observations in which no conflict was taking place.
@@
 We will eschew discussing the controls since the primary purpose of this analysis is to determine a baseline effect for civil war.
-Additionally, for the sake of space we do not show the full results from this regression, but they are available in section \ref{baseline} of the Appendix.
-The key result pertains to the civil war variable, the $\beta$ estimate is approximately -1.011 with a standard error of 0.521.
+Additionally, for the sake of space we do not show the full results from this regression, but they are available in section \ref{tab:baseline} of the Appendix.
+The key result pertains to the civil war variable, the $\beta$ estimate for this variable is approximately -2.568 with a standard error of 0.502.
 
@@
 \end{figure}
+\FloatBarrier
 
 The analysis here highlights that there is little distinguishable difference in the expected values of GDP growth by whether or not there a country was experiencing a civil war in the previous year.
+We argue that this is because the effect of civil conflict on economic growth becomes particularly relevant when that conflict is proximate to economic points of interest such as capital cities and major urban centers.
 
@@
 
-We depict the results of our models in figures \ref{fig:capCoef} and \ref{fig:cityCoef}.
+We depict the results of our conflict distance models in figures \ref{fig:capCoef} and \ref{fig:cityCoef}.
 The results across the two models are broadly consistent, so we will discuss them in tandem.

### 2015-08-25 R/Analysis/fullPanelModel.R

@@ -9,7 +9,7 @@ load('combinedData.rda')
 modData = fullData
 
 # Gen tikz?
-genTikz=TRUE
+genTikz=FALSE
 
 # CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
 ###################################################################
@@ -102,6 +102,10 @@ if(genTikz){ dev.off() }
 # Model results: Table
 library(stargazer)
 stargazer(plmFE)
+
+# Number of countries
+slice = na.omit( regData[,c('ccode','gdpGr_l0',kivs[1], cntrls)] )
+length(unique(slice$ccode))
 ###################################################################
 
 ###################################################################

### 2015-08-25 R/Analysis/models.R

@@ -72,7 +72,7 @@ otherCovars=c(
   'Duration$_{t-1}$', 'Area$_{t-1}$',
   'Number of conflicts$_{t-1}$',  
   'Upper Income', 'Ln(Inflation)$_{t-1}$', 'Democracy$_{t-1}$',
-  'Resource Rents/GDP$_{t}$', 'World GDP Growth$_{t}$')
+  'Resource Rents/GDP$_{t-1}$', 'World GDP Growth$_{t}$')
 
 vnames=c('Ln(Min. City Dist.)$_{t-1}$', otherCovars)
 temp <- ggcoefplot(coefData=summary(mCity)$'coefficients',
@@ -94,25 +94,12 @@ if(genTikz){ tikz(file='mCapCoefPlot.tex', width=4, height=6, standAlone=F)}
 temp
 if(genTikz){ dev.off() }
 
-vnames=c('Ln(Min. City Dist.)$_{t-1}$', "Ln(Inflation)$_{t-1}$","Democracy$_{t-1}$","Resource Rents/GDP$_{t}$","World GDP Growth$_{t}$")
-temp <- ggcoefplot(coefData=summary(mAcled)$'coefficients'[c(2,4,5,6,7),],
-                   vars=na.omit(rownames(summary(mAcled)$'coefficients')[c(2,4,5,6,7)]), 
-                   varNames=vnames, Noylabel=FALSE, coordFlip=TRUE,
-                   colorGrey=FALSE, grSTA=0.5, grEND=0.1)
-setwd(pathGraphics)
-if(genTikz){ tikz(file='mAcledCityCoefPlot.tex', width=4, height=6, standAlone=F)}
-temp
-if(genTikz){ dev.off() }
-
-vnames=c('Ln(Min. Capital Dist.)$_{t-1}$', "Ln(Inflation)$_{t-1}$","Democracy$_{t-1}$","Resource Rents/GDP$_{t}$","World GDP Growth$_{t}$")
-temp <- ggcoefplot(coefData=summary(mAcledCap)$'coefficients'[c(2,4,5,6,7),],
-                   vars=na.omit(rownames(summary(mAcledCap)$'coefficients')[c(2,4,5,6,7)]), 
-                   varNames=vnames, Noylabel=FALSE, coordFlip=TRUE,
-                   colorGrey=FALSE, grSTA=0.5, grEND=0.1)
-setwd(pathGraphics)
[…]

### 2015-08-26 LaTeX/RhodiumEmp.tex
fixed typos and stuff

@@
 This dataset contains information on the geographical centers of armed conflict events and the area covered by each conflict at a yearly level from 1989 to 2008.
-In recent years, other geo-referenced datasets have been developed that go beyond just providing information on conflict centroids and area to providing an actual spatial grid structure through which to conduct analysis \citep{tollefsen:etal:2012}.
+In recent years, other geo-referenced datasets have been developed that go beyond just providing information on conflict centroids and area to providing an actual spatial grid structure representing high-resolution spatial distributions of conflict \citep{tollefsen:etal:2012}.
 However, these data are not available globally and would therefore unnecessarily limit the external validity of the current analysis.\footnote{Nonetheless, we conduct a robustness test of our primary models using data from the Armed Conflict Location and Event Data (ACLED) Project.
@@
 Because the location of conflict is critical for this analysis, the urban bias of disaggregated event data is unacceptable.
-For the purpose of this analysis, we deliberately avoid using these datasets since our primary interest is in examining variation in changes to GDP growth at a national level.
 
 To construct a time-series cross-sectional database of urban centers, we turn to yearly editions of \emph{The World Alamanac}.
-More refined subnational data listing urban centers by their contribution to economic output would be the most direct way to test our hypothesis, however, cross-national data such as this over the time period of our analysis, especially for developing countries, is simply not available.
+More refined subnational data listing urban centers by their contribution to economic output would be the most direct way to test our hypothesis; however, cross-national data such as this over the time period of our analysis, especially for developing countries, is simply not available.
 \emph{The World Alamanac} lists the major cities in a country by population, thus providing us with a second best approximation of the urban centers that are most relevant for a particular national economy.
@@
 While our hypothesis is most accurately represented by distance from any major urban centers, distance from capital cities provides an appealing and consistent alternative measure.
-Every country has a capital city in our sample, so using this alternative measure does not rely on differing population or density thresholds across countries that must be used in coding major cities.
+Every country has a capital city in our sample so using this alternative measure does not rely on differing population or density thresholds across countries that must be used in coding major cities.
 
@@
 In most cases, this clustering is indicative of the same conflict moving within the geographic boundaries of a country over time.
-The blue diamonds in \ref{fig:CityConfMap} denote the locations of major cities from 1989 to 2008.
+The blue diamonds in figure \ref{fig:CityConfMap} denote the locations of major cities from 1989 to 2008.
 Countries shaded in grey are those for which no armed conflict took place in this period according to the PRIO dataset.
@@
 
-Using our geo-referenced conflict and urban center data, we proceed to compute the proximity of every civil armed conflict in a country-year from every urban center listed in that year.\footnote{Distances between centroid locations were computed using an iterative method of distance calculation proposed by \citet{vincenty:1975}.} Since our unit of analysis is the country-year, we aggregate the distance between conflicts and major cities by calculating the minimum logged distance any conflict is from a major city.
+Using our geo-referenced conflict and urban center data, we proceed to compute the proximity of every domestic armed conflict in a country-year to every urban center listed in that year.\footnote{Distances between centroid locations were computed using an iterative method of distance calculation proposed by \citet{vincenty:1975}.} Since our unit of analysis is the country-year, we aggregate the distance between conflicts and major cities by calculating the minimum logged distance any conflict is from a major city.
 For example, if a country faces four conflicts in a year, the datapoint for that country-year would be the minimum distance any conflict centroid is from any city centroid.
 In addition to identifying the minimum distance a conflict is from any city, we also create a variable that measures minimum distance of any conflict from the capital of the country.
-Given the importance of cities as drivers of macroeconomic growth the proximity of conflict to even one city should have at least a noticeable short-term impact on growth.
-Thus this choice of aggregation conforms clostest to our theoretical claims about how macroeconomic growth can be severely disrupted in cases where conflicts are proximate to major cities.
+Given the importance of cities as drivers of macroeconomic growth, the proximity of conflict to even one city should have at least a noticeable short-term impact on growth.
+Thus this choice of aggregation conforms closest to our theoretical claims about how macroeconomic growth can be severely disrupted in cases where conflicts are proximate to major cities.\footnote{We ran robustness tests using an alternative aggregation method for conflict distance.
+Rather than selecting the minimum distance of any conflict to any city in a given year, we took the average minimum distance of each conflict to the nearest city.
+The results were statistically significant and substantively similar across parameterizations.}
 
 Figure \ref{fig:distGdp} provides a cursory illustration of the relationship between GDP growth and our spatial proximity variables.
-Each bar on the rightmost panel represents the average GDP growth rate across country-years for which the minimum distance between the centroid of the conflict and capital city fell within a certain quartile range across our full sample.
+Each bar on the leftmost panel represents the average GDP growth rate across country-years for which the minimum distance between the centroid of the conflict and capital city fell within a certain quartile range across our full sample.
 Clearly, as the minimum distance from a conflict to capital city declines, there is a sharp decline in average growth rates for the following year.
@@
 Next, we move beyond this cursory illustration and explicate our full modeling strategy.
-Given how we constructed our spatial proximity of conflict variables, it would make little sense to include both within one model.
+Given how we constructed our spatial proximity of conflict variables, it would make little sense to include both capital distance and city distance within one model.
 The obvious problem we would run into is that there would be cases for which the minimum distance of a conflict to any city would be the same as the minimum distance to the capital.
@@
 From the PRIO Armed Conflict dataset we bring in additional information about conflict intensity, duration, the area covered by the conflict, and the number of conflicts \citep{themner:wallensteen:2014}.
-Conflict intensity is a binary that distinguishes between minor armed conflicts (between 25 and 999 annual battle deaths) and wars (at least 1000 annual battle deaths), and we set this equal to one if any of the conflicts in a country year were classified as a war and zero if not.
-In aggregating conflict duration to the country year level, we bring in the duration (measured in years) of the longest lasting conflict by a certain country-year.
+Conflict intensity is a binary that distinguishes between minor armed conflicts (between 25 and 999 annual battle deaths) and wars (at least 1000 annual battle deaths), and we set this equal to one if any of the conflicts in a country year were classified as a war and zero if not.\footnote{We also conduct robustness tests in which high intensity and low intensity subsets of the data are modeled separately.
+These can be found in Table \ref{tab:modHiLoIntensity} of the Appendix.} In aggregating conflict duration to the country year level, we bring in the duration (measured in years) of the longest lasting conflict by a certain country-year.
 Conflict area measures the conflict zone in square kilometers.
@@
 Given the findings in the extant literature, our expectation is that each of these measures should have a negative effect on economic growth.
-Though we also expect that the substantive implications of any one of these measures will matter less than the adverse effect to economic growth by the spatial proximity of conflict to urban centers.
+Though we also expect that the substantive implications of any one of these measures will matter less than the adverse effect to economic growth accounted for by the spatial proximity of conflict to urban centers.
 
 We also include a number of variables that help to capture structural and institutional aspects of the country itself.
-First, we include a binary for whether the country is classified as upper income by the World Bank and for the level of inflation in the country.
-Second, we also control for the level of democracy in the country using the polity index \citep{marshall:etal:2013}.
+First, we include binary indicators for whether the country is classified as upper income by the World Bank and for the level of inflation in the country.
+Second, we control for the level of democracy in the country using the polity index \citep{marshall:etal:2013}.
 We also control for the proportion of a country's GDP that is made up of natural resource rents.
 This is a particularly important variable to control for as countries that draw a large share of their GDP from natural resource rents likely rely less on urban centers to serve as drivers of growth.
-Finally, given that the timeframe of our sample overlaps with the occurrence of two major global economic crises, the 1997 Asian financial crisis and the 2008 financial crisis, we add a control for the average GDP growth across all countries in the world.
+Finally, given that the time frame of our sample overlaps with the occurrence of two major global economic crises, the 1997 Asian financial crisis and the 2008 financial crisis, we add a control for the average GDP growth across all countries in the world.
 
 To estimate variation in growth rates, we use a random effects model clustered on countries.
-A random effects specification is preferred to using fixed effects here as we are not interested in estimating the change in GDP within units over time, rather our purpose is to explain variation between units.
+A random effects specification is preferred to using fixed effects here as we are not interested in estimating the change in GDP within units over time; rather our purpose is to explain variation between units.
 However, to ensure that it is also statistically justifiable to make this choice we run a Hausman specification test \citep{greene:2008}.
-For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at either the 90 and 95\% confidence intervals, providing at least some initial evidence that we are justified in our choice.
-However, as \citet{clark:linzer:2015} note the Hausman test should not be the sole determination for choosing between fixed or random effects.
-We utilize their more nuanced typology for further arbitrating between fixed and random effects, and again we find that random effects are preferred in this case.\footnote{Specifically to take into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects.
+For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at both the 90 and 95\% confidence intervals, providing at least some initial evidence that we are justified in our choice.
+However, as \citet{clark:linzer:2015} note, the Hausman test should not be the sole determinant for choosing between fixed or random effects.
+We utilize their more nuanced typology for further arbitrating between fixed and random effects, and again we find that random effects are preferred in this case.\footnote{We take into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects.
 In our case, we have over 70 countries but for over half of those we only have five conflict instances or less.
-Given such a data structure Clark \& Linzer (2015) recommend to examine the level of correlation between the regressor and unit effects to determine the appropriate modeling framework.
+Given such a data structure, Clark \& Linzer (2015) recommend to examine the level of correlation between the regressor and unit effects to determine the appropriate modeling framework.
 For both our distance models, the level of correlation between the regressor and unit effects is less than 0.20, which accords with a random effects recommendation under the framework described by Clark \& Linzer (2015).}
 
-The total number of observations we have for this analysis are 505 country-year cases of civil war from 68 different countries during the period of 1989 to 2008.
-The estimation model is shown below, where $Ln(Min.
+For this analysis we have 505 country-year cases of civil war from 68 different countries during the period between 1989 to 2008.
+The model formula (omitting error terms) is shown below, where $Ln(Min.
 \; Conflict \; Dist.)_{i,t-1}$ is a placeholder for $Ln(Min.
@@
 
-Before we move to discussing the results of the model specification that we have described above we estimate a simple, baseline model to assess the effect of any civil conflict on growth.
+Before we move to discussing the results of the model specification that we have described above, we estimate a simple baseline model to assess the effect of any civil conflict on growth.
 For this model we use a specification as similar as possible to the one we explicated in the previous section, with the key difference being that this baseline model is estimated using a full country-year panel with fixed effects.\footnote{In choosing between fixed and random effects, we again began by running a Hausman test and followed the recommendations set out in \citet{clark:linzer:2015}.
-In this case, found that the fixed effects specification was preferred.} The dependent variable is again annual percent change in GDP from the World Development Indicators, and the key independent variable here is whether or not the country was engaged in a civil war in the previous year according to the PRIO Armed Conflict dataset.
+In this case we found that the fixed effects specification was preferred.} The dependent variable is again annual percent change in GDP from the World Development Indicators, and the key independent variable here is whether or not the country was engaged in a civil war in the previous year according to the PRIO Armed Conflict dataset.
 Since we are using a full country-year panel, we have to omit the PRIO conflict specific variables (e.g., conflict intensity, conflict duration) as they are undefined for country-year observations in which no conflict was taking place.
-The rest of the independent variables are similar to the model specified in the previous section, specifically, we include: whether or not the country is classified as upper income, lagged version of inflation, lagged version of polity, lagged version of resource rents as a proportion of GDP, and average GDP growth across all countries in the world.
+The rest of the independent variables are similar to the model specified in the previous section.
+Specifically, we include: whether or not the country is classified as upper income, the lagged version of inflation, the lagged version of polity, the lagged version of resource rents as a proportion of GDP, and the average GDP growth across all countries in the world.
 
@@
 Additionally, for the sake of space we do not show the full results from this regression, but they are available in section \ref{tab:baseline} of the Appendix.
-The key result pertains to the civil war variable, the $\beta$ estimate for this variable is approximately -2.568 with a standard error of 0.502.
+The key result pertains to the civil war variable for which we estimate a regression coefficient of approximately -2.568 with a standard error of 0.502.
 
-To assess the substantive significance of this variable we turn to a simulation based analysis.
-To to do this we set up two scenarios, one in which a civil war occurred and in the other no civil war, all the other parameters were set to their median value.
-Next, we conduct 1,000 random draws from a multivariate normal to obtain a distribution of point estimates of each regression coefficient.
-Last, we simply matrix multiply the draws from the multivariate normal with the transposed scenario matrix to obtain expected values of GDP growth by the two scenarios.
+To assess the substantive significance of this variable we turn to a simulation-based analysis.
+We simulate two scenarios, one in which a civil war occurred and another in which there is no civil war.
+All of the other parameters are set to their median value.
+Next, we conduct 1,000 random draws from a multivariate normal distribution to obtain a distribution of point estimates for each regression coefficient.
+Last, we simply matrix multiply the draws from the multivariate normal with the transposed scenario matrices to obtain expected values of GDP growth given the two scenarios.
 The resulting distributions are shown in figure \ref{fig:civWarEffect}.
@@
 
-The analysis here highlights that there is little distinguishable difference in the expected values of GDP growth by whether or not there a country was experiencing a civil war in the previous year.
+The analysis here highlights that there is little distinguishable difference in the expected values of GDP growth as a function of whether or not there a country was experiencing a civil war in the previous year.
 We argue that this is because the effect of civil conflict on economic growth becomes particularly relevant when that conflict is proximate to economic points of interest such as capital cities and major urban centers.
@@
 Turning to our hypothesis, we find strong support for the argument that spatial proximity of conflict to either a capital city or any major urban center is associated with lower levels of GDP growth.
-The positive coefficient on the logged, minimum conflict distance variables indicates that conflicts closer to major cities have an adverse effect on economic growth.
+The positive coefficient on the logged minimum conflict distance variables indicates that conflicts closer to major cities have an adverse effect on economic growth.
 
@@
 To assess the substantive effect of these results, we conduct a number of simulations.
-We set up scenarios where we hold all variables to their median except for logged, minimum conflict distance, which we range from its minimum to maximum value.
+We set up scenarios where we hold all variables to their medians except for logged minimum conflict distance, which we range from its minimum to maximum value.
 Next, we conduct 1,000 random draws from a multivariate normal to obtain distributions for the point estimates of each of the regression coefficients.
@@
 In both cases, conflicts located farther away from major cities have almost no adverse impact on economic growth, and, in fact, are likely to still see positive growth.
-As the proximity of conflicts to urban centers increases, however, we can clearly see substantive declines in growth rates start to emerge.
-Thus, through utilizing these spatial proximity measures we can start to explain why there is such meaningful variation in economic performance amongst countries facing internal armed conflict.
+As the proximity of conflicts to urban centers increases, however, we can clearly see substantive declines in growth rates.
+Thus, through utilizing these spatial proximity measures, we can begin to explain why there is such meaningful variation in economic performance amongst countries facing internal armed conflict.

### 2015-08-26 LaTeX/RhodiumLit.tex
recompiled with new intro
fixed typos and stuff

@@
 Widespread conflicts, they argue, are more likely to result in damage to infrastructure, divestment from normal state spending, and capital flight.
-Their results suggest that widespread civil wars are five times more costly than those fought over a narrower geographic area and can reduce GDP grotwh by 1.25\% annually.
+Their results suggest that widespread civil wars are five times more costly than those fought over a narrower geographic area and can reduce GDP growth by 1.25\% annually.
 
@@
 More specifically, they believe that strong economic growth proxies for robust governance and that states with low GDP growth likely have infrastructures that are unable to implement counter-insurgent policies.
-In an effort to parse out the causal effect of economic growth shocks on civil war, \citet{miguel:etal:2004} instrument income growth with rainfall.
+In an effort to parse out the causal effect of economic shocks on civil war, \citet{miguel:etal:2004} instrument income growth with rainfall.
 They find that rainfall is strongly correlated with income in sub-Saharan Africa, a region also prone to civil conflict in recent decades.
-Using a two-stage estimation approach, they conclude income is correlated with the likelihood of civil war.
+Using a two-stage estimation approach, they conclude that income is correlated with the likelihood of civil war.
 

### 2015-08-26 LaTeX/RhodiumTheory.tex
fixed typos and stuff

@@
 In the past three decades, as the pace of urbanization has accelerated, economists have devoted even more energy to investigating the role of city-level economic drivers \citep{lucas:1988, ciccone:hall:1996, begg:1999, henderson:wang:2007}.
-Most notably, \citeauthor{krugman:1991a} in his seminal 1991 article, ``Increasing Returns and Economic Geography'', convincingly showed the importance of studying economic outcomes within a spatial context.
+Most notably \citeauthor{krugman:1991a}, in his seminal 1991 article, ``Increasing Returns and Economic Geography'', convincingly showed the importance of studying economic outcomes within a spatial context.
 A key finding of Krugman's work on economic geography has been the importance of agglomeration effects, the idea that ``activities tend to cluster where markets are large and markets become larger where activities cluster'' \citep{krugman:1997}.
-\citet{henderson:2000} provides empirical evidence for why these agglomeration effects would manifest by showing that spatial clustering promotes economic efficiency in a variety of ways from simply enabling savings in transport costs to more efficiently functioning labor markets.
+\citet{henderson:2000} provides empirical evidence for why these agglomeration effects would manifest by showing that spatial clustering promotes economic efficiency in a variety of ways from simply enabling savings in transport costs to producing more efficiently functioning labor markets.
 
@@
 \citet{lucas:1988} provides a formal treatment of this argument and shows that the accumulation of human capital generates positive spillovers, where if even one worker acquires a new skill then spatially proximate workers would all become more productive.
-Empirical estimates of agglomeration effects indicate that a doubling of employment density correspond to a 5\% increase in labor productivity \citep{ciccone:hall:1996,ciccone:2002}.
+Empirical estimates of agglomeration effects indicate that a doubling of employment density corresponds to a 5\% increase in labor productivity \citep{ciccone:hall:1996,ciccone:2002}.
 \citet{glaeser:etal:1992} examine this problem empirically and show that cities are important for economic growth precisely because they lead to the knowledge spillovers that are important for innovation.
-Similar empirical results have been found by many others, which has led to a growing consensus on how cities can serve as important knowledge hubs for a national economy \citep{jaffe:etal:1993, glaeser:1994, firestone:2010}.
+Similar empirical results have been found by many others and have led to a growing consensus that cities can serve as important knowledge hubs for national economies \citep{jaffe:etal:1993, glaeser:1994, firestone:2010}.
 
@@
 However, as the tactics of warfare have shifted over the centuries, the relationship between violent conflict and cities has become more complex.
-Their dense populations also tempt belligerents and maximize the impact to cost ratio of a given violent action.
+Dense populations also tempt belligerents and maximize the impact to cost ratio of a given violent action.
 
 Additionally, warfare destroys transportation infrastructure, which can interfere both with commerce and with rebuilding during a conflict.
-In particular, conflict affects citizens ability and willingness to participate in commerce.
+In particular, conflict affects a citizen's ability and willingness to participate in commerce.
 When major population centers are threatened by violence, residents will be less likely to engage in economically productive activities.
@@
 	\includegraphics[width=.5\textwidth]{colombiaMap-crop}
-	\caption{This map illustrates the geographic distribution of all conflicts in Colombia, according to the PRIO Conflict Site Dataset, and major cities from 1989 to 2008.}
+	\caption{This map illustrates the geographic distribution of all conflict centroids in Colombia, according to the PRIO Conflict Site Dataset, and major cities from 1989 to 2008.}
 	\label{fig:columbiaMap}
@@
 The story from this map is clearly quite stark from that of Colombia.
-Whereas in Colombia conflict had come right to the gates of major cities, in India conflict clearly has been confined to the periphery.
+Whereas in Colombia conflict had come right to the gates of major cities, in India conflict has been primarily confined to the periphery.
 
@@
 	\includegraphics[width=.5\textwidth]{indiaMap-crop}
-	\caption{This map illustrates the geographic distribution of all conflicts in India, according to the PRIO Conflict Site Dataset, and major cities from 1989 to 2007. }
+	\caption{This map illustrates the geographic distribution of all conflict centroids in India, according to the PRIO Conflict Site Dataset, and major cities from 1989 to 2007. }
 	\label{fig:indiaMap}
@@
 For the period between 2009 and 2013, the National Consortium for the Study of Terrorism and Responses to Terrorism (START) described Boko Haram as ``among the deadliest [terrorist groups] in the world'' \citep{pate:etal:2014}.
-The groups tactics range from car and suicide bombings to direct assaults to mass kidnappings.
+The group's tactics range from car and suicide bombings to direct assaults to mass kidnappings.
 Nonetheless, Nigeria and Cameroon have both maintained strong economic growth during this period.
@@
 For much of this time, the cartel violence generally occurred in rural areas along drug trafficking routes and not within major cities.
-\citet{beittel:2011} writes in 2011 that ``drug trafficking-related killings remain concentrated in a relatively few cities.'' Meanwhile, several majors cities including the capital, Mexico City, have experienced relatively low levels of cartel violence.
+\citet{beittel:2011} writes that ``drug trafficking-related killings remain concentrated in a relatively few cities.'' Meanwhile, several majors cities including the capital, Mexico City, have experienced relatively low levels of cartel violence.
 

### 2015-08-26 LaTeX/Revision/editor.tex
negative to positive results

@@
 \textcolor{blue}{\emph{
-	We retested our hypothesis using the ACLED dataset and we find that our distance measure of conflict to major urban centers is significantly negative.
+	We retested our hypothesis using the ACLED dataset and we find that our distance measure of conflict to major urban centers is significantly positive.
 We have included these results in the Appendix under the subsection ACLED Analysis, we have also added in a footnote in the paper indicating that our results remain robust when estimated on this alternative dataset.

### 2015-08-26 LaTeX/RhodiumEmp.tex
stuff

@@
 Additionally, for the sake of space we do not show the full results from this regression, but they are available in section \ref{tab:baseline} of the Appendix.
-The key result pertains to the civil war variable for which we estimate a regression coefficient of approximately -2.568 with a standard error of 0.502.
+The key result pertains to the civil war variable for which we estimate a regression coefficient of approximately -2.568 with a standard error of 0.502.\footnote{This estimate corresponds closely to the result found by \citet{collier:1999}.}
 
@@
 
-The analysis here highlights that there is little distinguishable difference in the expected values of GDP growth as a function of whether or not there a country was experiencing a civil war in the previous year.
+The analysis here highlights that, while there is a noticeable substantive difference in the expected GDP growth of civil war and non-civil war countries, there is also a large amount of inferential uncertainty in these estimates.
 We argue that this is because the effect of civil conflict on economic growth becomes particularly relevant when that conflict is proximate to economic points of interest such as capital cities and major urban centers.
-
+In other words, the heterogeneity of civil war leads to a diversity of economic outcomes for affected states.
+%
 \section{Results}

### 2015-08-26 LaTeX/RhodiumTheory.tex
stuff

@@
 Nonetheless, Nigeria and Cameroon have both maintained strong economic growth during this period.
-The African Development Bank Group (AFDB) described Nigeria's economic growth from 2004 to 2014 as ``robust'' and projected ``moderate'' growth of 5\% for 2015 \citep{afdb:nigeria:2015}.
-On Cameroon, the AFDB said ``despite the security and humanitarian crisis in the region, Cameroonian growth remains strong at above 5\%'' \citep{afdb:cameroon:2015}.
+The African Development Bank Group (AFDB) described Nigeria's economic growth from 2004 to 2014 as ``robust'' and projected ``moderate'' growth of 5\% for 2015 (AFDB "Nigeria" 2015)\nocite{afdb:nigeria:2015}.
+On Cameroon, the AFDB said ``despite the security and humanitarian crisis in the region, Cameroonian growth remains strong at above 5\%'' (AFDB "Cameroon" 2015) \nocite{afdb:cameroon:2015}.
 

### 2015-08-26 LaTeX/Revision/editor.tex
cleanup, incorp edits from convo w ben, rename, recompile

@@
 We have added the reasoning described below to the relevant section in the actual paper as well.
-	For the ``Capital City'' and ``Any Major City'' models we ran a Hausman test to see if fixed or random effects were appropriate for our dataset, and in both cases we do not reject the null hypothesis of the Hausman test at a 90 or 95\% confidence interval indicating by at least that standard that both fixed and random effect approaches are consistent, with the latter obviously being more efficient.
+	For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at both the 90 and 95\% confidence intervals, providing at least some initial evidence that we are justified in our choice.
+}}
+
+\textcolor{blue}{\emph{
 	However, as Clark \& Linzer (2015) note the Hausman test should not be the sole determination for choosing between fixed or random effects.
 They perform a series of Monte Carlo simulations to determine the conditions under which a fixed or random effects model is appropriate and provide a rough typology.
-Specifically to take into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects.
+We take into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects.
 In our case, we have over 70 countries but for over half of those we only have five conflict instances or less.
@@
 For both our distance models, the level of correlation between the regressor and unit effects is less than 0.20, which accords with a random effects recommendation under the framework described by Clark \& Linzer (2015).
-	Another reason why we choose a random effects framework is because of our concerns with the unchanging and time invariant nature of where conflict is taking place relative to major urban centers.
+}}
+
+\textcolor{blue}{\emph{
+	Another reason why we choose to employ a random effects framework is because of our concerns with the unchanging and time invariant nature of where conflict is taking place relative to major urban centers.
 In Thailand, for example, the distance between conflict and urban centers in our dataset just ranges from approximately 790 to 810 kilometers, which basically indicates that conflicts are simply isolated to a specific part of the country.
-This same patterns holds for many other countries in our sample such as Mozambique (range: $\approx$ 705 - 860 km), Bangladesh (range: $\approx$ 198 - 237 km), Cambodia (range: $\approx$ 131 - 197 km), etc..
+This same patterns holds for many other countries in our sample such as Mozambique (range: $\approx$ 705 - 860 km), Bangladesh (range: $\approx$ 198 - 237 km), and Cambodia (range: $\approx$ 131 - 197 km).
 These ranges become even further compressed when we log them for use in our regression analysis.
@@
 \textcolor{blue}{\emph{
+	The manner in which both reviewers suggest running this analysis in a full country year setting is by introducing an interaction between a conflict dummy variable and the conflict distance variable.
 Including an interaction in this way is problematic for estimating the effect of conflict distance on conflict.
@@
 However, the choice of introducing a zero for the NAs would be arbitrary and problematic, as our variable would no longer truly be continuous.
-Instead it would be discontinuous in that we would have a large lump of observations at zero and then no observations until 1/7.31.
+Instead it would be ``discontinuous'' in that we would have a large lump of observations at zero and then no observations until 1/7.31.
+}}
+
+\textcolor{blue}{\emph{
 	Beyond the problems associated with transforming the variable in this way we would also run into issues of perfect collinearity with the inverted conflict distance measure and the interaction variable.
 The collinearity would result because the binary conflict variable is zero for every case that the inverted conflict distance variable is zero and one otherwise, meaning that multiplying the two will simply result in the inverted conflict distance variable again.
+}}
+
+\textcolor{blue}{\emph{
 	We have spent a fair bit of time trying to think of alternative approaches to modeling this in a full panel context using mixture or hierarchical approaches, but could find no mentions to develop a model for this type of data.

### 2015-08-26 LaTeX/Revision/rev1.tex
cleanup, incorp edits from convo w ben, rename, recompile

@@
 We have added the reasoning described below to the relevant section in the actual paper as well.
-	For the ``Capital City'' and ``Any Major City'' models we ran a Hausman test to see if fixed or random effects were appropriate for our dataset, and in both cases we do not reject the null hypothesis of the Hausman test at a 90 or 95\% confidence interval indicating by at least that standard that both fixed and random effect approaches are consistent, with the latter obviously being more efficient.
+	For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at both the 90 and 95\% confidence intervals, providing at least some initial evidence that we are justified in our choice.
+}}
+\item \textcolor{blue}{\emph{
 	However, as Clark \& Linzer (2015) note the Hausman test should not be the sole determination for choosing between fixed or random effects.
 They perform a series of Monte Carlo simulations to determine the conditions under which a fixed or random effects model is appropriate and provide a rough typology.
-Specifically to take into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects.
+We take into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects.
 In our case, we have over 70 countries but for over half of those we only have five conflict instances or less.
@@
 For both our distance models, the level of correlation between the regressor and unit effects is less than 0.20, which accords with a random effects recommendation under the framework described by Clark \& Linzer (2015).
-	Another reason why we choose a random effects framework is because of our concerns with the unchanging and time invariant nature of where conflict is taking place relative to major urban centers.
+}}
+\item \textcolor{blue}{\emph{
+	Another reason why we choose to employ a random effects framework is because of our concerns with the unchanging and time invariant nature of where conflict is taking place relative to major urban centers.
 In Thailand, for example, the distance between conflict and urban centers in our dataset just ranges from approximately 790 to 810 kilometers, which basically indicates that conflicts are simply isolated to a specific part of the country.
-This same patterns holds for many other countries in our sample such as Mozambique (range: $\approx$ 705 - 860 km), Bangladesh (range: $\approx$ 198 - 237 km), Cambodia (range: $\approx$ 131 - 197 km), etc..
+This same patterns holds for many other countries in our sample such as Mozambique (range: $\approx$ 705 - 860 km), Bangladesh (range: $\approx$ 198 - 237 km), and Cambodia (range: $\approx$ 131 - 197 km).
 These ranges become even further compressed when we log them for use in our regression analysis.
@@
 However, the choice of introducing a zero for the NAs would be arbitrary and problematic, as our variable would no longer truly be continuous.
-Instead it would be discontinuous in that we would have a large lump of observations at zero and then no observations until 1/7.31.
+Instead it would be ``discontinuous'' in that we would have a large lump of observations at zero and then no observations until 1/7.31.
+}} 
+\item \textcolor{blue}{\emph{
 	Beyond the problems associated with transforming the variable in this way we would also run into issues of perfect collinearity with the inverted conflict distance measure and the interaction variable.
 The collinearity would result because the binary conflict variable is zero for every case that the inverted conflict distance variable is zero and one otherwise, meaning that multiplying the two will simply result in the inverted conflict distance variable again.
+}}
+\item \textcolor{blue}{\emph{
 	We have spent a fair bit of time trying to think of alternative approaches to modeling this in a full panel context using mixture or hierarchical approaches, but could find no mentions to develop a model for this type of data.

### 2015-08-26 LaTeX/Revision/rev2.tex
cleanup, incorp edits from convo w ben, rename, recompile

@@
 For both our distance models, the level of correlation between the regressor and unit effects is less than 0.20, which accords with a random effects recommendation under the framework described by Clark \& Linzer (2015).
-	Another reason why we choose a random effects framework is because of our concerns with the unchanging and time invariant nature of where conflict is taking place relative to major urban centers.
+}}
+\item \textcolor{blue}{\emph{
+	Another reason why we choose to employ a random effects framework is because of our concerns with the unchanging and time invariant nature of where conflict is taking place relative to major urban centers.
 In Thailand, for example, the distance between conflict and urban centers in our dataset just ranges from approximately 790 to 810 kilometers, which basically indicates that conflicts are simply isolated to a specific part of the country.
-This same patterns holds for many other countries in our sample such as Mozambique (range: $\approx$ 705 - 860 km), Bangladesh (range: $\approx$ 198 - 237 km), Cambodia (range: $\approx$ 131 - 197 km), etc..
+This same patterns holds for many other countries in our sample such as Mozambique (range: $\approx$ 705 - 860 km), Bangladesh (range: $\approx$ 198 - 237 km), and Cambodia (range: $\approx$ 131 - 197 km).
 These ranges become even further compressed when we log them for use in our regression analysis.
 If we employed a fixed effects model to test our hypothesis we would in essence be removing many of these types of countries from our sample, or as Beck \& Katz (2001) would put it ``throwing out the baby with the bathwater''.
-	In terms of the roadmap mentioned by the reviewer, we have added an appendix item that runs the analysis in the way reviewer suggested and reports the results in a tabular format. 
 }}

### 2015-08-26 LaTeX/RhodiumEmp.tex
cleanup, incorp edits from convo w ben, rename, recompile

@@
 For both our distance models, the level of correlation between the regressor and unit effects is less than 0.20, which accords with a random effects recommendation under the framework described by Clark \& Linzer (2015).}
+
+Another reason why we choose to employ a random effects framework is because of our concerns with the unchanging and time invariant nature of where conflict is taking place relative to major urban centers.
+In Thailand, for example, the distance between conflict and urban centers in our dataset just ranges from approximately 790 to 810 kilometers, which basically indicates that conflicts are simply isolated to a specific part of the country.
+If we employed a fixed effects model to test our hypothesis we would in essence be removing many of these types of countries from our sample, or as \citet{beck:katz:2001} would put it ``throwing out the baby with the bathwater''.\footnote{This same patterns holds for many other countries in our sample such as Mozambique (range: $\approx$ 705 - 860 km), Bangladesh (range: $\approx$ 198 - 237 km), and Cambodia (range: $\approx$ 131 - 197 km).
+These ranges become even further compressed when we log them for use in our regression analysis.}
 

### 2015-08-26 LaTeX/RhodiumTheory.tex
cleanup, incorp edits from convo w ben, rename, recompile

@@
 Simultaneously, Syria's economy has shrunk dramatically.
-
-While FARC seems to exploit its ability to target areas of economic importance including cities, other insurgencies tend to be more peripheral.
+While FARC and insurgent groups in Syria seem to exploit their ability to target areas of economic importance including cities, other insurgencies tend to be more peripheral.
 India, for instance, has faced challenges by armed groups in its north-east for half a century.

### 2015-08-26 LaTeX/Revision/editor.tex
fixed up revise letter

@@
 \textcolor{blue}{\emph{
-	There are a number of reasons why we chose a random effects framework, however, we agree with the reviewers that these reasons were not clearly explicated in the text.
+	There are a number of reasons why we chose a random effects framework, however, we agree with the reviewers that these reasons were not at all clearly explicated in the text.
 The following discussion provides three reasons why we employ a random effects framework.
 We have added the reasoning described below to the relevant section in the actual paper as well.
-	For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at both the 90 and 95\% confidence intervals, providing at least some initial evidence that we are justified in our choice.
+	First, when running a Hausman specification test for our models using minimum conflict distance to any city and to capital city, we fail to reject the null hypothesis at both the 90 and 95\% confidence intervals, providing at least some initial evidence that we are justified in our choice (Greene, 2008).
 }}
@@
 They perform a series of Monte Carlo simulations to determine the conditions under which a fixed or random effects model is appropriate and provide a rough typology.
-We take into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects.
+Specifically, they suggest taking into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects.
 In our case, we have over 70 countries but for over half of those we only have five conflict instances or less.
@@
 	Another reason why we choose to employ a random effects framework is because of our concerns with the unchanging and time invariant nature of where conflict is taking place relative to major urban centers.
-In Thailand, for example, the distance between conflict and urban centers in our dataset just ranges from approximately 790 to 810 kilometers, which basically indicates that conflicts are simply isolated to a specific part of the country.
+In Thailand, for example, the distance between conflict and urban centers in our dataset just ranges from approximately 790 to 810 kilometers indicating that conflicts are simply isolated to a specific part of the country.
 This same patterns holds for many other countries in our sample such as Mozambique (range: $\approx$ 705 - 860 km), Bangladesh (range: $\approx$ 198 - 237 km), and Cambodia (range: $\approx$ 131 - 197 km).
 These ranges become even further compressed when we log them for use in our regression analysis.
-If we employed a fixed effects model to test our hypothesis we would in essence be removing many of these types of countries from our sample, or as Beck \& Katz (2001) would put it ``throwing out the baby with the bathwater''.
+If we employed a fixed effects model to test our hypothesis we would in essence be removing many of these types of countries from our sample, or as Beck \& Katz (2001) may put it ``throwing out the baby with the bathwater''.
 }}
@@
 \textcolor{blue}{\emph{
-	We have spent a fair bit of time trying to think of alternative approaches to modeling this in a full panel context using mixture or hierarchical approaches, but could find no mentions to develop a model for this type of data.
+	We have spent a fair bit of time trying to think of alternative approaches to modeling this in a full panel context using mixture or hierarchical approaches, but we found these approaches would be inappropriate here as well.
 	Despite this we strongly feel that our results are illustrative of an important and meaningful finding for the conflict literature.
@@
 	We do not include the conflict-specific measures (Distance, Intensity, Duration, and Area) from our distance model since they would just have a value of NA during non-conflict years.
-The key finding from this analysis is that a civil war is related to lower levels of GDP growth, however, this effect is marginal and only significant at a 90\% confidence interval.
-To determine the substantive significance of a civil war we employ a simulation based approach, similar to what we did to assess the effect of conflict distance from urban centers on growth, and we find that there is a marginal difference but the effect is highly uncertain.
+The key finding from this analysis is that a civil war is related to lower levels of GDP growth, however, the substantive effect of this variable is marginal.
+To determine the substantive significance of a civil war we employ a simulation based approach, similar to what we did to assess the effect of conflict distance from urban centers on growth, and we find that there is a noticeable difference but the effect is highly uncertain.
 We use this finding as a lead in to our main model describing the effect of conflict distance from urban centers on growth.
@@
 \textcolor{blue}{\emph{
-	We retested our hypothesis using the ACLED dataset and we find that our distance measure of conflict to major urban centers is significantly positive.
+	We retested our hypothesis using the ACLED dataset and we find that our distance measure of conflict to major urban centers is significantly positive, as expected.
 We have included these results in the Appendix under the subsection ACLED Analysis, we have also added in a footnote in the paper indicating that our results remain robust when estimated on this alternative dataset.

### 2015-08-26 LaTeX/Revision/rev1.tex
fixed up revise letter

@@
 \item \textcolor{blue}{\emph{
-	There are a number of reasons why we chose a random effects framework, however, we agree with the reviewers that these reasons were not clearly explicated in the text.
+	There are a number of reasons why we chose a random effects framework, however, we agree with the reviewers that these reasons were not at all clearly explicated in the text.
 The following discussion provides three reasons why we employ a random effects framework.
 We have added the reasoning described below to the relevant section in the actual paper as well.
-	For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at both the 90 and 95\% confidence intervals, providing at least some initial evidence that we are justified in our choice.
+	First, when running a Hausman specification test for our models using minimum conflict distance to any city and to capital city, we fail to reject the null hypothesis at both the 90 and 95\% confidence intervals, providing at least some initial evidence that we are justified in our choice (Greene, 2008).
 }}
@@
 \item \textcolor{blue}{\emph{
-	We have spent a fair bit of time trying to think of alternative approaches to modeling this in a full panel context using mixture or hierarchical approaches, but could find no mentions to develop a model for this type of data.
+	We have spent a fair bit of time trying to think of alternative approaches to modeling this in a full panel context using mixture or hierarchical approaches, but we found these approaches would be inappropriate here as well.
 	Despite this we strongly feel that our results are illustrative of an important and meaningful finding for the conflict literature.

### 2015-08-26 LaTeX/Revision/rev2.tex
fixed up revise letter

@@
 \item \textcolor{blue}{\emph{
-	We retested our hypothesis using the ACLED dataset and we find that our distance measure of conflict to major urban centers is significantly negative.
+	We retested our hypothesis using the ACLED dataset and we find that our distance measure of conflict to major urban centers is significantly positive, as expected.
 We have included these results in the Appendix under the subsection ACLED Analysis, we have also added in a footnote in the paper indicating that our results remain robust when estimated on this alternative dataset.

### 2015-08-26 LaTeX/RhodiumEmp.tex
final cleanups

--- 2015-08-26 LaTeX/RhodiumEmp.tex
@@
 In constructing our dataset, we thus restrict the cases we include to only those country-years in which there was an internal armed conflict.
-Additionally, the unit of observation for this analysis is the country-year.
+Additionally, the unit of observation for this analysis is the conflict-country-year.
 This enables us to directly explore whether variation in growth amongst countries experiencing internal conflict can be explained by the proximity of conflict to cities.
@@
 Thus this choice of aggregation conforms closest to our theoretical claims about how macroeconomic growth can be severely disrupted in cases where conflicts are proximate to major cities.\footnote{We ran robustness tests using an alternative aggregation method for conflict distance.
-Rather than selecting the minimum distance of any conflict to any city in a given year, we took the average minimum distance of each conflict to the nearest city.
+Rather than selecting the minimum distance of any conflict to any city in a given year, we took the average distance of each conflict to the nearest city.
 The results were statistically significant and substantively similar across parameterizations.}
@@
 Conflict area measures the conflict zone in square kilometers.
-To include this in our country-year model, we sum up the area covered by each conflict being fought and divide by the total land area of the country.
+To include this in our conflict-country-year model, we sum up the area covered by each conflict being fought and divide by the total land area of the country.
 Finally, the number of conflicts is simply a count of the number of ongoing internal armed conflicts in a country-year according to the PRIO dataset.
@@
 A random effects specification is preferred to using fixed effects here as we are not interested in estimating the change in GDP within units over time; rather our purpose is to explain variation between units.
-However, to ensure that it is also statistically justifiable to make this choice we run a Hausman specification test \citep{greene:2008}.
-For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at both the 90 and 95\% confidence intervals, providing at least some initial evidence that we are justified in our choice.
+However, to ensure that it is statistically justifiable to make this choice we run a Hausman specification test \citep{greene:2008}.
+For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at both the 90 and 95\% confidence intervals, which provides at least some initial evidence that we are justified in our choice.
 However, as \citet{clark:linzer:2015} note, the Hausman test should not be the sole determinant for choosing between fixed or random effects.
-We utilize their more nuanced typology for further arbitrating between fixed and random effects, and again we find that random effects are preferred in this case.\footnote{We take into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects.
+We utilize their more nuanced typology for further arbitrating between fixed and random effects, and again we find that random effects are preferred in this case.\footnote{Specifically, they suggest taking into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects.
 In our case, we have over 70 countries but for over half of those we only have five conflict instances or less.
@@
 For both our distance models, the level of correlation between the regressor and unit effects is less than 0.20, which accords with a random effects recommendation under the framework described by Clark \& Linzer (2015).}
+
+Another reason we choose to employ a random effects framework is because of our concerns with the unchanging and time invariant nature of where conflict is taking place relative to major urban centers.
+In Thailand, for example, the distance between conflict and urban centers in our dataset just ranges from approximately 790 to 810 kilometers indicating that conflicts are simply isolated to a specific part of the country.
+If we employed a fixed effects model to test our hypothesis we would in essence be removing countries such as these from our sample, or as \citet{beck:katz:2001} may put it ``throwing out the baby with the bathwater''.\footnote{This same patterns holds for many other countries in our sample such as Mozambique (range: $\approx$ 705 - 860 km), Bangladesh (range: $\approx$ 198 - 237 km), and Cambodia (range: $\approx$ 131 - 197 km).
+These ranges become even further compressed when we log them for use in our regression analysis.}
 
@@
 For this model we use a specification as similar as possible to the one we explicated in the previous section, with the key difference being that this baseline model is estimated using a full country-year panel with fixed effects.\footnote{In choosing between fixed and random effects, we again began by running a Hausman test and followed the recommendations set out in \citet{clark:linzer:2015}.
-In this case we found that the fixed effects specification was preferred.} The dependent variable is again annual percent change in GDP from the World Development Indicators, and the key independent variable here is whether or not the country was engaged in a civil war in the previous year according to the PRIO Armed Conflict dataset.
+In this case we found that the fixed effects specification was preferred.
+Results, however, are consistent if we were to employ a random effects specification.} The dependent variable is again annual percent change in GDP from the World Development Indicators, and the key independent variable here is whether or not the country was engaged in a civil war in the previous year according to the PRIO Armed Conflict dataset.
 Since we are using a full country-year panel, we have to omit the PRIO conflict specific variables (e.g., conflict intensity, conflict duration) as they are undefined for country-year observations in which no conflict was taking place.
@@
 Next, we conduct 1,000 random draws from a multivariate normal distribution to obtain a distribution of point estimates for each regression coefficient.
-Last, we simply matrix multiply the draws from the multivariate normal with the transposed scenario matrices to obtain expected values of GDP growth given the two scenarios.
+Last, we simply matrix multiply the draws from the multivariate normal with the transposed scenario matrix to obtain expected values of GDP growth given the two scenarios.
 The resulting distributions are shown in figure \ref{fig:civWarEffect}.
@@
 	\centering
-	\resizebox{.45\textwidth}{!}{\input{civWarEffect.tex}}
+	\resizebox{.6\textwidth}{!}{\input{civWarEffect.tex}}
 	\caption{Distributions of expected values for GDP growth based on whether or not a country experienced a civil war in the previous year.
@@
 The results across the two models are broadly consistent, so we will discuss them in tandem.
-Surprisingly, conflict duration and the number of conflicts a country is facing do not relate to GDP growth in the direction that we expected.
-The intensity of a conflict aligns in the direction that we would expect though its effect is marginal.
+Surprisingly, conflict duration and the number of conflicts a country is facing do not relate to GDP growth in the direction that we expected.\footnote{With respect to the duration finding our argument would be that more important to determining the effect of conflict on growth is its proximity to urban centers.
+Conflicts can be long lasting have an ambiguous effect on growth if they are simply occurring in the periphery of countries.
+Our response to the unexpected effect of the number of conflicts a country has faced on growth is similar.
+We would again argue that it is not just that a number of conflicts our occurring that would dampen growth but where they are occurring is what matters.} The intensity of a conflict aligns in the direction that we would expect though its effect is marginal.
 Additionally, the effect of having a high proportion of a country's land area immersed in conflict is sharply negative and aligns with the findings in the extant literature.

### 2015-08-26 LaTeX/coverLetter/rr_coverLetter.tex
added cover letter for resubmission

--- 2014-10-28 LaTeX/coverLetter/coverLetter.tex
@@
 
-This letter accompanies our submission of a manuscript for your consideration.
-The manuscript ``Enemy at the Gates: Variation in Economic Growth from Civil Conflict'' applies a subnational spatial analysis to explain variation in macroeconomic performance amongst countries experiencing intrastate conflict.
-Our theoretical argument, bridges the economic development literature on the importance of cities with extant literature on the effect of armed conflict to provide a novel explanation for the paradox of high macroeconomic growth in conflict ridden countries.
-We think this is a very timely topic and an important contribution to an ongoing debate about the economic effects of instrastate conflict.\\[1ex]
+This letter accompanies our resubmission of the manuscript ``Enemy at the Gates: Variation in Economic Growth from Civil Conflict'' (Manuscript ID: JCR- 14-0358), which applies a subnational spatial analysis to explain variation in macroeconomic performance amongst countries experiencing intrastate conflict.
+We feel confident that the revisions have made this a stronger manuscript and continue to think that the topic addressed by this manuscript is timely and serves an important contribution to the ongoing debate about the economic effects of instrastate conflict.\\[1ex]
 
@@
 
-\includegraphics [scale=.8]{/Users/janus829/Dropbox/Finances/signature.png}
+\includegraphics [scale=.8]{/Users/s7m/Dropbox/Finances/signature.png}
 

### 2015-10-25 LaTeX/Revision2/response.tex
rev letter 2

\section*{Reviewer: 2}

\begin{enumerate}
\item   Empirical strategy. As I have already mentioned in my first report, the empirical strategy is still a
major issue. I’m not convinced by the use of random fixed effects. At least, I would to like see a
table following the road map I gave in my previous comments. Last, I do not understand the last
argument about the weak time-variation of the distance to conflict. \\

\textcolor{blue}{\emph{
	stuff
}}

\item Sample. I am not sure about the accuracy of the answer to my third point. I asked for the use of a
full sample of countries. I don’t see a problem to estimate the following equation: $GDP_{it} = \beta_{1}Conflict_{it} + \beta_{2}Distance_{it}+\ldots+\zeta_{it}$. where $Distance_{it}=0$ when $Conflict_{it}=0$ and $Distance_{it}>0$ when $Conflict_{it}=1$. This specification allows to consider the full sample, to control for conflict and to estimate the main story about the distance to events. I expect the estimate of $\beta_{2}$ to be positive. \\

\textcolor{blue}{\emph{
	stuff
}}

\item Data. Considering the raw dataset on conflict, US and Spain were in war (Figure 3). PRIO defines different nature of conflicts. I would like to see results with this distinctions. \\

\textcolor{blue}{\emph{
	stuff
}}

\item The authors have to consider the country’s size. The distance has to be weighted by the country size. It cannot be an argument to rule out the possibility to use country fixed effects. \\

\textcolor{blue}{\emph{
	stuff
}}

\item The sub-section 3.3 on the descriptive cases is a good candidate for the (online) appendix. \\

\textcolor{blue}{\emph{
	stuff
}}

\item  The authors include binary indicators for whether the country is classified as upper income by the World Bank. It is highly endogeneous to the main variable of interest. \\

\textcolor{blue}{\emph{
	stuff
}}

\item The sample includes the 1997 Asian crisis and the 2008 financial crisis. The authors control for the average GDP growth across all countries. The better way to control for time-invariant common shocks is the inclusion of year fixed effects. \\

\textcolor{blue}{\emph{
	stuff
}}

\item The authors have to motivate why they decide to introduce the main variables with lags. Link to the introduction of lags, it would be interesting in the same framework to see whether it is possible \\

\textcolor{blue}{\emph{
	stuff
}}

\item Table 2. The authors mention random fixed effects with country, year or country + year. I do not understand what they mean. \\

\textcolor{blue}{\emph{
	stuff
}}

\item Tables have to be self-contained. \\

\textcolor{blue}{\emph{
	stuff
}}

\item The references have to actualized. \\

\textcolor{blue}{\emph{
	stuff
}}

\end{enumerate}

### 2015-10-25 LaTeX/Revision2/reviseLetter2.tex
rev letter 2

--- 2015-08-17 LaTeX/Revision/reviseLetter.tex
@@
 \usepackage{multirow}
+\usepackage{placeins}
 \usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry} 
@@
 
-\title[JCR-14-0358​]{JCR-14-0358​ entitled ``Enemy at the Gates: Variation in Economic Growth from Civil Conflict''}
+\title[JCR-14-0358.R1]{JCR-14-0358.R1 entitled ``Enemy at the Gates: Variation in Economic Growth from Civil Conflict''}
 
-\date{\today~~Version 0.01}
+\date{\today}
 \maketitle
@@
 
-We first would like to thank you for the opportunity to revise and resubmit our manuscript.
-We believe the manuscript has greatly benefitted from the Reviewers' helpful and thoughtful comments.
-We have thoroughly revised the manuscript, taking seriously each individual point raised by the Reviewers.
-The revision memo is organized by first responding to your comments and then addressing the reviewers' points.
+We first would like to thank you for the opportunity to revise and resubmit our manuscript once again.
+We have incorporated each of the comments made by R2 into the revised manuscript.
+The revision memo is organized in response to the bulleted set of questions that were posted with the decision letter.
 Our comments and responses are shown in \textcolor{blue}{\emph{BLUE}} below each point.
@@
 
-\input{editor.tex}
-\input{rev1.tex}
-\input{rev2.tex}
+\input{response.tex}
 

### 2015-11-06 LaTeX/Revision2/response.tex
create new appendix tables

@@
 
+\begin{enumerate}
+\item Empirical Strategy \& Sample: 
 \begin{enumerate}
@@
 	argument about the weak time-variation of the distance to conflict. \\
-
-\textcolor{blue}{\emph{
-	stuff
-}}
 
@@
 \\
+\end{enumerate}
 
 \textcolor{blue}{\emph{
-	stuff
+	The specification suggested above is one that we have now incorporated into our paper.
+We adopt the following specification suggested by the reviewer: $GDP_{it} = \beta_{1}Conflict_{it} + \beta_{2}Distance_{it}+\ldots+\zeta_{it}$.
+where $Distance_{it}=0$ when $Conflict_{it}=0$ and $Distance_{it}>0$ when $Conflict_{it}=1$.
+Further as suggested by the reviewer we estimate the model with fixed effects instead of random effects.
+The results are shown below
 }}

### 2015-11-06 R/setup.R

@@ -19,24 +19,22 @@ setwd(paste(pathMain,'/BuildingPanelData/',sep=''))
 load('panel.rda')
 
 # Loading libraries and functions
-library(abind)
-library(MASS)
-library(ggplot2)
+loadPkg=function(toLoad){
+  for(lib in toLoad){
+  if(! lib %in% installed.packages()[,1])
+    { install.packages(lib, repos='http://cran.rstudio.com/') }
+  suppressMessages( library(lib, character.only=TRUE) )
+  }
+}
+
+pks = c('abind', 'MASS', 'ggplot2', 'grid', 
+  'tikzDevice', 'RColorBrewer', 'sbgcop', 'reshape',
+  'foreign', 'doBy', 'lme4', 'shapefiles', 'cshapes',
+  'WDI', 'countrycode')
+loadPkg(pks)
+
+# gg theme
 theme_set(theme_bw())
-library(grid)
-library(tikzDevice)
-library(RColorBrewer)
-
-library(sbgcop)
-library(reshape)
-library(foreign)
-library(doBy)
-library(lme4)
-
-library(shapefiles)
-library(cshapes)
-library(WDI)
-library(countrycode)
 
 # Helpful functions
 numSM=function(x){as.numeric(as.character(x))}

### 2015-11-06 LaTeX/Revision2/response.tex
completed remaining analysis checks, all pass

@@
 Further as suggested by the reviewer we estimate the model with fixed effects instead of random effects.
-The results are shown below
+The results are shown below:
 }}
@@
 \textcolor{blue}{\emph{
-	stuff
+	We provide this distinction in
+
+	We reran the models per this specification and have included the results in the appendix.
+In both low intensity and high intensity cases we find that the distance variables remain significant and in the hypothesized direction.
 }}
@@
 \textcolor{blue}{\emph{
-	stuff
+	We reran the analysis weighting both of our conflict distance variables by area and the results again hold. We do not include them in the paper but show the results below. 
 }}
@@
 \textcolor{blue}{\emph{
-	stuff
+	Removing this variable has no effect on our analysis. We do not include this extra check in the paper but we show the results below.
 }}
@@
 \textcolor{blue}{\emph{
-	stuff
+	We run an alternative model using year fixed effects instead of a lagged GDP growth measure. Results are shown below are findings still hold.
 }}

### 2015-11-06 R/Analysis/fullPanelRevSpecification.R

@@ -1,68 +1,0 @@
-if(Sys.info()["user"]=="janus829" | Sys.info()["user"]=="s7m"){
-  source('~/Research/Rhodium/R/setup.R')}
-if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
-
-# Load conflict country year data
-setwd(pathData)
-load('fullData.rda')
-load('combinedData.rda')
-modData = fullData
-
-# Gen tikz?
-genTikz=TRUE
-
-# CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
-###################################################################
-# Log transforming DVs
-modData$lngdp_l0 = log(modData$gdp_l0)
-modData$lngdp = log(modData$gdp)
-modData$lngdpGr_l0 = (modData$lngdp_l0-modData$lngdp)/modData$lngdp_l0
-modData$lngdpGr_l0 = modData$gdpGr_l0
-
-# Transformations for other controls
-modData$lngdpCap = log(modData$gdpCap)
-modData$lninflation_l1 = logTrans(modData$inflation_l1)
-modData$democ = as.numeric(modData$polity2>=6)
-modData$polity2 = modData$polity2 + 11
-
-# Transformations for conflict variables
-modData$lnminDist.min <- log(modData$minDist.min+1)
-modData$lnminDist.min[is.na(modData$lnminDist.min)] <- 0
-modData$lncapDist.min <- log(modData$capDist.min+1)
-modData$lncapDist.min[is.na(modData$lncapDist.min)] <- 0
-modData$lnminDist.mean <- log(modData$minDist.mean+1)
-modData$lncapDist.mean <- log(modData$capDist.mean+1)
-modData$lnminDistACLED.min <- log(modData$minDistACLED.min+1)
-modData$lnminDistACLED.mean <- log(modData$minDistACLED.mean+1)
-modData$lncapDistACLED.min <- log(modData$acledCapDist.min+1)
-modData$lncapDistACLED.mean <- log(modData$acledCapDist.mean+1)
-modData$Int.max <- modData$Int.max-1
-
-###################################################################
-
-## MODELS FOR GDP GROWTH (ANNUAL %)
-###################################################################
-
-# Full model
[…]

### 2015-11-06 R/Analysis/revChecksStageTwo.R

@@ -1,0 +1,114 @@
+if(Sys.info()["user"]=="janus829" | Sys.info()["user"]=="s7m"){
+  source('~/Research/Rhodium/R/setup.R')}
+if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
+
+# Load conflict country year data
+setwd(pathData)
+load('fullData.rda')
+load('combinedData.rda')
+modData = fullData
+
+# Gen tikz?
+genTikz=TRUE
+
+# CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
+###################################################################
+# Log transforming DVs
+modData$lngdp_l0 = log(modData$gdp_l0)
+modData$lngdp = log(modData$gdp)
+modData$lngdpGr_l0 = (modData$lngdp_l0-modData$lngdp)/modData$lngdp_l0
+modData$lngdpGr_l0 = modData$gdpGr_l0
+
+# Transformations for other controls
+modData$lngdpCap = log(modData$gdpCap)
+modData$lninflation_l1 = logTrans(modData$inflation_l1)
+modData$democ = as.numeric(modData$polity2>=6)
+modData$polity2 = modData$polity2 + 11
+
+# Transformations for conflict variables
+modData$lnminDist.min <- log(modData$minDist.min+1)
+modData$lnminDist.min[is.na(modData$lnminDist.min)] <- 0
+modData$lncapDist.min <- log(modData$capDist.min+1)
+modData$lncapDist.min[is.na(modData$lncapDist.min)] <- 0
+modData$lnminDist.mean <- log(modData$minDist.mean+1)
+modData$lncapDist.mean <- log(modData$capDist.mean+1)
+modData$lnminDistACLED.min <- log(modData$minDistACLED.min+1)
+modData$lnminDistACLED.mean <- log(modData$minDistACLED.mean+1)
+modData$lncapDistACLED.min <- log(modData$acledCapDist.min+1)
+modData$lncapDistACLED.mean <- log(modData$acledCapDist.mean+1)
+modData$Int.max <- modData$Int.max-1
+
+###################################################################
+
+## MODELS FOR GDP GROWTH (ANNUAL %)
+###################################################################
+
+###################################################################
+# Full model
+regData <- modData[,c("gdpGr_l0","civwar","lnminDist.min","lncapDist.min","ccode","upperincome","lninflation_l1","polity2","resourceGDP","gdpGr.mean_l0",'year')]
+regData <- regData[complete.cases(regData),]
+
[…]

### 2015-11-06 R/Analysis/modelByPiece.R
add picewise models

@@ -44,7 +44,7 @@ cntrls = c(
   'upperincome', 'lninflation_l1',  'polity2', 'resourceGDP',  'gdpGr.mean_l0')
 
 # Run dist models in pieces
-library(magrittr)
+loadPkg('magrittr')
 mod1Any = modForm(ivs=c(kivs[1]), type='none') %>% lm(., data=modData)
 mod2Any = modForm(ivs=c(kivs[1], cntrls), type='none') %>% lm(., data=modData)
 mod3Any = modForm(ivs=c(kivs[1], cntrls), type='random', id=c('ccode')) %>% lmer(., data=modData)
@@ -60,7 +60,7 @@ mod5Cap = modForm(ivs=c(kivs[2], cntrls), type='random', id=c('ccode', 'year')) 
 
 ###################################################################
 # Regression Tables
-library(stargazer)
+loadPkg('stargazer')
 # Tabular depictions for PRIO city models
 stargazer(mod1Any, mod2Any, mod3Any, mod4Any, mod5Any)
 

### 2015-11-06 R/Analysis/revChecksStageTwo.R

@@ -37,31 +37,57 @@ modData$lnminDistACLED.mean <- log(modData$minDistACLED.mean+1)
 modData$lncapDistACLED.min <- log(modData$acledCapDist.min+1)
 modData$lncapDistACLED.mean <- log(modData$acledCapDist.mean+1)
 modData$Int.max <- modData$Int.max-1
-
 ###################################################################
 
 ## MODELS FOR GDP GROWTH (ANNUAL %)
 ###################################################################
 
 ###################################################################
-# Full model
+# Full model piecewise
 regData <- modData[,c("gdpGr_l0","civwar","lnminDist.min","lncapDist.min","ccode","upperincome","lninflation_l1","polity2","resourceGDP","gdpGr.mean_l0",'year')]
 regData <- regData[complete.cases(regData),]
 
 loadPkg('plm')
-minDistFE = plm(
-	gdpGr_l0 ~ civwar + lnminDist.min + 
+min1 = lm(
+	gdpGr_l0 ~ civwar + lnminDist.min, 
+	data=regData)
+min2 = lm(
+	gdpGr_l0 ~ civwar + lnminDist.min +
+	lninflation_l1 + polity2 + resourceGDP + gdpGr.mean_l0, 
+	data=regData)
+min3 = plm(
+	gdpGr_l0 ~ civwar + lnminDist.min +
 	lninflation_l1 + polity2 + resourceGDP + gdpGr.mean_l0, 
 	data=regData, model='within', effect='individual', index=c('ccode','year'))
-
-capDistFE = plm(
-	gdpGr_l0 ~ civwar + lncapDist.min + 
-	lninflation_l1 + polity2 + resourceGDP + gdpGr.mean_l0,
-	data=regData, model='within', effect='individual', index=c('ccode','year'))	
-
+min4 = plm(
+	gdpGr_l0 ~ civwar + lnminDist.min +
+	lninflation_l1 + polity2 + resourceGDP + gdpGr.mean_l0, 
+	data=regData, model='within', effect='twoways', index=c('ccode','year'))
 # Create stargazer tables
 loadPkg('stargazer')
-stargazer(minDistFE, capDistFE)
+stargazer(min1, min2, min3, min4)
+# Number of countries
+length(unique(regData$ccode))
+
+loadPkg('plm')
+cap1 = lm(
+	gdpGr_l0 ~ civwar + lncapDist.min, 
+	data=modData)
+cap2 = lm(
[…]

### 2015-11-06 LaTeX/Revision2/response.tex
add picewise models
incorp updated tables to rev letter and new appendix item

--- 2015-11-06 LaTeX/Revision2/response.tex
@@
-\section*{Reviewer: 2}
+\section*{Reviewer}
 
@@
 
-\textcolor{blue}{\emph{
+\begin{itemize}
+\item \textcolor{blue}{\emph{
 	The specification suggested above is one that we have now incorporated into our paper.
@@
 Further as suggested by the reviewer we estimate the model with fixed effects instead of random effects.
-The results are shown below
+The results are shown below for both our minimum city distance and minimum capital distance variables, see tables \ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE}, respectively.
+In line with the expectation the reviewer suggested the effect of $\beta_{2}$ is positive across each specification.
+We have included an appendix item into the paper describing these results.
 }} 
+\item City models
+\input{cityFullPiecewiseFE.tex}
+\item Capital city models
+\input{capFullPiecewiseFE.tex}
+\end{itemize}
+
+\newpage
+\item The authors have to consider the country’s size. The distance has to be weighted by the country size. It cannot be an argument to rule out the possibility to use country fixed effects. \\
+
+\begin{itemize}
+\item \textcolor{blue}{\emph{
+	We reran the analysis weighting both of our conflict distance variables by area and the results again hold. We do not include them in the paper but show the results below. 
+}}
+\input{distWeightArea.tex}
+\end{itemize}
+
+\item The sample includes the 1997 Asian crisis and the 2008 financial crisis.
+The authors control for the average GDP growth across all countries.
+The better way to control for time-invariant common shocks is the inclusion of year fixed effects.
+\\
+
+\begin{itemize}
+\item \textcolor{blue}{\emph{
+	We run an alternative model using year fixed effects instead of a lagged GDP growth measure. Results are shown below are findings still hold.
+}}
+\input{cntryTimeFE.tex}
+\end{itemize}
 
@@
 \textcolor{blue}{\emph{
-	stuff
-}}
-
-\item The authors have to consider the country’s size. The distance has to be weighted by the country size. It cannot be an argument to rule out the possibility to use country fixed effects. \\
-
-\textcolor{blue}{\emph{
-	stuff
+	We provide this distinction in 
+	We reran the models per this specification and have included the results in the appendix.
+In both low intensity and high intensity cases we find that the distance variables remain significant and in the hypothesized direction.
 }}
@@
 \textcolor{blue}{\emph{
-	stuff
-}}
-
-\item The sample includes the 1997 Asian crisis and the 2008 financial crisis.
-The authors control for the average GDP growth across all countries.
-The better way to control for time-invariant common shocks is the inclusion of year fixed effects.
-\\
-
-\textcolor{blue}{\emph{
-	stuff
+	Removing this variable has no effect on our analysis. We do not include this extra check in the paper but results are available upon request.
 }}
@@
 \textcolor{blue}{\emph{
-	stuff
+	We don't understand this point.
 }}
@@
 \textcolor{blue}{\emph{
-	stuff
+	We have replaced this table per your suggestion. 
 }}

### 2015-11-06 LaTeX/Revision2/reviseLetter2.tex
create new appendix tables
incorp updated tables to rev letter and new appendix item

@@
 
+% -------------------- customizations -------------------- %
+
+% references to graphics
+\makeatletter
+\def\input@path{{/Users/janus829/Dropbox/Research/Rhodium/Graphics/}, {/Users/Ben/Dropbox/Rhodium/Graphics/}, {/Users/s7m/Dropbox/Research/Rhodium/Graphics/}}
+\makeatother
+\graphicspath{{/Users/janus829/Dropbox/Research/Rhodium/Graphics/}, {/Users/Ben/Dropbox/Rhodium/Graphics/}, {/Users/s7m/Dropbox/Research/Rhodium/Graphics/}}
+
+% -------------------------------------------------------- %
+
 \doublespacing
@@
 
-We first would like to thank you for the opportunity to revise and resubmit our manuscript once again.
+Thank you for the opportunity to revise and resubmit our manuscript once again.
 We have incorporated each of the comments made by R2 into the revised manuscript.

### 2015-11-06 R/Analysis/revChecksStageTwo.R

@@ -1,3 +1,5 @@
+###################################################################
+# Load setup
 if(Sys.info()["user"]=="janus829" | Sys.info()["user"]=="s7m"){
   source('~/Research/Rhodium/R/setup.R')}
 if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
@@ -7,12 +9,10 @@ setwd(pathData)
 load('fullData.rda')
 load('combinedData.rda')
 modData = fullData
-
-# Gen tikz?
-genTikz=TRUE
-
-# CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
 ###################################################################
+
+###################################################################
+# CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
 # Log transforming DVs
 modData$lngdp_l0 = log(modData$gdp_l0)
 modData$lngdp = log(modData$gdp)
@@ -39,14 +39,12 @@ modData$lncapDistACLED.mean <- log(modData$acledCapDist.mean+1)
 modData$Int.max <- modData$Int.max-1
 ###################################################################
 
-## MODELS FOR GDP GROWTH (ANNUAL %)
-###################################################################
-
 ###################################################################
 # Full model piecewise
 regData <- modData[,c("gdpGr_l0","civwar","lnminDist.min","lncapDist.min","ccode","upperincome","lninflation_l1","polity2","resourceGDP","gdpGr.mean_l0",'year')]
 regData <- regData[complete.cases(regData),]
 
+# Run first for any city distance
 loadPkg('plm')
 min1 = lm(
 	gdpGr_l0 ~ civwar + lnminDist.min, 
@@ -61,7 +59,7 @@ min3 = plm(
 	data=regData, model='within', effect='individual', index=c('ccode','year'))
 min4 = plm(
 	gdpGr_l0 ~ civwar + lnminDist.min +
-	lninflation_l1 + polity2 + resourceGDP + gdpGr.mean_l0, 
+	lninflation_l1 + polity2 + resourceGDP, 
 	data=regData, model='within', effect='twoways', index=c('ccode','year'))
 # Create stargazer tables
 loadPkg('stargazer')
@@ -69,10 +67,10 @@ stargazer(min1, min2, min3, min4)
 # Number of countries
 length(unique(regData$ccode))
 
[…]

### 2015-11-09 LaTeX/RhodiumEmp.tex
Added footnote on lagged variables

@@
 The rest of the independent variables are similar to the model specified in the previous section.
-Specifically, we include: whether or not the country is classified as upper income, the lagged version of inflation, the lagged version of polity, the lagged version of resource rents as a proportion of GDP, and the average GDP growth across all countries in the world.
+Specifically, we include: whether or not the country is classified as upper income, the lagged version of inflation, the lagged version of polity, the lagged version of resource rents as a proportion of GDP, and the average GDP growth across all countries in the world.\footnote{We have chosen to lag certain independent variables, including civil war variables, due to the understanding that aggregate economic statistics are naturally delayed in their reflection of real world events.
+Lagged independent variables are common in the econometrics literature.
+In our case, lagging the civil war-related terms guarantees a temporal ordering of conflict followed by the GDP growth estimate so we can discount the possibility that our measures of conflict reflect events that happened near or at the end of the measurement period of the economic variables.
+If our assumption is incorrect, we anticipate that this will negatively impact our findings by moderating the effect of conflict on GDP growth.
+Indeed, previous work accords with this notion of a temporal lag of civil war's effect on economic performance.
+For example, \citet{collier:1999} estimates the effect of ``months since civil war'' on economic performance in addition to a contemporaneous effect of civil war on economic performance.
+The contemporaneous effect, in that case, is the result of a decade average of both variables that is not applicable to our country-year panel.
+The ``months since civil war'' is a generalization of our one year lagged parameterization.}
 

### 2015-11-10 LaTeX/RhodiumEmp.tex
Removed "Random is preferred to fixed effects..."

@@
 
+%A random effects specification is preferred to using fixed effects here as we are not interested in estimating the change in GDP within units over time; rather our purpose is to explain variation between units.
+However,
 To estimate variation in growth rates, we use a random effects model clustered on countries.
-A random effects specification is preferred to using fixed effects here as we are not interested in estimating the change in GDP within units over time; rather our purpose is to explain variation between units.
-However, to ensure that it is statistically justifiable to make this choice we run a Hausman specification test \citep{greene:2008}.
+To ensure that it is statistically justifiable to make this choice we run a Hausman specification test \citep{greene:2008}.
 For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at both the 90 and 95\% confidence intervals, which provides at least some initial evidence that we are justified in our choice.

### 2015-11-10 LaTeX/RhodiumAppendix.tex
fixed typos and stuff
final cleanups
incorp updated tables to rev letter and new appendix item
FE appendix blurb and footnote.

@@
+\newpage
 \section{Appendix}
@@
 \input{baseline.tex}
+\FloatBarrier
+\newpage
 
@@
 \FloatBarrier
-\nepage
+\newpage
 
@@
 \input{modelHiLoIntensity.tex}
+\FloatBarrier
+
+\newpage
+\subsection{Full Panel Fixed Effects Analysis}
+
+While we contend that random effects are preferred to fixed effects for the reasons outlined in the body of the paper, we have nonetheless repeated our analysis using fixed effects.
+The results are presented in Tables~\ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE}.
+These analyses are performed on the full panel of data and therefore are missing conflict-specific covariates that are unavailable for countries not experiencing civil war.
+
+City models
+\input{cityFullPiecewiseFE.tex}
+\FloatBarrier
+
+Capital models
+\input{capFullPiecewiseFE.tex}
 \FloatBarrier
@@
 \FloatBarrier
+\newpage

### 2015-11-10 LaTeX/RhodiumEmp.tex
FE appendix blurb and footnote.

@@
 To estimate variation in growth rates, we use a random effects model clustered on countries.
-To ensure that it is statistically justifiable to make this choice we run a Hausman specification test \citep{greene:2008}.
-For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at both the 90 and 95\% confidence intervals, which provides at least some initial evidence that we are justified in our choice.
+To ensure that it is statistically justifiable to make this choice we run a Hausman specification test \citep{greene:2008}.\footnote{Fixed effects models can be found in the Appendix, Tables~\ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE}.} For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at both the 90 and 95\% confidence intervals, which provides at least some initial evidence that we are justified in our choice.
 However, as \citet{clark:linzer:2015} note, the Hausman test should not be the sole determinant for choosing between fixed or random effects.

### 2015-11-26 LaTeX/Revision2/response.tex
almost done with new letter

--- 2015-11-06 LaTeX/Revision2/response.tex
@@
-\section*{Reviewer: 2}
+\section*{Reviewer}
 
 \begin{enumerate}
-\item Empirical Strategy \& Sample: 
+\item Empirical Strategy \& Sample: \textcolor{blue}{\emph{The reviewer reiterates a number of points regarding our empirical strategy.
+We have bundled these comments, each shown below, into this single section so that we can address them in a holistic manner.
+The main concerns the reviewer raises are with the issue of estimating on a full sample versus conflict-year sample, use of random effects, and the presentation of the results.}} \\
 \begin{enumerate}
-	\item   Empirical strategy. As I have already mentioned in my first report, the empirical strategy is still a
-	major issue. I’m not convinced by the use of random fixed effects. At least, I would to like see a
+	\item   Empirical strategy.
+As I have already mentioned in my first report, the empirical strategy is still a major issue.
+I’m not convinced by the use of random fixed effects.
+At least, I would to like see a
 	table following the road map I gave in my previous comments. Last, I do not understand the last
@@
 \\
-\end{enumerate}
-
-\textcolor{blue}{\emph{
-	The specification suggested above is one that we have now incorporated into our paper.
-We adopt the following specification suggested by the reviewer: $GDP_{it} = \beta_{1}Conflict_{it} + \beta_{2}Distance_{it}+\ldots+\zeta_{it}$.
-where $Distance_{it}=0$ when $Conflict_{it}=0$ and $Distance_{it}>0$ when $Conflict_{it}=1$.
-Further as suggested by the reviewer we estimate the model with fixed effects instead of random effects.
-The results are shown below
-}}
-
-\item Data. Considering the raw dataset on conflict, US and Spain were in war (Figure 3). PRIO defines different nature of conflicts. I would like to see results with this distinctions. \\
-
-\textcolor{blue}{\emph{
-	stuff
-}}
-
-\item The authors have to consider the country’s size. The distance has to be weighted by the country size. It cannot be an argument to rule out the possibility to use country fixed effects. \\
-
-\textcolor{blue}{\emph{
-	stuff
-}}
-
-\item The sub-section 3.3 on the descriptive cases is a good candidate for the (online) appendix. \\
-
-\textcolor{blue}{\emph{
-	stuff
-}}
-
-\item  The authors include binary indicators for whether the country is classified as upper income by the World Bank. It is highly endogeneous to the main variable of interest. \\
-
-\textcolor{blue}{\emph{
-	stuff
-}}
 
@@
 
+	\item  The authors include binary indicators for whether the country is classified as upper income by the World Bank. It is highly endogeneous to the main variable of interest. \\
+
+	\item Table 2. The authors mention random fixed effects with country, year or country + year. I do not understand what they mean. \\	
+\end{enumerate}
+
+\begin{itemize}
+\item \textcolor{blue}{\emph{
+	We adopt the following specification suggested by the reviewer: $GDP_{it} = \beta_{1}Conflict_{it} + \beta_{2}Distance_{it}+\ldots+\zeta_{it}$.
+where $Distance_{it}=0$ when $Conflict_{it}=0$ and $Distance_{it}>0$ when $Conflict_{it}=1$.
+Additionally, as suggested by the reviewer, we estimate the model with fixed instead of random effects.
+The results are shown below for both our minimum city distance and minimum capital distance variables, see tables \ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE}, respectively.
+In line with the expectation the reviewer suggested the effect of $\beta_{2}$ is positive across each specification.
+We have included an appendix item into the paper describing these results.
+}} \\
+
+\item \textcolor{blue}{\emph{
+	To deal with the reviewer's assertion that year fixed effects are more appropriate than a average GDP growth measure, in the last column of both tables \ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE} we exclude the average GDP growth measure and instead use year fixed effects.
+The results are still consistent with our hypotheses for both the minimum city and capital distance variables.
+}} \\
+
+\item \textcolor{blue}{\emph{
+	The reviewer also raises concerns about the endogeneity of the upper income variable, we exclude it in each of the fixed effects specifications here since it is time-invariant, and as you can see the results remain consistent with our hypotheses.
+}} \\
+
+\item \textcolor{blue}{\emph{
+	We had originally included results broken down by different hierarchies of effects according to earlier reviewer comments.
+Since those were unclear we redo the analysis shown in tables \ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE} by first just estimating the effects of our conflict variables, then we add controls, next we add country fixed effects, and last we include country+year fixed effects.
+}} \\
+
+\end{itemize}
+
+\input{cityFullPiecewiseFE.tex}
+\input{capFullPiecewiseFE.tex}
+\FloatBarrier
+
+\newpage
+\item The authors have to consider the country’s size. The distance has to be weighted by the country size. It cannot be an argument to rule out the possibility to use country fixed effects. \\
+
+\begin{itemize}
+\item \textcolor{blue}{\emph{
+	We reran the analysis weighting both of our conflict distance variables by area and the results remain consistent with our hypotheses.
+We do not include this set of findings in the appendix of our paper but would be happy to do so.
+}} \\
+\input{distWeightArea.tex}
+\end{itemize}
+\FloatBarrier
+
+\newpage
+\item Data. Considering the raw dataset on conflict, US and Spain were in war (Figure 3). PRIO defines different nature of conflicts. I would like to see results with this distinctions. \\
+
 \textcolor{blue}{\emph{
-	stuff
-}}
+	The reviewer comments from the first round had also suggested breaking down the results by different natures of conflict.
+To account for this, we re-did our primary models estimating the effect of distance on growth, but restricting to the civil conflicts coded as wars and then a separate model for civil conflicts coded as low intensity events.
+In both low intensity and high intensity cases we find that the conflict distance variables remain significant and in the expected direction, but the $\beta$ estimate of our distance variables is noticeably higher when using high intensity versus low intensity civil conflict cases.
+The results are presented in Table~\ref{tab:modHiLoIntensity} below and are included as an appendix item.
+}} \\
+\input{modelHiLoIntensity.tex}
+\FloatBarrier
 
@@
 \textcolor{blue}{\emph{
-	stuff
-}}
+	Lagged independent variables are common in the econometrics literature.
+In our case, lagging the civil war-related terms guarantees a temporal ordering of conflict followed by the GDP growth estimate so we can discount the possibility that our measures of conflict reflect events that happened near or at the end of the measurement period of the economic variables.
+If our assumption is incorrect, we anticipate that this will negatively impact our findings by moderating the effect of conflict on GDP growth.
+Indeed, previous work accords with this notion of a temporal lag of civil war's effect on economic performance.
+For example, Collier (1999) estimates the effect of ``months since civil war'' on economic performance in addition to a contemporaneous effect of civil war on economic performance.
+The contemporaneous effect, in that case, is the result of a decade average of both variables that is not applicable to our country-year panel.
+The ``months since civil war'' is a generalization of our one year lagged parameterization.
+}} \\
 
-\item Table 2. The authors mention random fixed effects with country, year or country + year. I do not understand what they mean. \\
+\item The sub-section 3.3 on the descriptive cases is a good candidate for the (online) appendix. \\
 
 \textcolor{blue}{\emph{
-	stuff
-}}
+	For now since we are still under the word limit, we would prefer to keep those descriptive cases in as they help the reader to understand our theory in the context of a few concrete examples. 
+}} \\
 
@@
 \textcolor{blue}{\emph{
-	stuff
-}}
+	We have added additional information in the captions for each of the tables.
+}} \\
 
@@
 \textcolor{blue}{\emph{
-	stuff
-}}
+	We have checked to make sure that all references have been made available.
+}} \\
 

### 2015-11-27 LaTeX/Revision2/response.tex
new version of manuscript and letter, ready to send

@@
 	We had originally included results broken down by different hierarchies of effects according to earlier reviewer comments.
-Since those were unclear we redo the analysis shown in tables \ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE} by first just estimating the effects of our conflict variables, then we add controls, next we add country fixed effects, and last we include country+year fixed effects.
+Since those were unclear we redo the analysis and present the results below in tables \ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE}.
+These analyses are performed on the full panel of data and therefore are missing conflict-specific covariates that are unavailable for countries not experiencing civil war.
+In the first column, we show the results of our baseline model without any fixed effects, next we add fixed effects for countries, and last we include country+year fixed effects.
 }} \\
@@
 \textcolor{blue}{\emph{
-	For now since we are still under the word limit, we would prefer to keep those descriptive cases in as they help the reader to understand our theory in the context of a few concrete examples. 
+	For now we would prefer to keep those descriptive cases in as they help the reader to understand our theory in the context of a few concrete examples.
+However, given word limits we would be happy to move those items to an appendix as well.
 }} \\

### 2015-11-27 LaTeX/RhodiumAppendix.tex
new version of manuscript and letter, ready to send

@@
 
-\subsection{Baseline Effect of Civil Conflict on Growth}
-
-In Table \ref{tab:baseline} below, we show the fixed effects regression results for the model in which we utilize a full country year panel in order to define a baseline effect of civil war on economic growth.
-
-\input{baseline.tex}
-\FloatBarrier
-\newpage
-
-\subsection{Conflict Distance Models in Tabular Format}
-
-Here we present the results of our models measuring the effect of conflict distance in a tabular format, results for distance from the capital city are shown in Table \ref{tab:capDistMod} and for any major city in Table \ref{tab:cityDistMod} below.
-The first column in each of the tables below is a simple linear model regressing the conflict distance parameter on GDP Growth, in the second we add our controls, in the third we include random effects, varying intercepts, for country, in the fourth random effects for year, and in the last random effects for both country and year.
-
-\input{capDistRegTable.tex}
-
-\input{cityDistRegTable.tex}
-
-\FloatBarrier
-\newpage
-
-\subsection{Estimating Models Separately for High and Low Intensity Conflicts}
-
-Here instead of treating conflict intensity as a control, we re-do our primary models estimating the effect of distance on growth, but restricting to the civil conflicts coded as wars and then a separate model for civil conflicts coded as low intensity events.
-In both low intensity and high intensity cases we find that the conflict distance variables remain significant and in the expected direction, but the $\beta$ estimate of our distance variables is noticeably higher when using high intensity versus low intensity civil conflict cases.
-The results are presented in Table~\ref{tab:modHiLoIntensity} below.
-
-\input{modelHiLoIntensity.tex}
-\FloatBarrier
-
-\newpage
 \subsection{Full Panel Fixed Effects Analysis}
 
-While we contend that random effects are preferred to fixed effects for the reasons outlined in the body of the paper, we have nonetheless repeated our analysis using fixed effects.
+While we contend that random effects are preferred to fixed effects for the reasons outlined in the body of the paper, we have nonetheless repeated our analysis using fixed effects on a full country-year panel dataset.
 The results are presented in Tables~\ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE}.
 These analyses are performed on the full panel of data and therefore are missing conflict-specific covariates that are unavailable for countries not experiencing civil war.
+When utilizing this alternative approach we still find strong support for the hypothesis that countries experiencing conflict that is more proximate to capital or major cities are more likely to see significant reductions in GDP growth than conflicts.
 
-City models
 \input{cityFullPiecewiseFE.tex}
@@
 
-Capital models
 \input{capFullPiecewiseFE.tex}
@@
 \newpage
+
+\subsection{Estimating Models Separately for High and Low Intensity Conflicts}
+
+Here instead of treating conflict intensity as a control, we re-do our primary random effect regression models estimating the effect of distance on growth, but restricting to the civil conflicts coded as wars and then a separate model for civil conflicts coded as low intensity events.
+In both low intensity and high intensity cases we find that the conflict distance variables remain significant and in the expected direction, and the $\beta$ estimate of our distance variables is noticeably higher when using high intensity versus low intensity civil conflict cases.
+The results are presented in Table~\ref{tab:modHiLoIntensity} below.
+
+\input{modelHiLoIntensity.tex}
+\FloatBarrier
+\newpage
+
+\subsection{Baseline Effect of Civil Conflict on Growth}
+
+In Table \ref{tab:baseline} below, we show the fixed effects regression results for the model in which we utilize a full country year panel in order to define a baseline effect of civil war on economic growth.
+
+\input{baseline.tex}
+\FloatBarrier
+\newpage
+
+\subsection{Conflict Distance Models in Tabular Format}
+
+Here we present the results of our models measuring the effect of conflict distance in a tabular format, results for distance from the capital city are shown in the first column of Table \ref{tab:capminDistMod} and for any major city in the second column.
+
+\input{capminDistRegMain.tex}
+
+\FloatBarrier
+\newpage

### 2015-11-27 LaTeX/RhodiumEmp.tex
new version of manuscript and letter, ready to send

@@
 
-Another reason we choose to employ a random effects framework is because of our concerns with the unchanging and time invariant nature of where conflict is taking place relative to major urban centers.
+% Another reason we choose to employ a random effects framework is because of our concerns with the unchanging and time invariant nature of where conflict is taking place relative to major urban centers.
 In Thailand, for example, the distance between conflict and urban centers in our dataset just ranges from approximately 790 to 810 kilometers indicating that conflicts are simply isolated to a specific part of the country.

### 2015-11-27 R/Analysis/modelByPiece.R

@@ -67,6 +67,9 @@ stargazer(mod1Any, mod2Any, mod3Any, mod4Any, mod5Any)
 # Tabular depictions for ACLED city models
 stargazer(mod1Cap, mod2Cap, mod3Cap, mod4Cap, mod5Cap)
 
+# Tabular depictions for combo city models
+stargazer(mod3Cap, mod3Any)
+
 # Count number of observations
 lapply(list(mod1Any, mod2Any, mod3Any, mod4Any, mod5Any), function(x) length(residuals(x)))
 # Count number of countries

### 2015-11-28 LaTeX/Revision2/response.tex
minor edits to letter, still need to recompile

@@
 \begin{enumerate}
-\item Empirical Strategy \& Sample: \textcolor{blue}{\emph{The reviewer reiterates a number of points regarding our empirical strategy.
+\item Empirical Strategy \& Sample: \textcolor{blue}{\emph{The reviewer discusses a number of points regarding our empirical strategy.
 We have bundled these comments, each shown below, into this single section so that we can address them in a holistic manner.
@@
 I’m not convinced by the use of random fixed effects.
-At least, I would to like see a
-	table following the road map I gave in my previous comments. Last, I do not understand the last
-	argument about the weak time-variation of the distance to conflict. \\
+At least, I would to like see a table following the road map I gave in my previous comments.
+Last, I do not understand the last argument about the weak time-variation of the distance to conflict.
+\\
 
-	\item Sample. I am not sure about the accuracy of the answer to my third point. I asked for the use of a
-	full sample of countries.
+	\item Sample.
+I am not sure about the accuracy of the answer to my third point.
+I asked for the use of a full sample of countries.
 I don’t see a problem to estimate the following equation: $GDP_{it} = \beta_{1}Conflict_{it} + \beta_{2}Distance_{it}+\ldots+\zeta_{it}$.
@@
 In line with the expectation the reviewer suggested the effect of $\beta_{2}$ is positive across each specification.
-We have included an appendix item into the paper describing these results.
+We have included an appendix item into the paper describing these results and have inserted a footnote within the empirical section referencing this additional analysis.
 }} \\
@@
 	We had originally included results broken down by different hierarchies of effects according to earlier reviewer comments.
-Since those were unclear we redo the analysis and present the results below in tables \ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE}.
+Since those were unclear we redid the analysis according to the specifications suggested by the reviewer and present the results below in tables \ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE}.
 These analyses are performed on the full panel of data and therefore are missing conflict-specific covariates that are unavailable for countries not experiencing civil war.

### 2015-11-28 LaTeX/Revision2/reviseLetter2.tex
minor edits to letter, still need to recompile

@@
 
-Thank you for the opportunity to revise and resubmit our manuscript once again.
-We have incorporated each of the comments made by R2 into the revised manuscript.
+Thank you for the opportunity to revise and resubmit our manuscript.
+We have addressed the remaining comments made by R2 and have made the relevant modifications to the revised manuscript.
 The revision memo is organized in response to the bulleted set of questions that were posted with the decision letter.
@@
 
-We hope you agree that the manuscript has greatly improved through this helpful process and we are looking forward to your response.\\ [1ex]
+We are looking forward to your response.\\ [1ex]
 

### 2015-11-28 LaTeX/Revision2/response.tex
more cleanup, need to add %delta gdp in tables, recompile

@@
 \item \textcolor{blue}{\emph{
-	We adopt the following specification suggested by the reviewer: $GDP_{it} = \beta_{1}Conflict_{it} + \beta_{2}Distance_{it}+\ldots+\zeta_{it}$.
-where $Distance_{it}=0$ when $Conflict_{it}=0$ and $Distance_{it}>0$ when $Conflict_{it}=1$.
+	We adopt the following specification suggested by the reviewer: $\% \delta GDP_{i,t} = \beta_{1}Conflict_{i,t-1} + \beta_{2}Distance_{i,t-1}+\ldots+\zeta_{i,t-1}$, where $Distance_{i,t-1}=0$ when $Conflict_{i,t-1}=0$ and $Distance_{i,t-1}>0$ when $Conflict_{i,t-1}=1$.
 Additionally, as suggested by the reviewer, we estimate the model with fixed instead of random effects.

### 2015-11-28 LaTeX/RhodiumAppendix.tex
changes in manuscript

@@
 
-While we contend that random effects are preferred to fixed effects for the reasons outlined in the body of the paper, we have nonetheless repeated our analysis using fixed effects on a full country-year panel dataset.
+Here we broaden the random effect conflict-year analysis presented in the paper to a country-year analysis in which we employ a fixed effects framework.
+Specifically, we estimate the following equation: $\% \delta GDP_{i,t} = \beta_{1}Conflict_{i,t-1} + \beta_{2}Distance_{i,t-1}+\ldots+\zeta_{i,t-1}$, where $Distance_{i,t-1}=0$ when $Conflict_{i,t-1}=0$ and $Distance_{i,t-1}>0$ when $Conflict_{i,t-1}=1$.
+The $\zeta_{i,t-1}$ term represents our bundle of control variables.
+This specification provides one way to consider the full sample, control for the presence of armed conflict, and test our key hypothesis regarding the role of conflict proximity to major urban centers.
+In this specification, we expect the estimate of $\beta_{2}$ to be positive.
+
 The results are presented in Tables~\ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE}.
-These analyses are performed on the full panel of data and therefore are missing conflict-specific covariates that are unavailable for countries not experiencing civil war.
-When utilizing this alternative approach we still find strong support for the hypothesis that countries experiencing conflict that is more proximate to capital or major cities are more likely to see significant reductions in GDP growth than conflicts.
+In the first column of these tables, we run a pooled country-year analysis in which we include our key variable of interest, distance to conflict, and controls.
+In the second column, we incorporate country fixed effects and in the last we utilize both country and year fixed effects.
+When adding year fixed effects we remove our global average GDP growth measure.
+Since these analyses are performed on the full panel of data we have to exclude the conflict-specific covariates from the PRIO dataset as they are undefined for countries not experiencing civil war.
+
+When utilizing this alternative approach we still find strong support for the hypotheses that countries experiencing conflict more proximate to capital or major cities are more likely to see significant reductions in GDP growth than conflicts that are farther away from these economically vital centers.
 
@@
 The results are presented in Table~\ref{tab:acledRegResults} below.
+
+When utilizing this alternative dataset we again find significant support for the argument that conflicts more proximate to urban centers have a greater adverse effect on economic growth than those farther away.
+Additionally, if we switched to a fixed effects framework, such as the one described in the previous appendix section, we still find significant support for the hypotheses laid out in our paper.
 

### 2015-11-28 LaTeX/Revision2/response.tex
new version submitted to jcr

--- 2015-11-28 LaTeX/Revision2/response.tex
@@
 \begin{enumerate}
-\item Empirical Strategy \& Sample: \textcolor{blue}{\emph{The reviewer discusses a number of points regarding our empirical strategy.
+\item Empirical Strategy \& Sample: \textcolor{blue}{\emph{The reviewer discusses a number of important points regarding our empirical strategy.
 We have bundled these comments, each shown below, into this single section so that we can address them in a holistic manner.
-The main concerns the reviewer raises are with the issue of estimating on a full sample versus conflict-year sample, use of random effects, and the presentation of the results.}} \\
+The key concerns the reviewer raises are with the issue of estimating on a full sample versus conflict-year sample and use of random effects.}} \\
 \begin{enumerate}
@@
 \item \textcolor{blue}{\emph{
-	We adopt the following specification suggested by the reviewer: $GDP_{it} = \beta_{1}Conflict_{it} + \beta_{2}Distance_{it}+\ldots+\zeta_{it}$.
-where $Distance_{it}=0$ when $Conflict_{it}=0$ and $Distance_{it}>0$ when $Conflict_{it}=1$.
+	Per the reviewer's suggestion, we utilize a full country-year panel and adopt the following empirical specification: $\% \Delta GDP_{i,t} = \beta_{1}Conflict_{i,t-1} + \beta_{2}Distance_{i,t-1}+\ldots+\zeta_{i,t-1}$, where $Distance_{i,t-1}=0$ when $Conflict_{i,t-1}=0$ and $Distance_{i,t-1}>0$ when $Conflict_{i,t-1}=1$.
 Additionally, as suggested by the reviewer, we estimate the model with fixed instead of random effects.
@@
 In line with the expectation the reviewer suggested the effect of $\beta_{2}$ is positive across each specification.
-We have included an appendix item into the paper describing these results and have inserted a footnote within the empirical section referencing this additional analysis.
+We have included an appendix item into the paper describing these results (see page 30) and have inserted a footnote within the empirical section referencing this additional analysis (see footnote 7 page 20).
 }} \\
@@
 \item \textcolor{blue}{\emph{
-	To deal with the reviewer's assertion that year fixed effects are more appropriate than a average GDP growth measure, in the last column of both tables \ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE} we exclude the average GDP growth measure and instead use year fixed effects.
+	To deal with the reviewer's assertion that year fixed effects are more appropriate than an average GDP growth measure, in the last column of both tables \ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE} we exclude the average GDP growth measure and instead use year fixed effects.
 The results are still consistent with our hypotheses for both the minimum city and capital distance variables.
@@
 In both low intensity and high intensity cases we find that the conflict distance variables remain significant and in the expected direction, but the $\beta$ estimate of our distance variables is noticeably higher when using high intensity versus low intensity civil conflict cases.
-The results are presented in Table~\ref{tab:modHiLoIntensity} below and are included as an appendix item.
+The results are presented in Table~\ref{tab:modHiLoIntensity} below and are included as an appendix item (see end of page 34-36).
 }} \\
@@
 The ``months since civil war'' is a generalization of our one year lagged parameterization.
+We have also inserted a footnote into the text noting our reasoning for employing this lag structure (see footnote 10 page 22).
 }} \\

### 2015-11-28 LaTeX/RhodiumAppendix.tex
new version submitted to jcr

@@
 Here we broaden the random effect conflict-year analysis presented in the paper to a country-year analysis in which we employ a fixed effects framework.
-Specifically, we estimate the following equation: $\% \delta GDP_{i,t} = \beta_{1}Conflict_{i,t-1} + \beta_{2}Distance_{i,t-1}+\ldots+\zeta_{i,t-1}$, where $Distance_{i,t-1}=0$ when $Conflict_{i,t-1}=0$ and $Distance_{i,t-1}>0$ when $Conflict_{i,t-1}=1$.
+Specifically, we estimate the following equation: $\% \Delta GDP_{i,t} = \beta_{1}Conflict_{i,t-1} + \beta_{2}Distance_{i,t-1}+\ldots+\zeta_{i,t-1}$, where $Distance_{i,t-1}=0$ when $Conflict_{i,t-1}=0$ and $Distance_{i,t-1}>0$ when $Conflict_{i,t-1}=1$.
 The $\zeta_{i,t-1}$ term represents our bundle of control variables.

### 2016-01-11 LaTeX/EnemyAtTheGates_MinhasRadford_OnlineAppendix.tex
Added online appendix.

\documentclass[12pt,onesided]{amsart}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% -------------------- defaults -------------------- %
% load lots o' packages

% layout control
\usepackage{geometry}
\geometry{verbose,tmargin=1.25in,bmargin=1.25in,lmargin=1.1in,rmargin=1.1in}
\usepackage[figuresright]{rotating}
\newenvironment{amssidewaysfigure}
  {\begin{sidewaysfigure}\vspace*{.8\textwidth}\begin{minipage}{\textheight}\centering}
  {\end{minipage}\end{sidewaysfigure}}
\usepackage{parallel}
\usepackage{parcolumns}

% math typesetting
\usepackage{array}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}

\usepackage[%
decimalsymbol=.,
digitsep=fullstop
]{siunitx}

% to adapt caption style
\usepackage[font={small},labelfont=bf]{caption}

% references
\usepackage{natbib}
% \usepackage[natbib=true, style=authoryear]{biblatex}
% \bibliography{master.bib}

% footnotes at bottom
\usepackage[bottom]{footmisc}

% to change enumeration symbols begin{enumerate}[(a)]
\usepackage{enumerate}

% to make enumerations and itemizations within paragraphs or
% lines. f.i. begin{inparaenum} for (a) is (b) and (c)
\usepackage{paralist}

% to colorize links in document. See color specification below
\usepackage[x11names]{xcolor}

% load the hyper-references package and set document info
\usepackage[pdftex]{hyperref}

% graphics stuff
\usepackage{subfig}
\usepackage{graphicx}
\usepackage[space]{grffile} % allows us to specify directories that have spaces
\usepackage[section]{placeins} % prevents floats from moving past a \FloatBarrier or section
\usepackage{tikz}

% Spacing
\usepackage[doublespacing]{setspace}

% define clickable links and their colors
\hypersetup{
	unicode=false,          % non-Latin characters in Acrobat's bookmarks
	pdftoolbar=true,        % show Acrobat's toolbar?
	pdfmenubar=true,        % show Acrobat's menu?
	pdffitwindow=false,     % window fit to page when opened
	pdfstartview={FitH},    % fits the width of the page to the window
	pdfnewwindow=true,%
	pdfauthor={Minhas and Radford},%
	pdftitle={Enemy at the Gates},%
	colorlinks,%
	citecolor=black,%
	filecolor=black,%
	linkcolor=black,%
	urlcolor=RoyalBlue4%
	}
% -------------------------------------------------- %

% -------------------- title -------------------- %

\title[Enemy at the Gates]{Enemy at the Gates: Variation in Economic Growth from Civil Conflict}
\date{\today}

\author[Minhas]{Shahryar Minhas}
\address{Shahryar Minhas: Department of Political Science}
\curraddr{Duke University, Durham, NC, 27708, USA}
\email{shahryar.minhas@duke.edu}

\author[Radford]{Benjamin J. Radford}
\address{Benjamin J. Radford: Department of Political Science}
\curraddr{Duke University, Durham, NC, 27708, USA}
\email{benjamin.radford@duke.edu}

% \thanks{We are grateful for comments on earlier versions of this paper received at the 72$^{nd}$ annual Midwest Political Science Association Conference in Chicago, April 2-6 2014. }

% ----------------------------------------------- %

% -------------------- customizations -------------------- %

% easy commands for number propers
\makeatletter
\def\input@path{{/Users/janus829/Dropbox/Research/Rhodium/Graphics/}, {/Users/Ben/Dropbox/Rhodium/Graphics/}, {/Users/s7m/Dropbox/Research/Rhodium/Graphics/}, {C:/Users/Ben/Dropbox/Rhodium/Graphics}}
\makeatother
\graphicspath{{/Users/janus829/Dropbox/Research/Rhodium/Graphics/}, {/Users/Ben/Dropbox/Rhodium/Graphics/}, {/Users/s7m/Dropbox/Research/Rhodium/Graphics/}, {C:/Users/Ben/Dropbox/Rhodium/Graphics/}}

% -------------------------------------------------------- %

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%% DOCUMENT %%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\doublespacing

\begin{document}
% Wordcount: 9814
\maketitle

\begin{abstract}
\singlespacing
\input{Abstract}
\end{abstract}

\newpage
\newpage\setcounter{page}{1}

%%%%% Appendix %%%%%
\input{RhodiumOnlineAppendix}
%%%%%%%%%%%%%%%%%%%%%%

\newpage

% \bibliographystyle{elsarticle-harv} 
\bibliographystyle{jpr}
\bibliography{master.bib}

\end{document}

### 2016-01-11 LaTeX/RhodiumAppendix.tex
Added online appendix.

@@
 \FloatBarrier
-
-\newpage
-\subsection{ACLED Analysis}
-\label{acled}
-
-The Armed Conflict Location and Event Dataset provides an alternative source of information on the subnational spatial distribution of armed conflict \citep{raleigh:linke:etal:2010}.
-This dataset is, at the time of writing, limited to Africa and therefore was not selected for the primary analysis presented in the text.
-It does, however, offer us a valuable opportunity to validate our results.
-Here, we have replicated the primary model described in Section~\ref{empirics}.
-
-In order to match our existing data structure, it was necessary to aggregate the ACLED data to the country-year level.
-We did this by first subsetting ACLED to the years 1989-2008 and then selecting only conflict sites with at least 25 fatalities in each given year.
-The 25 fatalities threshold is intended to mirror the PRIO coding criteria and to prevent very low-fatality events from biasing our estimates of conflict location toward high-population areas.
-Covariates created with PRIO but unavailable in ACLED are omitted.
-The analysis procedure then continues as described in Section~\ref{empirics}: the minimum distance measure is calculated as the natural logarithm of the average distance in kilometers from any conflict site to the nearest major city (or capital).
-The results are presented in Table~\ref{tab:acledRegResults} below.
-
-When utilizing this alternative dataset we again find significant support for the argument that conflicts more proximate to urban centers have a greater adverse effect on economic growth than those farther away.
-Additionally, if we switched to a fixed effects framework, such as the one described in the previous appendix section, we still find significant support for the hypotheses laid out in our paper.
-
-\input{acledModels.tex}
-\FloatBarrier
-\newpage
-
-\subsection{Estimating Models Separately for High and Low Intensity Conflicts}
-
-Here instead of treating conflict intensity as a control, we re-do our primary random effect regression models estimating the effect of distance on growth, but restricting to the civil conflicts coded as wars and then a separate model for civil conflicts coded as low intensity events.
-In both low intensity and high intensity cases we find that the conflict distance variables remain significant and in the expected direction, and the $\beta$ estimate of our distance variables is noticeably higher when using high intensity versus low intensity civil conflict cases.
-The results are presented in Table~\ref{tab:modHiLoIntensity} below.
-
-\input{modelHiLoIntensity.tex}
-\FloatBarrier
-\newpage
-
-\subsection{Baseline Effect of Civil Conflict on Growth}
-
-In Table \ref{tab:baseline} below, we show the fixed effects regression results for the model in which we utilize a full country year panel in order to define a baseline effect of civil war on economic growth.
-
-\input{baseline.tex}
-\FloatBarrier
-\newpage
-
-\subsection{Conflict Distance Models in Tabular Format}
-
-Here we present the results of our models measuring the effect of conflict distance in a tabular format, results for distance from the capital city are shown in the first column of Table \ref{tab:capminDistMod} and for any major city in the second column.
-
-\input{capminDistRegMain.tex}
-
-\FloatBarrier
-\newpage

### 2016-01-11 LaTeX/RhodiumOnlineAppendix.tex
Added online appendix.

\newpage
\section*{Online Appendix}
\label{online_appendix}

\subsection{Illustrative Maps}
\label{maps}

FARC advocates a number of political and economic reforms and chooses targets strategically related to these objectives. Figure \ref{fig:colombiaMap} shows the spatial distribution of violence in Colombia from 1989 to 2008, where Bogot\'{a} is designated by a black diamond and major cities by black triangles. To determine the centroid locations of conflict we use the PRIO conflict site database developed by \citet{hallberg:2012}.

\begin{figure}[ht]
	\centering
	\includegraphics[width=.5\textwidth]{colombiaMap-crop}
	\caption{This map illustrates the geographic distribution of all conflict centroids in Colombia, according to the PRIO Conflict Site Dataset, and major cities from 1989 to 2008.}
	\label{fig:colombiaMap}
\end{figure}

In figure \ref{fig:indiaMap}, we show the geographic distribution of conflict in India from 1989 to 2007 again using the PRIO conflict site database. The story from this map is clearly quite stark from that of Colombia. Whereas in Colombia conflict had come right to the gates of major cities, in India conflict has been primarily confined to the periphery.

\begin{figure}[ht]
	\centering
	\includegraphics[width=.5\textwidth]{indiaMap-crop}
	\caption{This map illustrates the geographic distribution of all conflict centroids in India, according to the PRIO Conflict Site Dataset, and major cities from 1989 to 2007. }
	\label{fig:indiaMap}
\end{figure}

\newpage
\subsection{ACLED Analysis}
\label{acled}

The Armed Conflict Location and Event Dataset provides an alternative source of information on the subnational spatial distribution of armed conflict \citep{raleigh:linke:etal:2010}. This dataset is, at the time of writing, limited to Africa and therefore was not selected for the primary analysis presented in the text. It does, however, offer us a valuable opportunity to validate our results. Here, we have replicated the primary model described in Section~\ref{empirics}.

In order to match our existing data structure, it was necessary to aggregate the ACLED data to the country-year level. We did this by first subsetting ACLED to the years 1989-2008 and then selecting only conflict sites with at least 25 fatalities in each given year. The 25 fatalities threshold is intended to mirror the PRIO coding criteria and to prevent very low-fatality events from biasing our estimates of conflict location toward high-population areas. Covariates created with PRIO but unavailable in ACLED are omitted. The analysis procedure then continues as described in Section~\ref{empirics}: the minimum distance measure is calculated as the natural logarithm of the average distance in kilometers from any conflict site to the nearest major city (or capital). The results are presented in Table~\ref{tab:acledRegResults} below.

When utilizing this alternative dataset we again find significant support for the argument that conflicts more proximate to urban centers have a greater adverse effect on economic growth than those farther away. Additionally, if we switched to a fixed effects framework, such as the one described in the previous appendix section, we still find significant support for the hypotheses laid out in our paper.

\input{acledModels.tex}
\FloatBarrier

\newpage
\subsection{Estimating Models Separately for High and Low Intensity Conflicts}

Here instead of treating conflict intensity as a control, we re-do our primary random effect regression models estimating the effect of distance on growth, but restricting to the civil conflicts coded as wars and then a separate model for civil conflicts coded as low intensity events. In both low intensity and high intensity cases we find that the conflict distance variables remain significant and in the expected direction, and the $\beta$ estimate of our distance variables is noticeably higher when using high intensity versus low intensity civil conflict cases. The results are presented in Table~\ref{tab:modHiLoIntensity} below.

\input{modelHiLoIntensity.tex}
\FloatBarrier

\newpage
\subsection{Baseline Effect of Civil Conflict on Growth}

In Table \ref{tab:baseline} below, we show the fixed effects regression results for the model in which we utilize a full country year panel in order to define a baseline effect of civil war on economic growth.

\input{baseline.tex}
\FloatBarrier

\newpage
\subsection{Conflict Distance Models in Tabular Format}

Here we present the results of our models measuring the effect of conflict distance in a tabular format, results for distance from the capital city are shown in the first column of Table \ref{tab:capminDistMod} and for any major city in the second column.

\input{capminDistRegMain.tex}

\FloatBarrier
\newpage

### 2016-01-11 LaTeX/RhodiumTheory.tex
Added online appendix.

@@
 However, the timing was likely not coincidental.
-FARC advocates a number of political and economic reforms and chooses targets strategically related to these objectives.
-Figure \ref{fig:columbiaMap} shows the spatial distribution of violence in Colombia from 1989 to 2008, where Bogot\'{a} is designated by a black diamond and major cities by black triangles.
-To determine the centroid locations of conflict we use the PRIO conflict site database developed by \citet{hallberg:2012}.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=.5\textwidth]{colombiaMap-crop}
-	\caption{This map illustrates the geographic distribution of all conflict centroids in Colombia, according to the PRIO Conflict Site Dataset, and major cities from 1989 to 2008.}
-	\label{fig:columbiaMap}
-\end{figure}
 
@@
 \begin{quote}
-	FARC's strategy and [beliefs have] always been to make economic pressure on both, multinational companies and the Colombian government.
+	FARC's strategy and [beliefs have] always been to make economic pressure on both multinational companies and the Colombian government.
 This has been done by attacking oil and natural gas infrastructure affecting companies such as Pacific Rubiales Energy, Oxy and Ecopetrol.
@@
 However, this area of India is remote, primarily agrarian, and relatively less populous than other parts of India.
-Indeed, for much of this period, India has experienced relatively robust economic growth.
-In figure \ref{fig:indiaMap}, we show the geographic distribution of conflict in India from 1989 to 2007 again using the PRIO conflict site database.
-The story from this map is clearly quite stark from that of Colombia.
-Whereas in Colombia conflict had come right to the gates of major cities, in India conflict has been primarily confined to the periphery.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=.5\textwidth]{indiaMap-crop}
-	\caption{This map illustrates the geographic distribution of all conflict centroids in India, according to the PRIO Conflict Site Dataset, and major cities from 1989 to 2007. }
-	\label{fig:indiaMap}
-\end{figure}
+Indeed, for much of this period, India has experienced relatively robust economic growth.\footnote{For illustrative maps of the Colombia and India cases, see the online supplemental appendix.}
 

### 2016-01-22 LaTeX/EnemyAtTheGates_MinhasRadford_OnlineAppendix.tex
repl files

@@
 % Spacing
-\usepackage[doublespacing]{setspace}
+\usepackage[singlespacing]{setspace}
 
@@
 
-\title[Enemy at the Gates]{Enemy at the Gates: Variation in Economic Growth from Civil Conflict}
+\title[Enemy at the Gates]{Online Appendix for \\ Enemy at the Gates: Variation in Economic Growth from Civil Conflict}
 \date{\today}
@@
 
-\doublespacing
-
 \begin{document}
@@
 \maketitle
-
-\begin{abstract}
-\singlespacing
-\input{Abstract}
-\end{abstract}
 
@@
 %%%%% Appendix %%%%%
-\input{RhodiumOnlineAppendix}
+\newpage
+\section*{Online Appendix}
+\label{online_appendix}
+
+\section{Illustrative Maps}
+\label{maps}
+
+FARC advocates a number of political and economic reforms and chooses targets strategically related to these objectives.
+Figure \ref{fig:colombiaMap} shows the spatial distribution of violence in Colombia from 1989 to 2008, where Bogot\'{a} is designated by a black diamond and major cities by black triangles.
+To determine the centroid locations of conflict we use the PRIO conflict site database developed by \citet{hallberg:2012}.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=.45\textwidth]{colombiaMap-crop}
+	\caption{This map illustrates the geographic distribution of all conflict centroids in Colombia, according to the PRIO Conflict Site Dataset, and major cities from 1989 to 2008.}
+	\label{fig:colombiaMap}
+\end{figure}
+
+\newpage
+In figure \ref{fig:indiaMap}, we show the geographic distribution of conflict in India from 1989 to 2007 again using the PRIO conflict site database.
+The story from this map is clearly quite stark from that of Colombia.
+Whereas in Colombia conflict had come right to the gates of major cities, in India conflict has been primarily confined to the periphery.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=.5\textwidth]{indiaMap-crop}
+	\caption{This map illustrates the geographic distribution of all conflict centroids in India, according to the PRIO Conflict Site Dataset, and major cities from 1989 to 2007. }
+	\label{fig:indiaMap}
+\end{figure}
+\FloatBarrier
+
+\clearpage
+\section{Conflict Distance Models in Tabular Format}
+
+Results of our models measuring the effect of conflict distance in a tabular format.
+
+\input{capminDistRegMain.tex}
+
+\clearpage
+\section{ACLED Analysis}
+\label{acled}
+
+The Armed Conflict Location and Event Dataset provides an alternative source of information on the subnational spatial distribution of armed conflict \citep{raleigh:linke:etal:2010}.
+This dataset is, at the time of writing, limited to Africa and therefore was not selected for the primary analysis presented in the text.
+It does, however, offer us a valuable opportunity to validate our results.
+Here, we have replicated the primary model described in Section 4.2.
+
+In order to match our existing data structure, it was necessary to aggregate the ACLED data to the country-year level.
+We did this by first subsetting ACLED to the years 1989-2008 and then selecting only conflict sites with at least 25 fatalities in each given year.
+The 25 fatalities threshold is intended to mirror the PRIO coding criteria and to prevent very low-fatality events from biasing our estimates of conflict location toward high-population areas.
+Covariates created with PRIO but unavailable in ACLED are omitted.
+The analysis procedure then continues as described in Section 4.2: the minimum distance measure is calculated as the natural logarithm of the average distance in kilometers from any conflict site to the nearest major city (or capital).
+The results are presented in Table~\ref{tab:acledRegResults} below.
+
+When utilizing this alternative dataset we again find significant support for the argument that conflicts more proximate to urban centers have a greater adverse effect on economic growth than those farther away.
+Additionally, if we switched to a fixed effects framework, such as the one described in the previous appendix section, we still find significant support for the hypotheses laid out in our paper.
+
+\input{acledModels.tex}
+\FloatBarrier
+
+\clearpage
+\section{Estimating Models Separately for High and Low Intensity Conflicts}
+
+Here instead of treating conflict intensity as a control, we re-do our primary random effect regression models estimating the effect of distance on growth, but restricting to the civil conflicts coded as wars and then a separate model for civil conflicts coded as low intensity events.
+In both low intensity and high intensity cases we find that the conflict distance variables remain significant and in the expected direction, and the $\beta$ estimate of our distance variables is noticeably higher when using high intensity versus low intensity civil conflict cases.
+The results are presented in Table~\ref{tab:modHiLoIntensity} below.
+
+\input{modelHiLoIntensity.tex}
+\FloatBarrier
+\newpage
 %%%%%%%%%%%%%%%%%%%%%%

### 2016-01-22 LaTeX/EnemyAtTheGates_MinhasRadford_Title.tex
repl files

--- 2016-01-11 LaTeX/EnemyAtTheGates_MinhasRadford_OnlineAppendix.tex
@@
 % references
-\usepackage{natbib}
-% \usepackage[natbib=true, style=authoryear]{biblatex}
-% \bibliography{master.bib}
+\usepackage[natbib=true, style=authoryear]{biblatex}
+\bibliography{master.bib}
 
@@
 
-% \thanks{We are grateful for comments on earlier versions of this paper received at the 72$^{nd}$ annual Midwest Political Science Association Conference in Chicago, April 2-6 2014. }
+\thanks{We are grateful for comments on earlier versions of this paper received at the 72$^{nd}$ annual Midwest Political Science Association Conference in Chicago, April 2-6 2014. }
 
@@
 \makeatletter
-\def\input@path{{/Users/janus829/Dropbox/Research/Rhodium/Graphics/}, {/Users/Ben/Dropbox/Rhodium/Graphics/}, {/Users/s7m/Dropbox/Research/Rhodium/Graphics/}, {C:/Users/Ben/Dropbox/Rhodium/Graphics}}
+\def\input@path{{/Users/janus829/Dropbox/Research/Rhodium/Graphics/}}
 \makeatother
-\graphicspath{{/Users/janus829/Dropbox/Research/Rhodium/Graphics/}, {/Users/Ben/Dropbox/Rhodium/Graphics/}, {/Users/s7m/Dropbox/Research/Rhodium/Graphics/}, {C:/Users/Ben/Dropbox/Rhodium/Graphics/}}
+\graphicspath{{/Users/janus829/Dropbox/Research/Rhodium/Graphics/}}
 
@@
 \begin{document}
-% Wordcount: 9814
+
 \maketitle
@@
 
-\newpage
-\newpage\setcounter{page}{1}
-
-%%%%% Appendix %%%%%
-\input{RhodiumOnlineAppendix}
-%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-
-% \bibliographystyle{elsarticle-harv} 
-\bibliographystyle{jpr}
-\bibliography{master.bib}
-
 \end{document}

### 2016-01-22 LaTeX/RhodiumEmp.tex
repl files

@@
 The results described here hold with the new data.
-A description of the ACLED modeling strategy and results can be found in the Appendix.} Other machine coded event datasets, while providing detailed coverage of events on a global scale, often approximate event locations based on descriptors in the source material or by the location of the reporting news agency itself.
+A description of the ACLED modeling strategy and results can be found in the Online Appendix.} Other machine coded event datasets, while providing detailed coverage of events on a global scale, often approximate event locations based on descriptors in the source material or by the location of the reporting news agency itself.
 Because the location of conflict is critical for this analysis, the urban bias of disaggregated event data is unacceptable.
@@
 
-In figure \ref{fig:CityConfMap}, we show the geographic distribution of conflicts and cities.
-The centroid locations of conflicts are shown by red dots.
-Not surprisingly, in many cases conflict locations are clustered within specific parts of a country.
-In most cases, this clustering is indicative of the same conflict moving within the geographic boundaries of a country over time.
-The blue diamonds in figure \ref{fig:CityConfMap} denote the locations of major cities from 1989 to 2008.
-Countries shaded in grey are those for which no armed conflict took place in this period according to the PRIO dataset.
-
 \begin{amssidewaysfigure}
@@
 \FloatBarrier
+
+In figure \ref{fig:CityConfMap}, we show the geographic distribution of conflicts and cities.
+The centroid locations of conflicts are shown by red dots.
+Not surprisingly, in many cases conflict locations are clustered within specific parts of a country.
+In most cases, this clustering is indicative of the same conflict moving within the geographic boundaries of a country over time.
+The blue diamonds in figure \ref{fig:CityConfMap} denote the locations of major cities from 1989 to 2008.
+Countries shaded in grey are those for which no armed conflict took place in this period according to the PRIO dataset.
 
@@
 Conflict intensity is a binary that distinguishes between minor armed conflicts (between 25 and 999 annual battle deaths) and wars (at least 1000 annual battle deaths), and we set this equal to one if any of the conflicts in a country year were classified as a war and zero if not.\footnote{We also conduct robustness tests in which high intensity and low intensity subsets of the data are modeled separately.
-These can be found in Table \ref{tab:modHiLoIntensity} of the Appendix.} In aggregating conflict duration to the country year level, we bring in the duration (measured in years) of the longest lasting conflict by a certain country-year.
+These can be found in the Online Appendix.} In aggregating conflict duration to the country year level, we bring in the duration (measured in years) of the longest lasting conflict by a certain country-year.
 Conflict area measures the conflict zone in square kilometers.
@@
 
-We depict the results of our conflict distance models in figures \ref{fig:capCoef} and \ref{fig:cityCoef}.
-The results across the two models are broadly consistent, so we will discuss them in tandem.
+We depict the results of our conflict distance models in figures \ref{fig:capCoef} and \ref{fig:cityCoef}.\footnote{In the Online Appendix, we include tabular versions of these plots.} The results across the two models are broadly consistent, so we will discuss them in tandem.
 Surprisingly, conflict duration and the number of conflicts a country is facing do not relate to GDP growth in the direction that we expected.\footnote{With respect to the duration finding our argument would be that more important to determining the effect of conflict on growth is its proximity to urban centers.
@@
 As expected, inflation has a sharp negative effect on GDP growth.
-Countries deriving greater shares of their GDP from natural resource rents see slighlty higher levels of growth, and, not surprisingly, the average of world GDP growth is positively related to our dependent variable.
+Countries deriving greater shares of their GDP from natural resource rents see slightly higher levels of growth, and, not surprisingly, the average of world GDP growth is positively related to our dependent variable.
 
@@
 	\label{fig:coefplot}
-\end{figure}
-
-To ensure that our parameter estimates are robust to changes in our sample, we run a six-fold cross-validation.
-This analysis helps us to understand whether some of the subsets in our dataset follow a different pattern than what is in the broader set \citep{beck2008time}.
-To conduct the cross-validation, we randomly split the 68 country observations in our dataset into seven approximately equal subsets.
-Each subset ends up containing a minimum of approximately 65 cases.
-We then run each model shown in figure \ref{fig:coefplot} seven times, where in each iteration we left out one subsample.
-The results of this analysis are depicted in \ref{fig:crossPlot}, and we can clearly see that the parameter estimates for our two spatial proximity variables remain consistent across the exclusion of any of the folds.
-
-\begin{figure}
-	\centering
-	\resizebox{.8\textwidth}{!}{\input{crossValPlot.tex}}
-	\caption{Each line here in the left panel shows the coefficient estimate of $Ln(Min.
-\; Capital \; Dist.)_{i,t-1}$ from rerunning the model on six random subsamples within the dataset.
-The panel on the right shows the same for $Ln(Min.
-\; City \; Dist.)_{i,t-1}$.
-All the covariates used in the initial model shown in figure \ref{fig:coefplot} were included as well.}
-	\label{fig:crossPlot}
 \end{figure}

### 2016-01-22 LaTeX/RhodiumTheory.tex
repl files

@@
 However, this area of India is remote, primarily agrarian, and relatively less populous than other parts of India.
-Indeed, for much of this period, India has experienced relatively robust economic growth.\footnote{For illustrative maps of the Colombia and India cases, see the online supplemental appendix.}
+Indeed, for much of this period, India has experienced relatively robust economic growth.\footnote{For illustrative maps of the Colombia and India cases, see the Online Appendix.}
 

### 2016-01-22 R/Analysis/descStats.R

@@ -1,5 +1,5 @@
 # Workspace
-if(Sys.info()["user"]=="janus829"){source('/Users/janus829/Desktop/Research/Rhodium/R/setup.R')}
+if(Sys.info()["user"]=="janus829"){source('/Users/janus829/Research/Rhodium/R/setup.R')}
 if(Sys.info()["user"]=="Ben"){source('/Users/Ben/Github/Rhodium/R/setup.R')}
 
 
@@ -36,9 +36,9 @@ tmp=tmp + theme( axis.title.y=element_text(vjust=1),
   panel.grid.major=element_blank(), panel.grid.minor=element_blank() )
 tmp
 setwd(pathGraphics)
-# tikz(file='distGdp.tex', width=7, height=4, standAlone=FALSE)
-# tmp
-# dev.off()
+tikz(file='distGdp.tex', width=7, height=4, standAlone=FALSE)
+tmp
+dev.off()
 ######################################################################
 
 ########################################################################

### 2016-01-22 R/Analysis/models.R

@@ -129,74 +129,25 @@ temp
 if(genTikz){ dev.off() }
 ###################################################################
 
-
 #### Begin Robustness checks
-
-###################################################################
-# Divide intro training and test
-train=modData[which(modData$year<=2000),]
-test=modData[which(modData$year>2000),]
-
-# Run model on train
-mCityTr=lmer(ctyForm, data=train)
-mCapTr=lmer(capForm, data=train)
-
-# Performance stats on test
-outSampPerf = function(dv, mod, testData){
-  res=summary(mod)$'coefficients'
-  tData=na.omit(
-    cbind(1, testData[,c(dv, rownames(res)[2:nrow(res)] ) ] ) 
-    )
-  y=tData[,2]; tData=data.matrix(tData[,c(1,3:ncol(tData))])
-  tY = tData %*% cbind(res[,1])
-  diff=y-tY
-  return( sqrt(mean(diff^2)) )
-}
-
-ggRMSE=data.frame(rbind(
-  cbind(var="Ln(Min. City Dist.)$_{t}$", type='In-Sample \n n=375 \n N=66', 
-    stat=rmse(mCityTr) ),
-  cbind("Ln(Min. City Dist.)$_{t}$", 'Out-Sample \n n=186 \n N=42', 
-    outSampPerf('lngdpGr_l0',mCityTr,test)),
-  cbind("Ln(Min. Capital Dist.)$_{t}$", 'In-Sample \n n=375 \n N=66', 
-    rmse(mCapTr) ),
-  cbind("Ln(Min. Capital Dist.)$_{t}$", 'Out-Sample \n n=186 \n N=42', 
-    outSampPerf('lngdpGr_l0',mCapTr,test))
-  ))
-ggRMSE$stat=numSM(ggRMSE$stat)
-
-# Bar plot
-temp=ggplot(ggRMSE, aes(x=type, y=stat))
-temp=temp + geom_bar(stat='identity') + ylab('RMSE') + xlab('')
-temp=temp + facet_wrap(~var)
-temp=temp + theme(axis.title.y=element_text(vjust=1),
-  legend.position='none', legend.title=element_blank(),
-  axis.ticks=element_blank(), panel.grid.major=element_blank(),
-  panel.grid.minor=element_blank())
-setwd(pathGraphics)
-if(genTikz){ tikz(file='rmseInOut.tex', width=7, height=4, standAlone=FALSE)}
-temp
-if(genTikz){ dev.off() }
[…]

### 2016-01-22 R/Replication/paperScripts/Figure1.R

@@ -1,0 +1,30 @@
+# Workspace
+source('paperScripts/setup.R')
+
+########################################################################
+# World map of cities and conflicts
+load(paste0(pathData, "cityTotPopLatLongvFinal.rda"))
+prioData=read.csv(paste0(pathData, "ConflictSite 4-2010_v3 Dataset.csv"))
+prioData$Conflict.territory=charSM(prioData$Conflict.territory)
+prioData$Conflict.territory[prioData$Conflict.territory=='Yugoslavia']='Serbia'
+prioData$Conflict.territory[prioData$Conflict.territory=='DRC']='Democratic Republic of Congo'
+prioData$cname=countrycode(prioData$Conflict.territory, 'country.name','country.name')
+cntries=unique(prioData$cname)
+
+# Color Non-Conflict countries
+worldmap=cshp(as.Date('2000-1-1'))
+worldmap$CNTRY_NAME=charSM(worldmap$CNTRY_NAME)
+worldmap$CNTRY_NAME[worldmap$CNTRY_NAME=='Congo, DRC']='Congo, Democratic Republic of'
+Wcntries=worldmap$CNTRY_NAME
+Wcntries=panel$cname[match(Wcntries, panel$CNTRY_NAME)]
+noConfCntries=setdiff(Wcntries, cntries)
+mapColors=rep('white',length(Wcntries))
+mapColors[which(Wcntries %in% noConfCntries)] = 'grey'
+
+## FIGURE 1 ##
+pdf(file=paste0(pathGraphics,'Figure1.pdf'), width=12, height=6)
+plot(worldmap, col=mapColors)
+points(fYrCty$cleanLong, fYrCty$cleanLat, col='blue', pch=18, cex=0.5)
+points(prioData$Longitude,prioData$Latitude, col='red', pch=16,cex=0.5)
+dev.off()
+########################################################################

### 2016-01-22 R/Replication/paperScripts/Figure2.R

@@ -1,0 +1,36 @@
+# Workspace
+source('paperScripts/setup.R')
+
+######################################################################
+# Aggregate GDP Growth and Distance
+load(paste0(pathData,'combinedData.rda'))
+
+# Create bucketed version of mindist and find averag GDP gr
+yData$cityDistCat=contToCat(yData$minDist.min, .25)
+yData$capDistCat=contToCat(yData$capDist.min, .25)
+
+# Conf intervals using summarySE:
+gdpByCityDist=na.omit( summarySE(data=yData, measurevar='gdpGr_l0', 
+	groupvars='cityDistCat', na.rm=TRUE) )
+gdpByCapDist=na.omit( summarySE(data=yData, measurevar='gdpGr_l0', 
+	groupvars='capDistCat', na.rm=TRUE) )
+
+names(gdpByCityDist)[1]='distCat'; names(gdpByCapDist)[1]='distCat'
+ggData=cbind(
+	rbind(gdpByCityDist, gdpByCapDist),
+	type=c(rep('Min. City Dist.$_{t-1}$',nrow(gdpByCityDist)),
+		rep('Min. Capital Dist.$_{t-1}$',nrow(gdpByCapDist)) ),
+	cut=rep( c('0-25$^{th}$','26-50$^{th}$','51-75$^{th}$','76-100$^{th}$'), 2 )
+	)
+
+## FIGURE 2 ##
+tmp=ggplot(ggData, aes(x=cut, y=gdpGr_l0))
+tmp=tmp + geom_bar(stat='identity', fill='grey')
+tmp=tmp + geom_errorbar(aes(ymin=gdpGr_l0-se, ymax=gdpGr_l0+se),width=.2)
+tmp=tmp + ylab("\\% $\\Delta$ GDP$_{t}$")+xlab('')
+tmp=tmp + facet_wrap(~type)
+tmp=tmp + theme( axis.title.y=element_text(vjust=1),
+  axis.ticks=element_blank(),legend.position='none',
+  panel.grid.major=element_blank(), panel.grid.minor=element_blank() )
+ggsave(file=paste0(pathGraphics, 'Figure2.pdf'), plot=tmp, width=7, height=4)
+######################################################################

### 2016-01-22 R/Replication/paperScripts/paperReplication.R

@@ -1,0 +1,6 @@
+# Run to replicate figures and tables in paper
+source('Figure1.R')
+source('Figure2.R')
+source('Figure3_Table1.R')
+source('Figures4-5.R')
+source('Tables2-3.R')

### 2016-01-22 R/Replication/paperScripts/setup.R

@@ -1,0 +1,117 @@
+# Clearing workspace
+rm(list=ls())
+
+# Setting working directory
+pathData='Data/'
+pathGraphics="Graphics/"
+
+# Load in panel dataframe
+load(paste0(pathData, 'panel.rda'))
+
+# Loading libraries and functions
+loadPkg=function(toLoad){
+  for(lib in toLoad){
+  if(! lib %in% installed.packages()[,1])
+    { install.packages(lib, repos='http://cran.rstudio.com/') }
+  suppressMessages( library(lib, character.only=TRUE) )
+  }
+}
+
+pks = c('ggplot2', 'grid', 'cshapes','tikzDevice',
+  'RColorBrewer', 'stargazer', 'reshape', 'countrycode',
+  'foreign', 'doBy', 'lme4', 'plm', 'MASS', 'latex2exp')
+loadPkg(pks)
+
+# gg theme
+theme_set(theme_bw())
+
+# Helpful functions
+numSM=function(x){as.numeric(as.character(x))}
+charSM=function(x){as.character(x)}
+contToCat=function(x,by=0.1){ cut(x, breaks=quantile(x,seq(0,1,by),na.rm=T)) }
+logTrans=function(x){ log( x + abs(min(x, na.rm=T)) + 1) }
+starOut = function(fname,starOutput){
+  output = capture.output(starOutput)
+  cat(paste(output, collapse = "\n"), "\n", file=fname, append=TRUE) }
+
+# Lagging vars
+lagTS <- function(x,l){
+  cuts <- (length(x)-(l-1)):length(x)
+  c(rep(NA,l), x[ -cuts ] )
+}
+
+lagDataSM <- function(data, country_year, country, varsTOlag, lag=1)
+{
+  data[,country_year] = numSM(data[,country_year])
+  data <- data[order(data[,country_year]),]
+  lagData <- apply(data[,varsTOlag], 2,
+    function(x){
+      unlist(by(x, data[,country], function(y) lagTS(y,lag) ) )
+    } )
+  colnames(lagData) <- paste('lag', lag, '_', varsTOlag, sep='')
+  cbind(data, lagData)
+}
+
+# Create model formula
+modForm = function(dv='gdpGr_l0', ivs, id='ccode', type='random'){
+  base = paste(dv, paste(ivs, collapse=' + '), sep=' ~ ')
+  if(type=='random'){
+    eff = paste0('(1 |', id, ')')
[…]

### 2016-01-22 R/Replication/replication.R

@@ -1,0 +1,7 @@
+# Run to replicate figures and tables in paper
+# To correctly print math in pictures, save output using tikz from tikzDevice pkg instead of ggsave
+print('Creating Figure 1......'); source('paperScripts/Figure1.R')
+print('Creating Figure 2......'); source('paperScripts/Figure2.R')
+print('Creating Figure 3 & Table 1......'); source('paperScripts/Figure3_Table1.R')
+print('Creating Figures 4 & 5......'); source('paperScripts/Figures4-5.R')
+print('Creating Tables 2 & 3......'); source('paperScripts/Tables2-3.R')

### 2016-01-22 R/Replication/onlineAppendixScripts/Figures1-2.R
added repl files for online appendix

@@ -1,0 +1,58 @@
+# Workspace
+source('onlineAppendixScripts/setup.R')
+
+# Load conflict country year data
+load(paste0(pathData,'combinedData.rda'))
+load(paste0(pathData,"cityTotPopLatLongvFinal.rda"))
+prio = read.csv(paste0(pathData,"ConflictSite 4-2010_v3 Dataset.csv"), stringsAsFactors=F)
+
+fYrCty$cname = toupper( countrycode( fYrCty$cname,"country.name","country.name") )
+prio$Conflict.territory = toupper( countrycode( prio$Conflict.territory,"country.name","country.name") )
+######################################################################
+# Trace conflict over time
+conflictMap = function(cname){
+	worldmap=cshp(date=as.Date("1990-01-01"),useGW=F)
+	ccode = countrycode(cname,"country.name","cown")
+	cntryShape = worldmap[worldmap$COWCODE==ccode,]
+	newprio = na.omit(prio[prio$Conflict.territory==cname,])
+
+	gpclibPermit()
+	ggmap = fortify(cntryShape, region = "COWCODE")
+	ggmapData = data.frame("id" = unique(ggmap$id))
+	ggmapData$id = as.numeric(as.character(ggmapData$id))
+
+	tmp = ggplot()
+	tmp = tmp + geom_map(data=ggmapData, aes(map_id = id), map=ggmap, fill='white', 
+		linetype=1, colour='black') + expand_limits(x = ggmap$long, y = ggmap$lat) 
+	tmp = tmp + geom_point(aes(
+		x=fYrCty$cleanLong[fYrCty$cname==cname & fYrCty$Capital==0], 
+		y=fYrCty$cleanLat[fYrCty$cname==cname & fYrCty$Capital==0]), 
+		pch=17,size=4,col='darkgrey')
+	tmp = tmp + geom_point(aes(
+		x=fYrCty$cleanLong[fYrCty$cname==cname & fYrCty$Capital!=0], 
+		y=fYrCty$cleanLat[fYrCty$cname==cname & fYrCty$Capital!=0]), 
+		pch=18,size=5,col='darkgrey')
+	tmp = tmp + geom_point(aes(x=newprio$Longitude, y=newprio$Latitude,
+		color=newprio$Year),size=4)
+	tmp = tmp + scale_colour_gradient('',
+		low=brewer.pal(9,'Blues')[2],high=brewer.pal(9,'Blues')[9],
[…]

### 2016-01-22 R/Replication/onlineAppendixScripts/Table1.R

@@ -1,0 +1,49 @@
+# Workspace
+source('onlineAppendixScripts/setup.R')
+
+# Load conflict country year data
+load(paste0(pathData,'combinedData.rda')); modData=yData
+
+# CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
+###################################################################
+# Log transforming DVs
+modData$lngdp_l0 = log(modData$gdp_l0)
+modData$lngdp = log(modData$gdp)
+modData$lngdpGr_l0 = (modData$lngdp_l0-modData$lngdp)/modData$lngdp_l0
+modData$lngdpGr_l0 = modData$gdpGr_l0
+
+# Transformations for conflict variables
+modData$lnminDist.min <- log(modData$minDist.min+1)
+modData$lncapDist.min <- log(modData$capDist.min+1)
+modData$lnminDist.mean <- log(modData$minDist.mean+1)
+modData$lncapDist.mean <- log(modData$capDist.mean+1)
+modData$Int.max <- modData$Int.max-1
+
+# Transformations for other controls
+modData$lngdpCap = log(modData$gdpCap)
+modData$lninflation_l1 = logTrans(modData$inflation_l1)
+modData$democ = as.numeric(modData$polity2>=6)
+modData$polity2 = modData$polity2 + 11
+###################################################################
+
+## MODELS FOR GDP GROWTH (ANNUAL %)
+###################################################################
+# Model parameters
+dv = 'gdpGr_l0'
+kivs = c('lnminDist.min', 'lncapDist.min')
+cntrls = c(
+  'Int.max',
+  'durSt1max',  'confAreaProp', 'nconf', 
+  'upperincome', 'lninflation_l1',  'polity2', 'resourceGDP',  'gdpGr.mean_l0')
+
+# Model specifications
+ctyForm=modForm(ivs=c(kivs[1], cntrls), type='random')
+capForm=modForm(ivs=c(kivs[2], cntrls), type='random')
+
+# Run models
+mCity = lmer(ctyForm, data = modData )
+mCap = lmer(capForm, data = modData )
+
+## TABLE 1 ##
+starOut(paste0(pathGraphics,"OnlineAppendix_Table1.tex"), stargazer(mCap, mCity) )
+###################################################################

### 2016-01-22 R/Replication/onlineAppendixScripts/Table2.R

@@ -1,0 +1,43 @@
+# Workspace
+source('onlineAppendixScripts/setup.R')
+
+# Load conflict country year data
+load(paste0(pathData,'combinedData.rda')); modData=yData
+
+# CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
+###################################################################
+# Log transforming DVs
+modData$lngdp_l0 = log(modData$gdp_l0)
+modData$lngdp = log(modData$gdp)
+modData$lngdpGr_l0 = (modData$lngdp_l0-modData$lngdp)/modData$lngdp_l0
+modData$lngdpGr_l0 = modData$gdpGr_l0
+
+# Transformations for conflict variables
+modData$lnminDistACLED.mean <- log(modData$minDistACLED.mean+1)
+modData$lncapDistACLED.mean <- log(modData$acledCapDist.mean+1)
+
+# Transformations for other controls
+modData$lngdpCap = log(modData$gdpCap)
+modData$lninflation_l1 = logTrans(modData$inflation_l1)
+modData$democ = as.numeric(modData$polity2>=6)
+modData$polity2 = modData$polity2 + 11
+###################################################################
+
+## MODELS FOR GDP GROWTH (ANNUAL %)
+###################################################################
+# Model parameters
+cntrls = c(
+  'nconf','lninflation_l1', 
+  'polity2', 'resourceGDP',  'gdpGr.mean_l0')
+
+# Model specifications
+acledForm = modForm(ivs=c('lnminDistACLED.mean', cntrls))
+acledFormCap = modForm(ivs=c('lncapDistACLED.mean', cntrls))
+
+# Run models
+mAcled = lmer(acledForm, data = modData )
+mAcledCap = lmer(acledFormCap, data=modData)
+
+## TABLE 2 ##
+starOut(paste0(pathGraphics,"OnlineAppendix_Table2.tex"), stargazer(mAcled, mAcledCap) )
+###################################################################

### 2016-01-22 R/Replication/onlineAppendixScripts/Table3.R

@@ -1,0 +1,59 @@
+# Workspace
+source('onlineAppendixScripts/setup.R')
+
+###################################################################
+# Functions and parameters
+# CREATE APPROPRIATE VARIABLES FOR REGRESSIONS
+prepData = function(modData){
+	modData$lngdp_l0 = log(modData$gdp_l0)
+	modData$lngdp = log(modData$gdp)
+	modData$lngdpGr_l0 = (modData$lngdp_l0-modData$lngdp)/modData$lngdp_l0
+	modData$lngdpGr_l0 = modData$gdpGr_l0
+
+	# Transformations for conflict variables
+	modData$lnminDist.min <- log(modData$minDist.min+1)
+	modData$lncapDist.min <- log(modData$capDist.min+1)
+
+	# Transformations for other controls
+	modData$lngdpCap = log(modData$gdpCap)
+	modData$lninflation_l1 = logTrans(modData$inflation_l1)
+	modData$democ = as.numeric(modData$polity2>=6)
+	modData$polity2 = modData$polity2 + 11
+	return(modData)
+}
+
+# Model specifications
+dv = 'gdpGr_l0'
+kivs = c('lnminDist.min', 'lncapDist.min')
+cntrls = c(
+  'durSt1max',  'confAreaProp', 'nconf', 
+  'upperincome', 'lninflation_l1',  'polity2', 'resourceGDP',  'gdpGr.mean_l0')
+
+# Run random effect models
+ctyForm=modForm(ivs=c(kivs[1], cntrls), type='random')
+capForm=modForm(ivs=c(kivs[2], cntrls), type='random')
+###################################################################
+
+###################################################################
+# Low intensity analysis
+load(paste0(pathData,'combinedData_loInt.rda')); modData=yData
+modData = prepData(modData)
+
+mCityLo = lmer(ctyForm, data = modData )
+mCapLo = lmer(capForm, data = modData )
+###################################################################
+
+###################################################################
+# High intensity analysis
+load(paste0(pathData,'combinedData_hiInt.rda')); modData=yData
+
+modData = prepData(modData)
+
+mCityHi = lmer(ctyForm, data = modData )
+mCapHi = lmer(capForm, data = modData )
+###################################################################
+
+###################################################################
+## TABLE 3 ##
+starOut(paste0(pathGraphics,"OnlineAppendix_Table3.tex"), stargazer(mCityLo, mCityHi, mCapLo, mCapHi))
+###################################################################

### 2016-01-22 R/Replication/onlineAppendixScripts/setup.R

@@ -28,7 +28,6 @@ theme_set(theme_bw())
 # Helpful functions
 numSM=function(x){as.numeric(as.character(x))}
 charSM=function(x){as.character(x)}
-contToCat=function(x,by=0.1){ cut(x, breaks=quantile(x,seq(0,1,by),na.rm=T)) }
 logTrans=function(x){ log( x + abs(min(x, na.rm=T)) + 1) }
 starOut = function(fname,starOutput){
   output = capture.output(starOutput)

### 2016-01-22 R/Replication/paperScripts/setup.R

@@ -29,6 +29,12 @@ theme_set(theme_bw())
 numSM=function(x){as.numeric(as.character(x))}
 charSM=function(x){as.character(x)}
 logTrans=function(x){ log( x + abs(min(x, na.rm=T)) + 1) }
+contToCat=function(x,byQ=0.1){ 
+  cut(x, 
+    breaks=(
+      quantile(x,seq(0,1,byQ),na.rm=T) - c(.1, rep(0,1/byQ) )
+      ) ) 
+}
 starOut = function(fname,starOutput){
   output = capture.output(starOutput)
   cat(paste(output, collapse = "\n"), "\n", file=fname, append=TRUE) }

### 2016-01-22 R/Replication/replication.R

@@ -5,3 +5,9 @@ print('Creating Figure 2......'); source('paperScripts/Figure2.R')
 print('Creating Figure 3 & Table 1......'); source('paperScripts/Figure3_Table1.R')
 print('Creating Figures 4 & 5......'); source('paperScripts/Figures4-5.R')
 print('Creating Tables 2 & 3......'); source('paperScripts/Tables2-3.R')
+
+# Run to replicate figures and tables in appendix
+print('Creating Online Appendix Figures 1 & 2......'); source('onlineAppendixScripts/Figures1-2.R')
+print('Creating Online Appendix Table 1......'); source('onlineAppendixScripts/Table1.R')
+print('Creating Online Appendix Table 2......'); source('onlineAppendixScripts/Table2.R')
+print('Creating Online Appendix Table 3......'); source('onlineAppendixScripts/Table3.R')

### 2016-01-23 R/Replication/replication.R
fix online app fig issue

@@ -1,13 +1,0 @@
-# Run to replicate figures and tables in paper
-# To correctly print math in pictures, save output using tikz from tikzDevice pkg instead of ggsave
-print('Creating Figure 1......'); source('paperScripts/Figure1.R')
-print('Creating Figure 2......'); source('paperScripts/Figure2.R')
-print('Creating Figure 3 & Table 1......'); source('paperScripts/Figure3_Table1.R')
-print('Creating Figures 4 & 5......'); source('paperScripts/Figures4-5.R')
-print('Creating Tables 2 & 3......'); source('paperScripts/Tables2-3.R')
-
-# Run to replicate figures and tables in appendix
-print('Creating Online Appendix Figures 1 & 2......'); source('onlineAppendixScripts/Figures1-2.R')
-print('Creating Online Appendix Table 1......'); source('onlineAppendixScripts/Table1.R')
-print('Creating Online Appendix Table 2......'); source('onlineAppendixScripts/Table2.R')
-print('Creating Online Appendix Table 3......'); source('onlineAppendixScripts/Table3.R')

### 2016-01-23 R/Replication/runReplication.R

@@ -1,0 +1,13 @@
+# # Run to replicate figures and tables in paper
+# # To correctly print math in pictures, save output using tikz from tikzDevice pkg instead of ggsave
+# print('Creating Figure 1......'); source('paperScripts/Figure1.R')
+# print('Creating Figure 2......'); source('paperScripts/Figure2.R')
+# print('Creating Figure 3 & Table 1......'); source('paperScripts/Figure3_Table1.R')
+# print('Creating Figures 4 & 5......'); source('paperScripts/Figures4-5.R')
+# print('Creating Tables 2 & 3......'); source('paperScripts/Tables2-3.R')
+
+# # Run to replicate figures and tables in appendix
+print('Creating Online Appendix Figures 1 & 2......'); source('onlineAppendixScripts/Figures1-2.R')
+# print('Creating Online Appendix Table 1......'); source('onlineAppendixScripts/Table1.R')
+# print('Creating Online Appendix Table 2......'); source('onlineAppendixScripts/Table2.R')
+# print('Creating Online Appendix Table 3......'); source('onlineAppendixScripts/Table3.R')

### 2016-01-23 LaTeX/EnemyAtTheGates_MinhasRadford_OnlineAppendix.tex
clean up online appendix

@@
 It does, however, offer us a valuable opportunity to validate our results.
-Here, we have replicated the primary model described in Section 4.2.
-
-In order to match our existing data structure, it was necessary to aggregate the ACLED data to the country-year level.
-We did this by first subsetting ACLED to the years 1989-2008 and then selecting only conflict sites with at least 25 fatalities in each given year.
-The 25 fatalities threshold is intended to mirror the PRIO coding criteria and to prevent very low-fatality events from biasing our estimates of conflict location toward high-population areas.
+We aggregate the ACLED data to the country-year level by first subsetting ACLED to the years 1989-2008 and then selecting only conflict sites with at least 25 fatalities in each given year.
 Covariates created with PRIO but unavailable in ACLED are omitted.
-The analysis procedure then continues as described in Section 4.2: the minimum distance measure is calculated as the natural logarithm of the average distance in kilometers from any conflict site to the nearest major city (or capital).
+The analysis procedure then continues as described in Section 4.2.
 The results are presented in Table~\ref{tab:acledRegResults} below.
-
-When utilizing this alternative dataset we again find significant support for the argument that conflicts more proximate to urban centers have a greater adverse effect on economic growth than those farther away.
-Additionally, if we switched to a fixed effects framework, such as the one described in the previous appendix section, we still find significant support for the hypotheses laid out in our paper.
+When utilizing this alternative dataset we again find significant support for our argument.
 
@@
 
-Here instead of treating conflict intensity as a control, we re-do our primary random effect regression models estimating the effect of distance on growth, but restricting to the civil conflicts coded as wars and then a separate model for civil conflicts coded as low intensity events.
-In both low intensity and high intensity cases we find that the conflict distance variables remain significant and in the expected direction, and the $\beta$ estimate of our distance variables is noticeably higher when using high intensity versus low intensity civil conflict cases.
-The results are presented in Table~\ref{tab:modHiLoIntensity} below.
+Here instead of treating conflict intensity as a control, we re-do our primary random effect regression models estimating the effect of distance on growth, but restricting to the civil conflicts coded as wars, and then separately for low intensity events.
 
@@
 \FloatBarrier
-\newpage
+\clearpage
 %%%%%%%%%%%%%%%%%%%%%%
@@
 \bibliography{master.bib}
+\newpage
 

### 2016-01-23 LaTeX/TeX/Manuscript/Abstract.tex
reorg for final submission to jcr

--- 2014-10-10 LaTeX/Abstract.tex
@@
 % Version submitted to MPSA:
-Within the conflict literature there has been much disagreement about the relationship between civil wars and state economic performance.
-While civil war is often associated with poor economic performance, some states have managed to weather domestic armed conflict during periods of robust growth.
-We find that this disagreement results from not accounting for the spatial distribution of conflict within a country.
-Literature in economics has recently stressed the importance of major cities to development and economic growth.
+There has been much disagreement about the relationship between civil wars and state economic performance.
+While civil war is often associated with poor economic performance, some states have managed robust growth despite periods of domestic armed conflict.
+We find this disagreement results from not accounting for the spatial distribution of conflict within a country.
+A robust literature in economics stresses the role major cities play in economic growth.
 We hypothesize that the economic impact of civil conflict is contingent on the conflict's location relative to major urban centers within a state.
@@
 In doing so, we bridge the economic development literature on the importance of cities with extant literature on the effect of armed conflict to provide a novel explanation for the paradox of high macroeconomic growth in conflict ridden countries.
-By doing so, we are able to resolve tensions in the literature regarding the relationship between economic performance and civil wars.
-We find that the proximity of civil war to major urban centers is negatively correlated with economic growth and use simulations to show that the estimated marginal effect of civil war proximity can mean the difference between robust growth and stagnation.

### 2016-01-23 LaTeX/TeX/Manuscript/Graphics/distGdp.tex
reorg for final submission to jcr

% Created by tikzDevice version 0.8.1 on 2016-01-23 06:21:33
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (505.89,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 31.66, 33.48) rectangle (262.78,264.47);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.66, 33.48) rectangle (262.78,264.47);
\definecolor{fillColor}{RGB}{190,190,190}

\path[fill=fillColor] ( 39.92, 43.98) rectangle ( 89.44,118.52);

\path[fill=fillColor] ( 94.94, 43.98) rectangle (144.47,156.08);

\path[fill=fillColor] (149.97, 43.98) rectangle (199.50,206.62);

\path[fill=fillColor] (205.00, 43.98) rectangle (254.52,210.92);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.18,166.05) --
	( 70.18,166.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.68,166.05) --
	( 64.68, 70.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.18, 70.99) --
	( 70.18, 70.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.20,196.90) --
	(125.21,196.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] (119.71,196.90) --
	(119.71,115.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.20,115.25) --
	(125.21,115.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (169.23,234.20) --
	(180.24,234.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] (174.73,234.20) --
	(174.73,179.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (169.23,179.04) --
	(180.24,179.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (224.26,230.50) --
	(235.26,230.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.76,230.50) --
	(229.76,191.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (224.26,191.33) --
	(235.26,191.33);
\definecolor{drawColor}{gray}{0.50}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.66, 33.48) rectangle (262.78,264.47);
\end{scope}
\begin{scope}
\path[clip] (268.78, 33.48) rectangle (499.89,264.47);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (268.78, 33.48) rectangle (499.89,264.47);
\definecolor{fillColor}{RGB}{190,190,190}

\path[fill=fillColor] (277.03, 43.98) rectangle (326.56,107.02);

\path[fill=fillColor] (332.06, 43.98) rectangle (381.58,140.28);

\path[fill=fillColor] (387.08, 43.98) rectangle (436.61,211.59);

\path[fill=fillColor] (442.11, 43.98) rectangle (491.64,230.95);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (296.29,149.26) --
	(307.30,149.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (301.79,149.26) --
	(301.79, 64.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (296.29, 64.78) --
	(307.30, 64.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (351.32,189.55) --
	(362.32,189.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] (356.82,189.55) --
	(356.82, 91.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (351.32, 91.00) --
	(362.32, 91.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (406.34,232.29) --
	(417.35,232.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (411.85,232.29) --
	(411.85,190.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] (406.34,190.89) --
	(417.35,190.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] (461.37,253.97) --
	(472.38,253.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (466.87,253.97) --
	(466.87,207.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (461.37,207.94) --
	(472.38,207.94);
\definecolor{drawColor}{gray}{0.50}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (268.78, 33.48) rectangle (499.89,264.47);
\end{scope}
\begin{scope}
\path[clip] ( 31.66,264.47) rectangle (262.78,283.08);
\definecolor{drawColor}{gray}{0.50}
\definecolor{fillColor}{gray}{0.80}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] ( 31.66,264.47) rectangle (262.78,283.08);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (147.22,270.47) {Min. Capital Dist.$_{t-1}$};
\end{scope}
\begin{scope}
\path[clip] (268.78,264.47) rectangle (499.89,283.08);
\definecolor{drawColor}{gray}{0.50}
\definecolor{fillColor}{gray}{0.80}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (268.78,264.47) rectangle (499.89,283.08);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (384.33,270.47) {Min. City Dist.$_{t-1}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 26.26, 40.67) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 26.26, 81.59) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 26.26,122.51) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 26.26,163.44) {3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 26.26,204.36) {4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 26.26,245.28) {5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 64.68, 21.46) {0-25$^{th}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (119.71, 21.46) {26-50$^{th}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (174.73, 21.46) {51-75$^{th}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (229.76, 21.46) {76-100$^{th}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (301.79, 21.46) {0-25$^{th}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (356.82, 21.46) {26-50$^{th}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (411.85, 21.46) {51-75$^{th}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (466.87, 21.46) {76-100$^{th}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at ( 16.66,148.97) {\% $\Delta$ Ln(GDP)$_{t}$};
\end{scope}
\end{tikzpicture}

### 2016-01-23 LaTeX/TeX/Manuscript/Graphics/mCapCoefPlot.tex
reorg for final submission to jcr

% Created by tikzDevice version 0.8.1 on 2015-08-25 14:10:34
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,433.62);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (289.08,433.62);
\end{scope}
\begin{scope}
\path[clip] (137.46, 34.03) rectangle (277.03,421.57);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (137.46, 34.03) rectangle (277.03,421.57);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (213.47, 56.83) -- (223.69, 56.83);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (213.37, 94.83) -- (214.72, 94.83);
\definecolor{drawColor}{RGB}{150,150,150}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (211.43,132.82) -- (214.83,132.82);
\definecolor{drawColor}{RGB}{222,45,38}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (179.19,170.81) -- (196.84,170.81);
\definecolor{drawColor}{RGB}{150,150,150}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (169.39,208.81) -- (270.69,208.81);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (215.48,246.80) -- (238.71,246.80);
\definecolor{drawColor}{RGB}{222,45,38}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (143.80,284.80) -- (192.56,284.80);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (214.05,322.79) -- (215.43,322.79);
\definecolor{drawColor}{RGB}{150,150,150}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (184.07,360.78) -- (220.64,360.78);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (215.48,398.78) -- (230.32,398.78);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 1.1pt,line join=round] (214.29, 56.83) -- (222.87, 56.83);

\path[draw=drawColor,line width= 1.1pt,line join=round] (213.48, 94.83) -- (214.61, 94.83);
\definecolor{drawColor}{gray}{0.59}

\path[draw=drawColor,line width= 1.1pt,line join=round] (211.71,132.82) -- (214.56,132.82);
\definecolor{drawColor}{RGB}{222,45,38}

\path[draw=drawColor,line width= 1.1pt,line join=round] (180.61,170.81) -- (195.42,170.81);
\definecolor{drawColor}{gray}{0.59}

\path[draw=drawColor,line width= 1.1pt,line join=round] (177.53,208.81) -- (262.55,208.81);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 1.1pt,line join=round] (217.35,246.80) -- (236.85,246.80);
\definecolor{drawColor}{RGB}{222,45,38}

\path[draw=drawColor,line width= 1.1pt,line join=round] (147.72,284.80) -- (188.64,284.80);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 1.1pt,line join=round] (214.16,322.79) -- (215.32,322.79);
\definecolor{drawColor}{gray}{0.59}

\path[draw=drawColor,line width= 1.1pt,line join=round] (187.01,360.78) -- (217.70,360.78);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 1.1pt,line join=round] (216.67,398.78) -- (229.13,398.78);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (213.36, 34.03) -- (213.36,421.57);
\definecolor{drawColor}{RGB}{54,144,192}
\definecolor{fillColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (222.90,398.78) circle (  2.85);
\definecolor{drawColor}{gray}{0.59}
\definecolor{fillColor}{gray}{0.59}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (202.36,360.78) circle (  2.85);
\definecolor{drawColor}{RGB}{54,144,192}
\definecolor{fillColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (214.74,322.79) circle (  2.85);
\definecolor{drawColor}{RGB}{222,45,38}
\definecolor{fillColor}{RGB}{222,45,38}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.18,284.80) circle (  2.85);
\definecolor{drawColor}{RGB}{54,144,192}
\definecolor{fillColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (227.10,246.80) circle (  2.85);
\definecolor{drawColor}{gray}{0.59}
\definecolor{fillColor}{gray}{0.59}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (220.04,208.81) circle (  2.85);
\definecolor{drawColor}{RGB}{222,45,38}
\definecolor{fillColor}{RGB}{222,45,38}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (188.02,170.81) circle (  2.85);
\definecolor{drawColor}{gray}{0.59}
\definecolor{fillColor}{gray}{0.59}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (213.13,132.82) circle (  2.85);
\definecolor{drawColor}{RGB}{54,144,192}
\definecolor{fillColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (214.05, 94.83) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (218.58, 56.83) circle (  2.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.69, 54.93) --
	(223.69, 58.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.69, 56.83) --
	(213.47, 56.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.47, 54.93) --
	(213.47, 58.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.72, 92.93) --
	(214.72, 96.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.72, 94.83) --
	(213.37, 94.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.37, 92.93) --
	(213.37, 96.72);
\definecolor{drawColor}{gray}{0.59}

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.83,130.92) --
	(214.83,134.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.83,132.82) --
	(211.43,132.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.43,130.92) --
	(211.43,134.72);
\definecolor{drawColor}{RGB}{222,45,38}

\path[draw=drawColor,line width= 0.6pt,line join=round] (196.84,168.91) --
	(196.84,172.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (196.84,170.81) --
	(179.19,170.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (179.19,168.91) --
	(179.19,172.71);
\definecolor{drawColor}{gray}{0.59}

\path[draw=drawColor,line width= 0.6pt,line join=round] (270.69,206.91) --
	(270.69,210.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (270.69,208.81) --
	(169.39,208.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (169.39,206.91) --
	(169.39,210.71);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 0.6pt,line join=round] (238.71,244.90) --
	(238.71,248.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (238.71,246.80) --
	(215.48,246.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] (215.48,244.90) --
	(215.48,248.70);
\definecolor{drawColor}{RGB}{222,45,38}

\path[draw=drawColor,line width= 0.6pt,line join=round] (192.56,282.90) --
	(192.56,286.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (192.56,284.80) --
	(143.80,284.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.80,282.90) --
	(143.80,286.70);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 0.6pt,line join=round] (215.43,320.89) --
	(215.43,324.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (215.43,322.79) --
	(214.05,322.79);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.05,320.89) --
	(214.05,324.69);
\definecolor{drawColor}{gray}{0.59}

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.64,358.88) --
	(220.64,362.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.64,360.78) --
	(184.07,360.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (184.07,358.88) --
	(184.07,362.68);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.32,396.88) --
	(230.32,400.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.32,398.78) --
	(215.48,398.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (215.48,396.88) --
	(215.48,400.68);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.46, 34.03) --
	(137.46,421.57);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 53.53) {World GDP Growth$_{t}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35, 91.52) {Resource Rents/GDP$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,129.51) {Democracy$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,167.51) {Ln(Inflation)$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,205.50) {Upper Income};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,243.50) {Number of conflicts$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,281.49) {Area$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,319.48) {Duration$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,357.48) {Intensity$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (130.35,395.47) {Ln(Min. Capital Dist.)$_{t-1}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.46, 34.03) --
	(277.03, 34.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (174.95, 20.31) {-4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (213.36, 20.31) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (251.77, 20.31) {4};
\end{scope}
\end{tikzpicture}

### 2016-01-23 LaTeX/TeX/Manuscript/Graphics/mCapSimPlot.tex
reorg for final submission to jcr

--- 2014-10-06 LaTeX/mCapSimPlot.tex
@@
-% Created by tikzDevice version 0.7.0 on 2014-10-06 19:44:45
+% Created by tikzDevice version 0.7.0 on 2014-10-09 04:51:37
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,105.62) --
-	( 60.61,108.24) --
-	( 64.85,109.70) --
-	( 64.98,109.74) --
-	( 78.30,114.31) --
-	( 86.71,117.20) --
-	( 92.34,119.13) --
-	( 95.59,120.24) --
-	(101.92,122.42) --
-	(110.88,125.49) --
-	(154.64,140.51) --
-	(158.01,141.66) --
-	(171.43,146.26) --
-	(178.49,148.69) --
-	(187.92,151.92) --
-	(192.71,153.57) --
-	(195.62,154.56) --
-	(195.71,154.59) --
-	(196.35,154.81) --
-	(198.04,155.39) --
-	(199.87,156.02) --
-	(204.99,157.78) --
-	(205.19,157.85) --
-	(209.65,159.38) --
-	(211.50,160.01) --
-	(215.87,161.51) --
-	(217.33,162.01) --
-	(217.43,162.05) --
-	(217.68,162.13) --
-	(218.17,162.30) --
-	(220.17,162.99) --
-	(220.33,163.04) --
-	(220.93,163.25) --
-	(221.63,163.49) --
-	(222.58,163.81) --
-	(223.29,164.06) --
-	(223.54,164.14) --
-	(223.59,164.16) --
-	(224.00,164.30) --
-	(229.14,166.07) --
-	(231.15,166.76) --
-	(231.34,166.82) --
-	(232.39,167.18) --
-	(233.34,167.51) --
-	(234.25,167.82) --
-	(235.24,168.16) --
-	(236.22,168.49) --
-	(237.40,168.90) --
-	(237.41,168.90) --
-	(239.29,169.55) --
-	(239.31,169.55) --
-	(240.03,169.80) --
-	(240.80,170.06) --
-	(241.27,170.23) --
-	(241.65,170.36) --
-	(242.95,170.80) --
-	(244.78,171.43) --
-	(248.30,172.64) --
-	(249.74,173.13) --
-	(250.22,173.30) --
-	(250.38,173.35) --
-	(250.69,173.46) --
-	(251.97,173.90) --
-	(252.46,174.07) --
-	(253.69,174.49) --
-	(253.89,174.55) --
-	(254.34,174.71) --
-	(255.74,175.19) --
-	(256.94,175.60) --
-	(258.99,176.31) --
-	(260.08,176.68) --
-	(260.16,176.71) --
-	(261.39,177.13) --
-	(262.57,177.53) --
-	(263.47,177.84) --
-	(264.14,178.07) --
-	(264.43,178.17) --
-	(264.94,178.35) --
-	(265.11,178.40) --
-	(265.48,178.53) --
-	(265.54,178.55) --
-	(266.69,178.95) --
-	(266.70,178.95) --
-	(267.74,179.31) --
-	(267.83,179.34) --
-	(267.95,179.38) --
-	(268.15,179.45) --
-	(268.32,179.51) --
-	(268.51,179.57) --
-	(268.75,179.66) --
-	(269.12,179.78) --
-	(269.30,179.84) --
-	(269.75,180.00) --
-	(269.91,180.05) --
-	(271.51,180.60) --
-	(272.31,180.88) --
-	(272.40,180.91) --
-	(272.91,181.08) --
-	(273.01,181.11) --
-	(273.29,181.21) --
-	(273.48,181.28) --
-	(274.31,181.56) --
-	(274.85,181.75) --
-	(274.88,181.76) --
-	(275.50,181.97) --
-	(276.03,182.15) --
-	(276.14,182.19) --
-	(276.73,182.39) --
-	(276.77,182.41) --
-	(277.28,182.58) --
-	(277.37,182.61) --
-	(278.83,183.11) --
-	(278.93,183.15) --
-	(278.99,183.17) --
-	(279.03,183.18) --
-	(279.36,183.30) --
-	(279.83,183.46) --
-	(279.90,183.48) --
-	(280.21,183.59) --
-	(280.36,183.64) --
-	(280.41,183.66) --
-	(280.47,183.68) --
-	(280.50,183.68) --
-	(280.60,183.72) --
-	(280.63,183.73) --
-	(281.16,183.91) --
-	(281.52,184.03) --
-	(281.60,184.06) --
-	(283.10,184.58) --
-	(283.28,184.64) --
-	(283.34,184.66) --
-	(283.74,184.80) --
-	(283.80,184.82) --
-	(284.26,184.97) --
-	(284.43,185.03) --
-	(284.75,185.14) --
-	(284.80,185.16) --
-	(284.81,185.16) --
-	(284.81,185.16) --
-	(284.84,185.18) --
-	(284.88,185.19) --
-	(285.44,185.38) --
-	(285.67,185.46) --
-	(286.04,185.59) --
-	(286.70,185.81) --
-	(286.95,185.90) --
-	(287.76,186.18) --
-	(288.16,186.31) --
-	(288.45,186.41) --
-	(288.86,186.55) --
-	(289.03,186.61) --
-	(289.13,186.65) --
-	(289.30,186.70) --
-	(289.61,186.81) --
-	(289.71,186.85) --
-	(289.99,186.94) --
-	(290.44,187.10) --
-	(291.29,187.39) --
-	(291.45,187.44) --
-	(291.58,187.49) --
-	(292.20,187.70) --
-	(292.36,187.75) --
-	(292.77,187.89) --
-	(292.78,187.90) --
-	(292.85,187.92) --
-	(292.94,187.95) --
-	(293.49,188.14) --
-	(293.61,188.18) --
-	(293.90,188.28) --
-	(293.94,188.30) --
-	(295.12,188.70) --
-	(295.85,188.95) --
-	(296.61,189.21) --
-	(297.11,189.38) --
-	(297.99,189.68) --
-	(298.09,189.72) --
-	(298.13,189.74) --
-	(298.21,189.76) --
-	(298.45,189.84) --
-	(298.48,189.85) --
-	(298.71,189.93) --
-	(298.89,190.00) --
-	(299.22,190.11) --
-	(300.07,190.40) --
-	(300.69,190.61) --
-	(301.34,190.83) --
-	(301.81,191.00) --
-	(301.86,191.01) --
-	(302.06,191.08) --
-	(302.08,191.09) --
-	(302.20,191.13) --
-	(302.30,191.16) --
-	(302.45,191.22) --
-	(302.52,191.24) --
-	(302.61,191.27) --
-	(302.89,191.37) --
-	(302.93,191.38) --
-	(303.17,191.46) --
-	(304.10,191.78) --
-	(304.31,191.85) --
-	(304.47,191.91) --
-	(304.48,191.91) --
-	(304.60,191.95) --
-	(304.68,191.98) --
-	(305.11,192.13) --
-	(305.28,192.19) --
-	(305.76,192.35) --
-	(305.86,192.39) --
-	(306.15,192.49) --
-	(307.03,192.79) --
-	(307.16,192.83) --
-	(307.37,192.90) --
-	(308.42,193.27) --
-	(308.63,193.34) --
-	(308.79,193.39) --
-	(309.08,193.49) --
-	(309.55,193.65) --
-	(309.72,193.71) --
-	(310.36,193.93) --
-	(310.45,193.96) --
-	(310.80,194.08) --
-	(310.98,194.14) --
-	(311.09,194.18) --
-	(311.49,194.32) --
-	(311.71,194.39) --
-	(311.87,194.45) --
-	(312.39,194.63) --
-	(312.68,194.73) --
-	(312.75,194.75) --
-	(314.09,195.21) --
-	(314.12,195.22) --
-	(314.55,195.37) --
-	(314.84,195.47) --
-	(315.05,195.54) --
-	(315.28,195.62) --
-	(315.54,195.71) --
-	(315.61,195.73) --
-	(315.65,195.75) --
-	(316.29,195.97) --
-	(316.37,195.99) --
-	(316.58,196.06) --
-	(316.61,196.07) --
-	(316.72,196.11) --
-	(317.13,196.25) --
-	(318.60,196.76) --
-	(319.14,196.94) --
-	(320.71,197.48) --
-	(321.34,197.70) --
-	(321.47,197.74) --
-	(322.56,198.12) --
-	(322.64,198.14) --
-	(322.93,198.24) --
-	(323.98,198.60) --
-	(324.06,198.63) --
-	(324.53,198.79) --
-	(324.82,198.89) --
-	(325.46,199.11) --
-	(325.85,199.24) --
-	(325.87,199.25) --
-	(325.91,199.27) --
-	(326.16,199.35) --
-	(326.46,199.45) --
-	(327.01,199.64) --
-	(327.50,199.81) --
-	(327.78,199.91) --
-	(328.37,200.11) --
-	(328.92,200.30) --
-	(330.17,200.73) --
-	(330.38,200.80) --
-	(330.88,200.97) --
-	(333.53,201.88) --
-	(333.56,201.89) --
-	(333.69,201.94) --
-	(333.82,201.98) --
-	(333.83,201.98) --
-	(335.38,202.51) --
-	(335.47,202.55) --
-	(337.65,203.29) --
-	(338.50,203.58) --
-	(338.83,203.70) --
-	(338.87,203.71) --
-	(339.04,203.77) --
-	(339.21,203.83) --
-	(339.40,203.89) --
-	(339.55,203.94) --
-	(339.76,204.02) --
-	(339.84,204.04) --
-	(340.15,204.15) --
-	(340.28,204.20) --
-	(340.65,204.32) --
-	(341.52,204.62) --
-	(342.53,204.97) --
-	(343.79,205.40) --
-	(343.95,205.45) --
-	(345.11,205.85) --
-	(345.20,205.89) --
-	(345.78,206.08) --
-	(346.49,206.33) --
-	(346.80,206.43) --
-	(346.94,206.48) --
-	(347.30,206.60) --
-	(348.63,207.06) --
-	(348.84,207.13) --
-	(349.59,207.39) --
-	(350.01,207.53) --
-	(350.27,207.62) --
-	(350.57,207.73) --
-	(351.61,208.08) --
-	(352.50,208.39) --
-	(354.60,209.11) --
-	(354.77,209.17) --
-	(355.03,209.26) --
-	(355.06,209.27) --
-	(355.38,209.38) --
-	(355.44,209.40) --
-	(355.66,209.47) --
-	(355.69,209.48) --
-	(356.06,209.61) --
-	(356.08,209.62) --
-	(356.57,209.78) --
-	(356.86,209.88) --
-	(356.99,209.93) --
-	(357.04,209.94) --
-	(357.10,209.97) --
-	(357.28,210.03) --
-	(357.68,210.17) --
-	(357.71,210.18) --
-	(358.36,210.40) --
-	(358.45,210.43) --
-	(358.80,210.55) --
-	(359.58,210.82) --
-	(360.14,211.01) --
-	(360.17,211.02) --
-	(360.28,211.06) --
-	(360.68,211.20) --
-	(362.54,211.83) --
-	(362.92,211.96) --
-	(362.99,211.99) --
-	(362.99,211.99) --
-	(363.68,212.22) --
-	(363.71,212.23) --
-	(364.25,212.42) --
-	(364.57,212.53) --
-	(364.77,212.60) --
-	(365.00,212.68) --
-	(365.26,212.76) --
-	(365.84,212.96) --
-	(365.84,212.96) --
-	(365.92,212.99) --
-	(366.04,213.03) --
-	(366.47,213.18) --
-	(367.05,213.38) --
-	(368.20,213.78) --
-	(368.39,213.84) --
-	(368.50,213.88) --
-	(370.21,214.46) --
-	(371.17,214.79) --
-	(371.58,214.94) --
-	(372.02,215.09) --
-	(373.58,215.62) --
-	(376.96,216.78) --
-	(378.52,217.32) --
-	(383.85,219.15) --
-	(384.44,219.35) --
-	(384.92,219.51) --
-	(385.30,219.64) --
-	(385.73,219.79) --
-	(385.96,219.87) --
-	(386.70,220.12) --
-	(386.81,220.16) --
-	(387.17,220.28) --
-	(387.19,220.29) --
-	(387.24,220.31) --
-	(387.39,220.36) --
-	(387.67,220.46) --
-	(388.26,220.66) --
-	(389.16,220.97) --
-	(389.82,221.19) --
-	(390.40,221.39) --
-	(390.44,221.41) --
-	(390.79,221.53) --
-	(391.07,221.62) --
-	(395.16,223.02) --
-	(396.00,223.31) --
-	(396.15,223.37) --
-	(403.52,225.89) --
-	(404.02,226.07);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,103.03) --
+	( 60.61,105.88) --
+	( 64.85,107.46) --
+	( 64.98,107.51) --
+	( 78.30,112.49) --
+	( 86.71,115.63) --
+	( 92.34,117.73) --
+	( 95.59,118.94) --
+	(101.92,121.31) --
+	(110.88,124.66) --
+	(154.64,141.01) --
+	(158.01,142.26) --
+	(171.43,147.28) --
+	(178.49,149.91) --
+	(187.92,153.44) --
+	(192.71,155.23) --
+	(195.62,156.31) --
+	(195.71,156.34) --
+	(196.35,156.58) --
+	(198.04,157.22) --
+	(199.87,157.90) --
+	(204.99,159.81) --
+	(205.19,159.89) --
+	(209.65,161.55) --
+	(211.50,162.24) --
+	(215.87,163.88) --
+	(217.33,164.42) --
+	(217.43,164.46) --
+	(217.68,164.55) --
+	(218.17,164.74) --
+	(220.17,165.48) --
+	(220.33,165.54) --
+	(220.93,165.77) --
+	(221.63,166.03) --
+	(222.58,166.39) --
+	(223.29,166.65) --
+	(223.54,166.74) --
+	(223.59,166.76) --
+	(224.00,166.92) --
+	(229.14,168.84) --
+	(231.15,169.59) --
+	(231.34,169.66) --
+	(232.39,170.05) --
+	(233.34,170.41) --
+	(234.24,170.74) --
+	(235.24,171.11) --
+	(236.22,171.48) --
+	(237.40,171.92) --
+	(237.41,171.93) --
+	(239.29,172.63) --
+	(239.31,172.63) --
+	(240.03,172.90) --
+	(240.80,173.19) --
+	(241.27,173.36) --
+	(241.65,173.51) --
+	(242.95,173.99) --
+	(244.78,174.68) --
+	(248.30,175.99) --
+	(249.74,176.53) --
+	(250.22,176.71) --
+	(250.38,176.77) --
+	(250.69,176.88) --
+	(251.97,177.36) --
+	(252.46,177.55) --
+	(253.69,178.00) --
+	(253.89,178.08) --
+	(254.34,178.25) --
+	(255.73,178.77) --
+	(256.94,179.22) --
+	(258.99,179.99) --
+	(260.08,180.39) --
+	(260.16,180.42) --
+	(261.39,180.88) --
+	(262.57,181.32) --
+	(263.47,181.66) --
+	(264.14,181.91) --
+	(264.43,182.02) --
+	(264.94,182.21) --
+	(265.11,182.27) --
+	(265.48,182.41) --
+	(265.54,182.43) --
+	(266.69,182.86) --
+	(266.70,182.87) --
+	(267.74,183.26) --
+	(267.83,183.29) --
+	(267.95,183.33) --
+	(268.15,183.41) --
+	(268.32,183.47) --
+	(268.51,183.54) --
+	(268.75,183.63) --
+	(269.12,183.77) --
+	(269.30,183.84) --
+	(269.75,184.01) --
+	(269.91,184.06) --
+	(271.51,184.66) --
+	(272.31,184.96) --
+	(272.40,184.99) --
+	(272.91,185.18) --
+	(273.01,185.22) --
+	(273.29,185.33) --
+	(273.48,185.40) --
+	(274.31,185.71) --
+	(274.85,185.91) --
+	(274.88,185.92) --
+	(275.50,186.15) --
+	(276.03,186.35) --
+	(276.14,186.39) --
+	(276.73,186.61) --
+	(276.77,186.63) --
+	(277.28,186.82) --
+	(277.37,186.85) --
+	(278.83,187.40) --
+	(278.93,187.44) --
+	(278.99,187.46) --
+	(279.03,187.47) --
+	(279.36,187.60) --
+	(279.83,187.77) --
+	(279.90,187.80) --
+	(280.21,187.91) --
+	(280.36,187.97) --
+	(280.41,187.99) --
+	(280.47,188.01) --
+	(280.50,188.02) --
+	(280.60,188.06) --
+	(280.63,188.07) --
+	(281.16,188.27) --
+	(281.52,188.40) --
+	(281.60,188.43) --
+	(283.10,188.99) --
+	(283.28,189.06) --
+	(283.34,189.08) --
+	(283.74,189.23) --
+	(283.80,189.25) --
+	(284.26,189.42) --
+	(284.43,189.49) --
+	(284.75,189.61) --
+	(284.80,189.63) --
+	(284.81,189.63) --
+	(284.81,189.63) --
+	(284.84,189.64) --
+	(284.88,189.66) --
+	(285.44,189.87) --
+	(285.67,189.95) --
+	(286.04,190.09) --
+	(286.70,190.34) --
+	(286.95,190.43) --
+	(287.76,190.74) --
+	(288.16,190.88) --
+	(288.45,190.99) --
+	(288.86,191.14) --
+	(289.03,191.21) --
+	(289.13,191.24) --
+	(289.30,191.31) --
+	(289.61,191.42) --
+	(289.71,191.46) --
+	(289.99,191.56) --
+	(290.44,191.73) --
+	(291.29,192.05) --
+	(291.45,192.11) --
+	(291.58,192.16) --
+	(292.20,192.39) --
+	(292.36,192.45) --
+	(292.77,192.60) --
+	(292.78,192.61) --
+	(292.85,192.64) --
+	(292.94,192.67) --
+	(293.49,192.88) --
+	(293.61,192.92) --
+	(293.90,193.03) --
+	(293.94,193.04) --
+	(295.12,193.48) --
+	(295.85,193.76) --
+	(296.61,194.04) --
+	(297.11,194.23) --
+	(297.99,194.55) --
+	(298.09,194.59) --
+	(298.13,194.61) --
+	(298.21,194.64) --
+	(298.45,194.73) --
+	(298.48,194.74) --
+	(298.71,194.82) --
+	(298.89,194.89) --
+	(299.22,195.01) --
+	(300.07,195.33) --
+	(300.69,195.56) --
+	(301.34,195.81) --
+	(301.81,195.98) --
+	(301.86,196.00) --
+	(302.06,196.07) --
+	(302.08,196.08) --
+	(302.20,196.13) --
+	(302.30,196.16) --
+	(302.45,196.22) --
+	(302.52,196.25) --
+	(302.61,196.28) --
+	(302.89,196.39) --
+	(302.93,196.40) --
+	(303.17,196.49) --
+	(304.10,196.84) --
+	(304.31,196.92) --
+	(304.47,196.98) --
+	(304.48,196.98) --
+	(304.60,197.02) --
+	(304.68,197.06) --
+	(305.11,197.22) --
+	(305.28,197.28) --
+	(305.76,197.46) --
+	(305.86,197.49) --
+	(306.15,197.60) --
+	(307.03,197.93) --
+	(307.16,197.98) --
+	(307.37,198.06) --
+	(308.42,198.45) --
+	(308.63,198.53) --
+	(308.79,198.59) --
+	(309.08,198.70) --
+	(309.55,198.87) --
+	(309.72,198.94) --
+	(310.36,199.18) --
+	(310.45,199.21) --
+	(310.80,199.34) --
+	(310.98,199.41) --
+	(311.09,199.45) --
+	(311.49,199.60) --
+	(311.71,199.68) --
+	(311.87,199.74) --
+	(312.39,199.93) --
+	(312.68,200.04) --
+	(312.75,200.07) --
+	(314.09,200.57) --
+	(314.12,200.58) --
+	(314.55,200.74) --
+	(314.84,200.85) --
+	(315.05,200.93) --
+	(315.28,201.01) --
+	(315.54,201.11) --
+	(315.61,201.14) --
+	(315.65,201.15) --
+	(316.29,201.39) --
+	(316.37,201.42) --
+	(316.58,201.50) --
+	(316.61,201.51) --
+	(316.72,201.55) --
+	(317.13,201.71) --
+	(318.60,202.25) --
+	(319.14,202.45) --
+	(320.71,203.04) --
+	(321.34,203.28) --
+	(321.47,203.33) --
+	(322.56,203.73) --
+	(322.64,203.76) --
+	(322.93,203.87) --
+	(323.98,204.26) --
+	(324.06,204.29) --
+	(324.53,204.47) --
+	(324.82,204.58) --
+	(325.46,204.82) --
+	(325.85,204.96) --
+	(325.87,204.97) --
+	(325.91,204.99) --
+	(326.16,205.08) --
+	(326.46,205.19) --
+	(327.01,205.40) --
+	(327.50,205.58) --
+	(327.78,205.68) --
+	(328.37,205.91) --
+	(328.92,206.11) --
+	(330.17,206.58) --
+	(330.38,206.66) --
+	(330.88,206.84) --
+	(333.53,207.83) --
+	(333.56,207.84) --
+	(333.69,207.89) --
+	(333.82,207.94) --
+	(333.83,207.94) --
+	(335.38,208.52) --
+	(335.47,208.56) --
+	(337.65,209.37) --
+	(338.50,209.69) --
+	(338.83,209.81) --
+	(338.87,209.83) --
+	(339.04,209.89) --
+	(339.21,209.95) --
+	(339.40,210.03) --
+	(339.55,210.08) --
+	(339.76,210.16) --
+	(339.84,210.19) --
+	(340.15,210.31) --
+	(340.28,210.35) --
+	(340.65,210.49) --
+	(341.52,210.82) --
+	(342.53,211.20) --
+	(343.79,211.66) --
+	(343.95,211.72) --
+	(345.11,212.16) --
+	(345.20,212.19) --
+	(345.78,212.41) --
+	(346.49,212.67) --
+	(346.80,212.79) --
+	(346.94,212.84) --
+	(347.30,212.98) --
+	(348.63,213.47) --
+	(348.84,213.55) --
+	(349.59,213.83) --
+	(350.01,213.99) --
+	(350.27,214.09) --
+	(350.57,214.20) --
+	(351.61,214.59) --
+	(352.50,214.92) --
+	(354.60,215.70) --
+	(354.77,215.77) --
+	(355.03,215.86) --
+	(355.06,215.88) --
+	(355.38,215.99) --
+	(355.44,216.02) --
+	(355.66,216.10) --
+	(355.69,216.11) --
+	(356.06,216.25) --
+	(356.08,216.25) --
+	(356.57,216.44) --
+	(356.86,216.55) --
+	(356.99,216.60) --
+	(357.04,216.61) --
+	(357.10,216.64) --
+	(357.28,216.70) --
+	(357.68,216.85) --
+	(357.71,216.86) --
+	(358.36,217.11) --
+	(358.45,217.14) --
+	(358.80,217.27) --
+	(359.58,217.56) --
+	(360.14,217.77) --
+	(360.17,217.78) --
+	(360.28,217.83) --
+	(360.68,217.98) --
+	(362.54,218.67) --
+	(362.92,218.81) --
+	(362.99,218.84) --
+	(362.99,218.84) --
+	(363.68,219.09) --
+	(363.71,219.11) --
+	(364.25,219.31) --
+	(364.57,219.43) --
+	(364.77,219.50) --
+	(365.00,219.59) --
+	(365.26,219.68) --
+	(365.84,219.90) --
+	(365.84,219.90) --
+	(365.92,219.93) --
+	(366.04,219.98) --
+	(366.47,220.14) --
+	(367.05,220.35) --
+	(368.20,220.78) --
+	(368.39,220.85) --
+	(368.50,220.90) --
+	(370.21,221.53) --
+	(371.17,221.89) --
+	(371.58,222.05) --
+	(372.02,222.21) --
+	(373.58,222.79) --
+	(376.96,224.06) --
+	(378.52,224.64) --
+	(383.85,226.63) --
+	(384.44,226.85) --
+	(384.92,227.03) --
+	(385.30,227.17) --
+	(385.73,227.33) --
+	(385.96,227.42) --
+	(386.70,227.69) --
+	(386.81,227.74) --
+	(387.17,227.87) --
+	(387.19,227.88) --
+	(387.24,227.89) --
+	(387.39,227.95) --
+	(387.67,228.06) --
+	(388.26,228.28) --
+	(389.16,228.61) --
+	(389.82,228.86) --
+	(390.40,229.08) --
+	(390.44,229.09) --
+	(390.79,229.22) --
+	(391.07,229.32) --
+	(395.16,230.85) --
+	(396.00,231.17) --
+	(396.15,231.23) --
+	(403.52,233.98) --
+	(404.02,234.17);
 \definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}
 
-\path[fill=fillColor,fill opacity=0.30] ( 52.97,165.20) --
-	( 60.61,166.06) --
-	( 64.85,166.50) --
-	( 64.98,166.52) --
-	( 78.30,168.34) --
-	( 86.71,169.62) --
-	( 92.34,170.49) --
-	( 95.59,171.09) --
-	(101.92,171.91) --
-	(110.88,173.03) --
-	(154.64,179.87) --
-	(158.01,180.61) --
-	(171.43,182.79) --
-	(178.49,184.14) --
-	(187.92,186.16) --
-	(192.71,186.96) --
-	(195.62,187.49) --
-	(195.71,187.52) --
-	(196.35,187.67) --
-	(198.04,187.95) --
-	(199.87,188.32) --
-	(204.99,189.26) --
-	(205.19,189.29) --
-	(209.65,190.35) --
-	(211.50,190.74) --
-	(215.87,191.88) --
-	(217.33,192.18) --
-	(217.43,192.18) --
-	(217.68,192.24) --
-	(218.17,192.39) --
-	(220.17,192.85) --
-	(220.33,192.86) --
-	(220.93,193.03) --
-	(221.63,193.24) --
-	(222.58,193.40) --
-	(223.29,193.54) --
-	(223.54,193.60) --
-	(223.59,193.62) --
-	(224.00,193.67) --
-	(229.14,194.98) --
-	(231.15,195.48) --
-	(231.34,195.52) --
-	(232.39,195.71) --
-	(233.34,195.91) --
-	(234.25,196.12) --
-	(235.24,196.41) --
-	(236.22,196.59) --
-	(237.40,196.88) --
-	(237.41,196.88) --
-	(239.29,197.35) --
-	(239.31,197.35) --
-	(240.03,197.54) --
-	(240.80,197.71) --
-	(241.27,197.83) --
-	(241.65,197.94) --
-	(242.95,198.33) --
-	(244.78,198.83) --
-	(248.30,199.74) --
-	(249.74,200.06) --
-	(250.22,200.25) --
-	(250.38,200.30) --
-	(250.69,200.38) --
-	(251.97,200.79) --
-	(252.46,200.89) --
-	(253.69,201.25) --
-	(253.89,201.30) --
-	(254.34,201.47) --
-	(255.74,201.84) --
-	(256.94,202.18) --
-	(258.99,202.81) --
-	(260.08,203.21) --
-	(260.16,203.23) --
-	(261.39,203.62) --
-	(262.57,204.01) --
-	(263.47,204.17) --
-	(264.14,204.36) --
-	(264.43,204.44) --
-	(264.94,204.64) --
-	(265.11,204.71) --
-	(265.48,204.84) --
-	(265.54,204.86) --
-	(266.69,205.27) --
-	(266.70,205.27) --
-	(267.74,205.67) --
-	(267.83,205.69) --
-	(267.95,205.73) --
-	(268.15,205.80) --
-	(268.32,205.86) --
-	(268.51,205.91) --
-	(268.75,206.03) --
-	(269.12,206.13) --
-	(269.30,206.19) --
-	(269.75,206.29) --
-	(269.91,206.34) --
-	(271.51,206.93) --
-	(272.31,207.26) --
-	(272.40,207.29) --
-	(272.91,207.46) --
-	(273.01,207.49) --
-	(273.29,207.60) --
-	(273.48,207.63) --
-	(274.31,207.88) --
-	(274.85,208.05) --
-	(274.88,208.05) --
-	(275.50,208.31) --
-	(276.03,208.51) --
-	(276.14,208.54) --
-	(276.73,208.71) --
-	(276.77,208.72) --
-	(277.28,208.92) --
-	(277.37,208.95) --
-	(278.83,209.44) --
-	(278.93,209.48) --
-	(278.99,209.50) --
-	(279.03,209.51) --
-	(279.36,209.57) --
-	(279.83,209.71) --
-	(279.90,209.72) --
-	(280.21,209.80) --
-	(280.36,209.87) --
-	(280.41,209.89) --
-	(280.47,209.91) --
-	(280.50,209.92) --
-	(280.60,209.95) --
-	(280.63,209.96) --
-	(281.16,210.14) --
-	(281.52,210.28) --
-	(281.60,210.32) --
-	(283.10,210.87) --
-	(283.28,210.96) --
-	(283.34,210.98) --
-	(283.74,211.11) --
-	(283.80,211.13) --
-	(284.26,211.28) --
-	(284.43,211.32) --
-	(284.75,211.44) --
-	(284.80,211.46) --
-	(284.81,211.46) --
-	(284.81,211.46) --
-	(284.84,211.48) --
-	(284.88,211.49) --
-	(285.44,211.69) --
-	(285.67,211.76) --
-	(286.04,211.88) --
-	(286.70,212.11) --
-	(286.95,212.19) --
-	(287.76,212.60) --
-	(288.16,212.75) --
-	(288.45,212.88) --
-	(288.86,212.98) --
-	(289.03,213.01) --
-	(289.13,213.03) --
-	(289.30,213.12) --
-	(289.61,213.30) --
-	(289.71,213.32) --
-	(289.99,213.40) --
-	(290.44,213.53) --
-	(291.29,213.87) --
-	(291.45,213.92) --
-	(291.58,213.96) --
-	(292.20,214.19) --
-	(292.36,214.26) --
-	(292.77,214.38) --
-	(292.78,214.39) --
-	(292.85,214.43) --
-	(292.94,214.45) --
-	(293.49,214.66) --
-	(293.61,214.72) --
-	(293.90,214.85) --
-	(293.94,214.86) --
-	(295.12,215.33) --
-	(295.85,215.63) --
-	(296.61,215.90) --
-	(297.11,216.10) --
-	(297.99,216.47) --
-	(298.09,216.52) --
-	(298.13,216.53) --
-	(298.21,216.57) --
-	(298.45,216.67) --
-	(298.48,216.68) --
-	(298.71,216.78) --
-	(298.89,216.86) --
-	(299.22,217.00) --
-	(300.07,217.37) --
-	(300.69,217.67) --
-	(301.34,217.95) --
-	(301.81,218.15) --
-	(301.86,218.17) --
-	(302.06,218.25) --
-	(302.08,218.25) --
-	(302.20,218.30) --
-	(302.30,218.33) --
-	(302.45,218.39) --
-	(302.52,218.41) --
-	(302.61,218.44) --
-	(302.89,218.54) --
-	(302.93,218.56) --
-	(303.17,218.62) --
-	(304.10,218.98) --
-	(304.31,219.07) --
-	(304.47,219.12) --
-	(304.48,219.12) --
-	(304.60,219.15) --
-	(304.68,219.18) --
-	(305.11,219.34) --
-	(305.28,219.40) --
-	(305.76,219.62) --
-	(305.86,219.66) --
-	(306.15,219.79) --
-	(307.03,220.15) --
-	(307.16,220.21) --
-	(307.37,220.28) --
-	(308.42,220.71) --
-	(308.63,220.77) --
-	(308.79,220.81) --
-	(309.08,220.91) --
-	(309.55,221.07) --
-	(309.72,221.11) --
-	(310.36,221.34) --
-	(310.45,221.38) --
-	(310.80,221.53) --
-	(310.98,221.58) --
-	(311.09,221.61) --
-	(311.49,221.78) --
-	(311.71,221.89) --
-	(311.87,221.97) --
-	(312.39,222.22) --
-	(312.68,222.34) --
-	(312.75,222.36) --
-	(314.09,222.97) --
-	(314.12,222.98) --
-	(314.55,223.10) --
-	(314.84,223.21) --
-	(315.05,223.29) --
-	(315.28,223.38) --
-	(315.54,223.48) --
-	(315.61,223.51) --
-	(315.65,223.53) --
-	(316.29,223.77) --
-	(316.37,223.80) --
-	(316.58,223.88) --
-	(316.61,223.90) --
-	(316.72,223.94) --
-	(317.13,224.10) --
-	(318.60,224.77) --
-	(319.14,224.99) --
-	(320.71,225.74) --
-	(321.34,226.00) --
-	(321.47,226.05) --
-	(322.56,226.60) --
-	(322.64,226.65) --
-	(322.93,226.81) --
-	(323.98,227.18) --
-	(324.06,227.23) --
-	(324.53,227.46) --
-	(324.82,227.58) --
-	(325.46,227.82) --
-	(325.85,227.92) --
-	(325.87,227.93) --
-	(325.91,227.95) --
-	(326.16,228.06) --
-	(326.46,228.20) --
-	(327.01,228.46) --
-	(327.50,228.65) --
-	(327.78,228.76) --
-	(328.37,229.01) --
-	(328.92,229.25) --
-	(330.17,229.78) --
-	(330.38,229.89) --
-	(330.88,230.12) --
-	(333.53,231.30) --
-	(333.56,231.31) --
-	(333.69,231.37) --
-	(333.82,231.43) --
-	(333.83,231.43) --
-	(335.38,232.11) --
-	(335.47,232.16) --
-	(337.65,233.11) --
-	(338.50,233.49) --
-	(338.83,233.64) --
-	(338.87,233.66) --
-	(339.04,233.73) --
-	(339.21,233.80) --
-	(339.40,233.89) --
-	(339.55,233.95) --
-	(339.76,234.05) --
-	(339.84,234.09) --
-	(340.15,234.23) --
-	(340.28,234.29) --
-	(340.65,234.46) --
-	(341.52,234.87) --
-	(342.53,235.38) --
-	(343.79,235.96) --
-	(343.95,236.03) --
-	(345.11,236.65) --
-	(345.20,236.70) --
-	(345.78,236.95) --
-	(346.49,237.30) --
-	(346.80,237.45) --
-	(346.94,237.52) --
-	(347.30,237.70) --
-	(348.63,238.33) --
-	(348.84,238.43) --
-	(349.59,238.82) --
-	(350.01,239.02) --
-	(350.27,239.13) --
-	(350.57,239.26) --
-	(351.61,239.72) --
-	(352.50,240.14) --
-	(354.60,241.18) --
-	(354.77,241.25) --
-	(355.03,241.37) --
-	(355.06,241.39) --
-	(355.38,241.55) --
-	(355.44,241.59) --
-	(355.66,241.70) --
-	(355.69,241.71) --
-	(356.06,241.93) --
-	(356.08,241.93) --
-	(356.57,242.19) --
-	(356.86,242.34) --
-	(356.99,242.41) --
-	(357.04,242.44) --
-	(357.10,242.47) --
-	(357.28,242.56) --
-	(357.68,242.77) --
-	(357.71,242.78) --
-	(358.36,243.06) --
-	(358.45,243.11) --
-	(358.80,243.27) --
-	(359.58,243.64) --
-	(360.14,243.89) --
-	(360.17,243.90) --
-	(360.28,243.94) --
-	(360.68,244.14) --
-	(362.54,245.11) --
-	(362.92,245.32) --
-	(362.99,245.36) --
-	(362.99,245.36) --
-	(363.68,245.73) --
-	(363.71,245.75) --
-	(364.25,246.04) --
-	(364.57,246.19) --
-	(364.77,246.29) --
-	(365.00,246.40) --
-	(365.26,246.54) --
-	(365.84,246.88) --
-	(365.84,246.88) --
-	(365.92,246.92) --
-	(366.04,246.98) --
-	(366.47,247.19) --
-	(367.05,247.46) --
-	(368.20,247.96) --
-	(368.39,248.07) --
-	(368.50,248.14) --
-	(370.21,248.93) --
-	(371.17,249.41) --
-	(371.58,249.67) --
-	(372.02,249.86) --
-	(373.58,250.61) --
-	(376.96,252.31) --
-	(378.52,252.97) --
-	(383.85,255.72) --
-	(384.44,256.00) --
-	(384.92,256.23) --
-	(385.30,256.42) --
-	(385.73,256.63) --
-	(385.96,256.74) --
-	(386.70,257.14) --
-	(386.81,257.19) --
-	(387.17,257.37) --
-	(387.19,257.37) --
-	(387.24,257.39) --
-	(387.39,257.47) --
-	(387.67,257.63) --
-	(388.26,257.95) --
-	(389.16,258.36) --
-	(389.82,258.71) --
-	(390.40,258.98) --
-	(390.44,259.01) --
-	(390.79,259.17) --
-	(391.07,259.30) --
-	(395.16,261.28) --
-	(396.00,261.69) --
-	(396.15,261.76) --
-	(403.52,265.67) --
+\path[fill=fillColor,fill opacity=0.30] ( 52.97,162.09) --
+	( 60.61,163.40) --
+	( 64.85,164.12) --
+	( 64.98,164.14) --
+	( 78.30,166.42) --
+	( 86.71,168.04) --
+	( 92.34,169.01) --
+	( 95.59,169.59) --
+	(101.92,170.70) --
+	(110.88,172.06) --
+	(154.64,179.67) --
+	(158.01,180.30) --
+	(171.43,182.97) --
+	(178.49,184.48) --
+	(187.92,186.36) --
+	(192.71,187.31) --
+	(195.62,187.86) --
+	(195.71,187.88) --
+	(196.35,187.99) --
+	(198.04,188.42) --
+	(199.87,188.91) --
+	(204.99,189.74) --
+	(205.19,189.76) --
+	(209.65,190.87) --
+	(211.50,191.30) --
+	(215.87,192.29) --
+	(217.33,192.57) --
+	(217.43,192.60) --
+	(217.68,192.66) --
+	(218.17,192.79) --
+	(220.17,193.36) --
+	(220.33,193.40) --
+	(220.93,193.57) --
+	(221.63,193.74) --
+	(222.58,193.90) --
+	(223.29,194.07) --
+	(223.54,194.12) --
+	(223.59,194.12) --
+	(224.00,194.20) --
+	(229.14,195.35) --
+	(231.15,195.91) --
+	(231.34,195.96) --
+	(232.39,196.26) --
+	(233.34,196.54) --
+	(234.24,196.77) --
+	(235.24,197.03) --
+	(236.22,197.29) --
+	(237.40,197.62) --
+	(237.41,197.63) --
+	(239.29,198.08) --
+	(239.31,198.09) --
+	(240.03,198.24) --
+	(240.80,198.41) --
+	(241.27,198.49) --
+	(241.65,198.60) --
+	(242.95,198.93) --
+	(244.78,199.36) --
+	(248.30,200.44) --
+	(249.74,200.85) --
+	(250.22,200.95) --
+	(250.38,200.98) --
+	(250.69,201.04) --
+	(251.97,201.34) --
+	(252.46,201.45) --
+	(253.69,201.74) --
+	(253.89,201.77) --
+	(254.34,201.93) --
+	(255.73,202.30) --
+	(256.94,202.63) --
+	(258.99,203.26) --
+	(260.08,203.53) --
+	(260.16,203.56) --
+	(261.39,203.93) --
+	(262.57,204.32) --
+	(263.47,204.60) --
+	(264.14,204.79) --
+	(264.43,204.83) --
+	(264.94,204.99) --
+	(265.11,205.04) --
+	(265.48,205.19) --
+	(265.54,205.22) --
+	(266.69,205.53) --
+	(266.70,205.53) --
+	(267.74,205.91) --
+	(267.83,205.95) --
+	(267.95,205.98) --
+	(268.15,206.06) --
+	(268.32,206.13) --
+	(268.51,206.20) --
+	(268.75,206.30) --
+	(269.12,206.38) --
+	(269.30,206.42) --
+	(269.75,206.58) --
+	(269.91,206.63) --
+	(271.51,207.18) --
+	(272.31,207.50) --
+	(272.40,207.51) --
+	(272.91,207.57) --
+	(273.01,207.60) --
+	(273.29,207.71) --
+	(273.48,207.75) --
+	(274.31,208.12) --
+	(274.85,208.26) --
+	(274.88,208.27) --
+	(275.50,208.41) --
+	(276.03,208.59) --
+	(276.14,208.64) --
+	(276.73,208.88) --
+	(276.77,208.90) --
+	(277.28,209.09) --
+	(277.37,209.13) --
+	(278.83,209.65) --
+	(278.93,209.68) --
+	(278.99,209.70) --
+	(279.03,209.72) --
+	(279.36,209.80) --
+	(279.83,209.97) --
+	(279.90,209.99) --
+	(280.21,210.08) --
+	(280.36,210.11) --
+	(280.41,210.13) --
+	(280.47,210.14) --
+	(280.50,210.15) --
+	(280.60,210.19) --
+	(280.63,210.21) --
+	(281.16,210.43) --
+	(281.52,210.53) --
+	(281.60,210.56) --
+	(283.10,211.02) --
+	(283.28,211.07) --
+	(283.34,211.08) --
+	(283.74,211.19) --
+	(283.80,211.20) --
+	(284.26,211.35) --
+	(284.43,211.41) --
+	(284.75,211.52) --
+	(284.80,211.53) --
+	(284.81,211.53) --
+	(284.81,211.53) --
+	(284.84,211.54) --
+	(284.88,211.55) --
+	(285.44,211.71) --
+	(285.67,211.78) --
+	(286.04,211.92) --
+	(286.70,212.18) --
+	(286.95,212.27) --
+	(287.76,212.58) --
+	(288.16,212.69) --
+	(288.45,212.78) --
+	(288.86,212.95) --
+	(289.03,213.03) --
+	(289.13,213.07) --
+	(289.30,213.15) --
+	(289.61,213.29) --
+	(289.71,213.33) --
+	(289.99,213.42) --
+	(290.44,213.59) --
+	(291.29,213.88) --
+	(291.45,213.94) --
+	(291.58,213.99) --
+	(292.20,214.21) --
+	(292.36,214.25) --
+	(292.77,214.40) --
+	(292.78,214.41) --
+	(292.85,214.44) --
+	(292.94,214.46) --
+	(293.49,214.61) --
+	(293.61,214.65) --
+	(293.90,214.73) --
+	(293.94,214.74) --
+	(295.12,215.14) --
+	(295.85,215.49) --
+	(296.61,215.80) --
+	(297.11,216.00) --
+	(297.99,216.38) --
+	(298.09,216.43) --
+	(298.13,216.45) --
+	(298.21,216.47) --
+	(298.45,216.56) --
+	(298.48,216.57) --
+	(298.71,216.64) --
+	(298.89,216.70) --
+	(299.22,216.84) --
+	(300.07,217.14) --
+	(300.69,217.37) --
+	(301.34,217.66) --
+	(301.81,217.84) --
+	(301.86,217.86) --
+	(302.06,217.94) --
+	(302.08,217.95) --
+	(302.20,218.00) --
+	(302.30,218.03) --
+	(302.45,218.06) --
+	(302.52,218.09) --
+	(302.61,218.13) --
+	(302.89,218.23) --
+	(302.93,218.25) --
+	(303.17,218.34) --
+	(304.10,218.73) --
+	(304.31,218.82) --
+	(304.47,218.89) --
+	(304.48,218.89) --
+	(304.60,218.94) --
+	(304.68,218.97) --
+	(305.11,219.14) --
+	(305.28,219.20) --
+	(305.76,219.36) --
+	(305.86,219.40) --
+	(306.15,219.51) --
+	(307.03,219.82) --
+	(307.16,219.89) --
+	(307.37,219.97) --
+	(308.42,220.36) --
+	(308.63,220.42) --
+	(308.79,220.48) --
+	(309.08,220.60) --
+	(309.55,220.82) --
+	(309.72,220.92) --
+	(310.36,221.19) --
+	(310.45,221.22) --
+	(310.80,221.35) --
+	(310.98,221.44) --
+	(311.09,221.48) --
+	(311.49,221.65) --
+	(311.71,221.75) --
+	(311.87,221.82) --
+	(312.39,222.07) --
+	(312.68,222.15) --
+	(312.75,222.17) --
+	(314.09,222.65) --
+	(314.12,222.66) --
+	(314.55,222.83) --
+	(314.84,222.95) --
+	(315.05,223.02) --
+	(315.28,223.08) --
+	(315.54,223.19) --
+	(315.61,223.22) --
+	(315.65,223.23) --
+	(316.29,223.52) --
+	(316.37,223.54) --
+	(316.58,223.62) --
+	(316.61,223.63) --
+	(316.72,223.68) --
+	(317.13,223.86) --
+	(318.60,224.46) --
+	(319.14,224.72) --
+	(320.71,225.38) --
+	(321.34,225.64) --
+	(321.47,225.69) --
+	(322.56,226.14) --
+	(322.64,226.17) --
+	(322.93,226.29) --
+	(323.98,226.72) --
+	(324.06,226.76) --
+	(324.53,226.99) --
+	(324.82,227.14) --
+	(325.46,227.43) --
+	(325.85,227.62) --
+	(325.87,227.63) --
+	(325.91,227.65) --
+	(326.16,227.75) --
+	(326.46,227.88) --
+	(327.01,228.14) --
+	(327.50,228.33) --
+	(327.78,228.44) --
+	(328.37,228.70) --
+	(328.92,228.96) --
+	(330.17,229.49) --
+	(330.38,229.57) --
+	(330.88,229.79) --
+	(333.53,230.95) --
+	(333.56,230.96) --
+	(333.69,231.02) --
+	(333.82,231.08) --
+	(333.83,231.08) --
+	(335.38,231.89) --
+	(335.47,231.96) --
+	(337.65,233.01) --
+	(338.50,233.37) --
+	(338.83,233.52) --
+	(338.87,233.54) --
+	(339.04,233.62) --
+	(339.21,233.70) --
+	(339.40,233.78) --
+	(339.55,233.85) --
+	(339.76,233.95) --
+	(339.84,234.00) --
+	(340.15,234.14) --
+	(340.28,234.22) --
+	(340.65,234.42) --
+	(341.52,234.76) --
+	(342.53,235.21) --
+	(343.79,235.83) --
+	(343.95,235.91) --
+	(345.11,236.49) --
+	(345.20,236.55) --
+	(345.78,236.86) --
+	(346.49,237.19) --
+	(346.80,237.32) --
+	(346.94,237.39) --
+	(347.30,237.51) --
+	(348.63,238.07) --
+	(348.84,238.18) --
+	(349.59,238.55) --
+	(350.01,238.72) --
+	(350.27,238.85) --
+	(350.57,238.98) --
+	(351.61,239.40) --
+	(352.50,239.80) --
+	(354.60,240.89) --
+	(354.77,240.99) --
+	(355.03,241.14) --
+	(355.06,241.16) --
+	(355.38,241.33) --
+	(355.44,241.36) --
+	(355.66,241.45) --
+	(355.69,241.46) --
+	(356.06,241.68) --
+	(356.08,241.69) --
+	(356.57,241.88) --
+	(356.86,242.01) --
+	(356.99,242.06) --
+	(357.04,242.08) --
+	(357.10,242.09) --
+	(357.28,242.15) --
+	(357.68,242.37) --
+	(357.71,242.39) --
+	(358.36,242.69) --
+	(358.45,242.72) --
+	(358.80,242.92) --
+	(359.58,243.34) --
+	(360.14,243.58) --
+	(360.17,243.60) --
+	(360.28,243.66) --
+	(360.68,243.88) --
+	(362.54,244.78) --
+	(362.92,244.96) --
+	(362.99,245.00) --
+	(362.99,245.00) --
+	(363.68,245.31) --
+	(363.71,245.32) --
+	(364.25,245.59) --
+	(364.57,245.76) --
+	(364.77,245.86) --
+	(365.00,245.96) --
+	(365.26,246.10) --
+	(365.84,246.41) --
+	(365.84,246.41) --
+	(365.92,246.46) --
+	(366.04,246.52) --
+	(366.47,246.74) --
+	(367.05,247.06) --
+	(368.20,247.63) --
+	(368.39,247.72) --
+	(368.50,247.78) --
+	(370.21,248.64) --
+	(371.17,249.05) --
+	(371.58,249.26) --
+	(372.02,249.50) --
+	(373.58,250.26) --
+	(376.96,251.99) --
+	(378.52,252.81) --
+	(383.85,255.52) --
+	(384.44,255.80) --
+	(384.92,256.05) --
+	(385.30,256.25) --
+	(385.73,256.49) --
+	(385.96,256.60) --
+	(386.70,256.96) --
+	(386.81,256.99) --
+	(387.17,257.20) --
+	(387.19,257.21) --
+	(387.24,257.24) --
+	(387.39,257.33) --
+	(387.67,257.51) --
+	(388.26,257.85) --
+	(389.16,258.34) --
+	(389.82,258.69) --
+	(390.40,258.97) --
+	(390.44,258.99) --
+	(390.79,259.16) --
+	(391.07,259.29) --
+	(395.16,261.33) --
+	(396.00,261.71) --
+	(396.15,261.78) --
+	(403.52,265.72) --
 	(404.02,265.99) --
-	(404.02,186.16) --
-	(403.52,186.07) --
-	(396.15,184.62) --
-	(396.00,184.56) --
-	(395.16,184.43) --
-	(391.07,183.78) --
-	(390.79,183.76) --
-	(390.44,183.72) --
-	(390.40,183.71) --
-	(389.82,183.64) --
-	(389.16,183.56) --
-	(388.26,183.43) --
-	(387.67,183.32) --
-	(387.39,183.25) --
-	(387.24,183.21) --
-	(387.19,183.20) --
-	(387.17,183.20) --
-	(386.81,183.11) --
-	(386.70,183.09) --
-	(385.96,182.98) --
-	(385.73,182.95) --
-	(385.30,182.87) --
-	(384.92,182.82) --
-	(384.44,182.79) --
-	(383.85,182.69) --
-	(378.52,181.63) --
-	(376.96,181.35) --
-	(373.58,180.87) --
-	(372.02,180.66) --
-	(371.58,180.64) --
-	(371.17,180.60) --
-	(370.21,180.44) --
-	(368.50,180.16) --
-	(368.39,180.14) --
-	(368.20,180.08) --
-	(367.05,179.83) --
-	(366.47,179.68) --
-	(366.04,179.56) --
-	(365.92,179.53) --
-	(365.84,179.51) --
-	(365.84,179.51) --
-	(365.26,179.35) --
-	(365.00,179.28) --
-	(364.77,179.25) --
-	(364.57,179.24) --
-	(364.25,179.17) --
-	(363.71,179.04) --
-	(363.68,179.03) --
-	(362.99,178.85) --
-	(362.99,178.85) --
-	(362.92,178.84) --
-	(362.54,178.74) --
-	(360.68,178.40) --
-	(360.28,178.30) --
-	(360.17,178.31) --
-	(360.14,178.31) --
-	(359.58,178.27) --
-	(358.80,178.08) --
-	(358.45,178.01) --
-	(358.36,177.98) --
-	(357.71,177.80) --
-	(357.68,177.80) --
-	(357.28,177.74) --
-	(357.10,177.72) --
-	(357.04,177.72) --
-	(356.99,177.71) --
-	(356.86,177.70) --
-	(356.57,177.64) --
-	(356.08,177.49) --
-	(356.06,177.49) --
-	(355.69,177.37) --
-	(355.66,177.36) --
-	(355.44,177.32) --
-	(355.38,177.31) --
-	(355.06,177.26) --
-	(355.03,177.25) --
-	(354.77,177.22) --
-	(354.60,177.19) --
-	(352.50,176.92) --
-	(351.61,176.70) --
-	(350.57,176.49) --
-	(350.27,176.47) --
-	(350.01,176.37) --
-	(349.59,176.23) --
-	(348.84,176.03) --
-	(348.63,175.98) --
-	(347.30,175.74) --
-	(346.94,175.67) --
-	(346.80,175.64) --
-	(346.49,175.53) --
-	(345.78,175.33) --
-	(345.20,175.23) --
-	(345.11,175.20) --
-	(343.95,174.89) --
-	(343.79,174.84) --
-	(342.53,174.62) --
-	(341.52,174.45) --
-	(340.65,174.27) --
-	(340.28,174.16) --
-	(340.15,174.10) --
-	(339.84,174.03) --
-	(339.76,174.02) --
-	(339.55,173.99) --
-	(339.40,173.93) --
-	(339.21,173.87) --
-	(339.04,173.82) --
-	(338.87,173.77) --
-	(338.83,173.76) --
-	(338.50,173.69) --
-	(337.65,173.44) --
-	(335.47,172.96) --
-	(335.38,172.95) --
-	(333.83,172.52) --
-	(333.82,172.52) --
-	(333.69,172.48) --
-	(333.56,172.45) --
-	(333.53,172.44) --
-	(330.88,171.81) --
-	(330.38,171.72) --
-	(330.17,171.68) --
-	(328.92,171.37) --
-	(328.37,171.15) --
-	(327.78,170.98) --
-	(327.50,170.92) --
-	(327.01,170.77) --
-	(326.46,170.62) --
-	(326.16,170.57) --
-	(325.91,170.51) --
-	(325.87,170.51) --
-	(325.85,170.51) --
-	(325.46,170.40) --
-	(324.82,170.21) --
-	(324.53,170.21) --
-	(324.06,170.15) --
-	(323.98,170.13) --
-	(322.93,169.85) --
-	(322.64,169.82) --
-	(322.56,169.82) --
-	(321.47,169.46) --
-	(321.34,169.40) --
-	(320.71,169.24) --
-	(319.14,168.74) --
-	(318.60,168.64) --
-	(317.13,168.18) --
-	(316.72,168.05) --
-	(316.61,168.01) --
-	(316.58,168.00) --
-	(316.37,167.93) --
-	(316.29,167.90) --
-	(315.65,167.68) --
-	(315.61,167.67) --
-	(315.54,167.65) --
-	(315.28,167.58) --
-	(315.05,167.51) --
-	(314.84,167.42) --
-	(314.55,167.33) --
-	(314.12,167.22) --
-	(314.09,167.21) --
-	(312.75,166.87) --
-	(312.68,166.86) --
-	(312.39,166.79) --
-	(311.87,166.57) --
-	(311.71,166.51) --
-	(311.49,166.45) --
-	(311.09,166.35) --
-	(310.98,166.33) --
-	(310.80,166.29) --
-	(310.45,166.23) --
-	(310.36,166.21) --
-	(309.72,166.00) --
-	(309.55,165.96) --
-	(309.08,165.82) --
-	(308.79,165.72) --
-	(308.63,165.67) --
-	(308.42,165.62) --
-	(307.37,165.33) --
-	(307.16,165.25) --
-	(307.03,165.22) --
-	(306.15,165.04) --
-	(305.86,164.98) --
-	(305.76,164.96) --
-	(305.28,164.84) --
-	(305.11,164.79) --
-	(304.68,164.71) --
-	(304.60,164.69) --
-	(304.48,164.65) --
-	(304.47,164.64) --
-	(304.31,164.58) --
-	(304.10,164.53) --
-	(303.17,164.22) --
-	(302.93,164.15) --
-	(302.89,164.14) --
-	(302.61,164.07) --
-	(302.52,164.04) --
-	(302.45,164.03) --
-	(302.30,164.00) --
-	(302.20,163.98) --
-	(302.08,163.95) --
-	(302.06,163.95) --
-	(301.86,163.90) --
-	(301.81,163.89) --
-	(301.34,163.78) --
-	(300.69,163.54) --
-	(300.07,163.35) --
-	(299.22,163.00) --
-	(298.89,162.91) --
-	(298.71,162.85) --
-	(298.48,162.77) --
-	(298.45,162.76) --
-	(298.21,162.69) --
-	(298.13,162.66) --
-	(298.09,162.65) --
-	(297.99,162.62) --
-	(297.11,162.35) --
-	(296.61,162.22) --
-	(295.85,161.97) --
-	(295.12,161.73) --
-	(293.94,161.38) --
-	(293.90,161.37) --
-	(293.61,161.27) --
-	(293.49,161.22) --
-	(292.94,161.03) --
-	(292.85,161.01) --
-	(292.78,160.99) --
-	(292.77,160.98) --
-	(292.36,160.87) --
-	(292.20,160.82) --
-	(291.58,160.61) --
-	(291.45,160.57) --
-	(291.29,160.52) --
-	(290.44,160.26) --
-	(289.99,160.13) --
-	(289.71,160.04) --
-	(289.61,160.00) --
-	(289.30,159.87) --
-	(289.13,159.80) --
-	(289.03,159.75) --
-	(288.86,159.69) --
-	(288.45,159.56) --
-	(288.16,159.43) --
-	(287.76,159.26) --
-	(286.95,158.94) --
-	(286.70,158.84) --
-	(286.04,158.62) --
-	(285.67,158.49) --
-	(285.44,158.44) --
-	(284.88,158.24) --
-	(284.84,158.23) --
-	(284.81,158.22) --
-	(284.81,158.22) --
-	(284.80,158.21) --
-	(284.75,158.20) --
-	(284.43,158.12) --
-	(284.26,158.06) --
-	(283.80,157.92) --
-	(283.74,157.91) --
-	(283.34,157.81) --
-	(283.28,157.79) --
-	(283.10,157.72) --
-	(281.60,157.19) --
-	(281.52,157.15) --
-	(281.16,157.04) --
-	(280.63,156.85) --
-	(280.60,156.83) --
-	(280.50,156.79) --
-	(280.47,156.78) --
-	(280.41,156.75) --
-	(280.36,156.73) --
-	(280.21,156.68) --
-	(279.90,156.59) --
-	(279.83,156.58) --
-	(279.36,156.45) --
-	(279.03,156.32) --
-	(278.99,156.30) --
-	(278.93,156.27) --
-	(278.83,156.20) --
-	(277.37,155.69) --
-	(277.28,155.66) --
-	(276.77,155.47) --
-	(276.73,155.45) --
-	(276.14,155.25) --
-	(276.03,155.23) --
-	(275.50,155.09) --
-	(274.88,154.85) --
-	(274.85,154.84) --
-	(274.31,154.63) --
-	(273.48,154.33) --
-	(273.29,154.26) --
-	(273.01,154.14) --
-	(272.91,154.08) --
-	(272.40,153.94) --
-	(272.31,153.91) --
-	(271.51,153.68) --
-	(269.91,153.18) --
-	(269.75,153.12) --
-	(269.30,153.01) --
-	(269.12,152.95) --
-	(268.75,152.83) --
-	(268.51,152.72) --
-	(268.32,152.61) --
-	(268.15,152.54) --
-	(267.95,152.45) --
-	(267.83,152.40) --
-	(267.74,152.36) --
-	(266.70,151.94) --
-	(266.69,151.93) --
-	(265.54,151.50) --
-	(265.48,151.48) --
-	(265.11,151.39) --
-	(264.94,151.31) --
-	(264.43,151.11) --
-	(264.14,151.03) --
-	(263.47,150.81) --
-	(262.57,150.47) --
-	(261.39,150.00) --
-	(260.16,149.54) --
-	(260.08,149.51) --
-	(258.99,149.05) --
-	(256.94,148.31) --
-	(255.74,147.96) --
-	(254.34,147.35) --
-	(253.89,147.15) --
-	(253.69,147.06) --
-	(252.46,146.62) --
-	(251.97,146.47) --
-	(250.69,145.91) --
-	(250.38,145.79) --
-	(250.22,145.74) --
-	(249.74,145.63) --
-	(248.30,145.02) --
-	(244.78,143.52) --
-	(242.95,142.71) --
-	(241.65,142.20) --
-	(241.27,142.05) --
-	(240.80,141.82) --
-	(240.03,141.56) --
-	(239.31,141.28) --
-	(239.29,141.27) --
-	(237.41,140.47) --
-	(237.40,140.46) --
-	(236.22,140.02) --
-	(235.24,139.60) --
-	(234.25,139.14) --
-	(233.34,138.79) --
-	(232.39,138.25) --
-	(231.34,137.82) --
-	(231.15,137.77) --
-	(229.14,136.99) --
-	(224.00,134.73) --
-	(223.59,134.56) --
-	(223.54,134.54) --
-	(223.29,134.42) --
-	(222.58,134.07) --
-	(221.63,133.64) --
-	(220.93,133.31) --
-	(220.33,132.98) --
-	(220.17,132.91) --
-	(218.17,132.08) --
-	(217.68,131.82) --
-	(217.43,131.70) --
-	(217.33,131.66) --
-	(215.87,130.99) --
-	(211.50,128.79) --
-	(209.65,127.84) --
-	(205.19,125.79) --
-	(204.99,125.71) --
-	(199.87,123.16) --
-	(198.04,122.29) --
-	(196.35,121.40) --
-	(195.71,121.10) --
-	(195.62,121.07) --
-	(192.71,119.57) --
-	(187.92,117.14) --
-	(178.49,112.49) --
-	(171.43,108.90) --
-	(158.01,101.95) --
-	(154.64,100.20) --
-	(110.88, 76.90) --
-	(101.92, 72.02) --
-	( 95.59, 68.42) --
-	( 92.34, 66.68) --
-	( 86.71, 63.70) --
-	( 78.30, 59.08) --
-	( 64.98, 51.79) --
-	( 64.85, 51.71) --
-	( 60.61, 49.49) --
+	(404.02,202.64) --
+	(403.52,202.55) --
+	(396.15,200.94) --
+	(396.00,200.90) --
+	(395.16,200.73) --
+	(391.07,199.81) --
+	(390.79,199.72) --
+	(390.44,199.64) --
+	(390.40,199.63) --
+	(389.82,199.51) --
+	(389.16,199.34) --
+	(388.26,199.15) --
+	(387.67,199.02) --
+	(387.39,198.95) --
+	(387.24,198.91) --
+	(387.19,198.90) --
+	(387.17,198.89) --
+	(386.81,198.80) --
+	(386.70,198.77) --
+	(385.96,198.58) --
+	(385.73,198.52) --
+	(385.30,198.41) --
+	(384.92,198.32) --
+	(384.44,198.22) --
+	(383.85,198.06) --
+	(378.52,196.79) --
+	(376.96,196.41) --
+	(373.58,195.67) --
+	(372.02,195.27) --
+	(371.58,195.19) --
+	(371.17,195.11) --
+	(370.21,194.87) --
+	(368.50,194.51) --
+	(368.39,194.48) --
+	(368.20,194.44) --
+	(367.05,194.20) --
+	(366.47,194.12) --
+	(366.04,194.05) --
+	(365.92,194.02) --
+	(365.84,193.99) --
+	(365.84,193.99) --
+	(365.26,193.84) --
+	(365.00,193.79) --
+	(364.77,193.75) --
+	(364.57,193.72) --
+	(364.25,193.65) --
+	(363.71,193.51) --
+	(363.68,193.50) --
+	(362.99,193.32) --
+	(362.99,193.32) --
+	(362.92,193.31) --
+	(362.54,193.22) --
+	(360.68,192.76) --
+	(360.28,192.68) --
+	(360.17,192.64) --
+	(360.14,192.63) --
+	(359.58,192.44) --
+	(358.80,192.25) --
+	(358.45,192.15) --
+	(358.36,192.14) --
+	(357.71,191.98) --
+	(357.68,191.97) --
+	(357.28,191.86) --
+	(357.10,191.82) --
+	(357.04,191.80) --
+	(356.99,191.79) --
+	(356.86,191.76) --
+	(356.57,191.69) --
+	(356.08,191.55) --
+	(356.06,191.54) --
+	(355.69,191.47) --
+	(355.66,191.46) --
+	(355.44,191.41) --
+	(355.38,191.39) --
+	(355.06,191.30) --
+	(355.03,191.29) --
+	(354.77,191.22) --
+	(354.60,191.19) --
+	(352.50,190.60) --
+	(351.61,190.32) --
+	(350.57,190.05) --
+	(350.27,189.97) --
+	(350.01,189.90) --
+	(349.59,189.82) --
+	(348.84,189.61) --
+	(348.63,189.54) --
+	(347.30,189.12) --
+	(346.94,189.00) --
+	(346.80,188.93) --
+	(346.49,188.80) --
+	(345.78,188.66) --
+	(345.20,188.54) --
+	(345.11,188.51) --
+	(343.95,188.21) --
+	(343.79,188.15) --
+	(342.53,187.83) --
+	(341.52,187.59) --
+	(340.65,187.33) --
+	(340.28,187.18) --
+	(340.15,187.13) --
+	(339.84,187.04) --
+	(339.76,187.00) --
+	(339.55,186.90) --
+	(339.40,186.85) --
+	(339.21,186.80) --
+	(339.04,186.75) --
+	(338.87,186.71) --
+	(338.83,186.69) --
+	(338.50,186.61) --
+	(337.65,186.36) --
+	(335.47,185.72) --
+	(335.38,185.72) --
+	(333.83,185.20) --
+	(333.82,185.19) --
+	(333.69,185.16) --
+	(333.56,185.12) --
+	(333.53,185.11) --
+	(330.88,184.32) --
+	(330.38,184.14) --
+	(330.17,184.07) --
+	(328.92,183.67) --
+	(328.37,183.54) --
+	(327.78,183.35) --
+	(327.50,183.25) --
+	(327.01,183.15) --
+	(326.46,182.99) --
+	(326.16,182.93) --
+	(325.91,182.88) --
+	(325.87,182.87) --
+	(325.85,182.87) --
+	(325.46,182.72) --
+	(324.82,182.53) --
+	(324.53,182.44) --
+	(324.06,182.29) --
+	(323.98,182.27) --
+	(322.93,181.94) --
+	(322.64,181.83) --
+	(322.56,181.79) --
+	(321.47,181.38) --
+	(321.34,181.35) --
+	(320.71,181.09) --
+	(319.14,180.58) --
+	(318.60,180.44) --
+	(317.13,179.95) --
+	(316.72,179.79) --
+	(316.61,179.74) --
+	(316.58,179.73) --
+	(316.37,179.65) --
+	(316.29,179.64) --
+	(315.65,179.42) --
+	(315.61,179.41) --
+	(315.54,179.40) --
+	(315.28,179.31) --
+	(315.05,179.22) --
+	(314.84,179.10) --
+	(314.55,179.02) --
+	(314.12,178.88) --
+	(314.09,178.88) --
+	(312.75,178.49) --
+	(312.68,178.46) --
+	(312.39,178.38) --
+	(311.87,178.23) --
+	(311.71,178.17) --
+	(311.49,178.10) --
+	(311.09,177.95) --
+	(310.98,177.89) --
+	(310.80,177.81) --
+	(310.45,177.64) --
+	(310.36,177.60) --
+	(309.72,177.36) --
+	(309.55,177.31) --
+	(309.08,177.15) --
+	(308.79,177.08) --
+	(308.63,177.02) --
+	(308.42,176.96) --
+	(307.37,176.53) --
+	(307.16,176.45) --
+	(307.03,176.41) --
+	(306.15,176.07) --
+	(305.86,175.92) --
+	(305.76,175.91) --
+	(305.28,175.72) --
+	(305.11,175.66) --
+	(304.68,175.54) --
+	(304.60,175.51) --
+	(304.48,175.47) --
+	(304.47,175.47) --
+	(304.31,175.40) --
+	(304.10,175.27) --
+	(303.17,174.94) --
+	(302.93,174.85) --
+	(302.89,174.84) --
+	(302.61,174.75) --
+	(302.52,174.72) --
+	(302.45,174.70) --
+	(302.30,174.65) --
+	(302.20,174.62) --
+	(302.08,174.58) --
+	(302.06,174.57) --
+	(301.86,174.50) --
+	(301.81,174.49) --
+	(301.34,174.29) --
+	(300.69,174.00) --
+	(300.07,173.79) --
+	(299.22,173.50) --
+	(298.89,173.35) --
+	(298.71,173.32) --
+	(298.48,173.26) --
+	(298.45,173.24) --
+	(298.21,173.11) --
+	(298.13,173.07) --
+	(298.09,173.05) --
+	(297.99,173.01) --
+	(297.11,172.73) --
+	(296.61,172.56) --
+	(295.85,172.31) --
+	(295.12,172.01) --
+	(293.94,171.63) --
+	(293.90,171.61) --
+	(293.61,171.52) --
+	(293.49,171.49) --
+	(292.94,171.23) --
+	(292.85,171.21) --
+	(292.78,171.19) --
+	(292.77,171.19) --
+	(292.36,171.08) --
+	(292.20,171.02) --
+	(291.58,170.76) --
+	(291.45,170.71) --
+	(291.29,170.65) --
+	(290.44,170.25) --
+	(289.99,170.10) --
+	(289.71,169.94) --
+	(289.61,169.89) --
+	(289.30,169.78) --
+	(289.13,169.71) --
+	(289.03,169.66) --
+	(288.86,169.61) --
+	(288.45,169.46) --
+	(288.16,169.35) --
+	(287.76,169.22) --
+	(286.95,168.92) --
+	(286.70,168.83) --
+	(286.04,168.49) --
+	(285.67,168.38) --
+	(285.44,168.29) --
+	(284.88,168.03) --
+	(284.84,168.02) --
+	(284.81,168.01) --
+	(284.81,168.01) --
+	(284.80,168.01) --
+	(284.75,167.99) --
+	(284.43,167.87) --
+	(284.26,167.80) --
+	(283.80,167.62) --
+	(283.74,167.59) --
+	(283.34,167.42) --
+	(283.28,167.39) --
+	(283.10,167.31) --
+	(281.60,166.68) --
+	(281.52,166.65) --
+	(281.16,166.51) --
+	(280.63,166.30) --
+	(280.60,166.28) --
+	(280.50,166.24) --
+	(280.47,166.23) --
+	(280.41,166.20) --
+	(280.36,166.18) --
+	(280.21,166.10) --
+	(279.90,165.95) --
+	(279.83,165.93) --
+	(279.36,165.75) --
+	(279.03,165.64) --
+	(278.99,165.63) --
+	(278.93,165.61) --
+	(278.83,165.58) --
+	(277.37,165.06) --
+	(277.28,165.02) --
+	(276.77,164.80) --
+	(276.73,164.77) --
+	(276.14,164.54) --
+	(276.03,164.50) --
+	(275.50,164.28) --
+	(274.88,164.02) --
+	(274.85,164.02) --
+	(274.31,163.84) --
+	(273.48,163.51) --
+	(273.29,163.46) --
+	(273.01,163.35) --
+	(272.91,163.30) --
+	(272.40,163.04) --
+	(272.31,162.99) --
+	(271.51,162.69) --
+	(269.91,161.99) --
+	(269.75,161.93) --
+	(269.30,161.75) --
+	(269.12,161.68) --
+	(268.75,161.52) --
+	(268.51,161.43) --
+	(268.32,161.35) --
+	(268.15,161.29) --
+	(267.95,161.21) --
+	(267.83,161.16) --
+	(267.74,161.13) --
+	(266.70,160.61) --
+	(266.69,160.61) --
+	(265.54,160.18) --
+	(265.48,160.15) --
+	(265.11,159.94) --
+	(264.94,159.85) --
+	(264.43,159.63) --
+	(264.14,159.49) --
+	(263.47,159.19) --
+	(262.57,158.82) --
+	(261.39,158.33) --
+	(260.16,157.81) --
+	(260.08,157.78) --
+	(258.99,157.29) --
+	(256.94,156.29) --
+	(255.73,155.75) --
+	(254.34,155.17) --
+	(253.89,154.99) --
+	(253.69,154.88) --
+	(252.46,154.32) --
+	(251.97,154.12) --
+	(250.69,153.48) --
+	(250.38,153.33) --
+	(250.22,153.25) --
+	(249.74,153.00) --
+	(248.30,152.37) --
+	(244.78,150.68) --
+	(242.95,149.71) --
+	(241.65,149.06) --
+	(241.27,148.89) --
+	(240.80,148.69) --
+	(240.03,148.33) --
+	(239.31,148.04) --
+	(239.29,148.03) --
+	(237.41,147.17) --
+	(237.40,147.17) --
+	(236.22,146.56) --
+	(235.24,146.06) --
+	(234.24,145.59) --
+	(233.34,145.15) --
+	(232.39,144.69) --
+	(231.34,144.13) --
+	(231.15,144.03) --
+	(229.14,142.99) --
+	(224.00,140.38) --
+	(223.59,140.17) --
+	(223.54,140.15) --
+	(223.29,140.00) --
+	(222.58,139.70) --
+	(221.63,139.18) --
+	(220.93,138.82) --
+	(220.33,138.54) --
+	(220.17,138.45) --
+	(218.17,137.32) --
+	(217.68,137.08) --
+	(217.43,136.96) --
+	(217.33,136.90) --
+	(215.87,136.14) --
+	(211.50,133.96) --
+	(209.65,132.93) --
+	(205.19,130.40) --
+	(204.99,130.31) --
+	(199.87,127.66) --
+	(198.04,126.77) --
+	(196.35,125.78) --
+	(195.71,125.40) --
+	(195.62,125.35) --
+	(192.71,123.92) --
+	(187.92,121.54) --
+	(178.49,116.32) --
+	(171.43,112.37) --
+	(158.01,104.88) --
+	(154.64,103.05) --
+	(110.88, 78.56) --
+	(101.92, 73.39) --
+	( 95.59, 69.91) --
+	( 92.34, 67.95) --
+	( 86.71, 64.74) --
+	( 78.30, 59.79) --
+	( 64.98, 52.06) --
+	( 64.85, 51.98) --
+	( 60.61, 49.42) --
 	( 52.97, 45.08) --
@@
 
-\path[fill=fillColor,fill opacity=0.50] ( 52.97,155.78) --
-	( 60.61,157.02) --
-	( 64.85,157.72) --
-	( 64.98,157.76) --
-	( 78.30,159.89) --
-	( 86.71,161.16) --
-	( 92.34,162.02) --
-	( 95.59,162.58) --
-	(101.92,163.75) --
-	(110.88,165.37) --
-	(154.64,173.25) --
-	(158.01,173.83) --
-	(171.43,176.44) --
-	(178.49,177.89) --
-	(187.92,179.93) --
-	(192.71,180.94) --
-	(195.62,181.57) --
-	(195.71,181.60) --
-	(196.35,181.78) --
-	(198.04,182.20) --
-	(199.87,182.59) --
-	(204.99,183.69) --
-	(205.19,183.74) --
-	(209.65,184.88) --
-	(211.50,185.32) --
-	(215.87,186.31) --
-	(217.33,186.70) --
-	(217.43,186.73) --
-	(217.68,186.79) --
-	(218.17,186.95) --
-	(220.17,187.43) --
-	(220.33,187.47) --
-	(220.93,187.59) --
-	(221.63,187.78) --
-	(222.58,188.03) --
-	(223.29,188.16) --
-	(223.54,188.25) --
-	(223.59,188.27) --
-	(224.00,188.40) --
-	(229.14,189.71) --
-	(231.15,190.26) --
-	(231.34,190.31) --
-	(232.39,190.62) --
-	(233.34,190.89) --
-	(234.25,191.19) --
-	(235.24,191.47) --
-	(236.22,191.82) --
-	(237.40,192.18) --
-	(237.41,192.18) --
-	(239.29,192.72) --
-	(239.31,192.73) --
-	(240.03,192.94) --
-	(240.80,193.15) --
-	(241.27,193.33) --
-	(241.65,193.46) --
-	(242.95,193.75) --
-	(244.78,194.25) --
-	(248.30,195.33) --
-	(249.74,195.76) --
-	(250.22,195.94) --
-	(250.38,196.01) --
-	(250.69,196.16) --
-	(251.97,196.55) --
-	(252.46,196.68) --
-	(253.69,197.01) --
-	(253.89,197.07) --
-	(254.34,197.22) --
-	(255.74,197.69) --
-	(256.94,198.07) --
-	(258.99,198.62) --
-	(260.08,198.96) --
-	(260.16,198.98) --
-	(261.39,199.44) --
-	(262.57,199.78) --
-	(263.47,200.03) --
-	(264.14,200.24) --
-	(264.43,200.36) --
-	(264.94,200.54) --
-	(265.11,200.57) --
-	(265.48,200.70) --
-	(265.54,200.72) --
-	(266.69,201.09) --
-	(266.70,201.09) --
-	(267.74,201.45) --
-	(267.83,201.46) --
-	(267.95,201.52) --
-	(268.15,201.60) --
-	(268.32,201.64) --
-	(268.51,201.73) --
-	(268.75,201.81) --
-	(269.12,201.95) --
-	(269.30,202.00) --
-	(269.75,202.18) --
-	(269.91,202.21) --
-	(271.51,202.79) --
-	(272.31,203.06) --
-	(272.40,203.09) --
-	(272.91,203.23) --
-	(273.01,203.25) --
-	(273.29,203.34) --
-	(273.48,203.41) --
-	(274.31,203.68) --
-	(274.85,203.89) --
-	(274.88,203.90) --
-	(275.50,204.08) --
-	(276.03,204.23) --
-	(276.14,204.27) --
-	(276.73,204.46) --
-	(276.77,204.47) --
-	(277.28,204.64) --
-	(277.37,204.66) --
-	(278.83,205.17) --
-	(278.93,205.20) --
-	(278.99,205.23) --
-	(279.03,205.25) --
-	(279.36,205.31) --
-	(279.83,205.47) --
-	(279.90,205.50) --
-	(280.21,205.61) --
-	(280.36,205.65) --
-	(280.41,205.68) --
-	(280.47,205.71) --
-	(280.50,205.71) --
-	(280.60,205.74) --
-	(280.63,205.75) --
-	(281.16,205.91) --
-	(281.52,206.01) --
-	(281.60,206.03) --
-	(283.10,206.58) --
-	(283.28,206.66) --
-	(283.34,206.68) --
-	(283.74,206.84) --
-	(283.80,206.86) --
-	(284.26,207.01) --
-	(284.43,207.07) --
-	(284.75,207.16) --
-	(284.80,207.18) --
-	(284.81,207.18) --
-	(284.81,207.18) --
-	(284.84,207.19) --
-	(284.88,207.20) --
-	(285.44,207.45) --
-	(285.67,207.54) --
-	(286.04,207.68) --
-	(286.70,207.89) --
-	(286.95,207.97) --
-	(287.76,208.27) --
-	(288.16,208.43) --
-	(288.45,208.57) --
-	(288.86,208.73) --
-	(289.03,208.78) --
-	(289.13,208.82) --
-	(289.30,208.87) --
-	(289.61,208.98) --
-	(289.71,209.02) --
-	(289.99,209.12) --
-	(290.44,209.29) --
-	(291.29,209.59) --
-	(291.45,209.64) --
-	(291.58,209.68) --
-	(292.20,209.90) --
-	(292.36,209.95) --
-	(292.77,210.11) --
-	(292.78,210.12) --
-	(292.85,210.14) --
-	(292.94,210.16) --
-	(293.49,210.35) --
-	(293.61,210.39) --
-	(293.90,210.51) --
-	(293.94,210.53) --
-	(295.12,210.90) --
-	(295.85,211.14) --
-	(296.61,211.47) --
-	(297.11,211.69) --
-	(297.99,212.07) --
-	(298.09,212.10) --
-	(298.13,212.11) --
-	(298.21,212.12) --
-	(298.45,212.21) --
-	(298.48,212.23) --
-	(298.71,212.30) --
-	(298.89,212.38) --
-	(299.22,212.51) --
-	(300.07,212.87) --
-	(300.69,213.09) --
-	(301.34,213.35) --
-	(301.81,213.52) --
-	(301.86,213.54) --
-	(302.06,213.61) --
-	(302.08,213.62) --
-	(302.20,213.66) --
-	(302.30,213.71) --
-	(302.45,213.79) --
-	(302.52,213.81) --
-	(302.61,213.85) --
-	(302.89,213.96) --
-	(302.93,213.97) --
-	(303.17,214.04) --
-	(304.10,214.40) --
-	(304.31,214.48) --
-	(304.47,214.53) --
-	(304.48,214.53) --
-	(304.60,214.58) --
-	(304.68,214.61) --
-	(305.11,214.78) --
-	(305.28,214.85) --
-	(305.76,215.07) --
-	(305.86,215.12) --
-	(306.15,215.24) --
-	(307.03,215.53) --
-	(307.16,215.60) --
-	(307.37,215.70) --
-	(308.42,216.07) --
-	(308.63,216.18) --
-	(308.79,216.26) --
-	(309.08,216.38) --
-	(309.55,216.59) --
-	(309.72,216.66) --
-	(310.36,216.92) --
-	(310.45,216.96) --
-	(310.80,217.15) --
-	(310.98,217.23) --
-	(311.09,217.27) --
-	(311.49,217.42) --
-	(311.71,217.50) --
-	(311.87,217.56) --
-	(312.39,217.84) --
-	(312.68,217.99) --
-	(312.75,218.02) --
-	(314.09,218.56) --
-	(314.12,218.57) --
-	(314.55,218.71) --
-	(314.84,218.84) --
-	(315.05,218.90) --
-	(315.28,218.98) --
-	(315.54,219.09) --
-	(315.61,219.12) --
-	(315.65,219.13) --
-	(316.29,219.37) --
-	(316.37,219.39) --
-	(316.58,219.47) --
-	(316.61,219.48) --
-	(316.72,219.52) --
-	(317.13,219.68) --
-	(318.60,220.33) --
-	(319.14,220.56) --
-	(320.71,221.16) --
-	(321.34,221.42) --
-	(321.47,221.48) --
-	(322.56,221.95) --
-	(322.64,221.98) --
-	(322.93,222.10) --
-	(323.98,222.52) --
-	(324.06,222.56) --
-	(324.53,222.78) --
-	(324.82,222.91) --
-	(325.46,223.17) --
-	(325.85,223.33) --
-	(325.87,223.34) --
-	(325.91,223.34) --
-	(326.16,223.46) --
-	(326.46,223.57) --
-	(327.01,223.82) --
-	(327.50,224.06) --
-	(327.78,224.16) --
-	(328.37,224.39) --
-	(328.92,224.61) --
-	(330.17,225.15) --
-	(330.38,225.24) --
-	(330.88,225.42) --
-	(333.53,226.62) --
-	(333.56,226.63) --
-	(333.69,226.70) --
-	(333.82,226.78) --
-	(333.83,226.78) --
-	(335.38,227.53) --
-	(335.47,227.58) --
-	(337.65,228.52) --
-	(338.50,228.87) --
-	(338.83,228.96) --
-	(338.87,228.99) --
-	(339.04,229.08) --
-	(339.21,229.15) --
-	(339.40,229.23) --
-	(339.55,229.29) --
-	(339.76,229.37) --
-	(339.84,229.40) --
-	(340.15,229.53) --
-	(340.28,229.58) --
-	(340.65,229.71) --
-	(341.52,230.07) --
-	(342.53,230.56) --
-	(343.79,231.08) --
-	(343.95,231.15) --
-	(345.11,231.69) --
-	(345.20,231.73) --
-	(345.78,231.99) --
-	(346.49,232.31) --
-	(346.80,232.47) --
-	(346.94,232.52) --
-	(347.30,232.67) --
-	(348.63,233.25) --
-	(348.84,233.35) --
-	(349.59,233.76) --
-	(350.01,233.97) --
-	(350.27,234.09) --
-	(350.57,234.23) --
-	(351.61,234.73) --
-	(352.50,235.16) --
-	(354.60,236.10) --
-	(354.77,236.18) --
-	(355.03,236.30) --
-	(355.06,236.31) --
-	(355.38,236.46) --
-	(355.44,236.49) --
-	(355.66,236.61) --
-	(355.69,236.61) --
-	(356.06,236.78) --
-	(356.08,236.79) --
-	(356.57,237.02) --
-	(356.86,237.14) --
-	(356.99,237.20) --
-	(357.04,237.22) --
-	(357.10,237.25) --
-	(357.28,237.33) --
-	(357.68,237.52) --
-	(357.71,237.53) --
-	(358.36,237.85) --
-	(358.45,237.89) --
-	(358.80,238.04) --
-	(359.58,238.38) --
-	(360.14,238.61) --
-	(360.17,238.62) --
-	(360.28,238.68) --
-	(360.68,238.85) --
-	(362.54,239.69) --
-	(362.92,239.87) --
-	(362.99,239.91) --
-	(362.99,239.91) --
-	(363.68,240.21) --
-	(363.71,240.22) --
-	(364.25,240.52) --
-	(364.57,240.68) --
-	(364.77,240.77) --
-	(365.00,240.87) --
-	(365.26,241.04) --
-	(365.84,241.33) --
-	(365.84,241.33) --
-	(365.92,241.37) --
-	(366.04,241.42) --
-	(366.47,241.62) --
-	(367.05,241.89) --
-	(368.20,242.45) --
-	(368.39,242.54) --
-	(368.50,242.59) --
-	(370.21,243.39) --
-	(371.17,243.81) --
-	(371.58,244.00) --
-	(372.02,244.21) --
-	(373.58,244.87) --
-	(376.96,246.54) --
-	(378.52,247.26) --
-	(383.85,249.83) --
-	(384.44,250.15) --
-	(384.92,250.40) --
-	(385.30,250.56) --
-	(385.73,250.74) --
-	(385.96,250.84) --
-	(386.70,251.22) --
-	(386.81,251.27) --
-	(387.17,251.44) --
-	(387.19,251.44) --
-	(387.24,251.46) --
-	(387.39,251.54) --
-	(387.67,251.67) --
-	(388.26,251.97) --
-	(389.16,252.36) --
-	(389.82,252.64) --
-	(390.40,252.95) --
-	(390.44,252.98) --
-	(390.79,253.21) --
-	(391.07,253.39) --
-	(395.16,255.52) --
-	(396.00,255.92) --
-	(396.15,255.99) --
-	(403.52,259.54) --
-	(404.02,259.83) --
-	(404.02,193.21) --
-	(403.52,193.10) --
-	(396.15,191.59) --
-	(396.00,191.58) --
-	(395.16,191.49) --
-	(391.07,190.75) --
-	(390.79,190.69) --
-	(390.44,190.64) --
-	(390.40,190.63) --
-	(389.82,190.53) --
-	(389.16,190.43) --
-	(388.26,190.20) --
-	(387.67,190.10) --
-	(387.39,190.05) --
-	(387.24,190.01) --
-	(387.19,190.01) --
-	(387.17,190.00) --
-	(386.81,189.94) --
-	(386.70,189.92) --
-	(385.96,189.70) --
-	(385.73,189.67) --
-	(385.30,189.58) --
-	(384.92,189.52) --
-	(384.44,189.44) --
-	(383.85,189.36) --
-	(378.52,187.97) --
-	(376.96,187.68) --
-	(373.58,186.94) --
-	(372.02,186.66) --
-	(371.58,186.58) --
-	(371.17,186.48) --
-	(370.21,186.18) --
-	(368.50,185.79) --
-	(368.39,185.78) --
-	(368.20,185.73) --
-	(367.05,185.54) --
-	(366.47,185.42) --
-	(366.04,185.30) --
-	(365.92,185.27) --
-	(365.84,185.25) --
-	(365.84,185.25) --
-	(365.26,185.12) --
-	(365.00,185.06) --
-	(364.77,185.00) --
-	(364.57,184.94) --
-	(364.25,184.87) --
-	(363.71,184.72) --
-	(363.68,184.71) --
-	(362.99,184.56) --
-	(362.99,184.56) --
-	(362.92,184.54) --
-	(362.54,184.46) --
-	(360.68,184.05) --
-	(360.28,183.92) --
-	(360.17,183.88) --
-	(360.14,183.88) --
-	(359.58,183.76) --
-	(358.80,183.59) --
-	(358.45,183.50) --
-	(358.36,183.48) --
-	(357.71,183.31) --
-	(357.68,183.31) --
-	(357.28,183.23) --
-	(357.10,183.18) --
-	(357.04,183.16) --
-	(356.99,183.15) --
-	(356.86,183.10) --
-	(356.57,183.03) --
-	(356.08,182.90) --
-	(356.06,182.90) --
-	(355.69,182.80) --
-	(355.66,182.80) --
-	(355.44,182.75) --
-	(355.38,182.73) --
-	(355.06,182.65) --
-	(355.03,182.64) --
-	(354.77,182.59) --
-	(354.60,182.56) --
-	(352.50,182.02) --
-	(351.61,181.81) --
-	(350.57,181.53) --
-	(350.27,181.44) --
-	(350.01,181.39) --
-	(349.59,181.29) --
-	(348.84,181.08) --
-	(348.63,181.04) --
-	(347.30,180.74) --
-	(346.94,180.63) --
-	(346.80,180.60) --
-	(346.49,180.52) --
-	(345.78,180.31) --
-	(345.20,180.18) --
-	(345.11,180.16) --
-	(343.95,179.88) --
-	(343.79,179.84) --
-	(342.53,179.55) --
-	(341.52,179.33) --
-	(340.65,179.17) --
-	(340.28,179.02) --
-	(340.15,178.96) --
-	(339.84,178.86) --
-	(339.76,178.82) --
-	(339.55,178.78) --
-	(339.40,178.76) --
-	(339.21,178.74) --
-	(339.04,178.70) --
-	(338.87,178.68) --
-	(338.83,178.66) --
-	(338.50,178.58) --
-	(337.65,178.29) --
-	(335.47,177.71) --
-	(335.38,177.68) --
-	(333.83,177.24) --
-	(333.82,177.24) --
-	(333.69,177.20) --
-	(333.56,177.17) --
-	(333.53,177.16) --
-	(330.88,176.48) --
-	(330.38,176.35) --
-	(330.17,176.29) --
-	(328.92,176.00) --
-	(328.37,175.84) --
-	(327.78,175.64) --
-	(327.50,175.55) --
-	(327.01,175.42) --
-	(326.46,175.32) --
-	(326.16,175.25) --
-	(325.91,175.20) --
-	(325.87,175.20) --
-	(325.85,175.19) --
-	(325.46,175.13) --
-	(324.82,174.98) --
-	(324.53,174.93) --
-	(324.06,174.82) --
-	(323.98,174.80) --
-	(322.93,174.54) --
-	(322.64,174.46) --
-	(322.56,174.44) --
-	(321.47,174.10) --
-	(321.34,174.07) --
-	(320.71,173.87) --
-	(319.14,173.48) --
-	(318.60,173.34) --
-	(317.13,172.94) --
-	(316.72,172.82) --
-	(316.61,172.81) --
-	(316.58,172.80) --
-	(316.37,172.74) --
-	(316.29,172.72) --
-	(315.65,172.55) --
-	(315.61,172.53) --
-	(315.54,172.52) --
-	(315.28,172.44) --
-	(315.05,172.37) --
-	(314.84,172.32) --
-	(314.55,172.24) --
-	(314.12,172.13) --
-	(314.09,172.13) --
-	(312.75,171.77) --
-	(312.68,171.75) --
-	(312.39,171.66) --
-	(311.87,171.50) --
-	(311.71,171.46) --
-	(311.49,171.39) --
-	(311.09,171.28) --
-	(310.98,171.25) --
-	(310.80,171.20) --
-	(310.45,171.10) --
-	(310.36,171.07) --
-	(309.72,170.92) --
-	(309.55,170.87) --
-	(309.08,170.76) --
-	(308.79,170.69) --
-	(308.63,170.64) --
-	(308.42,170.58) --
-	(307.37,170.23) --
-	(307.16,170.16) --
-	(307.03,170.09) --
-	(306.15,169.83) --
-	(305.86,169.74) --
-	(305.76,169.71) --
-	(305.28,169.58) --
-	(305.11,169.54) --
-	(304.68,169.40) --
-	(304.60,169.37) --
-	(304.48,169.34) --
-	(304.47,169.33) --
-	(304.31,169.29) --
-	(304.10,169.23) --
-	(303.17,168.95) --
-	(302.93,168.88) --
-	(302.89,168.88) --
-	(302.61,168.80) --
-	(302.52,168.79) --
-	(302.45,168.78) --
-	(302.30,168.73) --
-	(302.20,168.71) --
-	(302.08,168.67) --
-	(302.06,168.66) --
-	(301.86,168.62) --
-	(301.81,168.60) --
-	(301.34,168.41) --
-	(300.69,168.22) --
-	(300.07,168.01) --
-	(299.22,167.81) --
-	(298.89,167.74) --
-	(298.71,167.68) --
-	(298.48,167.60) --
-	(298.45,167.59) --
-	(298.21,167.50) --
-	(298.13,167.47) --
-	(298.09,167.46) --
-	(297.99,167.43) --
-	(297.11,167.14) --
-	(296.61,167.00) --
-	(295.85,166.72) --
-	(295.12,166.43) --
-	(293.94,166.08) --
-	(293.90,166.07) --
-	(293.61,165.97) --
-	(293.49,165.93) --
-	(292.94,165.77) --
-	(292.85,165.76) --
-	(292.78,165.72) --
-	(292.77,165.72) --
-	(292.36,165.59) --
-	(292.20,165.54) --
-	(291.58,165.36) --
-	(291.45,165.31) --
-	(291.29,165.25) --
-	(290.44,164.93) --
-	(289.99,164.78) --
-	(289.71,164.71) --
-	(289.61,164.68) --
-	(289.30,164.60) --
-	(289.13,164.54) --
-	(289.03,164.51) --
-	(288.86,164.44) --
-	(288.45,164.32) --
-	(288.16,164.21) --
-	(287.76,164.11) --
-	(286.95,163.86) --
-	(286.70,163.79) --
-	(286.04,163.59) --
-	(285.67,163.45) --
-	(285.44,163.36) --
-	(284.88,163.17) --
-	(284.84,163.16) --
-	(284.81,163.14) --
-	(284.81,163.14) --
-	(284.80,163.14) --
-	(284.75,163.11) --
-	(284.43,163.01) --
-	(284.26,162.95) --
-	(283.80,162.82) --
-	(283.74,162.80) --
-	(283.34,162.65) --
-	(283.28,162.64) --
-	(283.10,162.60) --
-	(281.60,162.07) --
-	(281.52,162.04) --
-	(281.16,161.89) --
-	(280.63,161.70) --
-	(280.60,161.69) --
-	(280.50,161.65) --
-	(280.47,161.64) --
-	(280.41,161.61) --
-	(280.36,161.59) --
-	(280.21,161.53) --
-	(279.90,161.42) --
-	(279.83,161.40) --
-	(279.36,161.22) --
-	(279.03,161.12) --
-	(278.99,161.10) --
-	(278.93,161.08) --
-	(278.83,161.05) --
-	(277.37,160.51) --
-	(277.28,160.48) --
-	(276.77,160.29) --
-	(276.73,160.28) --
-	(276.14,160.03) --
-	(276.03,159.99) --
-	(275.50,159.78) --
-	(274.88,159.56) --
-	(274.85,159.55) --
-	(274.31,159.34) --
-	(273.48,159.10) --
-	(273.29,159.00) --
-	(273.01,158.91) --
-	(272.91,158.87) --
-	(272.40,158.63) --
-	(272.31,158.61) --
-	(271.51,158.38) --
-	(269.91,157.84) --
-	(269.75,157.78) --
-	(269.30,157.63) --
-	(269.12,157.57) --
-	(268.75,157.44) --
-	(268.51,157.36) --
-	(268.32,157.28) --
-	(268.15,157.20) --
-	(267.95,157.14) --
-	(267.83,157.09) --
-	(267.74,157.07) --
-	(266.70,156.71) --
-	(266.69,156.71) --
-	(265.54,156.24) --
-	(265.48,156.21) --
-	(265.11,156.07) --
-	(264.94,156.00) --
-	(264.43,155.81) --
-	(264.14,155.71) --
-	(263.47,155.47) --
-	(262.57,155.16) --
-	(261.39,154.71) --
-	(260.16,154.24) --
-	(260.08,154.22) --
-	(258.99,153.78) --
-	(256.94,152.92) --
-	(255.74,152.43) --
-	(254.34,151.90) --
-	(253.89,151.74) --
-	(253.69,151.68) --
-	(252.46,151.14) --
-	(251.97,150.97) --
-	(250.69,150.46) --
-	(250.38,150.35) --
-	(250.22,150.29) --
-	(249.74,150.09) --
-	(248.30,149.50) --
-	(244.78,148.02) --
-	(242.95,147.32) --
-	(241.65,146.80) --
-	(241.27,146.62) --
-	(240.80,146.42) --
-	(240.03,146.15) --
-	(239.31,145.84) --
-	(239.29,145.83) --
-	(237.41,145.07) --
-	(237.40,145.07) --
-	(236.22,144.55) --
-	(235.24,144.17) --
-	(234.25,143.77) --
-	(233.34,143.45) --
-	(232.39,143.03) --
-	(231.34,142.62) --
-	(231.15,142.56) --
-	(229.14,141.64) --
-	(224.00,139.28) --
-	(223.59,139.09) --
-	(223.54,139.07) --
-	(223.29,138.97) --
-	(222.58,138.65) --
-	(221.63,138.25) --
-	(220.93,137.97) --
-	(220.33,137.73) --
-	(220.17,137.66) --
-	(218.17,136.81) --
-	(217.68,136.58) --
-	(217.43,136.47) --
-	(217.33,136.42) --
-	(215.87,135.77) --
-	(211.50,133.87) --
-	(209.65,133.08) --
-	(205.19,130.98) --
-	(204.99,130.88) --
-	(199.87,128.62) --
-	(198.04,127.77) --
-	(196.35,126.93) --
-	(195.71,126.63) --
-	(195.62,126.59) --
-	(192.71,125.33) --
-	(187.92,123.15) --
-	(178.49,118.78) --
-	(171.43,115.43) --
-	(158.01,108.85) --
-	(154.64,107.17) --
-	(110.88, 85.07) --
-	(101.92, 80.39) --
-	( 95.59, 77.11) --
-	( 92.34, 75.32) --
-	( 86.71, 72.24) --
-	( 78.30, 67.94) --
-	( 64.98, 61.14) --
-	( 64.85, 61.07) --
-	( 60.61, 58.89) --
-	( 52.97, 54.98) --
+\path[fill=fillColor,fill opacity=0.50] ( 52.97,152.14) --
+	( 60.61,153.49) --
+	( 64.85,154.42) --
+	( 64.98,154.43) --
+	( 78.30,157.17) --
+	( 86.71,158.92) --
+	( 92.34,160.24) --
+	( 95.59,160.95) --
+	(101.92,162.37) --
+	(110.88,164.20) --
+	(154.64,173.54) --
+	(158.01,174.22) --
+	(171.43,177.27) --
+	(178.49,178.74) --
+	(187.92,180.95) --
+	(192.71,182.13) --
+	(195.62,182.77) --
+	(195.71,182.80) --
+	(196.35,182.98) --
+	(198.04,183.34) --
+	(199.87,183.71) --
+	(204.99,184.94) --
+	(205.19,185.00) --
+	(209.65,186.26) --
+	(211.50,186.69) --
+	(215.87,187.74) --
+	(217.33,188.05) --
+	(217.43,188.07) --
+	(217.68,188.15) --
+	(218.17,188.27) --
+	(220.17,188.85) --
+	(220.33,188.89) --
+	(220.93,189.07) --
+	(221.63,189.28) --
+	(222.58,189.49) --
+	(223.29,189.64) --
+	(223.54,189.72) --
+	(223.59,189.74) --
+	(224.00,189.85) --
+	(229.14,191.13) --
+	(231.15,191.61) --
+	(231.34,191.66) --
+	(232.39,191.94) --
+	(233.34,192.16) --
+	(234.24,192.44) --
+	(235.24,192.69) --
+	(236.22,192.97) --
+	(237.40,193.25) --
+	(237.41,193.26) --
+	(239.29,193.78) --
+	(239.31,193.78) --
+	(240.03,194.00) --
+	(240.80,194.20) --
+	(241.27,194.32) --
+	(241.65,194.41) --
+	(242.95,194.77) --
+	(244.78,195.33) --
+	(248.30,196.19) --
+	(249.74,196.72) --
+	(250.22,196.86) --
+	(250.38,196.92) --
+	(250.69,197.02) --
+	(251.97,197.42) --
+	(252.46,197.60) --
+	(253.69,198.00) --
+	(253.89,198.08) --
+	(254.34,198.20) --
+	(255.73,198.68) --
+	(256.94,199.10) --
+	(258.99,199.77) --
+	(260.08,200.11) --
+	(260.16,200.13) --
+	(261.39,200.54) --
+	(262.57,200.88) --
+	(263.47,201.18) --
+	(264.14,201.41) --
+	(264.43,201.51) --
+	(264.94,201.69) --
+	(265.11,201.73) --
+	(265.48,201.83) --
+	(265.54,201.85) --
+	(266.69,202.20) --
+	(266.70,202.20) --
+	(267.74,202.52) --
+	(267.83,202.53) --
+	(267.95,202.57) --
+	(268.15,202.66) --
+	(268.32,202.72) --
+	(268.51,202.80) --
+	(268.75,202.88) --
+	(269.12,202.98) --
+	(269.30,203.04) --
+	(269.75,203.19) --
+	(269.91,203.24) --
+	(271.51,203.78) --
+	(272.31,203.99) --
+	(272.40,204.01) --
+	(272.91,204.18) --
+	(273.01,204.22) --
+	(273.29,204.32) --
+	(273.48,204.39) --
+	(274.31,204.67) --
+	(274.85,204.86) --
+	(274.88,204.88) --
+	(275.50,205.12) --
+	(276.03,205.26) --
+	(276.14,205.29) --
+	(276.73,205.49) --
+	(276.77,205.51) --
+	(277.28,205.72) --
+	(277.37,205.76) --
+	(278.83,206.28) --
+	(278.93,206.32) --
+	(278.99,206.34) --
+	(279.03,206.36) --
+	(279.36,206.48) --
+	(279.83,206.59) --
+	(279.90,206.61) --
+	(280.21,206.70) --
+	(280.36,206.74) --
+	(280.41,206.75) --
+	(280.47,206.77) --
+	(280.50,206.77) --
+	(280.60,206.82) --
+	(280.63,206.83) --
+	(281.16,207.01) --
+	(281.52,207.17) --
+	(281.60,207.20) --
+	(283.10,207.68) --
+	(283.28,207.75) --
+	(283.34,207.77) --
+	(283.74,207.89) --
+	(283.80,207.92) --
+	(284.26,208.08) --
+	(284.43,208.16) --
+	(284.75,208.28) --
+	(284.80,208.29) --
+	(284.81,208.30) --
+	(284.81,208.30) --
+	(284.84,208.31) --
+	(284.88,208.32) --
+	(285.44,208.54) --
+	(285.67,208.62) --
+	(286.04,208.78) --
+	(286.70,209.03) --
+	(286.95,209.10) --
+	(287.76,209.35) --
+	(288.16,209.51) --
+	(288.45,209.59) --
+	(288.86,209.71) --
+	(289.03,209.78) --
+	(289.13,209.82) --
+	(289.30,209.90) --
+	(289.61,209.99) --
+	(289.71,210.01) --
+	(289.99,210.13) --
+	(290.44,210.27) --
+	(291.29,210.57) --
+	(291.45,210.64) --
+	(291.58,210.69) --
+	(292.20,210.90) --
+	(292.36,210.96) --
+	(292.77,211.11) --
+	(292.78,211.11) --
+	(292.85,211.14) --
+	(292.94,211.17) --
+	(293.49,211.40) --
+	(293.61,211.45) --
+	(293.90,211.57) --
+	(293.94,211.58) --
+	(295.12,212.05) --
+	(295.85,212.29) --
+	(296.61,212.58) --
+	(297.11,212.76) --
+	(297.99,213.10) --
+	(298.09,213.14) --
+	(298.13,213.16) --
+	(298.21,213.17) --
+	(298.45,213.25) --
+	(298.48,213.26) --
+	(298.71,213.34) --
+	(298.89,213.42) --
+	(299.22,213.56) --
+	(300.07,213.86) --
+	(300.69,214.10) --
+	(301.34,214.34) --
+	(301.81,214.51) --
+	(301.86,214.52) --
+	(302.06,214.59) --
+	(302.08,214.60) --
+	(302.20,214.65) --
+	(302.30,214.68) --
+	(302.45,214.75) --
+	(302.52,214.78) --
+	(302.61,214.81) --
+	(302.89,214.91) --
+	(302.93,214.93) --
+	(303.17,215.01) --
+	(304.10,215.42) --
+	(304.31,215.53) --
+	(304.47,215.60) --
+	(304.48,215.60) --
+	(304.60,215.65) --
+	(304.68,215.69) --
+	(305.11,215.83) --
+	(305.28,215.88) --
+	(305.76,216.08) --
+	(305.86,216.12) --
+	(306.15,216.20) --
+	(307.03,216.55) --
+	(307.16,216.61) --
+	(307.37,216.71) --
+	(308.42,217.15) --
+	(308.63,217.22) --
+	(308.79,217.30) --
+	(309.08,217.42) --
+	(309.55,217.62) --
+	(309.72,217.70) --
+	(310.36,217.93) --
+	(310.45,217.96) --
+	(310.80,218.07) --
+	(310.98,218.12) --
+	(311.09,218.15) --
+	(311.49,218.32) --
+	(311.71,218.39) --
+	(311.87,218.46) --
+	(312.39,218.69) --
+	(312.68,218.82) --
+	(312.75,218.84) --
+	(314.09,219.38) --
+	(314.12,219.39) --
+	(314.55,219.55) --
+	(314.84,219.65) --
+	(315.05,219.73) --
+	(315.28,219.82) --
+	(315.54,219.92) --
+	(315.61,219.94) --
+	(315.65,219.96) --
+	(316.29,220.25) --
+	(316.37,220.28) --
+	(316.58,220.37) --
+	(316.61,220.38) --
+	(316.72,220.44) --
+	(317.13,220.63) --
+	(318.60,221.25) --
+	(319.14,221.47) --
+	(320.71,222.12) --
+	(321.34,222.40) --
+	(321.47,222.46) --
+	(322.56,222.95) --
+	(322.64,222.99) --
+	(322.93,223.09) --
+	(323.98,223.55) --
+	(324.06,223.58) --
+	(324.53,223.79) --
+	(324.82,223.91) --
+	(325.46,224.21) --
+	(325.85,224.40) --
+	(325.87,224.41) --
+	(325.91,224.43) --
+	(326.16,224.54) --
+	(326.46,224.64) --
+	(327.01,224.87) --
+	(327.50,225.07) --
+	(327.78,225.19) --
+	(328.37,225.45) --
+	(328.92,225.70) --
+	(330.17,226.24) --
+	(330.38,226.32) --
+	(330.88,226.55) --
+	(333.53,227.66) --
+	(333.56,227.67) --
+	(333.69,227.72) --
+	(333.82,227.79) --
+	(333.83,227.79) --
+	(335.38,228.52) --
+	(335.47,228.57) --
+	(337.65,229.57) --
+	(338.50,229.94) --
+	(338.83,230.09) --
+	(338.87,230.11) --
+	(339.04,230.20) --
+	(339.21,230.30) --
+	(339.40,230.39) --
+	(339.55,230.46) --
+	(339.76,230.55) --
+	(339.84,230.59) --
+	(340.15,230.73) --
+	(340.28,230.79) --
+	(340.65,230.98) --
+	(341.52,231.42) --
+	(342.53,231.84) --
+	(343.79,232.39) --
+	(343.95,232.47) --
+	(345.11,233.02) --
+	(345.20,233.07) --
+	(345.78,233.34) --
+	(346.49,233.62) --
+	(346.80,233.80) --
+	(346.94,233.87) --
+	(347.30,234.05) --
+	(348.63,234.66) --
+	(348.84,234.76) --
+	(349.59,235.10) --
+	(350.01,235.30) --
+	(350.27,235.42) --
+	(350.57,235.56) --
+	(351.61,236.04) --
+	(352.50,236.48) --
+	(354.60,237.42) --
+	(354.77,237.50) --
+	(355.03,237.62) --
+	(355.06,237.64) --
+	(355.38,237.77) --
+	(355.44,237.80) --
+	(355.66,237.88) --
+	(355.69,237.89) --
+	(356.06,238.04) --
+	(356.08,238.05) --
+	(356.57,238.27) --
+	(356.86,238.39) --
+	(356.99,238.45) --
+	(357.04,238.47) --
+	(357.10,238.51) --
+	(357.28,238.59) --
+	(357.68,238.81) --
+	(357.71,238.82) --
+	(358.36,239.14) --
+	(358.45,239.19) --
+	(358.80,239.35) --
+	(359.58,239.67) --
+	(360.14,239.89) --
+	(360.17,239.91) --
+	(360.28,239.95) --
+	(360.68,240.13) --
+	(362.54,240.94) --
+	(362.92,241.11) --
+	(362.99,241.14) --
+	(362.99,241.15) --
+	(363.68,241.48) --
+	(363.71,241.49) --
+	(364.25,241.78) --
+	(364.57,241.93) --
+	(364.77,242.01) --
+	(365.00,242.14) --
+	(365.26,242.26) --
+	(365.84,242.54) --
+	(365.84,242.54) --
+	(365.92,242.58) --
+	(366.04,242.63) --
+	(366.47,242.84) --
+	(367.05,243.08) --
+	(368.20,243.62) --
+	(368.39,243.70) --
+	(368.50,243.76) --
+	(370.21,244.53) --
+	(371.17,244.94) --
+	(371.58,245.16) --
+	(372.02,245.38) --
+	(373.58,246.14) --
+	(376.96,247.86) --
+	(378.52,248.56) --
+	(383.85,251.20) --
+	(384.44,251.51) --
+	(384.92,251.76) --
+	(385.30,251.92) --
+	(385.73,252.18) --
+	(385.96,252.31) --
+	(386.70,252.66) --
+	(386.81,252.72) --
+	(387.17,252.89) --
+	(387.19,252.90) --
+	(387.24,252.92) --
+	(387.39,253.01) --
+	(387.67,253.14) --
+	(388.26,253.40) --
+	(389.16,253.80) --
+	(389.82,254.12) --
+	(390.40,254.42) --
+	(390.44,254.45) --
+	(390.79,254.66) --
+	(391.07,254.78) --
+	(395.16,256.66) --
+	(396.00,257.08) --
+	(396.15,257.16) --
+	(403.52,260.83) --
+	(404.02,261.09) --
+	(404.02,207.00) --
+	(403.52,206.90) --
+	(396.15,205.09) --
+	(396.00,205.05) --
+	(395.16,204.86) --
+	(391.07,203.87) --
+	(390.79,203.81) --
+	(390.44,203.73) --
+	(390.40,203.72) --
+	(389.82,203.60) --
+	(389.16,203.45) --
+	(388.26,203.22) --
+	(387.67,203.09) --
+	(387.39,203.04) --
+	(387.24,203.01) --
+	(387.19,203.00) --
+	(387.17,203.00) --
+	(386.81,202.93) --
+	(386.70,202.90) --
+	(385.96,202.75) --
+	(385.73,202.70) --
+	(385.30,202.60) --
+	(384.92,202.52) --
+	(384.44,202.42) --
+	(383.85,202.28) --
+	(378.52,200.98) --
+	(376.96,200.53) --
+	(373.58,199.73) --
+	(372.02,199.39) --
+	(371.58,199.28) --
+	(371.17,199.17) --
+	(370.21,198.94) --
+	(368.50,198.51) --
+	(368.39,198.49) --
+	(368.20,198.45) --
+	(367.05,198.11) --
+	(366.47,197.91) --
+	(366.04,197.79) --
+	(365.92,197.75) --
+	(365.84,197.73) --
+	(365.84,197.73) --
+	(365.26,197.58) --
+	(365.00,197.50) --
+	(364.77,197.44) --
+	(364.57,197.38) --
+	(364.25,197.31) --
+	(363.71,197.21) --
+	(363.68,197.20) --
+	(362.99,197.04) --
+	(362.99,197.04) --
+	(362.92,197.02) --
+	(362.54,196.94) --
+	(360.68,196.45) --
+	(360.28,196.33) --
+	(360.17,196.30) --
+	(360.14,196.30) --
+	(359.58,196.13) --
+	(358.80,195.93) --
+	(358.45,195.85) --
+	(358.36,195.83) --
+	(357.71,195.63) --
+	(357.68,195.62) --
+	(357.28,195.52) --
+	(357.10,195.47) --
+	(357.04,195.45) --
+	(356.99,195.44) --
+	(356.86,195.41) --
+	(356.57,195.32) --
+	(356.08,195.18) --
+	(356.06,195.17) --
+	(355.69,195.03) --
+	(355.66,195.02) --
+	(355.44,194.96) --
+	(355.38,194.93) --
+	(355.06,194.82) --
+	(355.03,194.81) --
+	(354.77,194.76) --
+	(354.60,194.70) --
+	(352.50,194.12) --
+	(351.61,193.88) --
+	(350.57,193.61) --
+	(350.27,193.51) --
+	(350.01,193.44) --
+	(349.59,193.32) --
+	(348.84,193.11) --
+	(348.63,193.04) --
+	(347.30,192.70) --
+	(346.94,192.60) --
+	(346.80,192.56) --
+	(346.49,192.49) --
+	(345.78,192.27) --
+	(345.20,192.11) --
+	(345.11,192.08) --
+	(343.95,191.74) --
+	(343.79,191.69) --
+	(342.53,191.35) --
+	(341.52,191.05) --
+	(340.65,190.79) --
+	(340.28,190.71) --
+	(340.15,190.67) --
+	(339.84,190.57) --
+	(339.76,190.55) --
+	(339.55,190.51) --
+	(339.40,190.47) --
+	(339.21,190.39) --
+	(339.04,190.33) --
+	(338.87,190.26) --
+	(338.83,190.25) --
+	(338.50,190.18) --
+	(337.65,189.95) --
+	(335.47,189.38) --
+	(335.38,189.33) --
+	(333.83,188.81) --
+	(333.82,188.81) --
+	(333.69,188.77) --
+	(333.56,188.73) --
+	(333.53,188.72) --
+	(330.88,187.93) --
+	(330.38,187.75) --
+	(330.17,187.72) --
+	(328.92,187.34) --
+	(328.37,187.13) --
+	(327.78,186.96) --
+	(327.50,186.89) --
+	(327.01,186.77) --
+	(326.46,186.56) --
+	(326.16,186.46) --
+	(325.91,186.40) --
+	(325.87,186.39) --
+	(325.85,186.38) --
+	(325.46,186.24) --
+	(324.82,186.01) --
+	(324.53,185.94) --
+	(324.06,185.78) --
+	(323.98,185.75) --
+	(322.93,185.40) --
+	(322.64,185.31) --
+	(322.56,185.27) --
+	(321.47,184.86) --
+	(321.34,184.81) --
+	(320.71,184.61) --
+	(319.14,184.11) --
+	(318.60,183.94) --
+	(317.13,183.42) --
+	(316.72,183.28) --
+	(316.61,183.23) --
+	(316.58,183.22) --
+	(316.37,183.16) --
+	(316.29,183.13) --
+	(315.65,182.93) --
+	(315.61,182.92) --
+	(315.54,182.90) --
+	(315.28,182.82) --
+	(315.05,182.75) --
+	(314.84,182.69) --
+	(314.55,182.60) --
+	(314.12,182.46) --
+	(314.09,182.44) --
+	(312.75,182.05) --
+	(312.68,182.03) --
+	(312.39,181.92) --
+	(311.87,181.72) --
+	(311.71,181.67) --
+	(311.49,181.59) --
+	(311.09,181.42) --
+	(310.98,181.37) --
+	(310.80,181.28) --
+	(310.45,181.13) --
+	(310.36,181.09) --
+	(309.72,180.89) --
+	(309.55,180.82) --
+	(309.08,180.61) --
+	(308.79,180.52) --
+	(308.63,180.45) --
+	(308.42,180.39) --
+	(307.37,180.04) --
+	(307.16,179.96) --
+	(307.03,179.91) --
+	(306.15,179.54) --
+	(305.86,179.45) --
+	(305.76,179.42) --
+	(305.28,179.27) --
+	(305.11,179.21) --
+	(304.68,179.04) --
+	(304.60,179.01) --
+	(304.48,178.97) --
+	(304.47,178.96) --
+	(304.31,178.91) --
+	(304.10,178.86) --
+	(303.17,178.46) --
+	(302.93,178.38) --
+	(302.89,178.36) --
+	(302.61,178.26) --
+	(302.52,178.24) --
+	(302.45,178.21) --
+	(302.30,178.14) --
+	(302.20,178.11) --
+	(302.08,178.06) --
+	(302.06,178.05) --
+	(301.86,177.98) --
+	(301.81,177.96) --
+	(301.34,177.81) --
+	(300.69,177.60) --
+	(300.07,177.36) --
+	(299.22,177.06) --
+	(298.89,176.93) --
+	(298.71,176.85) --
+	(298.48,176.75) --
+	(298.45,176.74) --
+	(298.21,176.66) --
+	(298.13,176.64) --
+	(298.09,176.63) --
+	(297.99,176.58) --
+	(297.11,176.22) --
+	(296.61,176.00) --
+	(295.85,175.75) --
+	(295.12,175.48) --
+	(293.94,175.01) --
+	(293.90,174.99) --
+	(293.61,174.87) --
+	(293.49,174.84) --
+	(292.94,174.62) --
+	(292.85,174.60) --
+	(292.78,174.57) --
+	(292.77,174.57) --
+	(292.36,174.40) --
+	(292.20,174.35) --
+	(291.58,174.15) --
+	(291.45,174.11) --
+	(291.29,174.06) --
+	(290.44,173.75) --
+	(289.99,173.53) --
+	(289.71,173.41) --
+	(289.61,173.38) --
+	(289.30,173.25) --
+	(289.13,173.19) --
+	(289.03,173.16) --
+	(288.86,173.10) --
+	(288.45,172.93) --
+	(288.16,172.84) --
+	(287.76,172.69) --
+	(286.95,172.39) --
+	(286.70,172.30) --
+	(286.04,172.04) --
+	(285.67,171.89) --
+	(285.44,171.82) --
+	(284.88,171.58) --
+	(284.84,171.56) --
+	(284.81,171.55) --
+	(284.81,171.55) --
+	(284.80,171.55) --
+	(284.75,171.52) --
+	(284.43,171.40) --
+	(284.26,171.33) --
+	(283.80,171.13) --
+	(283.74,171.11) --
+	(283.34,170.94) --
+	(283.28,170.91) --
+	(283.10,170.84) --
+	(281.60,170.19) --
+	(281.52,170.15) --
+	(281.16,170.02) --
+	(280.63,169.83) --
+	(280.60,169.82) --
+	(280.50,169.78) --
+	(280.47,169.77) --
+	(280.41,169.74) --
+	(280.36,169.72) --
+	(280.21,169.66) --
+	(279.90,169.53) --
+	(279.83,169.51) --
+	(279.36,169.37) --
+	(279.03,169.21) --
+	(278.99,169.19) --
+	(278.93,169.17) --
+	(278.83,169.13) --
+	(277.37,168.50) --
+	(277.28,168.47) --
+	(276.77,168.27) --
+	(276.73,168.26) --
+	(276.14,168.01) --
+	(276.03,167.96) --
+	(275.50,167.75) --
+	(274.88,167.47) --
+	(274.85,167.46) --
+	(274.31,167.26) --
+	(273.48,166.93) --
+	(273.29,166.85) --
+	(273.01,166.73) --
+	(272.91,166.69) --
+	(272.40,166.52) --
+	(272.31,166.47) --
+	(271.51,166.13) --
+	(269.91,165.51) --
+	(269.75,165.45) --
+	(269.30,165.26) --
+	(269.12,165.17) --
+	(268.75,165.01) --
+	(268.51,164.91) --
+	(268.32,164.82) --
+	(268.15,164.76) --
+	(267.95,164.70) --
+	(267.83,164.66) --
+	(267.74,164.62) --
+	(266.70,164.19) --
+	(266.69,164.18) --
+	(265.54,163.66) --
+	(265.48,163.64) --
+	(265.11,163.48) --
+	(264.94,163.41) --
+	(264.43,163.21) --
+	(264.14,163.10) --
+	(263.47,162.81) --
+	(262.57,162.32) --
+	(261.39,161.82) --
+	(260.16,161.24) --
+	(260.08,161.20) --
+	(258.99,160.73) --
+	(256.94,159.82) --
+	(255.73,159.30) --
+	(254.34,158.73) --
+	(253.89,158.52) --
+	(253.69,158.43) --
+	(252.46,157.87) --
+	(251.97,157.62) --
+	(250.69,156.98) --
+	(250.38,156.83) --
+	(250.22,156.75) --
+	(249.74,156.55) --
+	(248.30,155.93) --
+	(244.78,154.29) --
+	(242.95,153.43) --
+	(241.65,152.86) --
+	(241.27,152.70) --
+	(240.80,152.52) --
+	(240.03,152.13) --
+	(239.31,151.82) --
+	(239.29,151.81) --
+	(237.41,150.90) --
+	(237.40,150.89) --
+	(236.22,150.32) --
+	(235.24,149.84) --
+	(234.24,149.34) --
+	(233.34,148.91) --
+	(232.39,148.49) --
+	(231.34,148.01) --
+	(231.15,147.94) --
+	(229.14,146.99) --
+	(224.00,144.60) --
+	(223.59,144.41) --
+	(223.54,144.39) --
+	(223.29,144.27) --
+	(222.58,143.94) --
+	(221.63,143.45) --
+	(220.93,143.13) --
+	(220.33,142.84) --
+	(220.17,142.77) --
+	(218.17,141.73) --
+	(217.68,141.52) --
+	(217.43,141.39) --
+	(217.33,141.35) --
+	(215.87,140.66) --
+	(211.50,138.54) --
+	(209.65,137.60) --
+	(205.19,135.28) --
+	(204.99,135.19) --
+	(199.87,132.69) --
+	(198.04,131.73) --
+	(196.35,130.96) --
+	(195.71,130.66) --
+	(195.62,130.61) --
+	(192.71,129.05) --
+	(187.92,126.62) --
+	(178.49,121.82) --
+	(171.43,118.16) --
+	(158.01,111.25) --
+	(154.64,109.38) --
+	(110.88, 86.06) --
+	(101.92, 81.35) --
+	( 95.59, 78.11) --
+	( 92.34, 76.25) --
+	( 86.71, 73.22) --
+	( 78.30, 68.68) --
+	( 64.98, 61.27) --
+	( 64.85, 61.20) --
+	( 60.61, 58.86) --
+	( 52.97, 54.68) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (195.71, 34.03) -- (195.71, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (195.70, 34.03) -- (195.70, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (240.80, 34.03) -- (240.80, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (240.79, 34.03) -- (240.79, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.75, 34.03) -- (267.75, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.74, 34.03) -- (267.74, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (323.97, 34.03) -- (323.97, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (323.98, 34.03) -- (323.98, 41.32);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.53, 34.03) -- (342.53, 41.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.54, 34.03) -- (342.54, 41.32);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31, 54.28) {-5};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,133.28) {0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,212.28) {5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31, 55.16) {-5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,131.43) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 28.31,207.71) {5};
 \end{scope}

### 2016-01-23 LaTeX/TeX/Manuscript/Graphics/mCityCoefPlot.tex
reorg for final submission to jcr

% Created by tikzDevice version 0.8.1 on 2015-08-25 14:10:23
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,433.62);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (289.08,433.62);
\end{scope}
\begin{scope}
\path[clip] (131.47, 34.03) rectangle (277.03,421.57);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (131.47, 34.03) rectangle (277.03,421.57);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (209.22, 56.83) -- (219.44, 56.83);

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (209.01, 94.83) -- (210.36, 94.83);
\definecolor{drawColor}{RGB}{150,150,150}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (207.25,132.82) -- (210.68,132.82);
\definecolor{drawColor}{RGB}{222,45,38}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (175.44,170.81) -- (193.20,170.81);
\definecolor{drawColor}{RGB}{150,150,150}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (167.80,208.81) -- (270.42,208.81);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (211.19,246.80) -- (234.59,246.80);
\definecolor{drawColor}{RGB}{222,45,38}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (138.09,284.80) -- (186.49,284.80);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (209.68,322.79) -- (211.07,322.79);
\definecolor{drawColor}{RGB}{150,150,150}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (179.23,360.78) -- (215.85,360.78);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,draw opacity=0.30,line width= 0.3pt,line join=round] (212.56,398.78) -- (228.04,398.78);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 1.1pt,line join=round] (210.04, 56.83) -- (218.62, 56.83);

\path[draw=drawColor,line width= 1.1pt,line join=round] (209.12, 94.83) -- (210.26, 94.83);
\definecolor{drawColor}{gray}{0.59}

\path[draw=drawColor,line width= 1.1pt,line join=round] (207.52,132.82) -- (210.40,132.82);
\definecolor{drawColor}{RGB}{222,45,38}

\path[draw=drawColor,line width= 1.1pt,line join=round] (176.87,170.81) -- (191.77,170.81);
\definecolor{drawColor}{gray}{0.59}

\path[draw=drawColor,line width= 1.1pt,line join=round] (176.05,208.81) -- (262.17,208.81);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 1.1pt,line join=round] (213.07,246.80) -- (232.71,246.80);
\definecolor{drawColor}{RGB}{222,45,38}

\path[draw=drawColor,line width= 1.1pt,line join=round] (141.98,284.80) -- (182.60,284.80);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 1.1pt,line join=round] (209.79,322.79) -- (210.96,322.79);
\definecolor{drawColor}{gray}{0.59}

\path[draw=drawColor,line width= 1.1pt,line join=round] (182.18,360.78) -- (212.90,360.78);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 1.1pt,line join=round] (213.80,398.78) -- (226.79,398.78);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (209.00, 34.03) -- (209.00,421.57);
\definecolor{drawColor}{RGB}{54,144,192}
\definecolor{fillColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (220.30,398.78) circle (  2.85);
\definecolor{drawColor}{gray}{0.59}
\definecolor{fillColor}{gray}{0.59}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (197.54,360.78) circle (  2.85);
\definecolor{drawColor}{RGB}{54,144,192}
\definecolor{fillColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (210.37,322.79) circle (  2.85);
\definecolor{drawColor}{RGB}{222,45,38}
\definecolor{fillColor}{RGB}{222,45,38}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.29,284.80) circle (  2.85);
\definecolor{drawColor}{RGB}{54,144,192}
\definecolor{fillColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (222.89,246.80) circle (  2.85);
\definecolor{drawColor}{gray}{0.59}
\definecolor{fillColor}{gray}{0.59}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (219.11,208.81) circle (  2.85);
\definecolor{drawColor}{RGB}{222,45,38}
\definecolor{fillColor}{RGB}{222,45,38}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.32,170.81) circle (  2.85);
\definecolor{drawColor}{gray}{0.59}
\definecolor{fillColor}{gray}{0.59}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.96,132.82) circle (  2.85);
\definecolor{drawColor}{RGB}{54,144,192}
\definecolor{fillColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.69, 94.83) circle (  2.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (214.33, 56.83) circle (  2.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (219.44, 54.93) --
	(219.44, 58.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] (219.44, 56.83) --
	(209.22, 56.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.22, 54.93) --
	(209.22, 58.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] (210.36, 92.93) --
	(210.36, 96.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (210.36, 94.83) --
	(209.01, 94.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.01, 92.93) --
	(209.01, 96.72);
\definecolor{drawColor}{gray}{0.59}

\path[draw=drawColor,line width= 0.6pt,line join=round] (210.68,130.92) --
	(210.68,134.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (210.68,132.82) --
	(207.25,132.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.25,130.92) --
	(207.25,134.72);
\definecolor{drawColor}{RGB}{222,45,38}

\path[draw=drawColor,line width= 0.6pt,line join=round] (193.20,168.91) --
	(193.20,172.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (193.20,170.81) --
	(175.44,170.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (175.44,168.91) --
	(175.44,172.71);
\definecolor{drawColor}{gray}{0.59}

\path[draw=drawColor,line width= 0.6pt,line join=round] (270.42,206.91) --
	(270.42,210.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (270.42,208.81) --
	(167.80,208.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (167.80,206.91) --
	(167.80,210.71);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 0.6pt,line join=round] (234.59,244.90) --
	(234.59,248.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (234.59,246.80) --
	(211.19,246.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.19,244.90) --
	(211.19,248.70);
\definecolor{drawColor}{RGB}{222,45,38}

\path[draw=drawColor,line width= 0.6pt,line join=round] (186.49,282.90) --
	(186.49,286.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (186.49,284.80) --
	(138.09,284.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] (138.09,282.90) --
	(138.09,286.70);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.07,320.89) --
	(211.07,324.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.07,322.79) --
	(209.68,322.79);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.68,320.89) --
	(209.68,324.69);
\definecolor{drawColor}{gray}{0.59}

\path[draw=drawColor,line width= 0.6pt,line join=round] (215.85,358.88) --
	(215.85,362.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] (215.85,360.78) --
	(179.23,360.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (179.23,358.88) --
	(179.23,362.68);
\definecolor{drawColor}{RGB}{54,144,192}

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.04,396.88) --
	(228.04,400.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.04,398.78) --
	(212.56,398.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (212.56,396.88) --
	(212.56,400.68);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (131.47, 34.03) --
	(131.47,421.57);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (124.36, 53.53) {World GDP Growth$_{t}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (124.36, 91.52) {Resource Rents/GDP$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (124.36,129.51) {Democracy$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (124.36,167.51) {Ln(Inflation)$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (124.36,205.50) {Upper Income};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (124.36,243.50) {Number of conflicts$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (124.36,281.49) {Area$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (124.36,319.48) {Duration$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (124.36,357.48) {Intensity$_{t-1}$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at (124.36,395.47) {Ln(Min. City Dist.)$_{t-1}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (131.47, 34.03) --
	(277.03, 34.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (132.00, 20.31) {-8};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (170.50, 20.31) {-4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (209.00, 20.31) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (247.49, 20.31) {4};
\end{scope}
\end{tikzpicture}

### 2016-01-23 LaTeX/TeX/Manuscript/RhodiumIntro.tex
reorg for final submission to jcr

--- 2015-08-18 LaTeX/RhodiumIntro.tex
@@
 Mexico has been engaged in a drug war since December 2006 and the number of deaths stemming from this civil conflict have only increased since that time.
-Yet, even as fatalities due to the drug war reached new peaks, in 2012, Vikram Pandit of Citigroup cited Mexico as being extremely well poised for growth and projected that its economy may surpass that of its much larger regional rival, Brazil, within a decade \citep{vardi:2012}.
+Yet, even as fatalities due to the drug war reached new peaks in 2012, Vikram Pandit of Citigroup cited Mexico as being extremely well poised for growth and projected that its economy may surpass that of its much larger regional rival, Brazil, within a decade \citep{vardi:2012}.
 In that same year, \emph{Barron's} ran a headline titled, ``Is Mexico the New China?'' \citep{kapadia:2012}.
@@
 What happens when cities themselves are threatened?
-In this paper, we bridge the economic development literature on the importance of cities with extant literature on the effect of armed conflict to provide a novel explanation for the paradox of high macroeconomic growth in conflict ridden countries.
+In this paper, we bridge the economic development literature on the importance of cities with extant literature on the effect of armed conflict to provide a novel explanation for the paradox of high macroeconomic growth in conflict-ridden countries.
 Specifically, we argue that to explain variation in economic performance between countries in the midst of civil war, it is necessary to account for the spatial location of the conflict relative to major urban centers.

### 2016-01-23 LaTeX/TeX/OnlineAppendix/EnemyAtTheGates_MinhasRadford_OnlineAppendix.tex
reorg for final submission to jcr

--- 2016-01-23 LaTeX/EnemyAtTheGates_MinhasRadford_OnlineAppendix.tex
@@
 \email{benjamin.radford@duke.edu}
-
-% \thanks{We are grateful for comments on earlier versions of this paper received at the 72$^{nd}$ annual Midwest Political Science Association Conference in Chicago, April 2-6 2014. }
-
 % ----------------------------------------------- %
@@
 
-% easy commands for number propers
-\makeatletter
-\def\input@path{{/Users/janus829/Dropbox/Research/Rhodium/Graphics/}, {/Users/Ben/Dropbox/Rhodium/Graphics/}, {/Users/s7m/Dropbox/Research/Rhodium/Graphics/}, {C:/Users/Ben/Dropbox/Rhodium/Graphics}}
-\makeatother
-\graphicspath{{/Users/janus829/Dropbox/Research/Rhodium/Graphics/}, {/Users/Ben/Dropbox/Rhodium/Graphics/}, {/Users/s7m/Dropbox/Research/Rhodium/Graphics/}, {C:/Users/Ben/Dropbox/Rhodium/Graphics/}}
+% % graphic refs
+% \makeatletter
+% \def\input@path{{/Users/janus829/Dropbox/Research/Rhodium/Graphics/}, {/Users/Ben/Dropbox/Rhodium/Graphics/}, {/Users/s7m/Dropbox/Research/Rhodium/Graphics/}, {C:/Users/Ben/Dropbox/Rhodium/Graphics}}
+% \makeatother
+% \graphicspath{{/Users/janus829/Dropbox/Research/Rhodium/Graphics/}, {/Users/Ben/Dropbox/Rhodium/Graphics/}, {/Users/s7m/Dropbox/Research/Rhodium/Graphics/}, {C:/Users/Ben/Dropbox/Rhodium/Graphics/}}
 
@@
 \begin{document}
-% Wordcount: 9814
 \maketitle
@@
 	\centering
-	\includegraphics[width=.45\textwidth]{colombiaMap-crop}
+	\includegraphics[width=.45\textwidth]{Graphics/colombiaMap-crop}
 	\caption{This map illustrates the geographic distribution of all conflict centroids in Colombia, according to the PRIO Conflict Site Dataset, and major cities from 1989 to 2008.}
@@
 	\centering
-	\includegraphics[width=.5\textwidth]{indiaMap-crop}
+	\includegraphics[width=.5\textwidth]{Graphics/indiaMap-crop}
 	\caption{This map illustrates the geographic distribution of all conflict centroids in India, according to the PRIO Conflict Site Dataset, and major cities from 1989 to 2007. }
@@
 
-\input{capminDistRegMain.tex}
+\input{Graphics/capminDistRegMain.tex}
 
@@
 
-\input{acledModels.tex}
+\input{Graphics/acledModels.tex}
 \FloatBarrier
@@
 
-\input{modelHiLoIntensity.tex}
+\input{Graphics/modelHiLoIntensity.tex}
 \FloatBarrier
@@
 
-% \bibliographystyle{elsarticle-harv} 
 \bibliographystyle{jpr}

### 2016-01-23 R/Analysis/gdpGr_minDist.R

@@ -11,7 +11,7 @@ slice$lnminDist.min = log(slice$minDist.min + 1)
 slice$lnminDist.min[is.na(slice$lnminDist.min)] = 0
 
 cntryData = slice[slice$ccode==100,]
-library(gridExtra)
+loadPkg('gridExtra')
 gdpTime = ggplot(cntryData, aes(x=year, y=gdpGr)) + geom_line()
 distTime = ggplot(cntryData, aes(x=year, y=minDist.min)) + geom_bar(stat='identity')
 grid.arrange(gdpTime, distTime)

### 2016-01-23 R/Replication/onlineAppendixScripts/setup.R
add pkg version note

@@ -19,7 +19,7 @@ loadPkg=function(toLoad){
 
 pks = c('ggplot2', 'grid', 'cshapes','tikzDevice',
   'RColorBrewer', 'stargazer', 'reshape', 'countrycode',
-  'foreign', 'doBy', 'lme4', 'plm', 'MASS', 'latex2exp')
+  'foreign', 'doBy', 'lme4', 'plm', 'MASS')
 loadPkg(pks)
 
 # gg theme

### 2016-01-23 R/Replication/runReplication.R

@@ -1,13 +1,29 @@
-# # Run to replicate figures and tables in paper
-# # To correctly print math in pictures, save output using tikz from tikzDevice pkg instead of ggsave
-# print('Creating Figure 1......'); source('paperScripts/Figure1.R')
-# print('Creating Figure 2......'); source('paperScripts/Figure2.R')
-# print('Creating Figure 3 & Table 1......'); source('paperScripts/Figure3_Table1.R')
-# print('Creating Figures 4 & 5......'); source('paperScripts/Figures4-5.R')
-# print('Creating Tables 2 & 3......'); source('paperScripts/Tables2-3.R')
+# Run to replicate figures and tables in paper
+# To correctly print math in pictures, save output using tikz from tikzDevice pkg instead of ggsave
+print('Creating Figure 1......'); source('paperScripts/Figure1.R')
+print('Creating Figure 2......'); source('paperScripts/Figure2.R')
+print('Creating Figure 3 & Table 1......'); source('paperScripts/Figure3_Table1.R')
+print('Creating Figures 4 & 5......'); source('paperScripts/Figures4-5.R')
+print('Creating Tables 2 & 3......'); source('paperScripts/Tables2-3.R')
 
 # # Run to replicate figures and tables in appendix
 print('Creating Online Appendix Figures 1 & 2......'); source('onlineAppendixScripts/Figures1-2.R')
-# print('Creating Online Appendix Table 1......'); source('onlineAppendixScripts/Table1.R')
-# print('Creating Online Appendix Table 2......'); source('onlineAppendixScripts/Table2.R')
-# print('Creating Online Appendix Table 3......'); source('onlineAppendixScripts/Table3.R')
+print('Creating Online Appendix Table 1......'); source('onlineAppendixScripts/Table1.R')
+print('Creating Online Appendix Table 2......'); source('onlineAppendixScripts/Table2.R')
+print('Creating Online Appendix Table 3......'); source('onlineAppendixScripts/Table3.R')
+
+### Please note package versions
+#              Package        Version 
+# ggplot2      "ggplot2"      "2.0.0" 
+# grid         "grid"         "3.2.2" 
+# cshapes      "cshapes"      "0.5-1" 
+# tikzDevice   "tikzDevice"   "0.8.1" 
+# RColorBrewer "RColorBrewer" "1.1-2" 
+# stargazer    "stargazer"    "5.2"   
[…]
